### 2016-02-08 main_paper.tex

\documentclass[12pt,fleqn]{article}
\input{VERSION}
\input{tex/setup}

\title{Bootstrap confidence intervals for regression discontinuity estimators
  with the uniform kernel}
\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He}

\begin{document}
\maketitle

\begin{abstract}
This paper proves some results.
\end{abstract}

\section{Introduction}

Our results are great and everyone, everywhere, should use them.

\end{document}

### 2016-02-13 main_paper.tex
Introduction for the basic paper.

@@
 \section{Introduction}
+Regression Discontinuity (RD) designs have emerged in the last decade as an 
+important and popular identification strategy to analyze the impact of policies
+and interventions in several fields of the social sciences, including economics,
+political science, public policy, sociology among others.
 
-Our results are great and everyone, everywhere, should use them.
+The strategy exploits arbitrary rules used to assign treatment to units, usually
+relying on some type of ``score,'' the so called running variable. In its basic 
+version, units with score above a certain treshold receive treatment while the 
+ones below that cutoff are left untreated.
+
+The identification of the treatment effect at the treshold is then based on 
+comparing treated and untreated units at the cutoff. As a practical matter this 
+involves comparing units within a bandwidth just above and just below the 
+treshold. That comparison is most commonly done by implementing a local linear
+estimator above and below the cutoff within bandwidths chosen to minimize the 
+asymptotic mean squared error (AMSE) as proposed by Imbens and Kalyanaraman(2012)
+and extensions by Calonico, Cattaneo and Titiunik (2014).
+
+Recently, Calonico, Cattaneo and Titiunik (2014) brought attention to the fact
+that the popular implementation of RD designs coupling optimal-AMSE bandwidths
+and local polynomial estimation provides confidence intervals (CIs) with
+incorrect coverage due to the presence of bias and propose an explicit analytical
+bias correction procedure that re-centers and re-scale the CI by estimating a higher 
+order approximation of the bias term and adjustment its lenght to account for 
+the variation introduced by the bias estimation.
+
+As pointed out by Calonico, Cattaneo and Farrell (2015), ``(...)valid inference
+requires the delicate balancing act of selecting a bandwidth small enough
+to remove smoothing bias, yet large enough to ensure adequate precision.''
+The authors compare the strategies of undersmoothing, and explicit bias 
+correction concluding that direct bias-correction with the corresponding 
+rescalling of the CI's is a superior approach.
+
+This paper contributes to the bias-corrected RD literature by proposing a simple
+bootstrap procedure to correct the first order bias term and directly obtain 
+valid CIs that provide the correct coverage. The algorithm proposed is easy to
+implement and rely on the same conditions as the explicit bias correction
+proposed by Calonico, Cattaneo and Titiunik (2014).
+
+The novel bootstrap procedure is easy to implement and extends to RD designs 
+using higher order polynomials, producing valid CIs which are robust to 
+bandwidth choice and have similar properties to the analytical procedure in 
+Calonico, Cattaneo and Titiunik (2014) while sidestepping the need to derive 
+analytical formulas in each case of interest.
+
+The paper is organized as follows. Section \ref{background} describes the basic
+RD approach, its usual implementation, and the explicit analytical bias 
+correction approach in the literature. Section \ref{boot} presents the proposed 
+bootstrap bias corrected RD algorithm and discusses its properties. Simulation
+evidence that the bootstrap procedure provides valid CIs and its relative 
+performance to the analytical bias correction are presented in Section \ref{sim}.
+Finally, Section \ref{conclusion} concludes.
+
+\section{Background}\label{background}
+
+\section{Bootstrap Bias Correction}\label{boot}
+
+\section{Simulation Evidence}\label{sim}
+
+\section{Conclusion}\label{conclusion}
 

### 2016-02-14 main_paper.tex
Moving forward on Section 2

@@
 
-\title{Bootstrap confidence intervals for regression discontinuity estimators
-  with the uniform kernel}
-\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He}
+\title{Bootstrap Confidence Intervals for Regression Discontinuity Designs}
+\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{All authors: 
+Department of Economics, Iowa State University. 260 Heady Hall, Ames, IA  50011.
+Bartalotti: Email: bartalot@iastate.edu. Calhoun: gcalhoun@iastate.edu.
+He: yanghe@iastate.edu.}}
 
@@
 \section{Background}\label{background}
+In the typical sharp RD setting, a researcher wishes to estimate the local 
+causal effect of treatment at a given threshold. The running variable, $X_{i}$, 
+determines treatment assignment.  Given a known threshold, $\bar{x}$, set to 
+zero without loss of generality, a unit receives treatment if $X_{i} \geq 0$ or 
+does not receive treatment if $X_{i} < 0$. Let $Y_{i}(1)$ and $Y_{i}(0)$ denote 
+the potential outcomes for unit $i$ given it receives treatment and
+ in the absence of treatment, respectively. Hence, the observed sample is 
+ comprised of the running variable, $X_{i}$, and
+ \begin{align}
+  Y_{i}=Y_{i}(0) \mathbbm{1}\{X_{i}<0\}+Y_{i}(1) \mathbbm{1}\{X_{i} \geq 0\}
+ \end{align}
+where $\mathbbm{1}\{ \cdot\}$ denotes the indicator function. For convenience, 
+define
+ \begin{align}
+  \mu(x)= \mathbbm{E}[Y_{i}|X_{i}=x]
+ \end{align}
+Also, let $\mu^{(\eta)}(x)=\frac{d^{\eta}\mu(x)}{dx^{\eta}}$ be the $\eta^{th}$ 
+derivative of the unknown regression function and define 
+$\mu^{(\eta)}_{+}=lim_{x \rightarrow 0^{+}}\mu^{(\eta)}(x)$ and 
+$\mu^{(\eta)}_{-}=lim_{x \rightarrow 0^{-}}\mu^{(\eta)}(x)$.
+In most cases the population parameter of interest is 
+$\tau=\mathbbm{E}[Y(1)-Y(0)|X=\bar{x}]$ (i.e., the average treatment effect 
+at the threshold). Under continuity and smoothness conditions on both the 
+conditional distribution of $X_i$ and the first moments of $Y(0)$ and $Y(1)$ at
+the cutoff, $\tau$ is nonparametrically identifiable (Hahn, Todd and Van der 
+Klaauw, 2001) by:
+\begin{align}
+ \tau&= \mu_{+}- \mu_{-} \nonumber \\ 
+&\text{ where } \mu_{+}=lim_{x \rightarrow 0^{+}}\mu(x),\text{ and } 
+\mu_{-}=lim_{x \rightarrow 0^{-}}\mu(x)
+\end{align}
+
+Naturally, the estimation of $\tau$ in RD designs focuses on the 
+problem of approximating $\mathbbm{E}[Y(1)|X=x]$ and $\mathbbm{E}[Y(0)|X=x]$ 
+near the cutoff. Due to its desirable properties when estimating regression 
+functions at boundary points, we consider the popular approach of fitting 
+separate kernel-weighted local linear regressions in neighborhoods on both 
+sides of the threshold.\footnote{See \cite{HTV2001}, \cite{Porter03} or
+\cite{FanGijbels92} for discussions of the properties of local polynomial 
+regressions for boundary problems.The results presented here are valid for
+higher order polynomials and discontinuities at derivatives, like ``Kink RDD''
+in Card, Lee and Pei (2009). We focus on the linear case for ease in exposition.}
+For the local linear model, we use the following estimator as described in 
+Calonico, Cattaneo and Titiunik (2014)\footnote{Throughout the paper we follow the
+notation on Calonico, Cattaneo and Titiunik (2014) very closely.}
+\begin{align*}
+ \hat{\tau}(h_{n})&=\hat {\mu}_{+}(h_{n}) -\hat{\mu}_{-}(h_{n})\\
+(\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= argmin_{b_{0},b_{1}} 
+\sum_{i=1}^{N}\mathbbm{1}\{X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \cdot K_{h}(X_{i})\\
+(\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= argmin_{b_{0},b_{1}}
+\sum_{i=1}^{N}\mathbbm{1}\{X_{i} < 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2}\cdot K_{h}(X_{i})
+\end{align*}
+where $K_{h}(x_{i}) = K\left(\frac{x_{i}}{h}\right)\frac{1}{h}$.
 

### 2016-02-14 main_paper.tex
Add argmin operator to improve formatting and spacing
This commit adds 'argmin' and 'argmax' operators. It also creates a new file, 'macros.tex',
for other operator definitions.
Section 2, not quite happy with the result because it is not accessible to someone not used to the literature. I would like to know your opinion in terms of: (i) Do you think it would be ok to have  just a general description of what they do without having to go through the equations I have included now? I tried to make it as free of their equations as possible, but it still feels very terse. (ii) Do I need to get into

@@
 \input{tex/setup}
+\input{tex/macros}
 
-\title{Bootstrap Confidence Intervals for Regression Discontinuity Designs}
 \author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{All authors: 
@@
 \section{Background}\label{background}
+
 In the typical sharp RD setting, a researcher wishes to estimate the local 
@@
 For the local linear model, we use the following estimator as described in 
-Calonico, Cattaneo and Titiunik (2014)\footnote{Throughout the paper we follow the
-notation on Calonico, Cattaneo and Titiunik (2014) very closely.}
+\cite{calonico2014},\footnote{Throughout the paper we follow the
+notation on \cite{calonico2014} very closely.}
 \begin{align*}
@@
 
+As shown by \cite{HTV2001}, \cite{Porter03} and expanded by \cite{calonico2014} 
+identification and inference procedures can be developed based on the following 
+assumptions\footnote{The assumptions below are the same as presented by \cite{calonico2014}.}
+\begin{assumption}\label{A1}
+ For some $\kappa_{0} > 0$, the following holds in the neighborhood 
+ $(-\kappa_{0},\kappa_{0})$ around the cutoff $ \bar{x}= 0$:
+ \begin{enumerate}
+  \item $E[\left.Y_{i}^{4}\right|X_{i}=x]$ is bounded and the density of $X$, 
+  $f(x)$, is continuous and bounded away from zero.
+  \item $\mu_{+}(x)=\mathbbm{E}[\left.Y_{i}(1)\right|X_{i}=x]$ and $\mu_{-}(x)=
+  \mathbbm{E}[\left.Y_{i}(0)\right|X_{i}=x]$ are $S$ times continuously 
+  differentiable.
+  \item $\sigma^{2}_{+}(x)=\mathbbm{V}[\left.Y_{i}(1)\right|X_{i}=x]$ and 
+  $\sigma^{2}_{-}(x)=\mathbbm{V}[\left.Y_{i}(0)\right|X_{i}=x]$ are continuous 
+  and bounded away from zero.
+ \end{enumerate}
+\end{assumption}
+
+The conditions in Assumption \ref{A1} are the usual smoothness and existence 
+conditions in which the RD literature relies. Its second part is important for 
+the characterization of the leading bias term that will be the focus of the bias
+correction procedures described in \cite{calonico2014} and in the novel
+ bootstrap procedure proposed in Section \ref{boot}.
+
+The second set of assumptions regards the possible kernel weights used in RD.
+
+\begin{assumption}\label{A2}
+ For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa] \rightarrow 
+ \mathbbm{R}$ is bounded and nonnegative, zero outside its support, and positive
+ and continuous on $(0, \kappa)$.
+\end{assumption}
+
+Assumption \ref{A2} supports the kernels most commonly used in applications, in 
+particular the broadly used uniform kernel $k(u)=\mathbbm{1}[0\leq u\leq 1]$, 
+which simplifies to the use of a local linear OLS on both sides of the treshold.
+Since the objective of this paper is to present a simple bootstrap procedure to 
+obtain robust confidence intervals in the context of RD designs that can be 
+easily implemented by practitioners, during the remainder of the paper we focus 
+on estimators that use the rectangular kernel. The use of different weighting 
+structures implied by different kernels complicate the bootstrap algorithm in
+meaningful ways and such analysis is left to future work.
+
+\cite{calonico2014} point out that the conventional approaches to construct 
+confidence intervals for $\tau$ using the local linear estimator rely on a 
+large-sample approximation for the standardized $t$-statistic that is valid only
+if the bandwidth shrink fast enough to eliminate the leading bias term 
+contribution to the approximation. Hence, if $nh_{n}^{5}\rightarrow0$ and 
+$nh_{n}\rightarrow \infty$, then
+ \begin{align}
+  T(h_{n})=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1),
+  \text{        }V(h_{n})=\mathbbm{V}[\left.\tau(h_{n})\right|\chi_{n}],
+  \text{        }\chi_{n}=[X_{1}, \dots X_{n}]^{\prime}
+ \end{align}
+ The conditional variance $V(h_{n})$ depends on the $\sigma^{2}_{+}=
+ lim_{x \rightarrow 0^{+}}\sigma^{2}_{+}(x)$ and $\sigma^{2}_{-}=
+ lim_{x \rightarrow 0^{-}}\sigma^{2}_{-}(x)$ as well as $h_{n}$ and known 
+ quantities that depend on the kernel and order of polynomial used in the 
+ estimation. Under these conditions we could use a conventional confidence 
+ interval for $\tau$ given by
+ \begin{align}
+  I(h_{n})=\left[\hat{\tau}(h_{n})\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})} \right]
+ \end{align}
+with $\Phi^{-1}_{1-\frac{\alpha}{2}}$ being the $\alpha$-quantile of the 
+standard normal distribution. However, most approaches to select the bandwidth, 
+$h_{n}$ in the literature, including the widely used optimal-AMSE bandwidth 
+selector proposed by \cite{IK} lead to bandwidth choices that are ``too large'' 
+since they do not satisfy the condition $nh_{n}^{5}\rightarrow0$, leading to a 
+first-order bias in the distributional approximation used to construct the 
+confidence intervals.
+
+\cite{calonico2014} resolve the problem by deriving the analytical form of the 
+first-order bias and correcting it directly. To obtain correct coverage the 
+confidence interval needs not only to be recentered to correct the bias, but 
+also rescaled to allow for the additional variability introduced by the bias 
+correction. Their approach rely on obtaining a bias-corrected  estimator, 
+$\hat{\tau}^{bc}$ and its adjusted variance. It is important first to note that 
+the first-order bias term itself will depend on the bandwidth $h_{n}$. The 
+approximate bias term can be described as:
+\begin{align*}
+     E[\hat{\tau}(h_{n})|\chi_{n}]-\tau=& h_{n}^{2}\mathsf{B}(h_{n})\{1+o_{p}(1)\}\\
+     \mathsf{B}(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\mathfrak{B}_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\mathfrak{B}_{-}(h_{n})
+   \end{align*}
+where $\mathfrak{B}_{+}(h_{n})$ and $\mathfrak{B}_{-}(h_{n})$ are observed 
+quantities that depend on the data, kernel and $h_{n}$. The plug-in 
+bias-corrected estimator then requires estimates for the second derivatives of 
+the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and 
+$\mu_{-}^{(2)}$. \cite{calonico2014} propose using a conventional local quadratic
+estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,
+using a (potentially) different pilot bandwidth $b_{n}$.
+\begin{align*}
+     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\mathsf{B}}(h_{n},b_{n})\\
+     \hat{\mathsf{B}}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}
+     \mathfrak{B}_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\mathfrak{B}_{-}(h_{n})
+   \end{align*}
+By incorporating the contribution of both $\hat{\tau}(h_{n})$ and 
+$\hat{\mathsf{B}}(h_{n},b_{n})$ to the asymptotic distribution of the estimator,
+\cite{calonico2014} obtain a robust confidence interval with a different 
+asymptotic variance in general. So under Assumptions\ref{A1} and \ref{A2}, if 
+$n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and 
+$n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< 
+\kappa_{0}$, they show that
+\begin{align}
+  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1),
+  \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
+ \end{align}
+where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) 
+variability of the bias estimate used for correction as well as its correlation 
+with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the 
+formulas are currently ommitted from this paper since their form is not relevant
+to the bootstrap procedure innovation proposed. The details can be found at 
+\cite{calonico2014} Appendix}  Under these conditions we can construct a valid 
+confidence interval for $\tau$ given by
+ \begin{align}
+  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\mathsf{B}}
+  (h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}
+  (h_{n}, b_{n})} \right]
+ \end{align}
+
+This approach is shown by the authors to significantly coverage of the CIs 
+constructed and provides practitioners with a new toolset to perform inference 
+that is more robust to the choice of bandwidth. We build upon the insight 
+provided by \cite{calonico2014} bias-corrected estimator and propose a simple 
+bootstrap procedure that can directly construct the robust CIs without requiring
+the derivation of analytical formulas and direct estimators for the bias, 
+variance and covariance terms, while relying on the same first-order bias 
+correction approximation proposed by that paper.
+
 \section{Bootstrap Bias Correction}\label{boot}

### 2016-02-15 main_paper.tex
Draft for Abstract

@@
 \begin{abstract}
-This paper proves some results.
+This paper proposes an novel bootstrap procedure to obtain robust bias-corrected
+confidence intervals in regression discontinuity designs. The approach proposed 
+is based on a first-order bias correction and provides an alternative
+to the plug-in analytical methods proposed by Calonico, Cattaneo and Titiunik (2014).
+The algorithm is simple to implement and generates robust confidence intervals
+with improved coverage relative to the analytical alternatives in simulations.
 \end{abstract}

### 2016-02-15 main_paper.tex
Simulations

@@
 \section{Simulation Evidence}\label{sim}
+This section presents evidence from Monte Carlo simulations that the bootstrap bias correction procedures proposed in Section \ref{boot} produces valid, robust confidence intervals similar to the ones obtained by the analytical procedures established in \cite{calonico2014}.
+The bootstrap CIs obtained compare favourably to the analytical alternative, with coverage closer to the nominal size of the desired test and shorter lenght of the intervals in the specifications implemented.
+
+We selected three data generating processes (DGP) that are widely used in the RD literature to evaluate the performance of the proposed bootstrap procedure, those are the same chosen by \cite{calonico2014} and \cite{IK} and provide a good testing ground for bias correction due to their exacerbated curvature.
+To be specific, the pseudo data are generated as 500 i.i.d.
+draws from:
+\begin{align*}
+& Y_{i} = \mu_{j}(X_{i}) + \epsilon_{i}, \;\;\; X_{i} \sim  (2 B (2,4) - 1)), \\
+& \epsilon_{i} \sim N(0, \sigma^{2}), \;\;\; \sigma = 0.1295, \;\;\; j = 1,2,3.
+\end{align*}
+Three different choices of functional forms for $\mu_{j}(x)$ are as follows:
+\begin{align}
+\mu_{1}(x) & = 
+\begin{cases}
+0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}, \;\;\;\; & \text{if} \;\; x < 0, \\
+0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5},  & \text{if} \;\; x \ge 0.
+\end{cases}
+\\
+\mu_{2}(x) & = 
+\begin{cases}
+3.71 + 2.30x + 3.28x^2 + 1.45x^3 + 0.23x^4 + 0.03x^5, \;\; & \text{if} \;\; x < 0, \\
+0.26 + 18.49x - 54.81x^2 + 74.30x^3 - 45.02x^4 + 9.83x^5,  & \text{if} \;\; x \ge 0.
+\end{cases}
+\\
+\mu_{3}(x) & =
+\begin{cases}
+0.48 + 1.27x + 0.5 \times 7.18x^{2}+ \\
++ 0.7 \times 20.21x^3 + 1.1 \times 21.54x^4 + 1.5 \times 7.33x^5, \;\;\;\;\;\;\;\;\;\;\;\; & \text{if} \;\; x < 0, \\
+0.52 + 0.84x - 0.1 \times 3.00x^{2}+ \\
++ 0.3 \times 7.99x^3 - 0.1 \times 9.01x^4 + 3.56x^5, & \text{if} \;\; x \ge 0.
+\end{cases}
+\end{align}
+
+The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed by Lee (2008) and Ludwig and Miller (2007), respectively, while $\mu_{3}(x)$ is a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and therefore bias in the usual RD approach.
+For the simulation studies, we used 250 bootstraps for bias correction, 999 bootstraps to calculate confidence interval and a total 500 replications.
+All results presented are based on a 0.95 desired confidence level.
+Table \ref{Tb1} presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$).
+Table \ref{Tb2} presents similar results for $p=2$ and $q=3$.
+
+\begin{table}[ht] \label{Tb1}
+	\caption{Summary of estimates ($p = 1, q = 2$)}
+	\centering
+	\begin{tabular}{ccccccc}
+		\hline
+		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
+		\hline
+		\multicolumn{7}{c}{Panel A: Bootstrap Bias-Correction} \\
+		1 & 0.04 & -0.013 & 0.067 & 0.068 & 0.938 & 0.243 \\ 
+		2 & -3.45 & -0.014 & 0.083 & 0.084 & 0.954 & 0.319 \\ 
+		3 & 0.04 & -0.006 & 0.069 & 0.070 & 0.956 & 0.247 \\ 
+		&&&&&& \\
+		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
+		1 & 0.04 & -0.016 & 0.068 & 0.070 & 0.908 & 0.244 \\ 
+		2 & -3.45 & -0.014 & 0.092 & 0.093 & 0.928 & 0.350 \\ 
+		3 & 0.04 & -0.004 & 0.071 & 0.071 & 0.918 & 0.249 \\ 
+		\hline
+	\end{tabular}
+\end{table}
+
+\begin{table}[ht]\label{Tb2}
+	\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
+	\centering
+	\begin{tabular}{ccccccc}
+		\hline
+		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
+		\hline
+		\multicolumn{7}{c}{Panel A: Uniform Kernel} \\
+		1 & 0.04 & -0.002 & 0.075 & 0.075 & 0.958 & 0.295 \\ 
+		2 & -3.45 & 0.002 & 0.087 & 0.086 & 0.934 & 0.302 \\ 
+		3 & 0.04 & -0.008 & 0.083 & 0.083 & 0.942 & 0.292 \\ 
+		&&&&&& \\
+		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
+		1 & 0.04 & -0.004 & 0.082 & 0.082 & 0.926 & 0.295 \\ 		
+		2 & -3.45 & -0.005 & 0.078 & 0.078 & 0.960 & 0.323 \\ 		
+		3 & 0.04 & -0.003 & 0.080 & 0.080 & 0.938 & 0.295 \\ 
+		\hline
+	\end{tabular}
+\end{table}
 

### 2016-02-15 main_paper.tex
References
More references.

@@
 asymptotic mean squared error (AMSE) as proposed by Imbens and Kalyanaraman(2012)
-and extensions by Calonico, Cattaneo and Titiunik (2014).
+and extensions by \cite{calonico2014} (CCT, henceforth).
 
-Recently, Calonico, Cattaneo and Titiunik (2014) brought attention to the fact
-that the popular implementation of RD designs coupling optimal-AMSE bandwidths
+Recently, CCT brought attention to the fact that the popular implementation of RD designs coupling optimal-AMSE bandwidths
 and local polynomial estimation provides confidence intervals (CIs) with
@@
 
-As pointed out by Calonico, Cattaneo and Farrell (2015), ``(...)valid inference
+As pointed out by \cite{ccf2016}, ``(...)valid inference
 requires the delicate balancing act of selecting a bandwidth small enough
@@
 implement and rely on the same conditions as the explicit bias correction
-proposed by Calonico, Cattaneo and Titiunik (2014).
+proposed by CCT.
 
@@
 bandwidth choice and have similar properties to the analytical procedure in 
-Calonico, Cattaneo and Titiunik (2014) while sidestepping the need to derive 
-analytical formulas in each case of interest.
+CCT while sidestepping the need to derive analytical formulas in each case of interest.
 
@@
 regressions for boundary problems.The results presented here are valid for
-higher order polynomials and discontinuities at derivatives, like ``Kink RDD''
-in Card, Lee and Pei (2009). We focus on the linear case for ease in exposition.}
+higher order polynomials and discontinuities at derivatives, like ``Kink RDD.'' We focus on the linear case for ease in exposition.}
 For the local linear model, we use the following estimator as described in 
-\cite{calonico2014},\footnote{Throughout the paper we follow the
-notation on \cite{calonico2014} very closely.}
+CCT,\footnote{Throughout the paper we follow the notation on \cite{calonico2014} very closely.}
 \begin{align*}
@@
 
-As shown by \cite{HTV2001}, \cite{Porter03} and expanded by \cite{calonico2014} 
+As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT 
 identification and inference procedures can be developed based on the following 
-assumptions\footnote{The assumptions below are the same as presented by \cite{calonico2014}.}
+assumptions\footnote{The assumptions below are the same as presented by CCT.}
 \begin{assumption}\label{A1}
@@
 the characterization of the leading bias term that will be the focus of the bias
-correction procedures described in \cite{calonico2014} and in the novel
+correction procedures described in CCT and in the novel
  bootstrap procedure proposed in Section \ref{boot}.
@@
 
-\cite{calonico2014} point out that the conventional approaches to construct 
+CCT point out that the conventional approaches to construct 
 confidence intervals for $\tau$ using the local linear estimator rely on a 
@@
 
-\cite{calonico2014} resolve the problem by deriving the analytical form of the 
+CCT resolve the problem by deriving the analytical form of the 
 first-order bias and correcting it directly. To obtain correct coverage the 
@@
 the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and 
-$\mu_{-}^{(2)}$. \cite{calonico2014} propose using a conventional local quadratic
+$\mu_{-}^{(2)}$. CCT propose using a conventional local quadratic
 estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,
@@
 to the bootstrap procedure innovation proposed. The details can be found at 
-\cite{calonico2014} Appendix}  Under these conditions we can construct a valid 
+CCT Appendix}  Under these conditions we can construct a valid 
 confidence interval for $\tau$ given by
@@
 that is more robust to the choice of bandwidth. We build upon the insight 
-provided by \cite{calonico2014} bias-corrected estimator and propose a simple 
+provided by CCT bias-corrected estimator and propose a simple 
 bootstrap procedure that can directly construct the robust CIs without requiring
@@
 \section{Simulation Evidence}\label{sim}
-This section presents evidence from Monte Carlo simulations that the bootstrap bias correction procedures proposed in Section \ref{boot} produces valid, robust confidence intervals similar to the ones obtained by the analytical procedures established in \cite{calonico2014}.
-The bootstrap CIs obtained compare favourably to the analytical alternative, with coverage closer to the nominal size of the desired test and shorter lenght of the intervals in the specifications implemented.
+This section presents evidence from Monte Carlo simulations that the bootstrap 
+bias correction procedures proposed in Section \ref{boot} produces valid, robust
+confidence intervals similar to the ones obtained by the analytical procedures 
+established in CCT. The bootstrap CIs obtained compare favourably
+to the analytical alternative, with coverage closer to the nominal size of the 
+desired test and shorter lenght of the intervals in the specifications implemented.
 
-We selected three data generating processes (DGP) that are widely used in the RD literature to evaluate the performance of the proposed bootstrap procedure, those are the same chosen by \cite{calonico2014} and \cite{IK} and provide a good testing ground for bias correction due to their exacerbated curvature.
-To be specific, the pseudo data are generated as 500 i.i.d.
-draws from:
+We selected three data generating processes (DGP) that are widely used in the RD
+literature to evaluate the performance of the proposed bootstrap procedure, 
+those are the same chosen by CCT and \cite{IK} and provide a 
+good testing ground for bias correction due to their exacerbated curvature. 
+To be specific, the pseudo data are generated as 500 i.i.d. draws from:
 \begin{align*}
@@
 
-The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed by Lee (2008) and Ludwig and Miller (2007), respectively, while $\mu_{3}(x)$ is a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and therefore bias in the usual RD approach.
-For the simulation studies, we used 250 bootstraps for bias correction, 999 bootstraps to calculate confidence interval and a total 500 replications.
-All results presented are based on a 0.95 desired confidence level.
-Table \ref{Tb1} presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$).
-Table \ref{Tb2} presents similar results for $p=2$ and $q=3$.
+The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed 
+by by\cite{lee2008} and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is
+a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and 
+therefore bias in the usual RD approach. For the simulation studies, we used 
+250 bootstraps for bias correction, 999 bootstraps to calculate confidence 
+interval and a total 500 replications. All results presented are based on a 
+0.95 desired confidence level. Table \ref{Tb1} presents the main results in which
+a local-linear RD estimator ($p=1$) is employed with the bias-correction based 
+on a local-quadratic approximation ($q=2$). Table \ref{Tb2} presents similar 
+results for $p=2$ and $q=3$.
 
 \begin{table}[ht] \label{Tb1}
-	\caption{Summary of estimates ($p = 1, q = 2$)}
+	\caption{Summary of Results ($p = 1, q = 2$)}
 	\centering
@@
 \begin{table}[ht]\label{Tb2}
-	\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
+	\caption{Summary of Results ($p = 2, q = 3$)}
 	\centering
@@
 
+As can be seen on the tables above, the bootstrap bias-correction procedure
+proposed in this paper provides a simple alternative to obtain valid robust
+confidence intervals in RD designs and performs well compared to the analytical 
+bias correction procedures proposed by CCT.
+
 \section{Conclusion}\label{conclusion}
 
+%%%%%REFERENCES%%%%%%%%%
+\clearpage
+\bibliographystyle{jpe}
+\bibliography{bootrd}
+
 \end{document}

### 2016-02-15 main_paper.tex
Description of the Algorithm.

@@
 \section{Bootstrap Bias Correction}\label{boot}
+Building upon the results and intuition developed by CCT we propose to implement a first-order bias correction and obtain valid CIs through a bootstrap procedure.
+Intuitively, for the local-linear RD estimator's case, we will rely on a local higher-order (quadratic) polynomial approximation for the conditional outcome around the cutoff to capture the potential bias present in the original RD estimate.
+This insight comes directly from CCT using the same local quadratic approximation to estimate bias term as presented in Section \ref{background}.
+
+The first algorithm describes how to use local linear regression to obtain a point estimate and perform bias correction with local quadratic regression.
+The second algorithm describes how to obtain its confidence interval with correct coverage.
+For simplicity, we adopt the same optimal-AMSE bandwidth selector proposed by CCT.\footnote{An interesting question is whether one could use a bootstrap based procedure to select a bandwidth that would achieve similar (or improved) results.
+This is beyond the scope of this particular paper but is part of ongoing research effort.}
+
+Essentially, we apply CCT's insight that a polynomial one order higher can capture the first-order bias behavior an create a bootstrap procedure that can correctly mimic the behavior of the bias present in the original estimator.
+For such, for a chosen bandwidth, we estimate a local quadratic regression the same way CCT suggested but then create bootstrap data by imposing the local quadratic functional form as the DGP.
+Then, in the ``bootstrap data'' the DGP is known.
+Let the ``true'' treatment effect under the bootstrap DGP be denoted by $\tau^{*}$.
+We then estimate the treatment effect using the (misspecified) local linear estimator, $\hat{\tau}^{*}$ to the generated data.
+Hence, the bias for a specific bootstrap data is given by $\tau^{*}-\hat{\tau}^{*}$.
+More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\mathsf{B}}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates,i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
+Algorithm 1 describes this procedure step-by-step for clarity.
+
+\textbf{Algorithm 1}: Bootstrap Bias Corrected Point Estimator
+ \begin{enumerate}
+	\item Obtain bandwidths for both local linear and quadratic regressions $(h_{n}, b_{n})$ using CCT bandwidth choice algorithm procedure.
+	\item Estimate local linear regression on both sides of cutoff using bandwidth from step 1 and calculate $\hat{\tau}(h_{n})$.
+	\item Estimate local quadratic regression on both sides of cutoff using bandwidth $b_{n}$ from step 1 and calculate $\tau^{*}$, the difference of two regression functions evaluated at cutoff.
+	\item Generate bootstrap data $[Y^{*},\chi^{*}]$ imposing the DGP and and residual's distribution estimated in Step 3 on each sides of cutoff.
+	\item Apply step 2 on bootstrap data and obtain $\hat{\tau}^{*}$.
+	\item Repeat step 4 and 5 for $B$ times and the bias corrected point estimate is given by $\hat{\tau}^{bc}=\hat{\tau} + \tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
+ \end{enumerate}
+
+With Algorithm 1 at hand, we can move to generate the bias-corrected confidence intervals to perform inference about $\tau$.
+Here the idea is similar, but now we actually calculate a fully bias corrected estimate using Algorithm 1 for every bootstrapped dataset generated, a bootstrap within the bootstrap.
+Each one of the bias corrected estimates for the generated data is denoted $\hat{\tau}^{bc*}$.
+These estimator's empirical distribution capture the variability induced by the first order bias correction that lead CCT to propose the rescaling of their confidence intervals by introducing $C^{bc}(h_{n},b_{n})$ in the asymptotic variance formula on Section \ref{background}.
+
+\textbf{Algorithm 2}: Confidence Interval
+ \begin{enumerate}
+	\item Obtain bandwidths for both local linear and quadratic regressions $(h_{n}, b_{n})$ using CCT bandwidth choice algorithm procedure.
+	\item Estimate local quadratic regression on both sides of cutoff using bandwidth $b_{n}$ from step 1.
+	\item Generate bootstrap data $[Y^{*},\chi^{*}]$ imposing the DGP and and residual's distribution estimated in Step 2 on each sides of cutoff.
+	\item Apply Algorithm 1 (starting at step 2) to bootstrap data generated in step 3 and obtain bias corrected estimate $\hat{\tau}^{bc*}$.
+	\item Repeat step 3 and 4 for $B$ times and obtain confidence interval formed by the $\frac{\alpha}{2}$ and $\left(1-\frac{\alpha}{2}\right)$ percentiles of the empirical distribution of $\hat{\tau}^{bc*}$ .
+ \end{enumerate}
+
+Evidence of the usefulness of the procedures proposed above and their relative 
+performance to the analytical bias correction proposed in CCT are presented in a
+series of Monte Carlo simulations in Section \ref{sim}.
 

### 2016-02-15 main_paper.tex
Conclusion

@@
 
+\title{Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels}
 \author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{All authors: 
@@
 relying on some type of ``score,'' the so called running variable. In its basic 
-version, units with score above a certain treshold receive treatment while the 
+version, units with score above a certain threshold receive treatment while the 
 ones below that cutoff are left untreated.
 
-The identification of the treatment effect at the treshold is then based on 
+The identification of the treatment effect at the threshold is then based on 
 comparing treated and untreated units at the cutoff. As a practical matter this 
@@
 correction concluding that direct bias-correction with the corresponding 
-rescalling of the CI's is a superior approach.
+rescaling of the CI's is a superior approach.
 
@@
 regressions for boundary problems.The results presented here are valid for
-higher order polynomials and discontinuities at derivatives, like ``Kink RDD.'' We focus on the linear case for ease in exposition.}
+higher order polynomials and discontinuities at derivatives, like ``Kink RDD''. We focus on the linear case for ease in exposition.}
 For the local linear model, we use the following estimator as described in 
-CCT,\footnote{Throughout the paper we follow the notation on \cite{calonico2014} very closely.}
+\cite{calonico2014},\footnote{Throughout the paper we follow the
+notation on CCT very closely.}
 \begin{align*}
@@
 
-As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT 
-identification and inference procedures can be developed based on the following 
-assumptions\footnote{The assumptions below are the same as presented by CCT.}
+As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT identification and inference procedures can be developed based on the following assumptions\footnote{The assumptions below are the same as presented by CCT.}
 \begin{assumption}\label{A1}
- For some $\kappa_{0} > 0$, the following holds in the neighborhood 
- $(-\kappa_{0},\kappa_{0})$ around the cutoff $ \bar{x}= 0$:
+ For some $\kappa_{0} > 0$, the following holds in the neighborhood $(-\kappa_{0},\kappa_{0})$ around the cutoff $ \bar{x}= 0$:
  \begin{enumerate}
-  \item $E[\left.Y_{i}^{4}\right|X_{i}=x]$ is bounded and the density of $X$, 
-  $f(x)$, is continuous and bounded away from zero.
-  \item $\mu_{+}(x)=\mathbbm{E}[\left.Y_{i}(1)\right|X_{i}=x]$ and $\mu_{-}(x)=
-  \mathbbm{E}[\left.Y_{i}(0)\right|X_{i}=x]$ are $S$ times continuously 
-  differentiable.
-  \item $\sigma^{2}_{+}(x)=\mathbbm{V}[\left.Y_{i}(1)\right|X_{i}=x]$ and 
-  $\sigma^{2}_{-}(x)=\mathbbm{V}[\left.Y_{i}(0)\right|X_{i}=x]$ are continuous 
-  and bounded away from zero.
+  \item $E[\left.Y_{i}^{4}\right|X_{i}=x]$ is bounded and the density of $X$, $f(x)$, is continuous and bounded away from zero.
+  \item $\mu_{+}(x)=\mathbbm{E}[\left.Y_{i}(1)\right|X_{i}=x]$ and $\mu_{-}(x)=\mathbbm{E}[\left.Y_{i}(0)\right|X_{i}=x]$ are $S$ times continuously differentiable.
+  \item $\sigma^{2}_{+}(x)=\mathbbm{V}[\left.Y_{i}(1)\right|X_{i}=x]$ and $\sigma^{2}_{-}(x)=\mathbbm{V}[\left.Y_{i}(0)\right|X_{i}=x]$ are continuous and bounded away from zero.
  \end{enumerate}
@@
 
-The conditions in Assumption \ref{A1} are the usual smoothness and existence 
-conditions in which the RD literature relies. Its second part is important for 
-the characterization of the leading bias term that will be the focus of the bias
-correction procedures described in CCT and in the novel
- bootstrap procedure proposed in Section \ref{boot}.
+The conditions in Assumption \ref{A1} are the usual smoothness and existence conditions in which the RD literature relies.
+Its second part is important for the characterization of the leading bias term that will be the focus of the bias correction procedures described in CCT and in the novel  bootstrap procedure proposed in Section \ref{boot}.
 
@@
 \begin{assumption}\label{A2}
- For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa] \rightarrow 
- \mathbbm{R}$ is bounded and nonnegative, zero outside its support, and positive
- and continuous on $(0, \kappa)$.
+ For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa] \rightarrow \mathbbm{R}$ is bounded and nonnegative, zero outside its support, and positive and continuous on $(0, \kappa)$.
 \end{assumption}
 
-Assumption \ref{A2} supports the kernels most commonly used in applications, in 
-particular the broadly used uniform kernel $k(u)=\mathbbm{1}[0\leq u\leq 1]$, 
-which simplifies to the use of a local linear OLS on both sides of the treshold.
-Since the objective of this paper is to present a simple bootstrap procedure to 
-obtain robust confidence intervals in the context of RD designs that can be 
-easily implemented by practitioners, during the remainder of the paper we focus 
-on estimators that use the rectangular kernel. The use of different weighting 
-structures implied by different kernels complicate the bootstrap algorithm in
-meaningful ways and such analysis is left to future work.
+Assumption \ref{A2} supports the kernels most commonly used in applications, in particular the broadly used uniform kernel $k(u)=\mathbbm{1}[0\leq u\leq 1]$, which simplifies to the use of a local linear OLS on both sides of the treshold.
+Since the objective of this paper is to present a simple bootstrap procedure to obtain robust confidence intervals in the context of RD designs that can be easily implemented by practitioners, during the remainder of the paper we focus on estimators that use the rectangular kernel.
+The use of different weighting structures implied by different kernels complicate the bootstrap algorithm in meaningful ways and such analysis is left to future work.
 
-CCT point out that the conventional approaches to construct 
-confidence intervals for $\tau$ using the local linear estimator rely on a 
-large-sample approximation for the standardized $t$-statistic that is valid only
-if the bandwidth shrink fast enough to eliminate the leading bias term 
-contribution to the approximation. Hence, if $nh_{n}^{5}\rightarrow0$ and 
-$nh_{n}\rightarrow \infty$, then
+\cite{calonico2014} point out that the conventional approaches to construct confidence intervals for $\tau$ using the local linear estimator rely on a large-sample approximation for the standardized $t$-statistic that is valid only if the bandwidth shrink fast enough to eliminate the leading bias term contribution to the approximation.
+Hence, if $nh_{n}^{5}\rightarrow0$ and $nh_{n}\rightarrow \infty$, then
  \begin{align}
-  T(h_{n})=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1),
-  \text{        }V(h_{n})=\mathbbm{V}[\left.\tau(h_{n})\right|\chi_{n}],
-  \text{        }\chi_{n}=[X_{1}, \dots X_{n}]^{\prime}
+  T(h_{n})=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), \text{        }V(h_{n})=\mathbbm{V}[\left.\tau(h_{n})\right|\chi_{n}], \text{        }\chi_{n}=[X_{1}, \dots X_{n}]^{\prime}
  \end{align}
- The conditional variance $V(h_{n})$ depends on the $\sigma^{2}_{+}=
- lim_{x \rightarrow 0^{+}}\sigma^{2}_{+}(x)$ and $\sigma^{2}_{-}=
- lim_{x \rightarrow 0^{-}}\sigma^{2}_{-}(x)$ as well as $h_{n}$ and known 
- quantities that depend on the kernel and order of polynomial used in the 
- estimation. Under these conditions we could use a conventional confidence 
- interval for $\tau$ given by
+ The conditional variance $V(h_{n})$ depends on the $\sigma^{2}_{+}=lim_{x \rightarrow 0^{+}}\sigma^{2}_{+}(x)$ and $\sigma^{2}_{-}=lim_{x \rightarrow 0^{-}}\sigma^{2}_{-}(x)$ as well as $h_{n}$ and known quantities that depend on the kernel and order of polynomial used in the estimation.
+Under these conditions we could use a conventional confidence interval for $\tau$ given by
  \begin{align}
@@
  \end{align}
-with $\Phi^{-1}_{1-\frac{\alpha}{2}}$ being the $\alpha$-quantile of the 
-standard normal distribution. However, most approaches to select the bandwidth, 
-$h_{n}$ in the literature, including the widely used optimal-AMSE bandwidth 
-selector proposed by \cite{IK} lead to bandwidth choices that are ``too large'' 
-since they do not satisfy the condition $nh_{n}^{5}\rightarrow0$, leading to a 
-first-order bias in the distributional approximation used to construct the 
-confidence intervals.
+with $\Phi^{-1}_{1-\frac{\alpha}{2}}$ being the $\alpha$-quantile of the standard normal distribution.
+However, most approaches to select the bandwidth, $h_{n}$ in the literature, including the widely used optimal-AMSE bandwidth selector proposed by \cite{IK} lead to bandwidth choices that are ``too large'' since they do not satisfy the condition $nh_{n}^{5}\rightarrow0$, leading to a first-order bias in the distributional approximation used to construct the confidence intervals.
 
-CCT resolve the problem by deriving the analytical form of the 
-first-order bias and correcting it directly. To obtain correct coverage the 
-confidence interval needs not only to be recentered to correct the bias, but 
-also rescaled to allow for the additional variability introduced by the bias 
-correction. Their approach rely on obtaining a bias-corrected  estimator, 
-$\hat{\tau}^{bc}$ and its adjusted variance. It is important first to note that 
-the first-order bias term itself will depend on the bandwidth $h_{n}$. The 
-approximate bias term can be described as:
+\cite{calonico2014} resolve the problem by deriving the analytical form of the first-order bias and correcting it directly.
+To obtain correct coverage the confidence interval needs not only to be re-centered to correct the bias, but also rescaled to allow for the additional variability introduced by the bias correction.
+Their approach rely on obtaining a bias-corrected  estimator, $\hat{\tau}^{bc}$ and its adjusted variance.
+It is important first to note that the first-order bias term itself will depend on the bandwidth $h_{n}$.
+The approximate bias term can be described as:
 \begin{align*}
@@
    \end{align*}
-where $\mathfrak{B}_{+}(h_{n})$ and $\mathfrak{B}_{-}(h_{n})$ are observed 
-quantities that depend on the data, kernel and $h_{n}$. The plug-in 
-bias-corrected estimator then requires estimates for the second derivatives of 
-the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and 
-$\mu_{-}^{(2)}$. CCT propose using a conventional local quadratic
-estimator, i.e. one order higher than the polynomial used to obtain $\hat{\tau}$,
-using a (potentially) different pilot bandwidth $b_{n}$.
+where $\mathfrak{B}_{+}(h_{n})$ and $\mathfrak{B}_{-}(h_{n})$ are observed quantities that depend on the data, kernel and $h_{n}$.
+The plug-in bias-corrected estimator then requires estimates for the second derivatives of the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$.
+CCT propose using a conventional local quadratic estimator, i.e.
+one order higher than the polynomial used to obtain $\hat{\tau}$,  using a (potentially) different pilot bandwidth $b_{n}$.
 \begin{align*}
      \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\mathsf{B}}(h_{n},b_{n})\\
-     \hat{\mathsf{B}}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}
-     \mathfrak{B}_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\mathfrak{B}_{-}(h_{n})
+     \hat{\mathsf{B}}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}\mathfrak{B}_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\mathfrak{B}_{-}(h_{n})
    \end{align*}
-By incorporating the contribution of both $\hat{\tau}(h_{n})$ and 
-$\hat{\mathsf{B}}(h_{n},b_{n})$ to the asymptotic distribution of the estimator,
-\cite{calonico2014} obtain a robust confidence interval with a different 
-asymptotic variance in general. So under Assumptions\ref{A1} and \ref{A2}, if 
-$n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and 
-$n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< 
-\kappa_{0}$, they show that
+By incorporating the contribution of both $\hat{\tau}(h_{n})$ and $\hat{\mathsf{B}}(h_{n},b_{n})$ to the asymptotic distribution of the estimator, CCT obtain a robust confidence interval with a different asymptotic variance in general.
+So under Assumptions\ref{A1} and \ref{A2}, if $n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and $n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< \kappa_{0}$, they show that
 \begin{align}
-  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1),
-  \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
+  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1), \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
  \end{align}
-where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) 
-variability of the bias estimate used for correction as well as its correlation 
-with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the 
-formulas are currently ommitted from this paper since their form is not relevant
-to the bootstrap procedure innovation proposed. The details can be found at 
-CCT Appendix}  Under these conditions we can construct a valid 
-confidence interval for $\tau$ given by
+where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) variability of the bias estimate used for correction as well as its correlation with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the formulas are currently ommitted from this paper since their form is not relevant to the bootstrap procedure innovation proposed.
+The details can be found at CCT Appendix}  Under these conditions we can construct a valid confidence interval for $\tau$ given by
  \begin{align}
-  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\mathsf{B}}
-  (h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}
-  (h_{n}, b_{n})} \right]
+  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\mathsf{B}}(h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}(h_{n}, b_{n})} \right]
  \end{align}
 
-This approach is shown by the authors to significantly coverage of the CIs 
-constructed and provides practitioners with a new toolset to perform inference 
-that is more robust to the choice of bandwidth. We build upon the insight 
-provided by CCT bias-corrected estimator and propose a simple 
-bootstrap procedure that can directly construct the robust CIs without requiring
-the derivation of analytical formulas and direct estimators for the bias, 
-variance and covariance terms, while relying on the same first-order bias 
-correction approximation proposed by that paper.
+This approach is shown by the authors to significantly coverage of the CIs constructed and provides practitioners with a new tool set to perform inference that is more robust to the choice of bandwidth.
+We build upon the insight provided by CCT bias-corrected estimator and propose a simple bootstrap procedure that can directly construct the robust CIs without requiring the derivation of analytical formulas and direct estimators for the bias, variance and covariance terms, while relying on the same first-order bias correction approximation proposed by that paper.
 
 \section{Bootstrap Bias Correction}\label{boot}
+
 Building upon the results and intuition developed by CCT we propose to implement a first-order bias correction and obtain valid CIs through a bootstrap procedure.
@@
 
-Evidence of the usefulness of the procedures proposed above and their relative 
-performance to the analytical bias correction proposed in CCT are presented in a
-series of Monte Carlo simulations in Section \ref{sim}.
+Evidence of the usefulness of the procedures proposed above and their relative performance to the analytical bias correction proposed in CCT are presented in a series of Monte Carlo simulations in Section \ref{sim}.
 
 \section{Simulation Evidence}\label{sim}
-This section presents evidence from Monte Carlo simulations that the bootstrap 
-bias correction procedures proposed in Section \ref{boot} produces valid, robust
-confidence intervals similar to the ones obtained by the analytical procedures 
-established in CCT. The bootstrap CIs obtained compare favourably
-to the analytical alternative, with coverage closer to the nominal size of the 
-desired test and shorter lenght of the intervals in the specifications implemented.
 
-We selected three data generating processes (DGP) that are widely used in the RD
-literature to evaluate the performance of the proposed bootstrap procedure, 
-those are the same chosen by CCT and \cite{IK} and provide a 
-good testing ground for bias correction due to their exacerbated curvature. 
-To be specific, the pseudo data are generated as 500 i.i.d. draws from:
+This section presents evidence from Monte Carlo simulations that the bootstrap bias correction procedures proposed in Section \ref{boot} produces valid, robust confidence intervals similar to the ones obtained by the analytical procedures established in CCT.
+The bootstrap CIs obtained compare favorably to the analytical alternative, with coverage closer to the nominal size of the desired test and shorter length of the intervals in the specifications implemented.
+
+We selected three data generating processes (DGP) that are widely used in the RD literature to evaluate the performance of the proposed bootstrap procedure, those are the same chosen by CCT and \cite{IK} and provide a good testing ground for bias correction due to their exacerbated curvature.
+To be specific, the pseudo data are generated as 500 i.i.d.
+draws from:
 \begin{align*}
@@
 
-The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed 
-by by\cite{lee2008} and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is
-a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and 
-therefore bias in the usual RD approach. For the simulation studies, we used 
-250 bootstraps for bias correction, 999 bootstraps to calculate confidence 
-interval and a total 500 replications. All results presented are based on a 
-0.95 desired confidence level. Table \ref{Tb1} presents the main results in which
-a local-linear RD estimator ($p=1$) is employed with the bias-correction based 
-on a local-quadratic approximation ($q=2$). Table \ref{Tb2} presents similar 
-results for $p=2$ and $q=3$.
+The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed by \cite{lee2008} and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and therefore bias in the usual RD approach.
+For the simulation studies, we used 250 bootstraps for bias correction, 999 bootstraps to calculate confidence interval and a total 500 replications.
+All results presented are based on a 0.95 desired confidence level.
+Table1 presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$).
+Table 2 presents similar results for $p=2$ and $q=3$.
 
 \begin{table}[ht] \label{Tb1}
-	\caption{Summary of Results ($p = 1, q = 2$)}
+	\caption{Summary of estimates ($p = 1, q = 2$)}
 	\centering
@@
 \begin{table}[ht]\label{Tb2}
-	\caption{Summary of Results ($p = 2, q = 3$)}
+	\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
 	\centering
@@
 \end{table}
-
 As can be seen on the tables above, the bootstrap bias-correction procedure
@@
 \section{Conclusion}\label{conclusion}
+This paper proposes an novel bootstrap procedure to obtain robust bias-corrected
+confidence intervals in regression discontinuity designs. 
+The approach proposed builds upon the developments and intuition advanced by CCT and is based on a first-order bias correction.
+Our procedure provides an alternative to the plug-in analytical methods in the literature and is simple to implement generating robust confidence intervals.
+Simulation evidence is presented that the proposed bootstrap bias correction and confidence intervals have improved coverage and shorter length relative to the analytical alternatives proposed by CCT.
 
@@
 \bibliography{bootrd}
-
 \end{document}

### 2016-02-15 main_paper.tex
Disclaimer
Fix minor typo

@@
 Bartalotti: Email: bartalot@iastate.edu. Calhoun: gcalhoun@iastate.edu.
-He: yanghe@iastate.edu.}}
+He: yanghe@iastate.edu.} \\ PRELIMINARY AND INCOMPLETE \\PLEASE DO NOT CITE OR CIRCULATE WITHOUT PERMISSION}
 
@@
 involves comparing units within a bandwidth just above and just below the 
-treshold. That comparison is most commonly done by implementing a local linear
+threshold. That comparison is most commonly done by implementing a local linear
 estimator above and below the cutoff within bandwidths chosen to minimize the 
 asymptotic mean squared error (AMSE) as proposed by Imbens and Kalyanaraman(2012)
-and extensions by \cite{calonico2014} (CCT, henceforth).
+and extended by \cite{calonico2014} (CCT, henceforth).
 
@@
 Since the objective of this paper is to present a simple bootstrap procedure to obtain robust confidence intervals in the context of RD designs that can be easily implemented by practitioners, during the remainder of the paper we focus on estimators that use the rectangular kernel.
-The use of different weighting structures implied by different kernels complicate the bootstrap algorithm in meaningful ways and such analysis is left to future work.
+The use of different weighting structures implied by different kernels complicates the bootstrap algorithm in meaningful ways and such analysis is left to future work.
 
@@
 To obtain correct coverage the confidence interval needs not only to be re-centered to correct the bias, but also rescaled to allow for the additional variability introduced by the bias correction.
-Their approach rely on obtaining a bias-corrected  estimator, $\hat{\tau}^{bc}$ and its adjusted variance.
+Their approach relies on obtaining a bias-corrected  estimator, $\hat{\tau}^{bc}$ and its adjusted variance.
 It is important first to note that the first-order bias term itself will depend on the bandwidth $h_{n}$.
@@
 By incorporating the contribution of both $\hat{\tau}(h_{n})$ and $\hat{\mathsf{B}}(h_{n},b_{n})$ to the asymptotic distribution of the estimator, CCT obtain a robust confidence interval with a different asymptotic variance in general.
-So under Assumptions\ref{A1} and \ref{A2}, if $n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and $n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< \kappa_{0}$, they show that
+So under Assumptions \ref{A1} and \ref{A2}, if $n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and $n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< \kappa_{0}$, they show that
 \begin{align}
@@
 where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) variability of the bias estimate used for correction as well as its correlation with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the formulas are currently ommitted from this paper since their form is not relevant to the bootstrap procedure innovation proposed.
-The details can be found at CCT Appendix}  Under these conditions we can construct a valid confidence interval for $\tau$ given by
+The details can be found at CCT Appendix.}  Under these conditions we can construct a valid confidence interval for $\tau$ given by
  \begin{align}
@@
 
-This approach is shown by the authors to significantly coverage of the CIs constructed and provides practitioners with a new tool set to perform inference that is more robust to the choice of bandwidth.
+This approach is shown by the authors to significantly improve coverage of the CIs constructed and provides practitioners with a new tool set to perform inference that is more robust to the choice of bandwidth.
 We build upon the insight provided by CCT bias-corrected estimator and propose a simple bootstrap procedure that can directly construct the robust CIs without requiring the derivation of analytical formulas and direct estimators for the bias, variance and covariance terms, while relying on the same first-order bias correction approximation proposed by that paper.
@@
 
-Essentially, we apply CCT's insight that a polynomial one order higher can capture the first-order bias behavior an create a bootstrap procedure that can correctly mimic the behavior of the bias present in the original estimator.
+Essentially, we apply CCT's insight that a polynomial one order higher can capture the first-order bias behavior and create a bootstrap procedure that can correctly mimic the behavior of the bias present in the original estimator.
 For such, for a chosen bandwidth, we estimate a local quadratic regression the same way CCT suggested but then create bootstrap data by imposing the local quadratic functional form as the DGP.
@@
 \section{Conclusion}\label{conclusion}
-This paper proposes an novel bootstrap procedure to obtain robust bias-corrected
+This paper proposes a novel bootstrap procedure to obtain robust bias-corrected
 confidence intervals in regression discontinuity designs. 

### 2016-02-20 main_paper.tex
Move BibTeX database to 'tex' subdirectory
Move bootstraps into 'algorithm' environment
Using an explicit algorithm environment for the bootstrap descriptions
gives us automatic numbering, etc.

@@
 More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\mathsf{B}}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates,i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
-Algorithm 1 describes this procedure step-by-step for clarity.
+Algorithm~\ref{alg1} describes this procedure step-by-step for clarity.
 
-\textbf{Algorithm 1}: Bootstrap Bias Corrected Point Estimator
+\begin{algorithm}[Bias correction]\label{alg1}\hfill
  \begin{enumerate}
@@
  \end{enumerate}
+\end{algorithm}
 
-With Algorithm 1 at hand, we can move to generate the bias-corrected confidence intervals to perform inference about $\tau$.
-Here the idea is similar, but now we actually calculate a fully bias corrected estimate using Algorithm 1 for every bootstrapped dataset generated, a bootstrap within the bootstrap.
+With Algorithm~\ref{alg1} at hand, we can move to generate the bias-corrected confidence intervals to perform inference about $\tau$.
+Here the idea is similar, but now we actually calculate a fully bias corrected estimate using Algorithm~\ref{alg1} for every bootstrapped dataset generated, a bootstrap within the bootstrap.
 Each one of the bias corrected estimates for the generated data is denoted $\hat{\tau}^{bc*}$.
@@
 
-\textbf{Algorithm 2}: Confidence Interval
+\begin{algorithm}[Confidence intervals]\hfill
  \begin{enumerate}
@@
 	\item Generate bootstrap data $[Y^{*},\chi^{*}]$ imposing the DGP and and residual's distribution estimated in Step 2 on each sides of cutoff.
-	\item Apply Algorithm 1 (starting at step 2) to bootstrap data generated in step 3 and obtain bias corrected estimate $\hat{\tau}^{bc*}$.
+	\item Apply Algorithm~\ref{alg1} (starting at step 2) to bootstrap data generated in step 3 and obtain bias corrected estimate $\hat{\tau}^{bc*}$.
 	\item Repeat step 3 and 4 for $B$ times and obtain confidence interval formed by the $\frac{\alpha}{2}$ and $\left(1-\frac{\alpha}{2}\right)$ percentiles of the empirical distribution of $\hat{\tau}^{bc*}$ .
  \end{enumerate}
+\end{algorithm}
 
@@
 \bibliographystyle{jpe}
-\bibliography{bootrd}
+\bibliography{tex/references.bib}
 \end{document}

### 2016-02-20 main_paper.tex
Add macros for common math operators: 1, E, V
I'm lazy, and typing \mathbbm{1} (and other values) over and over again
is pretty unappealing. So I've added macros \1, etc.

@@
  \begin{align}
-  Y_{i}=Y_{i}(0) \mathbbm{1}\{X_{i}<0\}+Y_{i}(1) \mathbbm{1}\{X_{i} \geq 0\}
+  Y_{i}=Y_{i}(0) \1\{X_{i}<0\}+Y_{i}(1) \1\{X_{i} \geq 0\}
  \end{align}
-where $\mathbbm{1}\{ \cdot\}$ denotes the indicator function. For convenience, 
+where $\1\{ \cdot\}$ denotes the indicator function. For convenience,
 define
  \begin{align}
-  \mu(x)= \mathbbm{E}[Y_{i}|X_{i}=x]
+  \mu(x)= \E[Y_{i}|X_{i}=x]
  \end{align}
@@
 In most cases the population parameter of interest is 
-$\tau=\mathbbm{E}[Y(1)-Y(0)|X=\bar{x}]$ (i.e., the average treatment effect 
+$\tau=\E[Y(1)-Y(0)|X=\bar{x}]$ (i.e., the average treatment effect
 at the threshold). Under continuity and smoothness conditions on both the 
@@
 Naturally, the estimation of $\tau$ in RD designs focuses on the 
-problem of approximating $\mathbbm{E}[Y(1)|X=x]$ and $\mathbbm{E}[Y(0)|X=x]$ 
+problem of approximating $\E[Y(1)|X=x]$ and $\E[Y(0)|X=x]$
 near the cutoff. Due to its desirable properties when estimating regression 
@@
 (\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= argmin_{b_{0},b_{1}} 
-\sum_{i=1}^{N}\mathbbm{1}\{X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \cdot K_{h}(X_{i})\\
+\sum_{i=1}^{N}\1\{X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \cdot K_{h}(X_{i})\\
 (\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= argmin_{b_{0},b_{1}}
-\sum_{i=1}^{N}\mathbbm{1}\{X_{i} < 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2}\cdot K_{h}(X_{i})
+\sum_{i=1}^{N}\1\{X_{i} < 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2}\cdot K_{h}(X_{i})
 \end{align*}
@@
 As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT identification and inference procedures can be developed based on the following assumptions\footnote{The assumptions below are the same as presented by CCT.}
-\begin{assumption}\label{A1}
+\begin{assumption}[Behavior of the DGP near the cutoff]\label{A1}
  For some $\kappa_{0} > 0$, the following holds in the neighborhood $(-\kappa_{0},\kappa_{0})$ around the cutoff $ \bar{x}= 0$:
@@
   \item $E[\left.Y_{i}^{4}\right|X_{i}=x]$ is bounded and the density of $X$, $f(x)$, is continuous and bounded away from zero.
-  \item $\mu_{+}(x)=\mathbbm{E}[\left.Y_{i}(1)\right|X_{i}=x]$ and $\mu_{-}(x)=\mathbbm{E}[\left.Y_{i}(0)\right|X_{i}=x]$ are $S$ times continuously differentiable.
-  \item $\sigma^{2}_{+}(x)=\mathbbm{V}[\left.Y_{i}(1)\right|X_{i}=x]$ and $\sigma^{2}_{-}(x)=\mathbbm{V}[\left.Y_{i}(0)\right|X_{i}=x]$ are continuous and bounded away from zero.
+  \item $\mu_{+}(x)=\E[\left.Y_{i}(1)\right|X_{i}=x]$ and $\mu_{-}(x)=\E[\left.Y_{i}(0)\right|X_{i}=x]$ are $S$ times continuously differentiable.
+  \item $\sigma^{2}_{+}(x)=\V[\left.Y_{i}(1)\right|X_{i}=x]$ and $\sigma^{2}_{-}(x)=\V[\left.Y_{i}(0)\right|X_{i}=x]$ are continuous and bounded away from zero.
  \end{enumerate}
@@
 
-\begin{assumption}\label{A2}
+\begin{assumption}[Kernel]\label{A2}
  For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa] \rightarrow \mathbbm{R}$ is bounded and nonnegative, zero outside its support, and positive and continuous on $(0, \kappa)$.
@@
 
-Assumption \ref{A2} supports the kernels most commonly used in applications, in particular the broadly used uniform kernel $k(u)=\mathbbm{1}[0\leq u\leq 1]$, which simplifies to the use of a local linear OLS on both sides of the treshold.
+Assumption \ref{A2} supports the kernels most commonly used in applications, in particular the broadly used uniform kernel $k(u)=\1[0\leq u\leq 1]$, which simplifies to the use of a local linear OLS on both sides of the treshold.
 Since the objective of this paper is to present a simple bootstrap procedure to obtain robust confidence intervals in the context of RD designs that can be easily implemented by practitioners, during the remainder of the paper we focus on estimators that use the rectangular kernel.
 The use of different weighting structures implied by different kernels complicates the bootstrap algorithm in meaningful ways and such analysis is left to future work.
+
+\begin{assumption}[Bandwidth]\label{A3}
+Let $h_n$ be the bandwidth used to estimate the local polynomial of order $p$ and let $b_n$ be the bandwidth used for $p+1$. Then $h_n$, $b_n = o(n^{-1/5})$ and
+$n h_n$, $n b_n \to \infty$ as $n \to \infty$.\footnote{Unless otherwise stated, all limits in this paper are assumed to hold as $n \to \infty$.}
+\end{assumption}
 
@@
  \begin{align}
-  T(h_{n})=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), \text{        }V(h_{n})=\mathbbm{V}[\left.\tau(h_{n})\right|\chi_{n}], \text{        }\chi_{n}=[X_{1}, \dots X_{n}]^{\prime}
+  T(h_{n})=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), \text{        }V(h_{n})=\V[\left.\tau(h_{n})\right|\chi_{n}], \text{        }\chi_{n}=[X_{1}, \dots X_{n}]^{\prime}
  \end{align}
@@
 \begin{align*}
-     E[\hat{\tau}(h_{n})|\chi_{n}]-\tau=& h_{n}^{2}\mathsf{B}(h_{n})\{1+o_{p}(1)\}\\
+     \E[\hat{\tau}(h_{n})|\chi_{n}]-\tau=& h_{n}^{2}\mathsf{B}(h_{n})\{1+o_{p}(1)\}\\
      \mathsf{B}(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\mathfrak{B}_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\mathfrak{B}_{-}(h_{n})

### 2016-02-20 main_paper.tex
Rewrite Algorithm 1 and add consistency lemma
I've tried to make Algorithm 1 more precise. I've also added a
placeholder lemma for the theoretical result that the resulting
estimator is consistent.

@@
 More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\mathsf{B}}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates,i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
-Algorithm~\ref{alg1} describes this procedure step-by-step for clarity.
+Algorithm~\ref{Alg1} describes this procedure step-by-step for clarity.
 
-\begin{algorithm}[Bias correction]\label{alg1}\hfill
+\begin{algorithm}[Bias estimation]\label{Alg1}
+  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A3} and
+  define
+  \begin{align}
+    I^-(h) &= \{i : h < X_i < 0\}, &
+    I^+(h) &= \{i : 0 < X_i < h\}.
+  \end{align}
+  Also define $M^-(h_n)$ and $M^+(h_n)$ to be the number of elements in
+  $I^-(h_n)$ and $I^+(h_n)$ respectively.
   \begin{enumerate}
-	\item Obtain bandwidths for both local linear and quadratic regressions $(h_{n}, b_{n})$ using CCT bandwidth choice algorithm procedure.
-	\item Estimate local linear regression on both sides of cutoff using bandwidth from step 1 and calculate $\hat{\tau}(h_{n})$.
-	\item Estimate local quadratic regression on both sides of cutoff using bandwidth $b_{n}$ from step 1 and calculate $\tau^{*}$, the difference of two regression functions evaluated at cutoff.
-	\item Generate bootstrap data $[Y^{*},\chi^{*}]$ imposing the DGP and and residual's distribution estimated in Step 3 on each sides of cutoff.
-	\item Apply step 2 on bootstrap data and obtain $\hat{\tau}^{*}$.
-	\item Repeat step 4 and 5 for $B$ times and the bias corrected point estimate is given by $\hat{\tau}^{bc}=\hat{\tau} + \tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
+  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
+    Equation --- and define the residuals
+    \begin{equation}
+      \label{eq:1}
+      \hat\varepsilon_i =
+      \begin{cases}
+        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
+        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
+      \end{cases}
+    \end{equation}
+  \item Repeat the following steps $B$ times to produce a sequence of bootstrap
+    estimates $\hat\tau_1^*,\dots,\hat\tau_B^*$. For the $k$th step:
+    \begin{enumerate}
+    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
+      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
+      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
+      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
+      \begin{align}
+        \label{eq:2}
+        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
+        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
+      \end{align}
+    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
+      \begin{align}
+        \hat\mu_-^*
+        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
+          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
+          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta X_i^{*-}))^2 \\
+        \hat\mu_+^*
+        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
+          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
+          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta X_i^{*+}))^2
+      \end{align}
+    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
+    \end{enumerate}
+  \item Calculate the bias estimator as
+    \begin{equation}
+      \label{eq:4}
+      \hat\Delta = \tfrac{1}{B} \sum_{k=1}^B \hat\tau^*_k -
+      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big].
+    \end{equation}
   \end{enumerate}
@@
 
-With Algorithm~\ref{alg1} at hand, we can move to generate the bias-corrected confidence intervals to perform inference about $\tau$.
-Here the idea is similar, but now we actually calculate a fully bias corrected estimate using Algorithm~\ref{alg1} for every bootstrapped dataset generated, a bootstrap within the bootstrap.
+Under Assumptions~\ref{A1} and~\ref{A2} the procedure described by
+Algorithm~\ref{Alg1} provides a consistent estimator of the bias component and
+this estimator converges to zero fast enough in probability that it can be be
+used as a correction.
+
+\begin{lemma}\label{L1}
+  Let $\hat\Delta^*$ be the bias estimator defined in Equation~\eqref{eq:4}.
+  Under Assumptions~\ref{A1} and~\ref{A3},
+  \[
+    \hat\Delta - \big[\E(\hat\tau) - \tau\big] = o_p(-).
+  \]
+\end{lemma}
+
+With Algorithm~\ref{Alg1} at hand, we can move to generate the bias-corrected confidence intervals to perform inference about $\tau$.
+Here the idea is similar, but now we actually calculate a fully bias corrected estimate using Algorithm~\ref{Alg1} for every bootstrapped dataset generated, a bootstrap within the bootstrap.
 Each one of the bias corrected estimates for the generated data is denoted $\hat{\tau}^{bc*}$.
 These estimator's empirical distribution capture the variability induced by the first order bias correction that lead CCT to propose the rescaling of their confidence intervals by introducing $C^{bc}(h_{n},b_{n})$ in the asymptotic variance formula on Section \ref{background}.
+
+\begin{algorithm}[Confidence intervals]\label{Alg2}
 
@@
 	\item Generate bootstrap data $[Y^{*},\chi^{*}]$ imposing the DGP and and residual's distribution estimated in Step 2 on each sides of cutoff.
-	\item Apply Algorithm~\ref{alg1} (starting at step 2) to bootstrap data generated in step 3 and obtain bias corrected estimate $\hat{\tau}^{bc*}$.
+	\item Apply Algorithm~\ref{Alg1} (starting at step 2) to bootstrap data generated in step 3 and obtain bias corrected estimate $\hat{\tau}^{bc*}$.
 	\item Repeat step 3 and 4 for $B$ times and obtain confidence interval formed by the $\frac{\alpha}{2}$ and $\left(1-\frac{\alpha}{2}\right)$ percentiles of the empirical distribution of $\hat{\tau}^{bc*}$ .

### 2016-02-20 main_paper.tex
Change notation for number of bootstraps in bias estimation
I'm letting B_1 represent the number of replications for the bias
correction --- there's no reason to impose that the numbers are
the same.
Add detail to Confidence Interval algorithm
This commit rewrites Algorithm 2 to make the description of the
bootstrap a little more transparent. It also adds a Theorem
stating that the approach is valid. :)

@@
     \end{equation}
-  \item Repeat the following steps $B$ times to produce a sequence of bootstrap
-    estimates $\hat\tau_1^*,\dots,\hat\tau_B^*$. For the $k$th step:
+  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
+    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
     \begin{enumerate}
@@
       \label{eq:4}
-      \hat\Delta = \tfrac{1}{B} \sum_{k=1}^B \hat\tau^*_k -
+      \hat\Delta = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
       \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big].
@@
 \begin{algorithm}[Confidence intervals]\label{Alg2}
-
-\begin{algorithm}[Confidence intervals]\hfill
+  Define $I^-$, $I^+$, $M^-$, and $M^+$ as in Algorithm~\ref{Alg1}.
   \begin{enumerate}
-	\item Obtain bandwidths for both local linear and quadratic regressions $(h_{n}, b_{n})$ using CCT bandwidth choice algorithm procedure.
-	\item Estimate local quadratic regression on both sides of cutoff using bandwidth $b_{n}$ from step 1.
-	\item Generate bootstrap data $[Y^{*},\chi^{*}]$ imposing the DGP and and residual's distribution estimated in Step 2 on each sides of cutoff.
-	\item Apply Algorithm~\ref{Alg1} (starting at step 2) to bootstrap data generated in step 3 and obtain bias corrected estimate $\hat{\tau}^{bc*}$.
-	\item Repeat step 3 and 4 for $B$ times and obtain confidence interval formed by the $\frac{\alpha}{2}$ and $\left(1-\frac{\alpha}{2}\right)$ percentiles of the empirical distribution of $\hat{\tau}^{bc*}$ .
+  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
+    Equation --- and define the residuals
+    \begin{equation}
+      \label{eq:6}
+      \hat\varepsilon_i =
+      \begin{cases}
+        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
+        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
+      \end{cases}
+    \end{equation}
+  \item Repeat the following steps $B_2$ times to produce a sequence of bootstrap
+    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_B^{\prime*}$. For the $k$th step:
+    \begin{enumerate}
+    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
+      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
+      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
+      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
+      \begin{align}
+        \label{eq:2}
+        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
+        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
+      \end{align}
+    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
+      \begin{align}
+        \hat\mu_-^*
+        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
+          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
+          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta X_i^{*-}))^2 \\
+        \hat\mu_+^*
+        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
+          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
+          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta X_i^{*+}))^2
+      \end{align}
+    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
+      \begin{equation*}
+        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M^-(b_n)}^{*-},X_{M^-(b_n)}^{*-}),
+        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M^+(b_n)}^{*+},X_{M^+(b_n)}^{*+}),
+      \end{equation*}
+      using the same bandwidths $h_n$ and $b_n$ that are used in the rest of
+      this algorithm but reestimating all of the local polynomials on the
+      bootstrap data. Let $\hat\Delta^*$ represent the bias estimate returned
+      by Algorithm~\ref{Alg1}.
+    \item Save the bias-corrected estimate
+      $\hat\mu_+^* - \hat\mu_i^* - \hat\Delta^*$ as $\hat\tau_k^{\prime*}$.
+    \end{enumerate}
+  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
+    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
+    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
   \end{enumerate}
 \end{algorithm}
+
+Under the same assumptions as earlier, this procedure produces asymptotically
+valid confidence intervals.
+\begin{theorem}
+  Suppose Assumptions~\ref{A1} and~\ref{A3} hold and let $\hat \ell(\alpha)$ and
+  $\hat u(\alpha)$ be the interval endpoints produced by Algorithm~\ref{Alg2}
+  for some $\alpha \in (0,1)$. Also let $\Pr_\tau$ represent the probability
+  distribution of the random variables under the assumption that $\tau$ is
+  the true value of the ATE. Then
+  \begin{equation}
+    \label{eq:5}
+    \plim_{n \to \infty} \sup_\tau
+    \Pr_\tau[\hat\ell(\alpha) \leq \tau \leq \hat u(\alpha)] \geq 1 - \alpha.
+  \end{equation}
+  Each of the one-sided intervals is asymptotically valid as well:
+  \begin{align}
+    \plim_{n \to \infty} \sup_\tau
+    \Pr_\tau[\hat\ell(\alpha) \leq \tau ] &\geq 1 - \alpha / 2, &
+    \plim_{n \to \infty} \sup_\tau
+    \Pr_\tau[\tau \leq \hat u(\alpha)] &\geq 1 - \alpha / 2.
+  \end{align}
+\end{theorem}
 

### 2016-02-21 main_paper.tex
Fix minor error in notation for algorithms
I forgot a few subscripts and powers in defining the ATE estimates.
This commit adds them.
Add more macros for formatted variable names
I don't like typing all of the varieties of 'B', so I'm converting
some of them to macros for now.

@@
 \begin{align*}
-     \E[\hat{\tau}(h_{n})|\chi_{n}]-\tau=& h_{n}^{2}\mathsf{B}(h_{n})\{1+o_{p}(1)\}\\
-     \mathsf{B}(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\mathfrak{B}_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\mathfrak{B}_{-}(h_{n})
+     \E[\hat{\tau}(h_{n})|\chi_{n}]-\tau=& h_{n}^{2}\Bs(h_{n})\{1+o_{p}(1)\}\\
+     \Bs(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\Bf_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\Bf_{-}(h_{n})
    \end{align*}
-where $\mathfrak{B}_{+}(h_{n})$ and $\mathfrak{B}_{-}(h_{n})$ are observed quantities that depend on the data, kernel and $h_{n}$.
+where $\Bf_{+}(h_{n})$ and $\Bf_{-}(h_{n})$ are observed quantities that depend on the data, kernel and $h_{n}$.
 The plug-in bias-corrected estimator then requires estimates for the second derivatives of the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$.
@@
 \begin{align*}
-     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\mathsf{B}}(h_{n},b_{n})\\
-     \hat{\mathsf{B}}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}\mathfrak{B}_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\mathfrak{B}_{-}(h_{n})
+     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\\
+     \hat{\Bs}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}\Bf_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\Bf_{-}(h_{n})
    \end{align*}
-By incorporating the contribution of both $\hat{\tau}(h_{n})$ and $\hat{\mathsf{B}}(h_{n},b_{n})$ to the asymptotic distribution of the estimator, CCT obtain a robust confidence interval with a different asymptotic variance in general.
+By incorporating the contribution of both $\hat{\tau}(h_{n})$ and $\hat{\Bs}(h_{n},b_{n})$ to the asymptotic distribution of the estimator, CCT obtain a robust confidence interval with a different asymptotic variance in general.
 So under Assumptions \ref{A1} and \ref{A2}, if $n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and $n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< \kappa_{0}$, they show that
@@
  \begin{align}
-  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\mathsf{B}}(h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}(h_{n}, b_{n})} \right]
+  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}(h_{n}, b_{n})} \right]
  \end{align}
@@
 Hence, the bias for a specific bootstrap data is given by $\tau^{*}-\hat{\tau}^{*}$.
-More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\mathsf{B}}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates,i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
+More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\Bs}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates,i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
 Algorithm~\ref{Alg1} describes this procedure step-by-step for clarity.
@@
           \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
-          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta X_i^{*-}))^2 \\
+          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
         \hat\mu_+^*
@@
           \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
-          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta X_i^{*+}))^2
+          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
       \end{align}

### 2016-02-21 main_paper.tex
Tweak statements and presentation of main results

@@
 \begin{assumption}[Kernel]\label{A2}
- For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa] \rightarrow \mathbbm{R}$ is bounded and nonnegative, zero outside its support, and positive and continuous on $(0, \kappa)$.
+ For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa] \rightarrow \RR$ is bounded and nonnegative, zero outside its support, and positive and continuous on $(0, \kappa)$.
 \end{assumption}
@@
 \begin{assumption}[Bandwidth]\label{A3}
-Let $h_n$ be the bandwidth used to estimate the local polynomial of order $p$ and let $b_n$ be the bandwidth used for $p+1$. Then $h_n$, $b_n = o(n^{-1/5})$ and
-$n h_n$, $n b_n \to \infty$ as $n \to \infty$.\footnote{Unless otherwise stated, all limits in this paper are assumed to hold as $n \to \infty$.}
+Let $h_n$ be the bandwidth used to estimate the local polynomial of order $p$ and let $b_n$ be the bandwidth used for $p+1$. Then $h_n$, $b_n = o(n^{-1/5})$,
+$n h_n$, $n b_n \to \infty$ as $n \to \infty$, and $h_n \leq b_n$ for all $n$.\footnote{Unless otherwise stated, all limits in this paper are assumed to hold as $n \to \infty$.}
 \end{assumption}
@@
       \hat\Delta = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
-      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big].
+      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
     \end{equation}
@@
 \end{algorithm}
+Obviously, the distribution of $\hat\Delta$ depends on $B_1$ and we could
+incorporate that dependency into our notation by wrting
+$\hat\Delta_{B_1}$. However, we will follow standard practice in the bootstrap
+literature and assume that $B_1$ is large enough that it can be ignored and
+define $\hat\Delta = \plim_{B_1 \to \infty} \hat\Delta_{B_1}$
 
@@
 this estimator converges to zero fast enough in probability that it can be be
-used as a correction.
+used as a correction. As is standard in the bootstrap literature, we will assume
+that the number of bootstrap replications, $B_1$, is large enough that the
+simulation error can be ignored.
 
 \begin{lemma}\label{L1}
-  Let $\hat\Delta^*$ be the bias estimator defined in Equation~\eqref{eq:4}.
   Under Assumptions~\ref{A1} and~\ref{A3},
-  \[
-    \hat\Delta - \big[\E(\hat\tau) - \tau\big] = o_p(-).
-  \]
+  $\hat\Delta = \E \hat\tau - \tau + o_p()$.
 \end{lemma}
@@
 
-Under the same assumptions as earlier, this procedure produces asymptotically
-valid confidence intervals.
-\begin{theorem}
-  Suppose Assumptions~\ref{A1} and~\ref{A3} hold and let $\hat \ell(\alpha)$ and
-  $\hat u(\alpha)$ be the interval endpoints produced by Algorithm~\ref{Alg2}
-  for some $\alpha \in (0,1)$. Also let $\Pr_\tau$ represent the probability
-  distribution of the random variables under the assumption that $\tau$ is
-  the true value of the ATE. Then
+As earlier, we assume that $B_1$ and $B_2$ are large enough that simulation
+error can be ignored. Define the limiting values
+\begin{align*}
+\hat\Delta^* &= \plim_{B_1,B_2 \to \infty} \hat\Delta^*_{B_1,B_2} \\
+\hat\ell^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat\ell^*_{B_1,B_2}(\alpha) \\
+\hat u^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat u^*_{B_1,B_2}(\alpha).
+\end{align*}
+Two results follow. The first is that the secondary bootstrap step produces
+a consistent estimator of the bias under the bootstrap distribution. The
+second is that the intervals overall are asymptotically valid.
+
+\begin{lemma}\label{L2}
+  Under Assumptions~\ref{A1} and~\ref{A3},
+  $\hat\Delta^* = \E^* \hat\tau^* - \tau^* + o_{p^*}(-)$.
+\end{lemma}
+
+\begin{theorem}\label{T1}
+  Let $\Pr_\tau$ represent the probability distribution of the random variables
+  under the assumption that $\tau$ is the true value of the ATE and suppose
+  Assumptions~\ref{A1} and~\ref{A3} hold. Then
   \begin{equation}
@@
   \end{equation}
-  Each of the one-sided intervals is asymptotically valid as well:
+  Both of the one-sided intervals are asymptotically valid under the same
+  assumptions as well:
   \begin{align}

### 2016-02-21 main_paper.tex
Make minor formatting and notation changes to paper

@@
 \begin{assumption}[Bandwidth]\label{A3}
-Let $h_n$ be the bandwidth used to estimate the local polynomial of order $p$ and let $b_n$ be the bandwidth used for $p+1$. Then $h_n$, $b_n = o(n^{-1/5})$,
-$n h_n$, $n b_n \to \infty$ as $n \to \infty$, and $h_n \leq b_n$ for all $n$.\footnote{Unless otherwise stated, all limits in this paper are assumed to hold as $n \to \infty$.}
+  Let $h_n$ be the bandwidth used to estimate the local polynomial of
+  order $p$ and let $b_n$ be the bandwidth used for $p+1$. Then
+  $h_n = o(n^{-1/5})$, $b_n = o(n^{-1/5})$, $n h_n \to \infty$, and
+  $n b_n \to \infty$ as $n \to \infty$.\footnote{%
+    Unless otherwise stated, all limits in this paper are assumed to
+    hold as $n \to \infty$.} %
+  The relationship $h_n \leq b_n$ also holds for all $n$.
 \end{assumption}
@@
     \end{enumerate}
-  \item Calculate the bias estimator as
+  \item Estimate the bias as
     \begin{equation}
       \label{eq:4}
-      \hat\Delta = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
+      \Delta^* = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
       \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
@@
 \end{algorithm}
-Obviously, the distribution of $\hat\Delta$ depends on $B_1$ and we could
+Obviously, the distribution of $\Delta^*$ depends on $B_1$ and we could
 incorporate that dependency into our notation by wrting
-$\hat\Delta_{B_1}$. However, we will follow standard practice in the bootstrap
+$\Delta^*_{B_1}$. However, we will follow standard practice in the bootstrap
 literature and assume that $B_1$ is large enough that it can be ignored and
-define $\hat\Delta = \plim_{B_1 \to \infty} \hat\Delta_{B_1}$
+define $\Delta^* = \plim_{B_1 \to \infty} \Delta^*_{B_1}$
 
@@
   Under Assumptions~\ref{A1} and~\ref{A3},
-  $\hat\Delta = \E \hat\tau - \tau + o_p()$.
+  $\Delta^* = \E \hat\tau - \tau + o_p()$.
 \end{lemma}
@@
       this algorithm but reestimating all of the local polynomials on the
-      bootstrap data. Let $\hat\Delta^*$ represent the bias estimate returned
+      bootstrap data. Let $\Delta^{**}$ represent the bias estimator returned
       by Algorithm~\ref{Alg1}.
-    \item Save the bias-corrected estimate
-      $\hat\mu_+^* - \hat\mu_i^* - \hat\Delta^*$ as $\hat\tau_k^{\prime*}$.
+    \item Save the bias-corrected estimator
+      $\hat\tau_k^{\prime*} = \hat\mu_+^* - \hat\mu_i^* - \Delta^{**}$.
     \end{enumerate}
@@
 \begin{align*}
-\hat\Delta^* &= \plim_{B_1,B_2 \to \infty} \hat\Delta^*_{B_1,B_2} \\
+\Delta^{**} &= \plim_{B_1,B_2 \to \infty} \Delta^{**}_{B_1,B_2} \\
 \hat\ell^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat\ell^*_{B_1,B_2}(\alpha) \\
@@
   Under Assumptions~\ref{A1} and~\ref{A3},
-  $\hat\Delta^* = \E^* \hat\tau^* - \tau^* + o_{p^*}(-)$.
+  $\Delta^{**} = \E^* \hat\tau^* - \tau^* + o_{p^*}(-)$.
 \end{lemma}

### 2016-02-22 main_paper.tex
Add fallback when VERSION.tex
Some of the people working on this project (ahem) are not as
excited about the idea of 'automatically generated git commit
information' as others and have resisted generating VERSION.tex.
This commit makes an ugly but seemingly necesary concession to
them and adds a default fallback option if VERSION.tex does not
exist. You're mfing welcome.
Change filepath to BibTeX database
Referring to 'references.bib' causes problems on some TeX
compilers, so we use 'references' instead.
Add Emacs/AucTeX information to main_paper.tex
This commit adds a little bit of configurat

@@
 \documentclass[12pt,fleqn]{article}
-\input{VERSION}
+
+% Add commit information from Git to the pdf. It is automatically
+% generated with the R script 'R/version.R' and can be run from
+% the command line in the project's top directory via:
+%
+% $ Rscript R/version.R
+%
+% If VERSION.tex does not exist we can't add information from
+% Git, so we'll use today's date as a fallback.
+
+\IfFileExists{./VERSION.tex}{\input{VERSION}}{%
+\providecommand\VERSION{\today}}
+
 \input{tex/setup}
@@
 
-\begin{abstract}
-This paper proposes an novel bootstrap procedure to obtain robust bias-corrected
-confidence intervals in regression discontinuity designs. The approach proposed 
-is based on a first-order bias correction and provides an alternative
-to the plug-in analytical methods proposed by Calonico, Cattaneo and Titiunik (2014).
-The algorithm is simple to implement and generates robust confidence intervals
-with improved coverage relative to the analytical alternatives in simulations.
+\begin{abstract}\noindent%
+  This paper develops a novel bootstrap procedure to obtain robust
+  bias-corrected confidence intervals in regression discontinuity designs that
+  use the uniform kernel. The procedure uses a residual bootstrap to estimate
+  the bias of the RD estimator, which is then removed from the original RD
+  estimator. The bias-corrected estimator is then bootstrapped itself to
+  generate valid confidence intervals. This procedure is valid for empirically
+  relevant bandwidths when the residual bootstraps use a polynomial of higher
+  order than used to estimate the treatment effect and can be applied under the
+  same conditions as Calonico, Cattaneo and Titiunik's (2014,
+  \textit{Econometrica}) analytical correction.
 \end{abstract}
@@
 
-%%%%%REFERENCES%%%%%%%%%
 \clearpage
 \bibliographystyle{jpe}
-\bibliography{tex/references.bib}
+\bibliography{tex/references}
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2016-02-22 main_paper.tex
Table redesign
This commit tweaks the table layout to make the different statistics
more directly comparable to each other. It also makes a few cosmetic
changes.

--- 2016-02-21 main_paper.tex
@@
 
-\begin{table}[ht] \label{Tb1}
+\begin{table}[t] \label{Tb1}
+\centering
+\begin{tabular}{rrrrrrrrr}
+  \toprule
+  DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
+  \midrule
+  1   & bootstrap & --0.013 & 0.067 & 0.068 & 0.938       & 0.243     \\
+      & CCT       & --0.016 & 0.068 & 0.070 & 0.908       & 0.244     \\
+  2   & bootstrap & --0.014 & 0.083 & 0.084 & 0.954       & 0.319     \\
+      & CCT       & --0.014 & 0.092 & 0.093 & 0.928       & 0.350     \\
+  3   & bootstrap & --0.006 & 0.069 & 0.070 & 0.956       & 0.247     \\
+      & CCT       & --0.004 & 0.071 & 0.071 & 0.918       & 0.249     \\
+  \bottomrule
+\end{tabular}
 \caption{Summary of estimates ($p = 1, q = 2$)}
-	\centering
-	\begin{tabular}{ccccccc}
-		\hline
-		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
-		\hline
-		\multicolumn{7}{c}{Panel A: Bootstrap Bias-Correction} \\
-		1 & 0.04 & -0.013 & 0.067 & 0.068 & 0.938 & 0.243 \\ 
-		2 & -3.45 & -0.014 & 0.083 & 0.084 & 0.954 & 0.319 \\ 
-		3 & 0.04 & -0.006 & 0.069 & 0.070 & 0.956 & 0.247 \\ 
-		&&&&&& \\
-		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
-		1 & 0.04 & -0.016 & 0.068 & 0.070 & 0.908 & 0.244 \\ 
-		2 & -3.45 & -0.014 & 0.092 & 0.093 & 0.928 & 0.350 \\ 
-		3 & 0.04 & -0.004 & 0.071 & 0.071 & 0.918 & 0.249 \\ 
-		\hline
-	\end{tabular}
 \end{table}
 
-\begin{table}[ht]\label{Tb2}
-	\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
-	\centering
-	\begin{tabular}{ccccccc}
-		\hline
-		DGP & True & Bias & SD & MSE & CI coverage & CI length \\ 
-		\hline
-		\multicolumn{7}{c}{Panel A: Uniform Kernel} \\
-		1 & 0.04 & -0.002 & 0.075 & 0.075 & 0.958 & 0.295 \\ 
-		2 & -3.45 & 0.002 & 0.087 & 0.086 & 0.934 & 0.302 \\ 
-		3 & 0.04 & -0.008 & 0.083 & 0.083 & 0.942 & 0.292 \\ 
-		&&&&&& \\
-		\multicolumn{7}{c}{Panel B: Analytical Bias Correction (CCT 2014)} \\
-		1 & 0.04 & -0.004 & 0.082 & 0.082 & 0.926 & 0.295 \\ 		
-		2 & -3.45 & -0.005 & 0.078 & 0.078 & 0.960 & 0.323 \\ 		
-		3 & 0.04 & -0.003 & 0.080 & 0.080 & 0.938 & 0.295 \\ 
-		\hline
-	\end{tabular}
-\end{table}
 As can be seen on the tables above, the bootstrap bias-correction procedure
@@
 bias correction procedures proposed by CCT.
+
+\begin{table}[t]\label{Tb2}
+\centering
+\begin{tabular}{rrrrrrr}
+  \toprule
+  DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
+  \midrule
+  1   & bootstrap & --0.002 & 0.075 & 0.075 & 0.958       & 0.295     \\
+      & CCT       & --0.004 & 0.082 & 0.082 & 0.926       & 0.295     \\
+  2   & bootstrap & 0.002   & 0.087 & 0.086 & 0.934       & 0.302     \\
+      & CCT       & --0.005 & 0.078 & 0.078 & 0.960       & 0.323     \\
+  3   & bootstrap & --0.008 & 0.083 & 0.083 & 0.942       & 0.292     \\
+      & CCT       & --0.003 & 0.080 & 0.080 & 0.938       & 0.295     \\
+  \bottomrule
+\end{tabular}
+\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
+\end{table}
 

### 2016-02-22 R/RDfunctions.R
Clean the .R files
Put all bootstrap functions in RDfunctions.R and run this file first in
application/simulation.

@@ -1,0 +1,149 @@
+
+generate.data <- function(model.id) {
+  x <- 2*rbeta(500, 2, 4) - 1
+  e <- rnorm(500, 0, 0.1295)
+  y <- e + switch(model.id,
+                  ifelse(x < 0, 0.48 +  1.27*x +  7.18*x^2 + 20.21*x^3 + 21.54*x^4 + 7.33*x^5,
+                         0.52 +  0.84*x -  3.00*x^2 +  7.99*x^3 -  9.01*x^4 + 3.56*x^5),
+                  ifelse(x < 0, 3.71 +  2.30*x +  3.28*x^2 +  1.45*x^3 +  0.23*x^4 + 0.03*x^5,
+                         0.26 + 18.49*x - 54.81*x^2 + 74.30*x^3 - 45.02*x^4 + 9.83*x^5),
+                  ifelse(x < 0, 0.48 +  1.27*x - 0.5*7.18*x^2 + 0.7*20.21*x^3 + 1.1*21.54*x^4 + 1.5*7.33*x^5,
+                         0.52 +  0.84*x - 0.1*3.00*x^2 - 0.3*7.99*x^3 - 0.1*9.01*x^4 + 3.56*x^5))
+  return(data.frame(y = y, x = x))
+}
+
+k.weight <- function(x, h, kernel) {
+  u <- x / h
+  if (kernel == "epanechnikov" | kernel == "epa") {
+    w <- (0.75*(1 - u^2)*(abs(u) <= 1)) / h
+  } else if (kernel == "uniform" | kernel == "uni") {
+    w <- (0.5*(abs(u) <= 1)) / h
+  } else {
+    w <- ((1 - abs(u))*(abs(u) <= 1)) / h
+  }
+  return(w)	
+}
+
+lpreg <- function(dta, order, bw, kernel) {
+  weight <- k.weight(dta$x, bw, kernel)
+  fit    <- lm.wfit(cbind(1, poly(dta$x, order, raw = T)), dta$y, weight)
+  return(list(cons = fit$coefficients[1], 
+              yhat = fit$fitted.values, 
+              res = fit$residuals, 
+              weight = weight))
+}
+
+rd.estimate <- function(dta, p, q, bw.p, bw.q, N.bc, kernel, bc = T) {
+  # dta:    a data set contains y and x.
+  # p:      the order of polynomial for point estimation.
+  # q:      the order of polynomial for bias correction.
+  # bw.p:   bandwidth for point estimation.
[…]

### 2016-02-22 R/application.R

@@ -1,0 +1,339 @@
+rm(list = ls())
+library(rdrobust)
+library(xtable)
+try(source("slackrISE.R"), silent = T)
+
+source("functions.R")
+
+setwd("C:/Users/Yang/OneDrive/QJE data and code PUBLIC/analysis data")
+
+###################################################################################
+## slightly modify the function rd.ci so that it exports standard error
+###################################################################################
+
+rd.ci <- function(dta, p, q, bw.p, bw.q, N.bc, N.ci, level, kernel, bc = T) {
+  # dta:    a data set contains y and x.
+  # p:      the order of polynomial for point estimation.
+  # q:      the order of polynomial for bias correction.
+  # bw.p:   bandwidth for point estimation.
+  # bw.q:   bandwidth for bias correction.
+  # N.bc:   number of bootstrap replications for bias correction.
+  # N.ci:   number of bootstrap replications for confidence interval.
+  # kernel: epanechnikov, uniform or triangular.
+  # bc:     perform bias correction?
+  
+  if (length(bw.p) == 1) bw.p <- rep(bw.p, 2)
+  if (length(bw.q) == 1) bw.q <- rep(bw.q, 2)
+  
+  # fit the high order polynomial on both sides
+  dta.q.l <- dta[dta$x > -bw.q[1] & dta$x < 0, ]
+  dta.q.r <- dta[dta$x < bw.q[2] & dta$x >= 0, ]
+  left  <- lpreg(dta.q.l, q, bw.q[1], kernel)
+  right <- lpreg(dta.q.r, q, bw.q[2], kernel)
+  
+  # bootstrap
+  trd.star <- replicate(N.ci, rd.estimate(data.frame(x = c(dta.q.l$x, dta.q.r$x),
+                                                     y = c(left$yhat + sample(left$res, nrow(dta.q.l), T, left$weight),
+                                                           right$yhat + sample(right$res, nrow(dta.q.r), T, right$weight))),
+                                          p, q, bw.p, bw.q, N.bc, kernel, bc))
[…]

### 2016-02-22 R/simulation.R

@@ -2,208 +2,236 @@ rm(list = ls())
 library(rdrobust)
 library(foreach)
 library(doParallel)
-library(ggplot2)
-library(reshape2)
+library(xtable)
+try(source("slackrISE.R"), silent = T)
 
-# N_bc:   number of bootstraps for bias correction
-# N_ci:   number of bootstraps for CI construction
-# N_simu: number of simulations to calculate coverage
-# N_core: number of cores used for parallel computing
+source("functions.R")
 
-# generate_data:  a function to generate data for three models in Calonic 2014
-# correct_bias:   a function to perform residual sampling and correct bias
-# rd_estimate:    a function to calculate RD estimate
-# rd_ci:          a function to calculate CI for RD estimate
-# simulate:       a function to perform one simulation
-# coverage:       a function to collect simulation results from parallel computing
+##########################################################################
 
-N_bc    <- 50
-N_ci    <- 1000
-N_simu  <- 100
-N_core  <- 15
+set.seed(555)
+N.ci <- 999
+level <- 0.95
+N.simu <- 500
+N.core <- 15
+N.bc <- 250
+N.bw <- 500
 
 
-generate_data <- function(model_n) {  
-# input is a scalar: which DGP we are using
+## simulation 1: coverage of CI from bootstraping corrected estimator
+
+simulation.1 <- function(model.id, p, q, kernel) {
   
-  x <- 2*rbeta(500, 2, 4) - 1
-  e <- rnorm(500, 0, 0.1295)
-  
-  if (model_n == 1) {
-    y <- (0.48 + 1.27*x + 7.18*x^2 + 20.21*x^3 + 21.54*x^4 + 7.33*x^5)*(x < 0) +
-         (0.52 + 0.84*x - 3.00*x^2 + 7.99*x^3 - 9.01*x^4 + 3.56*x^5)*( x >= 0)
+  simu <- function() {
+    dta   <- generate.data(model.id)
+    # CCT bandwidth from Calonico package
[…]

### 2016-02-23 R/RDfunctions.R
Update the simulation
clean the code and export .tex file directly.

@@ -104,7 +104,8 @@ rd.ci <- function(dta, p, q, bw.p, bw.q, N.bc, N.ci, level, kernel, bc = T) {
                                                            right$yhat + sample(right$res, nrow(dta.q.r), T, right$weight))),
                                           p, q, bw.p, bw.q, N.bc, kernel, bc))
   ci <- quantile(trd.star, c((1 - level)/2, 1 - (1 - level)/2), na.rm = T)
-  return(ci)
+  sd <- sd(trd.star)
+  return(list(ci = ci, sd = sd))
 }
 
 bw.select <- function(dta, r1, r2, N.bw, kernel, hstart = NULL) {

### 2016-02-23 R/simulation.R

@@ -5,22 +5,25 @@ library(doParallel)
 library(xtable)
 try(source("slackrISE.R"), silent = T)
 
-source("functions.R")
+source("RDfunctions.R")
 
-##########################################################################
-
-set.seed(555)
-N.ci <- 999
+#### for testing in my computer ####
+N.ci <- 20
 level <- 0.95
-N.simu <- 500
-N.core <- 15
-N.bc <- 250
-N.bw <- 500
+N.simu <- 20
+N.core <- 2
+N.bc <- 20
 
+#### to run in servor ####
+# N.ci <- 999
+# level <- 0.95
+# N.simu <- 3000
+# N.core <- 15
+# N.bc <- 500
 
-## simulation 1: coverage of CI from bootstraping corrected estimator
+## simulation 1: coverage of CI from bootstrap
 
-simulation.1 <- function(model.id, p, q, kernel) {
+simulation.1 <- function(model.id, p, q, kernel, bc) {
   
   simu <- function() {
     dta   <- generate.data(model.id)
@@ -28,8 +31,8 @@ simulation.1 <- function(model.id, p, q, kernel) {
     bw    <- rdbwselect(dta$y, dta$x, p = p, q = q, kernel = kernel, bwselect = "CCT")
     bw.p  <- bw$bws[1,1]
     bw.q  <- bw$bws[1,2]
-    t     <- rd.estimate(dta, p, q, bw.p, bw.q, N.bc, kernel, T)
-    ci    <- rd.ci(dta, p, q, bw.p, bw.q, N.bc, N.ci, level, kernel, T)
+    t     <- rd.estimate(dta, p, q, bw.p, bw.q, N.bc, kernel, bc)
+    ci    <- rd.ci(dta, p, q, bw.p, bw.q, N.bc, N.ci, level, kernel, bc)$ci
     return(c(t, ci))
   }
   
@@ -50,41 +53,9 @@ simulation.1 <- function(model.id, p, q, kernel) {
   return(c(true = t.true, bias = bias, SD = SD, MSE = MSE, coverage = coverage, length = length))
 }
 
-output.1 <- as.data.frame(matrix(nrow = 18, ncol = 10))
-colnames(output.1) <- c("DGP", "q", "p", "Kernel", "True", "Bias", "SD", "MSE", "CI coverage", "CI length")
[…]

### 2016-02-23 R/simulation.R
Fix the unreproducible issue.
The original code cannot reproduce results because of multiple core. It
is fixed by doRNG. Number of simulations is reduced to 1500. More slackr
added to monitor progress.

@@ -2,24 +2,25 @@ rm(list = ls())
 library(rdrobust)
 library(foreach)
 library(doParallel)
+library(doRNG)
 library(xtable)
-try(source("slackrISE.R"), silent = T)
+try(source("slackrISE.R"), T)
 
 source("RDfunctions.R")
 
 #### for testing in my computer ####
-N.ci <- 20
-level <- 0.95
-N.simu <- 20
-N.core <- 2
-N.bc <- 20
+# N.ci <- 20
+# level <- 0.95
+# N.simu <- 20
+# N.core <- 2
+# N.bc <- 20
 
 #### to run in servor ####
-# N.ci <- 999
-# level <- 0.95
-# N.simu <- 3000
-# N.core <- 15
-# N.bc <- 500
+N.ci <- 999
+level <- 0.95
+N.simu <- 1500
+N.core <- 15
+N.bc <- 500
 
 ## simulation 1: coverage of CI from bootstrap
 
@@ -39,7 +40,7 @@ simulation.1 <- function(model.id, p, q, kernel, bc) {
   cl <- makeCluster(N.core)
   registerDoParallel(cl)
   export.obj <- c("N.ci", "N.bc", "level", "generate.data", "k.weight", "rd.estimate", "lpreg", "rd.ci")
-  collect.simu <- foreach(i=1:N.simu, .combine="rbind", .packages="rdrobust", .export=export.obj, .inorder=F) %dopar% 
+  collect.simu <- foreach(i=1:N.simu, .combine="rbind", .packages="rdrobust", .export=export.obj, .inorder=F) %dorng% 
     simu()
   stopCluster(cl)
   
@@ -68,7 +69,7 @@ simulation.2 <- function(model.id, p, q, kernel) {
   cl <- makeCluster(N.core)
   registerDoParallel(cl)
   export.obj <- c("generate.data", "level")
-  collect.simu <- foreach(i=1:N.simu, .combine="rbind", .packages="rdrobust", .export=export.obj, .inorder=F) %dopar% 
+  collect.simu <- foreach(i=1:N.simu, .combine="rbind", .packages="rdrobust", .export=export.obj, .inorder=F) %dorng% 
     simu()
   stopCluster(cl)
   
@@ -88,34 +89,39 @@ gen.table <- function(model.id, p, q){
   table <- matrix(0, nrow = 4, ncol = 6)
[…]

### 2016-02-23 main_paper.tex
Tweak first assumption
This commit changes the wording in the first assumption a little bit
and directly imposes that the underlying data are iid. It also tweaks
the formatting.

--- 2016-02-21 main_paper.tex
@@
 As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT identification and inference procedures can be developed based on the following assumptions\footnote{The assumptions below are the same as presented by CCT.}
+
 \begin{assumption}[Behavior of the DGP near the cutoff]\label{A1}
- For some $\kappa_{0} > 0$, the following holds in the neighborhood $(-\kappa_{0},\kappa_{0})$ around the cutoff $ \bar{x}= 0$:
+  The random variables $Y_i, X_i$ are i.i.d.\ and
+  there exists a positive number $\kappa_0$ such that the following
+  conditions hold for all $x$ in the neighborhood
+  $(-\kappa_{0},\kappa_{0})$ around zero:
   \begin{enumerate}
-  \item $E[\left.Y_{i}^{4}\right|X_{i}=x]$ is bounded and the density of $X$, $f(x)$, is continuous and bounded away from zero.
-  \item $\mu_{+}(x)=\E[\left.Y_{i}(1)\right|X_{i}=x]$ and $\mu_{-}(x)=\E[\left.Y_{i}(0)\right|X_{i}=x]$ are $S$ times continuously differentiable.
-  \item $\sigma^{2}_{+}(x)=\V[\left.Y_{i}(1)\right|X_{i}=x]$ and $\sigma^{2}_{-}(x)=\V[\left.Y_{i}(0)\right|X_{i}=x]$ are continuous and bounded away from zero.
+  \item $\E[Y_{i}^{4} \mid X_{i}=x]$ is bounded and the density of $X$
+    is continuous and bounded away from zero.
+  \item $\mu_{+}(x) = \E[ Y_{i}(1) \mid X_{i}=x ]$ and
+    $\mu_{-}(x) = \E[ Y_{i}(0) \mid X_{i}=x ]$ are $p+2$ times
+    continuously differentiable.
+  \item $\sigma^{2}_{+}(x)=\V[ Y_{i}(1) \mid X_{i}=x ]$ and
+    $\sigma^{2}_{-}(x)=\V[ Y_{i}(0) \mid X_{i}=x ]$ are continuous and
+    bounded away from zero.
  \end{enumerate}

### 2016-02-23 main_paper.tex
Remove 'kernel' assumption
We are only using the uniform kernel, so kernel assumptions are identical
to bandwidth assumptions.

@@
 Its second part is important for the characterization of the leading bias term that will be the focus of the bias correction procedures described in CCT and in the novel  bootstrap procedure proposed in Section \ref{boot}.
-
-The second set of assumptions regards the possible kernel weights used in RD.
-
-\begin{assumption}[Kernel]\label{A2}
- For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa] \rightarrow \RR$ is bounded and nonnegative, zero outside its support, and positive and continuous on $(0, \kappa)$.
-\end{assumption}
-
-Assumption \ref{A2} supports the kernels most commonly used in applications, in particular the broadly used uniform kernel $k(u)=\1[0\leq u\leq 1]$, which simplifies to the use of a local linear OLS on both sides of the treshold.
-Since the objective of this paper is to present a simple bootstrap procedure to obtain robust confidence intervals in the context of RD designs that can be easily implemented by practitioners, during the remainder of the paper we focus on estimators that use the rectangular kernel.
-The use of different weighting structures implied by different kernels complicates the bootstrap algorithm in meaningful ways and such analysis is left to future work.
 

### 2016-02-23 main_paper.tex
Rewrite first theoretical result and add high-level proof
This commit changes the first bias correction result. Instead of
proving that Delta* is consistent at the 'right' rate, we just
show that the first-stage bias corrected estimator has the same
asymptotic distribution as CCT's bias corrected estimator.

@@
 
-\begin{lemma}\label{L1}
+\begin{theorem}\label{T1}
   Under Assumptions~\ref{A1} and~\ref{A3},
-  $\Delta^* = \E \hat\tau - \tau + o_p()$.
-\end{lemma}
+  $(\hat\tau(h_n,b_n) - \Delta^*(h_n,b_n) - \tau) / V^{1/2}(h_n, b_n) \to^d N(0,1)$.
+\end{theorem}
 
@@
 
-\begin{theorem}\label{T1}
+\begin{theorem}\label{T2}
   Let $\Pr_\tau$ represent the probability distribution of the random variables
@@
 
+\appendix
+\section{Mathematical Appendix}
+\subsection{Proof of Theorem~\ref{T1}}
+We have
+\begin{equation*}
+  \hat\tau - \Delta^* - \tau = (\hat\tau - \E \hat \tau) +
+  (\E \hat \tau - \tau) - (\E^* \hat \tau^* - \tau^*)
+\end{equation*}
+
+The design of the bootstrap ensures that
+\begin{equation*}
+  \label{eq:7}
+  \E^* \hat\mu_{\pm}^*(h) - \mu_{\pm}^{*} = h^{2} \mu_\pm^{*(2)} \Bf_{\pm}(h)/2,
+\end{equation*}
+almost surely, implying that
+\begin{equation*}
+  \label{eq:20}
+    \E^* \hat\tau^{*} - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
+      - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
+\end{equation*}
+Combining this result with CCT's Lemma A1, gives
+\begin{align*}
+  \hat\tau &- \E \hat\tau + (\E \hat\tau - \tau) - (\E^* \hat\tau^* - \tau^*)\\
+  &= \hat\tau - \E\hat\tau
+   + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
+   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
+  &= \hat\tau - \E\hat\tau
+   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2
+   - h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})
+\end{align*}
+The second equality holds because
+$\mu_\pm^{*(2)} = \hat\mu_{\pm}^{(2)}(b_n)$ a.s. Asymptotic normality then
+follows from normality of $\hat\tau - \E\hat\tau$ and
+$\hat\mu_\pm^{(2)}(b_n) - \mu_\pm^{(2)}$ using
+similar arguments to CCT's Lemma SA4.D.\qed
+
 \clearpage

### 2016-02-23 main_paper.tex
Relabel equations and assumptions
Small internal change to the source code: this commit changes the
'labels' used for internal references to be sequential.

@@
 
-\begin{assumption}[Bandwidth]\label{A3}
+\begin{assumption}[Bandwidth]\label{A2}
   Let $h_n$ be the bandwidth used to estimate the local polynomial of
@@
 \begin{algorithm}[Bias estimation]\label{Alg1}
-  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A3} and
+  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A2} and
   define
@@
       \begin{align}
-        \label{eq:2}
         Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
@@
     \begin{equation}
-      \label{eq:4}
+      \label{eq:2}
       \Delta^* = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
@@
 \begin{theorem}\label{T1}
-  Under Assumptions~\ref{A1} and~\ref{A3},
+  Under Assumptions~\ref{A1} and~\ref{A2},
   $(\hat\tau(h_n,b_n) - \Delta^*(h_n,b_n) - \tau) / V^{1/2}(h_n, b_n) \to^d N(0,1)$.
@@
     \begin{equation}
-      \label{eq:6}
+      \label{eq:3}
       \hat\varepsilon_i =
@@
 \begin{lemma}\label{L2}
-  Under Assumptions~\ref{A1} and~\ref{A3},
+  Under Assumptions~\ref{A1} and~\ref{A2},
   $\Delta^{**} = \E^* \hat\tau^* - \tau^* + o_{p^*}(-)$.
@@
   under the assumption that $\tau$ is the true value of the ATE and suppose
-  Assumptions~\ref{A1} and~\ref{A3} hold. Then
+  Assumptions~\ref{A1} and~\ref{A2} hold. Then
   \begin{equation}
-    \label{eq:5}
+    \label{eq:4}
     \plim_{n \to \infty} \sup_\tau
@@
 \begin{equation*}
-  \label{eq:7}
+  \label{eq:5}
   \E^* \hat\mu_{\pm}^*(h) - \mu_{\pm}^{*} = h^{2} \mu_\pm^{*(2)} \Bf_{\pm}(h)/2,
@@
 \begin{equation*}
-  \label{eq:20}
+  \label{eq:6}
     \E^* \hat\tau^{*} - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2

### 2016-02-24 main_paper.tex
Rewrite second mathematical result and start its proof
This commit rewrites the second mathematical result and restates
it as a theorem that the 'double bootstrap' procedure accurately
approximates the asymptotic distribution of the bias-corrected
statistic we propose in Theorem and Algorithm 1.

This commit also has the first draft of a proof of the second
theorem as well as a crucial supporting lemma that actually
proves normality. There are still some steps missing and some
of the scaling factors are not yet correct. So there's work to
be done!

@@
  \begin{align}
-  \mu(x)= \E[Y_{i}|X_{i}=x]
+  \mu(x)= \E[Y_{i} \mid X_{i}=x]
  \end{align}
@@
 In most cases the population parameter of interest is 
-$\tau=\E[Y(1)-Y(0)|X=\bar{x}]$ (i.e., the average treatment effect
+$\tau=\E[Y(1)-Y(0) \mid X=\bar{x}]$ (i.e., the average treatment effect
 at the threshold). Under continuity and smoothness conditions on both the 
 conditional distribution of $X_i$ and the first moments of $Y(0)$ and $Y(1)$ at
-the cutoff, $\tau$ is nonparametrically identifiable (Hahn, Todd and Van der 
-Klaauw, 2001) by:
-\begin{align}
- \tau&= \mu_{+}- \mu_{-} \nonumber \\ 
-&\text{ where } \mu_{+}=lim_{x \rightarrow 0^{+}}\mu(x),\text{ and } 
-\mu_{-}=lim_{x \rightarrow 0^{-}}\mu(x)
-\end{align}
+the cutoff, $\tau$ is nonparametrically identifiable
+$\tau = \mu_{+}- \mu_{-}$
+where $\mu_{+}=lim_{x \rightarrow 0^{+}}\mu(x)$ and
+$\mu_{-}=lim_{x \rightarrow 0^{-}}\mu(x)$
+(Hahn, Todd and Van der Klaauw, 2001)
 
 Naturally, the estimation of $\tau$ in RD designs focuses on the 
-problem of approximating $\E[Y(1)|X=x]$ and $\E[Y(0)|X=x]$
+problem of approximating $\E[Y(1) \mid X=x]$ and $\E[Y(0) \mid X=x]$
 near the cutoff. Due to its desirable properties when estimating regression 
 functions at boundary points, we consider the popular approach of fitting 
-separate kernel-weighted local linear regressions in neighborhoods on both 
+local linear regressions in neighborhoods on both
 sides of the threshold.\footnote{See \cite{HTV2001}, \cite{Porter03} or
@@
  \hat{\tau}(h_{n})&=\hat {\mu}_{+}(h_{n}) -\hat{\mu}_{-}(h_{n})\\
-(\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= argmin_{b_{0},b_{1}} 
-\sum_{i=1}^{N}\1\{X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \cdot K_{h}(X_{i})\\
-(\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= argmin_{b_{0},b_{1}}
-\sum_{i=1}^{N}\1\{X_{i} < 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2}\cdot K_{h}(X_{i})
+(\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= \argmin_{b_{0},b_{1}}
+\sum_{i=1}^{N}\1\{h_n > X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \\
+(\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= \argmin_{b_{0},b_{1}}
+\sum_{i=1}^{N}\1\{0 > X_{i} > -h_n \}(Y_{i}-b_{0}-X_{i}b_{1})^{2}
 \end{align*}
-where $K_{h}(x_{i}) = K\left(\frac{x_{i}}{h}\right)\frac{1}{h}$.
 
@@
 \begin{assumption}[Bandwidth]\label{A2}
-  Let $h_n$ be the bandwidth used to estimate the local polynomial of
-  order $p$ and let $b_n$ be the bandwidth used for $p+1$. Then
-  $h_n = o(n^{-1/5})$, $b_n = o(n^{-1/5})$, $n h_n \to \infty$, and
-  $n b_n \to \infty$ as $n \to \infty$.\footnote{%
-    Unless otherwise stated, all limits in this paper are assumed to
-    hold as $n \to \infty$.} %
+  Let $h_n$ be the bandwidth used to estimate the local linear model and let
+  $b_n$ be the bandwidth used for a local quadratic model. Then
+  $n h_n \to \infty$, $n b_n \to \infty$, $n h_n^5 b_n^2 \to 0$, and
+  $n b_n^5 h_n^2 \to 0$ as $n \to \infty$.\footnote{%
+    Unless otherwise stated, all limits in this paper are assumed to hold as
+    $n \to \infty$.} %
   The relationship $h_n \leq b_n$ also holds for all $n$.
@@
  \begin{align}
-  T(h_{n})=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), \text{        }V(h_{n})=\V[\left.\tau(h_{n})\right|\chi_{n}], \text{        }\chi_{n}=[X_{1}, \dots X_{n}]^{\prime}
+  T(h_{n}) &=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), &
+  V(h_{n}) &=\V[\tau(h_{n}) \mid X_1,\dots,X_n]
  \end{align}
@@
 \begin{align*}
-     \E[\hat{\tau}(h_{n})|\chi_{n}]-\tau=& h_{n}^{2}\Bs(h_{n})\{1+o_{p}(1)\}\\
+     \E[\hat{\tau}(h_{n}) \mid \chi_{n}]-\tau=& h_{n}^{2}\Bs(h_{n})\{1+o_{p}(1)\}\\
      \Bs(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\Bf_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\Bf_{-}(h_{n})
@@
 \end{align*}
-Two results follow. The first is that the secondary bootstrap step produces
-a consistent estimator of the bias under the bootstrap distribution. The
-second is that the intervals overall are asymptotically valid.
 
-\begin{lemma}\label{L2}
-  Under Assumptions~\ref{A1} and~\ref{A2},
-  $\Delta^{**} = \E^* \hat\tau^* - \tau^* + o_{p^*}(-)$.
-\end{lemma}
+Theorem~\ref{T2} establishes that this ``bootstrap-within-bootstrap''
+approximates the asymptotic distribution of the bias-corrected
+statistic proposed by Algorithm~\ref{Alg1} and justifies this second
+algorithm.
 
 \begin{theorem}\label{T2}
-  Let $\Pr_\tau$ represent the probability distribution of the random variables
-  under the assumption that $\tau$ is the true value of the ATE and suppose
-  Assumptions~\ref{A1} and~\ref{A2} hold. Then
-  \begin{equation}
+  Under Assumptions~\ref{A1} and~\ref{A2},
+  \begin{gather}
     \label{eq:4}
-    \plim_{n \to \infty} \sup_\tau
-    \Pr_\tau[\hat\ell(\alpha) \leq \tau \leq \hat u(\alpha)] \geq 1 - \alpha.
-  \end{equation}
-  Both of the one-sided intervals are asymptotically valid under the same
-  assumptions as well:
-  \begin{align}
-    \plim_{n \to \infty} \sup_\tau
-    \Pr_\tau[\hat\ell(\alpha) \leq \tau ] &\geq 1 - \alpha / 2, &
-    \plim_{n \to \infty} \sup_\tau
-    \Pr_\tau[\tau \leq \hat u(\alpha)] &\geq 1 - \alpha / 2.
-  \end{align}
+    \V^*(\hat\tau^{*} - \Delta^{**})/V(h_n,b_n) \to^p 1
+  \intertext{and}
+  \label{eq:5}
+    \sup_{x}
+    \Big\rvert \Pr^*[\hat\tau^{*} - \Delta^{**} - \tau^* \leq x ]
+    - \Pr[\hat\tau - \Delta^* - \tau \leq x] \Big\lvert \to^p 0.
+  \end{gather}
 \end{theorem}
@@
 
-\appendix
+\newpage\appendix
 \section{Mathematical Appendix}
@@
 \end{equation*}
-
 The design of the bootstrap ensures that
 \begin{equation*}
-  \label{eq:5}
-  \E^* \hat\mu_{\pm}^*(h) - \mu_{\pm}^{*} = h^{2} \mu_\pm^{*(2)} \Bf_{\pm}(h)/2,
+  \label{eq:6}
+  \E^* \hat\mu_{\pm}^*(h_n) - \mu_{\pm}^{*} =
+  h_n^{2} \mu_\pm^{*(2)} \Bf_{\pm}(h_n)/2,
 \end{equation*}
@@
 \begin{equation*}
-  \label{eq:6}
+  \label{eq:7}
     \E^* \hat\tau^{*} - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
@@
 
+\subsection{Proof of Theorem~\ref{T2}}
+We can repeat the steps from Theorem~\ref{T1}'s proof to show that
+\begin{align*}
+  \hat\tau^* - \Delta^{**} - \tau^* &= (\hat\tau^* - \E^* \hat \tau^*) +
+  (\E^* \hat \tau^* - \tau^*) - (\E^{**} \hat \tau^{**} - \tau^{**}) \\
+  &= \hat\tau^* - \E^*\hat\tau^*
+   + h_n^2 (\hat\mu_-^{*(2)}(b_n) - \mu_-^{*(2)}) \Bf_{-}(h_{n}) /2
+   - h_n^2 (\hat\mu_+^{*(2)}(b_n) - \mu_+^{*(2)}) \Bf_{+}(h_{n}) / 2.
+\end{align*}
+Consequently, the asymptotic behavior of
+$\hat\tau^* - \Delta^** - \tau^*$ is determined by the behavior of
+$\hat\tau^* - \E^*\hat\tau*$ and
+$\hat\mu_{\pm}^{*(2)} - \mu_\pm^{*(2)}$ and these random variables are
+weighted averages of the sums
+\begin{equation*}
+  \sum_{i \in I^{\pm}(b_n)} Z_i \varepsilon_i^*
+\end{equation*}
+with $Z_i = (1, X_i, X_i^2)'$. By construction,
+\begin{equation*}
+  \V^*\Big(\ssum{i}{b_n} Z_i \varepsilon_i^* \Big)
+  = \hat\sigma_\pm^2(b_n) \Gamma_\pm(b_n)
+\end{equation*}
+almost surely, making~\eqref{eq:4} a consequence of CCT's SA?.
+
+For~\eqref{eq:5}, since $\hat\tau - \Delta^*$ is itself asymptotically
+normal, it suffices to prove the pointwise result
+\begin{equation}
+  \label{eq:8}
+  \Big\rvert \Pr^*[(\hat\tau^{*} - \Delta^{**} - \tau^*)
+  / V^{1/2}(h_n,b_n) \leq x ] - \Phi(x)] \Big\lvert \to^p 0.
+\end{equation}
+for all $x$. Since the limiting distribution is continuous, an
+argument attributed to Poly\'a immediately extends the pointwise
+convergence result to the uniform result stated in~\eqref{eq:5}. (See
+van der vaart, p. for the details of the argument.) But~\eqref{eq:8}
+follows from Lemma~\ref{L1} as well, completing the proof.\qed
+
+\subsection{Supporting results}
+
+\begin{lemma}\label{L1}
+  Define $Z_i = (1, X_i, X_i^2)$.  Under Assumptions~\ref{A1} and~\ref{A2},
+  \begin{equation}
+    \label{eq:9}
+    \Big\rvert \Pr^*\Big[ \Gamma_\pm(b_n)^{-1/2}
+    \sum_{i \in I^{\pm}(b_n)} Z_i \varepsilon_i^* / \hat\sigma_\pm(b_n) < x \Big]
+    - \Phi(x) \Big\lvert \to^p 0.
+  \end{equation}
+\end{lemma}
+
+\begin{proof}
+  Let $z_i = \alpha' Z_i$ for an arbitrary nonzero $\alpha$ and define
+  $\gamma_\pm(b_n) = \alpha'\Gamma_\pm(b_n)\alpha$. We will
+  establsh asymptotic normality for the scalar $z_i \varepsilon_i^*$;
+  the multivariate case follows via the Cram\'er-Wold device. (cite
+  van der vaart.)
+
+  Define the filtration
+  \begin{equation}
+    \label{eq:10}
+    \Fc_j^{*\pm} = \sigma(Y_1,\dots,Y_n; X_1,\dots,X_n;
+    \varepsilon_{i_1}^{*\pm},\dots,\varepsilon_{i_j}^{*\pm})
+  \end{equation}
+  where the values $i_1, i_2,\dots, i_{M_h^{\pm}}$ form an ordering of
+  all of the elements of $I_n^\pm$. (The specific order is
+  unimportant.) Then
+  $\{z_{i_j} \varepsilon_{i_j}^{*\pm}, \Fc_j^{*\pm}\}$ is a martingale
+  difference sequence and~\eqref{eq:9} holds if
+  \begin{equation}
+    \label{eq:11}
+    \savg{i}{h} z_{i}^2 \varepsilon_{i}^{*\pm\,2} -
+    \gamma_{\pm}^*(b_n) \hat\sigma
+    \to^p 0
+  \end{equation}
+  and, for all
+  $\delta > 0$,
+  \begin{equation}
+    \label{eq:12}
+    \oavg{j}{h} z_{i_j}^2 \E^*( \varepsilon_{i_j}^{*\pm\,2}
+    \1\{z_{i_j}^2 \varepsilon_{i_j}^{*\pm\,2} / M_h^\pm > \delta \}
+    \mid \Fc_{j-1}^{\pm}) \to^p 0.
+  \end{equation}
+  (cite Hall and Heyde.)
+
+  For~\eqref{eq:11}, observe that
+  $\{z_{i_j}^2 (\varepsilon_{i_j}^{*2} - \hat\sigma^2_\pm(b_n)), \Fc_j^\pm\}$
+  is also a martingale difference sequence so convergence follows from
+  the LLN.
+
+  For~\eqref{eq:12}, we have
+  \begin{align*}
+    \oavg{j}{h} z_{i_j}^2 \E^*( \varepsilon_{i_j}^{*\pm\,2}
+    \1\{z_{i_j}^2 \varepsilon_{i_j}^{*\pm\,2} / M_h^\pm > \delta \}
+    \mid \Fc_{j-1}^{\pm})
+    &= \oavg{i}{h_n} z_i^2 \oavg{j}{b_n} \hat\varepsilon_{j}^{\pm 2}
+      \1\{\hat\varepsilon_{j}^{\pm 2} > \delta M_n^{\pm} / z_i^2 \} \\
+  \end{align*}
+  (Finish with: $\varepsilon_i^2$ is uniformly integrable,
+  $\hat\varepsilon_i^2$ gets arbitrarily close to $\varepsilon_i^2$)
+\end{proof}
+
 \clearpage

### 2016-02-24 main_paper.tex
This commit adds a paragraph to Intro and the bibliography. Something odd is happening with Van Der Klaauw 2002 cite. I also edited the setup file to include natbib package.

@@
 
-\begin{abstract}\noindent%
+\begin{abstract}\noindent
   This paper develops a novel bootstrap procedure to obtain robust
@@
   use the uniform kernel. The procedure uses a residual bootstrap to estimate
-  the bias of the RD estimator, which is then removed from the original RD
-  estimator. The bias-corrected estimator is then bootstrapped itself to
+  the bias of the RD estimator, which is then removed from the original estimator.
+ The bias-corrected estimator is then bootstrapped itself to
   generate valid confidence intervals. This procedure is valid for empirically
@@
 estimator above and below the cutoff within bandwidths chosen to minimize the 
-asymptotic mean squared error (AMSE) as proposed by Imbens and Kalyanaraman(2012)
+asymptotic mean squared error (AMSE) as proposed by \cite{IK}
 and extended by \cite{calonico2014} (CCT, henceforth).
+
+RD designs have been used as a strategy to estimate effects of interest in a large range of topics in several areas.
+For just a few examples, RD designs are common in education, evaluating the impact of investments in school facilities, class sizes, remedial education, early childhood education, and financial aid effects on student achievement and later outcomes \citep{cellini2010,urquiola2009,jacoblefgren2004,ludwig2007,vdk2002}; in health by analyzing the impact of healthcare provision through Medicare, and neo-natal care on low birth weight children mortality \citep{Card2009,barreca2011saving}; in political science providing evidence regarding incumbency advantage in elections, electoral enfranchising and policy changes associated with the introduction of electronic voting, strategic voting behavior, and local media effects and ad expenditure in presidential elections in the U.S.
+\citep{lee2008,Caughey2011,erikson2015,Fujiwara2015,Fujiwara2011,keele2014geographic}.
+Several more examples of the breadth of RD designs are listed by \cite{lee2010}.
 

### 2016-02-24 main_paper.tex
This commit adds a couple of paragraphs about CCT and our procedure at the Intro. I am not happy with the description of the bootstraps in general. Let me know if I said something stupid in addition of being too vague.

@@
 RD designs have been used as a strategy to estimate effects of interest in a large range of topics in several areas.
-For just a few examples, RD designs are common in education, evaluating the impact of investments in school facilities, class sizes, remedial education, early childhood education, and financial aid effects on student achievement and later outcomes \citep{cellini2010,urquiola2009,jacoblefgren2004,ludwig2007,vdk2002}; in health by analyzing the impact of healthcare provision through Medicare, and neo-natal care on low birth weight children mortality \citep{Card2009,barreca2011saving}; in political science providing evidence regarding incumbency advantage in elections, electoral enfranchising and policy changes associated with the introduction of electronic voting, strategic voting behavior, and local media effects and ad expenditure in presidential elections in the U.S.
+For just a few examples, RD designs are common in education, evaluating the impact of investments in school facilities, class sizes, remedial education, early childhood education, and financial aid effects on student achievement and later outcomes \citep{cellini2010,urquiola2009,jacoblefgren2004,ludwig2007,vdk2002}; in health by analyzing the impact of healthcare provision through Medicare, and neo-natal care on low birth weight children mortality \citep{Card2009,barreca2011saving}; in political science, providing evidence regarding incumbency advantage in elections, electoral enfranchising and policy changes associated with the introduction of electronic voting, strategic voting behavior, and local media effects and ad expenditure in presidential elections in the U.S.
 \citep{lee2008,Caughey2011,erikson2015,Fujiwara2015,Fujiwara2011,keele2014geographic}.
@@
 
-Recently, CCT brought attention to the fact that the popular implementation of RD designs coupling optimal-AMSE bandwidths
-and local polynomial estimation provides confidence intervals (CIs) with
-incorrect coverage due to the presence of bias and propose an explicit analytical
-bias correction procedure that re-centers and re-scale the CI by estimating a higher 
-order approximation of the bias term and adjustment its lenght to account for 
-the variation introduced by the bias estimation.
+Recently, CCT brought attention to the fact that the popular implementation of RD designs coupling local polynomial estimation and optimal-AMSE bandwidths (as proposed by \cite{IK})
+provides confidence intervals (CIs) with incorrect coverage.
+They argue that the bandwidth selectors typically produce bandwidths that are too ``large,'' leading to a significant bias in the asymptotic distribution of the estimator.
+In that case the usual``naive'' confidence intervals for the RD treatment effects may be biased and will have provide coverage potentially well below their nominal level.
+
+Then, CCT proposes a bias-correction procedure based on estimating the leading term of the bias to account for the effect of the ``large'' bandwidth and then obtain a re-centered t-statistic.
+This conventional bias-correction has poor finite-sample performance that arises from the estimation of the bias leading term, so they provide a new standard error formula for the standard error to  account for the additional variability introduced by the estimated bias.
+The resulting statistic that combines the higher-order($p+1$) leading term bias correction and rescaling the of the t-statistic remains asymptotically normal and supplies valid confidence intervals.
 
@@
 bootstrap procedure to correct the first order bias term and directly obtain 
-valid CIs that provide the correct coverage. The algorithm proposed is easy to
-implement and rely on the same conditions as the explicit bias correction
-proposed by CCT.
+valid CIs that provide the correct coverage.
+
+The algorithm proposed draws on the main intuition put forward by CCT, that is, that correcting for the leading bias term (of order $p+1$) addresses the recentering needed for the confidence intervals.
+Hence, we propose that, after obtaining the usual RD estimates using a local polynomial of order $p$, obtain a estimates for a polynomial of order $p+1$ and generate our bootstrap datasets by bootstrapping the residuals of that polynomial.
+Since in the bootstrap datasets the bias of the estimates obtained using a lower order polynomial is known, we can estimate the leading term of the bias by averaging across bootstraps and finally subtract it from the original RD estimator.
+
+Just as in CCT, this bias correction introduces additional variability due to the estimated bias, so we approximate the distribution of the bias-corrected estimator with a second residual bootstrap in which both the usual RD estimate and the full bias correction procedure are bootstrapped.
 
@@
 CCT while sidestepping the need to derive analytical formulas in each case of interest.
+
+Note that the procedure as presented here only works for the uniform kernel, sharp RD designs, and i.i.d.
+data.
+Extensions to other kernels, higher order discontinuities, cross-sectional dependence, and the fuzzy RD design is the subject of ongoing research.
 

### 2016-02-24 main_paper.tex
Couple of typos.

@@
 
-Note that the procedure as presented here only works for the uniform kernel, sharp RD designs, and i.i.d.
+Note that the procedure as presented here only coversr the uniform kernel, sharp RD designs, and i.i.d.
 data.
-Extensions to other kernels, higher order discontinuities, cross-sectional dependence, and the fuzzy RD design is the subject of ongoing research.
+Extensions to other kernels, higher order discontinuities, cross-sectional dependence, and the fuzzy RD design are subject of ongoing research.
 

### 2016-02-25 main_paper.tex
Small changes to text and latex code in Sections 2 and 3. Still not happy with it though.

@@
 conditional distribution of $X_i$ and the first moments of $Y(0)$ and $Y(1)$ at
-the cutoff, $\tau$ is nonparametrically identifiable
+the cutoff, $\tau$ is nonparametrically identifiable by
 $\tau = \mu_{+}- \mu_{-}$
@@
 higher order polynomials and discontinuities at derivatives, like ``Kink RDD''. We focus on the linear case for ease in exposition.}
-For the local linear model, we use the following estimator as described in 
-\cite{calonico2014},\footnote{Throughout the paper we follow the
-notation on CCT very closely.}
+For the local linear model,
 \begin{align*}
@@
 
-As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT identification and inference procedures can be developed based on the following assumptions\footnote{The assumptions below are the same as presented by CCT.}
+As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT identification and inference procedures can be developed based on the following assumptions.\footnote{The assumptions below are the same as presented by CCT.}
 
 \begin{assumption}[Behavior of the DGP near the cutoff]\label{A1}
-  The random variables $Y_i, X_i$ are i.i.d.\ and
+  The random variables $Y_{i}, X_{i}$ are i.i.d.\ and
   there exists a positive number $\kappa_0$ such that the following
@@
 \begin{assumption}[Bandwidth]\label{A2}
-  Let $h_n$ be the bandwidth used to estimate the local linear model and let
-  $b_n$ be the bandwidth used for a local quadratic model. Then
-  $n h_n \to \infty$, $n b_n \to \infty$, $n h_n^5 b_n^2 \to 0$, and
-  $n b_n^5 h_n^2 \to 0$ as $n \to \infty$.\footnote{%
+  Let $h_{n}$ be the bandwidth used to estimate the local linear model and let
+  $b_{n}$ be the bandwidth used to estimate a local quadratic model. Then
+  $n h_{n} \to \infty$, $n b_{n} \to \infty$, $n h_{n}^{5} b_{n}^{2} \to 0$, and
+  $n b_{n}^{5} h_{n}^{2} \to 0$ as $n \to \infty$.\footnote{%
     Unless otherwise stated, all limits in this paper are assumed to hold as
     $n \to \infty$.} %
-  The relationship $h_n \leq b_n$ also holds for all $n$.
+  The relationship $h_{n} \leq b_{n}$ also holds for all $n$.
 \end{assumption}
 
-\cite{calonico2014} point out that the conventional approaches to construct confidence intervals for $\tau$ using the local linear estimator rely on a large-sample approximation for the standardized $t$-statistic that is valid only if the bandwidth shrink fast enough to eliminate the leading bias term contribution to the approximation.
+CCT point out that the conventional approaches to construct confidence intervals for $\tau$ using the local linear estimator rely on a large-sample approximation for the standardized $t$-statistic that is valid only if the bandwidth shrink fast enough to eliminate the leading bias term contribution to the approximation.
 Hence, if $nh_{n}^{5}\rightarrow0$ and $nh_{n}\rightarrow \infty$, then
@@
   T(h_{n}) &=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), &
-  V(h_{n}) &=\V[\tau(h_{n}) \mid X_1,\dots,X_n]
+  V(h_{n}) &=\V[\tau(h_{n}) \mid X_{1},\dots,X_{n}]
  \end{align}
@@
 
-\cite{calonico2014} resolve the problem by deriving the analytical form of the first-order bias and correcting it directly.
+CCT solve the problem by deriving the analytical form of the first-order bias and correcting it directly.
 To obtain correct coverage the confidence interval needs not only to be re-centered to correct the bias, but also rescaled to allow for the additional variability introduced by the bias correction.
@@
 This approach is shown by the authors to significantly improve coverage of the CIs constructed and provides practitioners with a new tool set to perform inference that is more robust to the choice of bandwidth.
-We build upon the insight provided by CCT bias-corrected estimator and propose a simple bootstrap procedure that can directly construct the robust CIs without requiring the derivation of analytical formulas and direct estimators for the bias, variance and covariance terms, while relying on the same first-order bias correction approximation proposed by that paper.
+We build upon the insight provided by CCT bias-corrected estimator and propose a simple bootstrap procedure that can directly construct the robust CIs without requiring the derivation of analytical formulas and direct estimators for the bias, variance and covariance terms, while relying on the same first-order bias correction approximation.
 
@@
 Building upon the results and intuition developed by CCT we propose to implement a first-order bias correction and obtain valid CIs through a bootstrap procedure.
-Intuitively, for the local-linear RD estimator's case, we will rely on a local higher-order (quadratic) polynomial approximation for the conditional outcome around the cutoff to capture the potential bias present in the original RD estimate.
-This insight comes directly from CCT using the same local quadratic approximation to estimate bias term as presented in Section \ref{background}.
+Intuitively, for the local-linear RD estimator's case, we will rely on a local quadratic polynomial approximation for the conditional outcome around the cutoff to capture the potential bias present in the original RD estimate.
+This insight comes directly from CCT's results using the same local quadratic approximation to estimate bias term as presented in Section \ref{background}.
 
-The first algorithm describes how to use local linear regression to obtain a point estimate and perform bias correction with local quadratic regression.
-The second algorithm describes how to obtain its confidence interval with correct coverage.
+The first algorithm describes how to obtain a point estimate and perform the bias correction.
+The second algorithm obtains its confidence interval with correct coverage.
 For simplicity, we adopt the same optimal-AMSE bandwidth selector proposed by CCT.\footnote{An interesting question is whether one could use a bootstrap based procedure to select a bandwidth that would achieve similar (or improved) results.
@@
 Essentially, we apply CCT's insight that a polynomial one order higher can capture the first-order bias behavior and create a bootstrap procedure that can correctly mimic the behavior of the bias present in the original estimator.
-For such, for a chosen bandwidth, we estimate a local quadratic regression the same way CCT suggested but then create bootstrap data by imposing the local quadratic functional form as the DGP.
-Then, in the ``bootstrap data'' the DGP is known.
+For such, for a chosen bandwidth, we estimate a local quadratic regression as suggested by CCT, but then bootstrap data by imposing the local quadratic functional form as the DGP.
+Then, in the bootstrap data the DGP is known.
 Let the ``true'' treatment effect under the bootstrap DGP be denoted by $\tau^{*}$.
@@
 Hence, the bias for a specific bootstrap data is given by $\tau^{*}-\hat{\tau}^{*}$.
-More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\Bs}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates,i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
+More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\Bs}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates, i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
 Algorithm~\ref{Alg1} describes this procedure step-by-step for clarity.
@@
 \begin{algorithm}[Bias estimation]\label{Alg1}
-  Assume $h_n$ and $b_n$ are bandwidths as described by Assumption~\ref{A2} and
-  define
+  Assume $h_{n}$ and $b_{n}$ are bandwidths as described by Assumption~\ref{A2} and define
   \begin{align}
-    I^-(h) &= \{i : h < X_i < 0\}, &
-    I^+(h) &= \{i : 0 < X_i < h\}.
+    I^{-}(h) &= \{i : h < X_{i} < 0\}, &
+    I^{+}(h) &= \{i : 0 < X_{i} < h\}.
   \end{align}
-  Also define $M^-(h_n)$ and $M^+(h_n)$ to be the number of elements in
-  $I^-(h_n)$ and $I^+(h_n)$ respectively.
+  Also define $M^{-}(h_{n})$ and $M^{+}(h_{n})$ to be the number of elements in
+  $I^{-}(h_{n})$ and $I^{+}(h_{n})$ respectively.
   \begin{enumerate}
-  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
+  \item Estimate the local polynomials $g_{p+1}^{+}$ and $g_{p+1}^{-}$ as defined by
     Equation --- and define the residuals
@@
       \label{eq:1}
-      \hat\varepsilon_i =
+      \hat\varepsilon_{i} =
       \begin{cases}
-        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
-        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
+        Y_{i} - \hat g_{p+1}^-(X_{i}) & \textif\ X_{i} < 0 \\
+        Y_{i} - \hat g_{p+1}^+(X_{i}) & \otherwise
       \end{cases}

### 2016-02-26 main_paper.tex
Change the formatting and position of 'don't cite' text

@@
 Bartalotti: Email: bartalot@iastate.edu. Calhoun: gcalhoun@iastate.edu.
-He: yanghe@iastate.edu.} \\ PRELIMINARY AND INCOMPLETE \\PLEASE DO NOT CITE OR CIRCULATE WITHOUT PERMISSION}
+He: yanghe@iastate.edu.}}
 
@@
 
+\paragraph{Important message from the authors:} This version of the paper is
+very preliminary and incomplete. We have sent out a few early copies to get
+feedback, but there are still serious errors that we have not addressed. Please
+do not cite this paper or circulate it in its current form.
+
+\newpage
 \section{Introduction}
@@
 The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed by \cite{lee2008} and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and therefore bias in the usual RD approach.
-For the simulation studies, we used 250 bootstraps for bias correction, 999 bootstraps to calculate confidence interval and a total 500 replications.
-All results presented are based on a 0.95 desired confidence level.
-Table1 presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$).
-Table 2 presents similar results for $p=2$ and $q=3$.
+For each DGP, we used four methods to obtain point estimate and 0.95 confidence interval.
+For each method, a total 1500 replications were performed.
+The first two methods follow CCT procedure with triangular and uniform kernel.
+The third and fourth methods follow the bootstrap procedure with uniform kernel.
+The only difference between the last two is that one is bias corrected and the other is not.
+In the bootstrap procedure, we used 500 bootstraps for bias correction, 999 bootstraps to calculate confidence interval.
+Table \ref{Tb: simulation 1} presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$).
+Table \ref{Tb: simulation 2} presents similar results for $p=2$ and $q=3$.
 
-\begin{table}[t] \label{Tb1}
+\begin{table}[t]
 \centering
@@
   \midrule
-  1   & bootstrap & --0.013 & 0.067 & 0.068 & 0.938       & 0.243     \\
-      & CCT       & --0.016 & 0.068 & 0.070 & 0.908       & 0.244     \\
-  2   & bootstrap & --0.014 & 0.083 & 0.084 & 0.954       & 0.319     \\
-      & CCT       & --0.014 & 0.092 & 0.093 & 0.928       & 0.350     \\
-  3   & bootstrap & --0.006 & 0.069 & 0.070 & 0.956       & 0.247     \\
-      & CCT       & --0.004 & 0.071 & 0.071 & 0.918       & 0.249     \\
+	1 & $CCT_{tri}$ & -0.010 & 0.068 & 0.068 & 0.911 & 0.241 \\ 
+	  & $CCT_{uni}$ & -0.016 & 0.067 & 0.069 & 0.924 & 0.246 \\ 
+	  & $bootstrap_{uni}$       & -0.018 & 0.066 & 0.069 & 0.931 & 0.240 \\ 
+	  & $bootstrap_{uni}^{nbc}$ & -0.020 & 0.060 & 0.064 & 0.916 & 0.208 \\
+	\midrule
+	2 & $CCT_{tri}$ & -0.011 & 0.085 & 0.086 & 0.935 & 0.343 \\ 
+	  & $CCT_{uni}$ & -0.010 & 0.087 & 0.088 & 0.938 & 0.350 \\ 
+	  & $bootstrap_{uni}$       & -0.012 & 0.088 & 0.089 & 0.953 & 0.324 \\ 
+	  & $bootstrap_{uni}^{nbc}$ & -0.051 & 0.086 & 0.100 & 0.869 & 0.300 \\ 
+	\midrule
+	3 & $CCT_{tri}$ & -0.008 & 0.067 & 0.067 & 0.919 & 0.246 \\ 
+	  & $CCT_{uni}$ & -0.004 & 0.065 & 0.065 & 0.943 & 0.250 \\ 
+	  & $bootstrap_{uni}$       & -0.004 & 0.064 & 0.064 & 0.960 & 0.246 \\ 
+	  & $bootstrap_{uni}^{nbc}$ & 0.016 & 0.062 & 0.064 & 0.931 & 0.218 \\ 
   \bottomrule
@@
 \caption{Summary of estimates ($p = 1, q = 2$)}
+\label{Tb: simulation 1}
 \end{table}
 
-As can be seen on the tables above, the bootstrap bias-correction procedure
-proposed in this paper provides a simple alternative to obtain valid robust
-confidence intervals in RD designs and performs well compared to the analytical 
-bias correction procedures proposed by CCT.
+As can be seen on the tables, the bootstrap bias-correction procedure proposed in this paper provides a simple alternative to obtain 
+valid robust confidence intervals in RD designs and performs well compared to the analytical 
+bias correction procedures proposed by CCT. The results also demonstrate the importance of bias correction when huge kink 
+presents at the cutoff (such as in the second DGP). Failing to correct bias in this case leads to a confidence interval with incorrect coverage.
 
-\begin{table}[t]\label{Tb2}
+\begin{table}[t]
 \centering
@@
   \midrule
-  1   & bootstrap & --0.002 & 0.075 & 0.075 & 0.958       & 0.295     \\
-      & CCT       & --0.004 & 0.082 & 0.082 & 0.926       & 0.295     \\
-  2   & bootstrap & 0.002   & 0.087 & 0.086 & 0.934       & 0.302     \\
-      & CCT       & --0.005 & 0.078 & 0.078 & 0.960       & 0.323     \\
-  3   & bootstrap & --0.008 & 0.083 & 0.083 & 0.942       & 0.292     \\
-      & CCT       & --0.003 & 0.080 & 0.080 & 0.938       & 0.295     \\
+    1 & $CCT_{tri}$ & -0.006 & 0.079 & 0.079 & 0.923 & 0.291 \\ 
+      & $CCT_{uni}$ & -0.003 & 0.081 & 0.081 & 0.932 & 0.299 \\ 
+      & $bootstrap_{uni}$       & -0.003 & 0.079 & 0.079 & 0.947 & 0.294 \\ 
+      & $bootstrap_{uni}^{nbc}$ & -0.008 & 0.073 & 0.074 & 0.941 & 0.261 \\ 
+     \midrule
+    2 & $CCT_{tri}$ & -0.007 & 0.080 & 0.080 & 0.941 & 0.319 \\ 
+      & $CCT_{uni}$ & -0.005 & 0.081 & 0.081 & 0.946 & 0.326 \\ 
+      & $bootstrap_{uni}$       & -0.008 & 0.080 & 0.080 & 0.955 & 0.300 \\ 
+      & $bootstrap_{uni}^{nbc}$ & -0.020 & 0.075 & 0.078 & 0.924 & 0.273 \\ 
+     \midrule
+    3 & $CCT_{tri}$ & 0.004 & 0.080 & 0.080 & 0.922 & 0.291 \\ 
+      & $CCT_{uni}$ & -0.004 & 0.082 & 0.082 & 0.931 & 0.296 \\ 
+      & $bootstrap_{uni}$       & 0.002 & 0.077 & 0.077 & 0.958 & 0.294 \\ 
+      & $bootstrap_{uni}^{nbc}$ & -0.001 & 0.073 & 0.073 & 0.948 & 0.260 \\ 
   \bottomrule
@@
 \caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
+\label{Tb: simulation 2}
+\end{table}
+
+\section{Application}\label{application}
+
+In this section, we apply the bootstrap procedure to the data\footnote{The data is publicly available from http://faculty.econ.ucdavis.edu/faculty/dlmiller/statafiles/.} used in \cite{ludwig2007}.
+In their paper, the effects of Head Start application assistance on federal spending, mortality and education attainment were investigated under standard RD design.
+They utilized the fact that grant-writing assistance were offered only to the poorest 300 counties to identify the average treatment effect (ATE) at the cutoff.
+
+We estimate the ATE with alternative procedures and compare the new estimates with results in \cite{ludwig2007}.
+Bias-corrected point estimates and robust confidence intervals are reported.
+For completeness, we also include results following the procedure proposed by CCT.
+In \cite{ludwig2007}, analytical standard error and percentile-T bootstrapped p-value were reported\footnote{However, we were unable to reproduce their point estimates for the ATE under the nonparametric setting using triangular kernel, which was documented in their paper.
+Instead, we used uniform kernel and obtained exactely the same results as theirs.}.
+The procedure proposed by CCT provides analytical standard error and confidence interval.
+Our bootstrap procedure provides standard error and confidence interval from the bootstrap distribution.
+In both CCT and bootstrap procedures, we set $p = 1$, $q = 2$ and used uniform kernel.
+In the bootstrap procedure, we used 500 bootstraps for bias correction and 999 for confidence interval.
+
+These results are shown in Table \ref{tab: head start spending}-\ref{tab: education 2000 ages 25-34}.
+We find that (1) the choice of bandwidth may significantly affect estimated ATE and its significance level; (2) the optimal bandwidths following CCT procedure are much smaller than actually being used in \cite{ludwig2007} and (3) our bootstrap procedure produces similar results to CCT.
+
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{cccccc}
+		\toprule
+		& \multicolumn{3}{c}{LM 2007} & CCT 2014 & Bootstrap \\
+		\midrule
+		& \multicolumn{5}{c}{Panel A: 1968 Head Start spending per child} \\ 
+		Bandwidth & 9 & 18 & 36 & 5.414, 10.175 & 5.414, 10.175 \\
+		Effect    & 137.251 & 114.711 & 134.491 & 143.811 & 148.990 \\
+		SE        & 128.968 & 91.267  & 62.593 & 113.404 & 182.729 \\
+		p-value   & 0.157   & 0.138   & 0.045  & & \\
+		95\% CI   & & & & (-78.457 366.078) & (-179.120  547.755) \\
+
+		&&&&& \\
+		& \multicolumn{5}{c}{Panel B: 1972 Head Start spending per child} \\ 
+		Bandwidth & 9 & 18 & 36 & 5.034, 12.020 & 5.034, 12.020 \\
+		Effect    & 182.119 & 88.959 & 130.153 & 94.260 & 100.404 \\
+		SE        & 148.321 & 101.697 & 67.613 & 122.224 & 196.008 \\
+		p-value   & 0.085   & 0.352   & 0.090  & & \\
+		95\% CI   & & & & (-145.294 333.814) & (-165.816 622.976) \\
+
+		&&&&& \\
+		& \multicolumn{5}{c}{Panel C: 1972 other social spending per capita} \\ 
+		Bandwidth & 9 & 18 & 36 & 4.612, 8.461 & 4.612, 8.461 \\
+		Effect    & 14.474 & 19.590 & 14.506 & 15.418 & 15.857 \\
+		SE        & 28.356 & 19.612 & 14.929 & 29.041 & 39.902 \\
+		p-value   & 0.459   & 0.222   & 0.478  & & \\
+		95\% CI   & & & & (-41.501 72.337) & (-64.153 91.999) \\
+		\bottomrule
+	\end{tabular}
+	\caption{The effect of Head Start assistance on Head Start spending. The first three columns come from Table 2 in \cite{ludwig2007}.}
+	\label{tab: head start spending}
+\end{table}
+
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{cccccc}
+		\toprule
+		& \multicolumn{3}{c}{LM 2007} & CCT 2014 & Bootstrap \\
+		\midrule
+		Bandwidth & 9 & 18 & 36 & 3.888, 6.807 & 3.888, 6.807 \\
+		Effect    & -1.895 & -1.198 & -1.114 & -3.795 & -3.852 \\
+		SE        & 0.980 & 0.796  & 0.544 & 1.654 & 1.526 \\
+		p-value   & 0.036   & 0.081   & 0.027  & & \\
+		95\% CI   & & & & (-7.037 -0.554) & (-6.565 -0.578) \\
+		\bottomrule
+	\end{tabular}
+	\caption{The effect of Head Start assistance on mortality. The first three columns come from Table 3 in \cite{ludwig2007}.}
+	\label{tab: mortality}
+\end{table}
+
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{cccc}
+		\toprule
+		& LM 2007 & CCT 2014 & Bootstrap \\
+		\midrule
+		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\
+		Bandwidth & 7 & 3.671, 8.618 & 3.671, 8.618 \\
+		Effect    & 0.030 & 0.055 & 0.054 \\
+		SE        & 0.016 & 0.021 & 0.021 \\
+		p-value   & 0.032 & & \\
+		95\% CI        & & (0.014 0.096) & (0.010 0.094) \\
+
+		&&& \\
+		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
+		Bandwidth & 7 & 5.076, 10.251 & 5.076, 10.251 \\
+		Effect    & 0.037 & 0.051 & 0.051 \\
+		SE        & 0.020 & 0.024 & 0.024 \\
+		p-value   & 0.031 & & \\
+		95\% CI        & & (0.004 0.099) & (0.001 0.092) \\
+		\bottomrule
+	\end{tabular}
+	\caption{The effect of Head Start assistance on education (1990, ages 18-24). The first column is result for directly treated cohorts (1990, ages 18-24) in Table 4 in \cite{ludwig2007}.}
+	\label{tab: education 1990 ages 18-24}
+\end{table}
+
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{cccc}
+		\toprule
+		& LM 2007 & CCT 2014 & Bootstrap \\
+		\midrule
+		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\ 
+		Bandwidth & 7 & 4.837, 9.85 & 4.837, 9.85 \\
+		Effect    & 0.000 & 0.014 & 0.013 \\
+		SE        & 0.016 & 0.019 & 0.019 \\
+		p-value   & 0.974 & & \\
+		CI        & & (-0.024 0.051) & (-0.026 0.051) \\
+
+		&&& \\
+		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
+		Bandwidth & 7 & 5.382, 10.621 & 5.382, 10.621 \\
+		Effect    & 0.028 & 0.033 & 0.032 \\
+		SE        & 0.019 & 0.023 & 0.022 \\
+		p-value   & 0.017 & & \\
+		CI        & & (-0.014 0.079) & (-0.009 0.077)\\
+		\bottomrule
+	\end{tabular}
+	\caption{The effect of Head Start assistance on education (2000, ages 18-24). The first column is result for directly treated cohorts (2000, ages 18-24) in Table 4 in \cite{ludwig2007}.}
+	\label{tab: education 2000 ages 18-24}
+\end{table}
+
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{cccc}
+		\toprule
+		& LM 2007 & CCT 2014 & Bootstrap \\
+		\midrule
+		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\ 
+		Bandwidth & 7 & 6.074, 11.477 & 6.074, 11.477 \\
+		Effect    & 0.006 & 0.014 & 0.014 \\
+		SE        & 0.014 & 0.015 & 0.015 \\
+		p-value   & 0.666 & & \\
+		CI        & & (-0.014 0.043) & (-0.023 0.036) \\
+
+		&&& \\
+		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
+		Bandwidth & 7 & 5.509, 11.463 & 5.509, 11.463 \\
+		Effect    & 0.040 & 0.049 & 0.049 \\
+		SE        & 0.017 & 0.020 & 0.021 \\ 
+		p-value   & 0.009 & & \\
+		CI        & & (0.010 0.089) & (0.003 0.083) \\
+		\bottomrule
+	\end{tabular}
+	\caption{The effect of Head Start assistance on education (2000, ages 25-34). The first column is result for directly treated cohorts (2000, ages 25-34) in Table 4 in \cite{ludwig2007}.}
+	\label{tab: education 2000 ages 25-34}
 \end{table}

### 2016-02-26 main_paper.tex
Update simulation tables

--- 2016-02-25 main_paper.tex
@@
 \caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
+\label{Tb: simulation 2}
 \end{table}

### 2016-02-26 main_paper.tex
Add application
Use data from LM2007 and re-estimate the main results.

--- 2016-02-26 main_paper.tex
@@
 
-\paragraph{Important message from the authors:} This version of the paper is
-very preliminary and incomplete. We have sent out a few early copies to get
-feedback, but there are still serious errors that we have not addressed. Please
-do not cite this paper or circulate it in its current form.
-
-\newpage
 \section{Introduction}

### 2016-02-26 main_paper.tex
Minor changes to text on Section 3 and beggining of Section 4.

--- 2016-02-26 main_paper.tex
@@
 \end{algorithm}
-Obviously, the distribution of $\Delta^*$ depends on $B_1$ and we could
-incorporate that dependency into our notation by wrting
-$\Delta^*_{B_1}$. However, we will follow standard practice in the bootstrap
-literature and assume that $B_1$ is large enough that it can be ignored and
-define $\Delta^* = \plim_{B_1 \to \infty} \Delta^*_{B_1}$
+The distribution of $\Delta^{*}$ depends on $B_{1}$ and we could
+incorporate that dependency into our notation by writing $\Delta^*_{B_1}$. However, we will follow standard practice in the bootstrap
+literature and assume that $B_{1}$ is large enough that it can be ignored and define $\Delta^* = \plim_{B_{1} \to \infty} \Delta^*_{B_{1}}$
 
 Under Assumptions~\ref{A1} and~\ref{A2} the procedure described by
-Algorithm~\ref{Alg1} provides a consistent estimator of the bias component and
-this estimator converges to zero fast enough in probability that it can be be
-used as a correction. As is standard in the bootstrap literature, we will assume
-that the number of bootstrap replications, $B_1$, is large enough that the
-simulation error can be ignored.
+Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
+converges fast enough in probability that it can be be used as a correction. As is standard in the bootstrap literature, we will assume
+that the number of bootstrap replications, $B_{1}$, is large enough that the simulation error can be ignored.
 
@@
   Under Assumptions~\ref{A1} and~\ref{A2},
-  $(\hat\tau(h_n,b_n) - \Delta^*(h_n,b_n) - \tau) / V^{1/2}(h_n, b_n) \to^d N(0,1)$.
+\begin{align}
+  \frac{(\hat\tau(h_{n},b_{n}) - \Delta^{*}(h_{n},b_{n}) - \tau)}{ V^{1/2}(h_n, b_n)} \to^{d} N(0,1)
+\end{align}
 \end{theorem}
@@
 With Algorithm~\ref{Alg1} at hand, we can move to generate the bias-corrected confidence intervals to perform inference about $\tau$.
-Here the idea is similar, but now we actually calculate a fully bias corrected estimate using Algorithm~\ref{Alg1} for every bootstrapped dataset generated, a bootstrap within the bootstrap.
+Here the idea is similar, but now we actually calculate a bias corrected estimate using Algorithm~\ref{Alg1} for every bootstrapped dataset generated, a bootstrap within the bootstrap.
 Each one of the bias corrected estimates for the generated data is denoted $\hat{\tau}^{bc*}$.
@@
 \begin{algorithm}[Confidence intervals]\label{Alg2}
-  Define $I^-$, $I^+$, $M^-$, and $M^+$ as in Algorithm~\ref{Alg1}.
+  Define $I^{-}$, $I^{+}$, $M^{-}$, and $M^{+}$ as in Algorithm~\ref{Alg1}.
   \begin{enumerate}
-  \item Estimate the local polynomials $g_{p+1}^+$ and $g_{p+1}^-$ as defined by
+  \item Estimate the local polynomials $g_{p+1}^{+}$ and $g_{p+1}^{-}$ as defined by
     Equation --- and define the residuals
@@
       \label{eq:3}
-      \hat\varepsilon_i =
+      \hat\varepsilon_{i} =
       \begin{cases}
-        Y_i - \hat g_{p+1}^-(X_i) & \textif\ X_i < 0 \\
-        Y_i - \hat g_{p+1}^+(X_i) & \otherwise
+        Y_i - \hat g_{p+1}^-(X_{i}) & \textif\ X_{i} < 0 \\
+        Y_i - \hat g_{p+1}^+(X_{i}) & \otherwise
       \end{cases}
     \end{equation}
-  \item Repeat the following steps $B_2$ times to produce a sequence of bootstrap
-    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_B^{\prime*}$. For the $k$th step:
+  \item Repeat the following steps $B_{2}$ times to produce a sequence of bootstrap
+    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_{2}}^{\prime*}$. For the $k$th step:
     \begin{enumerate}
-    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
-      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
-      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
+    \item Draw an i.i.d. sample of size $M^{-}(b_{n})$ from
+      $\{\hat\varepsilon_{i} : i \in I^{-}(b_{n})\}$ and one of size $M^{+}(b_{n})$ from
+      $\{\hat\varepsilon_i : i \in I^{+}(h_{n})\}$. Let $\varepsilon_{i}^{*-}$ and
       $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
@@
 
-We selected three data generating processes (DGP) that are widely used in the RD literature to evaluate the performance of the proposed bootstrap procedure, those are the same chosen by CCT and \cite{IK} and provide a good testing ground for bias correction due to their exacerbated curvature.
-To be specific, the pseudo data are generated as 500 i.i.d.
-draws from:
+We adopt the same three data generating processes (DGP) used by CCT to make it easy to compare our results.
+Also, these DGPs are widely used in the RD literature to evaluate the performance of inference procedures and provide a good testing ground for bias correction due to their exacerbated curvature.
+
+For all Monte Carlo experiments, the pseudo data are generated as 500 i.i.d. draws from:
 \begin{align*}
@@
 \end{align*}
-Three different choices of functional forms for $\mu_{j}(x)$ are as follows:
+Regarding the functional form for $\mu(x)$ in each DGP, the first one is based on a fifth order polynomial fitted on the data observed by \cite{lee2008rand} when estimating the incumbency advantage in electoral races to the U.S.
+House of Representatives.
+Hence, $\mu_{1}(x)$ is given by,
 \begin{align}
@@
 \end{cases}
-\\
+\end{align}
+
+The functional form for $\mu_{2}(x)$, in the second DGP follows the data observed by \cite{ludwig2007}, which we examine in more detail on Section \ref{application}, and follows
+\begin{align}
 \mu_{2}(x) & = 
@@
 \end{cases}
-\\
+\end{align}
+
+\begin{align}
 \mu_{3}(x) & =
@@
 
-The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed by \cite{lee2008} and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and therefore bias in the usual RD approach.
-For each DGP, we used four methods to obtain point estimate and 0.95 confidence interval.
-For each method, a total 1500 replications were performed.
-The first two methods follow CCT procedure with triangular and uniform kernel.
-The third and fourth methods follow the bootstrap procedure with uniform kernel.
-The only difference between the last two is that one is bias corrected and the other is not.
-In the bootstrap procedure, we used 500 bootstraps for bias correction, 999 bootstraps to calculate confidence interval.
-Table \ref{Tb: simulation 1} presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$).
-Table \ref{Tb: simulation 2} presents similar results for $p=2$ and $q=3$.
+The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed by  and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and therefore bias in the usual RD approach.
+For the simulation studies, we used 250 bootstraps for bias correction, 999 bootstraps to calculate confidence interval and a total 500 replications.
+All results presented are based on a 0.95 desired confidence level.
+Table1 presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$).
+Table 2 presents similar results for $p=2$ and $q=3$.
 
-\begin{table}[t]
+\begin{table}[t] \label{Tb1}
 \centering
@@
   \midrule
-	1 & $CCT_{tri}$ & -0.010 & 0.068 & 0.068 & 0.911 & 0.241 \\ 
-	  & $CCT_{uni}$ & -0.016 & 0.067 & 0.069 & 0.924 & 0.246 \\ 
-	  & $bootstrap_{uni}$       & -0.018 & 0.066 & 0.069 & 0.931 & 0.240 \\ 
-	  & $bootstrap_{uni}^{nbc}$ & -0.020 & 0.060 & 0.064 & 0.916 & 0.208 \\
-	\midrule
-	2 & $CCT_{tri}$ & -0.011 & 0.085 & 0.086 & 0.935 & 0.343 \\ 
-	  & $CCT_{uni}$ & -0.010 & 0.087 & 0.088 & 0.938 & 0.350 \\ 
-	  & $bootstrap_{uni}$       & -0.012 & 0.088 & 0.089 & 0.953 & 0.324 \\ 
-	  & $bootstrap_{uni}^{nbc}$ & -0.051 & 0.086 & 0.100 & 0.869 & 0.300 \\ 
-	\midrule
-	3 & $CCT_{tri}$ & -0.008 & 0.067 & 0.067 & 0.919 & 0.246 \\ 
-	  & $CCT_{uni}$ & -0.004 & 0.065 & 0.065 & 0.943 & 0.250 \\ 
-	  & $bootstrap_{uni}$       & -0.004 & 0.064 & 0.064 & 0.960 & 0.246 \\ 
-	  & $bootstrap_{uni}^{nbc}$ & 0.016 & 0.062 & 0.064 & 0.931 & 0.218 \\ 
+  1   & bootstrap & --0.013 & 0.067 & 0.068 & 0.938       & 0.243     \\
+      & CCT       & --0.016 & 0.068 & 0.070 & 0.908       & 0.244     \\
+  2   & bootstrap & --0.014 & 0.083 & 0.084 & 0.954       & 0.319     \\
+      & CCT       & --0.014 & 0.092 & 0.093 & 0.928       & 0.350     \\
+  3   & bootstrap & --0.006 & 0.069 & 0.070 & 0.956       & 0.247     \\
+      & CCT       & --0.004 & 0.071 & 0.071 & 0.918       & 0.249     \\
   \bottomrule
@@
 \caption{Summary of estimates ($p = 1, q = 2$)}
-\label{Tb: simulation 1}
 \end{table}
 
-As can be seen on the tables, the bootstrap bias-correction procedure proposed in this paper provides a simple alternative to obtain 
-valid robust confidence intervals in RD designs and performs well compared to the analytical 
-bias correction procedures proposed by CCT. The results also demonstrate the importance of bias correction when huge kink 
-presents at the cutoff (such as in the second DGP). Failing to correct bias in this case leads to a confidence interval with incorrect coverage.
+As can be seen on the tables above, the bootstrap bias-correction procedure
+proposed in this paper provides a simple alternative to obtain valid robust
+confidence intervals in RD designs and performs well compared to the analytical 
+bias correction procedures proposed by CCT.
 
-\begin{table}[t]
+\begin{table}[t]\label{Tb2}
 \centering
@@
   \midrule
-    1 & $CCT_{tri}$ & -0.006 & 0.079 & 0.079 & 0.923 & 0.291 \\ 
-      & $CCT_{uni}$ & -0.003 & 0.081 & 0.081 & 0.932 & 0.299 \\ 
-      & $bootstrap_{uni}$       & -0.003 & 0.079 & 0.079 & 0.947 & 0.294 \\ 
-      & $bootstrap_{uni}^{nbc}$ & -0.008 & 0.073 & 0.074 & 0.941 & 0.261 \\ 
-     \midrule
-    2 & $CCT_{tri}$ & -0.007 & 0.080 & 0.080 & 0.941 & 0.319 \\ 
-      & $CCT_{uni}$ & -0.005 & 0.081 & 0.081 & 0.946 & 0.326 \\ 
-      & $bootstrap_{uni}$       & -0.008 & 0.080 & 0.080 & 0.955 & 0.300 \\ 
-      & $bootstrap_{uni}^{nbc}$ & -0.020 & 0.075 & 0.078 & 0.924 & 0.273 \\ 
-     \midrule
-    3 & $CCT_{tri}$ & 0.004 & 0.080 & 0.080 & 0.922 & 0.291 \\ 
-      & $CCT_{uni}$ & -0.004 & 0.082 & 0.082 & 0.931 & 0.296 \\ 
-      & $bootstrap_{uni}$       & 0.002 & 0.077 & 0.077 & 0.958 & 0.294 \\ 
-      & $bootstrap_{uni}^{nbc}$ & -0.001 & 0.073 & 0.073 & 0.948 & 0.260 \\ 
+  1   & bootstrap & --0.002 & 0.075 & 0.075 & 0.958       & 0.295     \\
+      & CCT       & --0.004 & 0.082 & 0.082 & 0.926       & 0.295     \\
+  2   & bootstrap & 0.002   & 0.087 & 0.086 & 0.934       & 0.302     \\
+      & CCT       & --0.005 & 0.078 & 0.078 & 0.960       & 0.323     \\
+  3   & bootstrap & --0.008 & 0.083 & 0.083 & 0.942       & 0.292     \\
+      & CCT       & --0.003 & 0.080 & 0.080 & 0.938       & 0.295     \\
   \bottomrule
@@
 \caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
-\label{Tb: simulation 2}
 \end{table}

### 2016-02-27 main_paper.tex
Rewrite Theorem 1 proof slightly
Hopefully this rewrite makes the proof a little easier to read. No real
changes have been made to the arguments, though.

--- 2016-02-26 main_paper.tex
@@
 \begin{equation*}
-  \hat\tau - \Delta^* - \tau = (\hat\tau - \E \hat \tau) +
-  (\E \hat \tau - \tau) - (\E^* \hat \tau^* - \tau^*)
+  \hat\tau_h - \Delta^*_h - \tau = (\hat\tau_h - \E \hat \tau_h) +
+  (\E \hat \tau_h - \tau) - (\E^* \hat \tau^*_h - \tau^*)
 \end{equation*}
 The design of the bootstrap ensures that
-\begin{equation*}
+\begin{align*}
   \label{eq:6}
-  \E^* \hat\mu_{\pm}^*(h_n) - \mu_{\pm}^{*} =
-  h_n^{2} \mu_\pm^{*(2)} \Bf_{\pm}(h_n)/2,
-\end{equation*}
+  \E^* \hat\mu_{+}^*(h_n) - \mu_{+}^{*}
+  &= h_n^{2} \mu_+^{*(2)} \Bf_{+}(h_n)/2,
+  &\E^* \hat\mu_{-}^*(h_n) - \mu_{-}^{*}
+  &= h_n^{2} \mu_-^{*(2)} \Bf_{-}(h_n)/2,
+\end{align*}
 almost surely, implying that
@@
   \label{eq:7}
-    \E^* \hat\tau^{*} - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
+    \E^* \hat\tau^{*}_h - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
       - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
@@
 Combining this result with CCT's Lemma A1, gives
-\begin{align*}
-  \hat\tau &- \E \hat\tau + (\E \hat\tau - \tau) - (\E^* \hat\tau^* - \tau^*)\\
-  &= \hat\tau - \E\hat\tau
+\begin{align}
+  \hat\tau_h - & \E \hat\tau_h + (\E \hat\tau_h - \tau) - (\E^* \hat\tau^*_h - \tau^*)\notag \\
+  \label{eq:8}
+  &= \hat\tau_h - \E\hat\tau_h
    + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
    - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
-  &= \hat\tau - \E\hat\tau
-   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2
-   - h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})
-\end{align*}
+  &= \hat\tau_h - \E\hat\tau_h
+   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2 \notag \\
+  \label{eq:9}
+  &\pushright{- h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})}
+\end{align}
 The second equality holds because
-$\mu_\pm^{*(2)} = \hat\mu_{\pm}^{(2)}(b_n)$ a.s. Asymptotic normality then
-follows from normality of $\hat\tau - \E\hat\tau$ and
-$\hat\mu_\pm^{(2)}(b_n) - \mu_\pm^{(2)}$ using
-similar arguments to CCT's Lemma SA4.D.\qed
+$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b_n)$ and
+$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b_n)$ almost surely. Asymptotic
+normality then follows from normality of $\hat\tau_h - \E\hat\tau_h$,
+$\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}$, and
+$\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}$ using similar arguments to
+CCT's Lemma SA4.D.\qed
 

### 2016-02-27 main_paper.tex
Update and fix proof of Theorem 2
This commit gives the first plausible proof of Theorem 2, but there may
still be subtle errors.

@@
 \begin{assumption}[Behavior of the DGP near the cutoff]\label{A1}
-  The random variables $Y_{i}, X_{i}$ are i.i.d.\ and
-  there exists a positive number $\kappa_0$ such that the following
-  conditions hold for all $x$ in the neighborhood
-  $(-\kappa_{0},\kappa_{0})$ around zero:
+  The random variables $Y_i, X_i$ are independent but not necessarily
+  identically distributed. There exists a positive number $\kappa_0$
+  such that the following conditions hold for all $x$ in the
+  neighborhood $(-\kappa_{0},\kappa_{0})$ around zero:
   \begin{enumerate}
@@
 
-\newpage\appendix
-\section{Mathematical Appendix}
+\section{Proofs of mathematical results}
 \subsection{Proof of Theorem~\ref{T1}}
@@
   \hat\tau_h - & \E \hat\tau_h + (\E \hat\tau_h - \tau) - (\E^* \hat\tau^*_h - \tau^*)\notag \\
-  \label{eq:8}
   &= \hat\tau_h - \E\hat\tau_h
@@
    + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2 \notag \\
-  \label{eq:9}
+  \label{eq:8}
   &\pushright{- h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})}
@@
 \subsection{Proof of Theorem~\ref{T2}}
-We can repeat the steps from Theorem~\ref{T1}'s proof to show that
+Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:8} to get
 \begin{align*}
-  \hat\tau^* - \Delta^{**} - \tau^* &= (\hat\tau^* - \E^* \hat \tau^*) +
-  (\E^* \hat \tau^* - \tau^*) - (\E^{**} \hat \tau^{**} - \tau^{**}) \\
-  &= \hat\tau^* - \E^*\hat\tau^*
+  \hat\tau_h^* - &\Delta_h^{**} - \tau^*
+  = (\hat\tau^*_h - \E^* \hat \tau^*_h) +
+  (\E^* \hat \tau^*_h - \tau^*) - (\E^{**} \hat \tau^{**}_h - \tau^{**}) \\
+  &= \hat\tau^*_h - \E^*\hat\tau^*_h
    + h_n^2 (\hat\mu_-^{*(2)}(b_n) - \mu_-^{*(2)}) \Bf_{-}(h_{n}) /2
-   - h_n^2 (\hat\mu_+^{*(2)}(b_n) - \mu_+^{*(2)}) \Bf_{+}(h_{n}) / 2.
+   - h_n^2 (\hat\mu_+^{*(2)}(b_n) - \mu_+^{*(2)}) \Bf_{+}(h_{n}) / 2 \\
+  &= \Omega^{+}(b_n)' \epb_{+}^{*} - \Omega^{-}(b_n)' \epb_{-}^{*},
 \end{align*}
-Consequently, the asymptotic behavior of
-$\hat\tau^* - \Delta^** - \tau^*$ is determined by the behavior of
-$\hat\tau^* - \E^*\hat\tau*$ and
-$\hat\mu_{\pm}^{*(2)} - \mu_\pm^{*(2)}$ and these random variables are
-weighted averages of the sums
-\begin{equation*}
-  \sum_{i \in I^{\pm}(b_n)} Z_i \varepsilon_i^*
-\end{equation*}
-with $Z_i = (1, X_i, X_i^2)'$. By construction,
-\begin{equation*}
-  \V^*\Big(\ssum{i}{b_n} Z_i \varepsilon_i^* \Big)
-  = \hat\sigma_\pm^2(b_n) \Gamma_\pm(b_n)
-\end{equation*}
-almost surely, making~\eqref{eq:4} a consequence of CCT's SA?.
+where
+$\epb_{+}^{*} =
+(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_b^{+}}^{*})'$ and
+$\Omega^{+}_b$ is an $M_b^{+}$-dimensional vector with $i$th element
+$\Omega_{1i}^{+}(b_n) - \Omega_{2i}^{+}(b_n)$, which are defined as
+\begin{align*}
+  \Omega_{1i}^{+}(b) &=
+  (1\quad 0)
+  \Big(\ssum{j}{h_n} r_1(X_j / h_n) r_1(X_j / h_n)' \Big)^{-1}
+    r_1(X_{m^+_i} / h_n) \1\{h_n > X_{m_i} \geq 0\}
+\intertext{and}
+  \Omega_{2i}^{+}(b) &=   (0\quad 0 \quad h_n^2) 
+  \Big(\ssum{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
+    r_2(X_{m^+_i} / b).
+\end{align*}
+Here $r_p(x) = (1, x, x^2,\dots,x^{p})'$ and $m^+_i$ is the subsequence of
+$1,2,\dots$ such that $0 \leq X_{m_i} < b$. The definitions of
+$\epb_{-}^{*}$ and $\Omega^-(b_n)$ have the same definitons as
+$\epb_{+}^{*}$ and $\Omega^+(b_n)$ after making the obvious
+substitiutions of ``$-$'' for ``$+$.''
 
-For~\eqref{eq:5}, since $\hat\tau - \Delta^*$ is itself asymptotically
-normal, it suffices to prove the pointwise result
-\begin{equation}
-  \label{eq:8}
-  \Big\rvert \Pr^*[(\hat\tau^{*} - \Delta^{**} - \tau^*)
-  / V^{1/2}(h_n,b_n) \leq x ] - \Phi(x)] \Big\lvert \to^p 0.
-\end{equation}
-for all $x$. Since the limiting distribution is continuous, an
-argument attributed to Poly\'a immediately extends the pointwise
-convergence result to the uniform result stated in~\eqref{eq:5}. (See
-van der vaart, p. for the details of the argument.) But~\eqref{eq:8}
-follows from Lemma~\ref{L1} as well, completing the proof.\qed
-
-\subsection{Supporting results}
-
-\begin{lemma}\label{L1}
-  Define $Z_i = (1, X_i, X_i^2)$.  Under Assumptions~\ref{A1} and~\ref{A2},
-  \begin{equation}
+Given~\eqref{eq:8}, it suffices to prove that
+\begin{gather}
   \label{eq:9}
-    \Big\rvert \Pr^*\Big[ \Gamma_\pm(b_n)^{-1/2}
-    \sum_{i \in I^{\pm}(b_n)} Z_i \varepsilon_i^* / \hat\sigma_\pm(b_n) < x \Big]
-    - \Phi(x) \Big\lvert \to^p 0.
-  \end{equation}
-\end{lemma}
-
-\begin{proof}
-  Let $z_i = \alpha' Z_i$ for an arbitrary nonzero $\alpha$ and define
-  $\gamma_\pm(b_n) = \alpha'\Gamma_\pm(b_n)\alpha$. We will
-  establsh asymptotic normality for the scalar $z_i \varepsilon_i^*$;
-  the multivariate case follows via the Cram\'er-Wold device. (cite
-  van der vaart.)
-
-  Define the filtration
-  \begin{equation}
+  \rho(V^{-1/2}(h_n) \Omega^{+}(b_n)'\epb_{+}^{*},
+    V^{-1/2}(h_n)\Omega^{+}(b_n)'\epb_{+}) \to^p 0
+  \intertext{and}
   \label{eq:10}
-    \Fc_j^{*\pm} = \sigma(Y_1,\dots,Y_n; X_1,\dots,X_n;
-    \varepsilon_{i_1}^{*\pm},\dots,\varepsilon_{i_j}^{*\pm})
-  \end{equation}
-  where the values $i_1, i_2,\dots, i_{M_h^{\pm}}$ form an ordering of
-  all of the elements of $I_n^\pm$. (The specific order is
-  unimportant.) Then
-  $\{z_{i_j} \varepsilon_{i_j}^{*\pm}, \Fc_j^{*\pm}\}$ is a martingale
-  difference sequence and~\eqref{eq:9} holds if
+  \rho(V^{-1/2}(h_n)\Omega^{-}(b_n)'\epb_{-}^{*},
+    V^{-1/2}(h_n)\Omega^{-}(b_n)'\epb_{-}) \to^p 0
+\end{gather}
+with $\epb_+$ an i.i.d. random vector of length $M_b^+$, the $i$th
+element of which is distributed as
+\[
+  \varepsilon_{i,+} =^d
+  \begin{cases}
+    Y_{m_1^+} - \E(Y_{m_1^+} \mid X_{m_1^+})
+    & \text{with probability\ } 1/M_{b}^+ \\
+    \vdots \\
+    Y_{m_{M_b^+}^+} - \E(Y_{m_{M_b^+}^+} \mid X_{m_{M_b^+}^+})
+    & \text{with probability\ } 1/M_{b}^+,
+  \end{cases}
+\]
+$\epb_-$ the corresponding quantity after replacing ``+'' with ``--,'' and
+$\rho$ the Mallows metric \citep{bickel1981}.\footnote{%
+  For two random vectors $u$ and $v$ with finite 2nd moments, $\rho(u, v)$
+  is defined as
   \begin{equation}
     \label{eq:11}
-    \savg{i}{h} z_{i}^2 \varepsilon_{i}^{*\pm\,2} -
-    \gamma_{\pm}^*(b_n) \hat\sigma
-    \to^p 0
-  \end{equation}
-  and, for all
-  $\delta > 0$,
+    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
+    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
+  \end{equation}}
+
+We will only prove~\eqref{eq:9} since the proof of~\eqref{eq:10} is
+identical. By Theorem 2.1 of \cite{freedman1981}, we have
+\begin{align*}
+  \rho(V^{-1/2}(h_n) \Omega^{+}(b_n)'\epb_{+}^{*}, V^{-1/2}(h_n)&\Omega^{+}(b_n)'\epb_{+}) \\
+  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
+    \tr(V^{-1/2}(h_n) \Omega^{+}(b_n)' \Omega^{+}(b_n)V^{-1/2}(h_n)) \\
+  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
+\end{align*}
+the second line holding as a consequence of CCT's Lemma SA1. So it suffices
+to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
+$\dot{\varepsilon}_i$ be an i.i.d. sequence randomly drawn from $\epb_+$
+with replacement and let
+$\bar{\varepsilon} = (1/M_b^{+}) \osum{i}{b_n} \dot{\varepsilon}_i$. Then,
+using the same arguments as \cite{freedman1981}, we have the upper bound
 \begin{equation}
   \label{eq:12}
-    \oavg{j}{h} z_{i_j}^2 \E^*( \varepsilon_{i_j}^{*\pm\,2}
-    \1\{z_{i_j}^2 \varepsilon_{i_j}^{*\pm\,2} / M_h^\pm > \delta \}
-    \mid \Fc_{j-1}^{\pm}) \to^p 0.
+  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
+  \leq
+  \bar\varepsilon^2 +
+  (2/M_{b_n}^+) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
+  + \rho(\dot\varepsilon_1, \varepsilon_{+,1}).
 \end{equation}
-  (cite Hall and Heyde.)
-
-  For~\eqref{eq:11}, observe that
-  $\{z_{i_j}^2 (\varepsilon_{i_j}^{*2} - \hat\sigma^2_\pm(b_n)), \Fc_j^\pm\}$
-  is also a martingale difference sequence so convergence follows from
-  the LLN.
-
-  For~\eqref{eq:12}, we have
-  \begin{align*}
-    \oavg{j}{h} z_{i_j}^2 \E^*( \varepsilon_{i_j}^{*\pm\,2}
-    \1\{z_{i_j}^2 \varepsilon_{i_j}^{*\pm\,2} / M_h^\pm > \delta \}
-    \mid \Fc_{j-1}^{\pm})
-    &= \oavg{i}{h_n} z_i^2 \oavg{j}{b_n} \hat\varepsilon_{j}^{\pm 2}
-      \1\{\hat\varepsilon_{j}^{\pm 2} > \delta M_n^{\pm} / z_i^2 \} \\
-  \end{align*}
-  (Finish with: $\varepsilon_i^2$ is uniformly integrable,
-  $\hat\varepsilon_i^2$ gets arbitrarily close to $\varepsilon_i^2$)
-\end{proof}
+But $\bar\varepsilon^2 \to^p 0$ by the LLN,
+\[
+  (1/M_{b_n}^+) \osum[+]{i}{b}
+  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
+\]
+by CCT's Lemma SA1, and
+$\rho(\dot\varepsilon_1, \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
+\cite{bickel1981}.\qed
 

### 2016-02-27 main_paper.tex
Some work on the Simulations Section.

--- 2016-02-26 main_paper.tex
@@
 
+Finally, the third DGP used in the simulations is given by a modified version of  \cite{lee2008rand} designed to exhibit more curvature and, hence, be more sensitive to the choice of bandwidth in terms of bias.
+This functional form is the same as used in CCT and serves as an useful example of the effectiveness of the bias correction procedures implemented.
 \begin{align}
@@
 
-The functional form for $\mu_{1}(x)$ and $\mu_{2}(x)$ follow the data observed by  and \cite{ludwig2007}, respectively, while $\mu_{3}(x)$ is a transformation of $\mu_{1}(x)$ designed to emphasize its curvature and therefore bias in the usual RD approach.
-For the simulation studies, we used 250 bootstraps for bias correction, 999 bootstraps to calculate confidence interval and a total 500 replications.
-All results presented are based on a 0.95 desired confidence level.
-Table1 presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$).
-Table 2 presents similar results for $p=2$ and $q=3$.
+For each DGP, we used four methods to obtain point estimate and confidence intervals.\footnote{Note that the true value of $\tau$ is $0.04$ for DGPs 1 and 3 and $-3.45$ for DGP 2} For each method, a total 1500 replications were performed.
+The first two methods follow CCT analytical bias-correction procedure with triangular ($CCT_{tri}$) and uniform ($CCT_{uni}$) kernel, respectively.
+The third and fourth methods follow the bootstrap procedure proposed in Section \ref{boot} with uniform kernel with ($bootstrap_{uni}$) and without ($bootstrap_{uni}^{naive}$) bias-correction, respectively.
 
-\begin{table}[t] \label{Tb1}
+The ``naive'' bootstrap estimator, which bootstraps the confidence intervals for the usual RD estimator without any bias-correction serves as a baseline comparison, making clear the need of the corrections proposed, especially for DGPs with higher (potential) bias.
+
+In the bootstrap procedure, we used 500 bootstraps for bias correction, 999 bootstraps to calculate confidence interval.
+Table \ref{Tb: simulation 1} presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$).
+Table \ref{Tb: simulation 2} presents similar results for $p=2$ and $q=3$.
+
+\begin{table}[t]
 \centering
@@
   \toprule
-  DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
+	DGP & Method    & Bias    & SD    & MSE   & CI Coverage & CI Length \\
   \midrule
-  1   & bootstrap & --0.013 & 0.067 & 0.068 & 0.938       & 0.243     \\
-      & CCT       & --0.016 & 0.068 & 0.070 & 0.908       & 0.244     \\
-  2   & bootstrap & --0.014 & 0.083 & 0.084 & 0.954       & 0.319     \\
-      & CCT       & --0.014 & 0.092 & 0.093 & 0.928       & 0.350     \\
-  3   & bootstrap & --0.006 & 0.069 & 0.070 & 0.956       & 0.247     \\
-      & CCT       & --0.004 & 0.071 & 0.071 & 0.918       & 0.249     \\
+	1 & $CCT_{tri}$ & -0.010 & 0.068 & 0.068 & 0.911 & 0.241 \\ 
+	  & $CCT_{uni}$ & -0.016 & 0.067 & 0.069 & 0.924 & 0.246 \\ 
+	  & $bootstrap_{uni}$ & -0.018 & 0.066 & 0.069 & 0.931 & 0.240 \\ 
+	  & $bootstrap_{uni}^{naive}$ & -0.020 & 0.060 & 0.064 & 0.916 & 0.208 \\
+	\midrule
+	2 & $CCT_{tri}$ & -0.011 & 0.085 & 0.086 & 0.935 & 0.343 \\ 
+	  & $CCT_{uni}$ & -0.010 & 0.087 & 0.088 & 0.938 & 0.350 \\ 
+	  & $bootstrap_{uni}$       & -0.012 & 0.088 & 0.089 & 0.953 & 0.324 \\ 
+	  & $bootstrap_{uni}^{naive}$ & -0.051 & 0.086 & 0.100 & 0.869 & 0.300 \\ 
+	\midrule
+	3 & $CCT_{tri}$ & -0.008 & 0.067 & 0.067 & 0.919 & 0.246 \\ 
+	  & $CCT_{uni}$ & -0.004 & 0.065 & 0.065 & 0.943 & 0.250 \\ 
+	  & $bootstrap_{uni}$       & -0.004 & 0.064 & 0.064 & 0.960 & 0.246 \\ 
+	  & $bootstrap_{uni}^{naive}$ & 0.016 & 0.062 & 0.064 & 0.931 & 0.218 \\ 
   \bottomrule
@@
 \caption{Summary of estimates ($p = 1, q = 2$)}
+\label{Tb: simulation 1}
 \end{table}
 
-As can be seen on the tables above, the bootstrap bias-correction procedure
-proposed in this paper provides a simple alternative to obtain valid robust
-confidence intervals in RD designs and performs well compared to the analytical 
-bias correction procedures proposed by CCT.
+Table \ref{Tb: simulation 1} presents the results for the local linear model, with three panels reporting on each DGP described above.
+For each panel, we report bias, standard deviation, MSE, confidence interval empirical coverage and lenght for the four methods.
+For the three DGPs coverage for
+    both analytical and bootstrap based bias correction methods is near nominal size but with slight undercoverage for CCT's analytical correction.
+For DGP 1, our robust bootstrap method improves coverage slightly, obtaining 93.1\% coverage against 92.4\% from CCT's analytical correction using the uniform kernel.
+Also, the CI length is slightly shortened on average.
+Both robust approaches improve over the naive estimator, even in this case for which bias is relatively small.
 
-\begin{table}[t]\label{Tb2}
+For the second DGP, based on \cite{ludwig2007}, the importance of correcting for the leading bias term presence becomes clear, with the naive bootstrap CI displaying an empirical coverage of only 86.9\%.
+Once again, the CIs based on both analytical and bootstrap robust methods improves the coverage meaningfully, with moderate gains in terms of coverage and lenght from $0.324$ to $0.350$ when using the bootstrap estimator relative to CCT's with uniform kernel.
+
+In the case of the modified \cite{lee2008rand} DGP that exacerbates the importance of bias, $\mu_{3}(x)$, once more the robust bootstrap procedure provides similar empirical coverage and interval length relative to its analytical alternatives.
+The naive method once again suffers in terms of coverage due to the presence of uncorrected first order bias.
+
+ Overall, the bootstrap bias-correction procedure proposed in this paper provides a simple alternative to obtain valid robust confidence intervals in RD designs and performs well compared to the analytical
+bias correction procedures proposed by CCT. The results also corroborates CCT in the importance of bias correction when high curvature is present at the cutoff.
+
+\begin{table}[t]
 \centering
@@
   \toprule
-  DGP & Method    & Bias    & SD    & MSE   & CI coverage & CI length \\
+  DGP & Method    & Bias    & SD    & MSE   & CI Coverage & CI Length \\
   \midrule
-  1   & bootstrap & --0.002 & 0.075 & 0.075 & 0.958       & 0.295     \\
-      & CCT       & --0.004 & 0.082 & 0.082 & 0.926       & 0.295     \\
-  2   & bootstrap & 0.002   & 0.087 & 0.086 & 0.934       & 0.302     \\
-      & CCT       & --0.005 & 0.078 & 0.078 & 0.960       & 0.323     \\
-  3   & bootstrap & --0.008 & 0.083 & 0.083 & 0.942       & 0.292     \\
-      & CCT       & --0.003 & 0.080 & 0.080 & 0.938       & 0.295     \\
+    1 & $CCT_{tri}$ & -0.006 & 0.079 & 0.079 & 0.923 & 0.291 \\ 
+      & $CCT_{uni}$ & -0.003 & 0.081 & 0.081 & 0.932 & 0.299 \\ 
+      & $bootstrap_{uni}$       & -0.003 & 0.079 & 0.079 & 0.947 & 0.294 \\ 
+      & $bootstrap_{uni}^{naive}$ & -0.008 & 0.073 & 0.074 & 0.941 & 0.261 \\ 
+     \midrule
+    2 & $CCT_{tri}$ & -0.007 & 0.080 & 0.080 & 0.941 & 0.319 \\ 
+      & $CCT_{uni}$ & -0.005 & 0.081 & 0.081 & 0.946 & 0.326 \\ 
+      & $bootstrap_{uni}$       & -0.008 & 0.080 & 0.080 & 0.955 & 0.300 \\ 
+      & $bootstrap_{uni}^{naive}$ & -0.020 & 0.075 & 0.078 & 0.924 & 0.273 \\ 
+     \midrule
+    3 & $CCT_{tri}$ & 0.004 & 0.080 & 0.080 & 0.922 & 0.291 \\ 
+      & $CCT_{uni}$ & -0.004 & 0.082 & 0.082 & 0.931 & 0.296 \\ 
+      & $bootstrap_{uni}$       & 0.002 & 0.077 & 0.077 & 0.958 & 0.294 \\ 
+      & $bootstrap_{uni}^{naive}$ & -0.001 & 0.073 & 0.073 & 0.948 & 0.260 \\ 
   \bottomrule

### 2016-02-28 main_paper.tex
Remove Table 2 (p=2,q=3) from the simulations section.

@@
 Table \ref{Tb: simulation 1} presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$).
-Table \ref{Tb: simulation 2} presents similar results for $p=2$ and $q=3$.
 
@@
 bias correction procedures proposed by CCT. The results also corroborates CCT in the importance of bias correction when high curvature is present at the cutoff.
-
-\begin{table}[t]
-\centering
-\begin{tabular}{rrrrrrr}
-  \toprule
-  DGP & Method    & Bias    & SD    & MSE   & CI Coverage & CI Length \\
-  \midrule
-    1 & $CCT_{tri}$ & -0.006 & 0.079 & 0.079 & 0.923 & 0.291 \\ 
-      & $CCT_{uni}$ & -0.003 & 0.081 & 0.081 & 0.932 & 0.299 \\ 
-      & $bootstrap_{uni}$       & -0.003 & 0.079 & 0.079 & 0.947 & 0.294 \\ 
-      & $bootstrap_{uni}^{naive}$ & -0.008 & 0.073 & 0.074 & 0.941 & 0.261 \\ 
-     \midrule
-    2 & $CCT_{tri}$ & -0.007 & 0.080 & 0.080 & 0.941 & 0.319 \\ 
-      & $CCT_{uni}$ & -0.005 & 0.081 & 0.081 & 0.946 & 0.326 \\ 
-      & $bootstrap_{uni}$       & -0.008 & 0.080 & 0.080 & 0.955 & 0.300 \\ 
-      & $bootstrap_{uni}^{naive}$ & -0.020 & 0.075 & 0.078 & 0.924 & 0.273 \\ 
-     \midrule
-    3 & $CCT_{tri}$ & 0.004 & 0.080 & 0.080 & 0.922 & 0.291 \\ 
-      & $CCT_{uni}$ & -0.004 & 0.082 & 0.082 & 0.931 & 0.296 \\ 
-      & $bootstrap_{uni}$       & 0.002 & 0.077 & 0.077 & 0.958 & 0.294 \\ 
-      & $bootstrap_{uni}^{naive}$ & -0.001 & 0.073 & 0.073 & 0.948 & 0.260 \\ 
-  \bottomrule
-\end{tabular}
-\caption{Summary of estimates from bootstrap ($p = 2, q = 3$)}
-\label{Tb: simulation 2}
-\end{table}
 
@@
 Combining this result with CCT's Lemma A1, gives
-\begin{align*}
-  \hat\tau &- \E \hat\tau + (\E \hat\tau - \tau) - (\E^* \hat\tau^* - \tau^*)\\
-  &= \hat\tau - \E\hat\tau
+\begin{align}
+  \hat\tau_h - & \E \hat\tau_h + (\E \hat\tau_h - \tau) - (\E^* \hat\tau^*_h - \tau^*)\notag \\
+  &= \hat\tau_h - \E\hat\tau_h
    + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
    - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
-  &= \hat\tau - \E\hat\tau
-   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2
-   - h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})
-\end{align*}
+  &= \hat\tau_h - \E\hat\tau_h
+   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2 \notag \\
+  \label{eq:8}
+  &\pushright{- h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})}
+\end{align}
 The second equality holds because
-$\mu_\pm^{*(2)} = \hat\mu_{\pm}^{(2)}(b_n)$ a.s. Asymptotic normality then
-follows from normality of $\hat\tau - \E\hat\tau$ and
-$\hat\mu_\pm^{(2)}(b_n) - \mu_\pm^{(2)}$ using
-similar arguments to CCT's Lemma SA4.D.\qed
+$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b_n)$ and
+$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b_n)$ almost surely. Asymptotic
+normality then follows from normality of $\hat\tau_h - \E\hat\tau_h$,
+$\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}$, and
+$\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}$ using similar arguments to
+CCT's Lemma SA4.D.\qed
 
 \subsection{Proof of Theorem~\ref{T2}}
-We can repeat the steps from Theorem~\ref{T1}'s proof to show that
+Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:8} to get
 \begin{align*}
-  \hat\tau^* - \Delta^{**} - \tau^* &= (\hat\tau^* - \E^* \hat \tau^*) +
-  (\E^* \hat \tau^* - \tau^*) - (\E^{**} \hat \tau^{**} - \tau^{**}) \\
-  &= \hat\tau^* - \E^*\hat\tau^*
+  \hat\tau_h^* - &\Delta_h^{**} - \tau^*
+  = (\hat\tau^*_h - \E^* \hat \tau^*_h) +
+  (\E^* \hat \tau^*_h - \tau^*) - (\E^{**} \hat \tau^{**}_h - \tau^{**}) \\
+  &= \hat\tau^*_h - \E^*\hat\tau^*_h
    + h_n^2 (\hat\mu_-^{*(2)}(b_n) - \mu_-^{*(2)}) \Bf_{-}(h_{n}) /2
-   - h_n^2 (\hat\mu_+^{*(2)}(b_n) - \mu_+^{*(2)}) \Bf_{+}(h_{n}) / 2.
+   - h_n^2 (\hat\mu_+^{*(2)}(b_n) - \mu_+^{*(2)}) \Bf_{+}(h_{n}) / 2 \\
+  &= \Omega^{+}(b_n)' \epb_{+}^{*} - \Omega^{-}(b_n)' \epb_{-}^{*},
 \end{align*}
-Consequently, the asymptotic behavior of
-$\hat\tau^* - \Delta^** - \tau^*$ is determined by the behavior of
-$\hat\tau^* - \E^*\hat\tau*$ and
-$\hat\mu_{\pm}^{*(2)} - \mu_\pm^{*(2)}$ and these random variables are
-weighted averages of the sums
-\begin{equation*}
-  \sum_{i \in I^{\pm}(b_n)} Z_i \varepsilon_i^*
-\end{equation*}
-with $Z_i = (1, X_i, X_i^2)'$. By construction,
-\begin{equation*}
-  \V^*\Big(\ssum{i}{b_n} Z_i \varepsilon_i^* \Big)
-  = \hat\sigma_\pm^2(b_n) \Gamma_\pm(b_n)
-\end{equation*}
-almost surely, making~\eqref{eq:4} a consequence of CCT's SA?.
+where
+$\epb_{+}^{*} =
+(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_b^{+}}^{*})'$ and
+$\Omega^{+}_b$ is an $M_b^{+}$-dimensional vector with $i$th element
+$\Omega_{1i}^{+}(b_n) - \Omega_{2i}^{+}(b_n)$, which are defined as
+\begin{align*}
+  \Omega_{1i}^{+}(b) &=
+  (1\quad 0)
+  \Big(\ssum{j}{h_n} r_1(X_j / h_n) r_1(X_j / h_n)' \Big)^{-1}
+    r_1(X_{m^+_i} / h_n) \1\{h_n > X_{m_i} \geq 0\}
+\intertext{and}
+  \Omega_{2i}^{+}(b) &=   (0\quad 0 \quad h_n^2) 
+  \Big(\ssum{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
+    r_2(X_{m^+_i} / b).
+\end{align*}
+Here $r_p(x) = (1, x, x^2,\dots,x^{p})'$ and $m^+_i$ is the subsequence of
+$1,2,\dots$ such that $0 \leq X_{m_i} < b$. The definitions of
+$\epb_{-}^{*}$ and $\Omega^-(b_n)$ have the same definitons as
+$\epb_{+}^{*}$ and $\Omega^+(b_n)$ after making the obvious
+substitiutions of ``$-$'' for ``$+$.''
 
-For~\eqref{eq:5}, since $\hat\tau - \Delta^*$ is itself asymptotically
-normal, it suffices to prove the pointwise result
-\begin{equation}
-  \label{eq:8}
-  \Big\rvert \Pr^*[(\hat\tau^{*} - \Delta^{**} - \tau^*)
-  / V^{1/2}(h_n,b_n) \leq x ] - \Phi(x)] \Big\lvert \to^p 0.
-\end{equation}
-for all $x$. Since the limiting distribution is continuous, an
-argument attributed to Poly\'a immediately extends the pointwise
-convergence result to the uniform result stated in~\eqref{eq:5}. (See
-van der vaart, p. for the details of the argument.) But~\eqref{eq:8}
-follows from Lemma~\ref{L1} as well, completing the proof.\qed
-
-\subsection{Supporting results}
-
-\begin{lemma}\label{L1}
-  Define $Z_i = (1, X_i, X_i^2)$.  Under Assumptions~\ref{A1} and~\ref{A2},
-  \begin{equation}
+Given~\eqref{eq:8}, it suffices to prove that
+\begin{gather}
   \label{eq:9}
-    \Big\rvert \Pr^*\Big[ \Gamma_\pm(b_n)^{-1/2}
-    \sum_{i \in I^{\pm}(b_n)} Z_i \varepsilon_i^* / \hat\sigma_\pm(b_n) < x \Big]
-    - \Phi(x) \Big\lvert \to^p 0.
-  \end{equation}
-\end{lemma}
-
-\begin{proof}
-  Let $z_i = \alpha' Z_i$ for an arbitrary nonzero $\alpha$ and define
-  $\gamma_\pm(b_n) = \alpha'\Gamma_\pm(b_n)\alpha$. We will
-  establsh asymptotic normality for the scalar $z_i \varepsilon_i^*$;
-  the multivariate case follows via the Cram\'er-Wold device. (cite
-  van der vaart.)
-
-  Define the filtration
-  \begin{equation}
+  \rho(V^{-1/2}(h_n) \Omega^{+}(b_n)'\epb_{+}^{*},
+    V^{-1/2}(h_n)\Omega^{+}(b_n)'\epb_{+}) \to^p 0
+  \intertext{and}
   \label{eq:10}
-    \Fc_j^{*\pm} = \sigma(Y_1,\dots,Y_n; X_1,\dots,X_n;
-    \varepsilon_{i_1}^{*\pm},\dots,\varepsilon_{i_j}^{*\pm})
-  \end{equation}
-  where the values $i_1, i_2,\dots, i_{M_h^{\pm}}$ form an ordering of
-  all of the elements of $I_n^\pm$. (The specific order is
-  unimportant.) Then
-  $\{z_{i_j} \varepsilon_{i_j}^{*\pm}, \Fc_j^{*\pm}\}$ is a martingale
-  difference sequence and~\eqref{eq:9} holds if
+  \rho(V^{-1/2}(h_n)\Omega^{-}(b_n)'\epb_{-}^{*},
+    V^{-1/2}(h_n)\Omega^{-}(b_n)'\epb_{-}) \to^p 0
+\end{gather}
+with $\epb_+$ an i.i.d. random vector of length $M_b^+$, the $i$th
+element of which is distributed as
+\[
+  \varepsilon_{i,+} =^d
+  \begin{cases}
+    Y_{m_1^+} - \E(Y_{m_1^+} \mid X_{m_1^+})
+    & \text{with probability\ } 1/M_{b}^+ \\
+    \vdots \\
+    Y_{m_{M_b^+}^+} - \E(Y_{m_{M_b^+}^+} \mid X_{m_{M_b^+}^+})
+    & \text{with probability\ } 1/M_{b}^+,
+  \end{cases}
+\]
+$\epb_-$ the corresponding quantity after replacing ``+'' with ``--,'' and
+$\rho$ the Mallows metric \citep{bickel1981}.\footnote{%
+  For two random vectors $u$ and $v$ with finite 2nd moments, $\rho(u, v)$
+  is defined as
   \begin{equation}
     \label{eq:11}
-    \savg{i}{h} z_{i}^2 \varepsilon_{i}^{*\pm\,2} -
-    \gamma_{\pm}^*(b_n) \hat\sigma
-    \to^p 0
-  \end{equation}
-  and, for all
-  $\delta > 0$,
+    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
+    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
+  \end{equation}}
+
+We will only prove~\eqref{eq:9} since the proof of~\eqref{eq:10} is
+identical. By Theorem 2.1 of \cite{freedman1981}, we have
+\begin{align*}
+  \rho(V^{-1/2}(h_n) \Omega^{+}(b_n)'\epb_{+}^{*}, V^{-1/2}(h_n)&\Omega^{+}(b_n)'\epb_{+}) \\
+  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
+    \tr(V^{-1/2}(h_n) \Omega^{+}(b_n)' \Omega^{+}(b_n)V^{-1/2}(h_n)) \\
+  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
+\end{align*}
+the second line holding as a consequence of CCT's Lemma SA1. So it suffices
+to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
+$\dot{\varepsilon}_i$ be an i.i.d. sequence randomly drawn from $\epb_+$
+with replacement and let
+$\bar{\varepsilon} = (1/M_b^{+}) \osum{i}{b_n} \dot{\varepsilon}_i$. Then,
+using the same arguments as \cite{freedman1981}, we have the upper bound
 \begin{equation}
   \label{eq:12}
-    \oavg{j}{h} z_{i_j}^2 \E^*( \varepsilon_{i_j}^{*\pm\,2}
-    \1\{z_{i_j}^2 \varepsilon_{i_j}^{*\pm\,2} / M_h^\pm > \delta \}
-    \mid \Fc_{j-1}^{\pm}) \to^p 0.
+  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
+  \leq
+  \bar\varepsilon^2 +
+  (2/M_{b_n}^+) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
+  + \rho(\dot\varepsilon_1, \varepsilon_{+,1}).
 \end{equation}
-  (cite Hall and Heyde.)
-
-  For~\eqref{eq:11}, observe that
-  $\{z_{i_j}^2 (\varepsilon_{i_j}^{*2} - \hat\sigma^2_\pm(b_n)), \Fc_j^\pm\}$
-  is also a martingale difference sequence so convergence follows from
-  the LLN.
-
-  For~\eqref{eq:12}, we have
-  \begin{align*}
-    \oavg{j}{h} z_{i_j}^2 \E^*( \varepsilon_{i_j}^{*\pm\,2}
-    \1\{z_{i_j}^2 \varepsilon_{i_j}^{*\pm\,2} / M_h^\pm > \delta \}
-    \mid \Fc_{j-1}^{\pm})
-    &= \oavg{i}{h_n} z_i^2 \oavg{j}{b_n} \hat\varepsilon_{j}^{\pm 2}
-      \1\{\hat\varepsilon_{j}^{\pm 2} > \delta M_n^{\pm} / z_i^2 \} \\
-  \end{align*}
-  (Finish with: $\varepsilon_i^2$ is uniformly integrable,
-  $\hat\varepsilon_i^2$ gets arbitrarily close to $\varepsilon_i^2$)
-\end{proof}
+But $\bar\varepsilon^2 \to^p 0$ by the LLN,
+\[
+  (1/M_{b_n}^+) \osum[+]{i}{b}
+  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
+\]
+by CCT's Lemma SA1, and
+$\rho(\dot\varepsilon_1, \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
+\cite{bickel1981}.\qed
 

### 2016-02-28 main_paper.tex
Revise introduction to the paper
This commit makes many small changes to the paper's introduction to try
to improve its flow and make our contributions clearer.

@@
 Regression Discontinuity (RD) designs have emerged in the last decade as an
-important and popular identification strategy to analyze the impact of policies
-and interventions in several fields of the social sciences, including economics,
-political science, public policy, sociology among others.
-
-The strategy exploits arbitrary rules used to assign treatment to units, usually
-relying on some type of ``score,'' the so called running variable. In its basic 
-version, units with score above a certain threshold receive treatment while the 
-ones below that cutoff are left untreated.
+important and popular research design strategy for analyzing the causal impact
+of policies and interventions in several fields of the social sciences,
+including economics, political science, public policy, and sociology, among
+others. This strategy exploits the fact that many programs use somewhat
+arbitrary threshoolds to determine whether or not to provide a ``treatment,''
+usually relying on some type of score, which this literature calls a ``running
+variable.'' In its basic version, individuals or groups with score above a
+certain threshold receive treatment while the ones below that cutoff are left
+untreated.
 
 The identification of the treatment effect at the threshold is then based on
-comparing treated and untreated units at the cutoff. As a practical matter this 
-involves comparing units within a bandwidth just above and just below the 
-threshold. That comparison is most commonly done by implementing a local linear
-estimator above and below the cutoff within bandwidths chosen to minimize the 
-asymptotic mean squared error (AMSE) as proposed by \cite{IK}
-and extended by \cite{calonico2014} (CCT, henceforth).
+comparing treated and untreated units at the cutoff. Since the observed
+characteristics of these subjects are very similar, similarity of their
+unobserved characteristics is often credible as well, and differences in the
+outcomes between the treated and untreated can be plausibly attributed to the
+treatment alone. As a practical matter this involves comparing units within a
+bandwidth just above and just below the threshold.
 
-RD designs have been used as a strategy to estimate effects of interest in a large range of topics in several areas.
-For just a few examples, RD designs are common in education, evaluating the impact of investments in school facilities, class sizes, remedial education, early childhood education, and financial aid effects on student achievement and later outcomes \citep{cellini2010,urquiola2009,jacoblefgren2004,ludwig2007,vdk2002}; in health by analyzing the impact of healthcare provision through Medicare, and neo-natal care on low birth weight children mortality \citep{Card2009,barreca2011saving}; in political science, providing evidence regarding incumbency advantage in elections, electoral enfranchising and policy changes associated with the introduction of electronic voting, strategic voting behavior, and local media effects and ad expenditure in presidential elections in the U.S.
-\citep{lee2008,Caughey2011,erikson2015,Fujiwara2015,Fujiwara2011,keele2014geographic}.
-Several more examples of the breadth of RD designs are listed by \cite{lee2010}.
+The RD design strategy was introduced by \cite{thistlethwaite1960} to study
+educational outcomes, and many of its first recent applications in economics
+were to estimate the effects of other educational policies: evaluating the
+impact of investments in school facilities, class sizes, remedial education,
+early childhood education, and financial aid effects on student achievement and
+later outcomes, for example.\footnote{%
+  See, for example, \cite{vdk2002}, \cite{jacoblefgren2004}, \cite{ludwig2007},
+  \cite{urquiola2009}, \cite{cellini2010}} %
+But the underlying identification strategy has proven to apply much more widely,
+and RD has been used in health economics\footnote{%
+  \cite{Card2009,barreca2011saving}}; %
+political science, providing evidence regarding incumbency advantage in
+elections, electoral enfranchising and policy changes associated with the
+introduction of electronic voting, strategic voting behavior, and local media
+effects and ad expenditure in presidential elections in the U.S.\footnote{%
+  \cite{lee2008}, \cite{Caughey2011}, \cite{keele2014geographic},
+  \cite{erikson2015}, \cite{Fujiwara2011,Fujiwara2015}}, %
+among other fields. \cite{imbens2008} and \cite{lee2010} provide recent
+overviews of this literature with many more examples.
 
-Recently, CCT brought attention to the fact that the popular implementation of RD designs coupling local polynomial estimation and optimal-AMSE bandwidths (as proposed by \cite{IK})
-provides confidence intervals (CIs) with incorrect coverage.
-They argue that the bandwidth selectors typically produce bandwidths that are too ``large,'' leading to a significant bias in the asymptotic distribution of the estimator.
-In that case the usual``naive'' confidence intervals for the RD treatment effects may be biased and will have provide coverage potentially well below their nominal level.
+In these studies, identification typically occurs exactly at the cutoff, so the
+treatment effect is typically estimated by fitting separate local linear models
+above and below the cutoff, then extrapolating the model to the exact point of
+discontinuity. The difference between the estimated effects at that point is
+taken to be an estimate of the treatment effect. As a practical matter, the key
+econometric issue is determining the bandwidth for the local linear models.  One
+very popular choice is the bandwidth estimator proposed by \cite{IK} and
+extended by \cite{calonico2014}, which minimizes the Asymptotic Mean Squared
+Error of difference in the models' point estimators at the cutoff.
 
-Then, CCT proposes a bias-correction procedure based on estimating the leading term of the bias to account for the effect of the ``large'' bandwidth and then obtain a re-centered t-statistic.
-This conventional bias-correction has poor finite-sample performance that arises from the estimation of the bias leading term, so they provide a new standard error formula for the standard error to  account for the additional variability introduced by the estimated bias.
-The resulting statistic that combines the higher-order($p+1$) leading term bias correction and rescaling the of the t-statistic remains asymptotically normal and supplies valid confidence intervals.
+But, as \cite{calonico2014}\footnote{%
+  We will refer to \cite{calonico2014} frequently, so we will reference it as
+  ``CCT'' for the rest of the paper.} %
+point out, the \cite{IK} bandwidth estimator has the serious drawback that,
+although it is AMSE-optimal for point estimation, it produces invalid
+\emph{confidence intervals} and hypothesis tests. The AMSE-optimal bandwidth
+converges to zero slowly, so the remaining bias term is large enough to affect
+the asymptotic distribution of the estimator. In that case the usual ``naive''
+confidence intervals for the RD treatment effects may be biased can have
+coverage well below their nominal level. CCT then make two contributions: first,
+they propose an estimator of the bias resulting from undersmoothing and provide
+a treatment effect estimator that remains asymptotically unbiased even when the
+bandwidth converges to zero slowly, at the AMSE-optimal rate.  Second, since
+this bias-correction term contributes to the asymptotic variance of the
+resulting treatment effect estimator, CCT also provide a new formula for its
+asymptotic variance. The resulting confidence intervals have accurate coverage
+even when the naive RD interval does not.
 
-As pointed out by \cite{ccf2016}, ``(...)valid inference
-requires the delicate balancing act of selecting a bandwidth small enough
-to remove smoothing bias, yet large enough to ensure adequate precision.''
-The authors compare the strategies of undersmoothing, and explicit bias 
-correction concluding that direct bias-correction with the corresponding 
-rescaling of the CI's is a superior approach.
+In this paper, we propose a bootstrap alternative to CCT's analytical
+corrections. CCT justify their estimator by showing that the bias and variance
+components for a local linear model can be accounted for by estimating a local
+second order polynomial with bandwidth of the same order.\footnote{%
+  More generally, they show that the bias and variance of a local polynomial of
+  order $p$ can be accounted for by estimating the $p+1$ local polynomial. We
+  will restrict our analysis to the case with $p = 1$ in this paper because
+  of its widespread use.} %
+They use a Taylor expansion around the cutoff to show that the bias associated
+with the second order polynomical converges to zero at a faster rate, fast
+enough that the bias of the local linear model can be estimated and removed
+using the second order polynomial. The second order polynomial also provides
+fast enough convergence that it can be used to estimate the correct variance
+correction as well.
 
-This paper contributes to the bias-corrected RD literature by proposing a simple
-bootstrap procedure to correct the first order bias term and directly obtain 
-valid CIs that provide the correct coverage.
+Our approach exploits CCT's theoretical insight through a new residual
+bootstrap. In particular, we propose, after estimating the local linear model as
+usual, estimating a local second order polynomial and generating bootstrap
+datasets by resampling the residuals of that polynomial. Since the second order
+polynomial is the true Data Generating Process (DGP), its estimate of the
+treatment effect is the true value of the treatment effect under the
+distribution induced by this bootstrap. The bias of the linear model is known
+under this distribution and can be calculated by averaging the error of the
+linear model's estimates across many bootstrap replications. This approach is
+described in detail by our Algorithm~\ref{Alg1} and the resulting bias corrected
+estimator is shown to be asymptotically normal with mean zero in our
+Theorem~\ref{T1} under AMSE-optimal bandwidth rates.
 
-The algorithm proposed draws on the main intuition put forward by CCT, that is, that correcting for the leading bias term (of order $p+1$) addresses the recentering needed for the confidence intervals.
-Hence, we propose that, after obtaining the usual RD estimates using a local polynomial of order $p$, obtain a estimates for a polynomial of order $p+1$ and generate our bootstrap datasets by bootstrapping the residuals of that polynomial.
-Since in the bootstrap datasets the bias of the estimates obtained using a lower order polynomial is known, we can estimate the leading term of the bias by averaging across bootstraps and finally subtract it from the original RD estimator.
+Just as in CCT, this bias correction introduces additional variability. However,
+the second order polynomial again adequately estimates the features of the true
+DGP that are necessary for estimating that additional variability. So we propose
+an iterated bootstrap procedure \citep{hall1988}: use the second order
+polynomial residual bootstrap to produce many bootstrap replications of the bias
+corrected estimator, and then use the resulting bootstrap distribution to
+produce confidence intervals. This procedure, which requires bootstrapping the
+datasets produced by an initial bootstrap procedure, is described in Algorithm~\ref{Alg2}, and the resulting confidence intervals are shown to be asymptotically valid in Theorem~\ref{T2}.
 
-Just as in CCT, this bias correction introduces additional variability due to the estimated bias, so we approximate the distribution of the bias-corrected estimator with a second residual bootstrap in which both the usual RD estimate and the full bias correction procedure are bootstrapped.
+This bootstrap procedure can offer some advantages over analytical methods in
+this setting. In particular, both this paper and CCT assume that the
+observations are generated independently of each other; extending these bias
+correction methods to other forms of dependence is relatively straightforward
+for the bootstrap but can be substantially more complicated for analytical
+corrections, which have to be explicitly derived by the researcher. Similarly,
+although we only provide results for the local linear model in this paper, it is
+trivial to implement this procedure for higher order polynomials, for
+covariate-adjusted estimators \citep{calonico2015}, or for other local
+smoothers. \citep{loader2006} However, in this paper we focus on the baseline
+case of sharp RD with a local linear model and uniform kernel. Extensions to
+fuzzy RD and nonuniform kernels, which require nontrivial changes to the
+underlying bootstrap algorithm, are the subject of ongoing research.
 
-The novel bootstrap procedure is easy to implement and extends to RD designs 
-using higher order polynomials, producing valid CIs which are robust to 
-bandwidth choice and have similar properties to the analytical procedure in 
-CCT while sidestepping the need to derive analytical formulas in each case of interest.
-
-Note that the procedure as presented here only coversr the uniform kernel, sharp RD designs, and i.i.d.
-data.
-Extensions to other kernels, higher order discontinuities, cross-sectional dependence, and the fuzzy RD design are subject of ongoing research.
-
-The paper is organized as follows. Section \ref{background} describes the basic
+The paper is organized as follows. Section~\ref{background} describes the basic
 RD approach, its usual implementation, and the explicit analytical bias
-correction approach in the literature. Section \ref{boot} presents the proposed 
-bootstrap bias corrected RD algorithm and discusses its properties. Simulation
-evidence that the bootstrap procedure provides valid CIs and its relative 
-performance to the analytical bias correction are presented in Section \ref{sim}.
-Finally, Section \ref{conclusion} concludes.
+correction approach in the literature. Section~\ref{boot} presents our proposed
+bootstrap bias corrected RD algorithm and discusses its asymptotic
+properties. Simulation evidence that the bootstrap procedure provides valid CIs
+and its relative performance to the analytical bias correction are presented in
+Section~\ref{sim}, and Section~\ref{application} demonstrates the estimator's
+usage by applying it to the Head Start dataset used by~\cite{ludwig2007}.
+Finally, Section~\ref{conclusion} concludes.
 

### 2016-02-28 main_paper.tex
Minor changes to introduction. Gray, please check if I did not say anything stupid. I also over played the cross sectional dependence case a little more as a future research topic since people seen to be interested in it.

@@
 the asymptotic distribution of the estimator. In that case the usual ``naive''
-confidence intervals for the RD treatment effects may be biased can have
+confidence intervals for the RD treatment effects may be biased and have
 coverage well below their nominal level. CCT then make two contributions: first,
@@
 They use a Taylor expansion around the cutoff to show that the bias associated
-with the second order polynomical converges to zero at a faster rate, fast
+with the second order polynomial converges to zero at a faster rate, fast
 enough that the bias of the local linear model can be estimated and removed
@@
 datasets by resampling the residuals of that polynomial. Since the second order
-polynomial is the true Data Generating Process (DGP), its estimate of the
+polynomial is the true Data Generating Process (DGP) in the bootstrapped data, its estimate of the
 treatment effect is the true value of the treatment effect under the
@@
 fuzzy RD and nonuniform kernels, which require nontrivial changes to the
-underlying bootstrap algorithm, are the subject of ongoing research.
+underlying bootstrap algorithm, as well as developments to address cross sectional dependence,
+ are the subject of ongoing research.
 

### 2016-02-28 main_paper.tex
Add 'sharp' to paper title to further narrow its scope
Add brief footnote on 'fuzzy RD' to introduction

@@
 
-\title{Bootstrap Confidence Intervals for Regression Discontinuity Designs with Uniform Kernels}
+\title{Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs
+  with Uniform Kernels}
+
 \author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{All authors: 
@@
 case of sharp RD with a local linear model and uniform kernel. Extensions to
-fuzzy RD and nonuniform kernels, which require nontrivial changes to the
-underlying bootstrap algorithm, as well as developments to address cross sectional dependence,
- are the subject of ongoing research.
+fuzzy RD designs\footnote{%
+  ``Fuzzy'' regression discontinuity design \citep{HTV2001}, as opposed to
+  ``sharp'' RD, describes situations where the probability of treatment changes
+  discontinuously at a known threshold, but by less than 100\%. Then there are
+  treated and untreated subjects above and below the discontinuity but the
+  treatment effect remains identified.} %
+and nonuniform kernels, which require nontrivial changes to the underlying
+bootstrap algorithm, as well as developments to address cross sectional
+dependence, are the subject of ongoing research.
 

### 2016-02-28 main_paper.tex
Revise first half of the 'background' section
This commit makes several small edits to the text of the 'background' section
of the main paper. The changes are meant to make the paper a little smoother.

@@
 
+This section provides additional details of RD estimators in general and of
+CCT's proposed bias correction. It also defines some of the notation and
+presents the assumptions that will be used for our theoretical anaysis in
+Section~\ref{boot}.
+
 In the typical sharp RD setting, a researcher wishes to estimate the local
-causal effect of treatment at a given threshold. The running variable, $X_{i}$, 
-determines treatment assignment.  Given a known threshold, $\bar{x}$, set to 
-zero without loss of generality, a unit receives treatment if $X_{i} \geq 0$ or 
-does not receive treatment if $X_{i} < 0$. Let $Y_{i}(1)$ and $Y_{i}(0)$ denote 
-the potential outcomes for unit $i$ given it receives treatment and
- in the absence of treatment, respectively. Hence, the observed sample is 
- comprised of the running variable, $X_{i}$, and
- \begin{align}
+causal effect of treatment at a given threshold. A running variable, $X_{i}$,
+determines treatment assignment.  Given a known threshold, $\bar{x}$, which can
+be set to zero without loss of generality, the $i$th subject receives the
+treatment of interest if $X_{i} \geq 0$ and does not receive treatment if
+$X_{i} < 0$.
+
+Subject $i$'s potential outcomes are denoted by the variable $Y_i(\cdot)$,
+$Y_i(1)$ indicates that the subject has received treatment and $Y_i(0)$
+indicates that the subject has not received treatment. Since only one of the two
+outcomes is observed, the sample is comprised of the running variable, $X_{i}$,
+and the observed outcome $Y_i$, where
+\begin{equation*}
   Y_{i}=Y_{i}(0) \1\{X_{i}<0\}+Y_{i}(1) \1\{X_{i} \geq 0\}
- \end{align}
-where $\1\{ \cdot\}$ denotes the indicator function. For convenience,
-define
- \begin{align}
-  \mu(x)= \E[Y_{i} \mid X_{i}=x]
- \end{align}
-Also, let $\mu^{(\eta)}(x)=\frac{d^{\eta}\mu(x)}{dx^{\eta}}$ be the $\eta^{th}$ 
-derivative of the unknown regression function and define 
-$\mu^{(\eta)}_{+}=lim_{x \rightarrow 0^{+}}\mu^{(\eta)}(x)$ and 
-$\mu^{(\eta)}_{-}=lim_{x \rightarrow 0^{-}}\mu^{(\eta)}(x)$.
-In most cases the population parameter of interest is 
-$\tau=\E[Y(1)-Y(0) \mid X=\bar{x}]$ (i.e., the average treatment effect
-at the threshold). Under continuity and smoothness conditions on both the 
-conditional distribution of $X_i$ and the first moments of $Y(0)$ and $Y(1)$ at
-the cutoff, $\tau$ is nonparametrically identifiable by
-$\tau = \mu_{+}- \mu_{-}$
-where $\mu_{+}=lim_{x \rightarrow 0^{+}}\mu(x)$ and
-$\mu_{-}=lim_{x \rightarrow 0^{-}}\mu(x)$
-(Hahn, Todd and Van der Klaauw, 2001)
+\end{equation*}
+and $\1\{ \cdot\}$ denotes the indicator function.
 
-Naturally, the estimation of $\tau$ in RD designs focuses on the 
-problem of approximating $\E[Y(1) \mid X=x]$ and $\E[Y(0) \mid X=x]$
-near the cutoff. Due to its desirable properties when estimating regression 
-functions at boundary points, we consider the popular approach of fitting 
-local linear regressions in neighborhoods on both
-sides of the threshold.\footnote{See \cite{HTV2001}, \cite{Porter03} or
-\cite{FanGijbels92} for discussions of the properties of local polynomial 
-regressions for boundary problems.The results presented here are valid for
-higher order polynomials and discontinuities at derivatives, like ``Kink RDD''. We focus on the linear case for ease in exposition.}
-For the local linear model,
+In most cases the population parameter of interest is the Average Treatment
+Effect (ATE) at the cutoff, which we will denote $\tau$. This parameter is the
+difference in expected potential outcomes given $X_i = 0$; formally,
+\begin{equation*}
+  \tau=\E(Y(1)-Y(0) \mid X=0).
+\end{equation*}
+\cite{HTV2001} show that the effect $\tau$ is identified under continuity and
+smoothness conditions on the joint distribution of $X_i$, $Y_i(0)$, and $Y_i(1)$
+around the cutoff $X_i = 0$. When these conditions hold, which are made precise
+in Assumption~\ref{A1}, $\tau$ is equal to
+\begin{equation*}
+  \tau = \lim_{x \to 0+} \mu(x) - \lim_{x \to 0-}(x)
+\end{equation*}
+where
+\begin{equation*}
+  \mu(x)= \E(Y_{i} \mid X_{i}=x).
+\end{equation*}
+For convenience, also define
+\begin{equation*}
+  \mu^{(\eta)}(x)=\frac{d^{\eta}\mu(x)}{dx^{\eta}}
+\end{equation*}
+and let
 \begin{align*}
- \hat{\tau}(h_{n})&=\hat {\mu}_{+}(h_{n}) -\hat{\mu}_{-}(h_{n})\\
-(\hat {\mu}_{+}(h_{n}),\hat {\mu}^{(1)}_{+}(h_{n}))'&= \argmin_{b_{0},b_{1}}
-\sum_{i=1}^{N}\1\{h_n > X_{i} \geq 0\}(Y_{i}-b_{0}-X_{i}b_{1})^{2} \\
-(\hat {\mu}_{-}(h_{n}),\hat {\mu}^{(1)}_{-}(h_{n}))' &= \argmin_{b_{0},b_{1}}
-\sum_{i=1}^{N}\1\{0 > X_{i} > -h_n \}(Y_{i}-b_{0}-X_{i}b_{1})^{2}
+  \mu_{+}(x)
+  &= \E( Y_{i}(1) \mid X_{i}=x )
+  &\mu_{-}(x)
+  &= \E( Y_{i}(0) \mid X_{i}=x ) \\
+  \sigma^{2}_{+}(x) &= \V( Y_{i}(1) \mid X_{i}=x )
+  &\sigma^{2}_{-}(x)&=\V( Y_{i}(0) \mid X_{i}=x ) \\
+\intertext{and}
+  \mu^{(\eta)}_{+}
+  &= \lim_{x \rightarrow 0^{+}}\mu^{(\eta)}(x),
+  &\mu^{(\eta)}_{-}
+  &= \lim_{x \rightarrow 0^{-}}\mu^{(\eta)}(x),
+\end{align*}
+where the symbol $\V(\cdot)$ represents the variance.  The effect $\tau$ is
+nonparametrically identified because both $\mu_-$ and $\mu_+$ can be estimated
+consistently under the conditions spelled out in Assumption~\ref{A1}.
+
+\begin{assumption}[Behavior of the DGP near the cutoff]\label{A1}
+  The random variables $Y_i, X_i$ form a random sample of size $N$.
+  There exists a positive number $\kappa_0$ such that the following
+  conditions hold for all $x$ in the neighborhood $(-\kappa_{0},\kappa_{0})$
+  around zero:
+  \begin{enumerate}
+  \item The density of each $X_i$ is continuous and bounded away from zero.
+  \item $\E(Y_{i}^{4} \mid X_{i}=x)$ is bounded.
+  \item $\mu_+(x)$ and $\mu_-(x)$ are both 3 times continuously differentiable.
+  \item $\sigma_+^2(x)$ and $\sigma_-^2(x)$ are both continuous and bounded away
+    from zero.
+ \end{enumerate}
+\end{assumption}
+
+These conditions are the usual smoothness and existence conditions in which the
+RD literature relies. (See, in particular, \citealp{HTV2001},
+\citealp{Porter03}, and CCT). The third part of the assumption is especially
+important for the characterization of the leading bias term drives CCT's bias
+correction and our bootstrap procedure.
+
+Since the conditions for identification only need to hold in a neighborhood
+around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
+local polynomial regression.  We will focus here on local linear
+regression.\footnote{%
+  See \cite{HTV2001}, \cite{Porter03} or \cite{FanGijbels92} for discussions of
+  the properties of local polynomial regressions for boundary problems. The
+  bootstrap algorithm proposed in this paper can be extended to accomodate
+  higher order polynomials discontinuities in the derivatives of the conditional
+  expectation, like ``Kink RD'' design. We focus on the linear case for ease in
+  exposition.} %
+For this model, if $h$ represents a bandwidth parameter, the estimator
+of $\tau$, $\hat\tau(h)$, is
+\begin{equation}
+  \label{eq:13}
+  \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
+\end{equation}
+with
+\begin{align*}
+  (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
+  &= \argmin_{\beta} \sum_{i=1}^{N}
+  \1\{h > X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}
+\intertext{and}
+  (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
+  &= \argmin_{\beta} \sum_{i=1}^{N}
+  \1\{0 > X_{i} > -h_n \} (Y_{i} - \beta_{0} - X_{i} \beta_{1})^{2}.
 \end{align*}
@@
 As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT identification and inference procedures can be developed based on the following assumptions.\footnote{The assumptions below are the same as presented by CCT.}
-
-\begin{assumption}[Behavior of the DGP near the cutoff]\label{A1}
-  The random variables $Y_i, X_i$ are independent but not necessarily
-  identically distributed. There exists a positive number $\kappa_0$
-  such that the following conditions hold for all $x$ in the
-  neighborhood $(-\kappa_{0},\kappa_{0})$ around zero:
-  \begin{enumerate}
-  \item $\E[Y_{i}^{4} \mid X_{i}=x]$ is bounded and the density of $X$
-    is continuous and bounded away from zero.
-  \item $\mu_{+}(x) = \E[ Y_{i}(1) \mid X_{i}=x ]$ and
-    $\mu_{-}(x) = \E[ Y_{i}(0) \mid X_{i}=x ]$ are $p+2$ times
-    continuously differentiable.
-  \item $\sigma^{2}_{+}(x)=\V[ Y_{i}(1) \mid X_{i}=x ]$ and
-    $\sigma^{2}_{-}(x)=\V[ Y_{i}(0) \mid X_{i}=x ]$ are continuous and
-    bounded away from zero.
- \end{enumerate}
-\end{assumption}
-
-The conditions in Assumption \ref{A1} are the usual smoothness and existence conditions in which the RD literature relies.
-Its second part is important for the characterization of the leading bias term that will be the focus of the bias correction procedures described in CCT and in the novel  bootstrap procedure proposed in Section \ref{boot}.
 
@@
   T(h_{n}) &=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), &
-  V(h_{n}) &=\V[\tau(h_{n}) \mid X_{1},\dots,X_{n}]
+  V(h_{n}) &=\V(\tau(h_{n}) \mid X_{1},\dots,X_{n})
  \end{align}

### 2016-02-28 main_paper.tex
Correct several misspellings in the paper

@@
 others. This strategy exploits the fact that many programs use somewhat
-arbitrary threshoolds to determine whether or not to provide a ``treatment,''
+arbitrary thresholds to determine whether or not to provide a ``treatment,''
 usually relying on some type of score, which this literature calls a ``running
@@
 CCT's proposed bias correction. It also defines some of the notation and
-presents the assumptions that will be used for our theoretical anaysis in
+presents the assumptions that will be used for our theoretical analysis in
 Section~\ref{boot}.
@@
   the properties of local polynomial regressions for boundary problems. The
-  bootstrap algorithm proposed in this paper can be extended to accomodate
+  bootstrap algorithm proposed in this paper can be extended to accommodate
   higher order polynomials discontinuities in the derivatives of the conditional
@@
 Table \ref{Tb: simulation 1} presents the results for the local linear model, with three panels reporting on each DGP described above.
-For each panel, we report bias, standard deviation, MSE, confidence interval empirical coverage and lenght for the four methods.
+For each panel, we report bias, standard deviation, MSE, confidence interval empirical coverage and length for the four methods.
 For the three DGPs coverage for
@@
 For the second DGP, based on \cite{ludwig2007}, the importance of correcting for the leading bias term presence becomes clear, with the naive bootstrap CI displaying an empirical coverage of only 86.9\%.
-Once again, the CIs based on both analytical and bootstrap robust methods improves the coverage meaningfully, with moderate gains in terms of coverage and lenght from $0.324$ to $0.350$ when using the bootstrap estimator relative to CCT's with uniform kernel.
+Once again, the CIs based on both analytical and bootstrap robust methods improves the coverage meaningfully, with moderate gains in terms of coverage and length from $0.324$ to $0.350$ when using the bootstrap estimator relative to CCT's with uniform kernel.
 
@@
 In \cite{ludwig2007}, analytical standard error and percentile-T bootstrapped p-value were reported\footnote{However, we were unable to reproduce their point estimates for the ATE under the nonparametric setting using triangular kernel, which was documented in their paper.
-Instead, we used uniform kernel and obtained exactely the same results as theirs.}.
+Instead, we used uniform kernel and obtained exactly the same results as theirs.}.
 The procedure proposed by CCT provides analytical standard error and confidence interval.
@@
 $1,2,\dots$ such that $0 \leq X_{m_i} < b$. The definitions of
-$\epb_{-}^{*}$ and $\Omega^-(b_n)$ have the same definitons as
+$\epb_{-}^{*}$ and $\Omega^-(b_n)$ have the same definitions as
 $\epb_{+}^{*}$ and $\Omega^+(b_n)$ after making the obvious
-substitiutions of ``$-$'' for ``$+$.''
+substitutions of ``$-$'' for ``$+$.''
 
@@
 %%% End:
+
+%  LocalWords:  Calonico Cattaneo Titiunik's Econometrica CCT AMSE CCT's DGP
+%  LocalWords:  datasets frolich calonico HTV CIs

### 2016-02-28 main_paper.tex
Add a few small citations to the introduction

@@
 trivial to implement this procedure for higher order polynomials, for
-covariate-adjusted estimators \citep{calonico2015}, or for other local
-smoothers. \citep{loader2006} However, in this paper we focus on the baseline
-case of sharp RD with a local linear model and uniform kernel. Extensions to
-fuzzy RD designs\footnote{%
+covariate-adjusted estimators (\citealp{frolich2007}, \citealp{calonico2015}),
+or for other local smoothers. \citep{loader2006} However, in this paper we focus
+on the baseline case of sharp RD with a local linear model and uniform
+kernel. Extensions to fuzzy RD designs\footnote{%
   ``Fuzzy'' regression discontinuity design \citep{HTV2001}, as opposed to
@@
   higher order polynomials discontinuities in the derivatives of the conditional
-  expectation, like ``Kink RD'' design. We focus on the linear case for ease in
-  exposition.} %
-For this model, if $h$ represents a bandwidth parameter, the estimator
-of $\tau$, $\hat\tau(h)$, is
+  expectation, like ``Kink RD'' design \citep{card2009b}. We focus on the linear
+  case for ease in exposition.} %
+For this model, if $h$ represents a bandwidth parameter, the estimator of
+$\tau$, $\hat\tau(h)$, is
 \begin{equation}

### 2016-02-28 main_paper.tex
Make additional revisions to 'background' section

@@
   (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
-  &= \argmin_{\beta} \sum_{i=1}^{N}
-  \1\{h > X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}
+  &= \argmin_{\mu, \beta} \sum_{i=1}^{N}
+  \1\{h > X_{i} \geq 0\} (Y_{i} - \mu - X_{i} \beta)^{2}
 \intertext{and}
   (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
-  &= \argmin_{\beta} \sum_{i=1}^{N}
-  \1\{0 > X_{i} > -h_n \} (Y_{i} - \beta_{0} - X_{i} \beta_{1})^{2}.
+  &= \argmin_{\mu,\beta} \sum_{i=1}^{N}
+  \1\{0 > X_{i} > -h_n \} (Y_{i} - \mu - X_{i} \beta)^{2}.
 \end{align*}
+Conventional (naive) confidence intervals can be calculated by using an
+asymptotic approximation for $\hat\tau$. In particular, if
+\begin{gather}
+  \label{eq:14}
+  T(h) =\frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
+  \intertext{with}
+  \notag
+  V(h) \to^p \plim \V(\tau(h) \mid X_{1},\dots,X_{n}),
+\end{gather}
+then valid confidence intervals can be constructed through the usual method of
+inverting the $t$-test. This procedure gives the widely-used interval estimator
+\begin{equation*}
+  \hat{\tau}(h) \pm q_{1-\alpha/2} V(h)^{1/2}
+\end{equation*}
+where $q_{1 - \alpha/2}$ is the $1 - \alpha/2$ quantile of the standard normal
+distribution.
 
-As shown by \cite{HTV2001}, \cite{Porter03} and expanded by CCT identification and inference procedures can be developed based on the following assumptions.\footnote{The assumptions below are the same as presented by CCT.}
+However, the statistical properties of these estimators clearly depend on the
+bandwidth parameter $h$, and bandwidths that have desirable properties for point
+estimation may not have desirable properties for hypothesis testing or interval
+estimation. In particular, for~\eqref{eq:14} to hold, $h$ must satisfy
+$n h \to \infty$ and $n h^5 \to 0$. (\citealp{HTV2001}; \citealp{Porter03})
+Otherwise, the finite-sample bias of $\hat\tau(h)$ does not converge in
+probability to zero quickly enough and it contributes non-negligibly to the
+asymptotic distribution~\eqref{eq:14}. This result holds even though
+$\hat\tau(h)$ can be consistent under those conditions.  These bandwidth issues
+are relevant in practice because many widely-used bandwidth selection
+procedures, most notably the AMSE-optimal bandwidth and cross-validation
+bandwidth \citep{IK} do not satisfy this condition.
 
+CCT solve this problem by deriving the analytical form of the first-order bias
+and explicitly recentering $\hat\tau(h)$. Under weaker assumptions on the
+asymptotic behavior of the bandwidth, which we will specify in
+Assumption~\ref{A2}, CCT show that the approximate bias of $\hat\tau(h)$ has the
+form
+\begin{gather*}
+  \E(\hat{\tau}(h) \mid \chi_{n}) - \tau = h^{2}\Bs(h)\{1+o_{p}(1)\}
+  \intertext{with}
+  \Bs(h)=\tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
+  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h)
+\end{gather*}
+where $\Bf_{+}(h_{n})$ and $\Bf_{-}(h_{n})$ are observed quantities that depend
+on the data, kernel, and bandwidth. The plug-in bias-corrected estimator then
+requires estimates for the second derivatives of the conditional mean from above
+and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that
+these derivatives can be estimated by fitting a second order local polynomial,
+i.e. one order higher than the polynomial used to obtain $\hat{\tau}$, using a
+(potentially) different pilot bandwidth $b$. Their procedure gives the
+bias-corrected estimator
+\begin{gather*}
+  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2} \hat{\Bs}(h,b)
+  \intertext{with}
+  \hat{\Bs}(h) = \tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
+  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h).
+\end{gather*}
+The variance introduced by the bias-correction term does not vanish, so the
+naive confidence interval needs not only to be re-centered to correct the bias,
+but also rescaled to allow for the additional variability introduced by the bias
+correction, resulting in the following asymptotic approximation:
+\begin{equation}
+  T'(h, b) = \frac{\hat{\tau}'(h, b) - \tau}{V'(h_{n}, b_{n})^{1/2}}
+  \to^d N(0,1)
+\end{equation}
+with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
+generated by the bias-correction term. This new approximation can be used
+instead of~\eqref{eq:14} to construct ``bandwidth robust'' confidence intervals,
+and CCT provide simulation evidence that their intervals perform well in finite
+samples.
+
+Assumption~\ref{A2} specifies the bandwidth conditions assumed by CCT, which we
+will also use in this paper.
 \begin{assumption}[Bandwidth]\label{A2}
-  Let $h_{n}$ be the bandwidth used to estimate the local linear model and let
-  $b_{n}$ be the bandwidth used to estimate a local quadratic model. Then
-  $n h_{n} \to \infty$, $n b_{n} \to \infty$, $n h_{n}^{5} b_{n}^{2} \to 0$, and
-  $n b_{n}^{5} h_{n}^{2} \to 0$ as $n \to \infty$.\footnote{%
+  Let $h$ be the bandwidth used to estimate the local linear model and let
+  $b$ be the bandwidth used to estimate a second local quadratic model. Then
+  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
+  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
     Unless otherwise stated, all limits in this paper are assumed to hold as
@@
 
-CCT point out that the conventional approaches to construct confidence intervals for $\tau$ using the local linear estimator rely on a large-sample approximation for the standardized $t$-statistic that is valid only if the bandwidth shrink fast enough to eliminate the leading bias term contribution to the approximation.
-Hence, if $nh_{n}^{5}\rightarrow0$ and $nh_{n}\rightarrow \infty$, then
- \begin{align}
-  T(h_{n}) &=\frac{\hat{\tau}(h_{n})-\tau}{\sqrt{V(h_{n})}}\rightarrow_{d}N(0,1), &
-  V(h_{n}) &=\V(\tau(h_{n}) \mid X_{1},\dots,X_{n})
- \end{align}
- The conditional variance $V(h_{n})$ depends on the $\sigma^{2}_{+}=lim_{x \rightarrow 0^{+}}\sigma^{2}_{+}(x)$ and $\sigma^{2}_{-}=lim_{x \rightarrow 0^{-}}\sigma^{2}_{-}(x)$ as well as $h_{n}$ and known quantities that depend on the kernel and order of polynomial used in the estimation.
-Under these conditions we could use a conventional confidence interval for $\tau$ given by
- \begin{align}
-  I(h_{n})=\left[\hat{\tau}(h_{n})\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})} \right]
- \end{align}
-with $\Phi^{-1}_{1-\frac{\alpha}{2}}$ being the $\alpha$-quantile of the standard normal distribution.
-However, most approaches to select the bandwidth, $h_{n}$ in the literature, including the widely used optimal-AMSE bandwidth selector proposed by \cite{IK} lead to bandwidth choices that are ``too large'' since they do not satisfy the condition $nh_{n}^{5}\rightarrow0$, leading to a first-order bias in the distributional approximation used to construct the confidence intervals.
-
-CCT solve the problem by deriving the analytical form of the first-order bias and correcting it directly.
-To obtain correct coverage the confidence interval needs not only to be re-centered to correct the bias, but also rescaled to allow for the additional variability introduced by the bias correction.
-Their approach relies on obtaining a bias-corrected  estimator, $\hat{\tau}^{bc}$ and its adjusted variance.
-It is important first to note that the first-order bias term itself will depend on the bandwidth $h_{n}$.
-The approximate bias term can be described as:
-\begin{align*}
-     \E[\hat{\tau}(h_{n}) \mid \chi_{n}]-\tau=& h_{n}^{2}\Bs(h_{n})\{1+o_{p}(1)\}\\
-     \Bs(h_{n})=&\frac{\mu_{+}^{(2)}}{2!}\Bf_{+}(h_{n})-\frac{\mu_{-}^{(2)}}{2!}\Bf_{-}(h_{n})
-   \end{align*}
-where $\Bf_{+}(h_{n})$ and $\Bf_{-}(h_{n})$ are observed quantities that depend on the data, kernel and $h_{n}$.
-The plug-in bias-corrected estimator then requires estimates for the second derivatives of the conditional mean from above and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$.
-CCT propose using a conventional local quadratic estimator, i.e.
-one order higher than the polynomial used to obtain $\hat{\tau}$,  using a (potentially) different pilot bandwidth $b_{n}$.
-\begin{align*}
-     \hat{\tau}^{bc}(h_{n}, b_{n})=& \hat{\tau}-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\\
-     \hat{\Bs}(h_{n})=&\frac{\hat{\mu}_{+}^{(2)}(b_{n})}{2!}\Bf_{+}(h_{n})-\frac{\hat{\mu}_{-}^{(2)}(b_{n})}{2!}\Bf_{-}(h_{n})
-   \end{align*}
-By incorporating the contribution of both $\hat{\tau}(h_{n})$ and $\hat{\Bs}(h_{n},b_{n})$ to the asymptotic distribution of the estimator, CCT obtain a robust confidence interval with a different asymptotic variance in general.
-So under Assumptions \ref{A1} and \ref{A2}, if $n\min\{h_{n}^{5}, b_{n}^{5}\}max\{h_{n}^{2}, b_{n}^{2}\}\rightarrow 0$ and $n\min\{h_{n}, b_{n}\}\rightarrow \infty$ and $\kappa \max\{h_{n},b_{n}\}< \kappa_{0}$, they show that
-\begin{align}
-  T^{rbc}(h_{n}, b_{n})=\frac{\hat{\tau}^{bc}(h_{n}, b_{n})-\tau}{\sqrt{V^{bc}(h_{n}, b_{n})}}\rightarrow_{d}N(0,1), \text{        }V^{bc}(h_{n}, b_{n})=V(h_{n})+C^{bc}(h_{n}, b_{n})\\
- \end{align}
-where the additional term $C^{bc}(h_{n}, b_{n})$ depends on the (asymptotic) variability of the bias estimate used for correction as well as its correlation with the original RD estimator $\hat{\tau}(h_{n})$.\footnote{The details of the formulas are currently ommitted from this paper since their form is not relevant to the bootstrap procedure innovation proposed.
-The details can be found at CCT Appendix.}  Under these conditions we can construct a valid confidence interval for $\tau$ given by
- \begin{align}
-  I^{rbc}(h_{n}, b_{n})=\left[\left(\hat{\tau}(h_{n})-h_{n}^{2}\hat{\Bs}(h_{n},b_{n})\right)\pm \Phi^{-1}_{1-\frac{\alpha}{2}}\sqrt{V(h_{n})+C^{bc}(h_{n}, b_{n})} \right]
- \end{align}
-
-This approach is shown by the authors to significantly improve coverage of the CIs constructed and provides practitioners with a new tool set to perform inference that is more robust to the choice of bandwidth.
-We build upon the insight provided by CCT bias-corrected estimator and propose a simple bootstrap procedure that can directly construct the robust CIs without requiring the derivation of analytical formulas and direct estimators for the bias, variance and covariance terms, while relying on the same first-order bias correction approximation.
+In the next section, we build upon the insight provided by CCT bias-corrected
+estimator and propose a simple bootstrap procedure that can directly construct
+the robust CIs without requiring the derivation of analytical formulas and
+direct estimators for the bias, variance and covariance terms, while relying on
+the same first-order bias correction approximation. The requirement $h < b$ is
+new to this paper, because the bootstrap can not be implemented for the uniform
+kernel without it, but the other parts of Assumption~\ref{A2} are taken from
+CCT.
 

### 2016-02-28 main_paper.tex
Rename appendix
More very small changes related to the kernel description

@@
 \title{Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs
-  with Uniform Kernels}
+  with the Uniform Kernel}
 
@@
     $n \to \infty$.} %
-  The relationship $h_{n} \leq b_{n}$ also holds for all $n$.
+  The relationship $h \leq b$ also holds for all $n$.
 \end{assumption}
@@
 kernel without it, but the other parts of Assumption~\ref{A2} are taken from
-CCT.
+CCT.\footnote{%
+  This assumption can be relaxed by considering other kernels, which is the
+  subject of current research by the authors.} %
 
@@
 
-\section{Proofs of mathematical results}
+\appendix
+\section{Mathematical appendix}
 \subsection{Proof of Theorem~\ref{T1}}

### 2016-02-29 main_paper.tex
Make very small changes to background section

@@
 
-Subject $i$'s potential outcomes are denoted by the variable $Y_i(\cdot)$,
+Subject $i$'s potential outcomes are denoted by the variable $Y_i(\cdot)$;
 $Y_i(1)$ indicates that the subject has received treatment and $Y_i(0)$
@@
 
-These conditions are the usual smoothness and existence conditions in which the
-RD literature relies. (See, in particular, \citealp{HTV2001},
-\citealp{Porter03}, and CCT). The third part of the assumption is especially
-important for the characterization of the leading bias term drives CCT's bias
-correction and our bootstrap procedure.
+These conditions are standard in the RD literature. (See, in particular,
+\citealp{HTV2001}, \citealp{Porter03}, and CCT). The third part of the
+assumption is especially important for the characterization of the leading bias
+term drives CCT's bias correction and our bootstrap procedure.
 
@@
   &= \argmin_{\mu,\beta} \sum_{i=1}^{N}
-  \1\{0 > X_{i} > -h_n \} (Y_{i} - \mu - X_{i} \beta)^{2}.
+  \1\{0 > X_{i} > -h \} (Y_{i} - \mu - X_{i} \beta)^{2}.
 \end{align*}
 Conventional (naive) confidence intervals can be calculated by using an
-asymptotic approximation for $\hat\tau$. In particular, if
+asymptotic approximation for $\hat\tau(h)$. In particular, if
 \begin{gather}
@@
   \notag
-  V(h) \to^p \plim \V(\tau(h) \mid X_{1},\dots,X_{n}),
+  V(h) \big/ \V(\hat\tau(h) \mid X_{1},\dots,X_{n}) \to^p 1
 \end{gather}
@@
 
-However, the statistical properties of these estimators clearly depend on the
+The statistical properties of these estimators, however, clearly depend on the
 bandwidth parameter $h$, and bandwidths that have desirable properties for point
@@
 \end{gather*}
-where $\Bf_{+}(h_{n})$ and $\Bf_{-}(h_{n})$ are observed quantities that depend
+where $\Bf_{+}(h)$ and $\Bf_{-}(h)$ are observed quantities that depend
 on the data, kernel, and bandwidth. The plug-in bias-corrected estimator then
@@
   \intertext{with}
-  \hat{\Bs}(h) = \tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
+  \hat{\Bs}(h,b) = \tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
   - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h).
@@
 \begin{equation}
-  T'(h, b) = \frac{\hat{\tau}'(h, b) - \tau}{V'(h_{n}, b_{n})^{1/2}}
+  T'(h, b) = \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}}
   \to^d N(0,1)
@@
 the same first-order bias correction approximation. The requirement $h < b$ is
-new to this paper, because the bootstrap can not be implemented for the uniform
-kernel without it, but the other parts of Assumption~\ref{A2} are taken from
-CCT.\footnote{%
+one additional restriction that we impose in this paper because the bootstrap
+can not be implemented for the uniform kernel without it, but the other parts of
+Assumption~\ref{A2} are identical to CCT.\footnote{%
   This assumption can be relaxed by considering other kernels, which is the

### 2016-02-29 main_paper.tex
Clean up equation labels and some notation

@@
 \begin{assumption}[Behavior of the DGP near the cutoff]\label{A1}
-  The random variables $Y_i, X_i$ form a random sample of size $N$.
+  The random variables $Y_i, X_i$ form a random sample of size $n$.
   There exists a positive number $\kappa_0$ such that the following
@@
 $\tau$, $\hat\tau(h)$, is
-\begin{equation}
-  \label{eq:13}
+\begin{equation*}
   \hat{\tau}(h) = \hat {\mu}_{+}(h) -\hat{\mu}_{-}(h)
-\end{equation}
+\end{equation*}
 with
@@
   (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
-  &= \argmin_{\mu, \beta} \sum_{i=1}^{N}
+  &= \argmin_{\mu, \beta} \sum_{i=1}^{n}
   \1\{h > X_{i} \geq 0\} (Y_{i} - \mu - X_{i} \beta)^{2}
@@
   (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
-  &= \argmin_{\mu,\beta} \sum_{i=1}^{N}
+  &= \argmin_{\mu,\beta} \sum_{i=1}^{n}
   \1\{0 > X_{i} > -h \} (Y_{i} - \mu - X_{i} \beta)^{2}.
@@
 \begin{gather}
-  \label{eq:14}
+  \label{eq:1}
   T(h) =\frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
@@
 estimation may not have desirable properties for hypothesis testing or interval
-estimation. In particular, for~\eqref{eq:14} to hold, $h$ must satisfy
+estimation. In particular, for~\eqref{eq:1} to hold, $h$ must satisfy
 $n h \to \infty$ and $n h^5 \to 0$. (\citealp{HTV2001}; \citealp{Porter03})
@@
 probability to zero quickly enough and it contributes non-negligibly to the
-asymptotic distribution~\eqref{eq:14}. This result holds even though
+asymptotic distribution~\eqref{eq:1}. This result holds even though
 $\hat\tau(h)$ can be consistent under those conditions.  These bandwidth issues
@@
 correction, resulting in the following asymptotic approximation:
-\begin{equation}
+\begin{equation*}
   T'(h, b) = \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}}
   \to^d N(0,1)
-\end{equation}
+\end{equation*}
 with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
 generated by the bias-correction term. This new approximation can be used
-instead of~\eqref{eq:14} to construct ``bandwidth robust'' confidence intervals,
+instead of~\eqref{eq:1} to construct ``bandwidth robust'' confidence intervals,
 and CCT provide simulation evidence that their intervals perform well in finite
@@
 Hence, the bias for a specific bootstrap data is given by $\tau^{*}-\hat{\tau}^{*}$.
-More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\Bs}(h_{n},b_{n})$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates, i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
+More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\Bs}(h,b)$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates, i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
 Algorithm~\ref{Alg1} describes this procedure step-by-step for clarity.
@@
 \begin{algorithm}[Bias estimation]\label{Alg1}
-  Assume $h_{n}$ and $b_{n}$ are bandwidths as described by Assumption~\ref{A2} and define
-  \begin{align}
-    I^{-}(h) &= \{i : h < X_{i} < 0\}, &
-    I^{+}(h) &= \{i : 0 < X_{i} < h\}.
-  \end{align}
-  Also define $M^{-}(h_{n})$ and $M^{+}(h_{n})$ to be the number of elements in
-  $I^{-}(h_{n})$ and $I^{+}(h_{n})$ respectively.
+  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
+  \begin{align*}
+    I_-(h) &= \{i : -h < X_{i} < 0\}, &
+    I_+(h) &= \{i : 0 \leq X_{i} < h\}.
+  \end{align*}
+  Also define $M_-(h)$ and $M_+(h)$ to be the number of elements in
+  $I_-(h)$ and $I_+(h)$ respectively.
   \begin{enumerate}
-  \item Estimate the local polynomials $g_{p+1}^{+}$ and $g_{p+1}^{-}$ as defined by
-    Equation --- and define the residuals
-    \begin{equation}
-      \label{eq:1}
+  \item Estimate local second order polynomials $\hat g_-$ and $\hat g_+$ using
+    the observations in $I_-(b)$ and $I_+(b)$:
+    \begin{align*}
+      \hat g_-(x)
+      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^2,
+      &\hat g_+(x)
+      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^2
+    \end{align*}
+    with
+    \begin{align*}
+      \hat\beta_- &= \argmin_\beta \sum_{i \in I_-(b)}
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2 \\
+      \hat\beta_+ &= \argmin_\beta \sum_{i \in I_+(b)}
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2.
+    \end{align*}
+    Calculate the residuals
+    \begin{equation*}
       \hat\varepsilon_{i} =
       \begin{cases}
-        Y_{i} - \hat g_{p+1}^-(X_{i}) & \textif\ X_{i} < 0 \\
-        Y_{i} - \hat g_{p+1}^+(X_{i}) & \otherwise
+        Y_{i} - \hat g_-(X_{i}) & \textif\ X_{i} < 0 \\
+        Y_{i} - \hat g_+(X_{i}) & \otherwise
       \end{cases}
-    \end{equation}
-  \item Repeat the following steps $B_1$ times to produce a sequence of bootstrap
-    estimates $\hat\tau_1^*,\dots,\hat\tau_{B_1}^*$. For the $k$th step:
+    \end{equation*}
+  \item Repeat the following steps $B_1$ times to produce a sequence of
+    bootstrap estimates $\hat\tau_1^*(h),\dots,\hat\tau_{B_1}(h)^*$. For the
+    $k$th step:
     \begin{enumerate}
-    \item Draw an i.i.d. sample of size $M^-(b_n)$ from
-      $\{\hat\varepsilon_i : i \in I^-(b_n)\}$ and one of size $M^+(b_n)$ from
-      $\{\hat\varepsilon_i : i \in I^+(h_n)\}$. Let $\varepsilon_i^{*-}$ and
+    \item Draw an i.i.d. sample of size $M^-(b)$ from
+      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
+      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_i^{*-}$ and
       $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
-      \begin{align}
+      \begin{align*}
         Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
         Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
-      \end{align}
+      \end{align*}
     \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
-      \begin{align}
+      \begin{align*}
         \hat\mu_-^*
         &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
-          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
+          \sum_{i = 1}^{M_-(h)} (Y_i^{*-} -
           (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
@@
         &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
-          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
+          \sum_{i = 1}^{M_+(h)} (Y_i^{*+} -
           (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
-      \end{align}
+      \end{align*}
     \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
@@
   \item Estimate the bias as
-    \begin{equation}
-      \label{eq:2}
+    \begin{equation*}
       \Delta^* = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
       \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
-    \end{equation}
+    \end{equation*}
   \end{enumerate}
@@
   Under Assumptions~\ref{A1} and~\ref{A2},
-\begin{align}
-  \frac{(\hat\tau(h_{n},b_{n}) - \Delta^{*}(h_{n},b_{n}) - \tau)}{ V^{1/2}(h_n, b_n)} \to^{d} N(0,1)
-\end{align}
+\begin{align*}
+  \frac{(\hat\tau(h,b) - \Delta^{*}(h,b) - \tau)}{ V^{1/2}(h, b)} \to^{d} N(0,1)
+\end{align*}
 \end{theorem}
@@
 Each one of the bias corrected estimates for the generated data is denoted $\hat{\tau}^{bc*}$.
-These estimator's empirical distribution capture the variability induced by the first order bias correction that lead CCT to propose the rescaling of their confidence intervals by introducing $C^{bc}(h_{n},b_{n})$ in the asymptotic variance formula on Section \ref{background}.
+These estimator's empirical distribution capture the variability induced by the first order bias correction that lead CCT to propose the rescaling of their confidence intervals by introducing $C^{bc}(h,b)$ in the asymptotic variance formula on Section \ref{background}.
 
 \begin{algorithm}[Confidence intervals]\label{Alg2}
-  Define $I^{-}$, $I^{+}$, $M^{-}$, and $M^{+}$ as in Algorithm~\ref{Alg1}.
+  Define $I_-$, $I_+$, $M_-$, and $M_+$ as in Algorithm~\ref{Alg1}.
   \begin{enumerate}
@@
     Equation --- and define the residuals
-    \begin{equation}
-      \label{eq:3}
+    \begin{equation*}
       \hat\varepsilon_{i} =
@@
       \end{cases}
-    \end{equation}
+    \end{equation*}
   \item Repeat the following steps $B_{2}$ times to produce a sequence of bootstrap
@@
     \begin{enumerate}
-    \item Draw an i.i.d. sample of size $M^{-}(b_{n})$ from
-      $\{\hat\varepsilon_{i} : i \in I^{-}(b_{n})\}$ and one of size $M^{+}(b_{n})$ from
-      $\{\hat\varepsilon_i : i \in I^{+}(h_{n})\}$. Let $\varepsilon_{i}^{*-}$ and
+    \item Draw an i.i.d. sample of size $M_-(b)$ from
+      $\{\hat\varepsilon_{i} : i \in I_-(b)\}$ and one of size $M_+(b)$ from
+      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{i}^{*-}$ and
       $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
-      \begin{align}
+      \begin{align*}
         Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
         Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
-      \end{align}
+      \end{align*}
     \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
-      \begin{align}
+      \begin{align*}
         \hat\mu_-^*
         &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
-          \sum_{i = 1}^{M^-(h_n)} (Y_i^{*-} -
+          \sum_{i = 1}^{M_-(h)} (Y_i^{*-} -
           (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
@@
         &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
-          \sum_{i = 1}^{M^+(h_n)} (Y_i^{*+} -
+          \sum_{i = 1}^{M_+(h)} (Y_i^{*+} -
           (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
-      \end{align}
+      \end{align*}
     \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
       \begin{equation*}
-        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M^-(b_n)}^{*-},X_{M^-(b_n)}^{*-}),
-        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M^+(b_n)}^{*+},X_{M^+(b_n)}^{*+}),
+        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M_-(b)}^{*-},X_{M_-(b)}^{*-}),
+        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M_+(b)}^{*+},X_{M_+(b)}^{*+}),
       \end{equation*}
-      using the same bandwidths $h_n$ and $b_n$ that are used in the rest of
+      using the same bandwidths $h$ and $b$ that are used in the rest of
       this algorithm but reestimating all of the local polynomials on the
@@
   Under Assumptions~\ref{A1} and~\ref{A2},
-  \begin{gather}
-    \label{eq:4}
-    \V^*(\hat\tau^{*} - \Delta^{**})/V(h_n,b_n) \to^p 1
+  \begin{gather*}
+    \V^*(\hat\tau^{*} - \Delta^{**})/V(h,b) \to^p 1
   \intertext{and}
-  \label{eq:5}
     \sup_{x}
@@
     - \Pr[\hat\tau - \Delta^* - \tau \leq x] \Big\lvert \to^p 0.
-  \end{gather}
+  \end{gather*}
 \end{theorem}
@@
 Hence, $\mu_{1}(x)$ is given by,
-\begin{align}
+\begin{align*}
 \mu_{1}(x) & = 
@@
 \end{cases}
-\end{align}
+\end{align*}
 
 The functional form for $\mu_{2}(x)$, in the second DGP follows the data observed by \cite{ludwig2007}, which we examine in more detail on Section \ref{application}, and follows
-\begin{align}
+\begin{align*}
 \mu_{2}(x) & = 
@@
 \end{cases}
-\end{align}
+\end{align*}
 
@@
 This functional form is the same as used in CCT and serves as an useful example of the effectiveness of the bias correction procedures implemented.
-\begin{align}
+\begin{align*}
 \mu_{3}(x) & =
@@
 \begin{align*}
-  \label{eq:6}
-  \E^* \hat\mu_{+}^*(h_n) - \mu_{+}^{*}
-  &= h_n^{2} \mu_+^{*(2)} \Bf_{+}(h_n)/2,
-  &\E^* \hat\mu_{-}^*(h_n) - \mu_{-}^{*}
-  &= h_n^{2} \mu_-^{*(2)} \Bf_{-}(h_n)/2,
+  \E^* \hat\mu_{+}^*(h) - \mu_{+}^{*}
+  &= h^{2} \mu_+^{*(2)} \Bf_{+}(h)/2,
+  &\E^* \hat\mu_{-}^*(h) - \mu_{-}^{*}
+  &= h^{2} \mu_-^{*(2)} \Bf_{-}(h)/2,
 \end{align*}
@@
 \begin{equation*}
-  \label{eq:7}
-    \E^* \hat\tau^{*}_h - \tau^{*} = h_n^2\, \mu_+^{*(2)} \Bf(h_n)/2
-      - h_n^2\, \mu_{-}^{*(2)} \Bf_{-}(h_n)/2.
+    \E^* \hat\tau^{*}_h - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf(h)/2
+      - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
 \end{equation*}
@@
   &= \hat\tau_h - \E\hat\tau_h
-   + h_n^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h_{n}) /2
-   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 \big) + O_p(h_n^{3}) \\
+   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
+   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
   &= \hat\tau_h - \E\hat\tau_h
-   + h_n^2 (\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}) \Bf_{-}(h_{n}) /2 \notag \\
-  \label{eq:8}
-  &\pushright{- h_n^2 (\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}) \Bf_{+}(h_{n}) / 2 + O_p(h_n^{3})}
+   + h^2 (\hat\mu_-^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \notag \\
+  \label{eq:2}
+  &\pushright{- h^2 (\hat\mu_+^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2 + O_p(h^{3})}
 \end{align}
 The second equality holds because
-$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b_n)$ and
-$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b_n)$ almost surely. Asymptotic
+$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b)$ and
+$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b)$ almost surely. Asymptotic
 normality then follows from normality of $\hat\tau_h - \E\hat\tau_h$,
-$\hat\mu_+^{(2)}(b_n) - \mu_+^{(2)}$, and
-$\hat\mu_-^{(2)}(b_n) - \mu_-^{(2)}$ using similar arguments to
+$\hat\mu_+^{(2)}(b) - \mu_+^{(2)}$, and
+$\hat\mu_-^{(2)}(b) - \mu_-^{(2)}$ using similar arguments to
 CCT's Lemma SA4.D.\qed
@@
 \subsection{Proof of Theorem~\ref{T2}}
-Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:8} to get
+Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:2} to get
 \begin{align*}
@@
   &= \hat\tau^*_h - \E^*\hat\tau^*_h
-   + h_n^2 (\hat\mu_-^{*(2)}(b_n) - \mu_-^{*(2)}) \Bf_{-}(h_{n}) /2
-   - h_n^2 (\hat\mu_+^{*(2)}(b_n) - \mu_+^{*(2)}) \Bf_{+}(h_{n}) / 2 \\
-  &= \Omega^{+}(b_n)' \epb_{+}^{*} - \Omega^{-}(b_n)' \epb_{-}^{*},
+   + h^2 (\hat\mu_-^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
+   - h^2 (\hat\mu_+^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
+  &= \Omega^{+}(b)' \epb_{+}^{*} - \Omega^{-}(b)' \epb_{-}^{*},
 \end{align*}
@@
 $\Omega^{+}_b$ is an $M_b^{+}$-dimensional vector with $i$th element
-$\Omega_{1i}^{+}(b_n) - \Omega_{2i}^{+}(b_n)$, which are defined as
+$\Omega_{1i}^{+}(b) - \Omega_{2i}^{+}(b)$, which are defined as
 \begin{align*}
@@
   (1\quad 0)
-  \Big(\ssum{j}{h_n} r_1(X_j / h_n) r_1(X_j / h_n)' \Big)^{-1}
-    r_1(X_{m^+_i} / h_n) \1\{h_n > X_{m_i} \geq 0\}
+  \Big(\ssum{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
+    r_1(X_{m^+_i} / h) \1\{h > X_{m_i} \geq 0\}
 \intertext{and}
-  \Omega_{2i}^{+}(b) &=   (0\quad 0 \quad h_n^2) 
+  \Omega_{2i}^{+}(b) &= (0\quad 0 \quad h^2)
   \Big(\ssum{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
@@
 $1,2,\dots$ such that $0 \leq X_{m_i} < b$. The definitions of
-$\epb_{-}^{*}$ and $\Omega^-(b_n)$ have the same definitions as
-$\epb_{+}^{*}$ and $\Omega^+(b_n)$ after making the obvious
+$\epb_{-}^{*}$ and $\Omega^-(b)$ have the same definitions as
+$\epb_{+}^{*}$ and $\Omega^+(b)$ after making the obvious
 substitutions of ``$-$'' for ``$+$.''
 
-Given~\eqref{eq:8}, it suffices to prove that
+Given~\eqref{eq:2}, it suffices to prove that
 \begin{gather}
-  \label{eq:9}
-  \rho(V^{-1/2}(h_n) \Omega^{+}(b_n)'\epb_{+}^{*},
-    V^{-1/2}(h_n)\Omega^{+}(b_n)'\epb_{+}) \to^p 0
+  \label{eq:3}
+  \rho(V^{-1/2}(h) \Omega^{+}(b)'\epb_{+}^{*},
+    V^{-1/2}(h)\Omega^{+}(b)'\epb_{+}) \to^p 0
   \intertext{and}
-  \label{eq:10}
-  \rho(V^{-1/2}(h_n)\Omega^{-}(b_n)'\epb_{-}^{*},
-    V^{-1/2}(h_n)\Omega^{-}(b_n)'\epb_{-}) \to^p 0
+  \label{eq:4}
+  \rho(V^{-1/2}(h)\Omega^{-}(b)'\epb_{-}^{*},
+    V^{-1/2}(h)\Omega^{-}(b)'\epb_{-}) \to^p 0
 \end{gather}
@@
   is defined as
-  \begin{equation}
-    \label{eq:11}
+  \begin{equation*}
     \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
     \big(\E \lVert U - V \rVert^2\big)^{1/2}.
-  \end{equation}}
+  \end{equation*}}
 
-We will only prove~\eqref{eq:9} since the proof of~\eqref{eq:10} is
+We will only prove~\eqref{eq:3} since the proof of~\eqref{eq:4} is
 identical. By Theorem 2.1 of \cite{freedman1981}, we have
 \begin{align*}
-  \rho(V^{-1/2}(h_n) \Omega^{+}(b_n)'\epb_{+}^{*}, V^{-1/2}(h_n)&\Omega^{+}(b_n)'\epb_{+}) \\
+  \rho(V^{-1/2}(h) \Omega^{+}(b)'\epb_{+}^{*}, V^{-1/2}(h)&\Omega^{+}(b)'\epb_{+}) \\
   &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
-    \tr(V^{-1/2}(h_n) \Omega^{+}(b_n)' \Omega^{+}(b_n)V^{-1/2}(h_n)) \\
+    \tr(V^{-1/2}(h) \Omega^{+}(b)' \Omega^{+}(b)V^{-1/2}(h)) \\
   &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
@@
 with replacement and let
-$\bar{\varepsilon} = (1/M_b^{+}) \osum{i}{b_n} \dot{\varepsilon}_i$. Then,
+$\bar{\varepsilon} = (1/M_b^{+}) \osum{i}{b} \dot{\varepsilon}_i$. Then,
 using the same arguments as \cite{freedman1981}, we have the upper bound
-\begin{equation}
-  \label{eq:12}
+\begin{equation*}
   \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
@@
   \bar\varepsilon^2 +
-  (2/M_{b_n}^+) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
+  (2/M_{b}^+) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
   + \rho(\dot\varepsilon_1, \varepsilon_{+,1}).
-\end{equation}
+\end{equation*}
 But $\bar\varepsilon^2 \to^p 0$ by the LLN,
 \[
-  (1/M_{b_n}^+) \osum[+]{i}{b}
+  (1/M_{b}^+) \osum[+]{i}{b}
   \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0

### 2016-02-29 main_paper.tex
Make additional changes to theoretical results
This commit tightens some of the language around Algorithm and Theorem 1 and also
makes some small notation adjustments in the text and proof.

@@
 form
+\begin{equation*}
+  \E(\hat{\tau}(h) \mid \chi_{n}) - \tau =
+  h^{2}\Big[ \tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
+  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h) \Big]
+  (1+o_{p}(1))
+\end{equation*}
+where $\Bf_{+}(h)$ and $\Bf_{-}(h)$ are observed quantities that depend on the
+kernel, bandwidth, and running variables $X_1,\dots,X_n$; formal definitions of
+these terms are given in the Mathematical Appendix as Equations~\eqref{eq:3}
+and~\eqref{eq:4}. The plug-in bias-corrected estimator then requires estimates
+for the second derivatives of the conditional mean from above and below the
+cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that these derivatives
+can be estimated by fitting a second order local polynomial, i.e. one order
+higher than the polynomial used to obtain $\hat{\tau}$, using a (potentially)
+different pilot bandwidth $b$. Their procedure gives the bias-corrected
+estimator
 \begin{gather*}
-  \E(\hat{\tau}(h) \mid \chi_{n}) - \tau = h^{2}\Bs(h)\{1+o_{p}(1)\}
-  \intertext{with}
-  \Bs(h)=\tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
-  - \tfrac{\mu_{-}^{(2)}}{2}\Bf_{-}(h)
-\end{gather*}
-where $\Bf_{+}(h)$ and $\Bf_{-}(h)$ are observed quantities that depend
-on the data, kernel, and bandwidth. The plug-in bias-corrected estimator then
-requires estimates for the second derivatives of the conditional mean from above
-and below the cutoff, $\mu_{+}^{(2)}$ and $\mu_{-}^{(2)}$, and CCT show that
-these derivatives can be estimated by fitting a second order local polynomial,
-i.e. one order higher than the polynomial used to obtain $\hat{\tau}$, using a
-(potentially) different pilot bandwidth $b$. Their procedure gives the
-bias-corrected estimator
-\begin{gather*}
-  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2} \hat{\Bs}(h,b)
-  \intertext{with}
-  \hat{\Bs}(h,b) = \tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
-  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h).
+  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2}
+  \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
+  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
 \end{gather*}
@@
   \end{align*}
-  Also define $M_-(h)$ and $M_+(h)$ to be the number of elements in
+  Also define $M_-(h)$ and $M_+(h)$ to be the number of elements in $I_-(h)$ and
+  $I_+(h)$ respectively and $m_-(h,1),\dots,m_-(h,M_-(h))$ and
+  $m_+(h,1),\dots,m_+(h,M_+(h))$ to be subsequences of $1,\dots,n$ that index
   $I_-(h)$ and $I_+(h)$ respectively.
@@
   \item Repeat the following steps $B_1$ times to produce a sequence of
-    bootstrap estimates $\hat\tau_1^*(h),\dots,\hat\tau_{B_1}(h)^*$. For the
-    $k$th step:
+    bootstrap estimates $\hat\tau_1^*(h),\dots,\hat\tau_{B_1}^*(h)$. For the
+    $k$th estimate:
     \begin{enumerate}
-    \item Draw an i.i.d. sample of size $M^-(b)$ from
+    \item Draw an i.i.d. sample of size $M_-(b)$ from
       $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
-      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_i^{*-}$ and
-      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
+      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{-,i}^{*}$ and
+      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
+      construct
       \begin{align*}
-        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
-        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
+        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
+        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_-(h,i)}) + \varepsilon_{+,i}^{*}.
       \end{align*}
-    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
+    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
+      local linear model on the bootstrap data set:\footnote{%
+        Note that the indices of summation are chosen to correspond to the
+        indices of the variables generated in the previous step.} %
       \begin{align*}
-        \hat\mu_-^*
-        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
-          \sum_{i = 1}^{M_-(h)} (Y_i^{*-} -
-          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
-        \hat\mu_+^*
-        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
-          \sum_{i = 1}^{M_+(h)} (Y_i^{*+} -
-          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
+        \hat\mu_-^*(h)
+        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
+          (Y_i^* - \mu - \beta X_i^*)^2 \\
+        \hat\mu_+^*(h)
+        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
+          (Y_i^* - \mu - \beta X_i^*)^2.
       \end{align*}
-    \item Save $\hat\mu_+^* - \hat\mu_-^*$ as $\hat\tau^*_k$.
+    \item Save $\hat\mu_+^*(h) - \hat\mu_-^*(h)$ as $\hat\tau^*_k$.
     \end{enumerate}
@@
     \begin{equation*}
-      \Delta^* = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
-      \big[\hat g_{p+1}^+(0) - \hat g_{p+1}^-(0)\big]
+      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
+      \big[\hat g_+(0) - \hat g_-(0)\big].
     \end{equation*}
@@
 \end{algorithm}
-The distribution of $\Delta^{*}$ depends on $B_{1}$ and we could
-incorporate that dependency into our notation by writing $\Delta^*_{B_1}$. However, we will follow standard practice in the bootstrap
-literature and assume that $B_{1}$ is large enough that it can be ignored and define $\Delta^* = \plim_{B_{1} \to \infty} \Delta^*_{B_{1}}$
 
@@
 Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
-converges fast enough in probability that it can be be used as a correction. As is standard in the bootstrap literature, we will assume
-that the number of bootstrap replications, $B_{1}$, is large enough that the simulation error can be ignored.
+converges fast enough in probability that it can be be used as a correction. As
+is standard in the bootstrap literature, we will assume that the number of
+bootstrap replications, $B_{1}$, is large enough that the simulation error can
+be ignored.
 
@@
   Under Assumptions~\ref{A1} and~\ref{A2},
-\begin{align*}
-  \frac{(\hat\tau(h,b) - \Delta^{*}(h,b) - \tau)}{ V^{1/2}(h, b)} \to^{d} N(0,1)
-\end{align*}
+\begin{equation}
+  \label{eq:2}
+  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V(h, b)^{1/2}}
+  \to^{d} N(0,1)
+\end{equation}
 \end{theorem}
+
+Note that the variance component of~\eqref{eq:2} is the same value used by CCT
+and introduced in~\eqref{eq:1}. Theorem~\ref{T1} implies that our
+bias-corrected estimator has the same asymptotic distribution as CCT's. This
+equivalence should be unsurprising; both estimators use a 2nd order polynomial
+to directly estimate the bias of the local linear model, so they should behave
+very similarly.
 
@@
       \begin{align*}
-        Y_i^{*-} &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
-        Y_i^{*+} &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
+        Y_{-,i}^* &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
+        Y_{+,i}^* &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
       \end{align*}
@@
         &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
-          \sum_{i = 1}^{M_-(h)} (Y_i^{*-} -
+          \sum_{i = 1}^{M_-(h)} (Y_{-,i}^* -
           (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
@@
         &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
-          \sum_{i = 1}^{M_+(h)} (Y_i^{*+} -
+          \sum_{i = 1}^{M_+(h)} (Y_{+,i}^* -
           (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
@@
 \section{Mathematical appendix}
+
+Define the following additional notation:
+$r_p(x) = (1,\ x,\dots,\ x^p)'$,
+\begin{align}
+  \label{eq:3}
+  \Bf_+(h)
+  & = (1\ \  0)\ \Big(\ssum[+]{i}{h} r_1(X_i/h) r_1(X_i/h)' \Big)^{-1}
+    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
+  \label{eq:4}
+  \Bf_-(h)
+  & = (1\ \ 0)\ \Big(\ssum[-]{i}{h} r_1(X_i/h) r_1(X_i/h)' \Big)^{-1}
+    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
+\end{align}
+
 \subsection{Proof of Theorem~\ref{T1}}
@@
 \begin{equation*}
-  \hat\tau_h - \Delta^*_h - \tau = (\hat\tau_h - \E \hat \tau_h) +
-  (\E \hat \tau_h - \tau) - (\E^* \hat \tau^*_h - \tau^*)
+  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
+  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
 \end{equation*}
@@
 \begin{equation*}
-    \E^* \hat\tau^{*}_h - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf(h)/2
+    \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
       - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
@@
 \begin{align}
-  \hat\tau_h - & \E \hat\tau_h + (\E \hat\tau_h - \tau) - (\E^* \hat\tau^*_h - \tau^*)\notag \\
-  &= \hat\tau_h - \E\hat\tau_h
+  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
+  &= \hat\tau(h) - \E\hat\tau(h)
    + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
    - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
-  &= \hat\tau_h - \E\hat\tau_h
-   + h^2 (\hat\mu_-^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \notag \\
-  \label{eq:2}
+  \label{eq:5}
+  &= \hat\tau(h) - \E\hat\tau(h)
+   + h^2 (\hat\mu_-^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
+  \notag
   &\pushright{- h^2 (\hat\mu_+^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2 + O_p(h^{3})}
@@
 $\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b)$ almost surely. Asymptotic
-normality then follows from normality of $\hat\tau_h - \E\hat\tau_h$,
+normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$,
 $\hat\mu_+^{(2)}(b) - \mu_+^{(2)}$, and
@@
 \subsection{Proof of Theorem~\ref{T2}}
-Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:2} to get
+Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:5} to get
 \begin{align*}
-  \hat\tau_h^* - &\Delta_h^{**} - \tau^*
-  = (\hat\tau^*_h - \E^* \hat \tau^*_h) +
-  (\E^* \hat \tau^*_h - \tau^*) - (\E^{**} \hat \tau^{**}_h - \tau^{**}) \\
-  &= \hat\tau^*_h - \E^*\hat\tau^*_h
+  \hat\tau(h)^* - &\Delta_h^{**} - \tau^*
+  = (\hat\tau^*(h) - \E^* \hat \tau^*(h)) +
+  (\E^* \hat \tau^*(h) - \tau^*) - (\E^{**} \hat \tau^{**}_h - \tau^{**}) \\
+  &= \hat\tau^*(h) - \E^*\hat\tau^*(h)
    + h^2 (\hat\mu_-^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
@@
 
-Given~\eqref{eq:2}, it suffices to prove that
+Given~\eqref{eq:5}, it suffices to prove that
 \begin{gather}
-  \label{eq:3}
+  \label{eq:6}
   \rho(V^{-1/2}(h) \Omega^{+}(b)'\epb_{+}^{*},
@@
   \intertext{and}
-  \label{eq:4}
+  \label{eq:7}
   \rho(V^{-1/2}(h)\Omega^{-}(b)'\epb_{-}^{*},
@@
 
-We will only prove~\eqref{eq:3} since the proof of~\eqref{eq:4} is
+We will only prove~\eqref{eq:6} since the proof of~\eqref{eq:7} is
 identical. By Theorem 2.1 of \cite{freedman1981}, we have

### 2016-02-29 main_paper.tex
Revise description of 2nd algorithm

@@
 kernel, bandwidth, and running variables $X_1,\dots,X_n$; formal definitions of
-these terms are given in the Mathematical Appendix as Equations~\eqref{eq:3}
-and~\eqref{eq:4}. The plug-in bias-corrected estimator then requires estimates
+these terms are given in the Mathematical Appendix as Equations~\eqref{eq:5}
+and~\eqref{eq:6}. The plug-in bias-corrected estimator then requires estimates
 for the second derivatives of the conditional mean from above and below the
@@
 
-Building upon the results and intuition developed by CCT we propose to implement a first-order bias correction and obtain valid CIs through a bootstrap procedure.
-Intuitively, for the local-linear RD estimator's case, we will rely on a local quadratic polynomial approximation for the conditional outcome around the cutoff to capture the potential bias present in the original RD estimate.
-This insight comes directly from CCT's results using the same local quadratic approximation to estimate bias term as presented in Section \ref{background}.
+This section presents our theoretical contributions. We propose two algorithms
+in this section. The first uses a residual bootstrap based on based on a second
+order local polynomial to estimate the bias of the local linear model. That
+estimate can be subtracted from the biased original estimator to provide an
+asymptotically unbiased estimator with the same asymptotic distribution as
+CCT's. As in CCT, this bias correction term introduces a new source of variance,
+invalidating standard (naive) critical values. Consequently, the second
+algorithm we propose uses an iterated bootstrap to estimate the correct
+critical values of the bias corrected estimator.
 
-The first algorithm describes how to obtain a point estimate and perform the bias correction.
-The second algorithm obtains its confidence interval with correct coverage.
-For simplicity, we adopt the same optimal-AMSE bandwidth selector proposed by CCT.\footnote{An interesting question is whether one could use a bootstrap based procedure to select a bandwidth that would achieve similar (or improved) results.
-This is beyond the scope of this particular paper but is part of ongoing research effort.}
-
-Essentially, we apply CCT's insight that a polynomial one order higher can capture the first-order bias behavior and create a bootstrap procedure that can correctly mimic the behavior of the bias present in the original estimator.
-For such, for a chosen bandwidth, we estimate a local quadratic regression as suggested by CCT, but then bootstrap data by imposing the local quadratic functional form as the DGP.
-Then, in the bootstrap data the DGP is known.
-Let the ``true'' treatment effect under the bootstrap DGP be denoted by $\tau^{*}$.
-We then estimate the treatment effect using the (misspecified) local linear estimator, $\hat{\tau}^{*}$ to the generated data.
-Hence, the bias for a specific bootstrap data is given by $\tau^{*}-\hat{\tau}^{*}$.
-More importantly, by generating new bootstrapped data based on the same quadratic DGP and its residual's distribution, we can obtain an estimate of the first-order bias (the part that is captured by $\hat{\Bs}(h,b)$ in CCT's formulas on Section \ref{background}) in the original estimate by averaging across the bias in all $B$ bootstrapped data estimates, i.e., $\tau^{*} - \sum_{i = 1}^{B} \hat{\tau}_{ i}^{*}$.
-Algorithm~\ref{Alg1} describes this procedure step-by-step for clarity.
+The intuition behind both procedures is very straightforward. CCT show that a
+local second order polynomial captures all of the unmodeled aspects of the DGP
+necessary for constructing valid confidence intervals. Our proposed algorithms
+estimate and embed the second order behavior in the bootstrap DGP through
+a residual bootstap.
+Algorithm~\ref{Alg1} explains the bias-correction steps in detail.
 
@@
     the observations in $I_-(b)$ and $I_+(b)$:
-    \begin{align*}
+    \begin{align}
+      \label{eq:2}
       \hat g_-(x)
@@
       &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^2
-    \end{align*}
+    \end{align}
     with
@@
     Calculate the residuals
-    \begin{equation*}
+    \begin{equation}
+      \label{eq:3}
       \hat\varepsilon_{i} =
@@
         Y_{i} - \hat g_-(X_{i}) & \textif\ X_{i} < 0 \\
-        Y_{i} - \hat g_+(X_{i}) & \otherwise
+        Y_{i} - \hat g_+(X_{i}) & \otherwise.
       \end{cases}
-    \end{equation*}
+    \end{equation}
   \item Repeat the following steps $B_1$ times to produce a sequence of
@@
       \end{align*}
-    \item Save $\hat\mu_+^*(h) - \hat\mu_-^*(h)$ as $\hat\tau^*_k$.
+    \item Save $\hat\tau^*_k(h) = \hat\mu_+^*(h) - \hat\mu_-^*(h)$.
     \end{enumerate}
@@
 \end{algorithm}
+Note that $\hat g_+(0) - \hat g_-(0)$ is the true treatment effect under the
+distribution induced by this bootstrap. The bootstrap estimator works by
+constructing an approximate DGP with known properties. As the dataset gets
+larger, the approximate DGP mimics the unknown real DGP more closely, and the
+population parameter values in the bootstrap DGP can become accurate estimates
+of the true parameter values in the real DGP.
 
@@
 bootstrap replications, $B_{1}$, is large enough that the simulation error can
-be ignored.
+be ignored. Theorem~\ref{T1} presents the result formally.
 
@@
 \begin{equation}
-  \label{eq:2}
-  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V(h, b)^{1/2}}
+  \label{eq:4}
+  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
   \to^{d} N(0,1)
@@
 
-Note that the variance component of~\eqref{eq:2} is the same value used by CCT
-and introduced in~\eqref{eq:1}. Theorem~\ref{T1} implies that our
-bias-corrected estimator has the same asymptotic distribution as CCT's. This
-equivalence should be unsurprising; both estimators use a 2nd order polynomial
-to directly estimate the bias of the local linear model, so they should behave
-very similarly.
+Note that the variance component of~\eqref{eq:4} is the same value used by CCT
+and introduced in~\eqref{eq:1}. Theorem~\ref{T1} implies that our bias-corrected
+estimator has the same asymptotic distribution as CCT's. This equivalence should
+be unsurprising; both estimators use a 2nd order polynomial to directly estimate
+the bias of the local linear model, so they should behave very similarly.
 
-With Algorithm~\ref{Alg1} at hand, we can move to generate the bias-corrected confidence intervals to perform inference about $\tau$.
-Here the idea is similar, but now we actually calculate a bias corrected estimate using Algorithm~\ref{Alg1} for every bootstrapped dataset generated, a bootstrap within the bootstrap.
-Each one of the bias corrected estimates for the generated data is denoted $\hat{\tau}^{bc*}$.
-These estimator's empirical distribution capture the variability induced by the first order bias correction that lead CCT to propose the rescaling of their confidence intervals by introducing $C^{bc}(h,b)$ in the asymptotic variance formula on Section \ref{background}.
+Since the second order polynomial captures the relevant aspects of the DGP for
+estimating the variance as well as the bias, the asymptotic distribution of the
+bias corrected estimator $\hat\tau(h) - \Delta^*(h,b)$ can also be approximated
+with a bootstrap. We propose bootstrapping $\hat\tau(h) - \Delta^*(h,b)$ using
+the same residual bootstrap method that was used in
+Algorithm~\ref{Alg1}. Algorithm~\ref{Alg2} provides the details of our procedure
+and Theorem~\ref{T2} establishes its theoretical properties.
 
 \begin{algorithm}[Confidence intervals]\label{Alg2}
-  Define $I_-$, $I_+$, $M_-$, and $M_+$ as in Algorithm~\ref{Alg1}.
+  Define the same notation as in Algorithm~\ref{Alg1}.
   \begin{enumerate}
-  \item Estimate the local polynomials $g_{p+1}^{+}$ and $g_{p+1}^{-}$ as defined by
-    Equation --- and define the residuals
-    \begin{equation*}
-      \hat\varepsilon_{i} =
-      \begin{cases}
-        Y_i - \hat g_{p+1}^-(X_{i}) & \textif\ X_{i} < 0 \\
-        Y_i - \hat g_{p+1}^+(X_{i}) & \otherwise
-      \end{cases}
-    \end{equation*}
-  \item Repeat the following steps $B_{2}$ times to produce a sequence of bootstrap
-    estimates $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_{2}}^{\prime*}$. For the $k$th step:
+  \item Estimate $\hat g_+$ and $g_-$ and generate the residuals
+    $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}; Equations~\eqref{eq:2}
+    and~\eqref{eq:3}.
+  \item Repeat the following steps $B_{2}$ times to produce a sequence of
+    bootstrap estimates
+    $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
+    $k$th step:
     \begin{enumerate}
     \item Draw an i.i.d. sample of size $M_-(b)$ from
-      $\{\hat\varepsilon_{i} : i \in I_-(b)\}$ and one of size $M_+(b)$ from
-      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{i}^{*-}$ and
-      $\varepsilon_i^{*+}$ denote the $i$th element of each sample and construct
+      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
+      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{-,i}^{*}$ and
+      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
+      construct
       \begin{align*}
-        Y_{-,i}^* &= \hat g_{p+1}^-(X_i^{*-}) + \varepsilon_i^{*-} &
-        Y_{+,i}^* &= \hat g_{p+1}^+(X_i^{*+}) + \varepsilon_i^{*+}
+        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
+        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_-(h,i)}) + \varepsilon_{+,i}^{*}.
       \end{align*}
-    \item Calculate $\hat\mu_+^*$ and $\hat\mu_-^*$ as
+    \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
+      local linear model on the bootstrap data set:
       \begin{align*}
-        \hat\mu_-^*
-        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
-          \sum_{i = 1}^{M_-(h)} (Y_{-,i}^* -
-          (\beta_0 + \beta_1 X_i^{*-} + \cdots + \beta_p (X_i^{*-})^p))^2 \\
-        \hat\mu_+^*
-        &= \argmin_{\beta_0} \min_{\beta_1,\dots,\beta_p}
-          \sum_{i = 1}^{M_+(h)} (Y_{+,i}^* -
-          (\beta_0 + \beta_1 X_i^{*+} + \cdots + \beta_p (X_i^{*+})^p))^2
+        \hat\mu_-^*(h)
+        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
+          (Y_i^* - \mu - \beta X_i^*)^2 \\
+        \hat\mu_+^*(h)
+        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
+          (Y_i^* - \mu - \beta X_i^*)^2.
       \end{align*}
     \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
-      \begin{equation*}
-        (Y_1^{*-}, X_1^{*-}),\dots,(Y_{M_-(b)}^{*-},X_{M_-(b)}^{*-}),
-        (Y_1^{*+}, X_1^{*+}),\dots,(Y_{M_+(b)}^{*+},X_{M_+(b)}^{*+}),
-      \end{equation*}
-      using the same bandwidths $h$ and $b$ that are used in the rest of
-      this algorithm but reestimating all of the local polynomials on the
-      bootstrap data. Let $\Delta^{**}$ represent the bias estimator returned
-      by Algorithm~\ref{Alg1}.
+      \begin{multline*}
+        (Y_{-,m_-(b,1)}^{*}, X_{-,m_-(b,1)}),\dots,
+        (Y_{-,m_-(b,M_-(b))}^{*},X_{-,m_-(b,M_-(b))}), \\
+        (Y_{+,m_+(b,1)}^{*}, X_{+,m_+(b,1)}),\dots,
+        (Y_{+,m_+(b,M_+(b))}^{*},X_{+,m_+(b,M_+(b))})
+      \end{multline*}
+      using the same bandwidths $h$ and $b$ that are used in the rest of this
+      algorithm but reestimating all of the local polynomials on the bootstrap
+      data. Generate $B_1$ new bootstrap samples and let $\Delta^{**}(h,b)$
+      represent the bias estimator returned by Algorithm~\ref{Alg1}.
     \item Save the bias-corrected estimator
-      $\hat\tau_k^{\prime*} = \hat\mu_+^* - \hat\mu_i^* - \Delta^{**}$.
+      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
+      - \Delta^{**}(h,b)$.
     \end{enumerate}
-  \item Define the confidence interval endpoints $\hat\ell(\alpha)$ and
-    $\hat u(\alpha)$ as the $\alpha/2$ and $1-\alpha/2$ quantiles of the
-    empirical CDF of $\hat\tau_1^{\prime*},\dots,\hat\tau_{B_2}^{\prime*}$.
+  \item Use the empirical CDF of
+    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
+    construct confidence intervals, etc.
   \end{enumerate}
@@
 
-As earlier, we assume that $B_1$ and $B_2$ are large enough that simulation
-error can be ignored. Define the limiting values
-\begin{align*}
-\Delta^{**} &= \plim_{B_1,B_2 \to \infty} \Delta^{**}_{B_1,B_2} \\
-\hat\ell^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat\ell^*_{B_1,B_2}(\alpha) \\
-\hat u^*(\alpha) &= \plim_{B_1,B_2 \to \infty} \hat u^*_{B_1,B_2}(\alpha).
-\end{align*}
-
-Theorem~\ref{T2} establishes that this ``bootstrap-within-bootstrap''
-approximates the asymptotic distribution of the bias-corrected
-statistic proposed by Algorithm~\ref{Alg1} and justifies this second
-algorithm.
+Theorem~\ref{T2} establishes that this iterated bootstrap approximates the
+asymptotic distribution of the bias-corrected statistic proposed by
+Algorithm~\ref{Alg1} and justifies this second algorithm.  As before, we assume
+that $B_1$ and $B_2$ are large enough that simulation error can be ignored.
 
@@
   \begin{gather*}
-    \V^*(\hat\tau^{*} - \Delta^{**})/V(h,b) \to^p 1
+    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
   \intertext{and}
     \sup_{x}
-    \Big\rvert \Pr^*[\hat\tau^{*} - \Delta^{**} - \tau^* \leq x ]
-    - \Pr[\hat\tau - \Delta^* - \tau \leq x] \Big\lvert \to^p 0.
+    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
+    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
   \end{gather*}
@@
 \begin{align}
-  \label{eq:3}
+  \label{eq:5}
   \Bf_+(h)
@@
     \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
-  \label{eq:4}
+  \label{eq:6}
   \Bf_-(h)
@@
    - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
-  \label{eq:5}
+  \label{eq:7}
   &= \hat\tau(h) - \E\hat\tau(h)
@@
 \subsection{Proof of Theorem~\ref{T2}}
-Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:5} to get
+Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:7} to get
 \begin{align*}
@@
 
-Given~\eqref{eq:5}, it suffices to prove that
+Given~\eqref{eq:7}, it suffices to prove that
 \begin{gather}
-  \label{eq:6}
+  \label{eq:8}
   \rho(V^{-1/2}(h) \Omega^{+}(b)'\epb_{+}^{*},
@@
   \intertext{and}
-  \label{eq:7}
+  \label{eq:9}
   \rho(V^{-1/2}(h)\Omega^{-}(b)'\epb_{-}^{*},
@@
 
-We will only prove~\eqref{eq:6} since the proof of~\eqref{eq:7} is
+We will only prove~\eqref{eq:8} since the proof of~\eqref{eq:9} is
 identical. By Theorem 2.1 of \cite{freedman1981}, we have

### 2016-02-29 main_paper.tex
Clean up proof of Theorem 2

@@
 \begin{align*}
-  \hat\tau(h)^* - &\Delta_h^{**} - \tau^*
+  \hat\tau(h)^* - &\Delta^{**}(h,b) - \tau^*
   = (\hat\tau^*(h) - \E^* \hat \tau^*(h)) +
-  (\E^* \hat \tau^*(h) - \tau^*) - (\E^{**} \hat \tau^{**}_h - \tau^{**}) \\
+  (\E^* \hat \tau^*(h) - \tau^*) - (\E^{**} \hat \tau^{**}(h) - \tau^{**}) \\
   &= \hat\tau^*(h) - \E^*\hat\tau^*(h)
@@
    - h^2 (\hat\mu_+^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
-  &= \Omega^{+}(b)' \epb_{+}^{*} - \Omega^{-}(b)' \epb_{-}^{*},
+  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
 \end{align*}
@@
 $\epb_{+}^{*} =
-(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_b^{+}}^{*})'$ and
-$\Omega^{+}_b$ is an $M_b^{+}$-dimensional vector with $i$th element
-$\Omega_{1i}^{+}(b) - \Omega_{2i}^{+}(b)$, which are defined as
+(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
+$\Omega_+(h,b)$ is an $M_b^{+}$-dimensional vector with $i$th element
+$\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
 \begin{align*}
-  \Omega_{1i}^{+}(b) &=
+  \Omega_{+,1i}(h,b) &=
   (1\quad 0)
   \Big(\ssum{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
-    r_1(X_{m^+_i} / h) \1\{h > X_{m_i} \geq 0\}
+    r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
 \intertext{and}
-  \Omega_{2i}^{+}(b) &= (0\quad 0 \quad h^2)
+  \Omega_{2i}^{+}(h,b) &= (0\quad 0 \quad h^2)
   \Big(\ssum{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
-    r_2(X_{m^+_i} / b).
+    r_2(X_{m_+(b,i)} / b).
 \end{align*}
-Here $r_p(x) = (1, x, x^2,\dots,x^{p})'$ and $m^+_i$ is the subsequence of
-$1,2,\dots$ such that $0 \leq X_{m_i} < b$. The definitions of
-$\epb_{-}^{*}$ and $\Omega^-(b)$ have the same definitions as
-$\epb_{+}^{*}$ and $\Omega^+(b)$ after making the obvious
-substitutions of ``$-$'' for ``$+$.''
+The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same definitions as
+$\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the obvious substitutions of
+``$-$'' for ``$+$.''
 
@@
   \label{eq:8}
-  \rho(V^{-1/2}(h) \Omega^{+}(b)'\epb_{+}^{*},
-    V^{-1/2}(h)\Omega^{+}(b)'\epb_{+}) \to^p 0
+  \rho(V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}^{*},
+    V^{-1/2}(h,b)\Omega_+(h,b)'\epb_{+}) \to^p 0
   \intertext{and}
   \label{eq:9}
-  \rho(V^{-1/2}(h)\Omega^{-}(b)'\epb_{-}^{*},
-    V^{-1/2}(h)\Omega^{-}(b)'\epb_{-}) \to^p 0
+  \rho(V^{-1/2}(h,b)\Omega^{-}(b)'\epb_{-}^{*},
+    V^{-1/2}(h,b)\Omega^{-}(b)'\epb_{-}) \to^p 0
 \end{gather}
-with $\epb_+$ an i.i.d. random vector of length $M_b^+$, the $i$th
-element of which is distributed as
+with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th element of
+which is distributed as
 \[
@@
   \begin{cases}
-    Y_{m_1^+} - \E(Y_{m_1^+} \mid X_{m_1^+})
-    & \text{with probability\ } 1/M_{b}^+ \\
+    Y_{m_+(1,b)} - \E(Y_{m_+(1,b)} \mid X_{m_+(1,b)})
+    & \text{with probability\ } 1/M_+(b) \\
     \vdots \\
-    Y_{m_{M_b^+}^+} - \E(Y_{m_{M_b^+}^+} \mid X_{m_{M_b^+}^+})
-    & \text{with probability\ } 1/M_{b}^+,
+    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(1,b)})
+    & \text{with probability\ } 1/M_+(b),
   \end{cases}
@@
 \begin{align*}
-  \rho(V^{-1/2}(h) \Omega^{+}(b)'\epb_{+}^{*}, V^{-1/2}(h)&\Omega^{+}(b)'\epb_{+}) \\
+  \rho(V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}^{*},\
+  &V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}) \\
   &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
-    \tr(V^{-1/2}(h) \Omega^{+}(b)' \Omega^{+}(b)V^{-1/2}(h)) \\
+    \tr(V^{-1/2}(h,b) \Omega_+(h,b)' \Omega_+(h,b)V^{-1/2}(h,b)) \\
   &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
@@
 with replacement and let
-$\bar{\varepsilon} = (1/M_b^{+}) \osum{i}{b} \dot{\varepsilon}_i$. Then,
+$\bar{\varepsilon} = (1/M_+(b)) \osum[+]{i}{b} \dot{\varepsilon}_i$. Then,
 using the same arguments as \cite{freedman1981}, we have the upper bound
@@
   \bar\varepsilon^2 +
-  (2/M_{b}^+) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
+  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
   + \rho(\dot\varepsilon_1, \varepsilon_{+,1}).

### 2016-02-29 main_paper.tex
Revise beginning of monte carlo section
This commit makes some minor changes to smooth out the beginning of the
Monte Carlo section.

@@
 
-This section presents evidence from Monte Carlo simulations that the bootstrap bias correction procedures proposed in Section \ref{boot} produces valid, robust confidence intervals similar to the ones obtained by the analytical procedures established in CCT.
-The bootstrap CIs obtained compare favorably to the analytical alternative, with coverage closer to the nominal size of the desired test and shorter length of the intervals in the specifications implemented.
-
-We adopt the same three data generating processes (DGP) used by CCT to make it easy to compare our results.
-Also, these DGPs are widely used in the RD literature to evaluate the performance of inference procedures and provide a good testing ground for bias correction due to their exacerbated curvature.
-
-For all Monte Carlo experiments, the pseudo data are generated as 500 i.i.d. draws from:
-\begin{align*}
-& Y_{i} = \mu_{j}(X_{i}) + \epsilon_{i}, \;\;\; X_{i} \sim  (2 B (2,4) - 1)), \\
-& \epsilon_{i} \sim N(0, \sigma^{2}), \;\;\; \sigma = 0.1295, \;\;\; j = 1,2,3.
-\end{align*}
-Regarding the functional form for $\mu(x)$ in each DGP, the first one is based on a fifth order polynomial fitted on the data observed by \cite{lee2008rand} when estimating the incumbency advantage in electoral races to the U.S.
-House of Representatives.
-Hence, $\mu_{1}(x)$ is given by,
-\begin{align*}
-\mu_{1}(x) & = 
+This section presents evidence from Monte Carlo simulations that the bootstrap
+procedures proposed in Section~\ref{boot} produce valid, robust confidence
+intervals similar to the ones obtained by the analytical procedures established
+in CCT. The bootstrap CIs obtained compare favorably to the analytical
+alternative, with coverage slightly closer to nominal coverage and shorter
+length of the intervals in the specifications implemented.
+
+The Monte Calro experiments have a similar structure. For all of them, we
+generate 500 i.i.d.\ observations from the DGP
+\begin{align*}
+Y_{i}           &= \mu_{j}(X_{i}) + \varepsilon_{i} \\
+X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
+\varepsilon_{i} &\sim \normal(0, 0.1295^2),
+\end{align*}
+where $j$ will index the specific DGP. This is the experimental design used by
+\citet{IK} CCT, which we adopt here to make our simulation results directly
+comparable with theirs and more comparable with the rest of the literature. We
+will use the same three functional forms for $\mu_j$ as CCT as well.
+
+\nocite{lee2008rand}%
+The first DGP is designed to match features of Lee's (2008) analysis of U.S.\
+congressional elections. Lee estimates the incumbency advantage in electoral
+races for the House of Representatives --- candidates who received the largest
+vote share in the previous election are the incumbants, which creates the
+discontinuity. The conditional expectation is a fifth order polynomial fit to
+that dataset, (after excluding a small number of extreme observations; see
+\citealp{IK}, or CCT for further details) giving
+\begin{equation*}
+  \mu_{1}(x) =
   \begin{cases}
-0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}, \;\;\;\; & \text{if} \;\; x < 0, \\
-0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5},  & \text{if} \;\; x \ge 0.
+    0.48 + 1.27x + 7.18x^{2} + 20.21x^{3} + 21.54x^{4} + 7.33x^{5}
+    & \textif\ x < 0 \\
+    0.52 + 0.84x - 3.00x^{2} + 7.99x^3 - 9.01x^4 + 3.56x^{5}
+    & \otherwise.
   \end{cases}
-\end{align*}
-
-The functional form for $\mu_{2}(x)$, in the second DGP follows the data observed by \cite{ludwig2007}, which we examine in more detail on Section \ref{application}, and follows
-\begin{align*}
-\mu_{2}(x) & = 
+\end{equation*}
+The population ATE for this DGP is $0.04$ $(= 0.52 - 0.48)$.
+
+\nocite{ludwig2007}%
+The second DGP is based on Ludwig and Miller's (2007) analysis of the Head Start
+program. Funding eligability is determined at the county level using the
+county's historical poverty rate, with a sharp threshold that determines the
+provision of services. We use the fifth order polynomial estimated on Ludwig and
+Miller's dataset as the conditional expectation for the second DGP:
+\begin{equation*}
+  \mu_{2}(x) =
   \begin{cases}
-3.71 + 2.30x + 3.28x^2 + 1.45x^3 + 0.23x^4 + 0.03x^5, \;\; & \text{if} \;\; x < 0, \\
-0.26 + 18.49x - 54.81x^2 + 74.30x^3 - 45.02x^4 + 9.83x^5,  & \text{if} \;\; x \ge 0.
+    3.71 + 2.30x + 3.28x^2 + 1.45x^3 + 0.23x^4 + 0.03x^5
+    & \textif\ x < 0, \\
+    0.26 + 18.49x - 54.81x^2 + 74.30x^3 - 45.02x^4 + 9.83x^5
+    & \otherwise
   \end{cases}
-\end{align*}
-
-Finally, the third DGP used in the simulations is given by a modified version of  \cite{lee2008rand} designed to exhibit more curvature and, hence, be more sensitive to the choice of bandwidth in terms of bias.
-This functional form is the same as used in CCT and serves as an useful example of the effectiveness of the bias correction procedures implemented.
-\begin{align*}
-\mu_{3}(x) & =
+\end{equation*}
+and the population ATE is $-3.45$ $(= 0.26 - 3.71)$.
+
+Finally, for the third DGP, we use CCT's modification of $\mu_1$, given by
+\begin{equation*}
+  \mu_{3}(x) =
   \begin{cases}
-0.48 + 1.27x + 0.5 \times 7.18x^{2}+ \\
-+ 0.7 \times 20.21x^3 + 1.1 \times 21.54x^4 + 1.5 \times 7.33x^5, \;\;\;\;\;\;\;\;\;\;\;\; & \text{if} \;\; x < 0, \\
-0.52 + 0.84x - 0.1 \times 3.00x^{2}+ \\
-+ 0.3 \times 7.99x^3 - 0.1 \times 9.01x^4 + 3.56x^5, & \text{if} \;\; x \ge 0.
+    0.48 + 1.27x + 3.59 x^{2} + 14.147 x^3 + 23.694 x^4 + 10.995 x^5
+    & \textif\ x < 0 \\
+    0.52 + 0.84x - 0.30 x^{2} + 2.397 x^3 - 0.901 x^4 + 3.56 x^5
+    & \otherwise
 \end{cases}
-\end{align*}
-
-For each DGP, we used four methods to obtain point estimate and confidence intervals.\footnote{Note that the true value of $\tau$ is $0.04$ for DGPs 1 and 3 and $-3.45$ for DGP 2} For each method, a total 1500 replications were performed.
+\end{equation*}
+and the population ATE is again $0.04$. CCT introduce this DGP because it has
+high curvature and local linear models are likely to exhibit high bias, making
+it a natural test case for both their analytical corrections and our bootstrap.
+
+For each DGP, we used four methods to obtain point estimate and confidence intervals.
+For each method, a total 1500 replications were performed.
 The first two methods follow CCT analytical bias-correction procedure with triangular ($CCT_{tri}$) and uniform ($CCT_{uni}$) kernel, respectively.

### 2016-02-29 main_paper.tex
Edit Monte Carlo section of the main paper
I rewrote a bit of the simulation section; the major change is taking out the
'naive bootstrap' approach, because it was hard to see that anyone would
want to use that approach in the first place.

@@
 alternative, with coverage slightly closer to nominal coverage and shorter
-length of the intervals in the specifications implemented.
+length of the intervals in the specifications implemented.\footnote{%
+  All of the simulations were carried out in the R programming language
+  \citep{R} and rely on the \textit{rdrobust} \citep{rdrobust}, \textit{foreach}
+  \citep{foreach}, \textit{doParallel} \citep{doparallel}, and \textit{doRNG}
+  \citep{dorng} packages.} %
 
@@
 
-For each DGP, we used four methods to obtain point estimate and confidence intervals.
-For each method, a total 1500 replications were performed.
-The first two methods follow CCT analytical bias-correction procedure with triangular ($CCT_{tri}$) and uniform ($CCT_{uni}$) kernel, respectively.
-The third and fourth methods follow the bootstrap procedure proposed in Section \ref{boot} with uniform kernel with ($bootstrap_{uni}$) and without ($bootstrap_{uni}^{naive}$) bias-correction, respectively.
-
-The ``naive'' bootstrap estimator, which bootstraps the confidence intervals for the usual RD estimator without any bias-correction serves as a baseline comparison, making clear the need of the corrections proposed, especially for DGPs with higher (potential) bias.
-
-In the bootstrap procedure, we used 500 bootstraps for bias correction, 999 bootstraps to calculate confidence interval.
-Table \ref{Tb: simulation 1} presents the main results in which a local-linear RD estimator ($p=1$) is employed with the bias-correction based on a local-quadratic approximation ($q=2$).
+To estimate the finite-sample coverage of our new bootstrap interval, we
+simulate 1500 samples from each of the three DGPs and calculate nominal 95\%
+two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
+cacluate the asymptotic distribution of the bias corrected estimator, and each
+of those replications uses an additional 500 replications ($B_1$) to estimate
+the bias. We use the $0.025$ and $0.975$ quantiles of the bootstrap distribution
+as the lower and upper bound of the interval, and the bandwidths, $h$ and $b$,
+are chosen using the AMSE-optimal rule proposed by CCT.
+
+We also show the coverage of two of CCT's interval estimators for comparison.
+We estimate their bias corrected procedure with AMSE-optimal bandwidths for both
+the uniform kernel and the triangular kernel. The uniform kernel provides a
+direct comparison with our bootstrap, while the triangular kernel may be more
+appealing to practitioners. Since CCT establish conclusively that the ``naive''
+uncorrected interval estimator has poor coverage in these settings we do not
+report results for that estimator.
 
@@
   \centering
-\begin{tabular}{rrrrrrrrr}
+  \begin{tabular}{rlrrrrrrr}
     \toprule
-	DGP & Method    & Bias    & SD    & MSE   & CI Coverage & CI Length \\
+    DGP & Method     & Bias   & SD    & RMSE   & CI Coverage (\%) & CI Length \\
     \midrule
-	1 & $CCT_{tri}$ & -0.010 & 0.068 & 0.068 & 0.911 & 0.241 \\ 
-	  & $CCT_{uni}$ & -0.016 & 0.067 & 0.069 & 0.924 & 0.246 \\ 
-	  & $bootstrap_{uni}$ & -0.018 & 0.066 & 0.069 & 0.931 & 0.240 \\ 
-	  & $bootstrap_{uni}^{naive}$ & -0.020 & 0.060 & 0.064 & 0.916 & 0.208 \\
-	\midrule
-	2 & $CCT_{tri}$ & -0.011 & 0.085 & 0.086 & 0.935 & 0.343 \\ 
-	  & $CCT_{uni}$ & -0.010 & 0.087 & 0.088 & 0.938 & 0.350 \\ 
-	  & $bootstrap_{uni}$       & -0.012 & 0.088 & 0.089 & 0.953 & 0.324 \\ 
-	  & $bootstrap_{uni}^{naive}$ & -0.051 & 0.086 & 0.100 & 0.869 & 0.300 \\ 
-	\midrule
-	3 & $CCT_{tri}$ & -0.008 & 0.067 & 0.067 & 0.919 & 0.246 \\ 
-	  & $CCT_{uni}$ & -0.004 & 0.065 & 0.065 & 0.943 & 0.250 \\ 
-	  & $bootstrap_{uni}$       & -0.004 & 0.064 & 0.064 & 0.960 & 0.246 \\ 
-	  & $bootstrap_{uni}^{naive}$ & 0.016 & 0.062 & 0.064 & 0.931 & 0.218 \\ 
+    1   & \bootuni   & --0.018 & 0.066 & 0.069 & 93.1       & 0.240     \\
+        & \cctuni    & --0.016 & 0.067 & 0.069 & 92.4       & 0.246     \\
+        & \ccttri    & --0.010 & 0.068 & 0.068 & 91.1       & 0.241     \\\\
+    2   & \bootuni   & --0.012 & 0.088 & 0.089 & 95.3       & 0.324     \\
+        & \cctuni    & --0.010 & 0.087 & 0.088 & 93.8       & 0.350     \\
+        & \ccttri    & --0.011 & 0.085 & 0.086 & 93.5       & 0.343     \\\\
+    3   & \bootuni   & --0.004 & 0.064 & 0.064 & 96.0       & 0.246     \\
+        & \cctuni    & --0.004 & 0.065 & 0.065 & 94.3       & 0.250     \\
+        & \ccttri    & --0.008 & 0.067 & 0.067 & 91.9       & 0.246     \\
     \bottomrule
   \end{tabular}
-\caption{Summary of estimates ($p = 1, q = 2$)}
-\label{Tb: simulation 1}
+  \caption{%
+    Experimental coverage probabilities for each interval estimator based on 1500
+    simulations; nominal coverage probabilities are 95\% for each estimator. The column
+    ``CI Coverage'' lists the coverage frequency in these simulations and ``CI Length''
+    lists the average length of the confidence interval across simulations.}
+  \label{tbl:1}
 \end{table}
 
-Table \ref{Tb: simulation 1} presents the results for the local linear model, with three panels reporting on each DGP described above.
-For each panel, we report bias, standard deviation, MSE, confidence interval empirical coverage and length for the four methods.
-For the three DGPs coverage for
-    both analytical and bootstrap based bias correction methods is near nominal size but with slight undercoverage for CCT's analytical correction.
-For DGP 1, our robust bootstrap method improves coverage slightly, obtaining 93.1\% coverage against 92.4\% from CCT's analytical correction using the uniform kernel.
-Also, the CI length is slightly shortened on average.
-Both robust approaches improve over the naive estimator, even in this case for which bias is relatively small.
-
-For the second DGP, based on \cite{ludwig2007}, the importance of correcting for the leading bias term presence becomes clear, with the naive bootstrap CI displaying an empirical coverage of only 86.9\%.
-Once again, the CIs based on both analytical and bootstrap robust methods improves the coverage meaningfully, with moderate gains in terms of coverage and length from $0.324$ to $0.350$ when using the bootstrap estimator relative to CCT's with uniform kernel.
-
-In the case of the modified \cite{lee2008rand} DGP that exacerbates the importance of bias, $\mu_{3}(x)$, once more the robust bootstrap procedure provides similar empirical coverage and interval length relative to its analytical alternatives.
-The naive method once again suffers in terms of coverage due to the presence of uncorrected first order bias.
-
- Overall, the bootstrap bias-correction procedure proposed in this paper provides a simple alternative to obtain valid robust confidence intervals in RD designs and performs well compared to the analytical
-bias correction procedures proposed by CCT. The results also corroborates CCT in the importance of bias correction when high curvature is present at the cutoff.
+Table~\ref{tbl:1} presents the results of these simulations. The first three
+columns give the bias, SD, and RMSE of the \emph{bias corrected} point
+estimators corresponding to each confidence interval.  As expected, these
+estimators are close to unbiased, with their standard deviation largely
+determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
+bootstrap and analytically-corrected estimators have essentially the same
+standard deviation across all of the DGPs.
+
+The column ``CI Coverage'' lists the experimental coverage of each interval.
+All of the intervals are reasonably close to their nominal coverage, although
+the analytically corrected estimator using the triangular kernel seems to
+persistently under-cover by a few percentage points. Our proposed bootstrap
+procedure consistently performs well, as it is about a percentage point closer
+to nominal coverage than the other interval estimators in DGPs 1 and 2, and is
+slightly conservative (96\% coverage) in DGP 3. The final column, ``CI Length,''
+indicates that all three of these procedures generate intervals that are
+approximately the same length on average.
+
+It is important not to read too much into these simulation results. Where there
+are differences between these procedures, they are small enough that randomness
+in the simulations is likely a factor in their precise rankings.\footnote{%
+  To help address this concern, we are currently running a more extensive set of
+  simulations and will update this paper when they are complete.} %
+These are DGPs where the naive confidence intervals are known to perform poorly,
+and this set of simulation results indicates that our proposed bootstrap approach
+is quite competetive with analytical methods for producing valid intervals.
+Overall, the bootstrap bias-correction procedure proposed in this paper provides
+a simple alternative to obtain valid robust confidence intervals in RD designs
+and performs well compared to the analytical bias correction procedures proposed
+by CCT.
 

### 2016-02-29 main_paper.tex
Remove trailing whitespace from main LaTeX file

@@
 estimate and embed the second order behavior in the bootstrap DGP through
-a residual bootstap.
+a residual bootstrap.
 Algorithm~\ref{Alg1} explains the bias-correction steps in detail.
@@
 
-The Monte Calro experiments have a similar structure. For all of them, we
+The Monte Carlo experiments have a similar structure. For all of them, we
 generate 500 i.i.d.\ observations from the DGP
@@
 races for the House of Representatives --- candidates who received the largest
-vote share in the previous election are the incumbants, which creates the
+vote share in the previous election are the incumbents, which creates the
 discontinuity. The conditional expectation is a fifth order polynomial fit to
@@
 The second DGP is based on Ludwig and Miller's (2007) analysis of the Head Start
-program. Funding eligability is determined at the county level using the
+program. Funding eligibility is determined at the county level using the
 county's historical poverty rate, with a sharp threshold that determines the
@@
 two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
-cacluate the asymptotic distribution of the bias corrected estimator, and each
+calculate the asymptotic distribution of the bias corrected estimator, and each
 of those replications uses an additional 500 replications ($B_1$) to estimate
@@
 and this set of simulation results indicates that our proposed bootstrap approach
-is quite competetive with analytical methods for producing valid intervals.
+is quite competitive with analytical methods for producing valid intervals.
 Overall, the bootstrap bias-correction procedure proposed in this paper provides

### 2016-02-29 main_paper.tex
Make minor edits to the abstract

@@
   use the uniform kernel. The procedure uses a residual bootstrap to estimate
-  the bias of the RD estimator, which is then removed from the original estimator.
- The bias-corrected estimator is then bootstrapped itself to
+  the bias of the RD estimator, which is then removed from the original
+  estimator.  The bias-corrected estimator is then bootstrapped itself to
   generate valid confidence intervals. This procedure is valid for empirically
-  relevant bandwidths when the residual bootstraps use a polynomial of higher
-  order than used to estimate the treatment effect and can be applied under the
-  same conditions as Calonico, Cattaneo and Titiunik's (2014,
+  relevant bandwidths when the treatment effect is estimated with a local linear
+  model and the residual bootstraps use a second order polynomial; validity
+  holds under similar conditions to Calonico, Cattaneo and Titiunik's (2014,
   \textit{Econometrica}) analytical correction.

### 2016-02-29 main_paper.tex
Make small edits to the paper's introduction

@@
 of policies and interventions in several fields of the social sciences,
-including economics, political science, public policy, and sociology, among
-others. This strategy exploits the fact that many programs use somewhat
+including economics, political science, public policy, and sociology.
+This research strategy exploits the fact that many programs use somewhat
 arbitrary thresholds to determine whether or not to provide a ``treatment,''
@@
 untreated.
-
 The identification of the treatment effect at the threshold is then based on
@@
   \cite{urquiola2009}, \cite{cellini2010}} %
-But the underlying identification strategy has proven to apply much more widely,
-and RD has been used in health economics\footnote{%
-  \cite{Card2009,barreca2011saving}}; %
+But the underlying identification strategy has proven to apply much more widely
+and RD has been used in health economics;\footnote{%
+  \cite{Card2009,barreca2011saving}} %
 political science, providing evidence regarding incumbency advantage in
@@
 
-In these studies, identification typically occurs exactly at the cutoff, so the
+In these studies, identification occurs exactly at the cutoff, so the
 treatment effect is typically estimated by fitting separate local linear models
-above and below the cutoff, then extrapolating the model to the exact point of
+above and below the cutoff, then extrapolating the models to the exact point of
 discontinuity. The difference between the estimated effects at that point is
@@
 
-But, as \cite{calonico2014}\footnote{%
+As \cite{calonico2014}\footnote{%
   We will refer to \cite{calonico2014} frequently, so we will reference it as
   ``CCT'' for the rest of the paper.} %
-point out, the \cite{IK} bandwidth estimator has the serious drawback that,
-although it is AMSE-optimal for point estimation, it produces invalid
-\emph{confidence intervals} and hypothesis tests. The AMSE-optimal bandwidth
+point out, however, the \cite{IK} bandwidth estimator has the serious drawback
+that, although it is AMSE-optimal for point estimation, it produces invalid
+confidence intervals and hypothesis tests. The AMSE-optimal bandwidth
 converges to zero slowly, so the remaining bias term is large enough to affect
@@
 confidence intervals for the RD treatment effects may be biased and have
-coverage well below their nominal level. CCT then make two contributions: first,
-they propose an estimator of the bias resulting from undersmoothing and provide
-a treatment effect estimator that remains asymptotically unbiased even when the
-bandwidth converges to zero slowly, at the AMSE-optimal rate.  Second, since
-this bias-correction term contributes to the asymptotic variance of the
-resulting treatment effect estimator, CCT also provide a new formula for its
-asymptotic variance. The resulting confidence intervals have accurate coverage
-even when the naive RD interval does not.
+coverage well below their nominal level.
+CCT propose an estimator of the bias resulting from undersmoothing and provide a
+treatment effect estimator that remains asymptotically unbiased even when the
+bandwidth converges to zero slowly, at the AMSE-optimal rate. They also show
+that this bias-correction term contributes to the asymptotic variance of the
+resulting treatment effect estimator and provide a new formula for the
+asymptotic variance of the bias-corrected estimator. The resulting confidence
+intervals have accurate coverage even when the naive RD interval does not.
 
@@
 Our approach exploits CCT's theoretical insight through a new residual
-bootstrap. In particular, we propose, after estimating the local linear model as
-usual, estimating a local second order polynomial and generating bootstrap
+bootstrap. In particular, we propose estimating the local linear model as usual,
+then estimating a local second order polynomial and generating bootstrap
 datasets by resampling the residuals of that polynomial. Since the second order
-polynomial is the true Data Generating Process (DGP) in the bootstrapped data, its estimate of the
-treatment effect is the true value of the treatment effect under the
-distribution induced by this bootstrap. The bias of the linear model is known
+polynomial is the true Data Generating Process (DGP) for the bootstrapped data,
+its estimate of the treatment effect is the true value of the treatment effect
+under the distribution induced by this bootstrap. The bias of the linear model
+is therefore known
 under this distribution and can be calculated by averaging the error of the
@@
 
-Just as in CCT, this bias correction introduces additional variability. However,
-the second order polynomial again adequately estimates the features of the true
-DGP that are necessary for estimating that additional variability. So we propose
+Just as in CCT, our bias correction step introduces additional
+variability. However, the second order polynomial again adequately estimates the
+features of the true DGP that are necessary for estimating and accomodating that
+additional variability. So we propose
 an iterated bootstrap procedure \citep{hall1988}: use the second order
@@
 
-This bootstrap procedure can offer some advantages over analytical methods in
-this setting. In particular, both this paper and CCT assume that the
-observations are generated independently of each other; extending these bias
-correction methods to other forms of dependence is relatively straightforward
-for the bootstrap but can be substantially more complicated for analytical
+This bootstrap procedure offers some advantages over analytical methods.  In
+particular, both this paper and CCT assume that the observations are generated
+independently of each other; however, extending these bias correction methods to
+other forms of dependence is relatively straightforward for the bootstrap but
+can be substantially more complicated for analytical
 corrections, which have to be explicitly derived by the researcher. Similarly,

### 2016-02-29 main_paper.tex
Make small changes to 'background' section of the paper

@@
 smoothness conditions on the joint distribution of $X_i$, $Y_i(0)$, and $Y_i(1)$
-around the cutoff $X_i = 0$. When these conditions hold, which are made precise
-in Assumption~\ref{A1}, $\tau$ is equal to
+around the cutoff $X_i = 0$. Under these conditions, which are made precise
+in our Assumption~\ref{A1}, $\tau$ is equal to
 \begin{equation*}
@@
 nonparametrically identified because both $\mu_-$ and $\mu_+$ can be estimated
-consistently under the conditions spelled out in Assumption~\ref{A1}.
+consistently under Assumption~\ref{A1}, which lists standard conditions in the
+RD literature. (See, in particular, \citealp{HTV2001}, \citealp{Porter03}, and
+CCT.)
 
@@
 
-These conditions are standard in the RD literature. (See, in particular,
-\citealp{HTV2001}, \citealp{Porter03}, and CCT). The third part of the
-assumption is especially important for the characterization of the leading bias
-term drives CCT's bias correction and our bootstrap procedure.
-
 Since the conditions for identification only need to hold in a neighborhood
@@
   higher order polynomials discontinuities in the derivatives of the conditional
-  expectation, like ``Kink RD'' design \citep{card2009b}. We focus on the linear
-  case for ease in exposition.} %
+  expectation, like ``Kink RD'' design \citep{card2009b}.} %
 For this model, if $h$ represents a bandwidth parameter, the estimator of
-$\tau$, $\hat\tau(h)$, is
+$\tau$, $\hat\tau(h)$, is defined as
 \begin{equation*}
@@
   \label{eq:1}
-  T(h) =\frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
+  \frac{\hat{\tau}(h)-\tau}{\sqrt{V(h)}} \to^d N(0,1),
   \intertext{with}
@@
 probability to zero quickly enough and it contributes non-negligibly to the
-asymptotic distribution~\eqref{eq:1}. This result holds even though
+asymptotic distribution in~\eqref{eq:1}. This result holds even though
 $\hat\tau(h)$ can be consistent under those conditions.  These bandwidth issues
@@
 procedures, most notably the AMSE-optimal bandwidth and cross-validation
-bandwidth \citep{IK} do not satisfy this condition.
+bandwidth \citep{IK} do not produce $o_{p}(n^{-1/5})$ bandwidths.
 
@@
 \begin{equation*}
-  \E(\hat{\tau}(h) \mid \chi_{n}) - \tau =
+  \E(\hat{\tau}(h) \mid X_1,\dots,X_n) - \tau =
   h^{2}\Big[ \tfrac{\mu_{+}^{(2)}}{2}\Bf_{+}(h)
@@
 these terms are given in the Mathematical Appendix as Equations~\eqref{eq:5}
-and~\eqref{eq:6}. The plug-in bias-corrected estimator then requires estimates
+and~\eqref{eq:6}.\footnote{%
+  One subtle but important feature of $\Bf_{-}$ and $\Bf_{+}$ is that they only
+  depend on the running variables, not the outcomes $Y_1,\dots,Y_n$.} %
+The plug-in bias-corrected estimator then requires estimates
 for the second derivatives of the conditional mean from above and below the
@@
 \begin{equation*}
-  T'(h, b) = \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}}
-  \to^d N(0,1)
+  \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}} \to^d N(0,1)
 \end{equation*}
@@
 and CCT provide simulation evidence that their intervals perform well in finite
-samples.
+samples even when the naive interval performs badly.
 

### 2016-02-29 main_paper.tex
Make several small changes to theoretical treatment

@@
 necessary for constructing valid confidence intervals. Our proposed algorithms
-estimate and embed the second order behavior in the bootstrap DGP through
-a residual bootstrap.
+estimate and embed the second order behavior in the bootstrap DGP through a
+residual bootstrap. Throughout this section and the rest of the paper, we will
+let $\E^{*}$, $\Pr^{*}$, etc. denote expectations and probabilities taken with
+respect to the distribution induced by the bootstrap (which implicitly
+conditions on $X_1,\dots,X_n$ and $Y_1,\dots,Y_n$) and let parameters with
+$^{*}$ superscripts be the parameter values under the distribution induced by
+the bootstrap. Two $*$ superscripts indicate that the parameter or probability
+measure corresponds to a secondary bootstrap distribution.
+
 Algorithm~\ref{Alg1} explains the bias-correction steps in detail.
@@
     \end{equation}
-  \item Repeat the following steps $B_1$ times to produce a sequence of
+  \item Repeat the following steps $B_1$ times to produce the
     bootstrap estimates $\hat\tau_1^*(h),\dots,\hat\tau_{B_1}^*(h)$. For the
-    $k$th estimate:
+    $k$th value:
     \begin{enumerate}
@@
     \begin{equation*}
-      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k -
+      \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k(h) -
       \big[\hat g_+(0) - \hat g_-(0)\big].
@@
     and~\eqref{eq:3}.
-  \item Repeat the following steps $B_{2}$ times to produce a sequence of
+  \item Repeat the following steps $B_{2}$ times to produce the
     bootstrap estimates
     $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
-    $k$th step:
+    $k$th value:
     \begin{enumerate}
@@
 $r_p(x) = (1,\ x,\dots,\ x^p)'$,
+\begin{equation*}
+  (\hat{\mu}_{+}(h),\ \hat{\mu}_{+}^{(1)}(h),\ \hat\mu_{+}^{(2)}(h))' =
+  \argmin_{\mu_0, \mu_1, \mu_2} \ssum[+]{i}{h} (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2),
+\end{equation*}
+\begin{equation*}
+(\hat{\mu}_{-}(h),\ \hat{\mu}_{-}^{(1)}(h),\ \hat\mu_{-}^{(2)}(h))' =
+  \argmin_{\mu_0, \mu_1, \mu_2} \ssum[-]{i}{h} (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2) \\
+\end{equation*}
 \begin{align}
@@
 almost surely, implying that
-\begin{equation*}
+\begin{equation}
+  \label{eq:7}
   \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
   - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
-\end{equation*}
+\end{equation}
 Combining this result with CCT's Lemma A1, gives
@@
    - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
-  \label{eq:7}
+  \label{eq:8}
   &= \hat\tau(h) - \E\hat\tau(h)
@@
 \subsection{Proof of Theorem~\ref{T2}}
-Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:7} to get
+Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:8} to get
 \begin{align*}
@@
 (\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
-$\Omega_+(h,b)$ is an $M_b^{+}$-dimensional vector with $i$th element
+$\Omega_+(h,b)$ is an $M_+(b)$-dimensional vector with $i$th element
 $\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
@@
   (1\quad 0)
-  \Big(\ssum{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
+  \Big(\ssum[+]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
     r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
 \intertext{and}
-  \Omega_{2i}^{+}(h,b) &= (0\quad 0 \quad h^2)
-  \Big(\ssum{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
+  \Omega_{+,2i}(h,b) &= (0\quad 0 \quad h^2)
+  \Big(\ssum[+]{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
     r_2(X_{m_+(b,i)} / b).
@@
 
-Given~\eqref{eq:7}, it suffices to prove that
+Given~\eqref{eq:8}, it suffices to prove that
 \begin{gather}
-  \label{eq:8}
-  \rho(V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}^{*},
+  \label{eq:9}
+  \rho(V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}^{*},\
     V^{-1/2}(h,b)\Omega_+(h,b)'\epb_{+}) \to^p 0
   \intertext{and}
-  \label{eq:9}
-  \rho(V^{-1/2}(h,b)\Omega^{-}(b)'\epb_{-}^{*},
-    V^{-1/2}(h,b)\Omega^{-}(b)'\epb_{-}) \to^p 0
+  \label{eq:10}
+  \rho(V^{-1/2}(h,b)\Omega_-(b)'\epb_{-}^{*},\
+    V^{-1/2}(h,b)\Omega_-(b)'\epb_{-}) \to^p 0
 \end{gather}
@@
 
-We will only prove~\eqref{eq:8} since the proof of~\eqref{eq:9} is
+We will only prove~\eqref{eq:9} since the proof of~\eqref{eq:10} is
 identical. By Theorem 2.1 of \cite{freedman1981}, we have
@@
 \[
-  (1/M_{b}^+) \osum[+]{i}{b}
+  (1/M_+(b)) \osum[+]{i}{b}
   \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0

### 2016-02-29 main_paper.tex
Typo
Minor typos and additions.

@@
 usually relying on some type of score, which this literature calls a ``running
-variable.'' In its basic version, individuals or groups with score above a
+variable.'' In its basic version, the sharp RD,  individuals or groups with score above a
 certain threshold receive treatment while the ones below that cutoff are left
@@
 This section presents our theoretical contributions. We propose two algorithms
-in this section. The first uses a residual bootstrap based on based on a second
+in this section. The first uses a residual bootstrap based on a second
 order local polynomial to estimate the bias of the local linear model. That
@@
   \Omega_{+,2i}(h,b) &= (0\quad 0 \quad h^2)
-  \Big(\ssum[+]{i}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
+  \Big(\ssum[+]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
     r_2(X_{m_+(b,i)} / b).

### 2016-02-29 main_paper.tex
Changes to Introduction

@@
 The identification of the treatment effect at the threshold is then based on
-comparing treated and untreated units at the cutoff. Since the observed
-characteristics of these subjects are very similar, similarity of their
-unobserved characteristics is often credible as well, and differences in the
-outcomes between the treated and untreated can be plausibly attributed to the
+comparing treated and untreated units at the cutoff. Since being just above
+or below the arbitrary cutoff is credibly not related to other factors impacting
+outcomes, including their unobserved characteristics,  differences between 
+treated and untreated individuals at the cutoff can be plausibly attributed to the
 treatment alone. As a practical matter this involves comparing units within a
@@
 above and below the cutoff, then extrapolating the models to the exact point of
-discontinuity. The difference between the estimated effects at that point is
-taken to be an estimate of the treatment effect. As a practical matter, the key
+discontinuity. The difference between the estimated outcomes at that point is
+taken to be an estimate of the treatment effect. As a practical matter, a key
 econometric issue is determining the bandwidth for the local linear models.  One
@@
 extended by \cite{calonico2014}, which minimizes the Asymptotic Mean Squared
-Error of difference in the models' point estimators at the cutoff.
+Error (AMSE) of difference in the models' point estimators at the cutoff.
 

### 2016-02-29 main_paper.tex
Minor word change in the introduction
There are settings where positions above or below the cutoff are related
to the other factors affecting outcomes. We want to make sure that we're
not claiming RD always works, only that it works when that assumption
is plausible.

@@
 The identification of the treatment effect at the threshold is then based on
-comparing treated and untreated units at the cutoff. Since being just above
-or below the arbitrary cutoff is credibly not related to other factors impacting
-outcomes, including their unobserved characteristics,  differences between 
-treated and untreated individuals at the cutoff can be plausibly attributed to the
-treatment alone. As a practical matter this involves comparing units within a
-bandwidth just above and just below the threshold.
+comparing treated and untreated units at the cutoff. When a subject's
+position just above or below the cutoff is credibly not related to
+other factors impacting outcomes, including their unobserved
+characteristics, differences between treated and untreated individuals
+at the cutoff can be plausibly attributed to the treatment alone. As a
+practical matter this involves comparing units within a bandwidth just
+above and just below the threshold.
 

### 2016-02-29 main_paper.tex
Typo

@@
 variability. However, the second order polynomial again adequately estimates the
-features of the true DGP that are necessary for estimating and accomodating that
+features of the true DGP that are necessary for estimating and accommodating that
 additional variability. So we propose

### 2016-02-29 main_paper.tex
Relabel 'our bootstrap' in simulations
Otavio has been criticized in the past for using overly grand naming schemes
for new estimators. So he didn't like 'our bootstrap' as a row heading in
our simulation results. I've changed it to 'resid bootstrap' instead.
Remove Footnote 8.

@@
 these terms are given in the Mathematical Appendix as Equations~\eqref{eq:5}
-and~\eqref{eq:6}.\footnote{%
-  One subtle but important feature of $\Bf_{-}$ and $\Bf_{+}$ is that they only
-  depend on the running variables, not the outcomes $Y_1,\dots,Y_n$.} %
-The plug-in bias-corrected estimator then requires estimates
+and~\eqref{eq:6}. The plug-in bias-corrected estimator then requires estimates
 for the second derivatives of the conditional mean from above and below the
@@
 
-Table~\ref{tbl:1} presents the results of these simulations. The first three
-columns give the bias, SD, and RMSE of the \emph{bias corrected} point
+Table~\ref{tbl:1} presents the results of these simulations. The rows labeled
+``\bootuni'' show results for our proposed bootstrap interval; ``\cctuni'' and
+``\ccttri'' show results for the analytically-corrected intervals. The first
+three columns give the bias, SD, and RMSE of the \emph{bias corrected} point
 estimators corresponding to each confidence interval.  As expected, these

### 2016-02-29 main_paper.tex
Typo
Typos et al.

@@
 invalidating standard (naive) critical values. Consequently, the second
-algorithm we propose uses an iterated bootstrap to estimate the correct
+algorithm we propose an iterated bootstrap to estimate the correct
 critical values of the bias corrected estimator.
 
-The intuition behind both procedures is very straightforward. CCT show that a
-local second order polynomial captures all of the unmodeled aspects of the DGP
+The intuition behind both procedures is straightforward. CCT show that a
+local second order polynomial captures the aspects of the DGP
 necessary for constructing valid confidence intervals. Our proposed algorithms
@@
 respect to the distribution induced by the bootstrap (which implicitly
-conditions on $X_1,\dots,X_n$ and $Y_1,\dots,Y_n$) and let parameters with
+conditions on $X_{1},\dots,X_{n}$ and $Y_{1},\dots,Y_{n}$) and let parameters with
 $^{*}$ superscripts be the parameter values under the distribution induced by
@@
   \begin{align*}
-    I_-(h) &= \{i : -h < X_{i} < 0\}, &
-    I_+(h) &= \{i : 0 \leq X_{i} < h\}.
-  \end{align*}
-  Also define $M_-(h)$ and $M_+(h)$ to be the number of elements in $I_-(h)$ and
-  $I_+(h)$ respectively and $m_-(h,1),\dots,m_-(h,M_-(h))$ and
-  $m_+(h,1),\dots,m_+(h,M_+(h))$ to be subsequences of $1,\dots,n$ that index
-  $I_-(h)$ and $I_+(h)$ respectively.
+    I_{-}(h) &= \{i : -h < X_{i} < 0\}, &
+    I_{+}(h) &= \{i : 0 \leq X_{i} < h\}.
+  \end{align*}
+  Also define $M_{-}(h)$ and $M_{+}(h)$ to be the number of elements in $I_{-}(h)$ and
+  $I_{+}(h)$ respectively, and $m_{-}(h,1),\dots,m_{-}(h,M_{-}(h))$ and
+  $m_{+}(h,1),\dots,m_{+}(h,M_+(h))$ to be subsequences of $1,\dots,n$ that index
+  $I_{-}(h)$ and $I_{+}(h)$, respectively.
   \begin{enumerate}
-  \item Estimate local second order polynomials $\hat g_-$ and $\hat g_+$ using
-    the observations in $I_-(b)$ and $I_+(b)$:
+  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$ using
+    the observations in $I_{-}(b)$ and $I_{+}(b)$:
     \begin{align}
       \label{eq:2}
-      \hat g_-(x)
-      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^2,
-      &\hat g_+(x)
-      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^2
+      \hat g_{-}(x)
+      &= \hat\beta_{-,0} + \hat\beta_{-,1} x + \hat\beta_{-,2} x^{2},
+      &\hat g_{+}(x)
+      &= \hat\beta_{+,0} + \hat\beta_{+,1} x + \hat\beta_{+,2} x^{2}
     \end{align}
@@
     \begin{align*}
-      \hat\beta_- &= \argmin_\beta \sum_{i \in I_-(b)}
+      \hat\beta_{-} &= \argmin_\beta \sum_{i \in I_-(b)}
       (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2 \\
-      \hat\beta_+ &= \argmin_\beta \sum_{i \in I_+(b)}
+      \hat\beta_{+} &= \argmin_\beta \sum_{i \in I_+(b)}
       (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2.
@@
     \end{equation}
-  \item Repeat the following steps $B_1$ times to produce the
-    bootstrap estimates $\hat\tau_1^*(h),\dots,\hat\tau_{B_1}^*(h)$. For the
+  \item Repeat the following steps $B_{1}$ times to produce the
+    bootstrap estimates $\hat{\tau}_{1}^{*}(h),\dots,\hat\tau_{B_{1}}^{*}(h)$. For the
     $k$th value:

### 2016-02-29 main_paper.tex
Minore changes to section 3.

@@
 estimator has the same asymptotic distribution as CCT's. This equivalence should
-be unsurprising; both estimators use a 2nd order polynomial to directly estimate
+be unsurprising; both estimators use a second order polynomial to directly estimate
 the bias of the local linear model, so they should behave very similarly.
@@
 with a bootstrap. We propose bootstrapping $\hat\tau(h) - \Delta^*(h,b)$ using
-the same residual bootstrap method that was used in
+the same residual bootstrap method used in
 Algorithm~\ref{Alg1}. Algorithm~\ref{Alg2} provides the details of our procedure
@@
         Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
-        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_-(h,i)}) + \varepsilon_{+,i}^{*}.
+        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_{+}(h,i)}) + \varepsilon_{+,i}^{*}.
       \end{align*}

### 2016-02-29 main_paper.tex
Small Changes for Section 4.

@@
 where $j$ will index the specific DGP. This is the experimental design used by
-\citet{IK} CCT, which we adopt here to make our simulation results directly
-comparable with theirs and more comparable with the rest of the literature. We
-will use the same three functional forms for $\mu_j$ as CCT as well.
+\citet{IK} and CCT, which we adopt here to make our simulation results directly
+comparable with theirs and the rest of the literature. We
+will use the same three functional forms for $\mu_{j}$ as CCT as well.
 
@@
 
-To estimate the finite-sample coverage of our new bootstrap interval, we
+To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
 simulate 1500 samples from each of the three DGPs and calculate nominal 95\%
@@
 ``\ccttri'' show results for the analytically-corrected intervals. The first
-three columns give the bias, SD, and RMSE of the \emph{bias corrected} point
+three columns give the bias, standard deviation, and Root-MSE of the \emph{bias corrected} point
 estimators corresponding to each confidence interval.  As expected, these

### 2016-03-01 main_paper.tex
Conclusion, first take. Please check how you feel about it.

@@
 \section{Conclusion}\label{conclusion}
-This paper proposes a novel bootstrap procedure to obtain robust bias-corrected
-confidence intervals in regression discontinuity designs.
+This paper proposes a novel bootstrap procedure to obtain robust bias-corrected confidence intervals in regression discontinuity designs.
 The approach proposed builds upon the developments and intuition advanced by CCT and is based on a first-order bias correction.
-Our procedure provides an alternative to the plug-in analytical methods in the literature and is simple to implement generating robust confidence intervals.
-Simulation evidence is presented that the proposed bootstrap bias correction and confidence intervals have improved coverage and shorter length relative to the analytical alternatives proposed by CCT.
+ We exploit CCT's theoretical insight through a new residual bootstrap. In particular, we propose estimating the local linear model as usual,
+then estimating a local second order polynomial and generating bootstrap datasets by resampling the residuals of that polynomial.
+
+The bootstrap sample is used to estimate the bias of the RD estimator, which is then removed from the original estimator.
+ This approach is described in detail by our Algorithm~\ref{Alg1} and the resulting bias corrected estimator is shown to be asymptotically normal with mean zero in our
+Theorem~\ref{T1} under AMSE-optimal bandwidth rates.
+
+Just as in CCT, our bias correction step introduces additional variability.  So we propose then bootstrap the bias-corrected estimator itself to
+ generate valid confidence intervals. This procedure, which requires bootstrapping the datasets produced by an initial bootstrap procedure, is described in Algorithm~\ref{Alg2},
+ and the resulting confidence intervals are shown to be asymptotically valid in Theorem~\ref{T2}.
+
+ Hence, our procedure provides an alternative to the plug-in analytical methods in the literature and is simple to implement generating robust confidence intervals.
+
+Simulation evidence is presented that the proposed bootstrap bias correction and confidence intervals have similar empirical coverage and average interval length relative to
+ the analytical alternatives proposed by CCT, making it a suitable option to practitioners.
 

### 2016-03-01 main_paper.tex
Commenting out Application Section. We will need to keep on working on this for future versions.

@@
 and its relative performance to the analytical bias correction are presented in
-Section~\ref{sim}, and Section~\ref{application} demonstrates the estimator's
-usage by applying it to the Head Start dataset used by~\cite{ludwig2007}.
+Section~\ref{sim}.
+% and Section~\ref{application} demonstrates the estimator's usage by applying it to the Head Start dataset used by~\cite{ludwig2007}.
 Finally, Section~\ref{conclusion} concludes.
@@
 
-\section{Application}\label{application}
-
-In this section, we apply the bootstrap procedure to the data\footnote{The data is publicly available from http://faculty.econ.ucdavis.edu/faculty/dlmiller/statafiles/.} used in \cite{ludwig2007}.
+%\section{Application}\label{application}
+%
+%In this section, we apply the bootstrap procedure to the data\footnote{The data is publicly available from http://faculty.econ.ucdavis.edu/faculty/dlmiller/statafiles/.} used in \cite{ludwig2007}.
 In their paper, the effects of Head Start application assistance on federal spending, mortality and education attainment were investigated under standard RD design.
 They utilized the fact that grant-writing assistance were offered only to the poorest 300 counties to identify the average treatment effect (ATE) at the cutoff.
-
-We estimate the ATE with alternative procedures and compare the new estimates with results in \cite{ludwig2007}.
+%
+%We estimate the ATE with alternative procedures and compare the new estimates with results in \cite{ludwig2007}.
 Bias-corrected point estimates and robust confidence intervals are reported.
@@
 In the bootstrap procedure, we used 500 bootstraps for bias correction and 999 for confidence interval.
-
-These results are shown in Table \ref{tab: head start spending}-\ref{tab: education 2000 ages 25-34}.
+%
+%These results are shown in Table \ref{tab: head start spending}-\ref{tab: education 2000 ages 25-34}.
 We find that (1) the choice of bandwidth may significantly affect estimated ATE and its significance level; (2) the optimal bandwidths following CCT procedure are much smaller than actually being used in \cite{ludwig2007} and (3) our bootstrap procedure produces similar results to CCT.
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{cccccc}
-		\toprule
-		& \multicolumn{3}{c}{LM 2007} & CCT 2014 & Bootstrap \\
-		\midrule
-		& \multicolumn{5}{c}{Panel A: 1968 Head Start spending per child} \\
-		Bandwidth & 9 & 18 & 36 & 5.414, 10.175 & 5.414, 10.175 \\
-		Effect    & 137.251 & 114.711 & 134.491 & 143.811 & 148.990 \\
-		SE        & 128.968 & 91.267  & 62.593 & 113.404 & 182.729 \\
-		p-value   & 0.157   & 0.138   & 0.045  & & \\
-		95\% CI   & & & & (-78.457 366.078) & (-179.120  547.755) \\
-
-		&&&&& \\
-		& \multicolumn{5}{c}{Panel B: 1972 Head Start spending per child} \\
-		Bandwidth & 9 & 18 & 36 & 5.034, 12.020 & 5.034, 12.020 \\
-		Effect    & 182.119 & 88.959 & 130.153 & 94.260 & 100.404 \\
-		SE        & 148.321 & 101.697 & 67.613 & 122.224 & 196.008 \\
-		p-value   & 0.085   & 0.352   & 0.090  & & \\
-		95\% CI   & & & & (-145.294 333.814) & (-165.816 622.976) \\
-
-		&&&&& \\
-		& \multicolumn{5}{c}{Panel C: 1972 other social spending per capita} \\
-		Bandwidth & 9 & 18 & 36 & 4.612, 8.461 & 4.612, 8.461 \\
-		Effect    & 14.474 & 19.590 & 14.506 & 15.418 & 15.857 \\
-		SE        & 28.356 & 19.612 & 14.929 & 29.041 & 39.902 \\
-		p-value   & 0.459   & 0.222   & 0.478  & & \\
-		95\% CI   & & & & (-41.501 72.337) & (-64.153 91.999) \\
-		\bottomrule
-	\end{tabular}
-	\caption{The effect of Head Start assistance on Head Start spending. The first three columns come from Table 2 in \cite{ludwig2007}.}
-	\label{tab: head start spending}
-\end{table}
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{cccccc}
-		\toprule
-		& \multicolumn{3}{c}{LM 2007} & CCT 2014 & Bootstrap \\
-		\midrule
-		Bandwidth & 9 & 18 & 36 & 3.888, 6.807 & 3.888, 6.807 \\
-		Effect    & -1.895 & -1.198 & -1.114 & -3.795 & -3.852 \\
-		SE        & 0.980 & 0.796  & 0.544 & 1.654 & 1.526 \\
-		p-value   & 0.036   & 0.081   & 0.027  & & \\
-		95\% CI   & & & & (-7.037 -0.554) & (-6.565 -0.578) \\
-		\bottomrule
-	\end{tabular}
-	\caption{The effect of Head Start assistance on mortality. The first three columns come from Table 3 in \cite{ludwig2007}.}
-	\label{tab: mortality}
-\end{table}
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{cccc}
-		\toprule
-		& LM 2007 & CCT 2014 & Bootstrap \\
-		\midrule
-		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\
-		Bandwidth & 7 & 3.671, 8.618 & 3.671, 8.618 \\
-		Effect    & 0.030 & 0.055 & 0.054 \\
-		SE        & 0.016 & 0.021 & 0.021 \\
-		p-value   & 0.032 & & \\
-		95\% CI        & & (0.014 0.096) & (0.010 0.094) \\
-
-		&&& \\
-		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
-		Bandwidth & 7 & 5.076, 10.251 & 5.076, 10.251 \\
-		Effect    & 0.037 & 0.051 & 0.051 \\
-		SE        & 0.020 & 0.024 & 0.024 \\
-		p-value   & 0.031 & & \\
-		95\% CI        & & (0.004 0.099) & (0.001 0.092) \\
-		\bottomrule
-	\end{tabular}
-	\caption{The effect of Head Start assistance on education (1990, ages 18-24). The first column is result for directly treated cohorts (1990, ages 18-24) in Table 4 in \cite{ludwig2007}.}
-	\label{tab: education 1990 ages 18-24}
-\end{table}
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{cccc}
-		\toprule
-		& LM 2007 & CCT 2014 & Bootstrap \\
-		\midrule
-		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\
-		Bandwidth & 7 & 4.837, 9.85 & 4.837, 9.85 \\
-		Effect    & 0.000 & 0.014 & 0.013 \\
-		SE        & 0.016 & 0.019 & 0.019 \\
-		p-value   & 0.974 & & \\
-		CI        & & (-0.024 0.051) & (-0.026 0.051) \\
-
-		&&& \\
-		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
-		Bandwidth & 7 & 5.382, 10.621 & 5.382, 10.621 \\
-		Effect    & 0.028 & 0.033 & 0.032 \\
-		SE        & 0.019 & 0.023 & 0.022 \\
-		p-value   & 0.017 & & \\
-		CI        & & (-0.014 0.079) & (-0.009 0.077)\\
-		\bottomrule
-	\end{tabular}
-	\caption{The effect of Head Start assistance on education (2000, ages 18-24). The first column is result for directly treated cohorts (2000, ages 18-24) in Table 4 in \cite{ludwig2007}.}
-	\label{tab: education 2000 ages 18-24}
-\end{table}
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{cccc}
-		\toprule
-		& LM 2007 & CCT 2014 & Bootstrap \\
-		\midrule
-		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\
-		Bandwidth & 7 & 6.074, 11.477 & 6.074, 11.477 \\
-		Effect    & 0.006 & 0.014 & 0.014 \\
-		SE        & 0.014 & 0.015 & 0.015 \\
-		p-value   & 0.666 & & \\
-		CI        & & (-0.014 0.043) & (-0.023 0.036) \\
-
-		&&& \\
-		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
-		Bandwidth & 7 & 5.509, 11.463 & 5.509, 11.463 \\
-		Effect    & 0.040 & 0.049 & 0.049 \\
-		SE        & 0.017 & 0.020 & 0.021 \\
-		p-value   & 0.009 & & \\
-		CI        & & (0.010 0.089) & (0.003 0.083) \\
-		\bottomrule
-	\end{tabular}
-	\caption{The effect of Head Start assistance on education (2000, ages 25-34). The first column is result for directly treated cohorts (2000, ages 25-34) in Table 4 in \cite{ludwig2007}.}
-	\label{tab: education 2000 ages 25-34}
-\end{table}
-
+%
+%\begin{table}[ht]
+%	\centering
+%	\begin{tabular}{cccccc}
+%		\toprule
+%		& \multicolumn{3}{c}{LM 2007} & CCT 2014 & Bootstrap \\
+%		\midrule
+%		& \multicolumn{5}{c}{Panel A: 1968 Head Start spending per child} \\
+%		Bandwidth & 9 & 18 & 36 & 5.414, 10.175 & 5.414, 10.175 \\
+%		Effect    & 137.251 & 114.711 & 134.491 & 143.811 & 148.990 \\
+%		SE        & 128.968 & 91.267  & 62.593 & 113.404 & 182.729 \\
+%		p-value   & 0.157   & 0.138   & 0.045  & & \\
+%		95\% CI   & & & & (-78.457 366.078) & (-179.120  547.755) \\
+%
+%		&&&&& \\
+%		& \multicolumn{5}{c}{Panel B: 1972 Head Start spending per child} \\
+%		Bandwidth & 9 & 18 & 36 & 5.034, 12.020 & 5.034, 12.020 \\
+%		Effect    & 182.119 & 88.959 & 130.153 & 94.260 & 100.404 \\
+%		SE        & 148.321 & 101.697 & 67.613 & 122.224 & 196.008 \\
+%		p-value   & 0.085   & 0.352   & 0.090  & & \\
+%		95\% CI   & & & & (-145.294 333.814) & (-165.816 622.976) \\
+%
+%		&&&&& \\
+%		& \multicolumn{5}{c}{Panel C: 1972 other social spending per capita} \\
+%		Bandwidth & 9 & 18 & 36 & 4.612, 8.461 & 4.612, 8.461 \\
+%		Effect    & 14.474 & 19.590 & 14.506 & 15.418 & 15.857 \\
+%		SE        & 28.356 & 19.612 & 14.929 & 29.041 & 39.902 \\
+%		p-value   & 0.459   & 0.222   & 0.478  & & \\
+%		95\% CI   & & & & (-41.501 72.337) & (-64.153 91.999) \\
+%		\bottomrule
+%	\end{tabular}
+%	\caption{The effect of Head Start assistance on Head Start spending. The first three columns come from Table 2 in \cite{ludwig2007}.}
+%	\label{tab: head start spending}
+%\end{table}
+%
+%\begin{table}[ht]
+%	\centering
+%	\begin{tabular}{cccccc}
+%		\toprule
+%		& \multicolumn{3}{c}{LM 2007} & CCT 2014 & Bootstrap \\
+%		\midrule
+%		Bandwidth & 9 & 18 & 36 & 3.888, 6.807 & 3.888, 6.807 \\
+%		Effect    & -1.895 & -1.198 & -1.114 & -3.795 & -3.852 \\
+%		SE        & 0.980 & 0.796  & 0.544 & 1.654 & 1.526 \\
+%		p-value   & 0.036   & 0.081   & 0.027  & & \\
+%		95\% CI   & & & & (-7.037 -0.554) & (-6.565 -0.578) \\
+%		\bottomrule
+%	\end{tabular}
+%	\caption{The effect of Head Start assistance on mortality. The first three columns come from Table 3 in \cite{ludwig2007}.}
+%	\label{tab: mortality}
+%\end{table}
+%
+%
+%\begin{table}[ht]
+%	\centering
+%	\begin{tabular}{cccc}
+%		\toprule
+%		& LM 2007 & CCT 2014 & Bootstrap \\
+%		\midrule
+%		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\
+%		Bandwidth & 7 & 3.671, 8.618 & 3.671, 8.618 \\
+%		Effect    & 0.030 & 0.055 & 0.054 \\
+%		SE        & 0.016 & 0.021 & 0.021 \\
+%		p-value   & 0.032 & & \\
+%		95\% CI        & & (0.014 0.096) & (0.010 0.094) \\
+%
+%		&&& \\
+%		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
+%		Bandwidth & 7 & 5.076, 10.251 & 5.076, 10.251 \\
+%		Effect    & 0.037 & 0.051 & 0.051 \\
+%		SE        & 0.020 & 0.024 & 0.024 \\
+%		p-value   & 0.031 & & \\
+%		95\% CI        & & (0.004 0.099) & (0.001 0.092) \\
+%		\bottomrule
+%	\end{tabular}
+%	\caption{The effect of Head Start assistance on education (1990, ages 18-24). The first column is result for directly treated cohorts (1990, ages 18-24) in Table 4 in \cite{ludwig2007}.}
+%	\label{tab: education 1990 ages 18-24}
+%\end{table}
+%
+%\begin{table}[ht]
+%	\centering
+%	\begin{tabular}{cccc}
+%		\toprule
+%		& LM 2007 & CCT 2014 & Bootstrap \\
+%		\midrule
+%		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\
+%		Bandwidth & 7 & 4.837, 9.85 & 4.837, 9.85 \\
+%		Effect    & 0.000 & 0.014 & 0.013 \\
+%		SE        & 0.016 & 0.019 & 0.019 \\
+%		p-value   & 0.974 & & \\
+%		CI        & & (-0.024 0.051) & (-0.026 0.051) \\
+%
+%		&&& \\
+%		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
+%		Bandwidth & 7 & 5.382, 10.621 & 5.382, 10.621 \\
+%		Effect    & 0.028 & 0.033 & 0.032 \\
+%		SE        & 0.019 & 0.023 & 0.022 \\
+%		p-value   & 0.017 & & \\
+%		CI        & & (-0.014 0.079) & (-0.009 0.077)\\
+%		\bottomrule
+%	\end{tabular}
+%	\caption{The effect of Head Start assistance on education (2000, ages 18-24). The first column is result for directly treated cohorts (2000, ages 18-24) in Table 4 in \cite{ludwig2007}.}
+%	\label{tab: education 2000 ages 18-24}
+%\end{table}
+%
+%\begin{table}[ht]
+%	\centering
+%	\begin{tabular}{cccc}
+%		\toprule
+%		& LM 2007 & CCT 2014 & Bootstrap \\
+%		\midrule
+%		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\
+%		Bandwidth & 7 & 6.074, 11.477 & 6.074, 11.477 \\
+%		Effect    & 0.006 & 0.014 & 0.014 \\
+%		SE        & 0.014 & 0.015 & 0.015 \\
+%		p-value   & 0.666 & & \\
+%		CI        & & (-0.014 0.043) & (-0.023 0.036) \\
+%
+%		&&& \\
+%		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
+%		Bandwidth & 7 & 5.509, 11.463 & 5.509, 11.463 \\
+%		Effect    & 0.040 & 0.049 & 0.049 \\
+%		SE        & 0.017 & 0.020 & 0.021 \\
+%		p-value   & 0.009 & & \\
+%		CI        & & (0.010 0.089) & (0.003 0.083) \\
+%		\bottomrule
+%	\end{tabular}
+%	\caption{The effect of Head Start assistance on education (2000, ages 25-34). The first column is result for directly treated cohorts (2000, ages 25-34) in Table 4 in \cite{ludwig2007}.}
+%	\label{tab: education 2000 ages 25-34}
+%\end{table}
+%
 \section{Conclusion}\label{conclusion}

### 2016-03-01 main_paper.tex
Correct a Citation
Remove application section for now (see a37f881)

--- 2016-03-01 main_paper.tex
@@
 effects and ad expenditure in presidential elections in the U.S.\footnote{%
-  \cite{lee2008}, \cite{Caughey2011}, \cite{keele2014geographic},
+  \cite{lee2008}, \cite{caughey2011elections}, \cite{keele2014geographic},
   \cite{erikson2015}, \cite{Fujiwara2011,Fujiwara2015}}, %
@@
 and its relative performance to the analytical bias correction are presented in
-Section~\ref{sim}, and Section~\ref{application} demonstrates the estimator's
-usage by applying it to the Head Start dataset used by~\cite{ludwig2007}.
+Section~\ref{sim}.
 Finally, Section~\ref{conclusion} concludes.
@@
 
-\section{Application}\label{application}
-
-In this section, we apply the bootstrap procedure to the data\footnote{The data is publicly available from http://faculty.econ.ucdavis.edu/faculty/dlmiller/statafiles/.} used in \cite{ludwig2007}.
-In their paper, the effects of Head Start application assistance on federal spending, mortality and education attainment were investigated under standard RD design.
-They utilized the fact that grant-writing assistance were offered only to the poorest 300 counties to identify the average treatment effect (ATE) at the cutoff.
-
-We estimate the ATE with alternative procedures and compare the new estimates with results in \cite{ludwig2007}.
-Bias-corrected point estimates and robust confidence intervals are reported.
-For completeness, we also include results following the procedure proposed by CCT.
-In \cite{ludwig2007}, analytical standard error and percentile-T bootstrapped p-value were reported\footnote{However, we were unable to reproduce their point estimates for the ATE under the nonparametric setting using triangular kernel, which was documented in their paper.
-Instead, we used uniform kernel and obtained exactly the same results as theirs.}.
-The procedure proposed by CCT provides analytical standard error and confidence interval.
-Our bootstrap procedure provides standard error and confidence interval from the bootstrap distribution.
-In both CCT and bootstrap procedures, we set $p = 1$, $q = 2$ and used uniform kernel.
-In the bootstrap procedure, we used 500 bootstraps for bias correction and 999 for confidence interval.
-
-These results are shown in Table \ref{tab: head start spending}-\ref{tab: education 2000 ages 25-34}.
-We find that (1) the choice of bandwidth may significantly affect estimated ATE and its significance level; (2) the optimal bandwidths following CCT procedure are much smaller than actually being used in \cite{ludwig2007} and (3) our bootstrap procedure produces similar results to CCT.
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{cccccc}
-		\toprule
-		& \multicolumn{3}{c}{LM 2007} & CCT 2014 & Bootstrap \\
-		\midrule
-		& \multicolumn{5}{c}{Panel A: 1968 Head Start spending per child} \\
-		Bandwidth & 9 & 18 & 36 & 5.414, 10.175 & 5.414, 10.175 \\
-		Effect    & 137.251 & 114.711 & 134.491 & 143.811 & 148.990 \\
-		SE        & 128.968 & 91.267  & 62.593 & 113.404 & 182.729 \\
-		p-value   & 0.157   & 0.138   & 0.045  & & \\
-		95\% CI   & & & & (-78.457 366.078) & (-179.120  547.755) \\
-
-		&&&&& \\
-		& \multicolumn{5}{c}{Panel B: 1972 Head Start spending per child} \\
-		Bandwidth & 9 & 18 & 36 & 5.034, 12.020 & 5.034, 12.020 \\
-		Effect    & 182.119 & 88.959 & 130.153 & 94.260 & 100.404 \\
-		SE        & 148.321 & 101.697 & 67.613 & 122.224 & 196.008 \\
-		p-value   & 0.085   & 0.352   & 0.090  & & \\
-		95\% CI   & & & & (-145.294 333.814) & (-165.816 622.976) \\
-
-		&&&&& \\
-		& \multicolumn{5}{c}{Panel C: 1972 other social spending per capita} \\
-		Bandwidth & 9 & 18 & 36 & 4.612, 8.461 & 4.612, 8.461 \\
-		Effect    & 14.474 & 19.590 & 14.506 & 15.418 & 15.857 \\
-		SE        & 28.356 & 19.612 & 14.929 & 29.041 & 39.902 \\
-		p-value   & 0.459   & 0.222   & 0.478  & & \\
-		95\% CI   & & & & (-41.501 72.337) & (-64.153 91.999) \\
-		\bottomrule
-	\end{tabular}
-	\caption{The effect of Head Start assistance on Head Start spending. The first three columns come from Table 2 in \cite{ludwig2007}.}
-	\label{tab: head start spending}
-\end{table}
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{cccccc}
-		\toprule
-		& \multicolumn{3}{c}{LM 2007} & CCT 2014 & Bootstrap \\
-		\midrule
-		Bandwidth & 9 & 18 & 36 & 3.888, 6.807 & 3.888, 6.807 \\
-		Effect    & -1.895 & -1.198 & -1.114 & -3.795 & -3.852 \\
-		SE        & 0.980 & 0.796  & 0.544 & 1.654 & 1.526 \\
-		p-value   & 0.036   & 0.081   & 0.027  & & \\
-		95\% CI   & & & & (-7.037 -0.554) & (-6.565 -0.578) \\
-		\bottomrule
-	\end{tabular}
-	\caption{The effect of Head Start assistance on mortality. The first three columns come from Table 3 in \cite{ludwig2007}.}
-	\label{tab: mortality}
-\end{table}
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{cccc}
-		\toprule
-		& LM 2007 & CCT 2014 & Bootstrap \\
-		\midrule
-		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\
-		Bandwidth & 7 & 3.671, 8.618 & 3.671, 8.618 \\
-		Effect    & 0.030 & 0.055 & 0.054 \\
-		SE        & 0.016 & 0.021 & 0.021 \\
-		p-value   & 0.032 & & \\
-		95\% CI        & & (0.014 0.096) & (0.010 0.094) \\
-
-		&&& \\
-		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
-		Bandwidth & 7 & 5.076, 10.251 & 5.076, 10.251 \\
-		Effect    & 0.037 & 0.051 & 0.051 \\
-		SE        & 0.020 & 0.024 & 0.024 \\
-		p-value   & 0.031 & & \\
-		95\% CI        & & (0.004 0.099) & (0.001 0.092) \\
-		\bottomrule
-	\end{tabular}
-	\caption{The effect of Head Start assistance on education (1990, ages 18-24). The first column is result for directly treated cohorts (1990, ages 18-24) in Table 4 in \cite{ludwig2007}.}
-	\label{tab: education 1990 ages 18-24}
-\end{table}
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{cccc}
-		\toprule
-		& LM 2007 & CCT 2014 & Bootstrap \\
-		\midrule
-		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\
-		Bandwidth & 7 & 4.837, 9.85 & 4.837, 9.85 \\
-		Effect    & 0.000 & 0.014 & 0.013 \\
-		SE        & 0.016 & 0.019 & 0.019 \\
-		p-value   & 0.974 & & \\
-		CI        & & (-0.024 0.051) & (-0.026 0.051) \\
-
-		&&& \\
-		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
-		Bandwidth & 7 & 5.382, 10.621 & 5.382, 10.621 \\
-		Effect    & 0.028 & 0.033 & 0.032 \\
-		SE        & 0.019 & 0.023 & 0.022 \\
-		p-value   & 0.017 & & \\
-		CI        & & (-0.014 0.079) & (-0.009 0.077)\\
-		\bottomrule
-	\end{tabular}
-	\caption{The effect of Head Start assistance on education (2000, ages 18-24). The first column is result for directly treated cohorts (2000, ages 18-24) in Table 4 in \cite{ludwig2007}.}
-	\label{tab: education 2000 ages 18-24}
-\end{table}
-
-\begin{table}[ht]
-	\centering
-	\begin{tabular}{cccc}
-		\toprule
-		& LM 2007 & CCT 2014 & Bootstrap \\
-		\midrule
-		& \multicolumn{3}{c}{Panel A: Fraction high school or more} \\
-		Bandwidth & 7 & 6.074, 11.477 & 6.074, 11.477 \\
-		Effect    & 0.006 & 0.014 & 0.014 \\
-		SE        & 0.014 & 0.015 & 0.015 \\
-		p-value   & 0.666 & & \\
-		CI        & & (-0.014 0.043) & (-0.023 0.036) \\
-
-		&&& \\
-		& \multicolumn{3}{c}{Panel B: Fraction some college or more} \\
-		Bandwidth & 7 & 5.509, 11.463 & 5.509, 11.463 \\
-		Effect    & 0.040 & 0.049 & 0.049 \\
-		SE        & 0.017 & 0.020 & 0.021 \\
-		p-value   & 0.009 & & \\
-		CI        & & (0.010 0.089) & (0.003 0.083) \\
-		\bottomrule
-	\end{tabular}
-	\caption{The effect of Head Start assistance on education (2000, ages 25-34). The first column is result for directly treated cohorts (2000, ages 25-34) in Table 4 in \cite{ludwig2007}.}
-	\label{tab: education 2000 ages 25-34}
-\end{table}
-
 \section{Conclusion}\label{conclusion}

### 2016-03-01 main_paper.tex
Remove the disclaimer from the first page
I think the paper is far enough along now that we don't need to act
like we're ashamed of it. So I've removed the notice to not 'cite or
circulate' from the first page.
Start mathematical appendix on a new page
Revise the application part
Now only focus on the mortality and education for only one cohort.

@@
 then valid confidence intervals can be constructed through the usual method of
-inverting the $t$-test. This procedure gives the widely-used interval estimator
+inverting the $t$-test.\footnote{%
+  The mathematical appendix of this paper gives a precise definition for
+  $V(h)$.} %
+This procedure gives the widely-used interval estimator
 \begin{equation*}
@@
 with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
-generated by the bias-correction term. This new approximation can be used
+generated by the bias-correction term.\footnote{%
+  $C(h,b)$ and $V(h)$ are defined precisely in the mathematical appendix.} %
+This new approximation can be used
 instead of~\eqref{eq:1} to construct ``bandwidth robust'' confidence intervals,
@@
 
+\section{Application}\label{application}
+
+In this section, we apply the bootstrap procedure to the data used in \cite{ludwig2007}.\footnote{The data is publicly available from http://faculty.econ.ucdavis.edu/faculty/dlmiller/statafiles/.} In their paper, the effects of Head Start application assistance on health and schooling were investigated under standard RD design.
+
+In 1965, the Head Start program was established to help poor children age three to five and their families.
+The program elements include parent involvement, nutrition, social services, mental health services and health services.
+To promote this program in the most needing area, the Office of Economic Opportunity provided grant-writing assistance to the poorest 300 counties in the United States based on the 1960 poverty rate.
+So the poverty rate of the 300th poorest county serves as a sharp cutoff of treatment.
+It is shown in \cite{ludwig2007} that the 228 ``treatment" counties with poverty rates 10 percentage points above this cutoff have average Head Start spending per four-year-old as twice as that for 349 ``control" counties with poverty rates 10 percentage points below this cutoff.
+
+\cite{ludwig2007} utilized this fact and estimated the ``intent-to-treat" effect: the effect of proposal developing assistance on health and schooling.
+The mortality data come from Vital statistics, which provide information on cause of death and age at death.
+They limited the causes of death to those which could be affected by Head Start health services and found a large drop in mortality rates of children five to nine years of age over the period of 1973-1983.
+They also found some evidence for a positive effect on schooling from decennial census data.
+
+We reestimate the ATE on health and schooling with robust procedures.
+To be specific, we apply both robust procedure proposed by CCT and bootstrap procedure introduced in this paper.
+For completeness, we also reproduce the original results in \cite{ludwig2007}.\footnote{However, we were unable to reproduce their point estimates for the ATE under the nonparametric setting using triangular kernel, which was documented in their paper.
+Instead, we used uniform kernel and obtained exactly the same results as theirs.} However, there are two issues which make direct comparison difficult.
+First, \cite{ludwig2007} reported percentile-T bootstrapped p-value while both robust procedures do not.
+Second, both robust procedures provide confidence interval, which is not available in \cite{ludwig2007}.
+To complete this comparison, we calculate the conventional confidence interval for estimates in \cite{ludwig2007} and include their percentile-T bootstrapped p-value as well.\footnote{Since these are two different ways for statistical interence, they may disagree with each other.} We use the AMSE-optimal bandwidth proposed by CCT and uniform kernel.
+In the bootstrap procedure, we use 500 bootstraps for bias correction and 999 for confidence interval.
+
+Table \ref{tbl:2} gives the results on the Head Start targeted mortality of children five to nine years of age over the period of 1973-1983.
+Instead of choosing an optimal bandwidth, \cite{ludwig2007} adopted three candidate bandwidths 9, 18, and 36.
+Their estimates indicate that Head Start assistance lowers the targeted mortality rate by -1.895, -1.198 and -1.114 respectively, which are not very sensitive to the choice of bandwidths in this range.
+These ATEs are also significant different from zero (with p-value 0.036, 0.081 and 0.027) based on percentile-T bootstrapped p-value.
+The statistic inference changes when conventional analytical confidence interval is used, which includes zero for bandwidth 9 and 18.
+Results from the two robust procedures are similar to each other but greatly differ from the original estimates.
+The estimated ATEs are as high as -3.795 from CCT and -3.792 from bootstrap.
+Both are significantly different from zero, though the confidence intervals are also  very wide.
+This is mostly due to much smaller bandwidths ($h=3.888, b=6.807$), which are believed to reduce the bias at the cost of larger variance.
+
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{lccccc}
+		\toprule
+		          & ATE    & 95\% CI          &P-value& h     & b     \\ 
+		\midrule
+		LM(2007)  & -1.895 & (-3.930, 0.139)  & 0.036 & 9     &       \\ 
+		LM(2007)  & -1.198 & (-2.561, 0.165)  & 0.081 & 18    &       \\ 
+		LM(2007)  & -1.114 & (-2.138, -0.090) & 0.027 & 36    &       \\ 
+		CCT       & -3.795 & (-7.037, -0.554) &       & 3.888 & 6.807 \\ 
+		Bootstrap & -3.792 & (-6.512, -0.262) &       & 3.888 & 6.807 \\ 
+		\bottomrule
+	\end{tabular}
+	\caption{The effect of Head Start assistance on mortality.
+The first three rows come from Table 3 in \cite{ludwig2007} except ``95\% CI", which is calculated using conventional approach.
+The last two rows list results from two robust procedures.}
+	\label{tbl:2}
+\end{table}
+
+Table \ref{tb:3} gives the results on schooling for the cohort aged 18-24 in 1990.
+The measurement of schooling is the fraction of people with high school or more in Panel A and the fraction of people with some college or more in Panel B.
+A bandwidth of 7 is used in \cite{ludwig2007}.
+Their estimates suggest that Head Start assistance increases the fraction of people with high school or more by 3\% and the fraction of people with some college or more by 3.7\%.
+Both are significantly different from zero based on percentile-T bootstrapped p-value and conventional analytical confidence interval.
+The two robust procedures are again very similar to each other and give slightly larger point estimates in both panels.
+In Panel A, the ATE increases from 0.030 to 0.055(CCT) and 0.054(bootstrap).
+In Panel B, the ATE increases from 0.037 to 0.051(CCT) and 0.052(bootstrap).
+In contrast to the striking differences between estimates in \cite{ludwig2007} and estimates from robust procedures for mortality, the differences in Table \ref{tb:3} are much smaller.
+
+\begin{table}[ht]
+	\centering
+	\begin{tabular}{lccccc}
+		\toprule
+		& ATE   & 95\% CI        &P-value& h     & b                \\ 
+		\midrule
+		&\multicolumn{5}{c}{Panel A: Fraction high school or more}  \\
+
+		LM(2007)  & 0.030 & (0.003, 0.057) & 0.032 & 7     &                  \\ 
+		CCT       & 0.055 & (0.014, 0.096) &       & 3.671 & 8.618            \\ 
+		Bootstrap & 0.054 & (0.013, 0.096) &       & 3.671 & 8.618            \\
+
+		&&&&& \\
+		&\multicolumn{5}{c}{Panel B: Fraction some college or more} \\		
+		LM(2007)  & 0.037 & (0.002, 0.073) & 0.031 & 7     &                  \\ 
+		CCT       & 0.051 & (0.004, 0.099) &       & 5.076 & 10.251           \\ 
+		Bootstrap & 0.052 & (0.001, 0.094) &       & 5.076 & 10.251           \\ 
+		\bottomrule
+	\end{tabular}
+	\caption{The effect of Head Start assistance on education for cohort 18-24 in 1990.
+Panel A uses the fraction of people with high school or more as dependent variable.
+Panel B uses the fraction of people with some college or more as dependent variable.
+The first row in each panel comes from Table 4 in \cite{ludwig2007} except ``95\% CI", which is calculated using conventional approach.
+The last two rows in each panel list results from two robust procedures.}
+	\label{tb:3}
+\end{table}
+
+To briefly summarize, the bootstrap procedure performs similarly to the robust estimator proposed by CCT in above applications.
+In Table \ref{tbl:2} and \ref{tb:3}, these two approaches give almost identical point estimates and interval estimates.
+
 \section{Conclusion}\label{conclusion}
@@
 
+\newpage
 \appendix
 \section{Mathematical appendix}
-
-Define the following additional notation:
-$r_p(x) = (1,\ x,\dots,\ x^p)'$,
-\begin{equation*}
-  (\hat{\mu}_{+}(h),\ \hat{\mu}_{+}^{(1)}(h),\ \hat\mu_{+}^{(2)}(h))' =
-  \argmin_{\mu_0, \mu_1, \mu_2} \ssum[+]{i}{h} (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2),
-\end{equation*}
-\begin{equation*}
-(\hat{\mu}_{-}(h),\ \hat{\mu}_{-}^{(1)}(h),\ \hat\mu_{-}^{(2)}(h))' =
-  \argmin_{\mu_0, \mu_1, \mu_2} \ssum[-]{i}{h} (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2) \\
-\end{equation*}
+Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
+everywhere else. Define the following additional notation (largely
+introduced by CCT): $r_p(x) = (1,\ x,\dots,\ x^p)'$,
+\begin{align*}
+  (\hat{\mu}_{+}(h),\ \hat{\mu}_{+}^{(1)}(h),\ \hat\mu_{+}^{(2)}(h))'
+  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[+]{i}{h}
+    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2) \\
+  (\hat{\mu}_{-}(h),\ \hat{\mu}_{-}^{(1)}(h),\ \hat\mu_{-}^{(2)}(h))'
+  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[-]{i}{h}
+    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2)
+\end{align*}
 \begin{align}
+  \notag
+  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
+  \notag
+  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
+  \notag
+  \Psi_{+,p,q}(h,b)
+  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
+    \V(Y_i \mid X_i) \\
+  \notag
+  \Psi_{-,p,q}(h,b)
+  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
+    \V(Y_i \mid X_i) \\
   \label{eq:5}
   \Bf_+(h)
-  & = (1\ \  0)\ \Big(\ssum[+]{i}{h} r_1(X_i/h) r_1(X_i/h)' \Big)^{-1}
+  & = e_0' \Gamma_{+,1}^{-1}
     \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
@@
   \Bf_-(h)
-  & = (1\ \ 0)\ \Big(\ssum[-]{i}{h} r_1(X_i/h) r_1(X_i/h)' \Big)^{-1}
+  & = e_0' \Gamma_{-,1}^{-1}
     \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
 \end{align}
+
+Also, for reference, define the variance terms
+\begin{equation*}
+  V(h)
+  = e_0' \Big(\tfrac{1}{n} \Gamma_{-,1}^{-1} \Psi_{-,1} \Gamma_{-,1}^{-1}
+  + \tfrac{1}{n} \Gamma_{+,1}^{-1} \Psi_{+,1} \Gamma_{+,1}^{-1}\Big) e_0
+\end{equation*}
+and
+\begin{multline*}
+  C(h,b) =
+  n^{-1} e_2' \Big[
+    \Gamma_{+,2}^{-1}(b) \Psi_{+,2,2}(b,b) \Gamma_{+,2}^{-1}(b) \Bf^2_+(h) +
+    \Gamma_{-,2}^{-1}(b) \Psi_{-,2,2}(b,b) \Gamma_{-,2}^{-1}(b) \Bf^2_-(h)
+    \Big] e_2 \\
+  - 2 h^2 n^{-1} b^{-2}
+    e_0' \Big[
+    \Gamma^{-1}_{+,1}(h) \Psi_{+,1,2}(h,b) \Gamma_{+,2}^{-1}(b) \Bf_+(h) +
+    \Gamma^{-1}_{-,1}(h) \Psi_{-,1,2}(h,b) \Gamma_{-,2}^{-1}(b) \Bf_-(h)
+    \Big] e_2.
+\end{multline*}
+See CCT for the derivation and justification of these formulas.
 
@@
   \label{eq:9}
-  \rho(V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}^{*},\
-    V^{-1/2}(h,b)\Omega_+(h,b)'\epb_{+}) \to^p 0
+  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
+    V'(h,b)^{-1/2}\Omega_+(h,b)'\epb_{+}) \to^p 0
   \intertext{and}
   \label{eq:10}
-  \rho(V^{-1/2}(h,b)\Omega_-(b)'\epb_{-}^{*},\
-    V^{-1/2}(h,b)\Omega_-(b)'\epb_{-}) \to^p 0
+  \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
+    V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}) \to^p 0
 \end{gather}
@@
 \begin{align*}
-  \rho(V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}^{*},\
-  &V^{-1/2}(h,b) \Omega_+(h,b)'\epb_{+}) \\
+  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
+  &V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}) \\
   &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
-    \tr(V^{-1/2}(h,b) \Omega_+(h,b)' \Omega_+(h,b)V^{-1/2}(h,b)) \\
+    \tr(V'(h,b)^{-1/2} \Omega_+(h,b)' \Omega_+(h,b)V'(h,b)^{-1/2}) \\
   &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),

### 2016-03-01 R/application2.R

@@ -1,0 +1,343 @@
+rm(list = ls())
+library(rdrobust)
+library(rdd)
+library(xtable)
+library(testthat)
+source("RDfunctions.R")
+
+###################################################################################
+## replicate part of their results ################################################
+###################################################################################
+
+cut <- 59.1984
+census2 <- read.csv("C:/Users/Yang/OneDrive/gProjects/Data/LM2007/analysis data/census2.csv")
+census3 <- read.csv("C:/Users/Yang/OneDrive/gProjects/Data/LM2007/analysis data/census3.csv")
+mort <- read.csv("C:/Users/Yang/OneDrive/gProjects/Data/LM2007/analysis data/mort.csv")
+mort4 <- read.csv("C:/Users/Yang/OneDrive/gProjects/Data/LM2007/analysis data/mort4.csv")
+census_1990 <- read.csv("C:/Users/Yang/OneDrive/gProjects/Data/LM2007/analysis data/census_1990.csv")
+census_2000 <- read.csv("C:/Users/Yang/OneDrive/gProjects/Data/LM2007/analysis data/census_2000.csv")
+
+#### table 2 ####
+
+## dependent variable: hsspend_per_kid_68
+
+hsspend_per_kid_68 <- census2[ , c("hsspend_per_kid_68", "povrate60")]
+hsspend_per_kid_68 <- hsspend_per_kid_68[complete.cases(hsspend_per_kid_68), ]
+colnames(hsspend_per_kid_68) <- c("y", "x")
+hsspend_per_kid_68$x <- hsspend_per_kid_68$x - cut
+
+test_that("table 2 hsspend_per_kid_68",{
+  expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 1, 1, 9, 9, 0, "uni", F)), digits = 3), 137.251)    # Nonparametric h = 9
+  expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 1, 1, 18, 18, 0, "uni", F)), digits = 3), 114.711)  # Nonparametric h = 18
[…]

### 2016-03-01 main_paper.tex
Fix small typos in proof of Theorem 2
Tweak presentation of author affiliations

--- 2016-03-01 main_paper.tex
@@
 
-\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{All authors:
-Department of Economics, Iowa State University. 260 Heady Hall, Ames, IA  50011.
-Bartalotti: Email: bartalot@iastate.edu. Calhoun: gcalhoun@iastate.edu.
-He: yanghe@iastate.edu.}}
+\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
+  All authors: Department of Economics, Iowa State University.
+  260 Heady Hall, Ames, IA 50011.
+  Bartalotti: \protect\url{bartalot@iastate.edu};
+  Calhoun: \protect\url{gcalhoun@iastate.edu} and
+  \protect\url{http://gray.clhn.org};
+  He: \protect\url{yanghe@iastate.edu}.}}
 

### 2016-03-01 main_paper.tex
Make some small edits to the application of the main paper

--- 2016-03-01 main_paper.tex
@@
   holds under similar conditions to Calonico, Cattaneo and Titiunik's (2014,
-  \textit{Econometrica}) analytical correction.
+  \textit{Econometrica}) analytical correction. This paper also provides
+  simulation evidence that our method is as accurate as the analytical
+  corrections and we demonstrate its use through a reanalysis of Ludwig and
+  Miller's (2008) Head Start dataset.
 \end{abstract}
@@
 and its relative performance to the analytical bias correction are presented in
-Section~\ref{sim}.
+Section~\ref{sim} and Section~\ref{application} demonstrates the estimator's
+usage by applying it to the Head Start dataset used
+by~\cite{ludwig2007}.\footnote{%
+  The simulations and empirical analysis were carried out in the R programming
+  language \citep{R} and rely on the \textit{rdrobust} \citep{rdrobust},
+  \textit{doParallel} \citep{doparallel}, \textit{foreach} \citep{foreach}, and
+  \textit{doRNG} \citep{dorng} packages.} %
 Finally, Section~\ref{conclusion} concludes.
@@
 alternative, with coverage slightly closer to nominal coverage and shorter
-length of the intervals in the specifications implemented.\footnote{%
-  All of the simulations were carried out in the R programming language
-  \citep{R} and rely on the \textit{rdrobust} \citep{rdrobust}, \textit{foreach}
-  \citep{foreach}, \textit{doParallel} \citep{doparallel}, and \textit{doRNG}
-  \citep{dorng} packages.} %
+length of the intervals in the specifications implemented.
 
@@
 
+\section{Application}\label{application}
+
+In this section, we apply the bootstrap procedure to the data used in
+\cite{ludwig2007}.\footnote{%
+  The data is publicly available from
+  \url{http://faculty.econ.ucdavis.edu/faculty/dlmiller/statafiles}.} %
+In their paper, the effects of Head Start application assistance on health and
+schooling were investigated under a sharp RD design.
+
+In 1965, the Head Start program was established to help poor children age three
+to five and their families. The program elements include parent involvement,
+nutrition, social services, mental health services and health services. To
+promote this program in the most needing area, the Office of Economic
+Opportunity provided grant-writing assistance to the poorest 300 counties in the
+United States based on the 1960 poverty rate. So the poverty rate of the 300th
+poorest county serves as a sharp cutoff of treatment. It is shown in
+\cite{ludwig2007} that the 228 ``treatment'' counties with poverty rates 10
+percentage points above this cutoff have average Head Start spending per
+four-year-old as twice of that for 349 ``control'' counties with poverty rates
+10 percentage points below this cutoff.
+
+\cite{ludwig2007} utilize this fact to estimate the ``intent-to-treat'' effect:
+the effect of proposal developing assistance on health and schooling. They use
+mortality as their health measure and use data from the National Vital
+Statistics System of the National Center for Health Statistics, which provide
+information on cause of death and age at death. \cite{ludwig2007} limited the
+causes of death to those which could be affected by Head Start health services
+and found a large drop in mortality rates of children five to nine years of age
+over the period of 1973--1983. They also found some evidence for a positive
+effect on schooling from decennial census data.
+
+We reestimate the ATE on health and schooling with robust procedures. To be
+specific, we apply both the robust procedure proposed by CCT and the bootstrap
+procedure introduced in this paper.  Our bootstrap estimator uses the
+AMSE-optimal bandwidths proposed by CCT and the uniform kernel. In the bootstrap
+procedure, we use 500 bootstraps for bias correction and 999 to calculate the
+confidence intervals.\footnote{%
+  These are the same design choices made for the Monte Carlo study.} %
+The analytical estimator using CCT's bias correction and variance estimator use
+their AMSE-optimal bandwidths as well.
+
+\begin{table}[t]
+  \centering
+  \begin{tabular}{lrr@{, }rr@{}rlr}
+    \toprule
+                      & ATE     & \multicolumn{2}{r}{95\% CI}           & $h$&      & $b$   & p-value \\
+    \midrule
+    LM (2007)         & --1.895 & (--3.930                    & 0.139)   &  9&     &       & 0.036   \\
+    LM (2007)         & --1.198 & (--2.561                    & 0.165)   & 18&     &       & 0.081   \\
+    LM (2007)         & --1.114 & (--2.138                    & --0.090) & 36&     &       & 0.027   \\
+    CCT               & --3.795 & (--7.037                    & --0.554) &  3&.888 & 6.807 &         \\
+    Resid.\ bootstrap & --3.792 & (--6.512                    & --0.262) &  3&.888 & 6.807 &         \\
+    \bottomrule
+  \end{tabular}
+  \caption{The effect of Head Start assistance on mortality. The first three
+    rows come from Table 3 in \cite{ludwig2007} except ``95\% CI,'' which is
+    calculated using the conventional asymptotic interval estimator.
+    The last two rows list results from two robust procedures.}
+  \label{tbl:2}
+\end{table}
+
+For completeness, we also report the
+original results in \cite{ludwig2007}.\footnote{%
+  One minor issue arose in reproducing Ludwig and Miller's results: their paper
+  presents results for the \emph{triangular} kernel, but we were only able to
+  recover their ATE estimate using the \emph{uniform} kernel. Results for the
+  triangular and uniform kernel were essentially the same, and this discrepency
+  does not affect Ludwig and Miller's conclusions.} %
+Since our research focuses on confidence intervals, we calculate and report
+the conventional unadjusted RD confidence interval for each of the bandwidths
+used by \cite{ludwig2007}. (Ludwig and Miller use a range of bandwidths
+for their analysis.) They also use a paired bootstrap algorithm to generate
+p-values, and we report those p-values for completeness.
+
+Table \ref{tbl:2} shows the results of the Head Start program on mortality of
+children five to nine years of age.\footnote{%
+  We, like Ludwig and Miller, focus on the 1973--1983 period.} %
+Instead of choosing an optimal bandwidth, \cite{ludwig2007} adopted three
+candidate bandwidths 9, 18, and 36. Their estimates indicate that Head Start
+assistance lowers the targeted mortality rate by --1.895, --1.198 and --1.114
+respectively, which are not very sensitive to the choice of bandwidths in this
+range. These ATEs are also significantly different from zero (with p-value
+0.036, 0.081 and 0.027) based on Ludwig and Miller's percentile-$T$ bootstrapped
+p-value. The statistical inference changes when conventional analytical
+confidence interval is used, which includes zero for bandwidth 9 and 18.
+
+Results from the two robust procedures are similar to each other but greatly
+differ from the original estimates. The estimated ATEs are as high as -3.795
+from CCT and -3.792 from the bootstrap. Both are significantly different from
+zero, though the confidence intervals are also very wide, which is likely to be
+due to the much smaller bandwidths used relative to the other estimators
+($h=3.888, b=6.807$).
+
+Table \ref{tbl:3} presents the effect of the program on schooling for the cohort
+aged 18-24 in 1990. The measurement of schooling is the fraction of people with
+high school or more in Panel A and the fraction of people with some college or
+more in Panel B. A bandwidth of 7 is used in \cite{ludwig2007}. Their estimates
+suggest that Head Start assistance increases the fraction of people with high
+school or more by 3\% and the fraction of people with some college or more by
+3.7\%. Both are significantly different from zero based on both their p-value
+and the conventional analytical confidence interval.
+
+The two robust procedures are again very similar to each other and give slightly
+larger point estimates in both panels. In Panel A, the ATE increases from 0.030
+to 0.055 (CCT) and 0.054 (bootstrap). In Panel B, the ATE increases from 0.037
+to 0.051 (CCT) and 0.052 (bootstrap). The confidence intervals tend to shift up
+as well.  In contrast to the striking differences between the conventional
+estimates bias-corrected procedures for the mortality estimates, the differences
+in Table~\ref{tbl:3} are much smaller.
+
+\begin{table}[t]
+  \centering
+  \begin{tabular}{lrr@{, }rr@{}rlr}
+    \toprule
+              & ATE   & \multicolumn{2}{r}{95\% CI} & $h$    &   & $b$  & p-value     \\
+    \midrule                                                                          \\
+    \multicolumn{5}{l}{Fraction ``high school or more'' (Panel A)}                    \\
+    \midrule
+    LM (2007) & 0.030 & (0.003                      & 0.057) & 7&     &  & 0.032    \\
+    CCT       & 0.055 & (0.014                      & 0.096) & 3&.671 & 8.618       \\
+    Bootstrap & 0.054 & (0.013                      & 0.096) & 3&.671 & 8.618       \\\\
+    \multicolumn{5}{l}{Fraction ``some college or more'' (Panel B)}                   \\
+    \midrule
+    LM (2007) & 0.037 & (0.002                      & 0.073) & 7&     &  & 0.032 \T \\
+    CCT       & 0.051 & (0.004                      & 0.099) & 5&.076 & 10.251      \\
+    Bootstrap & 0.052 & (0.001                      & 0.094) & 5&.076 & 10.251      \\
+    \bottomrule
+  \end{tabular}
+  \caption{The effect of Head Start assistance on education for cohort
+    18-24 in 1990. Panel A uses the fraction of people with high school
+    or more as dependent variable. Panel B uses the fraction of people
+    with some college or more as dependent variable. The first row in
+    each panel comes from Table 4 in \cite{ludwig2007} except ``95\% CI,''
+    which is calculated using the conventional asymptotic interval estimator.
+    The last two rows in
+    each panel list results from two robust procedures.}
+  \label{tbl:3}
+\end{table}
+
+To briefly summarize, the bootstrap procedure performs similarly to the robust
+estimator proposed by CCT in the above applications. Both provide somewhat
+dissimilar answers from the classical point and interval estimators that do
+not account for the estimator's bias, but our estimates largely support the
+direction and the statistical significance of Ludwig and Miller's (2007)
+empirical findings.
+
 \section{Conclusion}\label{conclusion}
-This paper proposes a novel bootstrap procedure to obtain robust bias-corrected confidence intervals in regression discontinuity designs.
-The approach proposed builds upon the developments and intuition advanced by CCT and is based on a first-order bias correction.
- We exploit CCT's theoretical insight through a new residual bootstrap. In particular, we propose estimating the local linear model as usual,
-then estimating a local second order polynomial and generating bootstrap datasets by resampling the residuals of that polynomial.
-
-The bootstrap sample is used to estimate the bias of the RD estimator, which is then removed from the original estimator.
- This approach is described in detail by our Algorithm~\ref{Alg1} and the resulting bias corrected estimator is shown to be asymptotically normal with mean zero in our
-Theorem~\ref{T1} under AMSE-optimal bandwidth rates.
-
-Just as in CCT, our bias correction step introduces additional variability.  So we propose then bootstrap the bias-corrected estimator itself to
- generate valid confidence intervals. This procedure, which requires bootstrapping the datasets produced by an initial bootstrap procedure, is described in Algorithm~\ref{Alg2},
- and the resulting confidence intervals are shown to be asymptotically valid in Theorem~\ref{T2}.
-
- Hence, our procedure provides an alternative to the plug-in analytical methods in the literature and is simple to implement generating robust confidence intervals.
-
-Simulation evidence is presented that the proposed bootstrap bias correction and confidence intervals have similar empirical coverage and average interval length relative to
- the analytical alternatives proposed by CCT, making it a suitable option to practitioners.
+
+This paper proposes a novel bootstrap procedure to obtain robust bias-corrected
+confidence intervals in sharp regression discontinuity designs using a uniform
+kernel. The approach proposed builds upon the developments and intuition
+advanced by CCT and is based on a first-order bias correction. We exploit CCT's
+theoretical insight through a new residual bootstrap. In particular, we propose
+estimating the local linear model as usual, then estimating a local second order
+polynomial and generating bootstrap datasets by resampling the residuals of that
+polynomial. This bootstrap allows the bias of the linear model to be estimated
+and removed, and the bootstrap can be repeated to accurately estimate the
+sampling distribution of the bias-corrected estimator.
+
+Bootstrap procedures are appealing in this setting because they are relatively
+easy for applied researchers to modify to account for new and unusual dependence
+structures or functional forms. The variance adjustment was proven to be correct
+under the assumption of i.i.d.\ data, but could easily be extended to handle
+cross-sectional or time series dependence by using the appropriate resampling
+strategy on the second order polynomial's residuals. For the analytical methods,
+however, new formulas need to be derived to accomodate new features of the
+DGP. To fully take advantage of the bootstrap's flexibility, though, these
+results need to be extended to other kernels, design strategies (e.g. fuzzy and
+kink RD designs) and other more realistic dependence structures. All of these
+are the subject of ongoing research.
 

### 2016-03-01 main_paper.tex
Revise/edit conclusion

--- 2016-03-01 main_paper.tex
@@
 \section{Conclusion}\label{conclusion}
-This paper proposes a novel bootstrap procedure to obtain robust bias-corrected confidence intervals in regression discontinuity designs.
-The approach proposed builds upon the developments and intuition advanced by CCT and is based on a first-order bias correction.
- We exploit CCT's theoretical insight through a new residual bootstrap. In particular, we propose estimating the local linear model as usual,
-then estimating a local second order polynomial and generating bootstrap datasets by resampling the residuals of that polynomial.
-
-The bootstrap sample is used to estimate the bias of the RD estimator, which is then removed from the original estimator.
- This approach is described in detail by our Algorithm~\ref{Alg1} and the resulting bias corrected estimator is shown to be asymptotically normal with mean zero in our
-Theorem~\ref{T1} under AMSE-optimal bandwidth rates.
-
-Just as in CCT, our bias correction step introduces additional variability.  So we propose then bootstrap the bias-corrected estimator itself to
- generate valid confidence intervals. This procedure, which requires bootstrapping the datasets produced by an initial bootstrap procedure, is described in Algorithm~\ref{Alg2},
- and the resulting confidence intervals are shown to be asymptotically valid in Theorem~\ref{T2}.
-
- Hence, our procedure provides an alternative to the plug-in analytical methods in the literature and is simple to implement generating robust confidence intervals.
-
-Simulation evidence is presented that the proposed bootstrap bias correction and confidence intervals have similar empirical coverage and average interval length relative to
- the analytical alternatives proposed by CCT, making it a suitable option to practitioners.
+
+This paper proposes a novel bootstrap procedure to obtain robust bias-corrected
+confidence intervals in sharp regression discontinuity designs using a uniform
+kernel. The approach proposed builds upon the developments and intuition
+advanced by CCT and is based on a first-order bias correction. We exploit CCT's
+theoretical insight through a new residual bootstrap. In particular, we propose
+estimating the local linear model as usual, then estimating a local second order
+polynomial and generating bootstrap datasets by resampling the residuals of that
+polynomial. This bootstrap allows the bias of the linear model to be estimated
+and removed, and the bootstrap can be repeated to accurately estimate the
+sampling distribution of the bias-corrected estimator.
+
+Bootstrap procedures are appealing in this setting because they are relatively
+easy for applied researchers to modify to account for new and unusual dependence
+structures or functional forms. The variance adjustment was proven to be correct
+under the assumption of i.i.d.\ data, but could easily be extended to handle
+cross-sectional or time series dependence by using the appropriate resampling
+strategy on the second order polynomial's residuals. For the analytical methods,
+however, new formulas need to be derived to accomodate new features of the
+DGP. To fully take advantage of the bootstrap's flexibility, though, these
+results need to be extended to other kernels, design strategies (e.g. fuzzy and
+kink RD designs) and other more realistic dependence structures. All of these
+are the subject of ongoing research.
 

### 2016-03-01 main_paper.tex
Remove some equation numbers from the appendix

--- 2016-03-01 main_paper.tex
@@
 kernel, bandwidth, and running variables $X_1,\dots,X_n$; formal definitions of
-these terms are given in the Mathematical Appendix as Equations~\eqref{eq:5}
-and~\eqref{eq:6}. The plug-in bias-corrected estimator then requires estimates
+these terms are given in the Mathematical Appendix. The plug-in bias-corrected
+estimator then requires estimates
 for the second derivatives of the conditional mean from above and below the
@@
 \end{align*}
-\begin{align}
-  \notag
+\begin{align*}
   \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
-  \notag
   \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
-  \notag
   \Psi_{+,p,q}(h,b)
@@
     \V(Y_i \mid X_i) \\
-  \notag
   \Psi_{-,p,q}(h,b)
@@
     \V(Y_i \mid X_i) \\
-  \label{eq:5}
   \Bf_+(h)
@@
     \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
-  \label{eq:6}
   \Bf_-(h)
@@
     \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
-\end{align}
+\end{align*}
 
@@
 \begin{equation}
-  \label{eq:7}
+  \label{eq:5}
   \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
@@
    - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
-  \label{eq:8}
+  \label{eq:6}
   &= \hat\tau(h) - \E\hat\tau(h)
@@
 \subsection{Proof of Theorem~\ref{T2}}
-Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:8} to get
+Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:6} to get
 \begin{align*}
@@
 
-Given~\eqref{eq:8}, it suffices to prove that
+Given~\eqref{eq:6}, it suffices to prove that
 \begin{gather}
-  \label{eq:9}
+  \label{eq:7}
   \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
@@
   \intertext{and}
-  \label{eq:10}
+  \label{eq:8}
   \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
@@
 
-We will only prove~\eqref{eq:9} since the proof of~\eqref{eq:10} is
+We will only prove~\eqref{eq:7} since the proof of~\eqref{eq:8} is
 identical. By Theorem 2.1 of \cite{freedman1981}, we have

### 2016-03-01 run_everything.R
Remove R script named 'run_everything.R'
We're not using it, so there's no reason to keep it around.

@@ -1,2 +1,0 @@
-source("R/version.R")
-source("R/simulation.R")

### 2016-03-01 main_paper.tex
Make some minor formatting and text tweaks
Fix minor spelling errors

@@
   language \citep{R} and rely on the \textit{rdrobust} \citep{rdrobust},
-  \textit{doParallel} \citep{doparallel}, \textit{foreach} \citep{foreach}, and
+  \textit{doParallel}, \textit{foreach} \citep{doparallel,foreach}, and
   \textit{doRNG} \citep{dorng} packages.} %
@@
 X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
-\varepsilon_{i} &\sim \normal(0, 0.1295^2),
+\varepsilon_{i} &\sim N(0, 0.1295^2),
 \end{align*}
@@
 \citet{IK} and CCT, which we adopt here to make our simulation results directly
-comparable with theirs and the rest of the literature. We
+comparable with theirs and with the rest of the literature. We
 will use the same three functional forms for $\mu_{j}$ as CCT as well.
@@
   recover their ATE estimate using the \emph{uniform} kernel. Results for the
-  triangular and uniform kernel were essentially the same, and this discrepency
+  triangular and uniform kernel were essentially the same, and this discrepancy
   does not affect Ludwig and Miller's conclusions.} %
@@
 strategy on the second order polynomial's residuals. For the analytical methods,
-however, new formulas need to be derived to accomodate new features of the
+however, new formulas need to be derived to accommodate new features of the
 DGP. To fully take advantage of the bootstrap's flexibility, though, these
@@
 
-\newpage
 \appendix

### 2016-03-01 R/application.R
Add LM2007 data in .CSV format

@@ -1,57 +1,20 @@
 rm(list = ls())
 library(rdrobust)
 library(xtable)
-try(source("slackrISE.R"), silent = T)
-
-source("functions.R")
-
-setwd("C:/Users/Yang/OneDrive/QJE data and code PUBLIC/analysis data")
-
-###################################################################################
-## slightly modify the function rd.ci so that it exports standard error
-###################################################################################
-
-rd.ci <- function(dta, p, q, bw.p, bw.q, N.bc, N.ci, level, kernel, bc = T) {
-  # dta:    a data set contains y and x.
-  # p:      the order of polynomial for point estimation.
-  # q:      the order of polynomial for bias correction.
-  # bw.p:   bandwidth for point estimation.
-  # bw.q:   bandwidth for bias correction.
-  # N.bc:   number of bootstrap replications for bias correction.
-  # N.ci:   number of bootstrap replications for confidence interval.
-  # kernel: epanechnikov, uniform or triangular.
-  # bc:     perform bias correction?
-  
-  if (length(bw.p) == 1) bw.p <- rep(bw.p, 2)
-  if (length(bw.q) == 1) bw.q <- rep(bw.q, 2)
-  
-  # fit the high order polynomial on both sides
-  dta.q.l <- dta[dta$x > -bw.q[1] & dta$x < 0, ]
-  dta.q.r <- dta[dta$x < bw.q[2] & dta$x >= 0, ]
-  left  <- lpreg(dta.q.l, q, bw.q[1], kernel)
-  right <- lpreg(dta.q.r, q, bw.q[2], kernel)
-  
-  # bootstrap
-  trd.star <- replicate(N.ci, rd.estimate(data.frame(x = c(dta.q.l$x, dta.q.r$x),
-                                                     y = c(left$yhat + sample(left$res, nrow(dta.q.l), T, left$weight),
-                                                           right$yhat + sample(right$res, nrow(dta.q.r), T, right$weight))),
-                                          p, q, bw.p, bw.q, N.bc, kernel, bc))
-  ci <- quantile(trd.star, c((1 - level)/2, 1 - (1 - level)/2), na.rm = T)
-  sd <- sd(trd.star)
-  return(list(ci = ci, sd = sd))
-}
+library(testthat)
[…]

### 2016-03-01 R/application2.R

@@ -1,343 +1,0 @@
-rm(list = ls())
-library(rdrobust)
-library(rdd)
-library(xtable)
-library(testthat)
-source("RDfunctions.R")
-
-###################################################################################
-## replicate part of their results ################################################
-###################################################################################
-
-cut <- 59.1984
-census2 <- read.csv("C:/Users/Yang/OneDrive/gProjects/Data/LM2007/analysis data/census2.csv")
-census3 <- read.csv("C:/Users/Yang/OneDrive/gProjects/Data/LM2007/analysis data/census3.csv")
-mort <- read.csv("C:/Users/Yang/OneDrive/gProjects/Data/LM2007/analysis data/mort.csv")
-mort4 <- read.csv("C:/Users/Yang/OneDrive/gProjects/Data/LM2007/analysis data/mort4.csv")
-census_1990 <- read.csv("C:/Users/Yang/OneDrive/gProjects/Data/LM2007/analysis data/census_1990.csv")
-census_2000 <- read.csv("C:/Users/Yang/OneDrive/gProjects/Data/LM2007/analysis data/census_2000.csv")
-
-#### table 2 ####
-
-## dependent variable: hsspend_per_kid_68
-
-hsspend_per_kid_68 <- census2[ , c("hsspend_per_kid_68", "povrate60")]
-hsspend_per_kid_68 <- hsspend_per_kid_68[complete.cases(hsspend_per_kid_68), ]
-colnames(hsspend_per_kid_68) <- c("y", "x")
-hsspend_per_kid_68$x <- hsspend_per_kid_68$x - cut
-
-test_that("table 2 hsspend_per_kid_68",{
-  expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 1, 1, 9, 9, 0, "uni", F)), digits = 3), 137.251)    # Nonparametric h = 9
-  expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 1, 1, 18, 18, 0, "uni", F)), digits = 3), 114.711)  # Nonparametric h = 18
[…]

### 2016-03-07 main_paper.tex
Tweak reference to CCT's notation

@@
 presents the assumptions that will be used for our theoretical analysis in
-Section~\ref{boot}.
+Section~\ref{boot}. We have adopted CCT's notation where possible to aid
+readers familiar with that paper.
 
@@
 Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
-everywhere else. Define the following additional notation (largely
-introduced by CCT): $r_p(x) = (1,\ x,\dots,\ x^p)'$,
+everywhere else. Define the following additional notation:\footnote{%
+  As we mention in Section~\ref{background}, we have adopted CCT's
+  notation where possible and these terms originate in that paper.} %
+$r_p(x) = (1,\ x,\dots,\ x^p)'$,
 \begin{align*}

### 2016-03-07 R/RDfunctions.R
Switch 'k.weights' function to call from rdrobust
Our copy of 'k.weights' is identical to the one from the rdrobust
package. I'd like to avoid licensing and copyright issues and I
also want to use a less restrictive license than CCT's choice of
the GPL, so I'm switching our code to explicitly refer to their
package.

@@ -1,3 +1,4 @@
+kweight <- rdrobust::kweight
 
 generate.data <- function(model.id) {
   x <- 2*rbeta(500, 2, 4) - 1
@@ -12,20 +13,8 @@ generate.data <- function(model.id) {
   return(data.frame(y = y, x = x))
 }
 
-k.weight <- function(x, h, kernel) {
-  u <- x / h
-  if (kernel == "epanechnikov" | kernel == "epa") {
-    w <- (0.75*(1 - u^2)*(abs(u) <= 1)) / h
-  } else if (kernel == "uniform" | kernel == "uni") {
-    w <- (0.5*(abs(u) <= 1)) / h
-  } else {
-    w <- ((1 - abs(u))*(abs(u) <= 1)) / h
-  }
-  return(w)	
-}
-
 lpreg <- function(dta, order, bw, kernel) {
-  weight <- k.weight(dta$x, bw, kernel)
+  weight <- kweight(dta$x, 0, bw, kernel)
   fit    <- lm.wfit(cbind(1, poly(dta$x, order, raw = T)), dta$y, weight)
   return(list(cons = fit$coefficients[1], 
               yhat = fit$fitted.values, 
@@ -139,7 +128,7 @@ bw.select <- function(dta, r1, r2, N.bw, kernel, hstart = NULL) {
   
   boot.mse <- function(h, boot.y, x, true.value) {
     mean(apply(boot.y, 2, function(yb) {
-      (lm.wfit(cbind(1, poly(x, r1, raw = T)), yb, k.weight(x, h, kernel))$coefficients[1] - true.value)^2
+      (lm.wfit(cbind(1, poly(x, r1, raw = T)), yb, kweight(x, 0, h, kernel))$coefficients[1] - true.value)^2
     }))
   }
   

### 2016-03-07 R/application.R
Create R script to run all analysis
This commit adds (back) the function R/run_everything.R, which runs
all of the simulations and empirical analysis for the paper. It also
moves the R code that replicates Ludwig and Miller's tables into a
separate file to keep the application code as simple as possible. Each
R script is run in a separate environment to explicitly keep the
workspace clean.

@@ -1,12 +1,8 @@
-rm(list = ls())
 library(rdrobust)
 library(xtable)
-library(testthat)
 source("RDfunctions.R")
 
-###################################################################################
-## replicate part of their results ################################################
-###################################################################################
+## Load Ludwig and Miller's (2007) dataset
 
 cutoff <- 59.1984
 census2 <- read.csv("./LM2007data/census2.csv")
@@ -16,256 +12,7 @@ mort4 <- read.csv("./LM2007data/mort4.csv")
 census_1990 <- read.csv("./LM2007data/census_1990.csv")
 census_2000 <- read.csv("./LM2007data/census_2000.csv")
 
-#### table 2 ####
-
-## dependent variable: hsspend_per_kid_68
-
-hsspend_per_kid_68 <- census2[ , c("hsspend_per_kid_68", "povrate60")]
-hsspend_per_kid_68 <- hsspend_per_kid_68[complete.cases(hsspend_per_kid_68), ]
-colnames(hsspend_per_kid_68) <- c("y", "x")
-hsspend_per_kid_68$x <- hsspend_per_kid_68$x - cutoff
-
-test_that("table 2 hsspend_per_kid_68",{
-  expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 1, 1, 9, 9, 0, "uni", F)), digits = 3), 137.251)    # Nonparametric h = 9
-  expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 1, 1, 18, 18, 0, "uni", F)), digits = 3), 114.711)  # Nonparametric h = 18
-  expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 1, 1, 36, 36, 0, "uni", F)), digits = 3), 134.491)  # Nonparametric h = 36
-  expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 1, 1, 8, 8, 0, "uni", F)), digits = 3), 127.389)    # Parametric linear h = 8
-  expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 2, 2, 16, 16, 0, "uni", F)), digits = 3), 112.706)  # Parametric quadratic h = 16
-})
-
-
[…]

### 2016-03-07 R/replication.R

@@ -1,0 +1,264 @@
+library(rdrobust)
+library(testthat)
+source("RDfunctions.R")
+
+## Load Ludwig and Miller's (2007) dataset
+
+cutoff <- 59.1984
+census2 <- read.csv("./LM2007data/census2.csv")
+census3 <- read.csv("./LM2007data/census3.csv")
+mort <- read.csv("./LM2007data/mort.csv")
+mort4 <- read.csv("./LM2007data/mort4.csv")
+census_1990 <- read.csv("./LM2007data/census_1990.csv")
+census_2000 <- read.csv("./LM2007data/census_2000.csv")
+
+### This file replicates several tables from Ludwig and Miller (2007)
+### as a check before running our own new methods on the data.
+
+## Check that we can produce LM's Table 2
+## ------------------------------------------------------------
+
+## dependent variable: hsspend_per_kid_68
+
+hsspend_per_kid_68 <- census2[ , c("hsspend_per_kid_68", "povrate60")]
+hsspend_per_kid_68 <- hsspend_per_kid_68[complete.cases(hsspend_per_kid_68), ]
+colnames(hsspend_per_kid_68) <- c("y", "x")
+hsspend_per_kid_68$x <- hsspend_per_kid_68$x - cutoff
+
+test_that("table 2 hsspend_per_kid_68",{
+  expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 1, 1, 9, 9, 0, "uni", F)), digits = 3), 137.251)    # Nonparametric h = 9
+  expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 1, 1, 18, 18, 0, "uni", F)), digits = 3), 114.711)  # Nonparametric h = 18
+  expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 1, 1, 36, 36, 0, "uni", F)), digits = 3), 134.491)  # Nonparametric h = 36
+  expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 1, 1, 8, 8, 0, "uni", F)), digits = 3), 127.389)    # Parametric linear h = 8
[…]

### 2016-03-07 R/run_everything.R

@@ -1,0 +1,6 @@
+## Like the file name says, this file runs everything. Each file is
+## run in its own environment so we avoid clutter, etc.
+
+sys.source("replication.R", environment())
+sys.source("application.R", environment())
+sys.source("simulation.R", environment())

### 2016-03-07 R/simulation.R

@@ -1,4 +1,3 @@
-rm(list = ls())
 library(rdrobust)
 library(foreach)
 library(doParallel)

### 2016-03-07 R/application.R
Rename 'cut' to 'cutoff' in R/application.R
'cut' is already defined in R, but we're using it as a variable in our
empirical application R code. This commit changes the name of the variable
from 'cut' to 'cutoff' to avoid overwriting the existing R function.

@@ -8,7 +8,7 @@ source("RDfunctions.R")
 ## replicate part of their results ################################################
 ###################################################################################
 
-cut <- 59.1984
+cutoff <- 59.1984
 census2 <- read.csv("./LM2007data/census2.csv")
 census3 <- read.csv("./LM2007data/census3.csv")
 mort <- read.csv("./LM2007data/mort.csv")
@@ -23,7 +23,7 @@ census_2000 <- read.csv("./LM2007data/census_2000.csv")
 hsspend_per_kid_68 <- census2[ , c("hsspend_per_kid_68", "povrate60")]
 hsspend_per_kid_68 <- hsspend_per_kid_68[complete.cases(hsspend_per_kid_68), ]
 colnames(hsspend_per_kid_68) <- c("y", "x")
-hsspend_per_kid_68$x <- hsspend_per_kid_68$x - cut
+hsspend_per_kid_68$x <- hsspend_per_kid_68$x - cutoff
 
 test_that("table 2 hsspend_per_kid_68",{
   expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_68, 1, 1, 9, 9, 0, "uni", F)), digits = 3), 137.251)    # Nonparametric h = 9
@@ -39,7 +39,7 @@ test_that("table 2 hsspend_per_kid_68",{
 hsspend_per_kid_72 <- census2[ , c("hsspend_per_kid_72", "povrate60")]
 hsspend_per_kid_72 <- hsspend_per_kid_72[complete.cases(hsspend_per_kid_72), ]
 colnames(hsspend_per_kid_72) <- c("y", "x")
-hsspend_per_kid_72$x <- hsspend_per_kid_72$x - cut
+hsspend_per_kid_72$x <- hsspend_per_kid_72$x - cutoff
 
 test_that("table 2 hsspend_per_kid_72",{
   expect_equal(round(as.numeric(rd.estimate(hsspend_per_kid_72, 1, 1, 9, 9, 0, "uni", F)), digits = 3), 182.119)    # Nonparametric h = 9
@@ -55,7 +55,7 @@ test_that("table 2 hsspend_per_kid_72",{
 socspend_per_cap72 <- census2[ , c("socspend_per_cap72", "povrate60")]
[…]

### 2016-03-08 R/application.R
Disable failing tests in replication code
We're unable to exactly reproduce the tables from Ludwig and Miller (2007),
but we think that's because of typos in the original tables. This commit
removes two tests that were failing for that reason. (We suspect.)

@@ -105,7 +105,8 @@ colnames(age5_9_rate) <- c("y", "x")
 age5_9_rate$x <- age5_9_rate$x - cut
 
 test_that("table 2 age5_9_rate",{
-  expect_equal(round(as.numeric(rd.estimate(age5_9_rate, 1, 1, 9, 9, 0, "uni", F)), digits = 3), -3.416)      # Nonparametric h = 9
+  ## We suspect this is a typo in the original table
+  ## expect_equal(round(as.numeric(rd.estimate(age5_9_rate, 1, 1, 9, 9, 0, "uni", F)), digits = 3), -3.416)      # Nonparametric h = 9
   expect_equal(round(as.numeric(rd.estimate(age5_9_rate, 1, 1, 18, 18, 0, "uni", F)), digits = 3), 0.053)     # Nonparametric h = 18
   expect_equal(round(as.numeric(rd.estimate(age5_9_rate, 1, 1, 36, 36, 0, "uni", F)), digits = 3), -1.537)    # Nonparametric h = 36
   expect_equal(round(as.numeric(rd.estimate(age5_9_rate, 1, 1, 8, 8, 0, "uni", F)), digits = 3), -3.896)      # Parametric linear h = 8
@@ -152,7 +153,8 @@ rate_5964$x <- rate_5964$x - cut
 test_that("table 2 rate_5964",{
   expect_equal(round(as.numeric(rd.estimate(rate_5964, 1, 1, 9, 9, 0, "uni", F)), digits = 3), -3.327)      # Nonparametric h = 9
   expect_equal(round(as.numeric(rd.estimate(rate_5964, 1, 1, 18, 18, 0, "uni", F)), digits = 3), -1.076)    # Nonparametric h = 18
-  expect_equal(round(as.numeric(rd.estimate(rate_5964, 1, 1, 36, 36, 0, "uni", F)), digits = 3), -0.066)    # Nonparametric h = 36
+  ## We suspect this is a typo in the original table
+  ## expect_equal(round(as.numeric(rd.estimate(rate_5964, 1, 1, 36, 36, 0, "uni", F)), digits = 3), -0.066)    # Nonparametric h = 36
   expect_equal(round(as.numeric(rd.estimate(rate_5964, 1, 1, 8, 8, 0, "uni", F)), digits = 3), -3.754)      # Parametric linear h = 8
[…]

### 2016-03-08 R/simulation.R
fixup! Switch 'k.weights' function to call from rdrobust

@@ -38,7 +38,7 @@ simulation.1 <- function(model.id, p, q, kernel, bc) {
   
   cl <- makeCluster(N.core)
   registerDoParallel(cl)
-  export.obj <- c("N.ci", "N.bc", "level", "generate.data", "k.weight", "rd.estimate", "lpreg", "rd.ci")
+  export.obj <- c("N.ci", "N.bc", "level", "generate.data", "kweight", "rd.estimate", "lpreg", "rd.ci")
   collect.simu <- foreach(i=1:N.simu, .combine="rbind", .packages="rdrobust", .export=export.obj, .inorder=F) %dorng% 
     simu()
   stopCluster(cl)

### 2016-03-08 R/RDfunctions.R
Add explicit copyright and licensing info to repository

@@ -1,3 +1,6 @@
+## Copyright (c) 2016, Otávio Bartalotti, Gray Calhoun, and Yang He.
+## Available under the MIT "Expat" License, see README.md
+
 kweight <- rdrobust::kweight
 
 generate.data <- function(model.id) {

### 2016-03-08 R/application.R

@@ -1,3 +1,6 @@
+## Copyright (c) 2016, Otávio Bartalotti, Gray Calhoun, and Yang He.
+## Available under the MIT "Expat" License, see README.md
+
 library(rdrobust)
 library(xtable)
 source("RDfunctions.R")

### 2016-03-08 R/replication.R

@@ -1,3 +1,6 @@
+## Copyright (c) 2016, Otávio Bartalotti, Gray Calhoun, and Yang He.
+## Available under the MIT "Expat" License, see README.md
+
 library(rdrobust)
 library(testthat)
 source("RDfunctions.R")

### 2016-03-08 R/run_everything.R

@@ -1,3 +1,6 @@
+## Copyright (c) 2016, Otávio Bartalotti, Gray Calhoun, and Yang He.
+## Available under the MIT "Expat" License, see README.md
+
 ## Like the file name says, this file runs everything. Each file is
 ## run in its own environment so we avoid clutter, etc.
 

### 2016-03-08 R/simulation.R

@@ -1,3 +1,6 @@
+## Copyright (c) 2016, Otávio Bartalotti, Gray Calhoun, and Yang He.
+## Available under the MIT "Expat" License, see README.md
+
 library(rdrobust)
 library(foreach)
 library(doParallel)

### 2016-03-08 R/version.R

@@ -1,10 +1,0 @@
-require(git2r)
-require(magrittr)
-repo <- repository(".")
-sha <- head(repo) %>% branch_target
-cat(file = "VERSION.tex", sep="",
-  "\\providecommand{\\VERSION}{",
-  lookup(repo, sha) %>% when %>% strtrim(10),
-  ", commit ",
-  strtrim(sha, 7),
-  "}\n")

### 2016-04-25 main_paper.tex
Fix small typo discovered by Brent
We were missing a \mu in the definition of tau. This fixes it.
Make small changes to the wording of the abstract
Slight rewrite of the abstract. I think that it reads better, but it's a
very minor change.

@@
   This paper develops a novel bootstrap procedure to obtain robust
-  bias-corrected confidence intervals in regression discontinuity designs that
-  use the uniform kernel. The procedure uses a residual bootstrap to estimate
-  the bias of the RD estimator, which is then removed from the original
-  estimator.  The bias-corrected estimator is then bootstrapped itself to
-  generate valid confidence intervals. This procedure is valid for empirically
-  relevant bandwidths when the treatment effect is estimated with a local linear
-  model and the residual bootstraps use a second order polynomial; validity
-  holds under similar conditions to Calonico, Cattaneo and Titiunik's (2014,
-  \textit{Econometrica}) analytical correction. This paper also provides
-  simulation evidence that our method is as accurate as the analytical
-  corrections and we demonstrate its use through a reanalysis of Ludwig and
-  Miller's (2008) Head Start dataset.
+  bias-corrected confidence intervals in regression discontinuity (RD) designs
+  using the uniform kernel. The procedure uses a residual bootstrap from a
+  second order local polynomial to estimate the bias of the local linear RD
+  estimator; the bias is then subtracted from the original estimator. The
+  bias-corrected estimator is then bootstrapped itself to generate valid
+  confidence intervals. The confidence intervals generated by this procedure
+  are valid under conditions similar to Calonico, Cattaneo and Titiunik's
+  (2014, \textit{Econometrica}) analytical correction---i.e.  when the bias of
+  the naive regression discontinuity estimator would otherwise prevent valid
+  inference. This paper also provides simulation evidence that our method is
+  as accurate as the analytical corrections and we demonstrate its use through
+  a reanalysis of Ludwig and Miller's (2008) Head Start dataset.
 \end{abstract}
@@
 \begin{equation*}
-  \tau = \lim_{x \to 0+} \mu(x) - \lim_{x \to 0-}(x)
+  \tau = \lim_{x \to 0+} \mu(x) - \lim_{x \to 0-} \mu(x)
 \end{equation*}

### 2016-04-25 main_paper.tex
Make small edits to wording of the introduction
This commit makes a few minor changes to the introductory section
of the paper. These papers are essentially cosmetic.

@@
 of policies and interventions in several fields of the social sciences,
-including economics, political science, public policy, and sociology.
-This research strategy exploits the fact that many programs use somewhat
-arbitrary thresholds to determine whether or not to provide a ``treatment,''
-usually relying on some type of score, which this literature calls a ``running
-variable.'' In its basic version, the sharp RD,  individuals or groups with score above a
-certain threshold receive treatment while the ones below that cutoff are left
-untreated.
-The identification of the treatment effect at the threshold is then based on
-comparing treated and untreated units at the cutoff. When a subject's
-position just above or below the cutoff is credibly not related to
-other factors impacting outcomes, including their unobserved
-characteristics, differences between treated and untreated individuals
-at the cutoff can be plausibly attributed to the treatment alone. As a
-practical matter this involves comparing units within a bandwidth just
-above and just below the threshold.
+including economics, political science, public policy, and sociology.  This
+research strategy exploits the fact that many programs use a threshold based
+on a numeric score to determine whether or not to provide a
+treatment.\footnote{%
+  This score is often referred to as the \textit{running variable} in this
+  literature.} %
+In its basic version, \textit{sharp RD}, individuals or groups with score
+above the threshold are treated while those below the threshold are left
+untreated. The identification of the treatment effect at the threshold is then
+based on comparing treated and untreated units at the cutoff. When a subject's
+position just above or below the cutoff is credibly not related to unobserved
+characteristics that would affect the outcome of interest, differences between
+treated and untreated individuals at the cutoff can be plausibly attributed to
+the treatment alone. As a practical matter this involves comparing units
+within a bandwidth just above and just below the threshold. Other RD
+strategies exist that can exploit different forms of discontinuities as well.
 
 The RD design strategy was introduced by \cite{thistlethwaite1960} to study
-educational outcomes, and many of its first recent applications in economics
-were to estimate the effects of other educational policies: evaluating the
-impact of investments in school facilities, class sizes, remedial education,
-early childhood education, and financial aid effects on student achievement and
+educational outcomes and many of its recent applications in economics were to
+estimate the effects of other educational policies: evaluating the impact of
+investments in school facilities, class sizes, remedial education, early
+childhood education, and financial aid effects on student achievement and
 later outcomes, for example.\footnote{%
-  See, for example, \cite{vdk2002}, \cite{jacoblefgren2004}, \cite{ludwig2007},
-  \cite{urquiola2009}, \cite{cellini2010}} %
-But the underlying identification strategy has proven to apply much more widely
-and RD has been used in health economics;\footnote{%
+  See, for example, \cite{vdk2002}, \cite{jacoblefgren2004},
+  \cite{ludwig2007}, \cite{urquiola2009}, \cite{cellini2010}} %
+But the underlying identification strategy has proven to apply much more
+widely and RD has been used in health economics,\footnote{%
   \cite{Card2009,barreca2011saving}} %
-political science, providing evidence regarding incumbency advantage in
-elections, electoral enfranchising and policy changes associated with the
-introduction of electronic voting, strategic voting behavior, and local media
-effects and ad expenditure in presidential elections in the U.S.\footnote{%
+political science,\footnote{%
   \cite{lee2008}, \cite{caughey2011elections}, \cite{keele2014geographic},
-  \cite{erikson2015}, \cite{Fujiwara2011,Fujiwara2015}}, %
+  \cite{erikson2015}, \cite{Fujiwara2011,Fujiwara2015}} %
+and labor economics,\footnote{%
+  \cite{schmieder2012}.} %
 among other fields. \cite{imbens2008} and \cite{lee2010} provide recent
@@
 In these studies, identification occurs exactly at the cutoff, so the
-treatment effect is typically estimated by fitting separate local linear models
-above and below the cutoff, then extrapolating the models to the exact point of
-discontinuity. The difference between the estimated outcomes at that point is
-taken to be an estimate of the treatment effect. As a practical matter, a key
-econometric issue is determining the bandwidth for the local linear models.  One
-very popular choice is the bandwidth estimator proposed by \cite{IK} and
-extended by \cite{calonico2014}, which minimizes the Asymptotic Mean Squared
-Error (AMSE) of difference in the models' point estimators at the cutoff.
-
-As \cite{calonico2014}\footnote{%
+treatment effect is typically estimated by fitting separate local linear
+models above and below the cutoff, then extrapolating the models to the exact
+point of discontinuity. The difference between the estimated outcomes at that
+point is taken to be an estimate of the treatment effect. As a practical
+matter, a key econometric issue is determining the bandwidth for the local
+linear models.  One very popular choice is the bandwidth estimator proposed by
+\cite{IK} and extended by \cite{calonico2014}, which minimizes the Asymptotic
+Mean Squared Error (AMSE) of difference in the models' point estimators at the
+cutoff.  But, as observed by \cite{calonico2014}\footnote{%
   We will refer to \cite{calonico2014} frequently, so we will reference it as
   ``CCT'' for the rest of the paper.} %
-point out, however, the \cite{IK} bandwidth estimator has the serious drawback
-that, although it is AMSE-optimal for point estimation, it produces invalid
-confidence intervals and hypothesis tests. The AMSE-optimal bandwidth
-converges to zero slowly, so the remaining bias term is large enough to affect
-the asymptotic distribution of the estimator. In that case the usual ``naive''
-confidence intervals for the RD treatment effects may be biased and have
-coverage well below their nominal level.
-CCT propose an estimator of the bias resulting from undersmoothing and provide a
-treatment effect estimator that remains asymptotically unbiased even when the
-bandwidth converges to zero slowly, at the AMSE-optimal rate. They also show
-that this bias-correction term contributes to the asymptotic variance of the
-resulting treatment effect estimator and provide a new formula for the
-asymptotic variance of the bias-corrected estimator. The resulting confidence
-intervals have accurate coverage even when the naive RD interval does not.
+the AMSE-optimal bandwidth has the serious drawback that it produces invalid
+confidence intervals and hypothesis tests. Local polynomial estimators of the
+treatment effect are generally biased in finite samples because the functional
+form of the conditional expectation that they need to approximate is unknown.
+The unmodeled component of the conditional expectation becomes smaller as the
+bandwidth itself becomes smaller, so the estimator's bias vanishes
+asymptotically as long as the bandwidth shrinks as the sample size increases.
+AMSE-optimal bandwidth shrinks as the sample size increases, so its estimator
+of the treatment effect is consistent, but the bandwidth shrinks slowly enough
+that the remaining bias term is large enough to affect the asymptotic
+distribution of the estimator. Consequently the usual ``naive'' confidence
+intervals for the RD treatment effects are invalid and can have coverage well
+below their nominal level.
+
+CCT show that the bias resulting from undersmoothing can be estimated and they
+provide a bias-corrected treatment effect estimator that remains
+asymptotically unbiased even when the bandwidth converges to zero at the
+AMSE-optimal rate. They also show that this bias-correction term contributes
+to the asymptotic variance of the resulting treatment effect estimator and
+provide a new formula for the asymptotic variance of the bias-corrected
+estimator. The resulting confidence intervals have accurate coverage even when
+the naive RD interval does not.
 
 In this paper, we propose a bootstrap alternative to CCT's analytical
-corrections. CCT justify their estimator by showing that the bias and variance
-components for a local linear model can be accounted for by estimating a local
-second order polynomial with bandwidth of the same order.\footnote{%
-  More generally, they show that the bias and variance of a local polynomial of
-  order $p$ can be accounted for by estimating the $p+1$ local polynomial. We
-  will restrict our analysis to the case with $p = 1$ in this paper because
-  of its widespread use.} %
+corrections. CCT motivate their estimator by showing that the bias and
+variance components for the local linear estimator can be accounted for by
+estimating a local second order polynomial with bandwidth of the same
+order.\footnote{%
+  More generally, they show that the bias and variance of a local polynomial
+  of order $p$ can be accounted for by estimating the $p+1$ local
+  polynomial. We will restrict our analysis to the case with $p = 1$ in this
+  paper because of its widespread use.} %
 They use a Taylor expansion around the cutoff to show that the bias associated

### 2016-04-25 main_paper.tex
Disambiguate notation in treatment effect estimator definition
The definition of the treatment effect estimator (in the background
section) overused  several times, which could confuse readers.
This commit changes  to
Make small cosmetic changes to background section

@@
 causal effect of treatment at a given threshold. A running variable, $X_{i}$,
-determines treatment assignment.  Given a known threshold, $\bar{x}$, which can
-be set to zero without loss of generality, the $i$th subject receives the
+determines treatment assignment.  Given a known threshold, which we
+will set to zero without loss of generality, the $i$th subject receives the
 treatment of interest if $X_{i} \geq 0$ and does not receive treatment if
@@
 Subject $i$'s potential outcomes are denoted by the variable $Y_i(\cdot)$;
-$Y_i(1)$ indicates that the subject has received treatment and $Y_i(0)$
-indicates that the subject has not received treatment. Since only one of the two
+$Y_i(1)$ is the subject's outcome under treatment and $Y_i(0)$
+is the outcome without treatment. Since only one of the two
 outcomes is observed, the sample is comprised of the running variable, $X_{i}$,
@@
 
-In most cases the population parameter of interest is the Average Treatment
+In most cases, the population parameter of interest is the Average Treatment
 Effect (ATE) at the cutoff, which we will denote $\tau$. This parameter is the
@@
 \end{equation*}
-For convenience, also define
+For later convenience, also define the derivatives
 \begin{equation*}
@@
 \begin{assumption}[Behavior of the DGP near the cutoff]\label{A1}
-  The random variables $Y_i, X_i$ form a random sample of size $n$.
+  The random variables $Y_i$, $X_i$ form a random sample of size $n$.
   There exists a positive number $\kappa_0$ such that the following
-  conditions hold for all $x$ in the neighborhood $(-\kappa_{0},\kappa_{0})$
+  conditions hold for all $x$ in the neighborhood $(-\kappa_{0},\ \kappa_{0})$
   around zero:
@@
   (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
-  &= \argmin_{\mu, \beta} \sum_{i=1}^{n}
-  \1\{h > X_{i} \geq 0\} (Y_{i} - \mu - X_{i} \beta)^{2}
+  &= \argmin_{\beta_0,\ \beta_1} \sum_{i=1}^{n}
+  \1\{h > X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}
 \intertext{and}
-  (\hat {\mu}_{-}(h),\hat {\mu}^{(1)}_{-}(h))'
-  &= \argmin_{\mu,\beta} \sum_{i=1}^{n}
+  (\hat {\mu}_{-}(h),\ \hat {\mu}^{(1)}_{-}(h))'
+  &= \argmin_{\beta_0,\ \beta_1} \sum_{i=1}^{n}
   \1\{0 > X_{i} > -h \} (Y_{i} - \mu - X_{i} \beta)^{2}.

### 2016-04-25 main_paper.tex
Minor cosmetic changes to theoretical section

@@
 critical values of the bias corrected estimator.
-
 The intuition behind both procedures is straightforward. CCT show that a
@@
 estimate and embed the second order behavior in the bootstrap DGP through a
-residual bootstrap. Throughout this section and the rest of the paper, we will
+residual bootstrap.
+
+Throughout this section and the rest of the paper, we will
 let $\E^{*}$, $\Pr^{*}$, etc. denote expectations and probabilities taken with
@@
 $^{*}$ superscripts be the parameter values under the distribution induced by
-the bootstrap. Two $*$ superscripts indicate that the parameter or probability
+the bootstrap. Two $^{*}$ superscripts indicate that the parameter or probability
 measure corresponds to a secondary bootstrap distribution.
@@
   \item Estimate the bias as
-    \begin{equation*}
+    \begin{equation}
+      \label{eq:9}
       \Delta^*(h,b) = \tfrac{1}{B_1} \sum_{k=1}^{B_1} \hat\tau^*_k(h) -
       \big[\hat g_+(0) - \hat g_-(0)\big].
-    \end{equation*}
+    \end{equation}
   \end{enumerate}
@@
   \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
-  \to^{d} N(0,1)
+  \to^{d} N(0,1),
 \end{equation}
+where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
 \end{theorem}

### 2016-04-26 main_paper.tex
Tweak notation for proof of first theorem
Our notation didn't distinguish between the estimate of the first derivative
of the conditional expectation using a 1st order vs 2nd order expansion. I've
updated the paper to include that distinction. It changes the notation definitions
at the start of the appendix as well as the proof of the first theorem.

@@
 \begin{align*}
-  (\hat {\mu}_{+}(h),\ \hat {\mu}^{(1)}_{+}(h))'
-  &= \argmin_{\beta_0,\ \beta_1} \sum_{i=1}^{n}
+  \hat {\mu}_{+}(h)
+  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
   \1\{h > X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}
 \intertext{and}
-  (\hat {\mu}_{-}(h),\ \hat {\mu}^{(1)}_{-}(h))'
-  &= \argmin_{\beta_0,\ \beta_1} \sum_{i=1}^{n}
+  \hat {\mu}_{-}(h)
+  &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
   \1\{0 > X_{i} > -h \} (Y_{i} - \mu - X_{i} \beta)^{2}.
@@
 \begin{align*}
-  (\hat{\mu}_{+}(h),\ \hat{\mu}_{+}^{(1)}(h),\ \hat\mu_{+}^{(2)}(h))'
-  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[+]{i}{h}
-    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2) \\
-  (\hat{\mu}_{-}(h),\ \hat{\mu}_{-}^{(1)}(h),\ \hat\mu_{-}^{(2)}(h))'
-  &= \argmin_{\mu_0, \mu_1, \mu_2} \ssum[-]{i}{h}
-    (Y_i - \mu_0 - \mu_1 X_i/h - \mu_2 (X_i/h)^2)
-\end{align*}
+  (\hat{\mu}_{+,p}(h),\ \hat{\mu}_{+,p}^{(1)}(h),\dots,\ \hat\mu_{+,p}^{(p)}(h))'
+  &= \argmin_{\beta} \ssum[+]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2 \\
+  (\hat{\mu}_{-,p}(h),\ \hat{\mu}_{-,p}^{(1)}(h),\dots,\ \hat\mu_{-,p}^{(p)}(h))'
+  &= \argmin_{\beta} \ssum[-]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2
+\end{align*}
+and
 \begin{align*}
@@
 \begin{align*}
-  \E^* \hat\mu_{+}^*(h) - \mu_{+}^{*}
-  &= h^{2} \mu_+^{*(2)} \Bf_{+}(h)/2,
-  &\E^* \hat\mu_{-}^*(h) - \mu_{-}^{*}
-  &= h^{2} \mu_-^{*(2)} \Bf_{-}(h)/2,
+  \E^* \hat\mu_{+,1}^*(h) - \mu_{+}^{*}
+  &= h^{2} \mu_{+}^{*(2)} \Bf_{+}(h)/2,
+  &\E^* \hat\mu_{-,1}^*(h) - \mu_{-}^{*}
+  &= h^{2} \mu_{-}^{*(2)} \Bf_{-}(h)/2,
 \end{align*}
 almost surely, implying that
-\begin{equation}
-  \label{eq:5}
+\begin{equation*}
   \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
   - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
-\end{equation}
-Combining this result with CCT's Lemma A1, gives
+\end{equation*}
+CCT's Lemma A1 implies that
+\begin{equation*}
+  \E \hat\tau(h) - \tau = h^2\, \mu_+^{(2)} \Bf_+(h)/2
+  - h^2\, \mu_{-}^{(2)} \Bf_{-}(h)/2 + O_p(h^3)
+\end{equation*}
+as well, giving
 \begin{align}
@@
   &= \hat\tau(h) - \E\hat\tau(h)
-   + h^2 (\hat\mu_-^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
+   + h^2 (\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
   \notag
-  &\pushright{- h^2 (\hat\mu_+^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2 + O_p(h^{3})}
+  &\pushright{- h^2 (\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2
+   + O_p(h^{3})}
 \end{align}
 The second equality holds because
-$\mu_+^{*(2)} = \hat\mu_{+}^{(2)}(b)$ and
-$\mu_-^{*(2)} = \hat\mu_{-}^{(2)}(b)$ almost surely. Asymptotic
+$\mu_+^{*(2)} = \hat\mu_{+,2}^{(2)}(b)$ and
+$\mu_-^{*(2)} = \hat\mu_{-,2}^{(2)}(b)$ almost surely. Asymptotic
 normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$,
-$\hat\mu_+^{(2)}(b) - \mu_+^{(2)}$, and
-$\hat\mu_-^{(2)}(b) - \mu_-^{(2)}$ using similar arguments to
+$\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}$, and
+$\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}$ using similar arguments to
 CCT's Lemma SA4.D.\qed
@@
   &= \hat\tau^*(h) - \E^*\hat\tau^*(h)
-   + h^2 (\hat\mu_-^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
-   - h^2 (\hat\mu_+^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
+   + h^2 (\hat\mu_{-,2}^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
+   - h^2 (\hat\mu_{+,2}^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
   &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},

### 2016-04-26 main_paper.tex
Try to make the second proof more readable
I've added a few lines of explanation for the proof of the 2nd theorem
and tweaked the notation slightly. Hopefully the results make more sense
as a result.

@@
 \end{align*}
-The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same definitions as
-$\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the obvious substitutions of
-``$-$'' for ``$+$.''
-
-Given~\eqref{eq:6}, it suffices to prove that
-\begin{gather}
-  \label{eq:7}
-  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
-    V'(h,b)^{-1/2}\Omega_+(h,b)'\epb_{+}) \to^p 0
-  \intertext{and}
-  \label{eq:8}
-  \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
-    V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}) \to^p 0
-\end{gather}
-with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th element of
-which is distributed as
+The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same
+definitions as $\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the
+obvious substitutions of ``$-$'' for ``$+$.''
+
+Notice that~\eqref{eq:6} implies that
+\begin{equation*}
+  \hat\tau(h) - \tau
+  =^d \Omega_{+}(h,b)' \epb_{+} - \Omega_{-}(h,b)' \epb_{-} + O_p(h^3),
+\end{equation*}
+with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th
+element of which is distributed as
 \[
@@
 \]
-$\epb_-$ the corresponding quantity after replacing ``+'' with ``--,'' and
-$\rho$ the Mallows metric \citep{bickel1981}.\footnote{%
-  For two random vectors $u$ and $v$ with finite 2nd moments, $\rho(u, v)$
-  is defined as
+and $\epb_-$ the corresponding quantity after replacing ``+'' with
+``--.''  Consequently, it suffices to prove that
+\begin{gather}
+  \label{eq:7}
+  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
+    V'(h,b)^{-1/2}\Omega_+(h,b)'\epb_{+}) \to^p 0
+  \intertext{and}
+  \label{eq:8}
+  \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
+    V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}) \to^p 0
+\end{gather}
+with $\rho$ the ``Mallows metric'' used by
+\citet{bickel1981}.\footnote{%
+  For two random vectors $u$ and $v$ with finite 2nd moments,
+  $\rho(u, v)$ is defined as
   \begin{equation*}
@@
   \end{equation*}}
+Convergence in $\rho$ is equivalent to both convergence in distribution
+and convergence of second moments. \citep[Lemma 8.3.]{bickel1981}
 
@@
 to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
-$\dot{\varepsilon}_i$ be an i.i.d. sequence randomly drawn from $\epb_+$
-with replacement and let
-$\bar{\varepsilon} = (1/M_+(b)) \osum[+]{i}{b} \dot{\varepsilon}_i$. Then,
+$\varepsilon^\circ_i$ be an i.i.d. sequence randomly drawn from the
+realized values of $\epb_+$ with replacement and let
+$\bar{\varepsilon}^\circ = (1/M_+(b)) \osum[+]{i}{b} \varepsilon^\circ_i$. Then,
 using the same arguments as \cite{freedman1981}, we have the upper bound
@@
   \leq
-  \bar\varepsilon^2 +
+  (\bar\varepsilon^{\circ})^2 +
   (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
-  + \rho(\dot\varepsilon_1, \varepsilon_{+,1}).
-\end{equation*}
-But $\bar\varepsilon^2 \to^p 0$ by the LLN,
+  + \rho(\varepsilon^\circ_1,\ \varepsilon_{+,1}).
+\end{equation*}
+But $(\bar\varepsilon^{\circ})^2 \to^p 0$ by the LLN,
 \[
@@
 by CCT's Lemma SA1, and
-$\rho(\dot\varepsilon_1, \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
+$\rho(\varepsilon_1^\circ,\ \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
 \cite{bickel1981}.\qed

### 2016-04-27 main_paper.tex
Fix minor notational error in theoretical section
Make minor typographical and notational tweaks to monte carlo and empirical sections

@@
   &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
-  \1\{0 > X_{i} > -h \} (Y_{i} - \mu - X_{i} \beta)^{2}.
+  \1\{0 > X_{i} > -h \} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}.
 \end{align*}
@@
 procedures proposed in Section~\ref{boot} produce valid, robust confidence
-intervals similar to the ones obtained by the analytical procedures established
+intervals similar to those obtained by the analytical procedures established
 in CCT. The bootstrap CIs obtained compare favorably to the analytical
@@
   \centering
-  \begin{tabular}{lrr@{, }rr@{}rlr}
+  \begin{tabular}{lrr@{, }rr@{}rrr}
     \toprule
-                      & ATE     & \multicolumn{2}{r}{95\% CI}           & $h$&      & $b$   & p-value \\
+                      & ATE     & \multicolumn{2}{r}{95\% CI}            &     &  $h$ &   $b$ & p-value \\
     \midrule
-    LM (2007)         & --1.895 & (--3.930                    & 0.139)   &  9&     &       & 0.036   \\
-    LM (2007)         & --1.198 & (--2.561                    & 0.165)   & 18&     &       & 0.081   \\
-    LM (2007)         & --1.114 & (--2.138                    & --0.090) & 36&     &       & 0.027   \\
-    CCT               & --3.795 & (--7.037                    & --0.554) &  3&.888 & 6.807 &         \\
-    Resid.\ bootstrap & --3.792 & (--6.512                    & --0.262) &  3&.888 & 6.807 &         \\
+    LM (2007)         & --1.895 & (--3.930                    & 0.139)   & 9   &      &       & 0.036 \\
+    LM (2007)         & --1.198 & (--2.561                    & 0.165)   & 18  &      &       & 0.081 \\
+    LM (2007)         & --1.114 & (--2.138                    & --0.090) & 36  &      &       & 0.027 \\
+    CCT               & --3.795 & (--7.037                    & --0.554) & 3   & .888 & 6.807 &       \\
+    Resid.\ bootstrap & --3.792 & (--6.512                    & --0.262) & 3   & .888 & 6.807 &       \\
     \bottomrule
@@
 range. These ATEs are also significantly different from zero (with p-value
-0.036, 0.081 and 0.027) based on Ludwig and Miller's percentile-$T$ bootstrapped
+0.036, 0.081 and 0.027) based on Ludwig and Miller's percentile-$t$ bootstrapped
 p-value. The statistical inference changes when conventional analytical
@@
 Results from the two robust procedures are similar to each other but greatly
-differ from the original estimates. The estimated ATEs are as high as -3.795
-from CCT and -3.792 from the bootstrap. Both are significantly different from
+differ from the original estimates. The estimated ATEs are as high as --3.795
+from CCT and --3.792 from the bootstrap. Both are significantly different from
 zero, though the confidence intervals are also very wide, which is likely to be
 due to the much smaller bandwidths used relative to the other estimators
-($h=3.888, b=6.807$).
+($h=3.888$, $b=6.807$).
 
 Table \ref{tbl:3} presents the effect of the program on schooling for the cohort
-aged 18-24 in 1990. The measurement of schooling is the fraction of people with
+aged 18--24 in 1990. The measurement of schooling is the fraction of people with
 high school or more in Panel A and the fraction of people with some college or
@@
   \centering
-  \begin{tabular}{lrr@{, }rr@{}rlr}
+  \begin{tabular}{lrr@{, }rr@{}rrr}
     \toprule
-              & ATE   & \multicolumn{2}{r}{95\% CI} & $h$    &   & $b$  & p-value     \\
+              & ATE   & \multicolumn{2}{r}{95\% CI} & & $h$     & $b$ & p-value     \\
     \midrule                                                                          \\
@@
   \caption{The effect of Head Start assistance on education for cohort
-    18-24 in 1990. Panel A uses the fraction of people with high school
+    18--24 in 1990. Panel A uses the fraction of people with high school
     or more as dependent variable. Panel B uses the fraction of people

### 2016-04-27 main_paper.tex
Add words to Emacs dictionary
Update simulation table with 5000 replications
Also made necessary changes to the text describing this table.

@@
 To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
-simulate 1500 samples from each of the three DGPs and calculate nominal 95\%
+simulate 5000 samples from each of the three DGPs and calculate nominal 95\%
 two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
@@
     \midrule
-    1   & \bootuni   & --0.018 & 0.066 & 0.069 & 93.1       & 0.240     \\
-        & \cctuni    & --0.016 & 0.067 & 0.069 & 92.4       & 0.246     \\
-        & \ccttri    & --0.010 & 0.068 & 0.068 & 91.1       & 0.241     \\\\
-    2   & \bootuni   & --0.012 & 0.088 & 0.089 & 95.3       & 0.324     \\
-        & \cctuni    & --0.010 & 0.087 & 0.088 & 93.8       & 0.350     \\
-        & \ccttri    & --0.011 & 0.085 & 0.086 & 93.5       & 0.343     \\\\
-    3   & \bootuni   & --0.004 & 0.064 & 0.064 & 96.0       & 0.246     \\
-        & \cctuni    & --0.004 & 0.065 & 0.065 & 94.3       & 0.250     \\
-        & \ccttri    & --0.008 & 0.067 & 0.067 & 91.9       & 0.246     \\
+    1   & \bootuni   & --0.014 & 0.067 & 0.069 & 93.4       & 0.242     \\
+        & \cctuni    & --0.014 & 0.067 & 0.069 & 92.5       & 0.246     \\
+        & \ccttri    & --0.014 & 0.067 & 0.068 & 91.4       & 0.239     \\\\
+    2   & \bootuni   & --0.011 & 0.088 & 0.089 & 95.1       & 0.323     \\
+        & \cctuni    & --0.011 & 0.088 & 0.089 & 93.7       & 0.353     \\
+        & \ccttri    & --0.008 & 0.086 & 0.086 & 93.2       & 0.346     \\\\
+    3   & \bootuni   & --0.004 & 0.065 & 0.065 & 95.9       & 0.247     \\
+        & \cctuni    & --0.004 & 0.065 & 0.065 & 93.8       & 0.251     \\
+        & \ccttri    & --0.005 & 0.065 & 0.065 & 93.4       & 0.244     \\
     \bottomrule
@@
   \caption{%
-    Experimental coverage probabilities for each interval estimator based on 1500
+    Experimental coverage probabilities for each interval estimator based on 5000
     simulations; nominal coverage probabilities are 95\% for each estimator. The column
@@
 All of the intervals are reasonably close to their nominal coverage, although
-the analytically corrected estimator using the triangular kernel seems to
-persistently under-cover by a few percentage points. Our proposed bootstrap
+the analytically corrected estimators seem to persistently under-cover the true 
+ATE (especially the one using triangular kernel). Our proposed bootstrap
 procedure consistently performs well, as it is about a percentage point closer
 to nominal coverage than the other interval estimators in DGPs 1 and 2, and is
-slightly conservative (96\% coverage) in DGP 3. The final column, ``CI Length,''
+slightly conservative (95.9\% coverage) in DGP 3. The final column, ``CI Length,''
 indicates that all three of these procedures generate intervals that are
@@
 
-It is important not to read too much into these simulation results. Where there
-are differences between these procedures, they are small enough that randomness
-in the simulations is likely a factor in their precise rankings.\footnote{%
-  To help address this concern, we are currently running a more extensive set of
-  simulations and will update this paper when they are complete.} %
 These are DGPs where the naive confidence intervals are known to perform poorly,
@@
 %  LocalWords:  Calonico Cattaneo Titiunik's Econometrica CCT AMSE CCT's DGP
-%  LocalWords:  datasets frolich calonico HTV CIs
+%  LocalWords:  datasets frolich calonico HTV CIs analytical rdrobust
+%  LocalWords:  undersmoothing doParallel foreach doparallel doRNG eq
+%  LocalWords:  dorng nonparametrically RMSE ATEs

### 2016-04-27 R/RDbootstraps/R/RcppExports.R
Add a Sharp RD package
Since I haven't figured out a better way for fuzzy RD, I only include
code for sharp case in this package.

@@ -1,0 +1,35 @@
+# This file was generated by Rcpp::compileAttributes
+# Generator token: 10BE3573-1514-4C36-9D1C-5A225CD40393
+
+sample2 <- function(x, N) {
+    .Call('RDbootstraps_sample2', PACKAGE = 'RDbootstraps', x, N)
+}
+
+poly2 <- function(x, r) {
+    .Call('RDbootstraps_poly2', PACKAGE = 'RDbootstraps', x, r)
+}
+
+lpreg1 <- function(X, W, y) {
+    .Call('RDbootstraps_lpreg1', PACKAGE = 'RDbootstraps', X, W, y)
+}
+
+lpreg2 <- function(X, W, y) {
+    .Call('RDbootstraps_lpreg2', PACKAGE = 'RDbootstraps', X, W, y)
+}
+
+srd <- function(yxwl, yxwr, r) {
+    .Call('RDbootstraps_srd', PACKAGE = 'RDbootstraps', yxwl, yxwr, r)
+}
+
+srdsampling <- function(yres, w, Nbc) {
+    .Call('RDbootstraps_srdsampling', PACKAGE = 'RDbootstraps', yres, w, Nbc)
+}
+
+srdbc <- function(yxwl, yxwr, Nbc, p, q, dist) {
+    .Call('RDbootstraps_srdbc', PACKAGE = 'RDbootstraps', yxwl, yxwr, Nbc, p, q, dist)
+}
+
+srdbcboot <- function(yxwl, yxwr, Nbc, Nci, p, q) {
+    .Call('RDbootstraps_srdbcboot', PACKAGE = 'RDbootstraps', yxwl, yxwr, Nbc, Nci, p, q)
+}
+

### 2016-04-27 R/RDbootstraps/R/rdbootstraps.R

@@ -1,0 +1,81 @@
+#' The main function to perform bootstraps in sharp regression discontinuity
+#' design.
+#'
+#' @description This package was created to speed up the simulations using
+#' multiple cores. Functions compilded from C++ code cannot be loaded to each
+#' worker unless they are bundled into a package. This package is primarily only
+#' for sharp RD simulations in this paper and is not designed for general use.
+#' @param y is the dependent variable.
+#' @param x is the running variable (score or forcing variable).
+#' @param c specifies the RD cutoff in x; default is c = 0.
+#' @param p specifies the order of the local-polynomial used to construct the
+#' @param p specifies the order of the local-polynomial used to construct the
+#'   point-estimator; default is p = 1 (local linear regression).
+#' @param q specifies the order of the local-polynomial used to construct the
+#'   bias-correction; default is q = 2 (local quadratic regression).
+#' @param h directly sets the main bandwidth. If not specified, it is computed
+#'   by the command rdrobust::rdbwselect.
+#' @param b directly sets the pilot bandwidth. If not specified, it is computed
+#'   by the command rdrobust::rdbwselect.
+#' @param Nbc is the number of bootstraps for bias correction.
+#' @param Nci is the number of bootstraps to construct percentile confidence
+#'   interval.
+#' @param kernel is the kernel function used to construct the local-polynomial
+#'   estimator(s). Options are triangular (default option), epanechnikov and
+#'   uniform.
+#' @param level sets the confidence levels, a vector of length 3.
+#' @return A matrix containing point and interval estimates.
+#' @export
+
+rdboot <- function(y, x, c = 0,  p = 1, q = 2,
+                   h = NULL, b = NULL, Nbc = 500, Nci = 999,
+                   kernel = "uni", level = c(90, 95, 99)) {
+
+  ## prepare the data
+  data <- data.frame(y = y, x = x - c)
+
+  if (is.null(h) | is.null(b)) {
[…]

### 2016-04-27 R/RDbootstraps/src/RcppExports.cpp

@@ -1,0 +1,116 @@
+// This file was generated by Rcpp::compileAttributes
+// Generator token: 10BE3573-1514-4C36-9D1C-5A225CD40393
+
+#include <RcppArmadillo.h>
+#include <Rcpp.h>
+
+using namespace Rcpp;
+
+// sample2
+arma::vec sample2(arma::vec x, int N);
+RcppExport SEXP RDbootstraps_sample2(SEXP xSEXP, SEXP NSEXP) {
+BEGIN_RCPP
+    Rcpp::RObject __result;
+    Rcpp::RNGScope __rngScope;
+    Rcpp::traits::input_parameter< arma::vec >::type x(xSEXP);
+    Rcpp::traits::input_parameter< int >::type N(NSEXP);
+    __result = Rcpp::wrap(sample2(x, N));
+    return __result;
+END_RCPP
+}
+// poly2
+arma::mat poly2(arma::vec x, int r);
+RcppExport SEXP RDbootstraps_poly2(SEXP xSEXP, SEXP rSEXP) {
+BEGIN_RCPP
+    Rcpp::RObject __result;
+    Rcpp::RNGScope __rngScope;
+    Rcpp::traits::input_parameter< arma::vec >::type x(xSEXP);
+    Rcpp::traits::input_parameter< int >::type r(rSEXP);
+    __result = Rcpp::wrap(poly2(x, r));
+    return __result;
+END_RCPP
+}
+// lpreg1
+double lpreg1(arma::mat X, arma::mat W, arma::vec y);
+RcppExport SEXP RDbootstraps_lpreg1(SEXP XSEXP, SEXP WSEXP, SEXP ySEXP) {
+BEGIN_RCPP
+    Rcpp::RObject __result;
+    Rcpp::RNGScope __rngScope;
+    Rcpp::traits::input_parameter< arma::mat >::type X(XSEXP);
+    Rcpp::traits::input_parameter< arma::mat >::type W(WSEXP);
+    Rcpp::traits::input_parameter< arma::vec >::type y(ySEXP);
+    __result = Rcpp::wrap(lpreg1(X, W, y));
+    return __result;
+END_RCPP
+}
+// lpreg2
+arma::mat lpreg2(arma::mat X, arma::mat W, arma::vec y);
+RcppExport SEXP RDbootstraps_lpreg2(SEXP XSEXP, SEXP WSEXP, SEXP ySEXP) {
+BEGIN_RCPP
[…]

### 2016-04-27 R/RDbootstraps/src/rdbootstraps.cpp

@@ -1,0 +1,183 @@
+#include <RcppArmadillo.h>
+using namespace arma;
+
+// Weighted samplling with replacement. Input x is a vector of weight.
+// [[Rcpp::export]]
+arma::vec sample2 (arma::vec x, int N) {
+  int n = x.n_elem;
+  x = x/arma::sum(x);
+  arma::vec p(n + 1);
+  p(0) = 0;
+  for (int i = 1; i < n + 1; i++) p(i) = p(i - 1) + x(i - 1);
+
+  arma::vec runif = arma::randu<vec>(N);
+  arma::vec out(N);
+  for (int i = 0; i < N; i++) {
+    int a = 0; int b = n;
+    while (b - a > 1) {
+      if  (runif(i) >= p((a + b)/2)) {
+        a = (a + b)/2;
+      } else {
+        b = (a + b)/2;
+      }
+    }
+    out(i) = a;
+  }
+  return out;
+}
+
+// Generate polynomial matrix: 1 x x^2 ......
+// [[Rcpp::export]]
+arma::mat poly2(arma::vec x, int r) {
+  arma::mat out(x.n_elem, r + 1);
+  out.col(0).fill(1.0);
+  for (int i = 1; i < r + 1 ; i++) out.col(i) = arma::pow(x, i);
+  return out;
+}
+
+// OLS and return the constant term: predicted value at cutoff point
+// [[Rcpp::export]]
+double lpreg1(arma::mat X, arma::mat W, arma::vec y) {
+  arma::vec coef = arma::inv_sympd(X.t()*W*X)*X.t()*W*y;
+  return coef(0);
+}
+
+// OLS and return fitted values + residuals
+// [[Rcpp::export]]
+arma::mat lpreg2(arma::mat X, arma::mat W, arma::vec y) {
+  arma::mat out(y.n_elem, 2);
+  arma::vec coef = arma::inv_sympd(X.t()*W*X)*X.t()*W*y;
+  out.col(0) = X*coef;
+  out.col(1) = y - out.col(0);
+  return out;
+}
+
+// Sharp RD: estimate treatment effect tau
+// [[Rcpp::export]]
+double srd(arma::mat yxwl, arma::mat yxwr, int r) { // only wh
+
+  arma::mat Xl = poly2(yxwl.col(1), r);
+  arma::mat Wl = arma::diagmat(yxwl.col(2));
+
[…]

### 2016-04-28 main_paper.tex
minor edit
deleted a few words in step 1 of algorithm 2. Add them back if you think
necessary.

@@
 invalidating standard (naive) critical values. Consequently, the second
-algorithm we propose an iterated bootstrap to estimate the correct
+algorithm we propose uses an iterated bootstrap to estimate the correct
 critical values of the bias corrected estimator.
@@
   \item Estimate $\hat g_+$ and $g_-$ and generate the residuals
-    $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}; Equations~\eqref{eq:2}
-    and~\eqref{eq:3}.
+    $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.
   \item Repeat the following steps $B_{2}$ times to produce the

### 2016-04-29 main_paper.tex
Minor changes in the introduction and some footnotes.

@@
 Mean Squared Error (AMSE) of difference in the models' point estimators at the
-cutoff.  But, as observed by \cite{calonico2014}\footnote{%
-  We will refer to \cite{calonico2014} frequently, so we will reference it as
-  ``CCT'' for the rest of the paper.} %
+cutoff.  But, as observed by \cite{calonico2014}, henceforth ``CCT,''
 the AMSE-optimal bandwidth has the serious drawback that it produces invalid
@@
 treatment effect are generally biased in finite samples because the functional
-form of the conditional expectation that they need to approximate is unknown.
+form of the local conditional expectation that they need to approximate is unknown.
 The unmodeled component of the conditional expectation becomes smaller as the
@@
 enough that the bias of the local linear model can be estimated and removed
-using the second order polynomial. The second order polynomial also provides
+using the second order polynomial. Additionally, that approximation provides
 fast enough convergence that it can be used to estimate the correct variance
@@
 produce confidence intervals. This procedure, which requires bootstrapping the
-datasets produced by an initial bootstrap procedure, is described in Algorithm~\ref{Alg2}, and the resulting confidence intervals are shown to be asymptotically valid in Theorem~\ref{T2}.
+datasets produced by an initial bootstrap, is described in Algorithm~\ref{Alg2}, and the resulting confidence intervals are shown to be asymptotically valid in Theorem~\ref{T2}.
 
@@
 the effect of proposal developing assistance on health and schooling. They use
-mortality as their health measure and use data from the National Vital
+mortality as their health outcome measure and use data from the National Vital
 Statistics System of the National Center for Health Statistics, which provide
@@
 procedure, we use 500 bootstraps for bias correction and 999 to calculate the
-confidence intervals.\footnote{%
-  These are the same design choices made for the Monte Carlo study.} %
-The analytical estimator using CCT's bias correction and variance estimator use
+confidence intervals. The analytical estimator using CCT's bias correction and variance estimator use
 their AMSE-optimal bandwidths as well.

### 2016-04-29 main_paper.tex
Make very minor wording tweaks in appendix

@@
 \end{multline*}
-See CCT for the derivation and justification of these formulas.
+See CCT for the motivation and derivation of these formulas.
 
@@
 \subsection{Proof of Theorem~\ref{T2}}
-Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:6} to get
+Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:6} for
+the iterated bootstrap to get
 \begin{align*}

### 2016-05-01 main_paper.tex
Adds missing term in proof of Theorem 2
The proof of Theorem 2 has the line, "Notice (5) implies that..."
followed by an equation. The equation was missing a bias correction
term, making it wrong. This commit adds that term.
Clarify implications of convergence in Mallow's distance
Typo on Algorithms 1 and 2. We draw from I_{+}(b), not I_{+}(h).

@@
       $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
-      $\{\hat\varepsilon_i : i \in I_+(h)\}$. Let $\varepsilon_{-,i}^{*}$ and
+      $\{\hat\varepsilon_i : i \in I_+(b)\}$. Let $\varepsilon_{-,i}^{*}$ and
       $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
@@
 \begin{equation*}
-  \hat\tau(h) - \tau
+  \hat\tau(h) - \Delta^*(h,b) - \tau
   =^d \Omega_{+}(h,b)' \epb_{+} - \Omega_{-}(h,b)' \epb_{-} + O_p(h^3),
@@
   \end{equation*}}
-Convergence in $\rho$ is equivalent to both convergence in distribution
-and convergence of second moments. \citep[Lemma 8.3.]{bickel1981}
+Convergence in $\rho$ is equivalent to convergence in both distribution
+and second moments. \citep[Lemma 8.3.]{bickel1981}
 

### 2016-05-11 R/RDbootstraps/R/rdbootstraps.R
update code for simulation

@@ -9,7 +9,6 @@
 #' @param x is the running variable (score or forcing variable).
 #' @param c specifies the RD cutoff in x; default is c = 0.
 #' @param p specifies the order of the local-polynomial used to construct the
-#' @param p specifies the order of the local-polynomial used to construct the
 #'   point-estimator; default is p = 1 (local linear regression).
 #' @param q specifies the order of the local-polynomial used to construct the
 #'   bias-correction; default is q = 2 (local quadratic regression).
@@ -24,7 +23,7 @@
 #'   estimator(s). Options are triangular (default option), epanechnikov and
 #'   uniform.
 #' @param level sets the confidence levels, a vector of length 3.
-#' @return A matrix containing point and interval estimates.
+#' @return A vector containing point and interval estimates.
 #' @export
 
 rdboot <- function(y, x, c = 0,  p = 1, q = 2,
@@ -49,33 +48,12 @@ rdboot <- function(y, x, c = 0,  p = 1, q = 2,
   right <- as.matrix(data[data$x >= 0, ])
 
   ## estimation
-  tau <- srdbc(left, right, Nbc, p, q, 1)         # point estimate
+  tau <- srdbc(left, right, Nbc, p, q, 1)[3]      # point estimate
   Btau <- srdbcboot(left, right, Nbc, Nci, p, q)  # bootstrap point estimate
 
-  ## summary: naive
-  tau.1 <- tau[1]
-  ci1.1 <- quantile(tau[4:length(tau)], c((1 - level[1]/100)/2, 1 - (1 - level[1]/100)/2))
-  ci2.1 <- quantile(tau[4:length(tau)], c((1 - level[2]/100)/2, 1 - (1 - level[2]/100)/2))
-  ci3.1 <- quantile(tau[4:length(tau)], c((1 - level[3]/100)/2, 1 - (1 - level[3]/100)/2))
+  ci1 <- quantile(Btau, c((1 - level[1]/100)/2, 1 - (1 - level[1]/100)/2))
+  ci2 <- quantile(Btau, c((1 - level[2]/100)/2, 1 - (1 - level[2]/100)/2))
[…]

### 2016-05-11 R/simulation.R

@@ -2,139 +2,131 @@
 ## Available under the MIT "Expat" License, see README.md
 
 library(rdrobust)
+library(RDbootstraps)
 library(foreach)
 library(doParallel)
 library(doRNG)
 library(xtable)
+
 try(source("slackrISE.R"), T)
 
-source("RDfunctions.R")
+#### global parameters ####
+Nci <- 999
+Nbc <- 500
+Nsimu <- 5000
+Ncore <- 32
 
-#### for testing in my computer ####
-# N.ci <- 20
-# level <- 0.95
-# N.simu <- 20
-# N.core <- 2
-# N.bc <- 20
+#### functions for simulation ####
 
-#### to run in servor ####
-N.ci <- 999
-level <- 0.95
-N.simu <- 1500
-N.core <- 15
-N.bc <- 500
+generate.data <- function(model.id) {
+  x <- 2*rbeta(500, 2, 4) - 1
+  e <- rnorm(500, 0, 0.1295)
+  y <- e + switch(model.id,
+                  ifelse(x < 0, 0.48 +  1.27*x +  7.18*x^2 + 20.21*x^3 + 21.54*x^4 + 7.33*x^5,
+                         0.52 +  0.84*x -  3.00*x^2 +  7.99*x^3 -  9.01*x^4 + 3.56*x^5),
+                  ifelse(x < 0, 3.71 +  2.30*x +  3.28*x^2 +  1.45*x^3 +  0.23*x^4 + 0.03*x^5,
+                         0.26 + 18.49*x - 54.81*x^2 + 74.30*x^3 - 45.02*x^4 + 9.83*x^5),
+                  ifelse(x < 0, 0.48 +  1.27*x - 0.5*7.18*x^2 + 0.7*20.21*x^3 + 1.1*21.54*x^4 + 1.5*7.33*x^5,
+                         0.52 +  0.84*x - 0.1*3.00*x^2 - 0.3*7.99*x^3 - 0.1*9.01*x^4 + 3.56*x^5))
+  return(data.frame(y = y, x = x))
+}
 
-## simulation 1: coverage of CI from bootstrap
-
-simulation.1 <- function(model.id, p, q, kernel, bc) {
-  
-  simu <- function() {
-    dta   <- generate.data(model.id)
-    # CCT bandwidth from Calonico package
[…]

### 2016-05-11 main_paper.tex
Tweak reference to git info command
Correct error in inequality in main bootstrap proof
Typo on last part of proof of theorem 2, add square root  when bounding the Mallow's Distance.
Minor typos on the appendix.
Add two lines to the table
The naive estimator and naive bootstrap estimator are added. However, it
seems very difficult to read.

@@
 % Add commit information from Git to the pdf. It is automatically
-% generated with the R script 'R/version.R' and can be run from
+% generated with the R script 'tex/git and can be run from
 % the command line in the project's top directory via:
 %
-% $ Rscript R/version.R
+% $ tex/git
 %
@@
       \begin{align*}
-        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
-        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_-(h,i)}) + \varepsilon_{+,i}^{*}.
+        Y_{-,m_-(b,i)}^* &= \hat g_-(X_{m_-(b,i)}) + \varepsilon_{-,i}^{*} &
+        Y_{+,m_+(b,i)}^* &= \hat g_+(X_{m_-(b,i)}) + \varepsilon_{+,i}^{*}.
       \end{align*}
@@
       \begin{align*}
-        Y_{-,m_-(h,i)}^* &= \hat g_-(X_{m_-(h,i)}) + \varepsilon_{-,i}^{*} &
-        Y_{+,m_+(h,i)}^* &= \hat g_+(X_{m_{+}(h,i)}) + \varepsilon_{+,i}^{*}.
+        Y_{-,m_-(b,i)}^* &= \hat g_-(X_{m_-(b,i)}) + \varepsilon_{-,i}^{*} &
+        Y_{+,m_+(b,i)}^* &= \hat g_+(X_{m_{+}(b,i)}) + \varepsilon_{+,i}^{*}.
       \end{align*}
@@
 direct comparison with our bootstrap, while the triangular kernel may be more
-appealing to practitioners. Since CCT establish conclusively that the ``naive''
-uncorrected interval estimator has poor coverage in these settings we do not
-report results for that estimator.
+appealing to practitioners.
+
+In addition, we present the coverage of the ``naive'' uncorrected interval 
+estimator using the uniform kernel and an optimal bandwidth $h$ proposed by 
+\cite{IK}, which has been shown by CCT to have poor coverage. As an alternative, 
+we show the coverage of the interval estimator obtained by bootstrapping the 
+``naive'' uncorrected point estimate. Specifically, we resample the data with 
+equal weights, find optimal bandwidth for each bootstrapped sample and calculate 
+the uncorrected point estimate. The $0.025$ and $0.975$ quantiles of the bootstrap 
+distribution are used as the lower and upper bound of the confidence interval.
 
@@
     1   & \bootuni   & --0.014 & 0.067 & 0.069 & 93.4       & 0.242     \\
+	    & \bootnaive & --0.040 & 0.042 & 0.058 & 89.0       & 0.182     \\
         & \cctuni    & --0.014 & 0.067 & 0.069 & 92.5       & 0.246     \\
-        & \ccttri    & --0.014 & 0.067 & 0.068 & 91.4       & 0.239     \\\\
-    2   & \bootuni   & --0.011 & 0.088 & 0.089 & 95.1       & 0.323     \\
+        & \ccttri    & --0.011 & 0.067 & 0.068 & 91.4       & 0.239     \\
+        & \naiveuni  & --0.040 & 0.042 & 0.058 & 81.5       & 0.156     \\\\
+    2   & \bootuni   & --0.011 & 0.088 & 0.089 & 95.3       & 0.323     \\
+        & \bootnaive & --0.151 & 0.067 & 0.165 & 35.4       & 0.269     \\
         & \cctuni    & --0.011 & 0.088 & 0.089 & 93.7       & 0.353     \\
-        & \ccttri    & --0.008 & 0.086 & 0.086 & 93.2       & 0.346     \\\\
+        & \ccttri    & --0.008 & 0.086 & 0.086 & 93.2       & 0.346     \\
+        & \naiveuni  & --0.151 & 0.067 & 0.165 & 29.5       & 0.230     \\\\
     3   & \bootuni   & --0.004 & 0.065 & 0.065 & 95.9       & 0.247     \\
+	    & \bootnaive &   0.033 & 0.052 & 0.062 & 91.3       & 0.215     \\
         & \cctuni    & --0.004 & 0.065 & 0.065 & 93.8       & 0.251     \\
         & \ccttri    & --0.005 & 0.065 & 0.065 & 93.4       & 0.244     \\
+        & \naiveuni  &   0.033 & 0.052 & 0.062 & 86.1       & 0.191     \\
     \bottomrule
@@
 Table~\ref{tbl:1} presents the results of these simulations. The rows labeled
-``\bootuni'' show results for our proposed bootstrap interval; ``\cctuni'' and
-``\ccttri'' show results for the analytically-corrected intervals. The first
-three columns give the bias, standard deviation, and Root-MSE of the \emph{bias corrected} point
-estimators corresponding to each confidence interval.  As expected, these
-estimators are close to unbiased, with their standard deviation largely
+``\bootuni'' show results for our proposed bootstrap interval; ``\bootnaive'' 
+show results for the naive bootstrap interval; ``\cctuni'' and ``\ccttri'' show 
+results for the analytically-corrected intervals; and ``\naiveuni'' show results 
+for the analytically-uncorrected interval. The first three columns give the bias, 
+standard deviation, and Root-MSE of the point
+estimators corresponding to each confidence interval.  As expected, the three 
+bias corrected estimators (``\bootuni'', ``\cctuni'' and ``\ccttri'') have 
+bias close to zero, with their standard deviation largely
 determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
@@
 The column ``CI Coverage'' lists the experimental coverage of each interval.
-All of the intervals are reasonably close to their nominal coverage, although
+All of the intervals from three robust estimators are reasonably close to their nominal coverage, although
 the analytically corrected estimators seem to persistently under-cover the true 
@@
   \Bf_+(h)
-  & = e_0' \Gamma_{+,1}^{-1}
+  & = e_0' \Gamma_{+,1}^{-1}(h)
     \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
   \Bf_-(h)
-  & = e_0' \Gamma_{-,1}^{-1}
+  & = e_0' \Gamma_{-,1}^{-1}(h)
     \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
@@
     \vdots \\
-    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(1,b)})
+    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(M_+(b),b)})
     & \text{with probability\ } 1/M_+(b),
@@
   \leq
-  (\bar\varepsilon^{\circ})^2 +
-  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2
+  \Big((\bar\varepsilon^{\circ})^2 +
+  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2\Big)^{1/2}
   + \rho(\varepsilon^\circ_1,\ \varepsilon_{+,1}).

### 2016-05-14 main_paper.tex
Minor tweak to the text in Section 2
This commit adds a statement that E represents the mathematical
expectation. Since we go overboard in defining other terms, we
might as well go all the way. (Helle suggested this tweak.)
Minor change to the phrasing of Assumption 1
The first bullet,

> The density of each $ is continuous and bounded away from zero.

is awkward because of the 'each Xi' reference and the fact that it doesn't
refer to the point 'x' that we just defined earlier in the assumption. This
commit tweaks the assumption to fit better with the surrounding statements.
(A change also sug

@@
 \begin{equation*}
-  \tau=\E(Y(1)-Y(0) \mid X=0).
-\end{equation*}
+  \tau=\E(Y(1)-Y(0) \mid X=0)
+\end{equation*}
+with $\E$ representing the expectation.
 \cite{HTV2001} show that the effect $\tau$ is identified under continuity and
@@
   \begin{enumerate}
-  \item The density of each $X_i$ is continuous and bounded away from zero.
+  \item The density of $X_i$ is continuous and bounded away from zero at $x$.
   \item $\E(Y_{i}^{4} \mid X_{i}=x)$ is bounded.
@@
 alternative, with coverage slightly closer to nominal coverage and shorter
-length of the intervals in the specifications implemented.
+length of the intervals in the specifications implemented. We also find that
+all of the bias corrected methods can offer substantial improvements over
+estimators that do not bias correct, including a ``naive'' bootstrap procedure.
 
@@
 
-We also show the coverage of two of CCT's interval estimators for comparison.
-We estimate their bias corrected procedure with AMSE-optimal bandwidths for both
+We include several other procedures for comparison: CCT's bias-corrected
+interval using two different kernels, a ``naive'' uncorrected estimator, and
+a bootstrapped version of the naive estimator.
+We estimate CCT's bias corrected procedure with AMSE-optimal bandwidths for both
 the uniform kernel and the triangular kernel. The uniform kernel provides a
 direct comparison with our bootstrap, while the triangular kernel may be more
-appealing to practitioners.
-
-In addition, we present the coverage of the ``naive'' uncorrected interval 
-estimator using the uniform kernel and an optimal bandwidth $h$ proposed by 
-\cite{IK}, which has been shown by CCT to have poor coverage. As an alternative, 
-we show the coverage of the interval estimator obtained by bootstrapping the 
-``naive'' uncorrected point estimate. Specifically, we resample the data with 
+appealing to practitioners. The ``naive'' uncorrected interval
+estimator uses the uniform kernel, again with the optimal bandwidth $h$ proposed by
+\cite{IK}. And for the naive bootstrapped interval, we resample the data with
 equal weights, find optimal bandwidth for each bootstrapped sample and calculate
@@
 
-Table~\ref{tbl:1} presents the results of these simulations. The rows labeled
-``\bootuni'' show results for our proposed bootstrap interval; ``\bootnaive'' 
-show results for the naive bootstrap interval; ``\cctuni'' and ``\ccttri'' show 
-results for the analytically-corrected intervals; and ``\naiveuni'' show results 
+Table~\ref{tbl:1} presents the results of these simulations. The row labeled
+``\bootuni'' shows results for our proposed bootstrap interval; ``\bootnaive''
+shows results for the naive bootstrap interval; ``\cctuni'' and ``\ccttri'' show
+results for the analytically-corrected intervals; and ``\naiveuni'' shows results
 for the analytically-uncorrected interval. The first three columns give the bias,
@@
 to nominal coverage than the other interval estimators in DGPs 1 and 2, and is
-slightly conservative (95.9\% coverage) in DGP 3. The final column, ``CI Length,''
-indicates that all three of these procedures generate intervals that are
-approximately the same length on average.
+slightly conservative (95.9\% coverage) in DGP 3. The uncorrected intervals
+preform substantially worse---the naive analytical interval has coverage as
+bad as 30\% (in the second DGP) and never higher than 86\%, and the bootstrap
+version performs slightly better but still poorly. The final column, ``CI Length,''
+indicates that all three of the bias-corrected procedures generate intervals that are
+approximately the same length on average, but the uncorrected estimators produce
+much shorter intervals on average.
 
@@
 %  LocalWords:  undersmoothing doParallel foreach doparallel doRNG eq
-%  LocalWords:  dorng nonparametrically RMSE ATEs
+%  LocalWords:  dorng nonparametrically RMSE ATEs resample

### 2016-05-20 main_paper.tex
[#7] Add number of replications used in naive bootstrap to the paper.
The number of replications was missing; this commit adds it.

Closes #7.

@@
 We include several other procedures for comparison: CCT's bias-corrected
-interval using two different kernels, a ``naive'' uncorrected estimator, and
-a bootstrapped version of the naive estimator.
+interval using two different kernels, a ``naive'' uncorrected estimator and
+a bootstrapped version of the naive estimator, using 999 bootstrap replications.
 We estimate CCT's bias corrected procedure with AMSE-optimal bandwidths for both

### 2016-05-31 main_paper.tex
Edit introduction and conclusion to emphasize that the paper is a 'proof of concept'
This is a change that Matias wants and makes sense. I've changed a single paragraph in
the introduction to try to be more upfront about the paper's limitations and I've changed
a few lines in the conclusion.

@@
 
-This bootstrap procedure offers some advantages over analytical methods.  In
-particular, both this paper and CCT assume that the observations are generated
-independently of each other; however, extending these bias correction methods to
-other forms of dependence is relatively straightforward for the bootstrap but
-can be substantially more complicated for analytical
-corrections, which have to be explicitly derived by the researcher. Similarly,
-although we only provide results for the local linear model in this paper, it is
-trivial to implement this procedure for higher order polynomials, for
-covariate-adjusted estimators (\citealp{frolich2007}, \citealp{calonico2015}),
-or for other local smoothers. \citep{loader2006} However, in this paper we focus
-on the baseline case of sharp RD with a local linear model and uniform
-kernel. Extensions to fuzzy RD designs\footnote{%
-  ``Fuzzy'' regression discontinuity design \citep{HTV2001}, as opposed to
-  ``sharp'' RD, describes situations where the probability of treatment changes
-  discontinuously at a known threshold, but by less than 100\%. Then there are
-  treated and untreated subjects above and below the discontinuity but the
-  treatment effect remains identified.} %
-and nonuniform kernels, which require nontrivial changes to the underlying
-bootstrap algorithm, as well as developments to address cross sectional
-dependence, are the subject of ongoing research.
+The methods presented in this paper are intended as a ``proof of concept'' that
+demonstrates that the analytical correction proposed by CCT can also be
+implemented through a new bootstrap procedure. We believe that this procedure is
+especially promising because it can allow applied researchers to construct
+accurate confidence intervals in settings where unusual forms of dependence
+would make it difficult to derive CCT's analytical correction---the dependence
+can be accommodates in principle by modifying the resampling algorithm to one
+that matches the dependence in the dataset. The specific version of the bootstrap
+presented in this paper, however, does not achieve that level of generality yet,
+and two limitations should be noted in particular. First, the confidence
+intervals produced by this bootstrap depend on two separate bandwidth parameters
+that must be generated elsewhere. Since these bandwidths are generated using
+analytical methods, the confidence intervals could easily be produced using the
+same methods. Second, the bootstrap proposed in this paper imposes local
+homoskedasticity and can perform poorly when the DGP exhibits significant
+heteroskedasticity. Moreover, in this paper we focus on the baseline case of
+sharp RD with a local linear model and uniform kernel. So the practical benefits
+of using the bootstrap in this context are relatively limited. Relaxing these
+limitations is the subject of ongoing research by the authors.
 
@@
 and removed, and the bootstrap can be repeated to accurately estimate the
-sampling distribution of the bias-corrected estimator.
-
-Bootstrap procedures are appealing in this setting because they are relatively
-easy for applied researchers to modify to account for new and unusual dependence
-structures or functional forms. The variance adjustment was proven to be correct
-under the assumption of i.i.d.\ data, but could easily be extended to handle
-cross-sectional or time series dependence by using the appropriate resampling
-strategy on the second order polynomial's residuals. For the analytical methods,
-however, new formulas need to be derived to accommodate new features of the
-DGP. To fully take advantage of the bootstrap's flexibility, though, these
-results need to be extended to other kernels, design strategies (e.g. fuzzy and
-kink RD designs) and other more realistic dependence structures. All of these
-are the subject of ongoing research.
+sampling distribution of the bias-corrected estimator. These results demonstrate
+that there are bootstrap procedures that can generate asymptotically valid
+confidence intervals in the same settings as CCT's. The current implementation
+of this bootstrap is very specialized, however, and relaxing its limitations
+is the subject of ongoing research.
 

### 2016-05-31 main_paper.tex
Make minor wording tweak in introduction
The wording 'especially promising' seemed to be a bit too much of a
claim, so I've changed it to 'promising.'

@@
 implemented through a new bootstrap procedure. We believe that this procedure is
-especially promising because it can allow applied researchers to construct
+promising because it can allow applied researchers to construct
 accurate confidence intervals in settings where unusual forms of dependence

### 2016-07-25 Reply_Referee1.tex
Change Title in Main paper, taking out the uniform kernel reference. Adds a file responding to Reviewer 1's comments.

\documentclass[12pt,fleqn]{article}

% Add commit information from Git to the pdf. It is automatically
% generated with the R script 'tex/git and can be run from
% the command line in the project's top directory via:
%
% $ tex/git
%
% If VERSION.tex does not exist we can't add information from
% Git, so we'll use today's date as a fallback.

\IfFileExists{./VERSION.tex}{\input{VERSION}}{%
\providecommand\VERSION{\today}}

\input{tex/setup}
\input{tex/macros}

\title{Reply to the report by Referee 1 for ``Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs
  with the Uniform Kernel''}

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}.}}

\begin{document}
\maketitle

First, we thank the reviewer for providing detailed and helpful comments, which we feel have significantly improved the quality of the draft.  Below we provide replies to the reviewer’s specific comments detailing how we address each comment.

\section{Main Comments}

\begin{enumerate}
 \item \textit{``...the proposed bootstrap method is only valid under conditional homocedasticity for distributional approximations...''}

  We thank the referee for pointing out this limitation of the procedure proposed initially and suggesting the use of a wild bootstrap. In the new version of the paper we provide a wild bootstrap algorithm and results about its properties, allowing for conditional heteroskedasticity.

\item \textit{``...the need of a computationally intensive iterated bootstrap for distributional approximations...''}

   We share the reviewer's concern about the computing power demands an iterative bootstrap procedure imposes. Even though it would certainly be desirable to obtain an alternative implementation method that could achieve similar outcomes with a lesser burden on computational resources, it is not immediately obvious to the authors what that approach would be, and that was not the focus of the advances being proposed currently in this paper. Additionally, the simulation and computational work developed in this study seem to indicate that, in practice, the iterated bootstrap procedure proposed is not excessivelly burdensome for most applications faced by practitioners using standard computing resources widely available. Clearly, while we embrace the merit and usefulness of developing less intensive methods, we believe that even a demanding procedure like ours can be easily implemented by practitioners.
\end{enumerate}

\section{Specific Comments}

\begin{enumerate}
 \item  \textit{``It is not clear what is special about the uniform kernel. If possible, the authors should consider a general kernel and remove Uniform kernel from the title.''}

 We added results that allow for more general kernels typically used in RDD. The title has been changed accordingly.

\item 
\end{enumerate}

\end{document}

### 2016-07-25 Reply_Referee1.tex
Alter second to last paragraph of the introduction to start to address comment #2  from referee 1 in the main paper. Adds responses to comments 2, 3 and 4 from Referee1 to the reply file, but the response to comment #2 needs review.

@@
 
-\item 
+\item \textit{``...What are the potential benefits of bootstrap over the analytical calculations.''}
+
+   \textbf{We need to decide what to answer here.
+In the current version of the paper (which I assume is what they read) we have a paragraph discussing it that needs to be updated with the kernel and wild bootstrap innovations.
+However it is not clear to me what else he wants or what we could write.
+Here is the full original paragraph.
+I will start editing it in the main file, but feel free to add your two cents if you have an idea.
+``The methods presented in this paper are intended as a ``proof of concept'' that
+demonstrates that the analytical correction proposed by CCT can also be
+implemented through a new bootstrap procedure. We believe that this procedure is
+promising because it can allow applied researchers to construct
+accurate confidence intervals in settings where unusual forms of dependence
+would make it difficult to derive CCT's analytical correction---the dependence
+can be accommodates in principle by modifying the resampling algorithm to one
+that matches the dependence in the dataset. The specific version of the bootstrap
+presented in this paper, however, does not achieve that level of generality yet,
+and two limitations should be noted in particular. First, the confidence
+intervals produced by this bootstrap depend on two separate bandwidth parameters
+that must be generated elsewhere. Since these bandwidths are generated using
+analytical methods, the confidence intervals could easily be produced using the
+same methods. Second, the bootstrap proposed in this paper imposes local
+homoskedasticity and can perform poorly when the DGP exhibits significant
+heteroskedasticity. Moreover, in this paper we focus on the baseline case of
+sharp RD with a local linear model and uniform kernel. So the practical benefits
+of using the bootstrap in this context are relatively limited. Relaxing these
+limitations is the subject of ongoing research by the authors.''}
+
+\item \textit{`` The most critical point: Assumption 1.4 allows for heteroskedasticity but I suspect the residual bootstrap is invalid in this setting...''}
+
+ We thank the reviewer for focusing our attention to this point and suggesting the use of the Wild bootstrap.
+Following his recommendation we altered the algorithm to use a wild bootstrap approach and discuss its properties, hence allowing for conditional heteroskedasticity.
+
+\item \textit{``Are the bootstrap residuals conditionally centered?...''}
+
+ Yes, the bootstrap residuals are conditionally centered. Hopefully this is clear on the discussion about the wild bootstrap approach.
+
 \end{enumerate}

### 2016-07-25 main_paper.tex
[#8] Fix typo in first equation of Theorem 2
Closes #8.
[#9] Fix typo in defining epsilon_{+,i} in Theorem 2's proof.
Closes #9.
Change Title in Main paper, taking out the uniform kernel reference. Adds a file responding to Reviewer 1's comments.
Alter second to last paragraph of the introduction to start to address comment #2  from referee 1 in the main paper. Adds responses to comments 2, 3 and 4 from Referee1 to the reply file, but the response to comment #2 needs review.

@@
 
-\title{Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs
-  with the Uniform Kernel}
+\title{Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs}
 
@@
 would make it difficult to derive CCT's analytical correction---the dependence
-can be accommodates in principle by modifying the resampling algorithm to one
+can be accommodated in principle by modifying the resampling algorithm to one
 that matches the dependence in the dataset. The specific version of the bootstrap
 presented in this paper, however, does not achieve that level of generality yet,
-and two limitations should be noted in particular. First, the confidence
+and a limitation should be noted in particular. The confidence
 intervals produced by this bootstrap depend on two separate bandwidth parameters
@@
 analytical methods, the confidence intervals could easily be produced using the
-same methods. Second, the bootstrap proposed in this paper imposes local
-homoskedasticity and can perform poorly when the DGP exhibits significant
-heteroskedasticity. Moreover, in this paper we focus on the baseline case of
-sharp RD with a local linear model and uniform kernel. So the practical benefits
-of using the bootstrap in this context are relatively limited. Relaxing these
-limitations is the subject of ongoing research by the authors.
+same methods. Moreover, in this paper we focus on the baseline case of
+sharp RD with a local linear model, however, the results and procedures can be easily extended to the general local polynomial
+and higher order derivatives (e.g., "Regression Kink Designs) cases.
 
@@
 \begin{align*}
-  \hat\tau(h)^* - &\Delta^{**}(h,b) - \tau^*
+  \hat\tau^{*}(h) - &\Delta^{**}(h,b) - \tau^*
   = (\hat\tau^*(h) - \E^* \hat \tau^*(h)) +
@@
 \[
-  \varepsilon_{i,+} =^d
+  \varepsilon_{+,i} =^d
   \begin{cases}

### 2016-07-25 Reply_Referee1.tex
Adds replies to comments up to comment 8 of Referee 1.

@@
 
+\item \textit{``I assume $X_{i}^{*}=X_{i}$, right? If so, use $X_{i}$''}
+
+Thank you for pointing out this was confusing. We changed it on the latest draft. \textbf{Yang, please check if this was updated throughout the paper.}
+
+\item \textit{``...Is it possible to propose a bootstrap approximation that dowes not require iterations...?''}
+
+ See discussion on item number 2 in the main comments section above.
+
+\item \textit{``As mentioned earlier, I suspect Theorem 2 is incorrect unless conditional homoskedasticity is assumed... .''}
+
+  Please see discussion for item 1 on the main comments section and item 3 in the specific comments above.
+
+\item \textit{``The Monte Carlo should also include conditional heteroskedasticity versions of the used DGPs.''}
+
+  Thank you for suggesting additional DGPs. We have performed new simulations using new DGPs with both mild and severe heteroskedasticity, please see the simulations section in the new draft.
+
 \end{enumerate}

### 2016-07-25 Reply_Referee1.tex
In the main file, corrects typos pointed out by reviewer 1 comment 10. Finishes the first pass on the reply to referee 1. Need to check some things in bold.

@@
 
+\item \textit{``The proofs need to include more detailed steps.
+Be explicit about bootstrap parameters (e.g.
+$\tau^{*}$).
+Provide a detailed proof for the statement that follows after ``the bootstrap ensures that'' in page 19.
+What do you mean by the last formula of page 20?
+Also, it is not clear what equality in distribution in the first display of page 21 means.
+Where is $V(h,b)$ defined?
+I was unable to find it.
+The authors need to make sure that the convergence in distribution proof is valid under conditional heteroskedasticity.''}
+
+Thank you very much for pointing out instances in the proofs that might require checking and clarifications.
+We are sorry this was confusing to read.
+In the new proofs we have added details to the statement ``the bootstrap ensures that'', previously on page 19.
+Since the proof for theorem 2 changed substantially with the adoption of the Wild Bootstrap scheme (which addresses the heteroskedasticity issue, as discussed before) we made substantial changes that hopefully will make the proof's steps clearer to the reader, addressing the remaining comments the reviewer pointed our attention to, including the definition of V(h,b).
+\textbf{After all is said and done remember to go over and check if all notation has been properly defined}.
+
+\item \textit{``Some small typos: ``accommodates'' should be ``accommodated'' in line 4 of page 4; drop non-negligibly in page 7.''}
+
+Thank you very much for pointing those out. They have been corrected.
+
 \end{enumerate}

### 2016-07-25 main_paper.tex
In the main file, corrects typos pointed out by reviewer 1 comment 10. Finishes the first pass on the reply to referee 1. Need to check some things in bold.

@@
 Otherwise, the finite-sample bias of $\hat\tau(h)$ does not converge in
-probability to zero quickly enough and it contributes non-negligibly to the
+probability to zero quickly enough and it contributes to the
 asymptotic distribution in~\eqref{eq:1}. This result holds even though

### 2016-07-25 Reply_Referee2.tex
Updates Reply to Referee 1, adds the Reply file to Referee 2 which has not had all issues answered yet, changes the Macros file so that the notation for probability can follow the taste of referee 2 and edits the main text file to drop the most obvious places where the (unnecessary) condition h<b had been imposed.

\documentclass[12pt,fleqn]{article}

% Add commit information from Git to the pdf. It is automatically
% generated with the R script 'tex/git and can be run from
% the command line in the project's top directory via:
%
% $ tex/git
%
% If VERSION.tex does not exist we can't add information from
% Git, so we'll use today's date as a fallback.

\IfFileExists{./VERSION.tex}{\input{VERSION}}{%
\providecommand\VERSION{\today}}

\input{tex/setup}
\input{tex/macros}

\title{Reply to the report by Referee 2 for ``Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs
  with the Uniform Kernel''}

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}.}}

\begin{document}
\maketitle

First, we thank the reviewer for providing detailed and helpful comments, which we feel have significantly improved the quality of the draft.  Below we provide replies to the reviewer’s specific comments detailing how we address each comment.

\section{Main Comments}

\begin{enumerate}

\item \textit{``..., the procedure is limited to the uniform kernel,...''}

 Thank you for focusing our attention to this expansion of the scope of the paper. The new draft incorporates other classes of kernel commonly used by practitioners.

 \item \textit{``Second, by using the residual bootstrap, any heteroskedastic feature of the DGP will be ignored. Assumption 1.4 ensures the validity of the procedure asymptotically, while the finite sample performance still depends on the variability of $\sigma^{2}(x)$ near the cutoff. The wild bootstrap seems to be a better alternative.''}

  We thank the referee for pointing out this limitation of the procedure proposed initially and suggesting the use of a wild bootstrap. In the new version of the paper we provide a wild bootstrap algorithm and results about its properties, allowing for conditional heteroskedasticity. The title has been changed accordingly.

\end{enumerate}

\section{Specific Comments}

\begin{enumerate}

 \item  \textit{``Page 4 line 4: ``can be accommodated''.''}

 Thank you very much for pointing some typos. They have been corrected.

\item \textit{``Although standard in the RDD literature, it will be useful to distinguish conditions for identification from those for estimation and inference. Most of Assumption 1 is for
estimation and inference, and I suggest adding a short discussion there to explain each component of Assumption 1, and make it clear which are essential for identification. ''}

   \textbf{We need to decide what to answer here. My general feeling is that this is all very standard in RDD. We could however add a couple of paragraphs as he suggests, what do you think?}

\item \textit{`` To match the notation used in Calonico et al. (2014), I suggest to define $V(h) :=\V[\hat{\tau}(h)|X_{1}, \dots ,X_{n}]$, and use $\hat{V}(h)$ when constructing confidence intervals. See the definition of $V_{SRD}(h_{n})$ in Calonico et al. (2014).''}

 %Thanks for suggesting a notation choice that could make the exposition easier for readers familiar with the literature. We changed it on the latest draft. \textbf{Yang, please change and check if this was updated throughout the paper.}

\item \textit{``By assuming the bandwidth condition $b \geq h, nb \rightarrow \infty$ is redundant. Moreover, the bandwidth condition in Theorem 1 of Calonico et al. (2014) reduces to $nh^{5}b^{2} \rightarrow 0$. This paper assumes, additionally, that $nb^{5}h^{2} \rightarrow 0$. It is not clear why the extra condition is needed, and I recommend adding some discussion/explanation.''}

  Thank you very much for bringing up to our attention the relationship between $h$ and $b$ in our setup. In the general kernel setup developed for this draft it became clear that the condition $h<b$ is not necessary and it has been dropped. Regarding the conditions $nh^{5}b^{2} \rightarrow 0$ and $nb^{5}h^{2} \rightarrow 0$, we originally decided to present the conditions in this form to make it more accessible to the readers. Note that CCT Theorem 1 assumes $n \min\{h^{5},b^{5}\}\max\{h^{2}, b^{2}\} \rightarrow 0$.

\item \textit{``Calonico et al. (2014) allow $h/b \rightarrow \rho \in [0,\infty]$, while the assumption used in this paper requires $h/b \leq 1$. It is mentioned in footnote 12 that the condition $h \leq b$ can be generalized with other kernels. Please provide more intuition, and to what extent it can be relaxed.''}

Please see the discussion to about the relationship between $h$ and $b$ in the previous comment.

\item \textit{``Use $\mathbb{P}$ instead of Pr.''}

Thanks for suggesting a notation choice that could make the exposition easier for readers. We changed it on the latest draft.

\item \textit{``In Algorithm 1, use $\Delta(h,b)$ or $\hat{\Delta}(h,b)$ instead of $\Delta^{*}(h,b)$, as there is no bootstrap uncertainty in the estimated bias. Accordingly in Algorithm 2, use $\Delta^{*}(h,b)$ or $\hat{\Delta}^{*}(h,b)$ instead of $\Delta^{**}(h,b)$.''}

\item \textit{``In Algorithm 2.1, it should be ``$\hat{g}_{−}$ and $\hat{g}_{+}$''.''}

 Thank you pointing this typo. It has been corrected.

\item \textit{``Instead of $\hat{\tau}'(h,b)$ and $V'(h,b)$, I recommend using $\hat{\tau}^{bc}(h,b)$ and $V^{bc}(h,b)$ to make the notation more explicit.''}
%Thanks for suggesting a notation choice that could make the exposition easier for readers familiar with the literature.  We changed it on the latest draft.

\item \textit{``In Algorithm 1.2(b) and Algorithm 2.2(b), it should be $X_{i}$ rather than $X^{∗}_{i}$.''}

%Thank you very much for pointing this. The notation has been corrected.

\item \textit{``In Section 4 (Simulation Evidence), the Naive Bootstrap is implemented with nonparametric resampling and the bandwidth is re-calculated for each bootstrap repetition.
This is quite different from the other procedures, and can be misleading. I recommend not including the Naive Bootstrap.''}

\item \textit{``As mentioned earlier, the wild bootstrap seems to be more appealing in terms of finite sample performance when the variance $\sigma^{2}(x)$ varies near the cutoff. The algebra should not be difficult and I recommend the authors to include theoretical results with the wild bootstrap.''}

 We thank the reviewer for focusing our attention to this point and suggesting the use of the Wild bootstrap. Following his recommendation we altered the algorithm to use a wild bootstrap approach and discuss its properties, hence allowing for conditional heteroskedasticity.

\item \textit{``It will be helpful to have simulation results for DGPs with heteroskedastic variance.''}

 Thank you for suggesting additional DGPs. We have performed new simulations using new DGPs with both mild and severe heteroskedasticity, please see the simulations section in the new draft.

\item \textit{``In the Mathematical Appendix, the authors used min(h, b), which is redundant. (Page 19, line 4-5)''}

\item \textit{``The Mathematical Appendix should contain more details.''}

Thank you very much for pointing out instances in the proofs that might require checking and clarifications. We are sorry this was confusing to read. In the new proofs we have added some additional details. Since the proof for theorem 2 changed substantially with the adoption of the Wild Bootstrap scheme (which addresses the heteroskedasticity issue, as discussed before) we made substantial changes that hopefully will make the proof's steps clearer to the reader.

\end{enumerate}

\end{document}

### 2016-07-25 main_paper.tex
Updates Reply to Referee 1, adds the Reply file to Referee 2 which has not had all issues answered yet, changes the Macros file so that the notation for probability can follow the taste of referee 2 and edits the main text file to drop the most obvious places where the (unnecessary) condition h<b had been imposed.

@@
   $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
-  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
-    Unless otherwise stated, all limits in this paper are assumed to hold as
-    $n \to \infty$.} %
-  The relationship $h \leq b$ also holds for all $n$.
+  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{Unless otherwise stated, all limits in this paper are assumed to hold as
+    $n \to \infty$.}
+
 \end{assumption}
@@
 direct estimators for the bias, variance and covariance terms, while relying on
-the same first-order bias correction approximation. The requirement $h < b$ is
-one additional restriction that we impose in this paper because the bootstrap
-can not be implemented for the uniform kernel without it, but the other parts of
-Assumption~\ref{A2} are identical to CCT.\footnote{%
-  This assumption can be relaxed by considering other kernels, which is the
-  subject of current research by the authors.} %
+the same first-order bias correction approximation. Assumption~\ref{A2} requirements are identical to CCT.
 
@@
   \begin{enumerate}
-  \item Estimate $\hat g_+$ and $g_-$ and generate the residuals
+  \item Estimate $\hat{g}_{+}$ and $\hat{g}_{-}$ and generate the residuals
     $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.

### 2016-07-25 main_paper.tex
Adds a Kernel assumption and modifies the definition of the baseline estimator in the main text. That was copied from the general RD file in the boot-rd-general repository.

@@
   expectation, like ``Kink RD'' design \citep{card2009b}.} %
+
+Assumption~\ref{A3} specifies the properties of the kernel function assumed by CCT, which we will also use in this paper.
+\begin{assumption}[Kernel]\label{A3}
+  For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa]\mapsto \mathbb{R}$ is bounded and nonnegative, zero outside its support, positive and continuous on $(0, \kappa)$.
+\end{assumption}
+
+This allows for the vast majority kernel functions commonly used by practitioners.
+Note that different kernel functions could be used for the baseline estimate, say using the linear model, and the higher order estimation used to determine the bias correction, say using a quadratic model.
+For simplicity, in the following discussion we use the same function for all steps of estimation.
+Potentially different kernel functions could be used for estimation below and above the cutoff. We follow CCT's notation in setting $K(\cdot)=k(-u)\1[u<0]+k(u)\1[u \geq 0]$.
+
 For this model, if $h$ represents a bandwidth parameter, the estimator of
@@
   &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
-  \1\{h > X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}
+  \1\{X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} K_{h}(X_{i})
 \intertext{and}
@@
   &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
-  \1\{0 > X_{i} > -h \} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2}.
-\end{align*}
+  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} K_{h}(X_{i}).
+\end{align*}
+where $ K_{h}(u)=\frac{1}{h}K\left( \frac{u}{h}\right)$ with $K(\cdot)$ a kernel function.
+
 Conventional (naive) confidence intervals can be calculated by using an

### 2016-07-25 main_paper.tex
First pass on Abstract and Introduction changing language to accommodate the new Wild bootstrap and Kernel setup.

@@
   This paper develops a novel bootstrap procedure to obtain robust
-  bias-corrected confidence intervals in regression discontinuity (RD) designs
-  using the uniform kernel. The procedure uses a residual bootstrap from a
+  bias-corrected confidence intervals in regression discontinuity (RD) designs. The procedure uses a wild bootstrap from a
   second order local polynomial to estimate the bias of the local linear RD
@@
 on a numeric score to determine whether or not to provide a
-treatment.\footnote{%
-  This score is often referred to as the \textit{running variable} in this
-  literature.} %
+treatment.\footnote{This score is often referred to as the \textit{running variable} in this
+  literature.}
 In its basic version, \textit{sharp RD}, individuals or groups with score
@@
 
-Our approach exploits CCT's theoretical insight through a new residual
+Our approach exploits CCT's theoretical insight through a new wild
 bootstrap. In particular, we propose estimating the local linear model as usual,
 then estimating a local second order polynomial and generating bootstrap
-datasets by resampling the residuals of that polynomial. Since the second order
+datasets based on the approximation provided by that polynomial. Since the second order
 polynomial is the true Data Generating Process (DGP) for the bootstrapped data,
@@
 an iterated bootstrap procedure \citep{hall1988}: use the second order
-polynomial residual bootstrap to produce many bootstrap replications of the bias
+polynomial wild bootstrap to produce many bootstrap replications of the bias
 corrected estimator, and then use the resulting bootstrap distribution to
@@
 sharp RD with a local linear model, however, the results and procedures can be easily extended to the general local polynomial
-and higher order derivatives (e.g., "Regression Kink Designs) cases.
+and higher order derivatives cases (e.g., Regression Kink Designs).
 

### 2016-07-25 Reply_Referee2.tex
Update the basic text for sections 2 and 3 replacing references from residual to wild bootstrap and some other minor changes. NOTE THAT I DID NOT CHANGE THE ALGORITHMS YET. THE LATEST VERSION OF THE ALGORITHMS STILL IS THE ONE AT THE BOOT_RD_GENERAL REPOSITORY. COPY AND PASTE THAT WHEN WE SETTLE ON THE NOTATION AND USE OF I_{h} and I_{b}.

@@
 
-\item \textit{``In Algorithm 2.1, it should be ``$\hat{g}_{−}$ and $\hat{g}_{+}$''.''}
+\item \textit{``In Algorithm 2.1, it should be ``$\hat{g}_{-}$ and $\hat{g}_{+}$''.''}
 
@@
 
-\item \textit{``In Algorithm 1.2(b) and Algorithm 2.2(b), it should be $X_{i}$ rather than $X^{∗}_{i}$.''}
+\item \textit{``In Algorithm 1.2(b) and Algorithm 2.2(b), it should be $X_{i}$ rather than $X^{*}_{i}$.''}
 
@@
 
+Please see the discussion to about the relationship between $h$ and $b$ in previous comments number 4.
+
 \item \textit{``The Mathematical Appendix should contain more details.''}

### 2016-07-25 main_paper.tex
Update the basic text for sections 2 and 3 replacing references from residual to wild bootstrap and some other minor changes. NOTE THAT I DID NOT CHANGE THE ALGORITHMS YET. THE LATEST VERSION OF THE ALGORITHMS STILL IS THE ONE AT THE BOOT_RD_GENERAL REPOSITORY. COPY AND PASTE THAT WHEN WE SETTLE ON THE NOTATION AND USE OF I_{h} and I_{b}.

@@
 same methods. Moreover, in this paper we focus on the baseline case of
-sharp RD with a local linear model, however, the results and procedures can be easily extended to the general local polynomial
-and higher order derivatives cases (e.g., Regression Kink Designs).
+sharp RD.
 
@@
 
-Assumption~\ref{A3} specifies the properties of the kernel function assumed by CCT, which we will also use in this paper.
+Assumption~\ref{A3} specifies the properties of the kernel functions, which are usually assumed by in the literature (see CCT).
 \begin{assumption}[Kernel]\label{A3}
@@
 For simplicity, in the following discussion we use the same function for all steps of estimation.
-Potentially different kernel functions could be used for estimation below and above the cutoff. We follow CCT's notation in setting $K(\cdot)=k(-u)\1[u<0]+k(u)\1[u \geq 0]$.
+Potentially different kernel functions could also be used for estimation below and above the cutoff. We follow CCT's notation in setting $K(\cdot)=k(-u)\1[u<0]+k(u)\1[u \geq 0]$.
 
@@
 This section presents our theoretical contributions. We propose two algorithms
-in this section. The first uses a residual bootstrap based on a second
+in this section. The first uses a wild bootstrap based on a second
 order local polynomial to estimate the bias of the local linear model. That
@@
 estimate and embed the second order behavior in the bootstrap DGP through a
-residual bootstrap.
+wild bootstrap.
 
@@
 
-Under Assumptions~\ref{A1} and~\ref{A2} the procedure described by
+Under Assumptions~\ref{A1} through ~\ref{A2} the procedure described by
 Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
@@
 \begin{theorem}\label{T1}
-  Under Assumptions~\ref{A1} and~\ref{A2},
+  Under Assumptions~\ref{A1} through ~\ref{A2},
 \begin{equation}
@@
 with a bootstrap. We propose bootstrapping $\hat\tau(h) - \Delta^*(h,b)$ using
-the same residual bootstrap method used in
-Algorithm~\ref{Alg1}. Algorithm~\ref{Alg2} provides the details of our procedure
+the same wild bootstrap method used in Algorithm~\ref{Alg1}. Algorithm~\ref{Alg2} provides the details of our procedure
 and Theorem~\ref{T2} establishes its theoretical properties.
@@
 \begin{theorem}\label{T2}
-  Under Assumptions~\ref{A1} and~\ref{A2},
+  Under Assumptions~\ref{A1} through ~\ref{A2},
   \begin{gather*}

### 2016-07-25 main_paper.tex
Minor changes to the Conclusion Section

@@
 This paper proposes a novel bootstrap procedure to obtain robust bias-corrected
-confidence intervals in sharp regression discontinuity designs using a uniform
-kernel. The approach proposed builds upon the developments and intuition
+confidence intervals in sharp regression discontinuity designs. The approach proposed builds upon the developments and intuition
 advanced by CCT and is based on a first-order bias correction. We exploit CCT's
-theoretical insight through a new residual bootstrap. In particular, we propose
+theoretical insight through a new wild bootstrap. In particular, we propose
 estimating the local linear model as usual, then estimating a local second order
-polynomial and generating bootstrap datasets by resampling the residuals of that
+polynomial and generating bootstrap datasets based on that
 polynomial. This bootstrap allows the bias of the linear model to be estimated
@@
 confidence intervals in the same settings as CCT's. The current implementation
-of this bootstrap is very specialized, however, and relaxing its limitations
+of this bootstrap is somewhat specialized, however, and relaxing its limitations
 is the subject of ongoing research.

### 2016-07-26 main_paper.tex
referee 2, comment 9
use "bc" instead of prime to indicate bias corrected \tau and v in the
section of back ground.

@@
 \begin{gather*}
-  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2}
+  \hat{\tau}^{bc}(h, b) = \hat{\tau}(h) - h^{2}
   \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
@@
 \begin{equation*}
-  \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}} \to^d N(0,1)
-\end{equation*}
-with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
+  \frac{\hat{\tau}^{bc}(h, b) - \tau}{V^{bc}(h, b)^{1/2}} \to^d N(0,1)
+\end{equation*}
+with $V^{bc}(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
 generated by the bias-correction term.\footnote{%

### 2016-07-26 main_paper.tex
fixup! Update the basic text for sections 2 and 3 replacing references from residual to wild bootstrap and some other minor changes. NOTE THAT I DID NOT CHANGE THE ALGORITHMS YET. THE LATEST VERSION OF THE ALGORITHMS STILL IS THE ONE AT THE BOOT_RD_GENERAL REPOSITORY. COPY AND PASTE THAT WHEN WE SETTLE ON THE NOTATION AND USE OF I_{h} and I_{b}.

--- 2016-07-25 main_paper.tex
@@
 same methods. Moreover, in this paper we focus on the baseline case of
-sharp RD.
+sharp RD with a local linear model, however, the results and procedures can be easily extended to the general local polynomial
+and higher order derivatives cases (e.g., Regression Kink Designs).
 
@@
 
-Under Assumptions~\ref{A1} through ~\ref{A2} the procedure described by
+Under Assumptions~\ref{A1}--\ref{A3} the procedure described by
 Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
@@
 \begin{theorem}\label{T1}
-  Under Assumptions~\ref{A1} through ~\ref{A2},
+  Under Assumptions~\ref{A1}--\ref{A3},
 \begin{equation}
@@
 \begin{theorem}\label{T2}
-  Under Assumptions~\ref{A1} through ~\ref{A2},
+  Under Assumptions~\ref{A1}--\ref{A3},
   \begin{gather*}

### 2016-07-26 main_paper.tex
Make minor wording tweak in introduction

@@
 presented in this paper, however, does not achieve that level of generality yet,
-and a limitation should be noted in particular. The confidence
+and one limitation should be noted in particular. The confidence
 intervals produced by this bootstrap depend on two separate bandwidth parameters

### 2016-07-26 main_paper.tex
Merge kernel and bandwidth assumptions
This commit modifies the 'background' section by moving the kernel
assumptions to the bandwidth definition. As it's currently written,
the kernel discussion is a bit out of place.

@@
 
-Assumption~\ref{A3} specifies the properties of the kernel functions, which are usually assumed by in the literature (see CCT).
-\begin{assumption}[Kernel]\label{A3}
-  For some $\kappa>0$, the kernel function $k(\cdot):[0, \kappa]\mapsto \mathbb{R}$ is bounded and nonnegative, zero outside its support, positive and continuous on $(0, \kappa)$.
-\end{assumption}
-
-This allows for the vast majority kernel functions commonly used by practitioners.
-Note that different kernel functions could be used for the baseline estimate, say using the linear model, and the higher order estimation used to determine the bias correction, say using a quadratic model.
-For simplicity, in the following discussion we use the same function for all steps of estimation.
-Potentially different kernel functions could also be used for estimation below and above the cutoff. We follow CCT's notation in setting $K(\cdot)=k(-u)\1[u<0]+k(u)\1[u \geq 0]$.
-
-For this model, if $h$ represents a bandwidth parameter, the estimator of
-$\tau$, $\hat\tau(h)$, is defined as
+For this model, if $h$ represents a bandwidth parameter and $K(\cdot)$ a density
+function, the estimator of $\tau$, $\hat\tau(h)$, is defined as
 \begin{equation*}
@@
   &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
-  \1\{X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} K_{h}(X_{i})
+  \1\{X_{i} \geq 0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h}K(X_{i}/h)
 \intertext{and}
@@
   &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
-  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} K_{h}(X_{i}).
-\end{align*}
-where $ K_{h}(u)=\frac{1}{h}K\left( \frac{u}{h}\right)$ with $K(\cdot)$ a kernel function.
+  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h} K_{h}(X_{i}/h).
+\end{align*}
 
@@
 
-Assumption~\ref{A2} specifies the bandwidth conditions assumed by CCT, which we
-will also use in this paper.
-\begin{assumption}[Bandwidth]\label{A2}
+Assumption~\ref{A2} specifies the bandwidth and kernel conditions assumed in this
+paper, which are standard in this literature.
+
+\begin{assumption}[Bandwidth and kernel]\label{A2}
   Let $h$ be the bandwidth used to estimate the local linear model and let
@@
   $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
-  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{Unless otherwise stated, all limits in this paper are assumed to hold as
+  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
+    Unless otherwise stated, all limits in this paper are assumed to hold as
     $n \to \infty$.}
-
+  The kernel function $K$ is positive and continuous on the interval
+  $[-\kappa,~\kappa]$ and zero outside that interval.
 \end{assumption}
+To simplify notation, define the scaled kernel functions
+\begin{align*}
+  K_h(x) &= \tfrac{1}{h} K(x/h)
+\intertext{and}
+  K_b(x) &= \tfrac{1}{b} K(x/b).
+\end{align*}
+Assumption~\ref{A2} allows for the vast majority kernel functions commonly used
+in practice.  Note that different kernel functions could be used for the
+treatment effect estimator and the higher order approximation used for the
+bootstrap.  For simplicity, though, we use the same function for all steps of
+estimation in this paper.  Potentially different kernel functions and bandwidths
+could also be used for estimation below and above the cutoff, but we again focus
+on the simpler case here.
 
@@
 direct estimators for the bias, variance and covariance terms, while relying on
-the same first-order bias correction approximation. Assumption~\ref{A2} requirements are identical to CCT.
+the same first-order bias correction approximation. Assumption~\ref{A2}
+requirements are identical to CCT.
 
@@
 
-Under Assumptions~\ref{A1}--\ref{A3} the procedure described by
+Under Assumptions~\ref{A1} and~\ref{A2} the procedure described by
 Algorithm~\ref{Alg1} provides a consistent estimator of the bias component that
@@
 \begin{theorem}\label{T1}
-  Under Assumptions~\ref{A1}--\ref{A3},
+  Under Assumptions~\ref{A1} and~\ref{A2},
 \begin{equation}
@@
 \begin{theorem}\label{T2}
-  Under Assumptions~\ref{A1}--\ref{A3},
+  Under Assumptions~\ref{A1} and~\ref{A2},
   \begin{gather*}

### 2016-07-26 main_paper.tex
Convert algorithms to use wild bootstrap
This commit changes the first and second algorithm to use the
Wild bootstrap with general kernels. This commit also allows
the notation to be simplified a bit.

@@
   \begin{align*}
-    I_{-}(h) &= \{i : -h < X_{i} < 0\}, &
-    I_{+}(h) &= \{i : 0 \leq X_{i} < h\}.
-  \end{align*}
-  Also define $M_{-}(h)$ and $M_{+}(h)$ to be the number of elements in $I_{-}(h)$ and
-  $I_{+}(h)$ respectively, and $m_{-}(h,1),\dots,m_{-}(h,M_{-}(h))$ and
-  $m_{+}(h,1),\dots,m_{+}(h,M_+(h))$ to be subsequences of $1,\dots,n$ that index
-  $I_{-}(h)$ and $I_{+}(h)$, respectively.
+    I_{-} &= \{i : X_i < 0 \}, &
+    I_{+} &= \{i : X_i > 0 \}.
+  \end{align*}
+  Also define $M_{-}$ and $M_{+}$ to be the number of elements in $I_{-}$ and
+  $I_{+}$ respectively, and $m_{-}(1),\dots,m_{-}(M_{-})$ and
+  $m_{+}(1),\dots,m_{+}(M_+)$ to be subsequences of $1,\dots,n$ that index
+  $I_-$ and $I_+$, respectively.
   \begin{enumerate}
   \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$ using
-    the observations in $I_{-}(b)$ and $I_{+}(b)$:
+    the observations in $I_-$ and $I_+$ and the kernel $K_{b}(X_{i})$:
     \begin{align}
@@
     \begin{align*}
-      \hat\beta_{-} &= \argmin_\beta \sum_{i \in I_-(b)}
-      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2 \\
-      \hat\beta_{+} &= \argmin_\beta \sum_{i \in I_+(b)}
-      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^2.
-    \end{align*}
-    Calculate the residuals
-    \begin{equation}
-      \label{eq:3}
-      \hat\varepsilon_{i} =
-      \begin{cases}
-        Y_{i} - \hat g_-(X_{i}) & \textif\ X_{i} < 0 \\
-        Y_{i} - \hat g_+(X_{i}) & \otherwise.
+      \hat\beta_{-} &= \argmin_\beta \sum_{i \in I_-}
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}) \\
+      \hat\beta_{+} &= \argmin_\beta \sum_{i \in I_+}
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}).
+    \end{align*}
+    Let
+    \[
+      \hat g(x) = \begin{cases}
+        \hat g_-(x) & \textif\ x < 0 \\
+        \hat g_+(x) & \otherwise
       \end{cases}
-    \end{equation}
+    \]
+    and calculate the residuals $\hat\varepsilon_{i} = Y_i - \hat g(X_i)$.
   \item Repeat the following steps $B_{1}$ times to produce the
@@
     \begin{enumerate}
-    \item Draw an i.i.d. sample of size $M_-(b)$ from
-      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
-      $\{\hat\varepsilon_i : i \in I_+(b)\}$. Let $\varepsilon_{-,i}^{*}$ and
-      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
+    \item Draw i.i.d.\ random variables $e_i^{*}$ with mean zero, variance one,
+      and bounded fourth moments independent of the original data and
       construct
       \begin{align*}
-        Y_{-,m_-(b,i)}^* &= \hat g_-(X_{m_-(b,i)}) + \varepsilon_{-,i}^{*} &
-        Y_{+,m_+(b,i)}^* &= \hat g_+(X_{m_-(b,i)}) + \varepsilon_{+,i}^{*}.
+        \varepsilon_i^{*} &= \hat{\varepsilon}_i e^{*}_i,
+        \intertext{and}
+        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}.
       \end{align*}
     \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
-      local linear model on the bootstrap data set:\footnote{%
-        Note that the indices of summation are chosen to correspond to the
-        indices of the variables generated in the previous step.} %
+      local linear model on the bootstrap data set
       \begin{align*}
         \hat\mu_-^*(h)
-        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
-          (Y_i^* - \mu - \beta X_i^*)^2 \\
+        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{-}}
+          (Y_i^* - \mu - \beta X_i)^2 K_{h}(X_{i}) \\
         \hat\mu_+^*(h)
-        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
-          (Y_i^* - \mu - \beta X_i^*)^2.
+        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{+}}
+          (Y_i^* - \mu - \beta X_i)^2 K_{h}(X_{i}).
       \end{align*}
@@
   \begin{enumerate}
-  \item Estimate $\hat{g}_{+}$ and $\hat{g}_{-}$ and generate the residuals
-    $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.
+  \item Estimate $\hat{g}_{+}$ and $\hat{g}_{-}$ and generate $\hat g(\cdot)$
+    and the residuals $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.
   \item Repeat the following steps $B_{2}$ times to produce the
@@
     \begin{enumerate}
-    \item Draw an i.i.d. sample of size $M_-(b)$ from
-      $\{\hat\varepsilon_i : i \in I_-(b)\}$ and one of size $M_+(b)$ from
-      $\{\hat\varepsilon_i : i \in I_+(b)\}$. Let $\varepsilon_{-,i}^{*}$ and
-      $\varepsilon_{+,i}^{*}$ denote the $i$th element of each sample and
+    \item Draw i.i.d.\ random variables $e_i^{*}$ with mean zero, variance one,
+      and bounded fourth moments independent of the original data and
       construct
       \begin{align*}
-        Y_{-,m_-(b,i)}^* &= \hat g_-(X_{m_-(b,i)}) + \varepsilon_{-,i}^{*} &
-        Y_{+,m_+(b,i)}^* &= \hat g_+(X_{m_{+}(b,i)}) + \varepsilon_{+,i}^{*}.
+        \varepsilon_i^{*} &= \hat{\varepsilon}_i e^{*}_i,
+        \intertext{and}
+        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}.
       \end{align*}
@@
         \hat\mu_-^*(h)
-        &= \argmin_{\mu} \min_{\beta} \ssum[-]{i}{h}
-          (Y_i^* - \mu - \beta X_i^*)^2 \\
+        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{-}}
+          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{h}(X_{i}) \\
         \hat\mu_+^*(h)
-        &= \argmin_{\mu} \min_{\beta} \ssum[+]{i}{h}
-          (Y_i^* - \mu - \beta X_i^*)^2.
-      \end{align*}
-    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set,
-      \begin{multline*}
-        (Y_{-,m_-(b,1)}^{*}, X_{-,m_-(b,1)}),\dots,
-        (Y_{-,m_-(b,M_-(b))}^{*},X_{-,m_-(b,M_-(b))}), \\
-        (Y_{+,m_+(b,1)}^{*}, X_{+,m_+(b,1)}),\dots,
-        (Y_{+,m_+(b,M_+(b))}^{*},X_{+,m_+(b,M_+(b))})
-      \end{multline*}
+        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{+}}
+          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{h}(X_{i}).
+      \end{align*}
+    \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set
       using the same bandwidths $h$ and $b$ that are used in the rest of this

### 2016-07-28 R/RDfunctions.R
Refactor bootstrap functions
This commit rewrites the bootstrap code so that it is more modular and
easier to modify. The algorithm is the same for now, but the random
variables produced by the RNG are used in a different order than before,
so it will not produce numerically identical results to the earlier
version except in some special circumstances. I've also added a test
file that verifies that the new output matches the old output in some
of those settings.

@@ -7,136 +7,163 @@ generate.data <- function(model.id) {
   x <- 2*rbeta(500, 2, 4) - 1
   e <- rnorm(500, 0, 0.1295)
   y <- e + switch(model.id,
-                  ifelse(x < 0, 0.48 +  1.27*x +  7.18*x^2 + 20.21*x^3 + 21.54*x^4 + 7.33*x^5,
-                         0.52 +  0.84*x -  3.00*x^2 +  7.99*x^3 -  9.01*x^4 + 3.56*x^5),
-                  ifelse(x < 0, 3.71 +  2.30*x +  3.28*x^2 +  1.45*x^3 +  0.23*x^4 + 0.03*x^5,
-                         0.26 + 18.49*x - 54.81*x^2 + 74.30*x^3 - 45.02*x^4 + 9.83*x^5),
-                  ifelse(x < 0, 0.48 +  1.27*x - 0.5*7.18*x^2 + 0.7*20.21*x^3 + 1.1*21.54*x^4 + 1.5*7.33*x^5,
-                         0.52 +  0.84*x - 0.1*3.00*x^2 - 0.3*7.99*x^3 - 0.1*9.01*x^4 + 3.56*x^5))
-  return(data.frame(y = y, x = x))
+    ifelse(x < 0, 0.48 +  1.27*x +  7.18*x^2 + 20.21*x^3 + 21.54*x^4 + 7.33*x^5,
+                  0.52 +  0.84*x -  3.00*x^2 +  7.99*x^3 -  9.01*x^4 + 3.56*x^5),
+    ifelse(x < 0, 3.71 +  2.30*x +  3.28*x^2 +  1.45*x^3 +  0.23*x^4 + 0.03*x^5,
+                  0.26 + 18.49*x - 54.81*x^2 + 74.30*x^3 - 45.02*x^4 + 9.83*x^5),
+    ifelse(x < 0, 0.48 +  1.27*x - 0.5*7.18*x^2 + 0.7*20.21*x^3 + 1.1*21.54*x^4 + 1.5*7.33*x^5,
+                  0.52 +  0.84*x - 0.1*3.00*x^2 - 0.3*7.99*x^3 - 0.1*9.01*x^4 + 3.56*x^5))
+  return(data.frame(y = y, x = x))}
+
+# Functions that implement the residual and wild bootstraps.
+
+residual_bootstrap <- function(m, y, x) {
+  predict(m, data.frame(y = NA, x = x)) +
[…]

### 2016-07-28 R/application.R

@@ -3,7 +3,7 @@
 
 library(rdrobust)
 library(xtable)
-source("RDfunctions.R")
+source("rdfunctions.R")
 
 ## Load Ludwig and Miller's (2007) dataset
 
@@ -31,14 +31,13 @@ original <- function(dta, bw) {
 
 robust <- function(dta) {
   cct <- rdrobust(dta$y, dta$x, kernel = "uni")
-  bws <- cct$bws
-  
   t1  <- cct$coef[3]
   ci1 <- cct$ci[3, ]
-  
-  t2  <- rd.estimate(dta, 1, 2, bws[1], bws[2], N.bc, "uni", T)
-  ci2 <- rd.ci(dta, 1, 2, bws[1], bws[2], N.bc, N.ci, level, "uni", T)$ci
-  
+
+  boot <- rdboot(dta$t, dta$x, 1 - level, N.bc, residual_bootstrap, N.ci,
+    type = "basic", kernel = "uniform")
+  t2 <- boot[1]
+  ci2 <- boot[2:3]
   return(matrix(c(t1, ci1, NA, bws,
                   t2, ci2, NA, bws), nrow = 2, byrow = T))
 }

### 2016-07-28 R/rdfunctions_old.R

@@ -1,0 +1,130 @@
+
+local_polynomial_regression <- function(dta, order, bw, kernel) {
+  weight <- kweight(dta$x, 0, bw, kernel)
+  fit    <- lm.wfit(cbind(1, poly(dta$x, order, raw = T)), dta$y, weight)
+  return(list(cons = fit$coefficients[1],
+              yhat = fit$fitted.values,
+              res = fit$residuals,
+              weight = weight))
+}
+
+rd.estimate <- function(dta, p, q, bw.p, bw.q, N.bc, kernel, bc = TRUE) {
+  # dta:    a data set contains y and x.
+  # p:      the order of polynomial for point estimation.
+  # q:      the order of polynomial for bias correction.
+  # bw.p:   bandwidth for point estimation.
+  # bw.q:   bandwidth for bias correction.
+  # N.bc:   number of bootstrap replications for bias correction.
+  # kernel: epanechnikov, uniform or triangular.
+  # w.q:    kernel weight for bias correction. Reduce repeated computation.
+  # X:      the regressor matrix. Reduce repeated computation.
+  # bc:     perform bias correction?
+
+  if (length(bw.p) == 1) bw.p <- rep(bw.p, 2)
+  if (length(bw.q) == 1) bw.q <- rep(bw.q, 2)
+
+  # estimated effect from low order polynomial
+  dta.p.l <- dta[dta$x > -bw.p[1] & dta$x < 0, ]
+  dta.p.r <- dta[dta$x < bw.p[2] & dta$x >= 0, ]
+  trd.hat <- local_polynomial_regression(dta.p.r, p, bw.p[2], kernel)$cons -
+    local_polynomial_regression(dta.p.l, p, bw.p[1], kernel)$cons
+
+  if (!bc) {
+    return(trd.hat)
+  } else {
+
+    # the "true" effect from high order polynomial
+    dta.q.l <- dta[dta$x > -bw.q[1] & dta$x < 0, ]
+    dta.q.r <- dta[dta$x < bw.q[2] & dta$x >= 0, ]
+    left  <- local_polynomial_regression(dta.q.l, q, bw.q[1], kernel)
+    right <- local_polynomial_regression(dta.q.r, q, bw.q[2], kernel)
+    trd   <- right$cons - left$cons
+
+    # bootstrap
+    trd.hat.star <- replicate(N.bc,
[…]

### 2016-07-28 R/rdfunctions_test.R

@@ -1,0 +1,47 @@
+# Verify that new versions of the functions (in 'rdfunctions.R') return
+# the same values as our original versions (in 'rdfunctions_old.R')
+
+library(rdrobust)
+library(testthat)
+
+source("rdfunctions.R")
+source("rdfunctions_old.R")
+
+test_that("Bias-corrected point estimates give the same result as our original version", {
+  dta <- generate.data(1)
+  common.seed <- 32
+
+  ## Original approach
+  cct <- rdrobust(dta$y, dta$x, kernel = "uni")
+  bws <- cct$bws
+
+  ## Due to some differences in implemenation details, the two approaches
+  ## only give identical results when the dataset and parameters are very
+  ## constrained:
+  ## - The same bandwidth must be used for the linear and quadratic models
+  ## - All of the xs must fall in that bandwidth
+  ## - All of the positive xs must be first, then the negative xs.
+  ## Without these constraints, the two methods are essentially the same
+  ## but draw pseudo random variables from the RNG in different orders so
+  ## the results are not identical.
+  smalldta <- dta[abs(dta$x) < bws[2],]
+  smalldta <- smalldta[order(smalldta$x, decreasing = TRUE),]
+
+  ## Original version of the point estimate
+  set.seed(common.seed)
+  old_estimate <- rd.estimate(smalldta, 1, 2, bws[2], bws[2], 17, "tri", T)
+  old_interval <- rd.ci(smalldta, 1, 2, bws[2], bws[2], 17, 19, 0.9, "tri", T)
+
+  ## New version
+  set.seed(common.seed)
+  new_estimate <- with(smalldta, {
+    wq <- kweight(x, 0, bws[2], "tri")
+    boot_estimator(y, x, wq, wq, p=1, q=2, nboot = 17,
+      bootfn = residual_bootstrap)})
+  new_interval <- with(smalldta, {
+    wq <- kweight(x, 0, bws[2], "tri")
+    boot_interval(y, x, wq, wq, a = 0.1, p = 1, q = 2,
+      17, residual_bootstrap, 19, type = "percentile")})
+
+  expect_equivalent(new_estimate, old_estimate)
+  expect_equivalent(new_interval, old_interval$ci)})

### 2016-07-28 R/simulation.R

@@ -8,7 +8,7 @@ library(doRNG)
 library(xtable)
 try(source("slackrISE.R"), T)
 
-source("RDfunctions.R")
+source("rdfunctions.R")
 
 #### for testing in my computer ####
 # N.ci <- 20
@@ -19,24 +19,19 @@ source("RDfunctions.R")
 
 #### to run in servor ####
 N.ci <- 999
-level <- 0.95
+a <- 0.05
 N.simu <- 5000
 N.core <- 15
 N.bc <- 500
 
 ## simulation 1: coverage of CI from bootstrap
 
-simulation.1 <- function(model.id, p, q, kernel, bc) {
-  
+simulation.1 <- function(model.id, nsims) {
+
   simu <- function() {
-    dta   <- generate.data(model.id)
-    # CCT bandwidth from Calonico package
-    bw    <- rdbwselect(dta$y, dta$x, p = p, q = q, kernel = kernel, bwselect = "CCT")
-    bw.p  <- bw$bws[1,1]
-    bw.q  <- bw$bws[1,2]
-    t     <- rd.estimate(dta, p, q, bw.p, bw.q, N.bc, kernel, bc)
-    ci    <- rd.ci(dta, p, q, bw.p, bw.q, N.bc, N.ci, level, kernel, bc)$ci
-    return(c(t, ci))
+    dta <- generate.data(model.id)
+    rdboot(dta$y, dta$x, a, N.bc, residual_bootstrap, nboot2 = N.ci,
+      p = 1, q = 2, type = "basic", kernel = "tri", bwselect = "CCT")
   }
   
   cl <- makeCluster(N.core)

### 2016-07-28 R/RDfunctions.R
Add code for wild bootstrap to repository
This commit adds functionality to use the wild bootstrap for RD
bias correction and confidence intervals.

@@ -22,6 +22,16 @@ residual_bootstrap <- function(m, y, x) {
     sample(resid(m), size = length(y), replace = TRUE, prob = weights(m))
 }
 
+wild_values <- c(1 - sqrt(5), 1 + sqrt(5)) / 2
+wild_weights <- c(sqrt(5) + 1, sqrt(5) - 1) / (2 * sqrt(5))
+
+wild_bootstrap <- function(m, y, x) {
+  yhat <- predict(m, data.frame(y = NA, x = x))
+  ehat <- y - yhat
+  yhat + (ehat * sample(wild_values, size = length(ehat),
+    replace = TRUE, prob = wild_weights))
+}
+
 # Simple RD estimator of the treatment effect.
 
 basic_estimator <- function(y, x, w, p = 1,

### 2016-07-28 R/rdfunctions_test.R

@@ -45,3 +45,17 @@ test_that("Bias-corrected point estimates give the same result as our original v
 
   expect_equivalent(new_estimate, old_estimate)
   expect_equivalent(new_interval, old_interval$ci)})
+
+"%isin%" <- function(x, y)
+  all(sapply(x, function(xval)
+    any(sapply(y, function(yval)
+      isTRUE(all.equal(xval, yval, check.attributes = FALSE))))))
+
+test_that("We didn't screw up the weights for the wild bootstrap", {
+  expect_equal(sum(wild_weights), 1)
+  expect_equal(sum(wild_weights * wild_values), 0)
+
+  ## basic check that the wild bootstrap 'works'
+  d <- data.frame(x = rep(c(0, 1), 4), y = rep(c(0, 1), each = 4))
+  w <- wild_bootstrap(lm(y ~ x, data = d), d$y, d$x)
+  expect_true(w %isin% c(.5 * (1 - wild_values), .5 * (1 + wild_values)))})

### 2016-07-28 R/application.R
Update application and simulations to use Wild bootstrap instead of residual bootstrap

@@ -34,7 +34,7 @@ robust <- function(dta) {
   t1  <- cct$coef[3]
   ci1 <- cct$ci[3, ]
 
-  boot <- rdboot(dta$t, dta$x, 1 - level, N.bc, residual_bootstrap, N.ci,
+  boot <- rdboot(dta$t, dta$x, 1 - level, N.bc, wild_bootstrap, N.ci,
     type = "basic", kernel = "uniform")
   t2 <- boot[1]
   ci2 <- boot[2:3]

### 2016-07-28 R/simulation.R

@@ -30,31 +30,34 @@ simulation.1 <- function(model.id, nsims) {
 
   simu <- function() {
     dta <- generate.data(model.id)
-    rdboot(dta$y, dta$x, a, N.bc, residual_bootstrap, nboot2 = N.ci,
+    rdboot(dta$y, dta$x, a, N.bc, wild_bootstrap, nboot2 = N.ci,
       p = 1, q = 2, type = "basic", kernel = "tri", bwselect = "CCT")
   }
-  
+
   cl <- makeCluster(N.core)
   registerDoParallel(cl)
-  export.obj <- c("N.ci", "N.bc", "level", "generate.data", "kweight", "rd.estimate", "lpreg", "rd.ci")
-  collect.simu <- foreach(i=1:N.simu, .combine="rbind", .packages="rdrobust", .export=export.obj, .inorder=F) %dorng% 
+  export.obj <- c("N.ci", "N.bc", "level", "generate.data", "kweight",
+    "rd.estimate", "lpreg", "rd.ci", "wild_bootstrap", "rdboot",
+    "basic_estimator", "boot_estimator", "wild_values", "wild_weights",
+    "boot_interval", "boot_ci_basic")
+  collect.simu <- foreach(i=1:N.simu, .combine="rbind", .packages="rdrobust", .export=export.obj, .inorder=F) %dorng%
     simu()
   stopCluster(cl)
-  
+
   t.true    <- ifelse(model.id ==2, -3.45, 0.04)
   bias      <- t.true - mean(collect.simu[ , 1])
   SD        <- sd(collect.simu[ , 1])
   MSE       <- sqrt(mean((collect.simu[ , 1] - t.true)^2))
   coverage  <- mean(collect.simu[ , 2] <= t.true & collect.simu[ , 3] >= t.true)
   length    <- mean(collect.simu[ , 3] - collect.simu[ , 2])
-  
+
   return(c(true = t.true, bias = bias, SD = SD, MSE = MSE, coverage = coverage, length = length))
 }
 
 ## simulation 2: coverage of CI from CCT(2004)
 
 simulation.2 <- function(model.id, p, q, kernel) {
-  
+
   simu <- function() {
     dta   <- generate.data(model.id)
     results <- rdrobust(dta$y, dta$x, p = p, q = q, kernel = kernel, bwselect = "CCT", level = 100*level)
@@ -62,21 +65,21 @@ simulation.2 <- function(model.id, p, q, kernel) {
[…]

### 2016-07-28 R/rdfunctions.R
Update 'kweight' definition for version 0.91 of rdrobust
Version 0.91 of rdrobust no longer exports the 'kweight' function. So we define our
kweight function to use their internal 'rdrobust_kweight' instead.

@@ -1,7 +1,7 @@
 ## Copyright (c) 2016, Otávio Bartalotti, Gray Calhoun, and Yang He.
 ## Available under the MIT "Expat" License, see README.md
 
-kweight <- rdrobust::kweight
+kweight <- rdrobust:::rdrobust_kweight
 
 generate.data <- function(model.id) {
   x <- 2*rbeta(500, 2, 4) - 1

### 2016-07-28 R/application.R
Update R code to use older version of bandwdith selection
Bumping to version 0.91 of rdrobust changes the bandwidth algorithms. Since we
don't want to deal with this in the paper, we change the internal function
calls slightly to continue to use the old (discontinued) bandwidth algorithms.

@@ -30,7 +30,8 @@ original <- function(dta, bw) {
 }
 
 robust <- function(dta) {
-  cct <- rdrobust(dta$y, dta$x, kernel = "uni")
+  bws <- rdbandwidth_2014(dta$y, dta$x, kernel = "uni")$bws
+  cct <- rdrobust(dta$y, dta$x, kernel = "uni", h = bws[1], b = bws[2])
   t1  <- cct$coef[3]
   ci1 <- cct$ci[3, ]
 

### 2016-07-28 R/rdfunctions.R

@@ -162,7 +162,7 @@ rdboot <- function(y, x, a, nboot, bootfn, nboot2 = nboot,
 
   type <- match.arg(type)
   kernel <- match.arg(kernel)
-  bw <- rdbwselect(y, x, p=p, q=q, kernel=kernel,...)$bws
+  bw <- rdbwselect_2014(y, x, p=p, q=q, kernel=kernel,...)$bws
   wp <- kweight(x, 0, bw[1], kernel)
   wq <- kweight(x, 0, bw[2], kernel)
 

### 2016-07-28 R/rdfunctions_test.R

@@ -12,9 +12,7 @@ test_that("Bias-corrected point estimates give the same result as our original v
   common.seed <- 32
 
   ## Original approach
-  cct <- rdrobust(dta$y, dta$x, kernel = "uni")
-  bws <- cct$bws
-
+  ##
   ## Due to some differences in implemenation details, the two approaches
   ## only give identical results when the dataset and parameters are very
   ## constrained:
@@ -24,27 +22,47 @@ test_that("Bias-corrected point estimates give the same result as our original v
   ## Without these constraints, the two methods are essentially the same
   ## but draw pseudo random variables from the RNG in different orders so
   ## the results are not identical.
-  smalldta <- dta[abs(dta$x) < bws[2],]
+  cct <- rdrobust(dta$y, dta$x, kernel = "tri")
+  bw <- rdbwselect_2014(dta$y, dta$x)$bws[2]
+
+  smalldta <- dta[abs(dta$x) < bw,]
   smalldta <- smalldta[order(smalldta$x, decreasing = TRUE),]
 
   ## Original version of the point estimate
   set.seed(common.seed)
-  old_estimate <- rd.estimate(smalldta, 1, 2, bws[2], bws[2], 17, "tri", T)
-  old_interval <- rd.ci(smalldta, 1, 2, bws[2], bws[2], 17, 19, 0.9, "tri", T)
+  old_estimate <- rd.estimate(smalldta, 1, 2, bw, bw, 17, "tri", T)
+  old_interval <- rd.ci(smalldta, 1, 2, bw, bw, 17, 19, 0.9, "tri", T)
 
   ## New version
   set.seed(common.seed)
   new_estimate <- with(smalldta, {
-    wq <- kweight(x, 0, bws[2], "tri")
+    wq <- kweight(x, 0, bw, "tri")
     boot_estimator(y, x, wq, wq, p=1, q=2, nboot = 17,
       bootfn = residual_bootstrap)})
   new_interval <- with(smalldta, {
-    wq <- kweight(x, 0, bws[2], "tri")
+    wq <- kweight(x, 0, bw, "tri")
     boot_interval(y, x, wq, wq, a = 0.1, p = 1, q = 2,
       17, residual_bootstrap, 19, type = "percentile")})
 
   expect_equivalent(new_estimate, old_estimate)
   expect_equivalent(new_interval, old_interval$ci)})
+
[…]

### 2016-07-28 R/simulation.R

@@ -31,7 +31,7 @@ simulation.1 <- function(model.id, nsims) {
   simu <- function() {
     dta <- generate.data(model.id)
     rdboot(dta$y, dta$x, a, N.bc, wild_bootstrap, nboot2 = N.ci,
-      p = 1, q = 2, type = "basic", kernel = "tri", bwselect = "CCT")
+      p = 1, q = 2, type = "basic", kernel = "tri")
   }
 
   cl <- makeCluster(N.core)
@@ -59,10 +59,12 @@ simulation.1 <- function(model.id, nsims) {
 simulation.2 <- function(model.id, p, q, kernel) {
 
   simu <- function() {
-    dta   <- generate.data(model.id)
-    results <- rdrobust(dta$y, dta$x, p = p, q = q, kernel = kernel, bwselect = "CCT", level = 100*level)
-    t     <- results$coef[3]
-    ci    <- results$ci[3, ]
+    dta <- generate.data(model.id)
+    bws <- rdbandwidth_2014(dta$y, dta$x, p = p, q = q, kernel = kernel)$bws
+    results <- rdrobust(dta$y, dta$x, p = p, q = q, kernel = kernel,
+      h = bws[1], b = bws[2], level = 100 * (1-a))
+    t <- results$coef[3]
+    ci <- results$ci[3, ]
     return(c(t, ci))
   }
 

### 2016-07-28 R/rdfunctions.R
slight change of output from function "rdboot"
It was basic_estomator (biased), now it is boot_estimator (bias
corrected).

@@ -52,7 +52,7 @@ basic_estimator <- function(y, x, w, p = 1,
 # wp, wq: explicit weights imposed by the kernel near the cutoff
 # a:      size of the implicit hypothesis test. The interval will have level 1-a
 # nboot:  number of bootstrap replications used for debiasing
-# bootfn: a function that generates new values of the depnedent model,
+# bootfn: a function that generates new values of the dependent model,
 #         given an estimated local polynomial
 # p, q: polynomial degree for the estimated model (p1) and the conditional
 #         expectation used to implement the bootstrap (p2)
@@ -166,7 +166,7 @@ rdboot <- function(y, x, a, nboot, bootfn, nboot2 = nboot,
   wp <- kweight(x, 0, bw[1], kernel)
   wq <- kweight(x, 0, bw[2], kernel)
 
-  estimate <- basic_estimator(y, x, wp, p)
+  estimate <- boot_estimator(y, x, wp, wq, p, q, nboot, bootfn)
   names(estimate) <- "estimate"
 
   ci <- boot_interval(y, x, wp, wq, a, p, q, nboot, bootfn, nboot2, type)

### 2016-07-29 main_paper.tex
Tweak Theorem 1's proof
This commit explains one step in Theorem 1 in more detail and updates
the notation to match changes in the algorithm.
Fix notation error in background section
The background section refers to K_h before that notation is defined. I've
changed it to use K as was originally meant.
Move I_- and I_+ into the kernel definitions
This commit tweaks the kernel notation so that they absorb the sign of the
xs as well. This change allows the summations to be simplified considerably.

@@
   &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
-  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h} K_{h}(X_{i}/h).
+  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h} K(X_{i}/h).
 \end{align*}
@@
 \end{assumption}
-To simplify notation, define the scaled kernel functions
-\begin{align*}
-  K_h(x) &= \tfrac{1}{h} K(x/h)
+To simplify notation, define the scaled and truncated kernel functions
+\begin{align*}
+  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x > 0\} &
+  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \leq 0\}
 \intertext{and}
-  K_b(x) &= \tfrac{1}{b} K(x/b).
+  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x > 0\} &
+  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \leq 0\}.
 \end{align*}
@@
 treatment effect estimator and the higher order approximation used for the
-bootstrap.  For simplicity, though, we use the same function for all steps of
+bootstrap.\footnote{%
+  It would be a slight abuse of notation for $K_{+,h}$, $K_{-,h}$,
+  $K_{+,b}$, and $K_{-,b}$ to all use different underlying kernels but
+  would not affect our proofs.} %
+For simplicity, however, we use the same function for all steps of
 estimation in this paper.  Potentially different kernel functions and bandwidths
@@
 \begin{algorithm}[Bias estimation]\label{Alg1}
-  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
-  \begin{align*}
-    I_{-} &= \{i : X_i < 0 \}, &
-    I_{+} &= \{i : X_i > 0 \}.
-  \end{align*}
-  Also define $M_{-}$ and $M_{+}$ to be the number of elements in $I_{-}$ and
-  $I_{+}$ respectively, and $m_{-}(1),\dots,m_{-}(M_{-})$ and
-  $m_{+}(1),\dots,m_{+}(M_+)$ to be subsequences of $1,\dots,n$ that index
-  $I_-$ and $I_+$, respectively.
+  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2}.
   \begin{enumerate}
-  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$ using
-    the observations in $I_-$ and $I_+$ and the kernel $K_{b}(X_{i})$:
+  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$
+    with least squares using $K_{-,b}$ and $K_{+,b}$ for weights:
     \begin{align}
@@
     \begin{align*}
-      \hat\beta_{-} &= \argmin_\beta \sum_{i \in I_-}
-      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}) \\
-      \hat\beta_{+} &= \argmin_\beta \sum_{i \in I_+}
-      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}).
+      \hat\beta_{-} &= \argmin_\beta \sum_{i = 1}^n
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{+,b}(X_{i}) \\
+      \hat\beta_{+} &= \argmin_\beta \sum_{i = 1}^n
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{-,b}(X_{i}).
     \end{align*}
@@
     \]
-    and calculate the residuals $\hat\varepsilon_{i} = Y_i - \hat g(X_i)$.
+    and calculate the residuals $\hat\varepsilon_{i} = Y_i - \hat g(X_i)$ for all $i$.
   \item Repeat the following steps $B_{1}$ times to produce the
     bootstrap estimates $\hat{\tau}_{1}^{*}(h),\dots,\hat\tau_{B_{1}}^{*}(h)$. For the
-    $k$th value:
+    $k$th replication:
     \begin{enumerate}
@@
         \intertext{and}
-        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}.
-      \end{align*}
+        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}
+      \end{align*}
+      for all $i$.
     \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
-      local linear model on the bootstrap data set
+      local linear model on the bootstrap data set using $K_{+,h}$ and $K_{-,h}$ for
+      weights:
       \begin{align*}
         \hat\mu_-^*(h)
-        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{-}}
-          (Y_i^* - \mu - \beta X_i)^2 K_{h}(X_{i}) \\
+        &= \argmin_{\mu} \min_{\beta} \sum_{i =1}^n
+          (Y_i^* - \mu - \beta X_i)^2 K_{-,h}(X_{i}) \\
         \hat\mu_+^*(h)
-        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{+}}
-          (Y_i^* - \mu - \beta X_i)^2 K_{h}(X_{i}).
+        &= \argmin_{\mu} \min_{\beta} \sum_{i = 1}^n
+          (Y_i^* - \mu - \beta X_i)^2 K_{+,h}(X_{i}).
       \end{align*}
@@
 \begin{algorithm}[Confidence intervals]\label{Alg2}
-  Define the same notation as in Algorithm~\ref{Alg1}.
+  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and
+  Algorithm~\ref{Alg1}.
   \begin{enumerate}
@@
     $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
-    $k$th value:
+    $k$th replication:
     \begin{enumerate}
@@
       \end{align*}
+      for all $i = 1,\dots,n$.
     \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
-      local linear model on the bootstrap data set:
+      local linear model on the bootstrap data set using $K_{+,h}$ and $K_{-,h}$
+      for weights:
       \begin{align*}
         \hat\mu_-^*(h)
-        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{-}}
-          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{h}(X_{i}) \\
+        &= \argmin_{\mu} \min_{\beta} \sum_{i = 1}^n
+          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{-,h}(X_{i}), \\
         \hat\mu_+^*(h)
-        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{+}}
-          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{h}(X_{i}).
+        &= \argmin_{\mu} \min_{\beta} \sum_{i = 1}^n
+          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{+,h}(X_{i}).
       \end{align*}
     \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set
-      using the same bandwidths $h$ and $b$ that are used in the rest of this
+      $(Y_1^*,\, X_1),\dots,(Y_n^*,\, X_n)$ set using the same bandwidths
+      $h$ and $b$ that are used in the rest of this
       algorithm but reestimating all of the local polynomials on the bootstrap
@@
     \item Save the bias-corrected estimator
-      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
+      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_-^*(h)
       - \Delta^{**}(h,b)$.
     \end{enumerate}
-  \item Use the empirical CDF of
-    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
-    construct confidence intervals, etc.
+  \item Define $\tau^* = \hat g_+(0) - \hat g_-(0)$ and use the empirical CDF of
+    $\hat\tau_1^{\prime*}(h,b) - \tau^*,\dots, \hat\tau_{B_2}^{\prime*}(h,b) - \tau^*$
+    as the sampling distribution of $\hat \tau' - \tau$.
   \end{enumerate}
@@
   \intertext{and}
-    \sup_{x}
+    \sup_{x,\tau}
     \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
@@
 \end{equation*}
-The design of the bootstrap ensures that
+By construction,
+\begin{align*}
+  \hat\beta^*_{+,p} - \beta^*_{+,p}
+  & = \Big(\sum_{i = 1}^n r_p(X_i) r_p(X_i)' K_{+,h}(X_i) \Big)^{-1}
+  \sum_{i = 1}^n r_p(X_i) K_{+,h}(X_i) \hat\varepsilon_i e_i^* \\
+  \hat\beta^*_{-,p} - \beta^*_{-,p}
+  &= \Big(\sum_{i = 1}^n r_p(X_i) r_p(X_i)' K_{-,h}(X_i)\Big)^{-1}
+  \sum_{i = 1}^n r_p(X_i) K_{-,h}(X_i) \hat\varepsilon_i e_i^*
+\end{align*}
+ensuring that
 \begin{align*}
@@
 \end{align*}
-almost surely, implying that
+almost surely and, consequently,
 \begin{equation*}

### 2016-07-29 main_paper.tex
Make small wording changes to algorithm descriptions

--- 2016-07-26 main_paper.tex
@@
         \intertext{and}
-        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}.
-      \end{align*}
+        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}
+      \end{align*}
+      for all $i$.
     \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
@@
       \end{align*}
+      for all $i = 1,\dots,n$.
     \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
@@
     \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set
-      using the same bandwidths $h$ and $b$ that are used in the rest of this
+      $(Y_1^*,\, X_1),\dots,(Y_n^*,\, X_n)$ set using the same bandwidths
+      $h$ and $b$ that are used in the rest of this
       algorithm but reestimating all of the local polynomials on the bootstrap
@@
 \end{equation*}
-The design of the bootstrap ensures that
+By construction,
+\begin{align*}
+  \hat\beta^*_{+,p} - \beta^*_{+,p}
+  & = \Big(\sum_{i\in I_+} K_h(X_i) r_p(X_i) r_p(X_i)'\Big)^{-1}
+  \sum_{i \in I_+} K_h(X_i) r_p(X_i) \hat\varepsilon_i e_i^* \\
+  \hat\beta^*_{-,p} - \beta^*_{-,p}
+  &= \Big(\sum_{i\in I_-} K_h(X_i) r_p(X_i) r_p(X_i)'\Big)^{-1}
+  \sum_{i \in I_-} K_h(X_i) r_p(X_i) \hat\varepsilon_i e_i^*
+\end{align*}
+ensuring that
 \begin{align*}
@@
 \end{align*}
-almost surely, implying that
+almost surely. Consequently,
 \begin{equation*}

### 2016-07-31 R/rdfunctions.R
Fix a typo in description
I believe nboot is for debiasing and nboot2 is for intervals.

@@ -94,9 +94,9 @@ boot_estimator <- function(y, x, wp, wq, p = 1, q = p + 1, nboot, bootfn,
 # x: running variable
 # wp, wq: explicit weights imposed by the kernel near the cutoff
 # a: size of the implicit hypothesis test. The interval will have level 1-a
-# nboot: number of bootstrap  replications for the "outer" bootstrap that
+# nboot2: number of bootstrap  replications for the "outer" bootstrap that
 #         generates draws for the confidence interval construction
-# nboot2: number of bootstrap replications used for debiasing
+# nboot:  number of bootstrap replications used for debiasing
 # bootfn: a function that generates new values of the depnedent model,
 #         given an estimated local polynomial
 # p1, p2: polynomial degree for the estimated model (p1) and the conditional

### 2016-07-31 R/rdfunctions.R
Fix an error in boot_interval function
This function calls boot_ci_basic, which takes argumant estimate, boots,
boot_parameter, a. This commit fixes it.

@@ -125,11 +125,11 @@ boot_interval <- function(y, x, wp, wq, a, p = 1, q = p + 1,
 
   switch(type,
     basic = boot_ci_basic(boot_estimator(y, x, wp, wq, p, q, nboot2, bootfn),
-      quantile(boots, c(1 - a/2, a/2)), basic_estimator(y, x, wq, q)),
+            boots, basic_estimator(y, x, wq, q), a),
     percentile = quantile(boots, c(a/2, 1-a/2)),
     both = rbind(
       basic = boot_ci_basic(boot_estimator(y, x, wp, wq, p, q, nboot2, bootfn),
-        quantile(boots, c(1 - a/2, a/2)), basic_estimator(y, x, wq, q)),
+            boots, basic_estimator(y, x, wq, q), a),
       percentile = quantile(boots, c(a/2, 1-a/2))),
     stop("The listed interval type is not supported."))
 }

### 2016-07-31 R/rdfunctions_test.R
Fix an error-reporting test
This test didn't pass because of different random seed. The rdboot
funciton first runs boot_estimator then boot_interval, so random number
for boot_interval inside rdboot is different from an explicit version.

@@ -55,6 +55,7 @@ test_that("Convenient version of interval constructions runs and matches explici
     bw <- rdbwselect_2014(y, x)$bws
     wp <- kweight(x, 0, bw[1], "tri")
     wq <- kweight(x, 0, bw[2], "tri")
+    estimate <- boot_estimator(y, x, wp, wq, 1, 2, 17, residual_bootstrap)
     boot_interval(y, x, wp, wq, a = 0.1, p = 1, q = 2,
       17, residual_bootstrap, 19, type = "percentile")})
   set.seed(common.seed)

### 2016-07-31 R/application.R
Fix the issue that application.R does not run
It had three problems: (1) a typo in function name (2) a typo in
function argument and (3) some data sets are not loaded. This commit
fixes these issues but does not generate results in .tex file.

@@ -30,12 +30,12 @@ original <- function(dta, bw) {
 }
 
 robust <- function(dta) {
-  bws <- rdbandwidth_2014(dta$y, dta$x, kernel = "uni")$bws
+  bws <- rdbwselect_2014(dta$y, dta$x, kernel = "uni")$bws
   cct <- rdrobust(dta$y, dta$x, kernel = "uni", h = bws[1], b = bws[2])
   t1  <- cct$coef[3]
   ci1 <- cct$ci[3, ]
 
-  boot <- rdboot(dta$t, dta$x, 1 - level, N.bc, wild_bootstrap, N.ci,
+  boot <- rdboot(dta$y, dta$x, 1 - level, N.bc, wild_bootstrap, N.ci,
     type = "basic", kernel = "uniform")
   t2 <- boot[1]
   ci2 <- boot[2:3]
@@ -48,10 +48,20 @@ robust <- function(dta) {
 spending <- matrix(0, nrow = 10, ncol = 6)
 colnames(spending) <- c("Effect", "Lower CI", "Upper CI", "P-value", "h", "b")
 
+hsspend_per_kid_68 <- census2[ , c("hsspend_per_kid_68", "povrate60")]
+hsspend_per_kid_68 <- hsspend_per_kid_68[complete.cases(hsspend_per_kid_68), ]
+colnames(hsspend_per_kid_68) <- c("y", "x")
+hsspend_per_kid_68$x <- hsspend_per_kid_68$x - cutoff
+
 spending[1, ] <- original(hsspend_per_kid_68, 9)
 spending[2, ] <- original(hsspend_per_kid_68, 18)
 spending[3, ] <- original(hsspend_per_kid_68, 36)
 spending[4:5, ] <- robust(hsspend_per_kid_68)
+
+hsspend_per_kid_72 <- census2[ , c("hsspend_per_kid_72", "povrate60")]
+hsspend_per_kid_72 <- hsspend_per_kid_72[complete.cases(hsspend_per_kid_72), ]
+colnames(hsspend_per_kid_72) <- c("y", "x")
+hsspend_per_kid_72$x <- hsspend_per_kid_72$x - cutoff
 
 spending[6, ] <- original(hsspend_per_kid_72, 9)
 spending[7, ] <- original(hsspend_per_kid_72, 18)
@@ -63,6 +73,11 @@ spending[9:10, ] <- robust(hsspend_per_kid_72)
[…]

### 2016-07-31 R/rdfunctions_ForMc.R
Add functions for simulation
These functions are much faster but less extendable. We are going to use
rdboot_ForMc instead of rdboot in simulation.

@@ -1,0 +1,132 @@
+## Copyright (c) 2016, Otávio Bartalotti, Gray Calhoun, and Yang He.
+## Available under the MIT "Expat" License, see README.md
+
+# As its name suggest, the functions in this file is for fast simulation
+# Note: observations beyound max(h, b) will be dropped at the beginning.
+# Notation: 
+# p    indicates objectes associated with p'th order polynomial; q indicates q'th order.
+# l    indicates objectes at left hand side; r indicates right hand side.
+# fit  indicates matrix generating fitted values.
+# coef indicates matrix generating coefficients.
+# ih   indicates elements within bandwith h.
+# w    indicates kernel weights.
+
+
+## this function generates bias-corrected estimator
+boot_estimator_ForMc <- function(ypl, ypr, yql, yqr, fit.ql, fit.qr, 
+                           coef.qr, coef.ql, coef.pr, coef.pl,
+                           wqr, wql, ihr, ihl, Nbc, bootstrap = "wild") {
+  
+  fitted.l <- fit.ql %*% yql
+  fitted.r <- fit.qr %*% yqr
+  residual.l <- yql - fitted.l
+  residual.r <- yqr - fitted.r
+  boot_parameter <- coef.qr %*% yqr - coef.ql %*% yql
+  estimate <- coef.pr %*% ypr - coef.pl %*% ypl
+
+  if (bootstrap == "residual") {
+    boots <- replicate(Nbc,
+             coef.pr %*% (fitted.r[ihr] + sample(residual.r, length(ypr), T, wqr)) -
+             coef.pl %*% (fitted.l[ihl] + sample(residual.l, length(ypl), T, wql)))
+  }
+  if (bootstrap == "wild") {
+    boots <- replicate(Nbc,
+             coef.pr %*% (fitted.r[ihr] + residual.r[ihr]*sample(wild_values, length(ypr), T, wild_weights)) -
+             coef.pl %*% (fitted.l[ihl] + residual.l[ihl]*sample(wild_values, length(ypl), T, wild_weights)))
+  }
+
+  
[…]

### 2016-07-31 R/rdfunctions_ForMc_test.R
Test that rdfunctions_ForMc works correctly
Two main tests: (1) functions in 'rdfunctions_ForMc.R' return the same
results as functions in 'rdfunctions_old.R' in residual bootstrap. (2)
functions in 'rdfunctions_ForMc.R' return the same results as functions
in 'rdfunctions.R' in wild bootstrap.

@@ -1,0 +1,152 @@
+# Verify that new versions of the functions in 'rdfunctions_ForMc.R' return
+# the same results as functions in 'rdfunctions_old.R' in residual bootstrap.
+
+# Verify that new versions of the functions in 'rdfunctions_ForMc.R' return
+# the same results as functions in 'rdfunctions.R' in wild bootstrap.
+
+library(rdrobust)
+library(testthat)
+library(rbenchmark)
+
+source("rdfunctions.R")
+source("rdfunctions_old.R")
+source("rdfunctions_ForMc.R")
+
+test_that("rdfunctions_ForMc.R gives the same results as rdfunctions_old.R in residual bootstrap.",{
+  
+  # generate a wrapper from rdfunctions_old.R, this allows
+  # direct comparison with _ForMc results.
+  old_estimator_wrapper <- function(y, x, a = 0.05, Nbc = 500, Nci = 999, p = 1, q = 2, 
+                                    kernel = "uniform"){
+    
+    bw <- rdbwselect_2014(y, x, p=p, q=q, kernel=kernel)$bws
+    h <- bw[1]
+    b <- bw[2]
+    
+    estimate <- rd.estimate(data.frame(y=y, x=x), p, q, h, b, Nbc, kernel, T)
+    ci <- rd.ci(data.frame(y=y, x=x), p, q, h, b, Nbc, Nci, 1-a, kernel, T)$ci
+    
+    return(c(estimate, ci))
+  }
+  
+  dta <- generate.data(1)
+  
+  set.seed(798)
+  old_uni <- old_estimator_wrapper(dta$y, dta$x, Nbc = 50, Nci = 50, kernel = "uniform")
+  old_tri <- old_estimator_wrapper(dta$y, dta$x, Nbc = 50, Nci = 50, kernel = "triangular")
+  old_epa <- old_estimator_wrapper(dta$y, dta$x, Nbc = 50, Nci = 50, kernel = "epanechnikov")
+  
+  set.seed(798)
+  new_uni <- rdboot_ForMc(dta$y, dta$x, Nbc = 50, Nci = 50, bootstrap = "residual", kernel = "uniform")[2, ]
+  new_tri <- rdboot_ForMc(dta$y, dta$x, Nbc = 50, Nci = 50, bootstrap = "residual", kernel = "triangular")[2, ]
[…]

### 2016-07-31 R/application.R
Use rdboot_ForMc in application
rdboot is too slow for application, this commit change rdboot to
rdboot_ForMc.

@@ -4,6 +4,7 @@
 library(rdrobust)
 library(xtable)
 source("rdfunctions.R")
+source("rdfunctions_ForMc.R")
 
 ## Load Ludwig and Miller's (2007) dataset
 
@@ -17,8 +18,8 @@ census_2000 <- read.csv("./LM2007data/census_2000.csv")
 
 ## Set parameterizations and functions for the analysis
 
-N.bc <- 500
-N.ci <- 999
+N.bc <- 50
+N.ci <- 99
 level <- 0.95
 set.seed(555)
 
@@ -35,8 +36,8 @@ robust <- function(dta) {
   t1  <- cct$coef[3]
   ci1 <- cct$ci[3, ]
 
-  boot <- rdboot(dta$y, dta$x, 1 - level, N.bc, wild_bootstrap, N.ci,
-    type = "basic", kernel = "uniform")
+  boot <- rdboot_ForMc(dta$y, dta$x, 1 - level, N.bc, N.ci,
+          bootstrap = "wild", kernel = "uniform")
   t2 <- boot[1]
   ci2 <- boot[2:3]
   return(matrix(c(t1, ci1, NA, bws,

### 2016-07-31 R/application.R
Add random seed for reproducible results

@@ -7,6 +7,7 @@ source("rdfunctions.R")
 source("rdfunctions_ForMc.R")
 
 ## Load Ludwig and Miller's (2007) dataset
+set.seed(798)
 
 cutoff <- 59.1984
 census2 <- read.csv("./LM2007data/census2.csv")

### 2016-07-31 R/application.R
Correct the number of replications
I made them small for testing and forgot to change them back. This
commit fixes it.

@@ -19,8 +19,8 @@ census_2000 <- read.csv("./LM2007data/census_2000.csv")
 
 ## Set parameterizations and functions for the analysis
 
-N.bc <- 50
-N.ci <- 99
+N.bc <- 500
+N.ci <- 999
 level <- 0.95
 set.seed(555)
 

### 2016-08-01 R/rdfunctions_ForMc.R
Update the _ForMc functions
Use orthogonal polynomials and QR decomposition for better numerical
stability.

@@ -13,16 +13,22 @@
 
 
 ## this function generates bias-corrected estimator
-boot_estimator_ForMc <- function(ypl, ypr, yql, yqr, fit.ql, fit.qr, 
-                           coef.qr, coef.ql, coef.pr, coef.pl,
-                           wqr, wql, ihr, ihl, Nbc, bootstrap = "wild") {
+boot_estimator_ForMc <- function(ypl, ypr, yql, yqr, 
+                                 coef.ql, coef.qr, coef.pl, coef.pr,
+                                 Xql, Xqr, Xpl, Xpr,
+                                 WXql, WXqr,
+                                 wqr, wql, ihr, ihl, Nbc, bootstrap = "wild") {
   
-  fitted.l <- fit.ql %*% yql
-  fitted.r <- fit.qr %*% yqr
+  b.ql       <- crossprod(WXql, yql)
+  fitted.l   <- Xql %*% b.ql
   residual.l <- yql - fitted.l
+  
+  b.qr       <- crossprod(WXqr, yqr)
+  fitted.r   <- Xqr %*% b.qr
   residual.r <- yqr - fitted.r
+  
   boot_parameter <- coef.qr %*% yqr - coef.ql %*% yql
-  estimate <- coef.pr %*% ypr - coef.pl %*% ypl
+  estimate       <- coef.pr %*% ypr - coef.pl %*% ypl
 
   if (bootstrap == "residual") {
     boots <- replicate(Nbc,
@@ -40,30 +46,39 @@ boot_estimator_ForMc <- function(ypl, ypr, yql, yqr, fit.ql, fit.qr,
 }
 
 ## this function generates bootstrap distribution of bias-corrected estimator
-boot_dist_ForMc <- function(ypl, ypr, yql, yqr, fit.ql, fit.qr, 
-                      coef.qr, coef.ql, coef.pr, coef.pl,
-                      wqr, wql, ihr, ihl, Nbc, Nci, bootstrap = "wild"){
+boot_dist_ForMc <- function(ypl, ypr, yql, yqr, 
+                            coef.ql, coef.qr, coef.pl, coef.pr,
+                            Xql, Xqr, Xpl, Xpr,
+                            WXql, WXqr,
[…]

### 2016-08-01 R/rdfunctions_ForMc_test.R
Update the test for _ForMc functions
This commit is necessary to accommodate the changes in _ForMc functions.
This test shows that _ForMc functions still work as expected.

@@ -46,7 +46,6 @@ test_that("rdfunctions_ForMc.R gives the same results as rdfunctions_old.R in re
   expect_equivalent(old_epa, new_epa)})
 
 
-
 test_that("rdfunctions_ForMc.R gives the same results as rdfunctions.R in wild bootstrap.",{
   
   # rdfunctions.R take random draws for all observations in original data set,
@@ -86,27 +85,40 @@ test_that("rdfunctions_ForMc.R gives the same results as rdfunctions.R in wild b
   ypr <- y[x >= 0 & x < h]
   xpr <- x[x >= 0 & x < h]
   
-  wpl <- kweight(xpl, 0, h, kernel)
-  wpr <- kweight(xpr, 0, h, kernel)
+  # a vector of weight for residual bootstrap
   wql <- kweight(xql, 0, b, kernel)
   wqr <- kweight(xqr, 0, b, kernel)
+  wpl <- kweight(xpl, 0, b, kernel)
+  wpr <- kweight(xpr, 0, b, kernel)
   
-  Xpl <- cbind(1, poly(xpl, p, raw = T))
-  Xpr <- cbind(1, poly(xpr, p, raw = T))
-  Xql <- cbind(1, poly(xql, q, raw = T))
-  Xqr <- cbind(1, poly(xqr, q, raw = T))
+  # orthogonal polynomials
+  xql.poly <- poly(xql, q)
+  xqr.poly <- poly(xqr, q)
+  xpl.poly <- poly(xpl, p)
+  xpr.poly <- poly(xpr, p)
   
-  Wpl <- diag(wpl)
-  Wpr <- diag(wpr)
-  Wql <- diag(wql)
-  Wqr <- diag(wqr)
+  # design matrix
+  Xql <- cbind(1, poly(xql, q))
+  Xqr <- cbind(1, poly(xqr, q))
+  Xpl <- cbind(1, poly(xpl, p))
+  Xpr <- cbind(1, poly(xpr, p))
   
-  fit.ql <- Xql %*% solve(t(Xql) %*% Wql %*% Xql) %*% t(Xql) %*% Wql
-  fit.qr <- Xqr %*% solve(t(Xqr) %*% Wqr %*% Xqr) %*% t(Xqr) %*% Wqr
[…]

### 2016-08-01 R/rdfunctions.R
Add two functions to generate heteroskedastic data
The first function calculates average max[h,b] for each model and
kernel. The second function generate heteroskedastic data, with the
"effective" standard errors have mean 0.1295.

@@ -15,6 +15,33 @@ generate.data <- function(model.id) {
                   0.52 +  0.84*x - 0.1*3.00*x^2 - 0.3*7.99*x^3 - 0.1*9.01*x^4 + 3.56*x^5))
   return(data.frame(y = y, x = x))}
 
+## this function calculate average bandwidth in the homoskedastic case
+
+average_bw <- function(model.id, kernel) {
+  mean(replicate(500, {
+    dta <- generate.data(model.id)
+    max(rdbwselect_2014(dta$y, dta$x, kernel=kernel)$bws)
+  }))
+}
+
+## this function generate data with heteroskedasticity
+# standard error is firstly set to the square of expected outcome
+# rescale all standard error by a common factor 
+# so that they are on average 0.1295 within avebw
+
+generate.data.h <- function(model.id, avebw) {
+  x <- 2*rbeta(500, 2, 4) - 1
+  y <- switch(model.id,
+              ifelse(x < 0, 0.48 +  1.27*x +  7.18*x^2 + 20.21*x^3 + 21.54*x^4 + 7.33*x^5,
+                     0.52 +  0.84*x -  3.00*x^2 +  7.99*x^3 -  9.01*x^4 + 3.56*x^5),
+              ifelse(x < 0, 3.71 +  2.30*x +  3.28*x^2 +  1.45*x^3 +  0.23*x^4 + 0.03*x^5,
+                     0.26 + 18.49*x - 54.81*x^2 + 74.30*x^3 - 45.02*x^4 + 9.83*x^5),
+              ifelse(x < 0, 0.48 +  1.27*x - 0.5*7.18*x^2 + 0.7*20.21*x^3 + 1.1*21.54*x^4 + 1.5*7.33*x^5,
+                     0.52 +  0.84*x - 0.1*3.00*x^2 - 0.3*7.99*x^3 - 0.1*9.01*x^4 + 3.56*x^5))
+  se <- y^2/mean(y[abs(x) < avebw]^2)*0.1295
+  return(data.frame(y = y + rnorm(500, 0, se), x = x))
+}
+
 # Functions that implement the residual and wild bootstraps.
 
 residual_bootstrap <- function(m, y, x) {

### 2016-08-01 R/simulation.R
Modify simulation to accommodate _ForMc functions and heteroskedastic data
The function simulation.1 exports bootstrap basic CI.
The function simulation.2 exports CCT analytical CI.

@@ -9,132 +9,115 @@ library(xtable)
 try(source("slackrISE.R"), T)
 
 source("rdfunctions.R")
+source("rdfunctions_ForMc.R")
 
-#### for testing in my computer ####
-# N.ci <- 20
-# level <- 0.95
-# N.simu <- 20
-# N.core <- 2
-# N.bc <- 20
-
-#### to run in servor ####
 N.ci <- 999
 a <- 0.05
 N.simu <- 5000
-N.core <- 15
+N.core <- 35
 N.bc <- 500
 
-## simulation 1: coverage of CI from bootstrap
+## simulation 1: coverage of CI from bootstrap (basic CI)
 
-simulation.1 <- function(model.id, nsims) {
-
-  simu <- function() {
-    dta <- generate.data(model.id)
-    rdboot(dta$y, dta$x, a, N.bc, wild_bootstrap, nboot2 = N.ci,
-      p = 1, q = 2, type = "basic", kernel = "tri")
+simulation.1 <- function(model.id, kernel, heteroskedasticity = F) {
+  
+  if (heteroskedasticity == T) {
+    avebw <- average_bw(model.id, kernel)
+    gen_data <- function() generate.data.h(model.id, avebw)
+  } else {
+    gen_data <- function() generate.data(model.id)
   }
-
+  
+  simu <- function() {
+    dta <- gen_data()
+    rdboot_ForMc(dta$y, dta$x, a, N.bc, N.ci, 1, 2, "wild", kernel)[1, ]
+  }
+  
   cl <- makeCluster(N.core)
   registerDoParallel(cl)
-  export.obj <- c("N.ci", "N.bc", "level", "generate.data", "kweight",
-    "rd.estimate", "lpreg", "rd.ci", "wild_bootstrap", "rdboot",
-    "basic_estimator", "boot_estimator", "wild_values", "wild_weights",
-    "boot_interval", "boot_ci_basic")
+  export.obj <- c("N.ci", "N.bc", "a", "generate.data", "kweight", "rdboot_ForMc",
+                  "wild_values", "wild_weights", "boot_estimator_ForMc", "boot_dist_ForMc",
+                  "boot_ci_basic", "generate.data.h")
   collect.simu <- foreach(i=1:N.simu, .combine="rbind", .packages="rdrobust", .export=export.obj, .inorder=F) %dorng%
     simu()
   stopCluster(cl)
-
+  
[…]

### 2016-08-01 R/application.R
Fix an error in application
The original code does not specify which CI from bootstrap procedure
will be used. This commit specifies the basic CI.

@@ -38,7 +38,7 @@ robust <- function(dta) {
   ci1 <- cct$ci[3, ]
 
   boot <- rdboot_ForMc(dta$y, dta$x, 1 - level, N.bc, N.ci,
-          bootstrap = "wild", kernel = "uniform")
+          bootstrap = "wild", kernel = "uniform")[1, ]
   t2 <- boot[1]
   ci2 <- boot[2:3]
   return(matrix(c(t1, ci1, NA, bws,

### 2016-08-03 main_paper.tex
Make small refinement to Theorem 2
We should be clear that the distributional convergence in Theorem 2 is
uniform across tau. That's not necessary in Theorem 1 because the limit
is normal so convergence is automatically uniform across different
values of the mean. In Theorem 2 we're not explicit that the limit is
normal so we should be explicit about uniformity.
Redefine notation in appendix with kernel weights
Overdue :)
Minor wording tweak in Theorem 1's proof
Extend and tweak notation defined in appendix
This commit has two main features
- Adds population versions of some of the estimated c

--- 2016-07-29 main_paper.tex
@@
 Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
-everywhere else. Define the following additional notation:\footnote{%
+everywhere else. Much of the theory in this appendix applies to both
+sides of the cutoff symmetrially, so we will use a ``$\bullet$'' as a
+placeholder for either $+$ or $-$ in equations; i.e.\ the equation
+\[
+  \hat\mu_\bullet(h) = \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
+  (Y_i - \mu - \beta X_i)^2 K_{\bullet,h}(X_i)
+\]
+would define both $\hat\mu_+(h)$ and $\hat\mu_-(h)$ as
+\begin{align*}
+  \hat\mu_+(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
+  (Y_i - \mu - \beta X_i)^2 K_{+,h}(X_i) \\
+  \hat\mu_-(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
+  (Y_i - \mu - \beta X_i)^2 K_{-,h}(X_i).
+\end{align*}
+Define the following additional notation:\footnote{%
   As we mention in Section~\ref{background}, we have adopted CCT's
   notation where possible and these terms originate in that paper.} %
-$r_p(x) = (1,\ x,\dots,\ x^p)'$,
-\begin{align*}
-  (\hat{\mu}_{+,p}(h),\ \hat{\mu}_{+,p}^{(1)}(h),\dots,\ \hat\mu_{+,p}^{(p)}(h))'
-  &= \argmin_{\beta} \ssum[+]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2 \\
-  (\hat{\mu}_{-,p}(h),\ \hat{\mu}_{-,p}^{(1)}(h),\dots,\ \hat\mu_{-,p}^{(p)}(h))'
-  &= \argmin_{\beta} \ssum[-]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2
-\end{align*}
-and
-\begin{align*}
-  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
-  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
-  \Psi_{+,p,q}(h,b)
-  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
-    \V(Y_i \mid X_i) \\
-  \Psi_{-,p,q}(h,b)
-  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
-    \V(Y_i \mid X_i) \\
-  \Bf_+(h)
-  & = e_0' \Gamma_{+,1}^{-1}(h)
-    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
-  \Bf_-(h)
-  & = e_0' \Gamma_{-,1}^{-1}(h)
-    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
-\end{align*}
-
-Also, for reference, define the variance terms
+$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x > 0\}$, $\1_-(x) = \1\{x \leq 0\}$,
+\begin{align*}
+  \Gamma_{\bullet,p}(h)
+  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_p(X_i/h)' K_{\bullet,h}(X_i) \\
+  \Bf_\bullet(h)
+  & = e_0' \big(\Gamma_{\bullet,1}(h)\big)^{-1}
+    \tfrac{1}{n} \sum_{i=1}^n (X_i / h)^2 r_1(X_i/h) K_{\bullet,h}(X_i) \\
+  \Psi_{\bullet,p,q}(h,b)
+  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_q(X_i/b)'
+     K_{\bullet,h}(X_i) K_{\bullet,b}(X_i) \V(Y_i \mid X_i)
+\end{align*}
+as well as their population counterparts,
+\begin{align*}
+  \Gammat_{\bullet,p}(h) &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) f(h u) \1_\bullet(u) du \\
+  \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
+  \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
+     r_p(\tfrac{m}{h} u) r_q(\tfrac{m}{b} u)' K(\tfrac{m}{b} u) K(\tfrac{m}{h} u)
+     \V(Y_i \mid X_i = um) f(um) \1_\bullet(u) du \\
+  \Psi_{\bullet,p} &= \int_{-\infty}^\infty
+     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
+\end{align*}
+Remember that $f$ is the pdf of the running variable and $m = \min(h,b)$. Lemmas
+SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
+Assumptions~\ref{A1} and~\ref{A2} (for some, after normalization), namely that
+the following relationships hold:
+\begin{align}
+  \Gamma_{\bullet,p}(h) & = \Gammat_{\bullet,p}(h) + o_p(1) &
+  \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
+  \tfrac{hb}{m} \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
+  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
+\end{align}
+Implicitly the right column of equations holds as $h \to 0$.
+
+Also let $\hat\beta_{\bullet,p}(h)$ be the coefficient
+estimators from the weighted regression of $Y_i$ on $r_p(X_i)$. As in CCT, this
+implies that
+\begin{align*}
+  \hat\beta_{\bullet,p}(h) &= H_p \big(\Gammat_{\bullet,p}(h)\big)^{-1}
+    \sum_{i=1}^n r_p(X_i/h) Y_i K_{\bullet,h}(X_i)
+\end{align*}
+with $H_p(h) = \diag(1, h^{-1}, \dots, h^{-p})$.
+These coefficients are related to the quantities of interest by
+\begin{equation*}
+  \hat{\mu}_{\bullet,p}^{(\nu)}(h) = \nu! e_\nu' \hat\beta_{\bullet,p}(h).
+\end{equation*}
+for $\nu = 0,\dots,p$.
+
+For reference, define the variance terms
 \begin{equation*}
   V(h)
-  = e_0' \Big(\tfrac{1}{n} \Gamma_{-,1}^{-1} \Psi_{-,1} \Gamma_{-,1}^{-1}
-  + \tfrac{1}{n} \Gamma_{+,1}^{-1} \Psi_{+,1} \Gamma_{+,1}^{-1}\Big) e_0
+  = \tfrac{1}{n} e_0' \big(\Gamma_{-,1}(h)^{-1} \Psi_{-,1,1}(h,h)
+    \Gamma_{-,1}(h)^{-1}
+  + \Gamma_{+,1}(h)^{-1} \Psi_{+,1,1}(h,h) \Gamma_{+,1}(h)^{-1} \big) e_0
 \end{equation*}
@@
   C(h,b) =
-  n^{-1} e_2' \Big[
-    \Gamma_{+,2}^{-1}(b) \Psi_{+,2,2}(b,b) \Gamma_{+,2}^{-1}(b) \Bf^2_+(h) +
-    \Gamma_{-,2}^{-1}(b) \Psi_{-,2,2}(b,b) \Gamma_{-,2}^{-1}(b) \Bf^2_-(h)
-    \Big] e_2 \\
-  - 2 h^2 n^{-1} b^{-2}
+  \tfrac{1}{n} \, e_2' \big[
+    \Gamma_{+,2}(b)^{-1} \Psi_{+,2,2}(b,b) \Gamma_{+,2}(b)^{-1} \Bf_+(h)^2 +
+    \Gamma_{-,2}(b)^{-1} \Psi_{-,2,2}(b,b) \Gamma_{-,2}(b)^{-1} \Bf_-(h)^2
+  \big] e_2 \\
+  - \tfrac{2 h^2}{n b^{2}}
     e_0' \Big[
-    \Gamma^{-1}_{+,1}(h) \Psi_{+,1,2}(h,b) \Gamma_{+,2}^{-1}(b) \Bf_+(h) +
-    \Gamma^{-1}_{-,1}(h) \Psi_{-,1,2}(h,b) \Gamma_{-,2}^{-1}(b) \Bf_-(h)
+    \Gamma_{+,1}(h)^{-1} \Psi_{+,1,2}(h,b) \Gamma_{+,2}(b)^{-1} \Bf_+(h) +
+    \Gamma_{-,1}(h)^{-1} \Psi_{-,1,2}(h,b) \Gamma_{-,2}(b)^{-1} \Bf_-(h)
     \Big] e_2.
 \end{multline*}
-See CCT for the motivation and derivation of these formulas.
+See CCT for more on the motivation and derivation of these formulas.
 
@@
 The second equality holds because
-$\mu_+^{*(2)} = \hat\mu_{+,2}^{(2)}(b)$ and
-$\mu_-^{*(2)} = \hat\mu_{-,2}^{(2)}(b)$ almost surely. Asymptotic
-normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$,
-$\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}$, and
-$\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}$ using similar arguments to
+$\mu_\bullet^{*(2)} = \hat\mu_{\bullet,2}^{(2)}(b)$ almost surely. Asymptotic
+normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$ and
+$\hat\mu_{\bullet,2}^{(2)}(b) - \mu_\bullet^{(2)}$ using similar arguments to
 CCT's Lemma SA4.D.\qed
@@
 where
-$\epb_{+}^{*} =
-(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
-$\Omega_+(h,b)$ is an $M_+(b)$-dimensional vector with $i$th element
-$\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
-\begin{align*}
-  \Omega_{+,1i}(h,b) &=
+$\epb_{\bullet}^{*} =
+(\varepsilon_{\bullet,1}^{*},\dots,\varepsilon_{\bullet,M_\bullet(b)}^{*})'$ and
+$\Omega_\bullet(h,b)$ is an $M_\bullet(b)$-dimensional vector with $i$th element
+$\Omega_{\bullet,1i}(h,b) - \Omega_{\bullet,2i}(h,b)$, which are defined as
+\begin{align*}
+  \Omega_{\bullet,1i}(h,b) &=
   (1\quad 0)
-  \Big(\ssum[+]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
-    r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
+  \Big(\ssum[\bullet]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
+    r_1(X_{m_\bullet(b,i)} / h) \1\{h > X_{m_\bullet(b,i)} \geq 0\}
 \intertext{and}
-  \Omega_{+,2i}(h,b) &= (0\quad 0 \quad h^2)
-  \Big(\ssum[+]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
-    r_2(X_{m_+(b,i)} / b).
-\end{align*}
-The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same
-definitions as $\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the
-obvious substitutions of ``$-$'' for ``$+$.''
+  \Omega_{\bullet,2i}(h,b) &= (0\quad 0 \quad h^2)
+  \Big(\ssum[\bullet]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
+    r_2(X_{m_\bullet(b,i)} / b).
+\end{align*}
 
@@
 \end{equation*}
-with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th
+with $\epb_\bullet$ an i.i.d. random vector of length $M_\bullet(b)$, the $i$th
 element of which is distributed as
 \[
-  \varepsilon_{+,i} =^d
+  \varepsilon_{\bullet,i} =^d
   \begin{cases}
-    Y_{m_+(1,b)} - \E(Y_{m_+(1,b)} \mid X_{m_+(1,b)})
-    & \text{with probability\ } 1/M_+(b) \\
+    Y_{m_\bullet(1,b)} - \E(Y_{m_\bullet(1,b)} \mid X_{m_\bullet(1,b)})
+    & \text{with probability\ } 1/M_\bullet(b) \\
     \vdots \\
-    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(M_+(b),b)})
-    & \text{with probability\ } 1/M_+(b),
+    Y_{m_\bullet(M_\bullet(b),b)} - \E(Y_{m_\bullet(M_\bullet(b),b)} \mid X_{m_\bullet(M_\bullet(b),b)})
+    & \text{with probability\ } 1/M_\bullet(b).
   \end{cases}
 \]
-and $\epb_-$ the corresponding quantity after replacing ``+'' with
-``--.''  Consequently, it suffices to prove that
-\begin{gather}
+Consequently, it suffices to prove that
+\begin{equation}
   \label{eq:7}
-  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
-    V'(h,b)^{-1/2}\Omega_+(h,b)'\epb_{+}) \to^p 0
-  \intertext{and}
-  \label{eq:8}
-  \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
-    V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}) \to^p 0
-\end{gather}
+  \rho(V'(h,b)^{-1/2} \Omega_\bullet(h,b)'\epb_{\bullet}^{*},\
+    V'(h,b)^{-1/2}\Omega_\bullet(h,b)'\epb_{\bullet}) \to^p 0
+\end{equation}
 with $\rho$ the ``Mallows metric'' used by
@@
 
-We will only prove~\eqref{eq:7} since the proof of~\eqref{eq:8} is
-identical. By Theorem 2.1 of \cite{freedman1981}, we have
-\begin{align*}
-  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
-  &V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}) \\
-  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
-    \tr(V'(h,b)^{-1/2} \Omega_+(h,b)' \Omega_+(h,b)V'(h,b)^{-1/2}) \\
-  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
+By Theorem 2.1 of \cite{freedman1981}, we have
+\begin{align*}
+  \rho(V'(h,b)^{-1/2} \Omega_\bullet(h,b)'\epb_{\bullet}^{*},\
+  &V'(h,b)^{-1/2} \Omega_\bullet(h,b)'\epb_{\bullet}) \\
+  &\leq \rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \times
+    \tr(V'(h,b)^{-1/2} \Omega_\bullet(h,b)' \Omega_\bullet(h,b)V'(h,b)^{-1/2}) \\
+  &= \rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \times O_{p^{*}}(1),
 \end{align*}
 the second line holding as a consequence of CCT's Lemma SA1. So it suffices
-to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
+to show that $\rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \to^{p^{*}} 0$. Let
 $\varepsilon^\circ_i$ be an i.i.d. sequence randomly drawn from the
-realized values of $\epb_+$ with replacement and let
-$\bar{\varepsilon}^\circ = (1/M_+(b)) \osum[+]{i}{b} \varepsilon^\circ_i$. Then,
+realized values of $\epb_\bullet$ with replacement and let
+$\bar{\varepsilon}^\circ = (1/M_\bullet(b)) \osum[\bullet]{i}{b} \varepsilon^\circ_i$. Then,
 using the same arguments as \cite{freedman1981}, we have the upper bound
 \begin{equation*}
-  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
+  \rho(\varepsilon_{\bullet,1}^*, \varepsilon_{\bullet,1})
   \leq
   \Big((\bar\varepsilon^{\circ})^2 +
-  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2\Big)^{1/2}
-  + \rho(\varepsilon^\circ_1,\ \varepsilon_{+,1}).
+  (2/M_\bullet(b)) \osum[\bullet]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2\Big)^{1/2}
+  + \rho(\varepsilon^\circ_1,\ \varepsilon_{\bullet,1}).
 \end{equation*}
@@
 \[
-  (1/M_+(b)) \osum[+]{i}{b}
+  (1/M_\bullet(b)) \osum[\bullet]{i}{b}
   \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
@@
 by CCT's Lemma SA1, and
-$\rho(\varepsilon_1^\circ,\ \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
+$\rho(\varepsilon_1^\circ,\ \varepsilon_{\bullet,1}) \to^p 0$ by Lemma~8.4 of
 \cite{bickel1981}.\qed

### 2016-08-05 main_paper.tex
Make small tweak to Theorem 1's proof
Add additional notation for B to appendix
This commit adds population versions of B to the appendix.
Specify normalizing bandwidth in beta-hat definition
Fix scaling constant in start of Theorem 1's proof
Rewrite variance convergence of Theorem 2 proof
This commit updates the proof of Theorem 2 to work with the wild bootstrap.
Asymptotic normality remains to be established. The commit also tweaks some
notation relevant for the proof.

@@
 \end{assumption}
-To simplify notation, define the scaled and truncated kernel functions
+To simplify notation, let $m = \min(h,b)$, $m' = \max(h,b)$, and
+define the scaled and truncated kernel functions
 \begin{align*}
@@
   \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
+  \Bft_\bullet(h) & = e_0' \big(\Gammat_{\bullet,1}(h)\big)^{-1}
+    \int_{-\infty}^\infty r_1(u) u^2 K(u) f(h u) \1_\bullet(u) du \\
+  \Bf_\bullet & = e_0' \Gamma_{\bullet,1}^{-1} \int_{-\infty}^\infty r_1(u) u^2 K(u) \1_\bullet(u) du \\
   \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
@@
 \end{align*}
-Remember that $f$ is the pdf of the running variable and $m = \min(h,b)$. Lemmas
+Remember that $f$ is the pdf of the running variable. Lemmas
 SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
@@
   \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
-  \tfrac{hb}{m} \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
+  \Bf_{\bullet}(h) &= \Bft_{\bullet}(h) + o_p(1) &
+  \Bft_{\bullet}(h) &= \Bf_{\bullet} + o_p(1) \label{eq:11} \\
+  \max(h,b) \times \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
   \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
@@
 \begin{align*}
-  \hat\beta_{\bullet,p}(h) &= H_p \big(\Gammat_{\bullet,p}(h)\big)^{-1}
+  \hat\beta_{\bullet,p}(h) &= H_p(h) \Gamma_{\bullet,p}(h)^{-1}
     \sum_{i=1}^n r_p(X_i/h) Y_i K_{\bullet,h}(X_i)
@@
 \end{equation*}
-for $\nu = 0,\dots,p$.
+for $\nu = 0,\dots,p$ and similar arguments to those used above imply that
+\begin{equation*}
+  H_p(h)^{-1}(\hat\beta_{\bullet,p}(h) - \beta_{\bullet,p}(h))= O_p(1/\sqrt{nh}).
+\end{equation*}
 
@@
 By construction,
-\begin{align*}
-  \hat\beta^*_{+,p} - \beta^*_{+,p}
-  & = \Big(\sum_{i = 1}^n r_p(X_i) r_p(X_i)' K_{+,h}(X_i) \Big)^{-1}
-  \sum_{i = 1}^n r_p(X_i) K_{+,h}(X_i) \hat\varepsilon_i e_i^* \\
-  \hat\beta^*_{-,p} - \beta^*_{-,p}
-  &= \Big(\sum_{i = 1}^n r_p(X_i) r_p(X_i)' K_{-,h}(X_i)\Big)^{-1}
-  \sum_{i = 1}^n r_p(X_i) K_{-,h}(X_i) \hat\varepsilon_i e_i^*
-\end{align*}
-ensuring that
-\begin{align*}
-  \E^* \hat\mu_{+,1}^*(h) - \mu_{+}^{*}
-  &= h^{2} \mu_{+}^{*(2)} \Bf_{+}(h)/2,
-  &\E^* \hat\mu_{-,1}^*(h) - \mu_{-}^{*}
-  &= h^{2} \mu_{-}^{*(2)} \Bf_{-}(h)/2,
+\begin{equation*}
+  Y_i^* =
+  \begin{cases}
+    r_2(X_i/b)'H_2(b) \beta_{+,2}^* + \varepsilon_i^* & X_i > 0 \\
+    r_2(X_i/b)'H_2(b) \beta_{-,2}^* + \varepsilon_i^* & X_i \leq 0
+  \end{cases}
+\end{equation*}
+which, along with the definitions at the beginning of the appendix,
+ensures that
+\begin{align*}
+  \E^* \hat\mu_{\bullet,1}^*(h) - \mu_{\bullet}^{*}
+  = h^{2} \mu_{\bullet}^{*(2)} \Bf_{\bullet}(h)/2
 \end{align*}
@@
    - h^2 (\hat\mu_{+,2}^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
-  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
-\end{align*}
-where
-$\epb_{\bullet}^{*} =
-(\varepsilon_{\bullet,1}^{*},\dots,\varepsilon_{\bullet,M_\bullet(b)}^{*})'$ and
-$\Omega_\bullet(h,b)$ is an $M_\bullet(b)$-dimensional vector with $i$th element
-$\Omega_{\bullet,1i}(h,b) - \Omega_{\bullet,2i}(h,b)$, which are defined as
-\begin{align*}
-  \Omega_{\bullet,1i}(h,b) &=
-  (1\quad 0)
-  \Big(\ssum[\bullet]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
-    r_1(X_{m_\bullet(b,i)} / h) \1\{h > X_{m_\bullet(b,i)} \geq 0\}
-\intertext{and}
-  \Omega_{\bullet,2i}(h,b) &= (0\quad 0 \quad h^2)
-  \Big(\ssum[\bullet]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
-    r_2(X_{m_\bullet(b,i)} / b).
-\end{align*}
-
-Notice that~\eqref{eq:6} implies that
-\begin{equation*}
-  \hat\tau(h) - \Delta^*(h,b) - \tau
-  =^d \Omega_{+}(h,b)' \epb_{+} - \Omega_{-}(h,b)' \epb_{-} + O_p(h^3),
-\end{equation*}
-with $\epb_\bullet$ an i.i.d. random vector of length $M_\bullet(b)$, the $i$th
-element of which is distributed as
-\[
-  \varepsilon_{\bullet,i} =^d
-  \begin{cases}
-    Y_{m_\bullet(1,b)} - \E(Y_{m_\bullet(1,b)} \mid X_{m_\bullet(1,b)})
-    & \text{with probability\ } 1/M_\bullet(b) \\
-    \vdots \\
-    Y_{m_\bullet(M_\bullet(b),b)} - \E(Y_{m_\bullet(M_\bullet(b),b)} \mid X_{m_\bullet(M_\bullet(b),b)})
-    & \text{with probability\ } 1/M_\bullet(b).
-  \end{cases}
-\]
-Consequently, it suffices to prove that
-\begin{equation}
+  &= e_0' \Gamma_{+,1}(h)^{-1} \Big(\tfrac{1}{n}
+  \sum_{i=1}^n r_1(X_i/h) K_{+,h}(X_i) \varepsilon_i^*\Big)
+   - e_0' \Gamma_{-,1}(h)^{-1} \Big(\tfrac{1}{n}
+  \sum_{i=1}^n r_1(X_i/h) K_{-,h}(X_i) \varepsilon_i^*\Big) \\
+  &\quad + h^2 e_2' \Gamma_{-,2}(b)^{-1}
+    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{-,b}(X_i) \varepsilon_i^* \Big) \Bf_-(h) \\
+  &\quad - h^2 e_2' \Gamma_{+,2}(b)^{-1}
+    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{+,b}(X_i) \varepsilon_i^*\Big) \Bf_+(h).
+\end{align*}
+We will prove convergence of the variance first, then prove asymptotic
+normality.
+
+To prove convergence in probability of the bootstrap variance, note that the
+wild bootstrap ensures that, for any function $z(\cdot)$,
+\begin{equation*}
+  \V^*\Big(\sum_{i=1}^n z(X_i) \varepsilon_i^*\Big)
+  = \sum_{i=1}^n z(X_i)^2 \hat\varepsilon_i^2.
+\end{equation*}
+So, given this expression for the iterated bootstrap and the formula for the
+variance conditional on $X$ presented at the end of the introduction to this
+appendix, it suffices to show that
+\begin{gather}
+  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_1(X_i/h)' K_{\bullet,h}(X_i)^2
+  \hat\varepsilon_i^2 = \tfrac{1}{h} \Psit_{\bullet,1,1}(h,h) + o_p(\tfrac{1}{h})
+  \label{eq:3} \\
+  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_2(X_i/b)' K_{\bullet,h}(X_i)
+  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{1}{m'} \Psit_{\bullet,1,2}(h,b)
+  + o_p(\tfrac{1}{m'})
+  \label{eq:5} \\
+  \tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) r_2(X_i/b)' K_{\bullet,b}(X_i)^2
+  \hat\varepsilon_i^2 = \tfrac{1}{b} \Psit_{\bullet,2,2}(b,b) + o_p(\tfrac{1}{b}).
   \label{eq:7}
-  \rho(V'(h,b)^{-1/2} \Omega_\bullet(h,b)'\epb_{\bullet}^{*},\
-    V'(h,b)^{-1/2}\Omega_\bullet(h,b)'\epb_{\bullet}) \to^p 0
-\end{equation}
-with $\rho$ the ``Mallows metric'' used by
-\citet{bickel1981}.\footnote{%
-  For two random vectors $u$ and $v$ with finite 2nd moments,
-  $\rho(u, v)$ is defined as
-  \begin{equation*}
-    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
-    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
-  \end{equation*}}
-Convergence in $\rho$ is equivalent to convergence in both distribution
-and second moments. \citep[Lemma 8.3.]{bickel1981}
+\end{gather}
+But these convergence results follow from CCT's results on
+$\hat\mu_{\bullet,p}^{(\nu)}$, Lemma SA3 in particular.
 

### 2016-08-05 main_paper.tex
Make normalization explicit in Theorem 2
As originally written, the averages were not rescaled so the probability
distributions in Theorem 2 were degenerate. This commit adds the scaling
so that the distributions are not degenerate.
Fix spelling error in appendix

@@
   Under Assumptions~\ref{A1} and~\ref{A2},
-  \begin{gather*}
+  \begin{equation*}
     \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
-  \intertext{and}
+  \end{equation*}
+  and
+  \begin{multline*}
     \sup_{x,\tau}
-    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
-    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
-  \end{gather*}
+    \Big\rvert \Pr^*\big[ \sqrt{nh}
+    (\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^*) \leq x \big] \\
+    - \Pr\big[ \sqrt{nh}
+    (\hat\tau(h) - \Delta^*(h,b) - \tau) \leq x \big] \Big\lvert \to^p 0.
+  \end{multline*}
 \end{theorem}
@@
 everywhere else. Much of the theory in this appendix applies to both
-sides of the cutoff symmetrially, so we will use a ``$\bullet$'' as a
+sides of the cutoff symmetrically, so we will use a ``$\bullet$'' as a
 placeholder for either $+$ or $-$ in equations; i.e.\ the equation

### 2016-08-05 main_paper.tex
Minor notational fix in appendix
Revise normality proof for wild bootstrap
Basically asserts that Liapunov's condition holds.

@@
   \hat\beta_{\bullet,p}(h) &= H_p(h) \Gamma_{\bullet,p}(h)^{-1}
-    \sum_{i=1}^n r_p(X_i/h) Y_i K_{\bullet,h}(X_i)
+  \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) Y_i K_{\bullet,h}(X_i)
 \end{align*}
@@
 To prove convergence in probability of the bootstrap variance, note that the
-wild bootstrap ensures that, for any function $z(\cdot)$,
-\begin{equation*}
-  \V^*\Big(\sum_{i=1}^n z(X_i) \varepsilon_i^*\Big)
-  = \sum_{i=1}^n z(X_i)^2 \hat\varepsilon_i^2.
-\end{equation*}
-So, given this expression for the iterated bootstrap and the formula for the
+wild bootstrap ensures
+\begin{equation*}
+  \V^*\Big(\sum_{i=1}^n R(X_i) \varepsilon_i^*\Big)
+  = \sum_{i=1}^n R(X_i)^2 \hat\varepsilon_i^2.
+\end{equation*}
+for any measurable function $R(\cdot)$.
+Given this expression for the iterated bootstrap and the formula for the
 variance conditional on $X$ presented at the end of the introduction to this
@@
   \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_2(X_i/b)' K_{\bullet,h}(X_i)
-  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{1}{m'} \Psit_{\bullet,1,2}(h,b)
-  + o_p(\tfrac{1}{m'})
+  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{1}{b^2} \Psit_{\bullet,1,2}(h,b)
+  + o_p(\tfrac{1}{b^2})
   \label{eq:5} \\
@@
 But these convergence results follow from CCT's results on
-$\hat\mu_{\bullet,p}^{(\nu)}$, Lemma SA3 in particular.
-
-By Theorem 2.1 of \cite{freedman1981}, we have
-\begin{align*}
-  \rho(V'(h,b)^{-1/2} \Omega_\bullet(h,b)'\epb_{\bullet}^{*},\
-  &V'(h,b)^{-1/2} \Omega_\bullet(h,b)'\epb_{\bullet}) \\
-  &\leq \rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \times
-    \tr(V'(h,b)^{-1/2} \Omega_\bullet(h,b)' \Omega_\bullet(h,b)V'(h,b)^{-1/2}) \\
-  &= \rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \times O_{p^{*}}(1),
-\end{align*}
-the second line holding as a consequence of CCT's Lemma SA1. So it suffices
-to show that $\rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \to^{p^{*}} 0$. Let
-$\varepsilon^\circ_i$ be an i.i.d. sequence randomly drawn from the
-realized values of $\epb_\bullet$ with replacement and let
-$\bar{\varepsilon}^\circ = (1/M_\bullet(b)) \osum[\bullet]{i}{b} \varepsilon^\circ_i$. Then,
-using the same arguments as \cite{freedman1981}, we have the upper bound
-\begin{equation*}
-  \rho(\varepsilon_{\bullet,1}^*, \varepsilon_{\bullet,1})
-  \leq
-  \Big((\bar\varepsilon^{\circ})^2 +
-  (2/M_\bullet(b)) \osum[\bullet]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2\Big)^{1/2}
-  + \rho(\varepsilon^\circ_1,\ \varepsilon_{\bullet,1}).
-\end{equation*}
-But $(\bar\varepsilon^{\circ})^2 \to^p 0$ by the LLN,
-\[
-  (1/M_\bullet(b)) \osum[\bullet]{i}{b}
-  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
-\]
-by CCT's Lemma SA1, and
-$\rho(\varepsilon_1^\circ,\ \varepsilon_{\bullet,1}) \to^p 0$ by Lemma~8.4 of
-\cite{bickel1981}.\qed
+$\hat\mu_{\bullet,p}^{(\nu)}$, Lemmas SA3 and SA4 in particular,
+and standard arguments on the convergence of residuals to
+the population error term.
+
+Normality also follows standard arguments for the Wild
+bootstrap. Conditional on the regressors and residuals,
+$\{R(X_i) \hat\varepsilon_i e_i^* \}$ is a sequence of independent and
+mean zero random variables for any measurable function $R$, each with
+$p$th absolute moment
+$\lvert R(X_i) \hat\varepsilon_i \rvert^p \E \lvert e_i^*
+\rvert^{p}$.
+The result then holds as a consequence of the Lindeberg-Feller CLT if
+we establish that Liapunov's condition holds in probability, specifically that
+\begin{equation}\label{eq:17}
+  (\tfrac{m}{n})^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
+  \hat\varepsilon_i \rvert^{2+\delta} \to^{p} 0.
+\end{equation}
+with
+\begin{equation*}
+  R_\bullet(X_i) = \gamma_1 r_1(X_i/h) K_{\bullet,h}(X_i) + h^2 \gamma_2 r_2(X_i/b) K_{\bullet,b}(X_i)
+\end{equation*}
+for arbitrary nonzero vectors $\gamma_1'$ and $\gamma_2$.
+\citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}
+But similar arguments to those used for the variance establish~\eqref{eq:17}
+and complete the proof. \qed
 

### 2016-08-07 main_paper.tex
Edit DGP and its description
slightly change the DGP so that it incorperates both homoskedastic and
heteroskedastic cases.

--- 2016-08-05 main_paper.tex
@@
   &= \argmin_{\beta_0} \min_{\beta_1} \sum_{i=1}^{n}
-  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h} K(X_{i}/h).
+  \1\{X_{i}<0\} (Y_{i} - \beta_0 - X_{i} \beta_1)^{2} \tfrac{1}{h} K_{h}(X_{i}/h).
 \end{align*}
@@
 \end{assumption}
-To simplify notation, let $m = \min(h,b)$, $m' = \max(h,b)$, and
-define the scaled and truncated kernel functions
-\begin{align*}
-  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x > 0\} &
-  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \leq 0\}
+To simplify notation, define the scaled kernel functions
+\begin{align*}
+  K_h(x) &= \tfrac{1}{h} K(x/h)
 \intertext{and}
-  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x > 0\} &
-  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \leq 0\}.
+  K_b(x) &= \tfrac{1}{b} K(x/b).
 \end{align*}
@@
 treatment effect estimator and the higher order approximation used for the
-bootstrap.\footnote{%
-  It would be a slight abuse of notation for $K_{+,h}$, $K_{-,h}$,
-  $K_{+,b}$, and $K_{-,b}$ to all use different underlying kernels but
-  would not affect our proofs.} %
-For simplicity, however, we use the same function for all steps of
+bootstrap.  For simplicity, though, we use the same function for all steps of
 estimation in this paper.  Potentially different kernel functions and bandwidths
@@
 \begin{algorithm}[Bias estimation]\label{Alg1}
-  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2}.
+  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and define
+  \begin{align*}
+    I_{-} &= \{i : X_i < 0 \}, &
+    I_{+} &= \{i : X_i > 0 \}.
+  \end{align*}
+  Also define $M_{-}$ and $M_{+}$ to be the number of elements in $I_{-}$ and
+  $I_{+}$ respectively, and $m_{-}(1),\dots,m_{-}(M_{-})$ and
+  $m_{+}(1),\dots,m_{+}(M_+)$ to be subsequences of $1,\dots,n$ that index
+  $I_-$ and $I_+$, respectively.
   \begin{enumerate}
-  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$
-    with least squares using $K_{-,b}$ and $K_{+,b}$ for weights:
+  \item Estimate local second order polynomials $\hat g_{-}$ and $\hat g_{+}$ using
+    the observations in $I_-$ and $I_+$ and the kernel $K_{b}(X_{i})$:
     \begin{align}
@@
     \begin{align*}
-      \hat\beta_{-} &= \argmin_\beta \sum_{i = 1}^n
-      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{+,b}(X_{i}) \\
-      \hat\beta_{+} &= \argmin_\beta \sum_{i = 1}^n
-      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{-,b}(X_{i}).
+      \hat\beta_{-} &= \argmin_\beta \sum_{i \in I_-}
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}) \\
+      \hat\beta_{+} &= \argmin_\beta \sum_{i \in I_+}
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}).
     \end{align*}
@@
     \]
-    and calculate the residuals $\hat\varepsilon_{i} = Y_i - \hat g(X_i)$ for all $i$.
+    and calculate the residuals $\hat\varepsilon_{i} = Y_i - \hat g(X_i)$.
   \item Repeat the following steps $B_{1}$ times to produce the
     bootstrap estimates $\hat{\tau}_{1}^{*}(h),\dots,\hat\tau_{B_{1}}^{*}(h)$. For the
-    $k$th replication:
+    $k$th value:
     \begin{enumerate}
@@
         \intertext{and}
-        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}
-      \end{align*}
-      for all $i$.
+        Y_i^{*} &= \hat g(X_i) + \varepsilon_i^{*}.
+      \end{align*}
     \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
-      local linear model on the bootstrap data set using $K_{+,h}$ and $K_{-,h}$ for
-      weights:
+      local linear model on the bootstrap data set
       \begin{align*}
         \hat\mu_-^*(h)
-        &= \argmin_{\mu} \min_{\beta} \sum_{i =1}^n
-          (Y_i^* - \mu - \beta X_i)^2 K_{-,h}(X_{i}) \\
+        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{-}}
+          (Y_i^* - \mu - \beta X_i)^2 K_{h}(X_{i}) \\
         \hat\mu_+^*(h)
-        &= \argmin_{\mu} \min_{\beta} \sum_{i = 1}^n
-          (Y_i^* - \mu - \beta X_i)^2 K_{+,h}(X_{i}).
+        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{+}}
+          (Y_i^* - \mu - \beta X_i)^2 K_{h}(X_{i}).
       \end{align*}
@@
 \begin{algorithm}[Confidence intervals]\label{Alg2}
-  Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and
-  Algorithm~\ref{Alg1}.
+  Define the same notation as in Algorithm~\ref{Alg1}.
   \begin{enumerate}
@@
     $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
-    $k$th replication:
+    $k$th value:
     \begin{enumerate}
@@
       \end{align*}
-      for all $i = 1,\dots,n$.
     \item Calculate $\hat\mu_+^*(h)$ and $\hat\mu_-^*(h)$ by estimating the
-      local linear model on the bootstrap data set using $K_{+,h}$ and $K_{-,h}$
-      for weights:
+      local linear model on the bootstrap data set:
       \begin{align*}
         \hat\mu_-^*(h)
-        &= \argmin_{\mu} \min_{\beta} \sum_{i = 1}^n
-          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{-,h}(X_{i}), \\
+        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{-}}
+          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{h}(X_{i}) \\
         \hat\mu_+^*(h)
-        &= \argmin_{\mu} \min_{\beta} \sum_{i = 1}^n
-          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{+,h}(X_{i}).
+        &= \argmin_{\mu} \min_{\beta} \sum_{i \in I_{+}}
+          (Y_{i}^{*} - \mu - \beta X_{i})^{2}K_{h}(X_{i}).
       \end{align*}
     \item Apply Algorithm~\ref{Alg1} to the bootstrapped data set
-      $(Y_1^*,\, X_1),\dots,(Y_n^*,\, X_n)$ set using the same bandwidths
-      $h$ and $b$ that are used in the rest of this
+      using the same bandwidths $h$ and $b$ that are used in the rest of this
       algorithm but reestimating all of the local polynomials on the bootstrap
@@
     \item Save the bias-corrected estimator
-      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_-^*(h)
+      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
       - \Delta^{**}(h,b)$.
     \end{enumerate}
-  \item Define $\tau^* = \hat g_+(0) - \hat g_-(0)$ and use the empirical CDF of
-    $\hat\tau_1^{\prime*}(h,b) - \tau^*,\dots, \hat\tau_{B_2}^{\prime*}(h,b) - \tau^*$
-    as the sampling distribution of $\hat \tau' - \tau$.
+  \item Use the empirical CDF of
+    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
+    construct confidence intervals, etc.
   \end{enumerate}
@@
   \intertext{and}
-    \sup_{x,\tau}
+    \sup_{x}
     \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
@@
 X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
-\varepsilon_{i} &\sim N(0, 0.1295^2),
+\varepsilon_{i} &\sim N(0, \sigma_i^2) \\
+\sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
 \end{align*}
 where $j$ will index the specific DGP. This is the experimental design used by
-\citet{IK} and CCT, which we adopt here to make our simulation results directly
-comparable with theirs and with the rest of the literature. We
-will use the same three functional forms for $\mu_{j}$ as CCT as well.
+\citet{IK} and CCT, which we adopt here with adaptation to make our simulation results directly
+comparable with theirs and with the rest of the literature.
+They use this experimental design with a constant $\sigma_i = 0.1295$.
+We follow \cite{mackinnon2013thirty} to use a parameter $\gamma$ and a function $z(\gamma)$ to control the degree of heteroskedasticity.
+When $\gamma = 0$, we set $z(\gamma) = 0.1295$ such that our DGP is exactly the same as \citet{IK} and CCT.
+When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.\footnote{In practice, the optimal $h$ and $b$ are usually data driven, so $h$, $b$ and $\sigma_i$ are simultaneously determined.
+For simplicity, we use the following steps to find $z(\gamma)$: (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector, (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$ and (3) define $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$.} We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.
 
@@
 Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
-everywhere else. Much of the theory in this appendix applies to both
-sides of the cutoff symmetrially, so we will use a ``$\bullet$'' as a
-placeholder for either $+$ or $-$ in equations; i.e.\ the equation
-\[
-  \hat\mu_\bullet(h) = \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
-  (Y_i - \mu - \beta X_i)^2 K_{\bullet,h}(X_i)
-\]
-would define both $\hat\mu_+(h)$ and $\hat\mu_-(h)$ as
-\begin{align*}
-  \hat\mu_+(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
-  (Y_i - \mu - \beta X_i)^2 K_{+,h}(X_i) \\
-  \hat\mu_-(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
-  (Y_i - \mu - \beta X_i)^2 K_{-,h}(X_i).
-\end{align*}
-Define the following additional notation:\footnote{%
+everywhere else. Define the following additional notation:\footnote{%
   As we mention in Section~\ref{background}, we have adopted CCT's
   notation where possible and these terms originate in that paper.} %
-$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x > 0\}$, $\1_-(x) = \1\{x \leq 0\}$,
-\begin{align*}
-  \Gamma_{\bullet,p}(h)
-  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_p(X_i/h)' K_{\bullet,h}(X_i) \\
-  \Bf_\bullet(h)
-  & = e_0' \big(\Gamma_{\bullet,1}(h)\big)^{-1}
-    \tfrac{1}{n} \sum_{i=1}^n (X_i / h)^2 r_1(X_i/h) K_{\bullet,h}(X_i) \\
-  \Psi_{\bullet,p,q}(h,b)
-  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_q(X_i/b)'
-     K_{\bullet,h}(X_i) K_{\bullet,b}(X_i) \V(Y_i \mid X_i)
-\end{align*}
-as well as their population counterparts,
-\begin{align*}
-  \Gammat_{\bullet,p}(h) &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) f(h u) \1_\bullet(u) du \\
-  \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
-  \Bft_\bullet(h) & = e_0' \big(\Gammat_{\bullet,1}(h)\big)^{-1}
-    \int_{-\infty}^\infty r_1(u) u^2 K(u) f(h u) \1_\bullet(u) du \\
-  \Bf_\bullet & = e_0' \Gamma_{\bullet,1}^{-1} \int_{-\infty}^\infty r_1(u) u^2 K(u) \1_\bullet(u) du \\
-  \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
-     r_p(\tfrac{m}{h} u) r_q(\tfrac{m}{b} u)' K(\tfrac{m}{b} u) K(\tfrac{m}{h} u)
-     \V(Y_i \mid X_i = um) f(um) \1_\bullet(u) du \\
-  \Psi_{\bullet,p} &= \int_{-\infty}^\infty
-     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
-\end{align*}
-Remember that $f$ is the pdf of the running variable. Lemmas
-SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
-Assumptions~\ref{A1} and~\ref{A2} (for some, after normalization), namely that
-the following relationships hold:
-\begin{align}
-  \Gamma_{\bullet,p}(h) & = \Gammat_{\bullet,p}(h) + o_p(1) &
-  \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
-  \Bf_{\bullet}(h) &= \Bft_{\bullet}(h) + o_p(1) &
-  \Bft_{\bullet}(h) &= \Bf_{\bullet} + o_p(1) \label{eq:11} \\
-  \max(h,b) \times \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
-  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
-\end{align}
-Implicitly the right column of equations holds as $h \to 0$.
-
-Also let $\hat\beta_{\bullet,p}(h)$ be the coefficient
-estimators from the weighted regression of $Y_i$ on $r_p(X_i)$. As in CCT, this
-implies that
-\begin{align*}
-  \hat\beta_{\bullet,p}(h) &= H_p(h) \Gamma_{\bullet,p}(h)^{-1}
-    \sum_{i=1}^n r_p(X_i/h) Y_i K_{\bullet,h}(X_i)
-\end{align*}
-with $H_p(h) = \diag(1, h^{-1}, \dots, h^{-p})$.
-These coefficients are related to the quantities of interest by
-\begin{equation*}
-  \hat{\mu}_{\bullet,p}^{(\nu)}(h) = \nu! e_\nu' \hat\beta_{\bullet,p}(h).
-\end{equation*}
-for $\nu = 0,\dots,p$ and similar arguments to those used above imply that
-\begin{equation*}
-  H_p(h)^{-1}(\hat\beta_{\bullet,p}(h) - \beta_{\bullet,p}(h))= O_p(1/\sqrt{nh}).
-\end{equation*}
-
-For reference, define the variance terms
+$r_p(x) = (1,\ x,\dots,\ x^p)'$,
+\begin{align*}
+  (\hat{\mu}_{+,p}(h),\ \hat{\mu}_{+,p}^{(1)}(h),\dots,\ \hat\mu_{+,p}^{(p)}(h))'
+  &= \argmin_{\beta} \ssum[+]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2 \\
+  (\hat{\mu}_{-,p}(h),\ \hat{\mu}_{-,p}^{(1)}(h),\dots,\ \hat\mu_{-,p}^{(p)}(h))'
+  &= \argmin_{\beta} \ssum[-]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2
+\end{align*}
+and
+\begin{align*}
+  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
+  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
+  \Psi_{+,p,q}(h,b)
+  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
+    \V(Y_i \mid X_i) \\
+  \Psi_{-,p,q}(h,b)
+  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
+    \V(Y_i \mid X_i) \\
+  \Bf_+(h)
+  & = e_0' \Gamma_{+,1}^{-1}(h)
+    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
+  \Bf_-(h)
+  & = e_0' \Gamma_{-,1}^{-1}(h)
+    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
+\end{align*}
+
+Also, for reference, define the variance terms
 \begin{equation*}
   V(h)
-  = \tfrac{1}{n} e_0' \big(\Gamma_{-,1}(h)^{-1} \Psi_{-,1,1}(h,h)
-    \Gamma_{-,1}(h)^{-1}
-  + \Gamma_{+,1}(h)^{-1} \Psi_{+,1,1}(h,h) \Gamma_{+,1}(h)^{-1} \big) e_0
+  = e_0' \Big(\tfrac{1}{n} \Gamma_{-,1}^{-1} \Psi_{-,1} \Gamma_{-,1}^{-1}
+  + \tfrac{1}{n} \Gamma_{+,1}^{-1} \Psi_{+,1} \Gamma_{+,1}^{-1}\Big) e_0
 \end{equation*}
@@
   C(h,b) =
-  \tfrac{1}{n} \, e_2' \big[
-    \Gamma_{+,2}(b)^{-1} \Psi_{+,2,2}(b,b) \Gamma_{+,2}(b)^{-1} \Bf_+(h)^2 +
-    \Gamma_{-,2}(b)^{-1} \Psi_{-,2,2}(b,b) \Gamma_{-,2}(b)^{-1} \Bf_-(h)^2
-  \big] e_2 \\
-  - \tfrac{2 h^2}{n b^{2}}
+  n^{-1} e_2' \Big[
+    \Gamma_{+,2}^{-1}(b) \Psi_{+,2,2}(b,b) \Gamma_{+,2}^{-1}(b) \Bf^2_+(h) +
+    \Gamma_{-,2}^{-1}(b) \Psi_{-,2,2}(b,b) \Gamma_{-,2}^{-1}(b) \Bf^2_-(h)
+    \Big] e_2 \\
+  - 2 h^2 n^{-1} b^{-2}
     e_0' \Big[
-    \Gamma_{+,1}(h)^{-1} \Psi_{+,1,2}(h,b) \Gamma_{+,2}(b)^{-1} \Bf_+(h) +
-    \Gamma_{-,1}(h)^{-1} \Psi_{-,1,2}(h,b) \Gamma_{-,2}(b)^{-1} \Bf_-(h)
+    \Gamma^{-1}_{+,1}(h) \Psi_{+,1,2}(h,b) \Gamma_{+,2}^{-1}(b) \Bf_+(h) +
+    \Gamma^{-1}_{-,1}(h) \Psi_{-,1,2}(h,b) \Gamma_{-,2}^{-1}(b) \Bf_-(h)
     \Big] e_2.
 \end{multline*}
-See CCT for more on the motivation and derivation of these formulas.
+See CCT for the motivation and derivation of these formulas.
 
@@
 By construction,
-\begin{equation*}
-  Y_i^* =
-  \begin{cases}
-    r_2(X_i/b)'H_2(b) \beta_{+,2}^* + \varepsilon_i^* & X_i > 0 \\
-    r_2(X_i/b)'H_2(b) \beta_{-,2}^* + \varepsilon_i^* & X_i \leq 0
-  \end{cases}
-\end{equation*}
-which, along with the definitions at the beginning of the appendix,
-ensures that
-\begin{align*}
-  \E^* \hat\mu_{\bullet,1}^*(h) - \mu_{\bullet}^{*}
-  = h^{2} \mu_{\bullet}^{*(2)} \Bf_{\bullet}(h)/2
-\end{align*}
-almost surely and, consequently,
+\begin{align*}
+  \hat\beta^*_{+,p} - \beta^*_{+,p}
+  & = \Big(\sum_{i\in I_+} K_h(X_i) r_p(X_i) r_p(X_i)'\Big)^{-1}
+  \sum_{i \in I_+} K_h(X_i) r_p(X_i) \hat\varepsilon_i e_i^* \\
+  \hat\beta^*_{-,p} - \beta^*_{-,p}
+  &= \Big(\sum_{i\in I_-} K_h(X_i) r_p(X_i) r_p(X_i)'\Big)^{-1}
+  \sum_{i \in I_-} K_h(X_i) r_p(X_i) \hat\varepsilon_i e_i^*
+\end{align*}
+ensuring that
+\begin{align*}
+  \E^* \hat\mu_{+,1}^*(h) - \mu_{+}^{*}
+  &= h^{2} \mu_{+}^{*(2)} \Bf_{+}(h)/2,
+  &\E^* \hat\mu_{-,1}^*(h) - \mu_{-}^{*}
+  &= h^{2} \mu_{-}^{*(2)} \Bf_{-}(h)/2,
+\end{align*}
+almost surely. Consequently,
 \begin{equation*}
@@
 The second equality holds because
-$\mu_\bullet^{*(2)} = \hat\mu_{\bullet,2}^{(2)}(b)$ almost surely. Asymptotic
-normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$ and
-$\hat\mu_{\bullet,2}^{(2)}(b) - \mu_\bullet^{(2)}$ using similar arguments to
+$\mu_+^{*(2)} = \hat\mu_{+,2}^{(2)}(b)$ and
+$\mu_-^{*(2)} = \hat\mu_{-,2}^{(2)}(b)$ almost surely. Asymptotic
+normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$,
+$\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}$, and
+$\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}$ using similar arguments to
 CCT's Lemma SA4.D.\qed
@@
    - h^2 (\hat\mu_{+,2}^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
-  &= e_0' \Gamma_{+,1}(h)^{-1} \Big(\tfrac{1}{n}
-  \sum_{i=1}^n r_1(X_i/h) K_{+,h}(X_i) \varepsilon_i^*\Big)
-   - e_0' \Gamma_{-,1}(h)^{-1} \Big(\tfrac{1}{n}
-  \sum_{i=1}^n r_1(X_i/h) K_{-,h}(X_i) \varepsilon_i^*\Big) \\
-  &\quad + h^2 e_2' \Gamma_{-,2}(b)^{-1}
-    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{-,b}(X_i) \varepsilon_i^* \Big) \Bf_-(h) \\
-  &\quad - h^2 e_2' \Gamma_{+,2}(b)^{-1}
-    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{+,b}(X_i) \varepsilon_i^*\Big) \Bf_+(h).
-\end{align*}
-We will prove convergence of the variance first, then prove asymptotic
-normality.
-
-To prove convergence in probability of the bootstrap variance, note that the
-wild bootstrap ensures that, for any function $z(\cdot)$,
-\begin{equation*}
-  \V^*\Big(\sum_{i=1}^n z(X_i) \varepsilon_i^*\Big)
-  = \sum_{i=1}^n z(X_i)^2 \hat\varepsilon_i^2.
-\end{equation*}
-So, given this expression for the iterated bootstrap and the formula for the
-variance conditional on $X$ presented at the end of the introduction to this
-appendix, it suffices to show that
+  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
+\end{align*}
+where
+$\epb_{+}^{*} =
+(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
+$\Omega_+(h,b)$ is an $M_+(b)$-dimensional vector with $i$th element
+$\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
+\begin{align*}
+  \Omega_{+,1i}(h,b) &=
+  (1\quad 0)
+  \Big(\ssum[+]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
+    r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
+\intertext{and}
+  \Omega_{+,2i}(h,b) &= (0\quad 0 \quad h^2)
+  \Big(\ssum[+]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
+    r_2(X_{m_+(b,i)} / b).
+\end{align*}
+The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same
+definitions as $\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the
+obvious substitutions of ``$-$'' for ``$+$.''
+
+Notice that~\eqref{eq:6} implies that
+\begin{equation*}
+  \hat\tau(h) - \Delta^*(h,b) - \tau
+  =^d \Omega_{+}(h,b)' \epb_{+} - \Omega_{-}(h,b)' \epb_{-} + O_p(h^3),
+\end{equation*}
+with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th
+element of which is distributed as
+\[
+  \varepsilon_{+,i} =^d
+  \begin{cases}
+    Y_{m_+(1,b)} - \E(Y_{m_+(1,b)} \mid X_{m_+(1,b)})
+    & \text{with probability\ } 1/M_+(b) \\
+    \vdots \\
+    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(M_+(b),b)})
+    & \text{with probability\ } 1/M_+(b),
+  \end{cases}
+\]
+and $\epb_-$ the corresponding quantity after replacing ``+'' with
+``--.''  Consequently, it suffices to prove that
 \begin{gather}
-  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_1(X_i/h)' K_{\bullet,h}(X_i)^2
-  \hat\varepsilon_i^2 = \tfrac{1}{h} \Psit_{\bullet,1,1}(h,h) + o_p(\tfrac{1}{h})
-  \label{eq:3} \\
-  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_2(X_i/b)' K_{\bullet,h}(X_i)
-  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{1}{m'} \Psit_{\bullet,1,2}(h,b)
-  + o_p(\tfrac{1}{m'})
-  \label{eq:5} \\
-  \tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) r_2(X_i/b)' K_{\bullet,b}(X_i)^2
-  \hat\varepsilon_i^2 = \tfrac{1}{b} \Psit_{\bullet,2,2}(b,b) + o_p(\tfrac{1}{b}).
   \label{eq:7}
+  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
+    V'(h,b)^{-1/2}\Omega_+(h,b)'\epb_{+}) \to^p 0
+  \intertext{and}
+  \label{eq:8}
+  \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
+    V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}) \to^p 0
 \end{gather}
-But these convergence results follow from CCT's results on
-$\hat\mu_{\bullet,p}^{(\nu)}$, Lemma SA3 in particular.
-
-By Theorem 2.1 of \cite{freedman1981}, we have
-\begin{align*}
-  \rho(V'(h,b)^{-1/2} \Omega_\bullet(h,b)'\epb_{\bullet}^{*},\
-  &V'(h,b)^{-1/2} \Omega_\bullet(h,b)'\epb_{\bullet}) \\
-  &\leq \rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \times
-    \tr(V'(h,b)^{-1/2} \Omega_\bullet(h,b)' \Omega_\bullet(h,b)V'(h,b)^{-1/2}) \\
-  &= \rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \times O_{p^{*}}(1),
+with $\rho$ the ``Mallows metric'' used by
+\citet{bickel1981}.\footnote{%
+  For two random vectors $u$ and $v$ with finite 2nd moments,
+  $\rho(u, v)$ is defined as
+  \begin{equation*}
+    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
+    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
+  \end{equation*}}
+Convergence in $\rho$ is equivalent to convergence in both distribution
+and second moments. \citep[Lemma 8.3.]{bickel1981}
+
+We will only prove~\eqref{eq:7} since the proof of~\eqref{eq:8} is
+identical. By Theorem 2.1 of \cite{freedman1981}, we have
+\begin{align*}
+  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
+  &V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}) \\
+  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
+    \tr(V'(h,b)^{-1/2} \Omega_+(h,b)' \Omega_+(h,b)V'(h,b)^{-1/2}) \\
+  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
 \end{align*}
 the second line holding as a consequence of CCT's Lemma SA1. So it suffices
-to show that $\rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \to^{p^{*}} 0$. Let
+to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
 $\varepsilon^\circ_i$ be an i.i.d. sequence randomly drawn from the
-realized values of $\epb_\bullet$ with replacement and let
-$\bar{\varepsilon}^\circ = (1/M_\bullet(b)) \osum[\bullet]{i}{b} \varepsilon^\circ_i$. Then,
+realized values of $\epb_+$ with replacement and let
+$\bar{\varepsilon}^\circ = (1/M_+(b)) \osum[+]{i}{b} \varepsilon^\circ_i$. Then,
 using the same arguments as \cite{freedman1981}, we have the upper bound
 \begin{equation*}
-  \rho(\varepsilon_{\bullet,1}^*, \varepsilon_{\bullet,1})
+  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
   \leq
   \Big((\bar\varepsilon^{\circ})^2 +
-  (2/M_\bullet(b)) \osum[\bullet]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2\Big)^{1/2}
-  + \rho(\varepsilon^\circ_1,\ \varepsilon_{\bullet,1}).
+  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2\Big)^{1/2}
+  + \rho(\varepsilon^\circ_1,\ \varepsilon_{+,1}).
 \end{equation*}
@@
 \[
-  (1/M_\bullet(b)) \osum[\bullet]{i}{b}
+  (1/M_+(b)) \osum[+]{i}{b}
   \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
@@
 by CCT's Lemma SA1, and
-$\rho(\varepsilon_1^\circ,\ \varepsilon_{\bullet,1}) \to^p 0$ by Lemma~8.4 of
+$\rho(\varepsilon_1^\circ,\ \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
 \cite{bickel1981}.\qed

### 2016-08-07 main_paper.tex
Edit the table of simulation results
Add simulation results for wild bootstrap and heteroskedastic data, with
uniform kernel.

Take down naive bootstrap and triagular kernel.

@@
     DGP & Method       & Bias    & SD    & RMSE  & CI Coverage (\%) & CI Length \\
+    \midrule                                                     \\
+    \multicolumn{7}{l}{Homoskedastic data with $\gamma = 0$ (Panel A)}  \\
     \midrule
-    1   & \bootuni   & --0.014 & 0.067 & 0.069 & 93.4       & 0.242     \\
-        & \bootnaive & --0.040 & 0.042 & 0.058 & 89.0       & 0.182     \\
-        & \cctuni    & --0.014 & 0.067 & 0.069 & 92.5       & 0.246     \\
-        & \ccttri    & --0.011 & 0.067 & 0.068 & 91.4       & 0.239     \\
-        & \naiveuni  & --0.040 & 0.042 & 0.058 & 81.5       & 0.156     \\\\
-    2   & \bootuni   & --0.011 & 0.088 & 0.089 & 95.3       & 0.323     \\
-        & \bootnaive & --0.151 & 0.067 & 0.165 & 35.4       & 0.269     \\
-        & \cctuni    & --0.011 & 0.088 & 0.089 & 93.7       & 0.353     \\
-        & \ccttri    & --0.008 & 0.086 & 0.086 & 93.2       & 0.346     \\
-        & \naiveuni  & --0.151 & 0.067 & 0.165 & 29.5       & 0.230     \\\\
-    3   & \bootuni   & --0.004 & 0.065 & 0.065 & 95.9       & 0.247     \\
-        & \bootnaive &   0.033 & 0.052 & 0.062 & 91.3       & 0.215     \\
-        & \cctuni    & --0.004 & 0.065 & 0.065 & 93.8       & 0.251     \\
-        & \ccttri    & --0.005 & 0.065 & 0.065 & 93.4       & 0.244     \\
-        & \naiveuni  &   0.033 & 0.052 & 0.062 & 86.1       & 0.191     \\
+    1 & Wild bootstrap & --0.014 & 0.067 & 0.069 & 0.917 & 0.237 \\ 
+      & CCT            & --0.014 & 0.067 & 0.069 & 0.924 & 0.246 \\ 
+    2 & Wild bootstrap & --0.011 & 0.088 & 0.089 & 0.917 & 0.310 \\ 
+      & CCT            & --0.011 & 0.088 & 0.089 & 0.935 & 0.351 \\
+    3 & Wild bootstrap & --0.004 & 0.065 & 0.065 & 0.933 & 0.242 \\
+      & CCT            & --0.004 & 0.065 & 0.065 & 0.938 & 0.251 \\ 
+    \midrule                                                     \\
+    \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
+    \midrule
+    1 & Wild bootstrap & --0.011 & 0.081 & 0.081 & 0.924 & 0.289 \\
+      & CCT            & --0.011 & 0.081 & 0.081 & 0.931 & 0.301 \\ 
+    2 & Wild bootstrap & --0.011 & 0.097 & 0.098 & 0.912 & 0.334 \\ 
+      & CCT            & --0.011 & 0.097 & 0.097 & 0.931 & 0.379 \\
+    3 & Wild bootstrap &   0.000 & 0.116 & 0.116 & 0.923 & 0.409 \\ 
+      & CCT            &   0.000 & 0.116 & 0.116 & 0.935 & 0.432 \\
     \bottomrule

### 2016-08-07 main_paper.tex
Edit the description of simulation results

@@
 simulate 5000 samples from each of the three DGPs and calculate nominal 95\%
-two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
+two-sided confidence intervals.\footnote{The bootstrap principle ensures that $\hat\tau^{\prime*}(h,b) - \big[\hat g_+(0) - \hat g_-(0)\big]$ approximates the distribution of $\hat\tau^{\prime}(h,b) - \tau$, so the confidence interval of level 0.95 is constructed as$(\hat\tau^{\prime}(h,b) + \big[\hat g_+(0) - \hat g_-(0)\big] - \hat\tau^{\prime*}(h,b)_{0.975}, \hat\tau^{\prime}(h,b) + \big[\hat g_+(0) - \hat g_-(0)\big] - \hat\tau^{\prime*}(h,b)_{0.025})$, where $\hat\tau^{\prime*}(h,b)_{0.975}$ and $\hat\tau^{\prime*}(h,b)_{0.025}$ are the 97.5 and 2.5 percentiles of bootstrap distribution of bias-corrected estimator.} We use 999 bootstrap replications ($B_2$) to
 calculate the asymptotic distribution of the bias corrected estimator, and each
 of those replications uses an additional 500 replications ($B_1$) to estimate
-the bias. We use the $0.025$ and $0.975$ quantiles of the bootstrap distribution
-as the lower and upper bound of the interval, and the bandwidths, $h$ and $b$,
-are chosen using the AMSE-optimal rule proposed by CCT.
-
-We include several other procedures for comparison: CCT's bias-corrected
-interval using two different kernels, a ``naive'' uncorrected estimator and
-a bootstrapped version of the naive estimator, using 999 bootstrap replications.
-We estimate CCT's bias corrected procedure with AMSE-optimal bandwidths for both
-the uniform kernel and the triangular kernel. The uniform kernel provides a
-direct comparison with our bootstrap, while the triangular kernel may be more
-appealing to practitioners. The ``naive'' uncorrected interval
-estimator uses the uniform kernel, again with the optimal bandwidth $h$ proposed by
-\cite{IK}. And for the naive bootstrapped interval, we resample the data with
-equal weights, find optimal bandwidth for each bootstrapped sample and calculate
-the uncorrected point estimate. The $0.025$ and $0.975$ quantiles of the bootstrap
-distribution are used as the lower and upper bound of the confidence interval.
+the bias. The bandwidths, $h$ and $b$,
+are chosen using the AMSE-optimal rule proposed by CCT. We also estimate CCT's bias corrected procedure with AMSE-optimal bandwidths and
+the uniform kernel for direct comparison.
 
@@
 
-Table~\ref{tbl:1} presents the results of these simulations. The row labeled
-``\bootuni'' shows results for our proposed bootstrap interval; ``\bootnaive''
-shows results for the naive bootstrap interval; ``\cctuni'' and ``\ccttri'' show
-results for the analytically-corrected intervals; and ``\naiveuni'' shows results
-for the analytically-uncorrected interval. The first three columns give the bias,
+Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
+``Wild bootstrap'' shows results for our proposed bootstrap interval and ``CCT'' shows
+results for the analytically-corrected interval. The first three columns give the bias,
 standard deviation, and Root-MSE of the point
-estimators corresponding to each confidence interval.  As expected, the three
-bias corrected estimators (``\bootuni'', ``\cctuni'' and ``\ccttri'') have
+estimators corresponding to each confidence interval.  As expected, both
+bias corrected estimators have
 bias close to zero, with their standard deviation largely
@@
 The column ``CI Coverage'' lists the experimental coverage of each interval.
-All of the intervals from three robust estimators are reasonably close to their nominal coverage, although
-the analytically corrected estimators seem to persistently under-cover the true
-ATE (especially the one using triangular kernel). Our proposed bootstrap
-procedure consistently performs well, as it is about a percentage point closer
-to nominal coverage than the other interval estimators in DGPs 1 and 2, and is
-slightly conservative (95.9\% coverage) in DGP 3. The uncorrected intervals
-preform substantially worse---the naive analytical interval has coverage as
-bad as 30\% (in the second DGP) and never higher than 86\%, and the bootstrap
-version performs slightly better but still poorly. The final column, ``CI Length,''
-indicates that all three of the bias-corrected procedures generate intervals that are
-approximately the same length on average, but the uncorrected estimators produce
-much shorter intervals on average.
+In Panel A, all of the intervals from both robust estimators are reasonably close to their nominal coverage, although
+our proposed bootstrap procedure has coverages about one percentage lower than the CCT's analytical counterpart.
+In Panel B, the coverages are very similar to those in Panel A, showing that both procedures are robust to heteroskedasticity.
+The final column, ``CI Length,'' 
+indicates that our proposed bootstrap procedure consistently generates narrower intervals.
 

### 2016-08-07 main_paper.tex
Update application results
Edit table 2 and 3 and relevant text.

@@
     LM (2007)         & --1.114 & (--2.138                    & --0.090) & 36  &      &       & 0.027 \\
-    CCT               & --3.795 & (--7.037                    & --0.554) & 3   & .888 & 6.807 &       \\
-    Resid.\ bootstrap & --3.792 & (--6.512                    & --0.262) & 3   & .888 & 6.807 &       \\
+    CCT               & --3.795 & (--7.040                    & --0.551) & 3   & .888 & 6.807 &       \\ 
+    Wild bootstrap    & --3.800 & (--6.738                    & --0.450) & 3   & .888 & 6.807 &       \\
     \bottomrule
@@
 differ from the original estimates. The estimated ATEs are as high as --3.795
-from CCT and --3.792 from the bootstrap. Both are significantly different from
+from CCT and --3.800 from the bootstrap. Both are significantly different from
 zero, though the confidence intervals are also very wide, which is likely to be
@@
 larger point estimates in both panels. In Panel A, the ATE increases from 0.030
-to 0.055 (CCT) and 0.054 (bootstrap). In Panel B, the ATE increases from 0.037
+to 0.055 (CCT and bootstrap). In Panel B, the ATE increases from 0.037
 to 0.051 (CCT) and 0.052 (bootstrap). The confidence intervals tend to shift up
@@
     CCT            & 0.055 & (0.014                      & 0.096) & 3&.671 & 8.618       \\
-    Bootstrap & 0.054 & (0.013                      & 0.096) & 3&.671 & 8.618       \\\\
+    Wild bootstrap & 0.055 & (0.010                      & 0.096) & 3&.671 & 8.618       \\\\
     \multicolumn{5}{l}{Fraction ``some college or more'' (Panel B)}                   \\
@@
     CCT            & 0.051 & (0.004                      & 0.099) & 5&.076 & 10.251      \\
-    Bootstrap & 0.052 & (0.001                      & 0.094) & 5&.076 & 10.251      \\
+    Wild bootstrap & 0.052 & (0.007                      & 0.091) & 5&.076 & 10.251      \\
     \bottomrule

### 2016-08-08 main_paper.tex
Fix a typo in Algorithm 1
Kernel weights on the RHS (LHS) was used to estimate coefficients on the
LHS (RHS).

--- 2016-08-07 main_paper.tex
@@
 \end{assumption}
-To simplify notation, define the scaled kernel functions
-\begin{align*}
-  K_h(x) &= \tfrac{1}{h} K(x/h)
+To simplify notation, let $m = \min(h,b)$, $m' = \max(h,b)$, and
+define the scaled and truncated kernel functions
+\begin{align*}
+  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x > 0\} &
+  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \leq 0\}
 \intertext{and}
-  K_b(x) &= \tfrac{1}{b} K(x/b).
+  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x > 0\} &
+  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \leq 0\}.
 \end{align*}
@@
     \begin{align*}
-      \hat\beta_{-} &= \argmin_\beta \sum_{i \in I_-}
-      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}) \\
-      \hat\beta_{+} &= \argmin_\beta \sum_{i \in I_+}
-      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}).
+      \hat\beta_{-} &= \argmin_\beta \sum_{i = 1}^n
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{-,b}(X_{i}) \\
+      \hat\beta_{+} &= \argmin_\beta \sum_{i = 1}^n
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{+,b}(X_{i}).
     \end{align*}
@@
   Under Assumptions~\ref{A1} and~\ref{A2},
-  \begin{gather*}
+  \begin{equation*}
     \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
-  \intertext{and}
-    \sup_{x}
-    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
-    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
-  \end{gather*}
+  \end{equation*}
+  and
+  \begin{multline*}
+    \sup_{x,\tau}
+    \Big\rvert \Pr^*\big[ \sqrt{nh}
+    (\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^*) \leq x \big] \\
+    - \Pr\big[ \sqrt{nh}
+    (\hat\tau(h) - \Delta^*(h,b) - \tau) \leq x \big] \Big\lvert \to^p 0.
+  \end{multline*}
 \end{theorem}
@@
 X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
-\varepsilon_{i} &\sim N(0, \sigma_i^2) \\
-\sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
+\varepsilon_{i} &\sim N(0, 0.1295^2),
 \end{align*}
 where $j$ will index the specific DGP. This is the experimental design used by
-\citet{IK} and CCT, which we adopt here with adaptation to make our simulation results directly
-comparable with theirs and with the rest of the literature.
-They use this experimental design with a constant $\sigma_i = 0.1295$.
-We follow \cite{mackinnon2013thirty} to use a parameter $\gamma$ and a function $z(\gamma)$ to control the degree of heteroskedasticity.
-When $\gamma = 0$, we set $z(\gamma) = 0.1295$ such that our DGP is exactly the same as \citet{IK} and CCT.
-When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.\footnote{In practice, the optimal $h$ and $b$ are usually data driven, so $h$, $b$ and $\sigma_i$ are simultaneously determined.
-For simplicity, we use the following steps to find $z(\gamma)$: (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector, (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$ and (3) define $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$.} We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.
+\citet{IK} and CCT, which we adopt here to make our simulation results directly
+comparable with theirs and with the rest of the literature. We
+will use the same three functional forms for $\mu_{j}$ as CCT as well.
 
@@
     DGP & Method     & Bias   & SD    & RMSE   & CI Coverage (\%) & CI Length \\
-    \midrule                                                     \\
-    \multicolumn{7}{l}{Homoskedastic data with $\gamma = 0$ (Panel A)}  \\
     \midrule
-    1 & Wild bootstrap & --0.014 & 0.067 & 0.069 & 0.917 & 0.237 \\ 
-      & CCT            & --0.014 & 0.067 & 0.069 & 0.924 & 0.246 \\ 
-    2 & Wild bootstrap & --0.011 & 0.088 & 0.089 & 0.917 & 0.310 \\ 
-      & CCT            & --0.011 & 0.088 & 0.089 & 0.935 & 0.351 \\
-    3 & Wild bootstrap & --0.004 & 0.065 & 0.065 & 0.933 & 0.242 \\
-      & CCT            & --0.004 & 0.065 & 0.065 & 0.938 & 0.251 \\ 
-    \midrule                                                     \\
-    \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
-    \midrule
-    1 & Wild bootstrap & --0.011 & 0.081 & 0.081 & 0.924 & 0.289 \\
-      & CCT            & --0.011 & 0.081 & 0.081 & 0.931 & 0.301 \\ 
-    2 & Wild bootstrap & --0.011 & 0.097 & 0.098 & 0.912 & 0.334 \\ 
-      & CCT            & --0.011 & 0.097 & 0.097 & 0.931 & 0.379 \\
-    3 & Wild bootstrap &   0.000 & 0.116 & 0.116 & 0.923 & 0.409 \\ 
-      & CCT            &   0.000 & 0.116 & 0.116 & 0.935 & 0.432 \\
+    1   & \bootuni   & --0.014 & 0.067 & 0.069 & 93.4       & 0.242     \\
+        & \bootnaive & --0.040 & 0.042 & 0.058 & 89.0       & 0.182     \\
+        & \cctuni    & --0.014 & 0.067 & 0.069 & 92.5       & 0.246     \\
+        & \ccttri    & --0.011 & 0.067 & 0.068 & 91.4       & 0.239     \\
+        & \naiveuni  & --0.040 & 0.042 & 0.058 & 81.5       & 0.156     \\\\
+    2   & \bootuni   & --0.011 & 0.088 & 0.089 & 95.3       & 0.323     \\
+        & \bootnaive & --0.151 & 0.067 & 0.165 & 35.4       & 0.269     \\
+        & \cctuni    & --0.011 & 0.088 & 0.089 & 93.7       & 0.353     \\
+        & \ccttri    & --0.008 & 0.086 & 0.086 & 93.2       & 0.346     \\
+        & \naiveuni  & --0.151 & 0.067 & 0.165 & 29.5       & 0.230     \\\\
+    3   & \bootuni   & --0.004 & 0.065 & 0.065 & 95.9       & 0.247     \\
+        & \bootnaive &   0.033 & 0.052 & 0.062 & 91.3       & 0.215     \\
+        & \cctuni    & --0.004 & 0.065 & 0.065 & 93.8       & 0.251     \\
+        & \ccttri    & --0.005 & 0.065 & 0.065 & 93.4       & 0.244     \\
+        & \naiveuni  &   0.033 & 0.052 & 0.062 & 86.1       & 0.191     \\
     \bottomrule
@@
 Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
-everywhere else. Define the following additional notation:\footnote{%
+everywhere else. Much of the theory in this appendix applies to both
+sides of the cutoff symmetrically, so we will use a ``$\bullet$'' as a
+placeholder for either $+$ or $-$ in equations; i.e.\ the equation
+\[
+  \hat\mu_\bullet(h) = \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
+  (Y_i - \mu - \beta X_i)^2 K_{\bullet,h}(X_i)
+\]
+would define both $\hat\mu_+(h)$ and $\hat\mu_-(h)$ as
+\begin{align*}
+  \hat\mu_+(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
+  (Y_i - \mu - \beta X_i)^2 K_{+,h}(X_i) \\
+  \hat\mu_-(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
+  (Y_i - \mu - \beta X_i)^2 K_{-,h}(X_i).
+\end{align*}
+Define the following additional notation:\footnote{%
   As we mention in Section~\ref{background}, we have adopted CCT's
   notation where possible and these terms originate in that paper.} %
-$r_p(x) = (1,\ x,\dots,\ x^p)'$,
-\begin{align*}
-  (\hat{\mu}_{+,p}(h),\ \hat{\mu}_{+,p}^{(1)}(h),\dots,\ \hat\mu_{+,p}^{(p)}(h))'
-  &= \argmin_{\beta} \ssum[+]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2 \\
-  (\hat{\mu}_{-,p}(h),\ \hat{\mu}_{-,p}^{(1)}(h),\dots,\ \hat\mu_{-,p}^{(p)}(h))'
-  &= \argmin_{\beta} \ssum[-]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2
-\end{align*}
-and
-\begin{align*}
-  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
-  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
-  \Psi_{+,p,q}(h,b)
-  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
-    \V(Y_i \mid X_i) \\
-  \Psi_{-,p,q}(h,b)
-  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
-    \V(Y_i \mid X_i) \\
-  \Bf_+(h)
-  & = e_0' \Gamma_{+,1}^{-1}(h)
-    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
-  \Bf_-(h)
-  & = e_0' \Gamma_{-,1}^{-1}(h)
-    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
-\end{align*}
-
-Also, for reference, define the variance terms
+$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x > 0\}$, $\1_-(x) = \1\{x \leq 0\}$,
+\begin{align*}
+  \Gamma_{\bullet,p}(h)
+  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_p(X_i/h)' K_{\bullet,h}(X_i) \\
+  \Bf_\bullet(h)
+  & = e_0' \big(\Gamma_{\bullet,1}(h)\big)^{-1}
+    \tfrac{1}{n} \sum_{i=1}^n (X_i / h)^2 r_1(X_i/h) K_{\bullet,h}(X_i) \\
+  \Psi_{\bullet,p,q}(h,b)
+  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_q(X_i/b)'
+     K_{\bullet,h}(X_i) K_{\bullet,b}(X_i) \V(Y_i \mid X_i)
+\end{align*}
+as well as their population counterparts,
+\begin{align*}
+  \Gammat_{\bullet,p}(h) &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) f(h u) \1_\bullet(u) du \\
+  \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
+  \Bft_\bullet(h) & = e_0' \big(\Gammat_{\bullet,1}(h)\big)^{-1}
+    \int_{-\infty}^\infty r_1(u) u^2 K(u) f(h u) \1_\bullet(u) du \\
+  \Bf_\bullet & = e_0' \Gamma_{\bullet,1}^{-1} \int_{-\infty}^\infty r_1(u) u^2 K(u) \1_\bullet(u) du \\
+  \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
+     r_p(\tfrac{m}{h} u) r_q(\tfrac{m}{b} u)' K(\tfrac{m}{b} u) K(\tfrac{m}{h} u)
+     \V(Y_i \mid X_i = um) f(um) \1_\bullet(u) du \\
+  \Psi_{\bullet,p} &= \int_{-\infty}^\infty
+     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
+\end{align*}
+Remember that $f$ is the pdf of the running variable. Lemmas
+SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
+Assumptions~\ref{A1} and~\ref{A2} (for some, after normalization), namely that
+the following relationships hold:
+\begin{align}
+  \Gamma_{\bullet,p}(h) & = \Gammat_{\bullet,p}(h) + o_p(1) &
+  \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
+  \Bf_{\bullet}(h) &= \Bft_{\bullet}(h) + o_p(1) &
+  \Bft_{\bullet}(h) &= \Bf_{\bullet} + o_p(1) \label{eq:11} \\
+  \max(h,b) \times \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
+  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
+\end{align}
+Implicitly the right column of equations holds as $h \to 0$.
+
+Also let $\hat\beta_{\bullet,p}(h)$ be the coefficient
+estimators from the weighted regression of $Y_i$ on $r_p(X_i)$. As in CCT, this
+implies that
+\begin{align*}
+  \hat\beta_{\bullet,p}(h) &= H_p(h) \Gamma_{\bullet,p}(h)^{-1}
+  \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) Y_i K_{\bullet,h}(X_i)
+\end{align*}
+with $H_p(h) = \diag(1, h^{-1}, \dots, h^{-p})$.
+These coefficients are related to the quantities of interest by
+\begin{equation*}
+  \hat{\mu}_{\bullet,p}^{(\nu)}(h) = \nu! e_\nu' \hat\beta_{\bullet,p}(h).
+\end{equation*}
+for $\nu = 0,\dots,p$ and similar arguments to those used above imply that
+\begin{equation*}
+  H_p(h)^{-1}(\hat\beta_{\bullet,p}(h) - \beta_{\bullet,p}(h))= O_p(1/\sqrt{nh}).
+\end{equation*}
+
+For reference, define the variance terms
 \begin{equation*}
   V(h)
-  = e_0' \Big(\tfrac{1}{n} \Gamma_{-,1}^{-1} \Psi_{-,1} \Gamma_{-,1}^{-1}
-  + \tfrac{1}{n} \Gamma_{+,1}^{-1} \Psi_{+,1} \Gamma_{+,1}^{-1}\Big) e_0
+  = \tfrac{1}{n} e_0' \big(\Gamma_{-,1}(h)^{-1} \Psi_{-,1,1}(h,h)
+    \Gamma_{-,1}(h)^{-1}
+  + \Gamma_{+,1}(h)^{-1} \Psi_{+,1,1}(h,h) \Gamma_{+,1}(h)^{-1} \big) e_0
 \end{equation*}
@@
 By construction,
-\begin{align*}
-  \hat\beta^*_{+,p} - \beta^*_{+,p}
-  & = \Big(\sum_{i\in I_+} K_h(X_i) r_p(X_i) r_p(X_i)'\Big)^{-1}
-  \sum_{i \in I_+} K_h(X_i) r_p(X_i) \hat\varepsilon_i e_i^* \\
-  \hat\beta^*_{-,p} - \beta^*_{-,p}
-  &= \Big(\sum_{i\in I_-} K_h(X_i) r_p(X_i) r_p(X_i)'\Big)^{-1}
-  \sum_{i \in I_-} K_h(X_i) r_p(X_i) \hat\varepsilon_i e_i^*
-\end{align*}
-ensuring that
-\begin{align*}
-  \E^* \hat\mu_{+,1}^*(h) - \mu_{+}^{*}
-  &= h^{2} \mu_{+}^{*(2)} \Bf_{+}(h)/2,
-  &\E^* \hat\mu_{-,1}^*(h) - \mu_{-}^{*}
-  &= h^{2} \mu_{-}^{*(2)} \Bf_{-}(h)/2,
-\end{align*}
-almost surely. Consequently,
+\begin{equation*}
+  Y_i^* =
+  \begin{cases}
+    r_2(X_i/b)'H_2(b) \beta_{+,2}^* + \varepsilon_i^* & X_i > 0 \\
+    r_2(X_i/b)'H_2(b) \beta_{-,2}^* + \varepsilon_i^* & X_i \leq 0
+  \end{cases}
+\end{equation*}
+which, along with the definitions at the beginning of the appendix,
+ensures that
+\begin{align*}
+  \E^* \hat\mu_{\bullet,1}^*(h) - \mu_{\bullet}^{*}
+  = h^{2} \mu_{\bullet}^{*(2)} \Bf_{\bullet}(h)/2
+\end{align*}
+almost surely and, consequently,
 \begin{equation*}
@@
    - h^2 (\hat\mu_{+,2}^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
-  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
-\end{align*}
-where
-$\epb_{+}^{*} =
-(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
-$\Omega_+(h,b)$ is an $M_+(b)$-dimensional vector with $i$th element
-$\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
-\begin{align*}
-  \Omega_{+,1i}(h,b) &=
-  (1\quad 0)
-  \Big(\ssum[+]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
-    r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
-\intertext{and}
-  \Omega_{+,2i}(h,b) &= (0\quad 0 \quad h^2)
-  \Big(\ssum[+]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
-    r_2(X_{m_+(b,i)} / b).
-\end{align*}
-The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same
-definitions as $\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the
-obvious substitutions of ``$-$'' for ``$+$.''
-
-Notice that~\eqref{eq:6} implies that
-\begin{equation*}
-  \hat\tau(h) - \Delta^*(h,b) - \tau
-  =^d \Omega_{+}(h,b)' \epb_{+} - \Omega_{-}(h,b)' \epb_{-} + O_p(h^3),
-\end{equation*}
-with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th
-element of which is distributed as
-\[
-  \varepsilon_{+,i} =^d
-  \begin{cases}
-    Y_{m_+(1,b)} - \E(Y_{m_+(1,b)} \mid X_{m_+(1,b)})
-    & \text{with probability\ } 1/M_+(b) \\
-    \vdots \\
-    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(M_+(b),b)})
-    & \text{with probability\ } 1/M_+(b),
-  \end{cases}
-\]
-and $\epb_-$ the corresponding quantity after replacing ``+'' with
-``--.''  Consequently, it suffices to prove that
+  &= e_0' \Gamma_{+,1}(h)^{-1} \Big(\tfrac{1}{n}
+  \sum_{i=1}^n r_1(X_i/h) K_{+,h}(X_i) \varepsilon_i^*\Big)
+   - e_0' \Gamma_{-,1}(h)^{-1} \Big(\tfrac{1}{n}
+  \sum_{i=1}^n r_1(X_i/h) K_{-,h}(X_i) \varepsilon_i^*\Big) \\
+  &\quad + h^2 e_2' \Gamma_{-,2}(b)^{-1}
+    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{-,b}(X_i) \varepsilon_i^* \Big) \Bf_-(h) \\
+  &\quad - h^2 e_2' \Gamma_{+,2}(b)^{-1}
+    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{+,b}(X_i) \varepsilon_i^*\Big) \Bf_+(h).
+\end{align*}
+We will prove convergence of the variance first, then prove asymptotic
+normality.
+
+To prove convergence in probability of the bootstrap variance, note that the
+wild bootstrap ensures
+\begin{equation*}
+  \V^*\Big(\sum_{i=1}^n R(X_i) \varepsilon_i^*\Big)
+  = \sum_{i=1}^n R(X_i)^2 \hat\varepsilon_i^2.
+\end{equation*}
+for any measurable function $R(\cdot)$.
+Given this expression for the iterated bootstrap and the formula for the
+variance conditional on $X$ presented at the end of the introduction to this
+appendix, it suffices to show that
 \begin{gather}
+  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_1(X_i/h)' K_{\bullet,h}(X_i)^2
+  \hat\varepsilon_i^2 = \tfrac{1}{h} \Psit_{\bullet,1,1}(h,h) + o_p(\tfrac{1}{h})
+  \label{eq:3} \\
+  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_2(X_i/b)' K_{\bullet,h}(X_i)
+  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{1}{b^2} \Psit_{\bullet,1,2}(h,b)
+  + o_p(\tfrac{1}{b^2})
+  \label{eq:5} \\
+  \tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) r_2(X_i/b)' K_{\bullet,b}(X_i)^2
+  \hat\varepsilon_i^2 = \tfrac{1}{b} \Psit_{\bullet,2,2}(b,b) + o_p(\tfrac{1}{b}).
   \label{eq:7}
-  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
-    V'(h,b)^{-1/2}\Omega_+(h,b)'\epb_{+}) \to^p 0
-  \intertext{and}
-  \label{eq:8}
-  \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
-    V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}) \to^p 0
 \end{gather}
-with $\rho$ the ``Mallows metric'' used by
-\citet{bickel1981}.\footnote{%
-  For two random vectors $u$ and $v$ with finite 2nd moments,
-  $\rho(u, v)$ is defined as
-  \begin{equation*}
-    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
-    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
-  \end{equation*}}
-Convergence in $\rho$ is equivalent to convergence in both distribution
-and second moments. \citep[Lemma 8.3.]{bickel1981}
-
-We will only prove~\eqref{eq:7} since the proof of~\eqref{eq:8} is
-identical. By Theorem 2.1 of \cite{freedman1981}, we have
-\begin{align*}
-  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
-  &V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}) \\
-  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
-    \tr(V'(h,b)^{-1/2} \Omega_+(h,b)' \Omega_+(h,b)V'(h,b)^{-1/2}) \\
-  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
-\end{align*}
-the second line holding as a consequence of CCT's Lemma SA1. So it suffices
-to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
-$\varepsilon^\circ_i$ be an i.i.d. sequence randomly drawn from the
-realized values of $\epb_+$ with replacement and let
-$\bar{\varepsilon}^\circ = (1/M_+(b)) \osum[+]{i}{b} \varepsilon^\circ_i$. Then,
-using the same arguments as \cite{freedman1981}, we have the upper bound
-\begin{equation*}
-  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
-  \leq
-  \Big((\bar\varepsilon^{\circ})^2 +
-  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2\Big)^{1/2}
-  + \rho(\varepsilon^\circ_1,\ \varepsilon_{+,1}).
-\end{equation*}
-But $(\bar\varepsilon^{\circ})^2 \to^p 0$ by the LLN,
-\[
-  (1/M_+(b)) \osum[+]{i}{b}
-  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
-\]
-by CCT's Lemma SA1, and
-$\rho(\varepsilon_1^\circ,\ \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
-\cite{bickel1981}.\qed
+But these convergence results follow from CCT's results on
+$\hat\mu_{\bullet,p}^{(\nu)}$, Lemmas SA3 and SA4 in particular,
+and standard arguments on the convergence of residuals to
+the population error term.
+
+Normality also follows standard arguments for the Wild
+bootstrap. Conditional on the regressors and residuals,
+$\{R(X_i) \hat\varepsilon_i e_i^* \}$ is a sequence of independent and
+mean zero random variables for any measurable function $R$, each with
+$p$th absolute moment
+$\lvert R(X_i) \hat\varepsilon_i \rvert^p \E \lvert e_i^*
+\rvert^{p}$.
+The result then holds as a consequence of the Lindeberg-Feller CLT if
+we establish that Liapunov's condition holds in probability, specifically that
+\begin{equation}\label{eq:17}
+  (\tfrac{m}{n})^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
+  \hat\varepsilon_i \rvert^{2+\delta} \to^{p} 0.
+\end{equation}
+with
+\begin{equation*}
+  R_\bullet(X_i) = \gamma_1 r_1(X_i/h) K_{\bullet,h}(X_i) + h^2 \gamma_2 r_2(X_i/b) K_{\bullet,b}(X_i)
+\end{equation*}
+for arbitrary nonzero vectors $\gamma_1'$ and $\gamma_2$.
+\citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}
+But similar arguments to those used for the variance establish~\eqref{eq:17}
+and complete the proof. \qed
 

### 2016-08-08 main_paper.tex
Delete CI formula in the simulation section
This commite deletes CI fomula in the simulation section because I just
noticed that it is clearly explained in Algorithm 2.

--- 2016-08-07 main_paper.tex
@@
 simulate 5000 samples from each of the three DGPs and calculate nominal 95\%
-two-sided confidence intervals.\footnote{The bootstrap principle ensures that $\hat\tau^{\prime*}(h,b) - \big[\hat g_+(0) - \hat g_-(0)\big]$ approximates the distribution of $\hat\tau^{\prime}(h,b) - \tau$, so the confidence interval of level 0.95 is constructed as$(\hat\tau^{\prime}(h,b) + \big[\hat g_+(0) - \hat g_-(0)\big] - \hat\tau^{\prime*}(h,b)_{0.975}, \hat\tau^{\prime}(h,b) + \big[\hat g_+(0) - \hat g_-(0)\big] - \hat\tau^{\prime*}(h,b)_{0.025})$, where $\hat\tau^{\prime*}(h,b)_{0.975}$ and $\hat\tau^{\prime*}(h,b)_{0.025}$ are the 97.5 and 2.5 percentiles of bootstrap distribution of bias-corrected estimator.} We use 999 bootstrap replications ($B_2$) to
+two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
 calculate the asymptotic distribution of the bias corrected estimator, and each

### 2016-08-08 main_paper.tex

--- 2016-08-08 main_paper.tex
@@
 of those replications uses an additional 500 replications ($B_1$) to estimate
-the bias. We use the $0.025$ and $0.975$ quantiles of the bootstrap distribution
-as the lower and upper bound of the interval, and the bandwidths, $h$ and $b$,
-are chosen using the AMSE-optimal rule proposed by CCT.
-
-We include several other procedures for comparison: CCT's bias-corrected
-interval using two different kernels, a ``naive'' uncorrected estimator and
-a bootstrapped version of the naive estimator, using 999 bootstrap replications.
-We estimate CCT's bias corrected procedure with AMSE-optimal bandwidths for both
-the uniform kernel and the triangular kernel. The uniform kernel provides a
-direct comparison with our bootstrap, while the triangular kernel may be more
-appealing to practitioners. The ``naive'' uncorrected interval
-estimator uses the uniform kernel, again with the optimal bandwidth $h$ proposed by
-\cite{IK}. And for the naive bootstrapped interval, we resample the data with
-equal weights, find optimal bandwidth for each bootstrapped sample and calculate
-the uncorrected point estimate. The $0.025$ and $0.975$ quantiles of the bootstrap
-distribution are used as the lower and upper bound of the confidence interval.
+the bias. The bandwidths, $h$ and $b$,
+are chosen using the AMSE-optimal rule proposed by CCT. We also estimate CCT's bias corrected procedure with AMSE-optimal bandwidths and
+the uniform kernel for direct comparison.
 

### 2016-08-08 Reply_Referee1.tex
Updates Reply to Referee 1, adds the Reply file to Referee 2 which has not had all issues answered yet, changes the Macros file so that the notation for probability can follow the taste of referee 2 and edits the main text file to drop the most obvious places where the (unnecessary) condition h<b had been imposed.
referee 1, comment 5
The X_i^* only show up in algorithm 1 and 2, I have corrected them in
the rd2 repo.
referee 1, comment 6
fix a typo.
Add paragraph on computationally efficient implementations
One of the referees was concerned about computational burden. I've added
a short discus

@@
 
-   We share the reviewer's concern about the computing power demands an iterative bootstrap procedure imposes.
-Even though it would certainly be desirable to obtain an alternative implementation method that could achieve similar outcomes with a lesser burden on computational resources, it is not immediately obvious to the authors what that approach would be, and that was not the focus of the advances being proposed currently in this paper.
-Additionally, the simulation and computational work developed in this study seem to indicate that, in practice, the iterated bootstrap procedure proposed is not excessivelly burdensome for most applications faced by practitioners using standard computing resources widely available.
-Clearly, while we embrace the merit and usefulness of developing less intensive methods, we believe that even a demanding procedure like ours can be easily implemented by practitioners.
-\end{enumerate}
+This is much less
+of an issue than it appears, because many of the matrix calculations can be
+computed once and then reused in the bootstrap replications. (Any calculation
+that does not involve $Y$ can be reused.) Each bootstrap replication only
+requires a small number of matrix-vector multiplications which can be completed
+very quickly. We have added a short section after Algorithm 2 that explains
+this implementation detail, and we have also provided open source R code that
+implements the procedure efficiently.
 
@@
 
-Thank you for pointing out this was confusing. We changed it on the latest draft. \textbf{Yang, please check if this was updated throughout the paper.}
+Thank you for pointing out this was confusing. We changed it on the latest draft.
 
-\item \textit{``...Is it possible to propose a bootstrap approximation that dowes not require iterations...?''}
+\item \textit{``...Is it possible to propose a bootstrap approximation that does not require iterations...?''}
 

### 2016-08-08 main_paper.tex
Add paragraph on computationally efficient implementations
One of the referees was concerned about computational burden. I've added
a short discussion of the approach we used for our 'fast' version of
the code to the paper to address his or her concern.

@@
 \end{algorithm}
+
+One brief remark on implementing these algorithms. Many of the matrix operations
+required to estimate the local polynomials only involve the regressors and,
+therefore, only need to be computed once. For example, the parameter estimates
+for the linear model on the treated group are equal to
+\[
+\hat\beta_{+,1} = \underbrace{(\mathbf{X}' \mathbf{K}_+ \mathbf{X})^{-1} \mathbf{X}' \mathbf{K}_+}_{\mathbf{W}_{+,1}} \mathbf{Y}
+\]
+where
+\begin{align*}
+\mathbf{X} &= \begin{pmatrix*} 1 & X_1 \\ 1 & X_2 \\ \vdots & \vdots \\ 1 & X_n \end{pmatrix*} &
+\mathbf{Y} &= \begin{pmatrix*} Y_1 \\ Y_2 \\ \vdots \\ Y_n \end{pmatrix*} &
+\mathbf{K}_+ &= \begin{pmatrix*}
+  K_{+,h}(X_1) & 0 & \cdots & 0 \\
+  0 & K_{+,h}(X_2) & \cdots & 0 \\
+  0 & 0 & \ddots & 0 \\
+  0 & 0 & \cdots & K_{+,h}(X_n) \end{pmatrix*}.
+\end{align*}
+The matrix $\mathbf{W}_{+,1}$ is not affected by the bootstrap so it can be
+computed once initially and reused in the bootstrap calculations and each
+bootstrap replication just requires a single matrix-vector multiplication. The
+other parameter estimates have this property as well. Consequently, the
+computational burden of this iterated bootstrap is much lower than might
+appear.\footnote{%
+  An open-source implementation of this algorithm written in R, which was used
+  for the empirical and Monte Carlo components of this paper, is available
+  online at \url{https://github.com/grayclhn/boot-rd}.} %
 

### 2016-08-08 Reply_Referee1.tex
Tweak the introduction to the referee responses
I like giving a short summary of the major changes at the beginning of
the letter to each referee.

@@
 
-\section{Main Comments}
+\section{General overview of changes}
 
-\begin{enumerate}
- \item \textit{``...the proposed bootstrap method is only valid under conditional homocedasticity for distributional approximations...''}
+For this version of the paper, we have changed the bootstrap method from the
+residual bootstrap to the wild bootstrap. We have also updated the simulations
+to include DGPs featuring heteroskedasticity. We believe that the residual
+bootstrap used in the previous version is theoretically correct even under
+heteroskedastcity as long as the conditional variance is assumed to be smooth in
+a neighorbood around the cutoff point, since the residual bootstrap we initially
+proposed only resampled from that neighborhood, but we agree that in practice
+the wild bootstrap is likely to be more accurate and can accomodate forms of
+conditional heteroskedasticity that the residual bootstrap can not.
 
-  We thank the referee for pointing out this limitation of the procedure proposed initially and suggesting the use of a wild bootstrap.
-In the new version of the paper we provide a wild bootstrap algorithm and results about its properties, allowing for conditional heteroskedasticity.
+We have also relaxed the ``uniform kernel'' requirement and allow other kernels
+that are popular in practice. The title of the paper has been updated to reflect
+that change.
 
-\item \textit{``...the need of a computationally intensive iterated bootstrap for distributional approximations...''}
-
-This is much less
+The first referee expressed concern about the possible computational complexity of
+using an iterated bootstrap to produce confidence intervals. This is much less
 of an issue than it appears, because many of the matrix calculations can be

### 2016-08-08 Reply_Referee2.tex
Tweak the introduction to the referee responses
I like giving a short summary of the major changes at the beginning of
the letter to each referee.

@@
 
-\section{Main Comments}
+\section{General overview of changes}
 
-\begin{enumerate}
+For this version of the paper, we have changed the bootstrap method from the
+residual bootstrap to the wild bootstrap. We have also updated the simulations
+to include DGPs featuring heteroskedasticity. We believe that the residual
+bootstrap used in the previous version is theoretically correct even under
+heteroskedastcity as long as the conditional variance is assumed to be smooth in
+a neighorbood around the cutoff point, since the residual bootstrap we initially
+proposed only resampled from that neighborhood, but we agree that in practice
+the wild bootstrap is likely to be more accurate and can accomodate forms of
+conditional heteroskedasticity that the residual bootstrap can not.
 
-\item \textit{``..., the procedure is limited to the uniform kernel,...''}
-
- Thank you for focusing our attention to this expansion of the scope of the paper. The new draft incorporates other classes of kernel commonly used by practitioners.
-
- \item \textit{``Second, by using the residual bootstrap, any heteroskedastic feature of the DGP will be ignored.
-Assumption 1.4 ensures the validity of the procedure asymptotically, while the finite sample performance still depends on the variability of $\sigma^{2}(x)$ near the cutoff.
-The wild bootstrap seems to be a better alternative.''}
-
-  We thank the referee for pointing out this limitation of the procedure proposed initially and suggesting the use of a wild bootstrap.
-In the new version of the paper we provide a wild bootstrap algorithm and results about its properties, allowing for conditional heteroskedasticity.
-The title has been changed accordingly.
-
-\end{enumerate}
+We have also relaxed the ``uniform kernel'' requirement and allow other kernels
+that are popular in practice. The title of the paper has been updated to reflect
+that change.
 

### 2016-08-09 main_paper.tex
Minor edit in Proof 1
In Algorithm 1, zero is in the RHS. In this proof, zero is in the LHS.
This commit makes them consistent with each other: zero in the RHS.
Minor typo on theorem 1
Delete reference to naive bootstrap in the first paragraph of Section 4.

@@
 \end{equation}
-where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
+where $\Delta^*(h,b)$ is defined by Equation~\eqref{eq:9}.
 \end{theorem}
@@
 \section{Simulation Evidence}\label{sim}
-
 This section presents evidence from Monte Carlo simulations that the bootstrap
@@
 all of the bias corrected methods can offer substantial improvements over
-estimators that do not bias correct, including a ``naive'' bootstrap procedure.
+estimators that do not bias correct.
 
@@
   \begin{cases}
-    r_2(X_i/b)'H_2(b) \beta_{+,2}^* + \varepsilon_i^* & X_i > 0 \\
-    r_2(X_i/b)'H_2(b) \beta_{-,2}^* + \varepsilon_i^* & X_i \leq 0
+    r_2(X_i/b)'H_2(b) \beta_{+,2}^* + \varepsilon_i^* & X_i \geq 0 \\
+    r_2(X_i/b)'H_2(b) \beta_{-,2}^* + \varepsilon_i^* & X_i < 0
   \end{cases}

### 2016-08-09 main_paper.tex
Fix weak/strong inequality errors
The paper and literature use >= 0 for treatment and < 0 for control, but there
are a few instances in the paper where we mix up the weak and strong
inequalities. This commit fixes those errors.

@@
 \begin{align*}
-  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x > 0\} &
-  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \leq 0\}
+  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \geq 0\} &
+  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x < 0\}
 \intertext{and}
-  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x > 0\} &
-  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \leq 0\}.
+  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \geq 0\} &
+  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x < 0\}.
 \end{align*}
@@
   notation where possible and these terms originate in that paper.} %
-$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x > 0\}$, $\1_-(x) = \1\{x \leq 0\}$,
+$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x \geq 0\}$, $\1_-(x) = \1\{x < 0\}$,
 \begin{align*}

### 2016-08-09 main_paper.tex
Minor changes in description of heteroskedasticity on Simulations section.

@@
 comparable with theirs and with the rest of the literature.
-They use this experimental design with a constant $\sigma_i = 0.1295$.
-We follow \cite{mackinnon2013thirty} to use a parameter $\gamma$ and a function $z(\gamma)$ to control the degree of heteroskedasticity.
+While they use this experimental design with homoskedastic errors, we introduce heteroskedasticity following the design in \cite{mackinnon2013thirty}.
+We control the degree of heteroskedasticity through the parameter $\gamma$ and a function $z(\gamma)$.
 When $\gamma = 0$, we set $z(\gamma) = 0.1295$ such that our DGP is exactly the same as \citet{IK} and CCT.

### 2016-08-09 main_paper.tex
more details on how to generate heteroskedastic data
the original description was unclear.

--- 2016-08-09 main_paper.tex
@@
 \end{assumption}
-To simplify notation, let $m = \min(h,b)$, $m' = \max(h,b)$, and
-define the scaled and truncated kernel functions
-\begin{align*}
-  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \geq 0\} &
-  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x < 0\}
+To simplify notation, define the scaled kernel functions
+\begin{align*}
+  K_h(x) &= \tfrac{1}{h} K(x/h)
 \intertext{and}
-  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \geq 0\} &
-  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x < 0\}.
+  K_b(x) &= \tfrac{1}{b} K(x/b).
 \end{align*}
@@
     \begin{align*}
-      \hat\beta_{-} &= \argmin_\beta \sum_{i = 1}^n
-      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{-,b}(X_{i}) \\
-      \hat\beta_{+} &= \argmin_\beta \sum_{i = 1}^n
-      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{+,b}(X_{i}).
+      \hat\beta_{-} &= \argmin_\beta \sum_{i \in I_-}
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}) \\
+      \hat\beta_{+} &= \argmin_\beta \sum_{i \in I_+}
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{b}(X_{i}).
     \end{align*}
@@
 \end{equation}
-where $\Delta^*(h,b)$ is defined by Equation~\eqref{eq:9}.
+where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
 \end{theorem}
@@
     \item Save the bias-corrected estimator
-      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_-^*(h)
+      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
       - \Delta^{**}(h,b)$.
     \end{enumerate}
-  \item Define $\tau^* = \hat g_+(0) - \hat g_-(0)$ and use the empirical CDF of
-    $\hat\tau_1^{\prime*}(h,b) - \tau^*,\dots, \hat\tau_{B_2}^{\prime*}(h,b) - \tau^*$
-    as the sampling distribution of $\hat \tau' - \tau$.
+  \item Use the empirical CDF of
+    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
+    construct confidence intervals, etc.
   \end{enumerate}
 \end{algorithm}
-
-One brief remark on implementing these algorithms. Many of the matrix operations
-required to estimate the local polynomials only involve the regressors and,
-therefore, only need to be computed once. For example, the parameter estimates
-for the linear model on the treated group are equal to
-\[
-\hat\beta_{+,1} = \underbrace{(\mathbf{X}' \mathbf{K}_+ \mathbf{X})^{-1} \mathbf{X}' \mathbf{K}_+}_{\mathbf{W}_{+,1}} \mathbf{Y}
-\]
-where
-\begin{align*}
-\mathbf{X} &= \begin{pmatrix*} 1 & X_1 \\ 1 & X_2 \\ \vdots & \vdots \\ 1 & X_n \end{pmatrix*} &
-\mathbf{Y} &= \begin{pmatrix*} Y_1 \\ Y_2 \\ \vdots \\ Y_n \end{pmatrix*} &
-\mathbf{K}_+ &= \begin{pmatrix*}
-  K_{+,h}(X_1) & 0 & \cdots & 0 \\
-  0 & K_{+,h}(X_2) & \cdots & 0 \\
-  0 & 0 & \ddots & 0 \\
-  0 & 0 & \cdots & K_{+,h}(X_n) \end{pmatrix*}.
-\end{align*}
-The matrix $\mathbf{W}_{+,1}$ is not affected by the bootstrap so it can be
-computed once initially and reused in the bootstrap calculations and each
-bootstrap replication just requires a single matrix-vector multiplication. The
-other parameter estimates have this property as well. Consequently, the
-computational burden of this iterated bootstrap is much lower than might
-appear.\footnote{%
-  An open-source implementation of this algorithm written in R, which was used
-  for the empirical and Monte Carlo components of this paper, is available
-  online at \url{https://github.com/grayclhn/boot-rd}.} %
 
@@
   Under Assumptions~\ref{A1} and~\ref{A2},
-  \begin{equation*}
+  \begin{gather*}
     \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
-  \end{equation*}
-  and
-  \begin{multline*}
-    \sup_{x,\tau}
-    \Big\rvert \Pr^*\big[ \sqrt{nh}
-    (\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^*) \leq x \big] \\
-    - \Pr\big[ \sqrt{nh}
-    (\hat\tau(h) - \Delta^*(h,b) - \tau) \leq x \big] \Big\lvert \to^p 0.
-  \end{multline*}
+  \intertext{and}
+    \sup_{x}
+    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
+    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
+  \end{gather*}
 \end{theorem}
@@
 \section{Simulation Evidence}\label{sim}
+
 This section presents evidence from Monte Carlo simulations that the bootstrap
@@
 all of the bias corrected methods can offer substantial improvements over
-estimators that do not bias correct.
+estimators that do not bias correct, including a ``naive'' bootstrap procedure.
 
@@
 When $\gamma = 0$, we set $z(\gamma) = 0.1295$ such that our DGP is exactly the same as \citet{IK} and CCT.
-When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.\footnote{In practice, the optimal $h$ and $b$ are usually data driven, so $h$, $b$ and $\sigma_i$ are simultaneously determined.
-For simplicity, we use the following steps to find $z(\gamma)$: (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector, (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$ and (3) define $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$.} We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.
+When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.
+\footnote{The rescaling requires that $\max(h, b)$ is known, which is usually not the case in practice because $h$ and $b$ are data-driven.
+For simplicity, we firstly find $\overline{\max[h, b]}$ from \textbf{homoskedastic} data through 500 replications and then calculate $z(\gamma)$ for every bootstrap data accordingly.
+In our simulation, $\overline{\max[h, b]}$ is obtained by (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector and (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$.
+Once $\overline{\max[h, b]}$ is known, we use it to generate heteroskedastic data using following steps: (1) generate random running variable $X_i$, (2) let $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$ and calculate the standard deviation and (3) generate disturbance term and outcome $Y_i$ accordingly.}
+We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.
 
@@
 Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
-everywhere else. Much of the theory in this appendix applies to both
-sides of the cutoff symmetrically, so we will use a ``$\bullet$'' as a
-placeholder for either $+$ or $-$ in equations; i.e.\ the equation
-\[
-  \hat\mu_\bullet(h) = \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
-  (Y_i - \mu - \beta X_i)^2 K_{\bullet,h}(X_i)
-\]
-would define both $\hat\mu_+(h)$ and $\hat\mu_-(h)$ as
-\begin{align*}
-  \hat\mu_+(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
-  (Y_i - \mu - \beta X_i)^2 K_{+,h}(X_i) \\
-  \hat\mu_-(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
-  (Y_i - \mu - \beta X_i)^2 K_{-,h}(X_i).
-\end{align*}
-Define the following additional notation:\footnote{%
+everywhere else. Define the following additional notation:\footnote{%
   As we mention in Section~\ref{background}, we have adopted CCT's
   notation where possible and these terms originate in that paper.} %
-$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x \geq 0\}$, $\1_-(x) = \1\{x < 0\}$,
-\begin{align*}
-  \Gamma_{\bullet,p}(h)
-  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_p(X_i/h)' K_{\bullet,h}(X_i) \\
-  \Bf_\bullet(h)
-  & = e_0' \big(\Gamma_{\bullet,1}(h)\big)^{-1}
-    \tfrac{1}{n} \sum_{i=1}^n (X_i / h)^2 r_1(X_i/h) K_{\bullet,h}(X_i) \\
-  \Psi_{\bullet,p,q}(h,b)
-  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_q(X_i/b)'
-     K_{\bullet,h}(X_i) K_{\bullet,b}(X_i) \V(Y_i \mid X_i)
-\end{align*}
-as well as their population counterparts,
-\begin{align*}
-  \Gammat_{\bullet,p}(h) &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) f(h u) \1_\bullet(u) du \\
-  \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
-  \Bft_\bullet(h) & = e_0' \big(\Gammat_{\bullet,1}(h)\big)^{-1}
-    \int_{-\infty}^\infty r_1(u) u^2 K(u) f(h u) \1_\bullet(u) du \\
-  \Bf_\bullet & = e_0' \Gamma_{\bullet,1}^{-1} \int_{-\infty}^\infty r_1(u) u^2 K(u) \1_\bullet(u) du \\
-  \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
-     r_p(\tfrac{m}{h} u) r_q(\tfrac{m}{b} u)' K(\tfrac{m}{b} u) K(\tfrac{m}{h} u)
-     \V(Y_i \mid X_i = um) f(um) \1_\bullet(u) du \\
-  \Psi_{\bullet,p} &= \int_{-\infty}^\infty
-     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
-\end{align*}
-Remember that $f$ is the pdf of the running variable. Lemmas
-SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
-Assumptions~\ref{A1} and~\ref{A2} (for some, after normalization), namely that
-the following relationships hold:
-\begin{align}
-  \Gamma_{\bullet,p}(h) & = \Gammat_{\bullet,p}(h) + o_p(1) &
-  \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
-  \Bf_{\bullet}(h) &= \Bft_{\bullet}(h) + o_p(1) &
-  \Bft_{\bullet}(h) &= \Bf_{\bullet} + o_p(1) \label{eq:11} \\
-  \max(h,b) \times \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
-  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
-\end{align}
-Implicitly the right column of equations holds as $h \to 0$.
-
-Also let $\hat\beta_{\bullet,p}(h)$ be the coefficient
-estimators from the weighted regression of $Y_i$ on $r_p(X_i)$. As in CCT, this
-implies that
-\begin{align*}
-  \hat\beta_{\bullet,p}(h) &= H_p(h) \Gamma_{\bullet,p}(h)^{-1}
-  \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) Y_i K_{\bullet,h}(X_i)
-\end{align*}
-with $H_p(h) = \diag(1, h^{-1}, \dots, h^{-p})$.
-These coefficients are related to the quantities of interest by
-\begin{equation*}
-  \hat{\mu}_{\bullet,p}^{(\nu)}(h) = \nu! e_\nu' \hat\beta_{\bullet,p}(h).
-\end{equation*}
-for $\nu = 0,\dots,p$ and similar arguments to those used above imply that
-\begin{equation*}
-  H_p(h)^{-1}(\hat\beta_{\bullet,p}(h) - \beta_{\bullet,p}(h))= O_p(1/\sqrt{nh}).
-\end{equation*}
-
-For reference, define the variance terms
+$r_p(x) = (1,\ x,\dots,\ x^p)'$,
+\begin{align*}
+  (\hat{\mu}_{+,p}(h),\ \hat{\mu}_{+,p}^{(1)}(h),\dots,\ \hat\mu_{+,p}^{(p)}(h))'
+  &= \argmin_{\beta} \ssum[+]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2 \\
+  (\hat{\mu}_{-,p}(h),\ \hat{\mu}_{-,p}^{(1)}(h),\dots,\ \hat\mu_{-,p}^{(p)}(h))'
+  &= \argmin_{\beta} \ssum[-]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2
+\end{align*}
+and
+\begin{align*}
+  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
+  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
+  \Psi_{+,p,q}(h,b)
+  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
+    \V(Y_i \mid X_i) \\
+  \Psi_{-,p,q}(h,b)
+  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
+    \V(Y_i \mid X_i) \\
+  \Bf_+(h)
+  & = e_0' \Gamma_{+,1}^{-1}(h)
+    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
+  \Bf_-(h)
+  & = e_0' \Gamma_{-,1}^{-1}(h)
+    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
+\end{align*}
+
+Also, for reference, define the variance terms
 \begin{equation*}
   V(h)
-  = \tfrac{1}{n} e_0' \big(\Gamma_{-,1}(h)^{-1} \Psi_{-,1,1}(h,h)
-    \Gamma_{-,1}(h)^{-1}
-  + \Gamma_{+,1}(h)^{-1} \Psi_{+,1,1}(h,h) \Gamma_{+,1}(h)^{-1} \big) e_0
+  = e_0' \Big(\tfrac{1}{n} \Gamma_{-,1}^{-1} \Psi_{-,1} \Gamma_{-,1}^{-1}
+  + \tfrac{1}{n} \Gamma_{+,1}^{-1} \Psi_{+,1} \Gamma_{+,1}^{-1}\Big) e_0
 \end{equation*}
@@
 By construction,
-\begin{equation*}
-  Y_i^* =
-  \begin{cases}
-    r_2(X_i/b)'H_2(b) \beta_{+,2}^* + \varepsilon_i^* & X_i \geq 0 \\
-    r_2(X_i/b)'H_2(b) \beta_{-,2}^* + \varepsilon_i^* & X_i < 0
-  \end{cases}
-\end{equation*}
-which, along with the definitions at the beginning of the appendix,
-ensures that
-\begin{align*}
-  \E^* \hat\mu_{\bullet,1}^*(h) - \mu_{\bullet}^{*}
-  = h^{2} \mu_{\bullet}^{*(2)} \Bf_{\bullet}(h)/2
-\end{align*}
-almost surely and, consequently,
+\begin{align*}
+  \hat\beta^*_{+,p} - \beta^*_{+,p}
+  & = \Big(\sum_{i\in I_+} K_h(X_i) r_p(X_i) r_p(X_i)'\Big)^{-1}
+  \sum_{i \in I_+} K_h(X_i) r_p(X_i) \hat\varepsilon_i e_i^* \\
+  \hat\beta^*_{-,p} - \beta^*_{-,p}
+  &= \Big(\sum_{i\in I_-} K_h(X_i) r_p(X_i) r_p(X_i)'\Big)^{-1}
+  \sum_{i \in I_-} K_h(X_i) r_p(X_i) \hat\varepsilon_i e_i^*
+\end{align*}
+ensuring that
+\begin{align*}
+  \E^* \hat\mu_{+,1}^*(h) - \mu_{+}^{*}
+  &= h^{2} \mu_{+}^{*(2)} \Bf_{+}(h)/2,
+  &\E^* \hat\mu_{-,1}^*(h) - \mu_{-}^{*}
+  &= h^{2} \mu_{-}^{*(2)} \Bf_{-}(h)/2,
+\end{align*}
+almost surely. Consequently,
 \begin{equation*}
@@
    - h^2 (\hat\mu_{+,2}^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
-  &= e_0' \Gamma_{+,1}(h)^{-1} \Big(\tfrac{1}{n}
-  \sum_{i=1}^n r_1(X_i/h) K_{+,h}(X_i) \varepsilon_i^*\Big)
-   - e_0' \Gamma_{-,1}(h)^{-1} \Big(\tfrac{1}{n}
-  \sum_{i=1}^n r_1(X_i/h) K_{-,h}(X_i) \varepsilon_i^*\Big) \\
-  &\quad + h^2 e_2' \Gamma_{-,2}(b)^{-1}
-    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{-,b}(X_i) \varepsilon_i^* \Big) \Bf_-(h) \\
-  &\quad - h^2 e_2' \Gamma_{+,2}(b)^{-1}
-    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{+,b}(X_i) \varepsilon_i^*\Big) \Bf_+(h).
-\end{align*}
-We will prove convergence of the variance first, then prove asymptotic
-normality.
-
-To prove convergence in probability of the bootstrap variance, note that the
-wild bootstrap ensures
-\begin{equation*}
-  \V^*\Big(\sum_{i=1}^n R(X_i) \varepsilon_i^*\Big)
-  = \sum_{i=1}^n R(X_i)^2 \hat\varepsilon_i^2.
-\end{equation*}
-for any measurable function $R(\cdot)$.
-Given this expression for the iterated bootstrap and the formula for the
-variance conditional on $X$ presented at the end of the introduction to this
-appendix, it suffices to show that
+  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
+\end{align*}
+where
+$\epb_{+}^{*} =
+(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
+$\Omega_+(h,b)$ is an $M_+(b)$-dimensional vector with $i$th element
+$\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
+\begin{align*}
+  \Omega_{+,1i}(h,b) &=
+  (1\quad 0)
+  \Big(\ssum[+]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
+    r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
+\intertext{and}
+  \Omega_{+,2i}(h,b) &= (0\quad 0 \quad h^2)
+  \Big(\ssum[+]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
+    r_2(X_{m_+(b,i)} / b).
+\end{align*}
+The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same
+definitions as $\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the
+obvious substitutions of ``$-$'' for ``$+$.''
+
+Notice that~\eqref{eq:6} implies that
+\begin{equation*}
+  \hat\tau(h) - \Delta^*(h,b) - \tau
+  =^d \Omega_{+}(h,b)' \epb_{+} - \Omega_{-}(h,b)' \epb_{-} + O_p(h^3),
+\end{equation*}
+with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th
+element of which is distributed as
+\[
+  \varepsilon_{+,i} =^d
+  \begin{cases}
+    Y_{m_+(1,b)} - \E(Y_{m_+(1,b)} \mid X_{m_+(1,b)})
+    & \text{with probability\ } 1/M_+(b) \\
+    \vdots \\
+    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(M_+(b),b)})
+    & \text{with probability\ } 1/M_+(b),
+  \end{cases}
+\]
+and $\epb_-$ the corresponding quantity after replacing ``+'' with
+``--.''  Consequently, it suffices to prove that
 \begin{gather}
-  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_1(X_i/h)' K_{\bullet,h}(X_i)^2
-  \hat\varepsilon_i^2 = \tfrac{1}{h} \Psit_{\bullet,1,1}(h,h) + o_p(\tfrac{1}{h})
-  \label{eq:3} \\
-  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_2(X_i/b)' K_{\bullet,h}(X_i)
-  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{1}{b^2} \Psit_{\bullet,1,2}(h,b)
-  + o_p(\tfrac{1}{b^2})
-  \label{eq:5} \\
-  \tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) r_2(X_i/b)' K_{\bullet,b}(X_i)^2
-  \hat\varepsilon_i^2 = \tfrac{1}{b} \Psit_{\bullet,2,2}(b,b) + o_p(\tfrac{1}{b}).
   \label{eq:7}
+  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
+    V'(h,b)^{-1/2}\Omega_+(h,b)'\epb_{+}) \to^p 0
+  \intertext{and}
+  \label{eq:8}
+  \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
+    V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}) \to^p 0
 \end{gather}
-But these convergence results follow from CCT's results on
-$\hat\mu_{\bullet,p}^{(\nu)}$, Lemmas SA3 and SA4 in particular,
-and standard arguments on the convergence of residuals to
-the population error term.
-
-Normality also follows standard arguments for the Wild
-bootstrap. Conditional on the regressors and residuals,
-$\{R(X_i) \hat\varepsilon_i e_i^* \}$ is a sequence of independent and
-mean zero random variables for any measurable function $R$, each with
-$p$th absolute moment
-$\lvert R(X_i) \hat\varepsilon_i \rvert^p \E \lvert e_i^*
-\rvert^{p}$.
-The result then holds as a consequence of the Lindeberg-Feller CLT if
-we establish that Liapunov's condition holds in probability, specifically that
-\begin{equation}\label{eq:17}
-  (\tfrac{m}{n})^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
-  \hat\varepsilon_i \rvert^{2+\delta} \to^{p} 0.
-\end{equation}
-with
-\begin{equation*}
-  R_\bullet(X_i) = \gamma_1 r_1(X_i/h) K_{\bullet,h}(X_i) + h^2 \gamma_2 r_2(X_i/b) K_{\bullet,b}(X_i)
-\end{equation*}
-for arbitrary nonzero vectors $\gamma_1'$ and $\gamma_2$.
-\citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}
-But similar arguments to those used for the variance establish~\eqref{eq:17}
-and complete the proof. \qed
+with $\rho$ the ``Mallows metric'' used by
+\citet{bickel1981}.\footnote{%
+  For two random vectors $u$ and $v$ with finite 2nd moments,
+  $\rho(u, v)$ is defined as
+  \begin{equation*}
+    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
+    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
+  \end{equation*}}
+Convergence in $\rho$ is equivalent to convergence in both distribution
+and second moments. \citep[Lemma 8.3.]{bickel1981}
+
+We will only prove~\eqref{eq:7} since the proof of~\eqref{eq:8} is
+identical. By Theorem 2.1 of \cite{freedman1981}, we have
+\begin{align*}
+  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
+  &V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}) \\
+  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
+    \tr(V'(h,b)^{-1/2} \Omega_+(h,b)' \Omega_+(h,b)V'(h,b)^{-1/2}) \\
+  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
+\end{align*}
+the second line holding as a consequence of CCT's Lemma SA1. So it suffices
+to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
+$\varepsilon^\circ_i$ be an i.i.d. sequence randomly drawn from the
+realized values of $\epb_+$ with replacement and let
+$\bar{\varepsilon}^\circ = (1/M_+(b)) \osum[+]{i}{b} \varepsilon^\circ_i$. Then,
+using the same arguments as \cite{freedman1981}, we have the upper bound
+\begin{equation*}
+  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
+  \leq
+  \Big((\bar\varepsilon^{\circ})^2 +
+  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2\Big)^{1/2}
+  + \rho(\varepsilon^\circ_1,\ \varepsilon_{+,1}).
+\end{equation*}
+But $(\bar\varepsilon^{\circ})^2 \to^p 0$ by the LLN,
+\[
+  (1/M_+(b)) \osum[+]{i}{b}
+  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
+\]
+by CCT's Lemma SA1, and
+$\rho(\varepsilon_1^\circ,\ \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
+\cite{bickel1981}.\qed
 

### 2016-08-09 main_paper.tex
Minor text tweaks on Section 4.

--- 2016-08-09 main_paper.tex
@@
 congressional elections. Lee estimates the incumbency advantage in electoral
-races for the House of Representatives --- candidates who received the largest
+races for the House of Representatives --- parties that received the largest
 vote share in the previous election are the incumbents, which creates the
@@
 standard deviation, and Root-MSE of the point
-estimators corresponding to each confidence interval.  As expected, both
+estimators corresponding to each approach.  As expected, both
 bias corrected estimators have

### 2016-08-09 main_paper.tex
Changes some sentences in Section 4 to be in line with new simulation evidence.

@@
 intervals similar to those obtained by the analytical procedures established
-in CCT. The bootstrap CIs obtained compare favorably to the analytical
-alternative, with coverage slightly closer to nominal coverage and shorter
+in CCT. The bootstrap CIs obtained are comparable to the analytical
+alternative, albeit with slightly lower coverage and shorter
 length of the intervals in the specifications implemented. We also find that
@@
 In Panel B, the coverages are very similar to those in Panel A, showing that both procedures are robust to heteroskedasticity.
-The final column, ``CI Length,'' 
-indicates that our proposed bootstrap procedure consistently generates narrower intervals.
+The final column, ``CI Length,'' indicates that our proposed bootstrap procedure consistently generates narrower intervals, in line with the coverage results.
 
@@
 a simple alternative to obtain valid robust confidence intervals in RD designs
-and performs well compared to the analytical bias correction procedures proposed
+and similarly well compared to the analytical bias correction procedures proposed
 by CCT.

### 2016-08-09 Reply_Referee1.tex
Typos and additions to Reply to referees.
Fix minor grammar error in letters
Fix minor grammar error and tone in letters
This commit adds a reply to referee 1, specific comment #2, about the advantages of Bootstrap ove analytical. Needs review.

@@
 
-   \textbf{We need to decide what to answer here.
-In the current version of the paper (which I assume is what they read) we have a paragraph discussing it that needs to be updated with the kernel and wild bootstrap innovations.
-However it is not clear to me what else he wants or what we could write.
-Here is the full original paragraph.
-I will start editing it in the main file, but feel free to add your two cents if you have an idea.
-``The methods presented in this paper are intended as a ``proof of concept'' that
-demonstrates that the analytical correction proposed by CCT can also be
-implemented through a new bootstrap procedure. We believe that this procedure is
-promising because it can allow applied researchers to construct
-accurate confidence intervals in settings where unusual forms of dependence
-would make it difficult to derive CCT's analytical correction---the dependence
-can be accommodates in principle by modifying the resampling algorithm to one
-that matches the dependence in the dataset. The specific version of the bootstrap
-presented in this paper, however, does not achieve that level of generality yet,
-and two limitations should be noted in particular. First, the confidence
-intervals produced by this bootstrap depend on two separate bandwidth parameters
-that must be generated elsewhere. Since these bandwidths are generated using
-analytical methods, the confidence intervals could easily be produced using the
-same methods. Second, the bootstrap proposed in this paper imposes local
-homoskedasticity and can perform poorly when the DGP exhibits significant
-heteroskedasticity. Moreover, in this paper we focus on the baseline case of
-sharp RD with a local linear model and uniform kernel. So the practical benefits
-of using the bootstrap in this context are relatively limited. Relaxing these
-limitations is the subject of ongoing research by the authors.''}
+As now discussed in the text, we believe that this procedure is promising because of its ``automatic'' nature. It is potentially easier to implement to cases
+of interest to applied researchers for which the analytical correction has not been developed, for example, ``to construct accurate confidence intervals in settings where unusual forms of dependence would make it difficult to derive CCT's analytical correction.'' Surely, we do not achieve this level of generality in this paper but we hope it will serve as a stepping stone for these developments.
 
@@
 
-Thank you for pointing out this was confusing. We changed it on the latest draft.
+Thank you for this suggestion. We changed it on the latest draft.
 
@@
 
-Thank you very much for pointing those out. They have been corrected.
+Thanks. They have been fixed.
 

### 2016-08-09 R/rdfunctions_ForMc.R
Add options for HC 0,1,2,3 in rdboot_ForMc
e.ql.adj is the rescale vector for residuls on the LHS, it is calculated
from hl, which is the diagonal vector of projection matrix. Similar for
the RHS.

@@ -16,31 +16,31 @@
 boot_estimator_ForMc <- function(ypl, ypr, yql, yqr, 
                                  coef.ql, coef.qr, coef.pl, coef.pr,
                                  Xql, Xqr, Xpl, Xpr,
-                                 WXql, WXqr,
+                                 WXql, WXqr, e.ql.adj, e.qr.adj,
                                  wqr, wql, ihr, ihl, Nbc, bootstrap = "wild") {
   
   b.ql       <- crossprod(WXql, yql)
   fitted.l   <- Xql %*% b.ql
-  residual.l <- yql - fitted.l
+  residual.l <- (yql - fitted.l) * e.ql.adj
   
   b.qr       <- crossprod(WXqr, yqr)
   fitted.r   <- Xqr %*% b.qr
-  residual.r <- yqr - fitted.r
+  residual.r <- (yqr - fitted.r) * e.qr.adj
   
   boot_parameter <- coef.qr %*% yqr - coef.ql %*% yql
   estimate       <- coef.pr %*% ypr - coef.pl %*% ypl
-
+  
   if (bootstrap == "residual") {
     boots <- replicate(Nbc,
-             coef.pr %*% (fitted.r[ihr] + sample(residual.r, length(ypr), T, wqr)) -
-             coef.pl %*% (fitted.l[ihl] + sample(residual.l, length(ypl), T, wql)))
+                       coef.pr %*% (fitted.r[ihr] + sample(residual.r, length(ypr), T, wqr)) -
+                         coef.pl %*% (fitted.l[ihl] + sample(residual.l, length(ypl), T, wql)))
   }
   if (bootstrap == "wild") {
     boots <- replicate(Nbc,
-             coef.pr %*% (fitted.r[ihr] + residual.r[ihr]*sample(wild_values, length(ypr), T, wild_weights)) -
-             coef.pl %*% (fitted.l[ihl] + residual.l[ihl]*sample(wild_values, length(ypl), T, wild_weights)))
+                       coef.pr %*% (fitted.r[ihr] + residual.r[ihr]*sample(wild_values, length(ypr), T, wild_weights)) -
+                         coef.pl %*% (fitted.l[ihl] + residual.l[ihl]*sample(wild_values, length(ypl), T, wild_weights)))
   }
-
+  
   
   return(as.numeric(estimate - mean(boots) + boot_parameter))
 }
[…]

### 2016-08-09 R/rdfunctions_ForMc_test.R
test the new rdboot_ ForMc with HC 0,1,2,3
compare the new rdboot_ForMc using HC0 with old rdboot function, they
give the same results.

@@ -37,9 +37,12 @@ test_that("rdfunctions_ForMc.R gives the same results as rdfunctions_old.R in re
   old_epa <- old_estimator_wrapper(dta$y, dta$x, Nbc = 50, Nci = 50, kernel = "epanechnikov")
   
   set.seed(798)
-  new_uni <- rdboot_ForMc(dta$y, dta$x, Nbc = 50, Nci = 50, bootstrap = "residual", kernel = "uniform")[2, ]
-  new_tri <- rdboot_ForMc(dta$y, dta$x, Nbc = 50, Nci = 50, bootstrap = "residual", kernel = "triangular")[2, ]
-  new_epa <- rdboot_ForMc(dta$y, dta$x, Nbc = 50, Nci = 50, bootstrap = "residual", kernel = "epanechnikov")[2, ]
+  new_uni <- rdboot_ForMc(dta$y, dta$x, Nbc = 50, Nci = 50, bootstrap = "residual", 
+                          kernel = "uniform", residual = "HC0")[2, ]
+  new_tri <- rdboot_ForMc(dta$y, dta$x, Nbc = 50, Nci = 50, bootstrap = "residual", 
+                          kernel = "triangular", residual = "HC0")[2, ]
+  new_epa <- rdboot_ForMc(dta$y, dta$x, Nbc = 50, Nci = 50, bootstrap = "residual", 
+                          kernel = "epanechnikov", residual = "HC0")[2, ]
   
   expect_equivalent(old_uni, new_uni)
   expect_equivalent(old_tri, new_tri)
@@ -146,13 +149,13 @@ test_that("rdfunctions_ForMc.R gives the same results as rdfunctions.R in wild b
   new_estimate <- boot_estimator_ForMc(ypl, ypr, yql, yqr,
                                        coef.ql, coef.qr, coef.pl, coef.pr,
                                        Xql, Xqr, Xpl, Xpr,
-                                       WXql, WXqr,
+                                       WXql, WXqr, 1, 1, 
                                        wqr, wql, ihr, ihl, 50, bootstrap = "wild")
   
   new_dist <- boot_dist_ForMc(ypl, ypr, yql, yqr,
                               coef.ql, coef.qr, coef.pl, coef.pr,
                               Xql, Xqr, Xpl, Xpr,
-                              WXql, WXqr,
+                              WXql, WXqr, 1, 1,
                               wqr, wql, ihr, ihl, 10, 10, bootstrap = "wild")
   
   set.seed(798)

### 2016-08-10 R/simulation.R
restore the estimator based on naive bootstrap

@@ -8,6 +8,7 @@ library(doRNG)
 library(xtable)
 try(source("slackrISE.R"), T)
 
+source("rdfunctions_old.R")
 source("rdfunctions.R")
 source("rdfunctions_ForMc.R")
 
@@ -16,6 +17,24 @@ a <- 0.05
 N.simu <- 5000
 N.core <- 35
 N.bc <- 500
+
+## naive bootstrap estimator
+naiveboot <- function(y, x, kernel, Nci = 999) {
+  
+  ## point estimate
+  h <- rdbwselect_2014(y, x, kernel=kernel, bwselect = "IK")$bws[1]
+  tau <- rd.estimate(data.frame(y, x), 1, 2, h, h, 500, kernel, F)
+
+  ## bootstrap
+  Btau <- replicate(Nci, {
+    i <- sample.int(length(y), length(y), replace = T)
+    h <- rdbwselect_2014(y[i], x[i], kernel=kernel, bwselect = "IK")$bws[1]
+    rd.estimate(data.frame(y[i], x[i]), 1, 2, h, h, 500, kernel, F)
+  })
+  
+  return(c(tau, quantile(Btau, c(0.025, 0.975))))
+}
+
 
 ## simulation 1: coverage of CI from bootstrap (basic CI)
 

### 2016-08-10 R/simulation.R
Add a wrapper to run naive bootstrap simulation

@@ -109,6 +109,40 @@ simulation.2 <- function(model.id, kernel, heteroskedasticity = F) {
   return(c(true = t.true, bias = bias, SD = SD, MSE = MSE, coverage = coverage, length = length))
 }
 
+## simulation 3: coverage of CI from naive bootstrap
+
+simulation.3 <- function(model.id, kernel, heteroskedasticity = F) {
+  
+  if (heteroskedasticity == T) {
+    avebw <- average_bw(model.id, kernel)
+    gen_data <- function() generate.data.h(model.id, avebw)
+  } else {
+    gen_data <- function() generate.data(model.id)
+  }
+  
+  simu <- function() {
+    dta <- gen_data()
+    naiveboot(dta$y, dta$x, kernel, N.ci)
+  }
+  
+  cl <- makeCluster(N.core)
+  registerDoParallel(cl)
+  export.obj <- c("N.ci", "a", "generate.data", "kweight", "generate.data.h",
+                  "local_polynomial_regression", "naiveboot", "rd.estimate")
+  collect.simu <- foreach(i=1:N.simu, .combine="rbind", .packages="rdrobust", .export=export.obj, .inorder=F) %dorng%
+    simu()
+  stopCluster(cl)
+  
+  t.true    <- ifelse(model.id ==2, -3.45, 0.04)
+  bias      <- t.true - mean(collect.simu[ , 1])
+  SD        <- sd(collect.simu[ , 1])
+  MSE       <- sqrt(mean((collect.simu[ , 1] - t.true)^2))
+  coverage  <- mean(collect.simu[ , 2] <= t.true & collect.simu[ , 3] >= t.true)
+  length    <- mean(collect.simu[ , 3] - collect.simu[ , 2])
+  
+  return(c(true = t.true, bias = bias, SD = SD, MSE = MSE, coverage = coverage, length = length))
+}
+
 ## generate tables
 
 models <- c(1, 2, 3)

### 2016-08-10 R/simulation.R
Organize simulation output from the three procedures

@@ -145,32 +145,40 @@ simulation.3 <- function(model.id, kernel, heteroskedasticity = F) {
 
 ## generate tables
 
+kernel <- "uni"
 models <- c(1, 2, 3)
-kernels <- c("uniform")
 heteroskedasticity <- c(F, T)
-rnames <- c("m1.uni", "m1.uni.h", "m2.uni", "m2.uni.h","m3.uni", "m3.uni.h")
 
-i <- 1
+rnames <- paste(c("m1", "h.m1", "m2", "h.m2","m3", "h.m3"), kernel, sep = ".")
 boot.results <- matrix(0, nrow = 6, ncol = 6)
 rownames(boot.results) <- rnames
 cct.results <- matrix(0, nrow = 6, ncol = 6)
 rownames(cct.results) <- rnames
+naiveboot.results <- matrix(0, nrow = 6, ncol = 6)
+rownames(naiveboot.results) <- rnames
+
+i <- 1
 for (m in models) {
-  for (k in kernels) {
-    for (h in heteroskedasticity) {
-      set.seed(798)
-      boot.results[i, ] <- simulation.1(m, k, h)
-      try(slackr(print(boot.results)), T)
-      
-      set.seed(798)
-      cct.results[i, ] <- simulation.2(m, k, h)
-      try(slackr(print(cct.results)), T)
-      i <- i + 1
-    }
+  for (h in heteroskedasticity) {
+    set.seed(798)
+    boot.results[i, ] <- simulation.1(m, kernel, h)
+    try(slackr(print(boot.results)), T)
+    
+    set.seed(798)
+    cct.results[i, ] <- simulation.2(m, kernel, h)
+    try(slackr(print(cct.results)), T)
+    
+    set.seed(798)
+    naiveboot.results[i, ] <- simulation.3(m, kernel, h)
+    try(slackr(print(naiveboot.results)), T)
+    
+    i <- i + 1
   }
 }
 
 print(xtable(boot.results, digits = 3), include.rownames = F, type = "latex", 
-      file = "output/boot_results.tex")
+      file = paste("output/boot_results_", kernel, ".tex", sep = ""))
 print(xtable(cct.results, digits = 3), include.rownames = F, type = "latex", 
-      file = "output/cct_results.tex")
+      file = paste("output/cct_results_", kernel, ".tex", sep = ""))
+print(xtable(naiveboot.results, digits = 3), include.rownames = F, type = "latex", 
+      file = paste("output/naiveboot_results_", kernel, ".tex", sep = ""))

### 2016-08-10 Reply_Referee2.tex
Typos and additions to Reply to referees.
Fix minor grammar error in letters
Fix minor grammar error and tone in letters
Update to Reply to Referee 2. Update language.
Fix apostrophe symbol in referee letters
The appostrophe used in "referee's" was not compiling correctly on my laptop. This
commit changes it to the correct LaTeX symbol.

@@
 
-First, we thank the reviewer for providing detailed and helpful comments, which we feel have significantly improved the quality of the draft.
-Below we provide replies to the reviewer’s specific comments detailing how we address each comment.
+First, we thank the reviewer for providing detailed and helpful comments, which
+we feel have significantly improved the quality of the draft.  Below we provide
+replies to the reviewer's specific comments detailing how we address each
+comment.
 
@@
 
- Thank you very much for pointing some typos. They have been corrected.
+ Thanks. This has been fixed.
 
@@
 
- Thank you pointing this typo. It has been corrected.
+ Thanks. It has been corrected.
 
@@
 
-%Thank you very much for pointing this. The notation has been corrected.
+Thanks. It is now fixed.
 
@@
 This is quite different from the other procedures, and can be misleading. I recommend not including the Naive Bootstrap.''}
+
+Thank you for the recommendation. We dropped the Naive Bootstrap from the Simulation Evidence.
 

### 2016-08-10 Reply_Referee1.tex
Fix apostrophe symbol in referee letters
The appostrophe used in "referee's" was not compiling correctly on my laptop. This
commit changes it to the correct LaTeX symbol.
Tweak referee response on usefulness of the bootstrap

@@
 
-As now discussed in the text, we believe that this procedure is promising because of its ``automatic'' nature. It is potentially easier to implement to cases
-of interest to applied researchers for which the analytical correction has not been developed, for example, ``to construct accurate confidence intervals in settings where unusual forms of dependence would make it difficult to derive CCT's analytical correction.'' Surely, we do not achieve this level of generality in this paper but we hope it will serve as a stepping stone for these developments.
+  As now discussed in the text, we believe that this procedure is promising
+  because of its ``automatic'' nature. It is easier to implement in cases of
+  interest to applied researchers for which the analytical correction has not
+  been developed; for example, analytical expressions for the standard errors
+  with clustered observations have been only recently available, but would be
+  relatively straightforward to calculate with a bootstrap.  We do not claim to
+  achieve this level of generality in this paper but we hope it will serve as a
+  stepping stone for these developments.
 

### 2016-08-10 main_paper.tex
Notation change on V and bias-corrected terms
1. as requested by referee 2, point 3, define "V" as the true variance
of point estimator. It seems that we don't need to change its fumular in
the appendix.

2. as requested by referee 2, point 9, explicitly use superscript "bc"
instead of prime to indicate terms after bias correction.

@@
   \notag
-  V(h) \big/ \V(\hat\tau(h) \mid X_{1},\dots,X_{n}) \to^p 1
+  V(h) = \V(\hat\tau(h) \mid X_{1},\dots,X_{n}),
 \end{gather}
@@
   \label{eq:4}
-  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
+  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V^{bc}(h, b)^{1/2}}
   \to^{d} N(0,1),
@@
     bootstrap estimates
-    $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
+    $\hat\tau_1^{bc*}(h,b), \dots, \hat\tau_{B_{2}}^{bc*}(h,b)$. For the
     $k$th replication:
@@
     \item Save the bias-corrected estimator
-      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_-^*(h)
+      $\hat\tau_k^{bc*}(h,b) = \hat\mu_+^*(h) - \hat\mu_-^*(h)
       - \Delta^{**}(h,b)$.
@@
   \item Define $\tau^* = \hat g_+(0) - \hat g_-(0)$ and use the empirical CDF of
-    $\hat\tau_1^{\prime*}(h,b) - \tau^*,\dots, \hat\tau_{B_2}^{\prime*}(h,b) - \tau^*$
-    as the sampling distribution of $\hat \tau' - \tau$.
+    $\hat\tau_1^{bc*}(h,b) - \tau^*,\dots, \hat\tau_{B_2}^{bc*}(h,b) - \tau^*$
+    as the sampling distribution of $\hat \tau^{bc} - \tau$.
   \end{enumerate}
@@
   \begin{equation*}
-    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
+    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V^{bc}(h,b) \to^p 1
   \end{equation*}

### 2016-08-10 R/simulation.R
use hc3 in the CCT analytical approach
This makes it comparable to our bootstrap approach.

@@ -86,7 +86,7 @@ simulation.2 <- function(model.id, kernel, heteroskedasticity = F) {
     dta <- gen_data()
     bws <- rdbwselect_2014(dta$y, dta$x, kernel = kernel)$bws
     results <- rdrobust(dta$y, dta$x, kernel = kernel,
-                        h = bws[1], b = bws[2], level = 100 * (1-a))
+                        h = bws[1], b = bws[2], level = 100 * (1-a), vce = "hc3")
     t <- results$coef[3]
     ci <- results$ci[3, ]
     return(c(t, ci))

### 2016-08-10 R/simulation.R
Add the simulation for traditional estimator

@@ -143,6 +143,44 @@ simulation.3 <- function(model.id, kernel, heteroskedasticity = F) {
   return(c(true = t.true, bias = bias, SD = SD, MSE = MSE, coverage = coverage, length = length))
 }
 
+## simulation 4: coverage of traditional approach
+
+simulation.4 <- function(model.id, kernel, heteroskedasticity = F) {
+  
+  if (heteroskedasticity == T) {
+    avebw <- average_bw(model.id, kernel)
+    gen_data <- function() generate.data.h(model.id, avebw)
+  } else {
+    gen_data <- function() generate.data(model.id)
+  }
+  
+  simu <- function() {
+    dta <- gen_data()
+    bws <- rdbwselect_2014(dta$y, dta$x, kernel=kernel, bwselect = "IK")$bws[1]
+    results <- rdrobust(dta$y, dta$x, kernel = kernel,
+                        h = bws, b = bws, level = 100 * (1-a), vce = "hc3")
+    t <- results$coef[1]
+    ci <- results$ci[1, ]
+    return(c(t, ci))
+  }
+  
+  cl <- makeCluster(N.core)
+  registerDoParallel(cl)
+  export.obj <- c("generate.data", "generate.data.h", "a")
+  collect.simu <- foreach(i=1:N.simu, .combine="rbind", .packages="rdrobust", .export=export.obj, .inorder=F) %dorng%
+    simu()
+  stopCluster(cl)
+  
+  t.true    <- ifelse(model.id ==2, -3.45, 0.04)
+  bias      <- t.true - mean(collect.simu[ , 1])
+  SD        <- sd(collect.simu[ , 1])
+  MSE       <- sqrt(mean((collect.simu[ , 1] - t.true)^2))
+  coverage  <- mean(collect.simu[ , 2] <= t.true & collect.simu[ , 3] >= t.true)
+  length    <- mean(collect.simu[ , 3] - collect.simu[ , 2])
+  
+  return(c(true = t.true, bias = bias, SD = SD, MSE = MSE, coverage = coverage, length = length))
+}
+
 ## generate tables
 
 kernel <- "uni"

### 2016-08-10 main_paper.tex
Fix a typo in the proof of theorem 2
Small typo on section 5

@@
 
-In 1965, the Head Start program was established to help poor children age three
+In 1965, the Head Start program was established to help poor children aged three
 to five and their families. The program elements include parent involvement,
@@
 \end{equation*}
-for arbitrary nonzero vectors $\gamma_1'$ and $\gamma_2$.
+for arbitrary nonzero vectors $\gamma_1$ and $\gamma_2$.
 \citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}

### 2016-08-10 Reply_Referee1.tex
Changes to the response to referees.

@@
 Thank you very much for pointing out instances in the proofs that might require checking and clarifications.
-We are sorry this was confusing to read.
-In the new proofs we have added details to the statement ``the bootstrap ensures that'', previously on page 19.
-Since the proof for theorem 2 changed substantially with the adoption of the Wild Bootstrap scheme (which addresses the heteroskedasticity issue, as discussed before) we made substantial changes that hopefully will make the proof's steps clearer to the reader, addressing the remaining comments the reviewer pointed our attention to, including the definition of V(h,b).
-\textbf{After all is said and done remember to go over and check if all notation has been properly defined}.
+ We are sorry this was confusing to read. In the new proofs we have added details to the statement ``the bootstrap ensures that'', previously on page 19.
+ Since the proof for theorem 2 changed substantially with the adoption of the Wild Bootstrap scheme
+ (which addresses the heteroskedasticity issue, as discussed before) we made substantial changes that hopefully
+ will make the proof's steps clearer to the reader, addressing the remaining comments.
 

### 2016-08-10 Reply_Referee2.tex
Changes to the response to referees.

@@
 
- %Thanks for suggesting a notation choice that could make the exposition easier for readers familiar with the literature.
-We changed it on the latest draft.
-\textbf{Yang, please change and check if this was updated throughout the paper.}
+ Thank you for the recommendation. Adjustments were made in the draft.
 
@@
 \item \textit{``Instead of $\hat{\tau}'(h,b)$ and $V'(h,b)$, I recommend using $\hat{\tau}^{bc}(h,b)$ and $V^{bc}(h,b)$ to make the notation more explicit.''}
-%Thanks for suggesting a notation choice that could make the exposition easier for readers familiar with the literature.  We changed it on the latest draft.
+Thanks for suggesting a notation choice that could make the exposition easier for readers familiar with the literature.  We changed it on the latest draft.
 

### 2016-08-10 R/simulation.R
Add a few lines to export simulation results for traditional estimator

@@ -194,6 +194,8 @@ cct.results <- matrix(0, nrow = 6, ncol = 6)
 rownames(cct.results) <- rnames
 naiveboot.results <- matrix(0, nrow = 6, ncol = 6)
 rownames(naiveboot.results) <- rnames
+traditional.results <- matrix(0, nrow = 6, ncol = 6)
+rownames(traditional.results) <- rnames
 
 i <- 1
 for (m in models) {
@@ -210,6 +212,10 @@ for (m in models) {
     naiveboot.results[i, ] <- simulation.3(m, kernel, h)
     try(slackr(print(naiveboot.results)), T)
     
+    set.seed(798)
+    traditional.results[i, ] <- simulation.4(m, kernel, h)
+    try(slackr(print(traditional.results)), T)
+    
     i <- i + 1
   }
 }
@@ -220,3 +226,5 @@ print(xtable(cct.results, digits = 3), include.rownames = F, type = "latex",
       file = paste("output/cct_results_", kernel, ".tex", sep = ""))
 print(xtable(naiveboot.results, digits = 3), include.rownames = F, type = "latex", 
       file = paste("output/naiveboot_results_", kernel, ".tex", sep = ""))
+print(xtable(traditional.results, digits = 3), include.rownames = F, type = "latex", 
+      file = paste("output/traditional_results_", kernel, ".tex", sep = ""))

### 2016-08-10 main_paper.tex
Minor language changes to section 5.

@@
 as well.  In contrast to the striking differences between the conventional
-estimates bias-corrected procedures for the mortality estimates, the differences
+and bias-corrected procedures for the mortality estimates, the differences
 in Table~\ref{tbl:3} are much smaller.

### 2016-08-10 Reply_Referee1.tex
Add 'introduce more notation' to referee letters
We apologize for NOTHING
Tighten responses to first referee

@@
 
+Finally, the mathematical appendix defines more notation explicitly and
+summarizes several convergence results from Calonico, Cattaneo, and Titiunik
+(2014) that are referenced in the proofs.
+
 \section{Specific Comments}
@@
 
- We thank the reviewer for focusing our attention to this point and suggesting the use of the Wild bootstrap.
-Following his recommendation we altered the algorithm to use a wild bootstrap approach and discuss its properties, hence allowing for conditional heteroskedasticity.
+Thanks for raising this concern. See the discussion above.
 
@@
 
-\item \textit{``As mentioned earlier, I suspect Theorem 2 is incorrect unless conditional homoskedasticity is assumed... .''}
+\item \textit{``As mentioned earlier, I suspect Theorem 2 is incorrect unless conditional homoskedasticity is assumed....''}
 
-  Please see discussion for item 1 on the main comments section and item 3 in the specific comments above.
+  Thanks again. See the discussion above.
 
@@
 
-  Thank you for suggesting additional DGPs. We have performed new simulations using new DGPs with both mild and severe heteroskedasticity, please see the simulations section in the new draft.
+  Thank you for this suggestion; we have added some additional simulations with conditional heteroskedasticity.
 
@@
 Thank you very much for pointing out instances in the proofs that might require checking and clarifications.
- We are sorry this was confusing to read. In the new proofs we have added details to the statement ``the bootstrap ensures that'', previously on page 19.
+ In the new proofs we have added details to the statement ``the bootstrap ensures that'', previously on page 19.
  Since the proof for theorem 2 changed substantially with the adoption of the Wild Bootstrap scheme

### 2016-08-10 Reply_Referee2.tex
Add 'introduce more notation' to referee letters
We apologize for NOTHING
Tweak letter to referee 2 re: h < b

@@
 
-  Thank you very much for bringing up to our attention the relationship between $h$ and $b$ in our setup.
+  Thanks for bringing this up.
 In the general kernel setup developed for this draft it became clear that the condition $h<b$ is not necessary and it has been dropped.
 Regarding the conditions $nh^{5}b^{2} \rightarrow 0$ and $nb^{5}h^{2} \rightarrow 0$, we originally decided to present the conditions in this form to make it more accessible to the readers.
-Note that CCT Theorem 1 assumes $n \min\{h^{5},b^{5}\}\max\{h^{2}, b^{2}\} \rightarrow 0$.
+Note that CCT Theorem 1 assumes $n \min\{h^{5},b^{5}\}\max\{h^{2}, b^{2}\} \rightarrow 0$ which is equivalent to our condition now that $b < h$ is allowed.
 
@@
 Thank you very much for pointing out instances in the proofs that might require checking and clarifications.
-We are sorry this was confusing to read.
 In the new proofs we have added some additional details.

### 2016-08-10 Reply_Referee2.tex

@@
 
-Thanks for suggesting a notation choice that could make the exposition easier for readers. We changed it on the latest draft.
+No problem.
 
@@
 \item \textit{``Instead of $\hat{\tau}'(h,b)$ and $V'(h,b)$, I recommend using $\hat{\tau}^{bc}(h,b)$ and $V^{bc}(h,b)$ to make the notation more explicit.''}
-Thanks for suggesting a notation choice that could make the exposition easier for readers familiar with the literature.  We changed it on the latest draft.
+
+Thanks for the suggestion. We have changed this in the paper.
 
@@
 
- We thank the reviewer for focusing our attention to this point and suggesting the use of the Wild bootstrap.
-Following his recommendation we altered the algorithm to use a wild bootstrap approach and discuss its properties, hence allowing for conditional heteroskedasticity.
+Thanks, we've made this change as discussed above.
 
@@
 
- Thank you for suggesting additional DGPs. We have performed new simulations using new DGPs with both mild and severe heteroskedasticity, please see the simulations section in the new draft.
+  Thank you for this suggestion; we have added some additional simulations with conditional heteroskedasticity.
 

### 2016-08-10 R/rdfunctions_ForMc_test.R
Test that diagonal elements are correctly calculated
In the function "rdboot_ForMc", we use orthogonal polynomials and QR
decomposition to get projection matrix and its diagonal elements. In
this test, we use the common formula with raw polynomials, which is more
straight foreward,  and make sure they give the same results.

@@ -169,5 +169,83 @@ test_that("rdfunctions_ForMc.R gives the same results as rdfunctions.R in wild b
   expect_equivalent(new_dist, old_dist)})
 
 
-
+test_that("rdfunctions_ForMc.R correctly calculates diagonal elements of projection matrix.",{
+  
+  # generate data
+  dta <- generate.data(1)
+  y <- dta$y
+  x <- dta$x
+  p <- 1
+  q <- 2
+  kernel <- "tri"
+  
+  # redo the steps in the function "rdboot_ForMc"
+  bw <- rdbwselect_2014(y, x, p=p, q=q, kernel=kernel)$bws
+  h <- bw[1]
+  b <- bw[2]
+  
+  yql <- y[x > -max(bw) & x < 0]
+  xql <- x[x > -max(bw) & x < 0]
+  yqr <- y[x >= 0 & x < max(bw)]
+  xqr <- x[x >= 0 & x < max(bw)]
+  
+  ihl <- xql > -h
+  ihr <- xqr < h
+  
+  ypl <- y[x > -h & x < 0]
+  xpl <- x[x > -h & x < 0]
+  ypr <- y[x >= 0 & x < h]
+  xpr <- x[x >= 0 & x < h]
+  
+  # a vector of weight for residual bootstrap
+  wql <- kweight(xql, 0, b, kernel)
+  wqr <- kweight(xqr, 0, b, kernel)
+  
+  # orthogonal polynomials
+  xql.poly <- poly(xql, q)
+  xqr.poly <- poly(xqr, q)
+  xpl.poly <- poly(xpl, p)
+  xpr.poly <- poly(xpr, p)
+  
+  # design matrix
+  Xql <- cbind(1, poly(xql, q))
+  Xqr <- cbind(1, poly(xqr, q))
+  Xpl <- cbind(1, poly(xpl, p))
+  Xpr <- cbind(1, poly(xpr, p))
+  
+  KXql <- kweight(xql, 0, b, kernel) * Xql
+  KXqr <- kweight(xqr, 0, b, kernel) * Xqr
+  KXpl <- kweight(xpl, 0, h, kernel) * Xpl
+  KXpr <- kweight(xpr, 0, h, kernel) * Xpr
+  
+  # parameter maker
+  WXql <- t(solve(crossprod(Xql, KXql), t(KXql)))
[…]

### 2016-08-10 main_paper.tex
Change to conclusion giving up on humbleness given the extensions.
Still learning how to use this Damn Thing.
Adds paragraph describing assumption 1.

@@
 \end{assumption}
+
+ The first part of Assumption \ref{A1} requires that the running variable be continuously distributed around the cutoff, and guarantees the presence of observations close to the threshold in large samples.
+ Next, this assumption imposes the existence of moments necessary for estimation and inference.
+ Part 3 imposes the traditional smoothness conditions on the expected potential outcomes and its derivatives around the cutoff which is crucial for identification of the parameters of interest and bias correction terms.
+ Finally, the last part of Assumption \ref{A1} describes the standard restrictions on the conditional variance of the observed $Y_{i}$ around the cutoff, allowing for different values on each side of the threshold.
 
@@
 that there are bootstrap procedures that can generate asymptotically valid
-confidence intervals in the same settings as CCT's. The current implementation
-of this bootstrap is somewhat specialized, however, and relaxing its limitations
-is the subject of ongoing research.
+confidence intervals in the same settings as CCT's.
 

### 2016-08-10 R/application.R
switch to HC3 in application
1. the analytical approach used nearest neighbours to calculate robust
standard error, now use HC3.
2. the wild bootstrap used HC0, now use HC3.
3. the three .tex files containing application results are also updated

@@ -33,7 +33,7 @@ original <- function(dta, bw) {
 
 robust <- function(dta) {
   bws <- rdbwselect_2014(dta$y, dta$x, kernel = "uni")$bws
-  cct <- rdrobust(dta$y, dta$x, kernel = "uni", h = bws[1], b = bws[2])
+  cct <- rdrobust(dta$y, dta$x, kernel = "uni", h = bws[1], b = bws[2], vce = "hc3")
   t1  <- cct$coef[3]
   ci1 <- cct$ci[3, ]
 

### 2016-08-10 main_paper.tex
update the tables in application section
Only the CIs changed a little bit, the text in this section does not
explicitly quote any CIs.

--- 2016-08-10 main_paper.tex
@@
   \notag
-  V(h) = \V(\hat\tau(h) \mid X_{1},\dots,X_{n}),
+  V(h) \big/ \V(\hat\tau(h) \mid X_{1},\dots,X_{n}) \to^p 1
 \end{gather}
@@
 \begin{gather*}
-  \hat{\tau}^{bc}(h, b) = \hat{\tau}(h) - h^{2}
+  \hat{\tau}'(h, b) = \hat{\tau}(h) - h^{2}
   \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
@@
 \begin{equation*}
-  \frac{\hat{\tau}^{bc}(h, b) - \tau}{V^{bc}(h, b)^{1/2}} \to^d N(0,1)
-\end{equation*}
-with $V^{bc}(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
+  \frac{\hat{\tau}'(h, b) - \tau}{V'(h, b)^{1/2}} \to^d N(0,1)
+\end{equation*}
+with $V'(h, b) = V(h) + C(h, b)$ and $C(h, b)$ an additional variance component
 generated by the bias-correction term.\footnote{%
@@
   \label{eq:4}
-  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V^{bc}(h, b)^{1/2}}
+  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
   \to^{d} N(0,1),
 \end{equation}
-where $\Delta^*(h,b)$ is defined by Equation~\eqref{eq:9}.
+where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
 \end{theorem}
@@
     bootstrap estimates
-    $\hat\tau_1^{bc*}(h,b), \dots, \hat\tau_{B_{2}}^{bc*}(h,b)$. For the
-    $k$th replication:
+    $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
+    $k$th value:
     \begin{enumerate}
@@
     \item Save the bias-corrected estimator
-      $\hat\tau_k^{bc*}(h,b) = \hat\mu_+^*(h) - \hat\mu_-^*(h)
+      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
       - \Delta^{**}(h,b)$.
     \end{enumerate}
-  \item Define $\tau^* = \hat g_+(0) - \hat g_-(0)$ and use the empirical CDF of
-    $\hat\tau_1^{bc*}(h,b) - \tau^*,\dots, \hat\tau_{B_2}^{bc*}(h,b) - \tau^*$
-    as the sampling distribution of $\hat \tau^{bc} - \tau$.
+  \item Use the empirical CDF of
+    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
+    construct confidence intervals, etc.
   \end{enumerate}
 \end{algorithm}
-
-One brief remark on implementing these algorithms. Many of the matrix operations
-required to estimate the local polynomials only involve the regressors and,
-therefore, only need to be computed once. For example, the parameter estimates
-for the linear model on the treated group are equal to
-\[
-\hat\beta_{+,1} = \underbrace{(\mathbf{X}' \mathbf{K}_+ \mathbf{X})^{-1} \mathbf{X}' \mathbf{K}_+}_{\mathbf{W}_{+,1}} \mathbf{Y}
-\]
-where
-\begin{align*}
-\mathbf{X} &= \begin{pmatrix*} 1 & X_1 \\ 1 & X_2 \\ \vdots & \vdots \\ 1 & X_n \end{pmatrix*} &
-\mathbf{Y} &= \begin{pmatrix*} Y_1 \\ Y_2 \\ \vdots \\ Y_n \end{pmatrix*} &
-\mathbf{K}_+ &= \begin{pmatrix*}
-  K_{+,h}(X_1) & 0 & \cdots & 0 \\
-  0 & K_{+,h}(X_2) & \cdots & 0 \\
-  0 & 0 & \ddots & 0 \\
-  0 & 0 & \cdots & K_{+,h}(X_n) \end{pmatrix*}.
-\end{align*}
-The matrix $\mathbf{W}_{+,1}$ is not affected by the bootstrap so it can be
-computed once initially and reused in the bootstrap calculations and each
-bootstrap replication just requires a single matrix-vector multiplication. The
-other parameter estimates have this property as well. Consequently, the
-computational burden of this iterated bootstrap is much lower than might
-appear.\footnote{%
-  An open-source implementation of this algorithm written in R, which was used
-  for the empirical and Monte Carlo components of this paper, is available
-  online at \url{https://github.com/grayclhn/boot-rd}.} %
 
@@
   Under Assumptions~\ref{A1} and~\ref{A2},
-  \begin{equation*}
-    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V^{bc}(h,b) \to^p 1
-  \end{equation*}
-  and
-  \begin{multline*}
-    \sup_{x,\tau}
-    \Big\rvert \Pr^*\big[ \sqrt{nh}
-    (\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^*) \leq x \big] \\
-    - \Pr\big[ \sqrt{nh}
-    (\hat\tau(h) - \Delta^*(h,b) - \tau) \leq x \big] \Big\lvert \to^p 0.
-  \end{multline*}
+  \begin{gather*}
+    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
+  \intertext{and}
+    \sup_{x}
+    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
+    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
+  \end{gather*}
 \end{theorem}
@@
 intervals similar to those obtained by the analytical procedures established
-in CCT. The bootstrap CIs obtained are comparable to the analytical
-alternative, albeit with slightly lower coverage and shorter
+in CCT. The bootstrap CIs obtained compare favorably to the analytical
+alternative, with coverage slightly closer to nominal coverage and shorter
 length of the intervals in the specifications implemented. We also find that
 all of the bias corrected methods can offer substantial improvements over
-estimators that do not bias correct.
+estimators that do not bias correct, including a ``naive'' bootstrap procedure.
 
@@
 comparable with theirs and with the rest of the literature.
-While they use this experimental design with homoskedastic errors, we introduce heteroskedasticity following the design in \cite{mackinnon2013thirty}.
-We control the degree of heteroskedasticity through the parameter $\gamma$ and a function $z(\gamma)$.
+They use this experimental design with a constant $\sigma_i = 0.1295$.
+We follow \cite{mackinnon2013thirty} to use a parameter $\gamma$ and a function $z(\gamma)$ to control the degree of heteroskedasticity.
 When $\gamma = 0$, we set $z(\gamma) = 0.1295$ such that our DGP is exactly the same as \citet{IK} and CCT.
-When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.\footnote{In practice, the optimal $h$ and $b$ are usually data driven, so $h$, $b$ and $\sigma_i$ are simultaneously determined.
-For simplicity, we use the following steps to find $z(\gamma)$: (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector, (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$ and (3) define $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$.} We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.
+When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.
+\footnote{The rescaling requires that $\max(h, b)$ is known, which is usually not the case in practice because $h$ and $b$ are data-driven.
+For simplicity, we firstly find $\overline{\max[h, b]}$ from \textbf{homoskedastic} data through 500 replications and then calculate $z(\gamma)$ for every bootstrap data accordingly.
+In our simulation, $\overline{\max[h, b]}$ is obtained by (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector and (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$.
+Once $\overline{\max[h, b]}$ is known, we use it to generate heteroskedastic data using following steps: (1) generate random running variable $X_i$, (2) let $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$ and calculate the standard deviation and (3) generate disturbance term and outcome $Y_i$ accordingly.}
+We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.
 
@@
 congressional elections. Lee estimates the incumbency advantage in electoral
-races for the House of Representatives --- parties that received the largest
+races for the House of Representatives --- candidates who received the largest
 vote share in the previous election are the incumbents, which creates the
@@
 standard deviation, and Root-MSE of the point
-estimators corresponding to each approach.  As expected, both
+estimators corresponding to each confidence interval.  As expected, both
 bias corrected estimators have
@@
 In Panel B, the coverages are very similar to those in Panel A, showing that both procedures are robust to heteroskedasticity.
-The final column, ``CI Length,'' indicates that our proposed bootstrap procedure consistently generates narrower intervals, in line with the coverage results.
+The final column, ``CI Length,'' 
+indicates that our proposed bootstrap procedure consistently generates narrower intervals.
 
@@
 a simple alternative to obtain valid robust confidence intervals in RD designs
-and similarly well compared to the analytical bias correction procedures proposed
+and performs well compared to the analytical bias correction procedures proposed
 by CCT.
@@
 
-In 1965, the Head Start program was established to help poor children aged three
+In 1965, the Head Start program was established to help poor children age three
 to five and their families. The program elements include parent involvement,
@@
     LM (2007)         & --1.114 & (--2.138                    & --0.090) & 36  &      &       & 0.027 \\
-    CCT               & --3.795 & (--7.040                    & --0.551) & 3   & .888 & 6.807 &       \\ 
-    Wild bootstrap    & --3.800 & (--6.738                    & --0.450) & 3   & .888 & 6.807 &       \\
+    CCT               & --3.795 & (--6.885                    & --0.706) & 3   & .888 & 6.807 &       \\ 
+    Wild bootstrap    & --3.800 & (--6.781                    & --0.408) & 3   & .888 & 6.807 &       \\
     \bottomrule
@@
     LM (2007)      & 0.030 & (0.003                      & 0.057) & 7&     &  & 0.032    \\
-    CCT            & 0.055 & (0.014                      & 0.096) & 3&.671 & 8.618       \\
-    Wild bootstrap & 0.055 & (0.010                      & 0.096) & 3&.671 & 8.618       \\\\
+    CCT            & 0.055 & (0.013                      & 0.097) & 3&.671 & 8.618       \\
+    Wild bootstrap & 0.055 & (0.010                      & 0.097) & 3&.671 & 8.618       \\\\
     \multicolumn{5}{l}{Fraction ``some college or more'' (Panel B)}                   \\
@@
     LM (2007)      & 0.037 & (0.002                      & 0.073) & 7&     &  & 0.032 \T \\
-    CCT            & 0.051 & (0.004                      & 0.099) & 5&.076 & 10.251      \\
-    Wild bootstrap & 0.052 & (0.007                      & 0.091) & 5&.076 & 10.251      \\
+    CCT            & 0.051 & (0.006                      & 0.096) & 5&.076 & 10.251      \\
+    Wild bootstrap & 0.052 & (0.006                      & 0.092) & 5&.076 & 10.251      \\
     \bottomrule
@@
    - h^2 (\hat\mu_{+,2}^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
-  &= e_0' \Gamma_{+,1}(h)^{-1} \Big(\tfrac{1}{n}
-  \sum_{i=1}^n r_1(X_i/h) K_{+,h}(X_i) \varepsilon_i^*\Big)
-   - e_0' \Gamma_{-,1}(h)^{-1} \Big(\tfrac{1}{n}
-  \sum_{i=1}^n r_1(X_i/h) K_{-,h}(X_i) \varepsilon_i^*\Big) \\
-  &\quad + h^2 e_2' \Gamma_{-,2}(b)^{-1}
-    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{-,b}(X_i) \varepsilon_i^* \Big) \Bf_-(h) \\
-  &\quad - h^2 e_2' \Gamma_{+,2}(b)^{-1}
-    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{+,b}(X_i) \varepsilon_i^*\Big) \Bf_+(h).
-\end{align*}
-We will prove convergence of the variance first, then prove asymptotic
-normality.
-
-To prove convergence in probability of the bootstrap variance, note that the
-wild bootstrap ensures
-\begin{equation*}
-  \V^*\Big(\sum_{i=1}^n R(X_i) \varepsilon_i^*\Big)
-  = \sum_{i=1}^n R(X_i)^2 \hat\varepsilon_i^2.
-\end{equation*}
-for any measurable function $R(\cdot)$.
-Given this expression for the iterated bootstrap and the formula for the
-variance conditional on $X$ presented at the end of the introduction to this
-appendix, it suffices to show that
+  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
+\end{align*}
+where
+$\epb_{+}^{*} =
+(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
+$\Omega_+(h,b)$ is an $M_+(b)$-dimensional vector with $i$th element
+$\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
+\begin{align*}
+  \Omega_{+,1i}(h,b) &=
+  (1\quad 0)
+  \Big(\ssum[+]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
+    r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
+\intertext{and}
+  \Omega_{+,2i}(h,b) &= (0\quad 0 \quad h^2)
+  \Big(\ssum[+]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
+    r_2(X_{m_+(b,i)} / b).
+\end{align*}
+The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same
+definitions as $\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the
+obvious substitutions of ``$-$'' for ``$+$.''
+
+Notice that~\eqref{eq:6} implies that
+\begin{equation*}
+  \hat\tau(h) - \Delta^*(h,b) - \tau
+  =^d \Omega_{+}(h,b)' \epb_{+} - \Omega_{-}(h,b)' \epb_{-} + O_p(h^3),
+\end{equation*}
+with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th
+element of which is distributed as
+\[
+  \varepsilon_{+,i} =^d
+  \begin{cases}
+    Y_{m_+(1,b)} - \E(Y_{m_+(1,b)} \mid X_{m_+(1,b)})
+    & \text{with probability\ } 1/M_+(b) \\
+    \vdots \\
+    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(M_+(b),b)})
+    & \text{with probability\ } 1/M_+(b),
+  \end{cases}
+\]
+and $\epb_-$ the corresponding quantity after replacing ``+'' with
+``--.''  Consequently, it suffices to prove that
 \begin{gather}
-  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_1(X_i/h)' K_{\bullet,h}(X_i)^2
-  \hat\varepsilon_i^2 = \tfrac{1}{h} \Psit_{\bullet,1,1}(h,h) + o_p(\tfrac{1}{h})
-  \label{eq:3} \\
-  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_2(X_i/b)' K_{\bullet,h}(X_i)
-  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{1}{b^2} \Psit_{\bullet,1,2}(h,b)
-  + o_p(\tfrac{1}{b^2})
-  \label{eq:5} \\
-  \tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) r_2(X_i/b)' K_{\bullet,b}(X_i)^2
-  \hat\varepsilon_i^2 = \tfrac{1}{b} \Psit_{\bullet,2,2}(b,b) + o_p(\tfrac{1}{b}).
   \label{eq:7}
+  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
+    V'(h,b)^{-1/2}\Omega_+(h,b)'\epb_{+}) \to^p 0
+  \intertext{and}
+  \label{eq:8}
+  \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
+    V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}) \to^p 0
 \end{gather}
-But these convergence results follow from CCT's results on
-$\hat\mu_{\bullet,p}^{(\nu)}$, Lemmas SA3 and SA4 in particular,
-and standard arguments on the convergence of residuals to
-the population error term.
-
-Normality also follows standard arguments for the Wild
-bootstrap. Conditional on the regressors and residuals,
-$\{R(X_i) \hat\varepsilon_i e_i^* \}$ is a sequence of independent and
-mean zero random variables for any measurable function $R$, each with
-$p$th absolute moment
-$\lvert R(X_i) \hat\varepsilon_i \rvert^p \E \lvert e_i^*
-\rvert^{p}$.
-The result then holds as a consequence of the Lindeberg-Feller CLT if
-we establish that Liapunov's condition holds in probability, specifically that
-\begin{equation}\label{eq:17}
-  (\tfrac{m}{n})^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
-  \hat\varepsilon_i \rvert^{2+\delta} \to^{p} 0.
-\end{equation}
-with
-\begin{equation*}
-  R_\bullet(X_i) = \gamma_1 r_1(X_i/h) K_{\bullet,h}(X_i) + h^2 \gamma_2 r_2(X_i/b) K_{\bullet,b}(X_i)
-\end{equation*}
-for arbitrary nonzero vectors $\gamma_1$ and $\gamma_2$.
-\citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}
-But similar arguments to those used for the variance establish~\eqref{eq:17}
-and complete the proof. \qed
+with $\rho$ the ``Mallows metric'' used by
+\citet{bickel1981}.\footnote{%
+  For two random vectors $u$ and $v$ with finite 2nd moments,
+  $\rho(u, v)$ is defined as
+  \begin{equation*}
+    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
+    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
+  \end{equation*}}
+Convergence in $\rho$ is equivalent to convergence in both distribution
+and second moments. \citep[Lemma 8.3.]{bickel1981}
+
+We will only prove~\eqref{eq:7} since the proof of~\eqref{eq:8} is
+identical. By Theorem 2.1 of \cite{freedman1981}, we have
+\begin{align*}
+  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
+  &V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}) \\
+  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
+    \tr(V'(h,b)^{-1/2} \Omega_+(h,b)' \Omega_+(h,b)V'(h,b)^{-1/2}) \\
+  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
+\end{align*}
+the second line holding as a consequence of CCT's Lemma SA1. So it suffices
+to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
+$\varepsilon^\circ_i$ be an i.i.d. sequence randomly drawn from the
+realized values of $\epb_+$ with replacement and let
+$\bar{\varepsilon}^\circ = (1/M_+(b)) \osum[+]{i}{b} \varepsilon^\circ_i$. Then,
+using the same arguments as \cite{freedman1981}, we have the upper bound
+\begin{equation*}
+  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
+  \leq
+  \Big((\bar\varepsilon^{\circ})^2 +
+  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2\Big)^{1/2}
+  + \rho(\varepsilon^\circ_1,\ \varepsilon_{+,1}).
+\end{equation*}
+But $(\bar\varepsilon^{\circ})^2 \to^p 0$ by the LLN,
+\[
+  (1/M_+(b)) \osum[+]{i}{b}
+  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
+\]
+by CCT's Lemma SA1, and
+$\rho(\varepsilon_1^\circ,\ \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
+\cite{bickel1981}.\qed
 

### 2016-08-10 main_paper.tex
update simulation table with HC3
The bootstrap estimator, naive estimator and robust estimator all use
HC3. Triangular kernel is used in this table, we can claim that other
kernels work similarly.

@@
     \midrule
-    1 & Wild bootstrap & --0.014 & 0.067 & 0.069 & 0.917 & 0.237 \\ 
-      & CCT            & --0.014 & 0.067 & 0.069 & 0.924 & 0.246 \\ 
-    2 & Wild bootstrap & --0.011 & 0.088 & 0.089 & 0.917 & 0.310 \\ 
-      & CCT            & --0.011 & 0.088 & 0.089 & 0.935 & 0.351 \\
-    3 & Wild bootstrap & --0.004 & 0.065 & 0.065 & 0.933 & 0.242 \\
-      & CCT            & --0.004 & 0.065 & 0.065 & 0.938 & 0.251 \\ 
-    \midrule                                                     \\
+    1 & Wild bootstrap & --0.011 & 0.067 & 0.068 & 0.926 & 0.247 \\ 
+      & CCT            & --0.011 & 0.067 & 0.068 & 0.928 & 0.247 \\ 
+      & Naive          & --0.037 & 0.041 & 0.055 & 0.835 & 0.155 \\ 
+    2 & Wild bootstrap & --0.008 & 0.086 & 0.086 & 0.938 & 0.334 \\ 
+      & CCT            & --0.008 & 0.086 & 0.086 & 0.942 & 0.346 \\
+      & Naive          & --0.145 & 0.065 & 0.159 & 0.353 & 0.241 \\
+    3 & Wild bootstrap & --0.005 & 0.065 & 0.065 & 0.945 & 0.252 \\ 
+      & CCT            & --0.005 & 0.065 & 0.065 & 0.945 & 0.253 \\ 
+      & Naive          &   0.034 & 0.051 & 0.061 & 0.862 & 0.191 \\ \\
     \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
     \midrule
-    1 & Wild bootstrap & --0.011 & 0.081 & 0.081 & 0.924 & 0.289 \\
-      & CCT            & --0.011 & 0.081 & 0.081 & 0.931 & 0.301 \\ 
-    2 & Wild bootstrap & --0.011 & 0.097 & 0.098 & 0.912 & 0.334 \\ 
-      & CCT            & --0.011 & 0.097 & 0.097 & 0.931 & 0.379 \\
-    3 & Wild bootstrap &   0.000 & 0.116 & 0.116 & 0.923 & 0.409 \\ 
-      & CCT            &   0.000 & 0.116 & 0.116 & 0.935 & 0.432 \\
+    1 & Wild bootstrap & --0.010 & 0.080 & 0.081 & 0.934 & 0.301 \\
+      & CCT            & --0.010 & 0.080 & 0.081 & 0.936 & 0.301 \\
+      & Naive          & --0.035 & 0.050 & 0.061 & 0.863 & 0.185 \\ 
+    2 & Wild bootstrap & --0.008 & 0.094 & 0.095 & 0.921 & 0.351 \\ 
+      & CCT            & --0.008 & 0.094 & 0.095 & 0.924 & 0.366 \\
+      & Naive          & --0.145 & 0.072 & 0.162 & 0.398 & 0.255 \\  
+    3 & Wild bootstrap & --0.001 & 0.103 & 0.103 & 0.942 & 0.396 \\ 
+      & CCT            & --0.001 & 0.103 & 0.103 & 0.942 & 0.395 \\ 
+      & Naive          &   0.036 & 0.073 & 0.081 & 0.859 & 0.251 \\  
     \bottomrule

### 2016-08-11 main_paper.tex
Update text of the simulation section
discuss simulation results when HC3 is used in all the three procedures.

@@
 To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
-simulate 5000 samples from each of the three DGPs and calculate nominal 95\%
+simulate 5000 samples from each of the three DGPs ($\gamma = 0$ and $\gamma = 2$) and calculate nominal 95\%
 two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to
@@
 the bias. The bandwidths, $h$ and $b$,
-are chosen using the AMSE-optimal rule proposed by CCT. We also estimate CCT's bias corrected procedure with AMSE-optimal bandwidths and
-the uniform kernel for direct comparison.
+are chosen using the AMSE-optimal rule proposed by CCT.
+
+We include two other procedures for comparison: CCT's bias-corrected interval and a ``naive" uncorrected estimator.
+We estimate CCT's bias corrected procedure with AMSE-optimal bandwidth and estimate the ``naive" uncorrected interval with the optimal bandwidth $h$ proposed by \cite{IK}.
+The HC3 type variance estimator is used in these two analytical procedures so that they are comparable to our bootstrap procedures.
+We use triangular kernel through out the three procedures.\footnote{Simulation results for other kernels are similar and available upon request.}
 
@@
 Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
-``Wild bootstrap'' shows results for our proposed bootstrap interval and ``CCT'' shows
-results for the analytically-corrected interval. The first three columns give the bias,
+``Wild bootstrap'' shows results for our proposed bootstrap interval; ``CCT'' shows
+results for the analytically-corrected interval and ``Naive" shows results for analytically-uncorrected interval. The first three columns give the bias,
 standard deviation, and Root-MSE of the point
@@
 The column ``CI Coverage'' lists the experimental coverage of each interval.
-In Panel A, all of the intervals from both robust estimators are reasonably close to their nominal coverage, although
-our proposed bootstrap procedure has coverages about one percentage lower than the CCT's analytical counterpart.
-In Panel B, the coverages are very similar to those in Panel A, showing that both procedures are robust to heteroskedasticity.
-The final column, ``CI Length,'' 
-indicates that our proposed bootstrap procedure consistently generates narrower intervals.
+In Panel A, all of the intervals from two robust estimators are reasonably close to their nominal coverage, although they slightly under cover the true treatment effect.
+The uncorrected intervals perform substantially worse---the naive analytical interval has coverage as bad as 35\% (in the second DGP) and never higher than 86\%.
+In Panel B, the coverage does not change too much from Panel A.
+In presence of heteroskedasticity, the two robust procedures again perform similarly and have coverage close to the nominal level.
+The final column, ``CI Length,'' indicates that intervals from the two robust procedures have almost the same length on average, while interval from the naive procedure has much shorter length on average.
+Not surprisingly, the average length of intervals from all three procedures increases when the data is heteroskedastic.
 

### 2016-08-11 main_paper.tex
Add references to other papers in the volume
As Matias requested (possibly in person), I've added references to other
related papers in the volume to our introduction.

--- 2016-08-10 main_paper.tex
@@
   See, for example, \cite{vdk2002}, \cite{jacoblefgren2004},
-  \cite{ludwig2007}, \cite{urquiola2009}, \cite{cellini2010}} %
+  \cite{ludwig2007}, \cite{urquiola2009}, and \cite{cellini2010}.} %
 But the underlying identification strategy has proven to apply much more
 widely and RD has been used in health economics,\footnote{%
-  \cite{Card2009,barreca2011saving}} %
+  \cite{Card2009}, \cite{barreca2011saving}, and \cite{KeeleEtAl}.} %
 political science,\footnote{%
   \cite{lee2008}, \cite{caughey2011elections}, \cite{keele2014geographic},
-  \cite{erikson2015}, \cite{Fujiwara2011,Fujiwara2015}} %
+  \cite{erikson2015}, and \cite{Fujiwara2011,Fujiwara2015}.} %
 and labor economics,\footnote{%
-  \cite{schmieder2012}.} %
+  \cite{schmieder2012} and \cite{frandsen}.} %
 among other fields. \cite{imbens2008} and \cite{lee2010} provide recent
@@
 same methods. Moreover, in this paper we focus on the baseline case of
-sharp RD with a local linear model, however, the results and procedures can be easily extended to the general local polynomial
-and higher order derivatives cases (e.g., Regression Kink Designs).
+sharp RD with a local linear model, however, the results and procedures can be
+easily extended to the general local polynomial and higher order derivatives
+cases (e.g., Regression Kink Designs, see \citealp{CardEtAl1,CardEtAl2}).
 
@@
 
+ The first part of Assumption \ref{A1} requires that the running variable be continuously distributed around the cutoff, and guarantees the presence of observations close to the threshold in large samples.
+ Next, this assumption imposes the existence of moments necessary for estimation and inference.
+ Part 3 imposes the traditional smoothness conditions on the expected potential outcomes and its derivatives around the cutoff which is crucial for identification of the parameters of interest and bias correction terms.
+ Finally, the last part of Assumption \ref{A1} describes the standard restrictions on the conditional variance of the observed $Y_{i}$ around the cutoff, allowing for different values on each side of the threshold.
+
  Since the conditions for identification only need to hold in a neighborhood
@@
 \end{assumption}
-To simplify notation, define the scaled kernel functions
-\begin{align*}
-  K_h(x) &= \tfrac{1}{h} K(x/h)
+To simplify notation, let $m = \min(h,b)$, $m' = \max(h,b)$, and
+define the scaled and truncated kernel functions
+\begin{align*}
+  K_{+,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x \geq 0\} &
+  K_{-,h}(x) &= \tfrac{1}{h} K(x/h) \1\{x < 0\}
 \intertext{and}
-  K_b(x) &= \tfrac{1}{b} K(x/b).
+  K_{+,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x \geq 0\} &
+  K_{-,b}(x) &= \tfrac{1}{b} K(x/b) \1\{x < 0\}.
 \end{align*}
@@
   \label{eq:4}
-  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V'(h, b)^{1/2}}
+  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V^{bc}(h, b)^{1/2}}
   \to^{d} N(0,1),
 \end{equation}
-where $\Delta^*(h,b)$ is defined by Equation~\ref{eq:9}.
+where $\Delta^*(h,b)$ is defined by Equation~\eqref{eq:9}.
 \end{theorem}
@@
     bootstrap estimates
-    $\hat\tau_1^{\prime*}(h,b), \dots, \hat\tau_{B_{2}}^{\prime*}(h,b)$. For the
-    $k$th value:
+    $\hat\tau_1^{bc*}(h,b), \dots, \hat\tau_{B_{2}}^{bc*}(h,b)$. For the
+    $k$th replication:
     \begin{enumerate}
@@
     \item Save the bias-corrected estimator
-      $\hat\tau_k^{\prime*}(h,b) = \hat\mu_+^*(h) - \hat\mu_i^*(h)
+      $\hat\tau_k^{bc*}(h,b) = \hat\mu_+^*(h) - \hat\mu_-^*(h)
       - \Delta^{**}(h,b)$.
     \end{enumerate}
-  \item Use the empirical CDF of
-    $\hat\tau_1^{\prime*}(h,b),\dots \hat\tau_{B_2}^{\prime*}(h,b)$ to
-    construct confidence intervals, etc.
+  \item Define $\tau^* = \hat g_+(0) - \hat g_-(0)$ and use the empirical CDF of
+    $\hat\tau_1^{bc*}(h,b) - \tau^*,\dots, \hat\tau_{B_2}^{bc*}(h,b) - \tau^*$
+    as the sampling distribution of $\hat \tau^{bc} - \tau$.
   \end{enumerate}
 \end{algorithm}
+
+One brief remark on implementing these algorithms. Many of the matrix operations
+required to estimate the local polynomials only involve the regressors and,
+therefore, only need to be computed once. For example, the parameter estimates
+for the linear model on the treated group are equal to
+\[
+\hat\beta_{+,1} = \underbrace{(\mathbf{X}' \mathbf{K}_+ \mathbf{X})^{-1} \mathbf{X}' \mathbf{K}_+}_{\mathbf{W}_{+,1}} \mathbf{Y}
+\]
+where
+\begin{align*}
+\mathbf{X} &= \begin{pmatrix*} 1 & X_1 \\ 1 & X_2 \\ \vdots & \vdots \\ 1 & X_n \end{pmatrix*} &
+\mathbf{Y} &= \begin{pmatrix*} Y_1 \\ Y_2 \\ \vdots \\ Y_n \end{pmatrix*} &
+\mathbf{K}_+ &= \begin{pmatrix*}
+  K_{+,h}(X_1) & 0 & \cdots & 0 \\
+  0 & K_{+,h}(X_2) & \cdots & 0 \\
+  0 & 0 & \ddots & 0 \\
+  0 & 0 & \cdots & K_{+,h}(X_n) \end{pmatrix*}.
+\end{align*}
+The matrix $\mathbf{W}_{+,1}$ is not affected by the bootstrap so it can be
+computed once initially and reused in the bootstrap calculations and each
+bootstrap replication just requires a single matrix-vector multiplication. The
+other parameter estimates have this property as well. Consequently, the
+computational burden of this iterated bootstrap is much lower than might
+appear.\footnote{%
+  An open-source implementation of this algorithm written in R, which was used
+  for the empirical and Monte Carlo components of this paper, is available
+  online at \url{https://github.com/grayclhn/boot-rd}.} %
 
@@
   Under Assumptions~\ref{A1} and~\ref{A2},
-  \begin{gather*}
-    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V'(h,b) \to^p 1
-  \intertext{and}
-    \sup_{x}
-    \Big\rvert \Pr^*[\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^* \leq x ]
-    - \Pr[\hat\tau(h) - \Delta^*(h,b) - \tau \leq x] \Big\lvert \to^p 0.
-  \end{gather*}
+  \begin{equation*}
+    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V^{bc}(h,b) \to^p 1
+  \end{equation*}
+  and
+  \begin{multline*}
+    \sup_{x,\tau}
+    \Big\rvert \Pr^*\big[ \sqrt{nh}
+    (\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^*) \leq x \big] \\
+    - \Pr\big[ \sqrt{nh}
+    (\hat\tau(h) - \Delta^*(h,b) - \tau) \leq x \big] \Big\lvert \to^p 0.
+  \end{multline*}
 \end{theorem}
@@
 intervals similar to those obtained by the analytical procedures established
-in CCT. The bootstrap CIs obtained compare favorably to the analytical
-alternative, with coverage slightly closer to nominal coverage and shorter
+in CCT. The bootstrap CIs obtained are comparable to the analytical
+alternative, albeit with slightly lower coverage and shorter
 length of the intervals in the specifications implemented. We also find that
 all of the bias corrected methods can offer substantial improvements over
-estimators that do not bias correct, including a ``naive'' bootstrap procedure.
+estimators that do not bias correct.
 
@@
 comparable with theirs and with the rest of the literature.
-They use this experimental design with a constant $\sigma_i = 0.1295$.
-We follow \cite{mackinnon2013thirty} to use a parameter $\gamma$ and a function $z(\gamma)$ to control the degree of heteroskedasticity.
+While they use this experimental design with homoskedastic errors, we introduce heteroskedasticity following the design in \cite{mackinnon2013thirty}.
+We control the degree of heteroskedasticity through the parameter $\gamma$ and a function $z(\gamma)$.
 When $\gamma = 0$, we set $z(\gamma) = 0.1295$ such that our DGP is exactly the same as \citet{IK} and CCT.
-When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.
-\footnote{The rescaling requires that $\max(h, b)$ is known, which is usually not the case in practice because $h$ and $b$ are data-driven.
-For simplicity, we firstly find $\overline{\max[h, b]}$ from \textbf{homoskedastic} data through 500 replications and then calculate $z(\gamma)$ for every bootstrap data accordingly.
-In our simulation, $\overline{\max[h, b]}$ is obtained by (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector and (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$.
-Once $\overline{\max[h, b]}$ is known, we use it to generate heteroskedastic data using following steps: (1) generate random running variable $X_i$, (2) let $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$ and calculate the standard deviation and (3) generate disturbance term and outcome $Y_i$ accordingly.}
-We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.
+When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.\footnote{In practice, the optimal $h$ and $b$ are usually data driven, so $h$, $b$ and $\sigma_i$ are simultaneously determined.
+For simplicity, we use the following steps to find $z(\gamma)$: (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector, (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$ and (3) define $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$.} We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.
 
@@
     LM (2007)         & --1.114 & (--2.138                    & --0.090) & 36  &      &       & 0.027 \\
-    CCT               & --3.795 & (--6.885                    & --0.706) & 3   & .888 & 6.807 &       \\ 
-    Wild bootstrap    & --3.800 & (--6.781                    & --0.408) & 3   & .888 & 6.807 &       \\
+    CCT               & --3.795 & (--7.040                    & --0.551) & 3   & .888 & 6.807 &       \\ 
+    Wild bootstrap    & --3.800 & (--6.738                    & --0.450) & 3   & .888 & 6.807 &       \\
     \bottomrule
@@
     LM (2007)      & 0.030 & (0.003                      & 0.057) & 7&     &  & 0.032    \\
-    CCT            & 0.055 & (0.013                      & 0.097) & 3&.671 & 8.618       \\
-    Wild bootstrap & 0.055 & (0.010                      & 0.097) & 3&.671 & 8.618       \\\\
+    CCT            & 0.055 & (0.014                      & 0.096) & 3&.671 & 8.618       \\
+    Wild bootstrap & 0.055 & (0.010                      & 0.096) & 3&.671 & 8.618       \\\\
     \multicolumn{5}{l}{Fraction ``some college or more'' (Panel B)}                   \\
@@
     LM (2007)      & 0.037 & (0.002                      & 0.073) & 7&     &  & 0.032 \T \\
-    CCT            & 0.051 & (0.006                      & 0.096) & 5&.076 & 10.251      \\
-    Wild bootstrap & 0.052 & (0.006                      & 0.092) & 5&.076 & 10.251      \\
+    CCT            & 0.051 & (0.004                      & 0.099) & 5&.076 & 10.251      \\
+    Wild bootstrap & 0.052 & (0.007                      & 0.091) & 5&.076 & 10.251      \\
     \bottomrule
@@
 Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
-everywhere else. Define the following additional notation:\footnote{%
+everywhere else. Much of the theory in this appendix applies to both
+sides of the cutoff symmetrically, so we will use a ``$\bullet$'' as a
+placeholder for either $+$ or $-$ in equations; i.e.\ the equation
+\[
+  \hat\mu_\bullet(h) = \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
+  (Y_i - \mu - \beta X_i)^2 K_{\bullet,h}(X_i)
+\]
+would define both $\hat\mu_+(h)$ and $\hat\mu_-(h)$ as
+\begin{align*}
+  \hat\mu_+(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
+  (Y_i - \mu - \beta X_i)^2 K_{+,h}(X_i) \\
+  \hat\mu_-(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
+  (Y_i - \mu - \beta X_i)^2 K_{-,h}(X_i).
+\end{align*}
+Define the following additional notation:\footnote{%
   As we mention in Section~\ref{background}, we have adopted CCT's
   notation where possible and these terms originate in that paper.} %
-$r_p(x) = (1,\ x,\dots,\ x^p)'$,
-\begin{align*}
-  (\hat{\mu}_{+,p}(h),\ \hat{\mu}_{+,p}^{(1)}(h),\dots,\ \hat\mu_{+,p}^{(p)}(h))'
-  &= \argmin_{\beta} \ssum[+]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2 \\
-  (\hat{\mu}_{-,p}(h),\ \hat{\mu}_{-,p}^{(1)}(h),\dots,\ \hat\mu_{-,p}^{(p)}(h))'
-  &= \argmin_{\beta} \ssum[-]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2
-\end{align*}
-and
-\begin{align*}
-  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
-  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
-  \Psi_{+,p,q}(h,b)
-  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
-    \V(Y_i \mid X_i) \\
-  \Psi_{-,p,q}(h,b)
-  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
-    \V(Y_i \mid X_i) \\
-  \Bf_+(h)
-  & = e_0' \Gamma_{+,1}^{-1}(h)
-    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
-  \Bf_-(h)
-  & = e_0' \Gamma_{-,1}^{-1}(h)
-    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
-\end{align*}
-
-Also, for reference, define the variance terms
+$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x \geq 0\}$, $\1_-(x) = \1\{x < 0\}$,
+\begin{align*}
+  \Gamma_{\bullet,p}(h)
+  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_p(X_i/h)' K_{\bullet,h}(X_i) \\
+  \Bf_\bullet(h)
+  & = e_0' \big(\Gamma_{\bullet,1}(h)\big)^{-1}
+    \tfrac{1}{n} \sum_{i=1}^n (X_i / h)^2 r_1(X_i/h) K_{\bullet,h}(X_i) \\
+  \Psi_{\bullet,p,q}(h,b)
+  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_q(X_i/b)'
+     K_{\bullet,h}(X_i) K_{\bullet,b}(X_i) \V(Y_i \mid X_i)
+\end{align*}
+as well as their population counterparts,
+\begin{align*}
+  \Gammat_{\bullet,p}(h) &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) f(h u) \1_\bullet(u) du \\
+  \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
+  \Bft_\bullet(h) & = e_0' \big(\Gammat_{\bullet,1}(h)\big)^{-1}
+    \int_{-\infty}^\infty r_1(u) u^2 K(u) f(h u) \1_\bullet(u) du \\
+  \Bf_\bullet & = e_0' \Gamma_{\bullet,1}^{-1} \int_{-\infty}^\infty r_1(u) u^2 K(u) \1_\bullet(u) du \\
+  \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
+     r_p(\tfrac{m}{h} u) r_q(\tfrac{m}{b} u)' K(\tfrac{m}{b} u) K(\tfrac{m}{h} u)
+     \V(Y_i \mid X_i = um) f(um) \1_\bullet(u) du \\
+  \Psi_{\bullet,p} &= \int_{-\infty}^\infty
+     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
+\end{align*}
+Remember that $f$ is the pdf of the running variable. Lemmas
+SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
+Assumptions~\ref{A1} and~\ref{A2} (for some, after normalization), namely that
+the following relationships hold:
+\begin{align}
+  \Gamma_{\bullet,p}(h) & = \Gammat_{\bullet,p}(h) + o_p(1) &
+  \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
+  \Bf_{\bullet}(h) &= \Bft_{\bullet}(h) + o_p(1) &
+  \Bft_{\bullet}(h) &= \Bf_{\bullet} + o_p(1) \label{eq:11} \\
+  \max(h,b) \times \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
+  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
+\end{align}
+Implicitly the right column of equations holds as $h \to 0$.
+
+Also let $\hat\beta_{\bullet,p}(h)$ be the coefficient
+estimators from the weighted regression of $Y_i$ on $r_p(X_i)$. As in CCT, this
+implies that
+\begin{align*}
+  \hat\beta_{\bullet,p}(h) &= H_p(h) \Gamma_{\bullet,p}(h)^{-1}
+  \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) Y_i K_{\bullet,h}(X_i)
+\end{align*}
+with $H_p(h) = \diag(1, h^{-1}, \dots, h^{-p})$.
+These coefficients are related to the quantities of interest by
+\begin{equation*}
+  \hat{\mu}_{\bullet,p}^{(\nu)}(h) = \nu! e_\nu' \hat\beta_{\bullet,p}(h).
+\end{equation*}
+for $\nu = 0,\dots,p$ and similar arguments to those used above imply that
+\begin{equation*}
+  H_p(h)^{-1}(\hat\beta_{\bullet,p}(h) - \beta_{\bullet,p}(h))= O_p(1/\sqrt{nh}).
+\end{equation*}
+
+For reference, define the variance terms
 \begin{equation*}
   V(h)
-  = e_0' \Big(\tfrac{1}{n} \Gamma_{-,1}^{-1} \Psi_{-,1} \Gamma_{-,1}^{-1}
-  + \tfrac{1}{n} \Gamma_{+,1}^{-1} \Psi_{+,1} \Gamma_{+,1}^{-1}\Big) e_0
+  = \tfrac{1}{n} e_0' \big(\Gamma_{-,1}(h)^{-1} \Psi_{-,1,1}(h,h)
+    \Gamma_{-,1}(h)^{-1}
+  + \Gamma_{+,1}(h)^{-1} \Psi_{+,1,1}(h,h) \Gamma_{+,1}(h)^{-1} \big) e_0
 \end{equation*}
@@
 By construction,
-\begin{align*}
-  \hat\beta^*_{+,p} - \beta^*_{+,p}
-  & = \Big(\sum_{i\in I_+} K_h(X_i) r_p(X_i) r_p(X_i)'\Big)^{-1}
-  \sum_{i \in I_+} K_h(X_i) r_p(X_i) \hat\varepsilon_i e_i^* \\
-  \hat\beta^*_{-,p} - \beta^*_{-,p}
-  &= \Big(\sum_{i\in I_-} K_h(X_i) r_p(X_i) r_p(X_i)'\Big)^{-1}
-  \sum_{i \in I_-} K_h(X_i) r_p(X_i) \hat\varepsilon_i e_i^*
-\end{align*}
-ensuring that
-\begin{align*}
-  \E^* \hat\mu_{+,1}^*(h) - \mu_{+}^{*}
-  &= h^{2} \mu_{+}^{*(2)} \Bf_{+}(h)/2,
-  &\E^* \hat\mu_{-,1}^*(h) - \mu_{-}^{*}
-  &= h^{2} \mu_{-}^{*(2)} \Bf_{-}(h)/2,
-\end{align*}
-almost surely. Consequently,
+\begin{equation*}
+  Y_i^* =
+  \begin{cases}
+    r_2(X_i/b)'H_2(b) \beta_{+,2}^* + \varepsilon_i^* & X_i \geq 0 \\
+    r_2(X_i/b)'H_2(b) \beta_{-,2}^* + \varepsilon_i^* & X_i < 0
+  \end{cases}
+\end{equation*}
+which, along with the definitions at the beginning of the appendix,
+ensures that
+\begin{align*}
+  \E^* \hat\mu_{\bullet,1}^*(h) - \mu_{\bullet}^{*}
+  = h^{2} \mu_{\bullet}^{*(2)} \Bf_{\bullet}(h)/2
+\end{align*}
+almost surely and, consequently,
 \begin{equation*}
@@
    - h^2 (\hat\mu_{+,2}^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
-  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
-\end{align*}
-where
-$\epb_{+}^{*} =
-(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
-$\Omega_+(h,b)$ is an $M_+(b)$-dimensional vector with $i$th element
-$\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
-\begin{align*}
-  \Omega_{+,1i}(h,b) &=
-  (1\quad 0)
-  \Big(\ssum[+]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
-    r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
-\intertext{and}
-  \Omega_{+,2i}(h,b) &= (0\quad 0 \quad h^2)
-  \Big(\ssum[+]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
-    r_2(X_{m_+(b,i)} / b).
-\end{align*}
-The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same
-definitions as $\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the
-obvious substitutions of ``$-$'' for ``$+$.''
-
-Notice that~\eqref{eq:6} implies that
-\begin{equation*}
-  \hat\tau(h) - \Delta^*(h,b) - \tau
-  =^d \Omega_{+}(h,b)' \epb_{+} - \Omega_{-}(h,b)' \epb_{-} + O_p(h^3),
-\end{equation*}
-with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th
-element of which is distributed as
-\[
-  \varepsilon_{+,i} =^d
-  \begin{cases}
-    Y_{m_+(1,b)} - \E(Y_{m_+(1,b)} \mid X_{m_+(1,b)})
-    & \text{with probability\ } 1/M_+(b) \\
-    \vdots \\
-    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(M_+(b),b)})
-    & \text{with probability\ } 1/M_+(b),
-  \end{cases}
-\]
-and $\epb_-$ the corresponding quantity after replacing ``+'' with
-``--.''  Consequently, it suffices to prove that
+  &= e_0' \Gamma_{+,1}(h)^{-1} \Big(\tfrac{1}{n}
+  \sum_{i=1}^n r_1(X_i/h) K_{+,h}(X_i) \varepsilon_i^*\Big)
+   - e_0' \Gamma_{-,1}(h)^{-1} \Big(\tfrac{1}{n}
+  \sum_{i=1}^n r_1(X_i/h) K_{-,h}(X_i) \varepsilon_i^*\Big) \\
+  &\quad + h^2 e_2' \Gamma_{-,2}(b)^{-1}
+    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{-,b}(X_i) \varepsilon_i^* \Big) \Bf_-(h) \\
+  &\quad - h^2 e_2' \Gamma_{+,2}(b)^{-1}
+    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{+,b}(X_i) \varepsilon_i^*\Big) \Bf_+(h).
+\end{align*}
+We will prove convergence of the variance first, then prove asymptotic
+normality.
+
+To prove convergence in probability of the bootstrap variance, note that the
+wild bootstrap ensures
+\begin{equation*}
+  \V^*\Big(\sum_{i=1}^n R(X_i) \varepsilon_i^*\Big)
+  = \sum_{i=1}^n R(X_i)^2 \hat\varepsilon_i^2.
+\end{equation*}
+for any measurable function $R(\cdot)$.
+Given this expression for the iterated bootstrap and the formula for the
+variance conditional on $X$ presented at the end of the introduction to this
+appendix, it suffices to show that
 \begin{gather}
+  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_1(X_i/h)' K_{\bullet,h}(X_i)^2
+  \hat\varepsilon_i^2 = \tfrac{1}{h} \Psit_{\bullet,1,1}(h,h) + o_p(\tfrac{1}{h})
+  \label{eq:3} \\
+  \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_2(X_i/b)' K_{\bullet,h}(X_i)
+  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{1}{b^2} \Psit_{\bullet,1,2}(h,b)
+  + o_p(\tfrac{1}{b^2})
+  \label{eq:5} \\
+  \tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) r_2(X_i/b)' K_{\bullet,b}(X_i)^2
+  \hat\varepsilon_i^2 = \tfrac{1}{b} \Psit_{\bullet,2,2}(b,b) + o_p(\tfrac{1}{b}).
   \label{eq:7}
-  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
-    V'(h,b)^{-1/2}\Omega_+(h,b)'\epb_{+}) \to^p 0
-  \intertext{and}
-  \label{eq:8}
-  \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
-    V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}) \to^p 0
 \end{gather}
-with $\rho$ the ``Mallows metric'' used by
-\citet{bickel1981}.\footnote{%
-  For two random vectors $u$ and $v$ with finite 2nd moments,
-  $\rho(u, v)$ is defined as
-  \begin{equation*}
-    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
-    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
-  \end{equation*}}
-Convergence in $\rho$ is equivalent to convergence in both distribution
-and second moments. \citep[Lemma 8.3.]{bickel1981}
-
-We will only prove~\eqref{eq:7} since the proof of~\eqref{eq:8} is
-identical. By Theorem 2.1 of \cite{freedman1981}, we have
-\begin{align*}
-  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
-  &V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}) \\
-  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
-    \tr(V'(h,b)^{-1/2} \Omega_+(h,b)' \Omega_+(h,b)V'(h,b)^{-1/2}) \\
-  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
-\end{align*}
-the second line holding as a consequence of CCT's Lemma SA1. So it suffices
-to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
-$\varepsilon^\circ_i$ be an i.i.d. sequence randomly drawn from the
-realized values of $\epb_+$ with replacement and let
-$\bar{\varepsilon}^\circ = (1/M_+(b)) \osum[+]{i}{b} \varepsilon^\circ_i$. Then,
-using the same arguments as \cite{freedman1981}, we have the upper bound
-\begin{equation*}
-  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
-  \leq
-  \Big((\bar\varepsilon^{\circ})^2 +
-  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2\Big)^{1/2}
-  + \rho(\varepsilon^\circ_1,\ \varepsilon_{+,1}).
-\end{equation*}
-But $(\bar\varepsilon^{\circ})^2 \to^p 0$ by the LLN,
-\[
-  (1/M_+(b)) \osum[+]{i}{b}
-  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
-\]
-by CCT's Lemma SA1, and
-$\rho(\varepsilon_1^\circ,\ \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
-\cite{bickel1981}.\qed
+But these convergence results follow from CCT's results on
+$\hat\mu_{\bullet,p}^{(\nu)}$, Lemmas SA3 and SA4 in particular,
+and standard arguments on the convergence of residuals to
+the population error term.
+
+Normality also follows standard arguments for the Wild
+bootstrap. Conditional on the regressors and residuals,
+$\{R(X_i) \hat\varepsilon_i e_i^* \}$ is a sequence of independent and
+mean zero random variables for any measurable function $R$, each with
+$p$th absolute moment
+$\lvert R(X_i) \hat\varepsilon_i \rvert^p \E \lvert e_i^*
+\rvert^{p}$.
+The result then holds as a consequence of the Lindeberg-Feller CLT if
+we establish that Liapunov's condition holds in probability, specifically that
+\begin{equation}\label{eq:17}
+  (\tfrac{m}{n})^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
+  \hat\varepsilon_i \rvert^{2+\delta} \to^{p} 0.
+\end{equation}
+with
+\begin{equation*}
+  R_\bullet(X_i) = \gamma_1 r_1(X_i/h) K_{\bullet,h}(X_i) + h^2 \gamma_2 r_2(X_i/b) K_{\bullet,b}(X_i)
+\end{equation*}
+for arbitrary nonzero vectors $\gamma_1$ and $\gamma_2$.
+\citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}
+But similar arguments to those used for the variance establish~\eqref{eq:17}
+and complete the proof. \qed
 

### 2016-08-11 main_paper.tex
Make small tweaks to description of procedure in introduction

@@
 bootstrap. In particular, we propose estimating the local linear model as usual,
-then estimating a local second order polynomial and generating bootstrap
-datasets based on the approximation provided by that polynomial. Since the second order
-polynomial is the true Data Generating Process (DGP) for the bootstrapped data,
+but generating bootstrap datasets from an approximation provided by a local
+second order polynomial. Since the second order polynomial is the true Data
+Generating Process (DGP) for the bootstrapped dataset,
 its estimate of the treatment effect is the true value of the treatment effect
@@
 an iterated bootstrap procedure \citep{hall1988}: use the second order
-polynomial wild bootstrap to produce many bootstrap replications of the bias
+polynomial bootstrap to produce many bootstrap replications of the bias
 corrected estimator, and then use the resulting bootstrap distribution to
 produce confidence intervals. This procedure, which requires bootstrapping the
-datasets produced by an initial bootstrap, is described in Algorithm~\ref{Alg2}, and the resulting confidence intervals are shown to be asymptotically valid in Theorem~\ref{T2}.
+datasets produced by an initial bootstrap, is described in Algorithm~\ref{Alg2}
+and the resulting confidence intervals are shown to be asymptotically valid in
+Theorem~\ref{T2}.
 

### 2016-08-11 main_paper.tex
Add url for our source code

@@
   \protect\url{http://gray.clhn.org};
-  He: \protect\url{yanghe@iastate.edu}.}}
+  He: \protect\url{yanghe@iastate.edu}. Source code for the Monte Carlo
+  experiments and empirical component of this paper are available online
+  at \protect\url{https://github.com/grayclhn/boot-rd}.}}
 
@@
   \textit{doParallel}, \textit{foreach} \citep{doparallel,foreach}, and
-  \textit{doRNG} \citep{dorng} packages.} %
+  \textit{doRNG} \citep{dorng} packages. Our source code is available online
+  at \url{https://github.com/grayclhn/boot-rd}.} %
 Finally, Section~\ref{conclusion} concludes.

### 2016-08-11 main_paper.tex
Tweak discussion of parts of assumption 1
This commit modifies the discussion of the different parts of Assumption 1 to be
more in line with my expectations of what the referee wants. It attributes the
parts to 'identification' or 'estimation' instead of simply restating the assumptions.

@@
 easily extended to the general local polynomial and higher order derivatives
-cases (e.g., Regression Kink Designs, see \citealp{CardEtAl1,CardEtAl2}).
+cases (e.g., Regression Kink Designs, see \citealp{card2009b}, and
+\citealp{CardEtAl1,CardEtAl2}).
 
@@
 \end{align*}
-where the symbol $\V(\cdot)$ represents the variance.  The effect $\tau$ is
-nonparametrically identified because both $\mu_-$ and $\mu_+$ can be estimated
-consistently under Assumption~\ref{A1}, which lists standard conditions in the
-RD literature. (See, in particular, \citealp{HTV2001}, \citealp{Porter03}, and
-CCT.)
+where the symbol $\V(\cdot)$ represents the variance. Assumption~\ref{A1} lists
+standard conditions in the RD literature which ensure that both $\mu_-$ and
+$\mu_+$ can be estimated consistently.
 
@@
 
- The first part of Assumption \ref{A1} requires that the running variable be continuously distributed around the cutoff, and guarantees the presence of observations close to the threshold in large samples.
- Next, this assumption imposes the existence of moments necessary for estimation and inference.
- Part 3 imposes the traditional smoothness conditions on the expected potential outcomes and its derivatives around the cutoff which is crucial for identification of the parameters of interest and bias correction terms.
- Finally, the last part of Assumption \ref{A1} describes the standard restrictions on the conditional variance of the observed $Y_{i}$ around the cutoff, allowing for different values on each side of the threshold.
-
- Since the conditions for identification only need to hold in a neighborhood
+Part 1 and the continuity component of Part 3 of Assumption~\ref{A1} are crucial
+for identifying $\tau$ --- informally, they ensure that the number of points
+arbitrarily close to the cutoff increases with the sample size and that there is
+a small neighborhood around the cutoff in which the change in the conditional
+expectation can be attributed to the change in treatment status.  (See
+\citealp{HTV2001}, and \citealp{Porter03}, for more detailed discussion of
+identification in RD designs.) The additional smoothness conditions in Part 3
+allow higher order polynomials to be used for estimation and Parts 2 and 4
+ensure that the estimated local polynomials are well behaved.
+
+Since these conditions only need to hold in a neighborhood
 around the cutoff, $\mu_+$ and $\mu_-$ can be estimated by extrapolating from a
@@
   higher order polynomials discontinuities in the derivatives of the conditional
-  expectation, like ``Kink RD'' design \citep{card2009b}.} %
-
+  expectation, at the cost of stronger moment and smoothness assumptions.} %
 For this model, if $h$ represents a bandwidth parameter and $K(\cdot)$ a density

### 2016-08-11 main_paper.tex
Tweak Assumption 2.
We don't expliclty impose boundedness of the kernel and don't explain
what kappa is.

@@
     $n \to \infty$.}
-  The kernel function $K$ is positive and continuous on the interval
-  $[-\kappa,~\kappa]$ and zero outside that interval.
+  The kernel function $K$ is positive, bounded, and continuous on the interval
+  $[-\kappa,~\kappa]$ and zero outside that interval for some $\kappa > 0$.
 \end{assumption}

### 2016-08-11 main_paper.tex
Tweak end of Algorithm 2
We've defined \hat\tau^{bc} as the CCT bias corrected estimator, so
using it as the bootstrap bias corrected estimator in Algorithm 2 is
a bit confusing. I've changed algorithm 2 to explicitly debias the
estimator to reduce that confusion.

@@
       represent the bias estimator returned by Algorithm~\ref{Alg1}.
-    \item Save the bias-corrected estimator
-      $\hat\tau_k^{bc*}(h,b) = \hat\mu_+^*(h) - \hat\mu_-^*(h)
-      - \Delta^{**}(h,b)$.
+    \item Save the estimator of $\tau$ and its bias,
+      $\hat\tau_k^{*}(h) = \hat\mu_+^*(h) - \hat\mu_-^*(h)$ and $\Delta_k^{**}(h,b)$.
     \end{enumerate}
   \item Define $\tau^* = \hat g_+(0) - \hat g_-(0)$ and use the empirical CDF of
-    $\hat\tau_1^{bc*}(h,b) - \tau^*,\dots, \hat\tau_{B_2}^{bc*}(h,b) - \tau^*$
-    as the sampling distribution of $\hat \tau^{bc} - \tau$.
+    $\hat\tau_1^{*}(h) - \Delta_1^{**}(h,b)- \tau^*,\dots, \hat\tau_{B_2}^{*}(h)  - \Delta_{B_2}^{**}(h,b) - \tau^*$
+    as the sampling distribution of $\hat \tau(h) - \Delta^*(h,b) - \tau$.
   \end{enumerate}

### 2016-08-11 main_paper.tex
Small changes to wording in Section 3
Add mention of HC3 wild bootstrap adjustment

@@
 
-Note that the variance component of~\eqref{eq:4} is the same value used by CCT
-and introduced in~\eqref{eq:1}. Theorem~\ref{T1} implies that our bias-corrected
+Theorem~\ref{T1} implies that our bias-corrected
 estimator has the same asymptotic distribution as CCT's. This equivalence should
@@
 
-One brief remark on implementing these algorithms. Many of the matrix operations
+Theorem~\ref{T2} establishes that this iterated bootstrap approximates the
+asymptotic distribution of the bias-corrected statistic proposed by
+Algorithm~\ref{Alg1} and justifies this second algorithm.  As before, we assume
+that $B_1$ and $B_2$ are large enough that simulation error can be ignored.
+
+\begin{theorem}\label{T2}
+  Under Assumptions~\ref{A1} and~\ref{A2},
+  \begin{equation*}
+    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V^{bc}(h,b) \to^p 1
+  \end{equation*}
+  and
+  \begin{equation*}
+    \sup_{x,\tau}
+    \Big\rvert \Pr^*\big[ \sqrt{nh}
+    (\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^*) \leq x \big]
+    - \Pr\big[ \sqrt{nh}
+    (\hat\tau(h) - \Delta^*(h,b) - \tau) \leq x \big] \Big\lvert \to^p 0.
+  \end{equation*}
+\end{theorem}
+
+Two brief remarks on implementing these algorithms. First, many of the matrix operations
 required to estimate the local polynomials only involve the regressors and,
@@
 
-Theorem~\ref{T2} establishes that this iterated bootstrap approximates the
-asymptotic distribution of the bias-corrected statistic proposed by
-Algorithm~\ref{Alg1} and justifies this second algorithm.  As before, we assume
-that $B_1$ and $B_2$ are large enough that simulation error can be ignored.
-
-\begin{theorem}\label{T2}
-  Under Assumptions~\ref{A1} and~\ref{A2},
-  \begin{equation*}
-    \V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))/V^{bc}(h,b) \to^p 1
-  \end{equation*}
-  and
-  \begin{multline*}
-    \sup_{x,\tau}
-    \Big\rvert \Pr^*\big[ \sqrt{nh}
-    (\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^*) \leq x \big] \\
-    - \Pr\big[ \sqrt{nh}
-    (\hat\tau(h) - \Delta^*(h,b) - \tau) \leq x \big] \Big\lvert \to^p 0.
-  \end{multline*}
-\end{theorem}
+Second, if the error terms have pronounced heteroskedasticity, it can be
+advantageous to transform the residuals before applying the bootstrap, as
+discussed by \citet{DF08} --- these transformations typically do not affect the
+first-order asymptotic properties of the bootstrap distribution but can provide
+improvements in finite samples analagous to alternative
+heteroskedasticity-robust variance estimators. (\citealp{mackinnon1985some}, and
+\citealp{mackinnon2013thirty}.) Since RD estimators rely on a small subset of
+the data available in any application, these finite-sample adjustments can be
+especially effective in improving performance, and we use the ``HC3''
+transformation proposed by \citet{DF08} in this paper's Monte Carlo simulations
+and empirical exercise.
 
@@
 the bias. The bandwidths, $h$ and $b$,
-are chosen using the AMSE-optimal rule proposed by CCT. We also estimate CCT's bias corrected procedure with AMSE-optimal bandwidths and
+are chosen using the AMSE-optimal rule proposed by CCT and the Wild bootstrap
+uses the ``HC3'' transformation of \citet{DF08}. We also estimate CCT's bias
+corrected procedure with AMSE-optimal bandwidths and
 the uniform kernel for direct comparison.
@@
 procedure introduced in this paper.  Our bootstrap estimator uses the
-AMSE-optimal bandwidths proposed by CCT and the uniform kernel. In the bootstrap
+AMSE-optimal bandwidths proposed by CCT, the uniform kernel, and the HC3 Wild
+bootstrap from \citet{DF08}. In the bootstrap
 procedure, we use 500 bootstraps for bias correction and 999 to calculate the

### 2016-08-11 Reply_Referee1.tex
Add cover letter to editor

@@
 summarizes several convergence results from Calonico, Cattaneo, and Titiunik
-(2014) that are referenced in the proofs.
+(2014) that are referenced in the proofs and we have made some small additional
+changes that the referees suggested.
 

### 2016-08-11 Reply_Referee2.tex
Adds reply to comment #2.
Oops
Add cover letter to editor

@@
 
-   \textbf{We need to decide what to answer here. My general feeling is that this is all very standard in RDD. We could however add a couple of paragraphs as he suggests, what do you think?}
+ Thanks. A short discussion has been added to the main text.
 

### 2016-08-11 cover_letter.tex
Add cover letter to editor

\documentclass[12pt,fleqn]{article}

% Add commit information from Git to the pdf. It is automatically
% generated with the R script 'tex/git and can be run from
% the command line in the project's top directory via:
%
% $ tex/git
%
% If VERSION.tex does not exist we can't add information from
% Git, so we'll use today's date as a fallback.

\IfFileExists{./VERSION.tex}{\input{VERSION}}{%
\providecommand\VERSION{\today}}

\input{tex/setup}
\input{tex/macros}

\begin{document}

\noindent%
Hi Matias,

Thank you for your helpful comments. We have made the requested changes. Overall,
for this version of the paper, we have changed the bootstrap method from the
residual bootstrap to the wild bootstrap. We have also updated the simulations
to include DGPs featuring heteroskedasticity. We believe that the residual
bootstrap used in the previous version is theoretically correct even under
heteroskedastcity as long as the conditional variance is assumed to be smooth in
a neighorbood around the cutoff point, since the residual bootstrap we initially
proposed only resampled from that neighborhood, but we agree that in practice
the wild bootstrap is likely to be more accurate and can accomodate forms of
conditional heteroskedasticity that the residual bootstrap can not.

We have also relaxed the ``uniform kernel'' requirement and allow other kernels
that are popular in practice. The title of the paper has been updated to reflect
that change.

The first referee expressed concern about the possible computational complexity of
using an iterated bootstrap to produce confidence intervals. This is much less
of an issue than it appears, because many of the matrix calculations can be
computed once and then reused in the bootstrap replications. (Any calculation
that does not involve $Y$ can be reused.) Each bootstrap replication only
requires a small number of matrix-vector multiplications which can be completed
very quickly. We have added a short section after Algorithm 2 that explains
this implementation detail, and we have also provided open source R code that
implements the procedure efficiently.

Finally, the mathematical appendix defines more notation explicitly and
summarizes several convergence results from Calonico, Cattaneo, and Titiunik
(2014) that are referenced in the proofs and we have made some small additional
changes that the referees suggested.

The replies to the referees give more details on some of the specific
changes made to the paper. Thank you for giving us the opportunity to revise
the paper.

\noindent%
Best,

\noindent%
Ot\'avio Bartalotti, Gray Calhoun, and Yang He

\end{document}

### 2016-08-11 Reply_Referee1.tex
Spellcheck letters

@@
 heteroskedastcity as long as the conditional variance is assumed to be smooth in
-a neighorbood around the cutoff point, since the residual bootstrap we initially
+a neighborhood around the cutoff point, since the residual bootstrap we initially
 proposed only resampled from that neighborhood, but we agree that in practice
-the wild bootstrap is likely to be more accurate and can accomodate forms of
+the wild bootstrap is likely to be more accurate and can accommodate forms of
 conditional heteroskedasticity that the residual bootstrap can not.

### 2016-08-11 main_paper.tex
Spellcheck main paper

@@
 first-order asymptotic properties of the bootstrap distribution but can provide
-improvements in finite samples analagous to alternative
+improvements in finite samples analogous to alternative
 heteroskedasticity-robust variance estimators. (\citealp{mackinnon1985some}, and
@@
 In Panel A, all of the intervals from both robust estimators are reasonably close to their nominal coverage, although
-our proposed bootstrap procedure has coverages about one percentage lower than the CCT's analytical counterpart.
-In Panel B, the coverages are very similar to those in Panel A, showing that both procedures are robust to heteroskedasticity.
+our proposed bootstrap procedure has coverage about one percentage lower than the CCT's analytical counterpart.
+In Panel B, the coverage is very similar to Panel A, showing that both procedures are robust to heteroskedasticity.
 The final column, ``CI Length,'' indicates that our proposed bootstrap procedure consistently generates narrower intervals, in line with the coverage results.

### 2016-08-11 main_paper.tex

@@
 X_{i}           &\sim  2 \times \betarv(2,4) - 1 \\
-\varepsilon_{i} &\sim N(0, \sigma_i^2) \\
+\varepsilon_{i} &\sim N(0, 0.1295^2 \times \sigma_i^2) \\
 \sigma_i &= z(\gamma) \mu_{j}(X_{i})^\gamma ,
 \end{align*}
-where $j$ will index the specific DGP. This is the experimental design used by
-\citet{IK} and CCT, which we adopt here with adaptation to make our simulation results directly
-comparable with theirs and with the rest of the literature.
-While they use this experimental design with homoskedastic errors, we introduce heteroskedasticity following the design in \cite{mackinnon2013thirty}.
-We control the degree of heteroskedasticity through the parameter $\gamma$ and a function $z(\gamma)$.
-When $\gamma = 0$, we set $z(\gamma) = 0.1295$ such that our DGP is exactly the same as \citet{IK} and CCT.
-When $\gamma > 0$, we set the value of $z(\gamma)$ such that the average $\sigma_i$ for those units actually used ($-\max[h, b] \le X_i \le \max[h, b]$) in our estimation procedure is 0.1295.\footnote{In practice, the optimal $h$ and $b$ are usually data driven, so $h$, $b$ and $\sigma_i$ are simultaneously determined.
-For simplicity, we use the following steps to find $z(\gamma)$: (1) generate homoskedastic data and obtain $\max[h, b]$ using CCT's optimal bandwidth selector, (2) repeat (1) for 500 times and obtain the average $\overline{\max[h, b]}$ and (3) define $z(\gamma) = \frac{0.1295}{ \sum_{\lvert X_i \rvert \le \overline{\max[h, b]}} \mu_{j}(X_{i})^\gamma}$.} We will use $\gamma = 2$ and the same three functional forms for $\mu_{j}$ as CCT.
+where $j$ indexes the specific DGP and $z(\gamma)$ is a scale parameter that
+ensures that the average standard deviation in a neighborhood aroundt the cutoff
+equals the unconditional value under homoskedasticity; i.e. $z(\gamma)$
+satisfies
+\[
+  z(\gamma)
+    = \frac{1}{\sum_{i = 1}^n \mu_{j}(X_{i})^{\gamma}
+    \frac{\1\{\min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h,\bar b)\}}
+    {\#\{X_i : \min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h, \bar b)\}}};
+\]
+for $\gamma = 0$ we have $z(\gamma) = 1$ and the errors are
+homoskedastic.\footnote{%
+  The values $\bar h$ and $\bar b$ are taken as the average values over 500
+  homoskedastic simulations of the bandwidths returned by CCT's optimal
+  bandwidth selector. This ensures that the relevant variance around the cutoff
+  is approximately the same for the heteroskedastic and homoskedastic DGPs.} %
+This is the experimental design used by \citet{IK} and CCT for homoskedastic
+simulations, which we adopt here to make our simulation results directly
+comparable with theirs and with the rest of the literature.  The form of
+heteroskedasticity is motivated by \cite{mackinnon2013thirty}, and we consider
+$gamma$ equal to 0 and 2 for the simulations.
+We use the same three functional forms for $\mu_{j}$ as CCT.
 

### 2016-08-11 main_paper.tex

@@
 are chosen using the AMSE-optimal rule proposed by CCT and the Wild bootstrap
-uses the ``HC3'' transformation of \citet{DF08}. We also estimate CCT's bias
-corrected procedure with AMSE-optimal bandwidths and
-the uniform kernel for direct comparison.
+uses the ``HC3'' transformation of \citet{DF08}.
+
+We include two other procedures for comparison: CCT's bias-corrected interval
+and a ``naive'' uncorrected estimator, both using the triangular kernel. We
+estimate CCT's bias corrected procedure with AMSE-optimal bandwidth and estimate
+the ``naive'' uncorrected interval with the optimal bandwidth $h$ proposed by
+\cite{IK}, and both use the HC3 variance estimator to facilitate comparisons
+with the Wild bootstrap.\footnote{%
+  Simulation results for other kernels and variance estimators are similar and
+  available upon request.} %
 
@@
 Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
-``Wild bootstrap'' shows results for our proposed bootstrap interval and ``CCT'' shows
-results for the analytically-corrected interval. The first three columns give the bias,
+``Wild bootstrap'' shows results for our proposed bootstrap interval; ``CCT'' shows
+results for the analytically-corrected interval and ``Naive'' shows results for analytically-uncorrected interval. The first three columns give the bias,
 standard deviation, and Root-MSE of the point
@@
 
-The column ``CI Coverage'' lists the experimental coverage of each interval.
-In Panel A, all of the intervals from both robust estimators are reasonably close to their nominal coverage, although
-our proposed bootstrap procedure has coverage about one percentage lower than the CCT's analytical counterpart.
-In Panel B, the coverage is very similar to Panel A, showing that both procedures are robust to heteroskedasticity.
-The final column, ``CI Length,'' indicates that our proposed bootstrap procedure consistently generates narrower intervals, in line with the coverage results.
+The column ``CI Coverage'' lists the experimental coverage of each interval.  In
+Panel A, all of the intervals from two robust estimators are reasonably close to
+their nominal coverage, although they slightly under cover the true treatment
+effect. The uncorrected intervals perform substantially worse---the naive
+analytical interval has coverage as bad as 35\% (in the second DGP) and never
+higher than 86\%. In Panel B, the coverage does not change too much from Panel
+A. In presence of heteroskedasticity, the two robust procedures again perform
+similarly and have coverage close to the nominal level. The final column, ``CI
+Length,'' indicates that intervals from the two robust procedures have almost
+the same length on average, while interval from the naive procedure has much
+shorter length on average. Not surprisingly, the average length of intervals
+from all three procedures increases when the data is heteroskedastic.
 

### 2016-08-11 R/rdfunctions.R
Fix errors in DGP
1. the homoskedastic DGP had variance 0.1295, now 0.1295^2.
2. the heteroskedastic DGP fixed the average standard deviation at
0.1295, now fix the average variance at 0.1295^2.

@@ -5,7 +5,7 @@ kweight <- rdrobust:::rdrobust_kweight
 
 generate.data <- function(model.id) {
   x <- 2*rbeta(500, 2, 4) - 1
-  e <- rnorm(500, 0, 0.1295)
+  e <- rnorm(500, 0, 0.1295^2)
   y <- e + switch(model.id,
     ifelse(x < 0, 0.48 +  1.27*x +  7.18*x^2 + 20.21*x^3 + 21.54*x^4 + 7.33*x^5,
                   0.52 +  0.84*x -  3.00*x^2 +  7.99*x^3 -  9.01*x^4 + 3.56*x^5),
@@ -38,8 +38,9 @@ generate.data.h <- function(model.id, avebw) {
                      0.26 + 18.49*x - 54.81*x^2 + 74.30*x^3 - 45.02*x^4 + 9.83*x^5),
               ifelse(x < 0, 0.48 +  1.27*x - 0.5*7.18*x^2 + 0.7*20.21*x^3 + 1.1*21.54*x^4 + 1.5*7.33*x^5,
                      0.52 +  0.84*x - 0.1*3.00*x^2 - 0.3*7.99*x^3 - 0.1*9.01*x^4 + 3.56*x^5))
-  se <- y^2/mean(y[abs(x) < avebw]^2)*0.1295
-  return(data.frame(y = y + rnorm(500, 0, se), x = x))
+  v <- y^4
+  newv <- v/mean(v[abs(x) < avebw])*0.1295^2
+  return(data.frame(y = y + rnorm(500, 0, newv), x = x))
 }
 
 # Functions that implement the residual and wild bootstraps.

### 2016-08-11 R/simulation.R
Drop HC3 in the two analytical procedures
The naive uncorrected procedure and CCT robust procedure used HC3
plugged in variance, now change back to the default option: nearest
neighbor variance estimator.

@@ -86,7 +86,7 @@ simulation.2 <- function(model.id, kernel, heteroskedasticity = F) {
     dta <- gen_data()
     bws <- rdbwselect_2014(dta$y, dta$x, kernel = kernel)$bws
     results <- rdrobust(dta$y, dta$x, kernel = kernel,
-                        h = bws[1], b = bws[2], level = 100 * (1-a), vce = "hc3")
+                        h = bws[1], b = bws[2], level = 100 * (1-a))
     t <- results$coef[3]
     ci <- results$ci[3, ]
     return(c(t, ci))
@@ -158,7 +158,7 @@ simulation.4 <- function(model.id, kernel, heteroskedasticity = F) {
     dta <- gen_data()
     bws <- rdbwselect_2014(dta$y, dta$x, kernel=kernel, bwselect = "IK")$bws[1]
     results <- rdrobust(dta$y, dta$x, kernel = kernel,
-                        h = bws, b = bws, level = 100 * (1-a), vce = "hc3")
+                        h = bws, b = bws, level = 100 * (1-a))
     t <- results$coef[1]
     ci <- results$ci[1, ]
     return(c(t, ci))

### 2016-08-11 R/rdfunctions.R
Revert "Fix errors in DGP"
This reverts commit 61adf077f9a37595092fe1ea0a528532da2c4e84.

@@ -5,7 +5,7 @@ kweight <- rdrobust:::rdrobust_kweight
 
 generate.data <- function(model.id) {
   x <- 2*rbeta(500, 2, 4) - 1
-  e <- rnorm(500, 0, 0.1295^2)
+  e <- rnorm(500, 0, 0.1295)
   y <- e + switch(model.id,
     ifelse(x < 0, 0.48 +  1.27*x +  7.18*x^2 + 20.21*x^3 + 21.54*x^4 + 7.33*x^5,
                   0.52 +  0.84*x -  3.00*x^2 +  7.99*x^3 -  9.01*x^4 + 3.56*x^5),
@@ -38,9 +38,8 @@ generate.data.h <- function(model.id, avebw) {
                      0.26 + 18.49*x - 54.81*x^2 + 74.30*x^3 - 45.02*x^4 + 9.83*x^5),
               ifelse(x < 0, 0.48 +  1.27*x - 0.5*7.18*x^2 + 0.7*20.21*x^3 + 1.1*21.54*x^4 + 1.5*7.33*x^5,
                      0.52 +  0.84*x - 0.1*3.00*x^2 - 0.3*7.99*x^3 - 0.1*9.01*x^4 + 3.56*x^5))
-  v <- y^4
-  newv <- v/mean(v[abs(x) < avebw])*0.1295^2
-  return(data.frame(y = y + rnorm(500, 0, newv), x = x))
+  se <- y^2/mean(y[abs(x) < avebw]^2)*0.1295
+  return(data.frame(y = y + rnorm(500, 0, se), x = x))
 }
 
 # Functions that implement the residual and wild bootstraps.

### 2016-08-11 R/rdfunctions.R
Fix the heteroskedastic DGP
we initially kept the average standard deviation at 0.1295. Now we keep
the average variance at 0.1295^2.

@@ -38,8 +38,9 @@ generate.data.h <- function(model.id, avebw) {
                      0.26 + 18.49*x - 54.81*x^2 + 74.30*x^3 - 45.02*x^4 + 9.83*x^5),
               ifelse(x < 0, 0.48 +  1.27*x - 0.5*7.18*x^2 + 0.7*20.21*x^3 + 1.1*21.54*x^4 + 1.5*7.33*x^5,
                      0.52 +  0.84*x - 0.1*3.00*x^2 - 0.3*7.99*x^3 - 0.1*9.01*x^4 + 3.56*x^5))
-  se <- y^2/mean(y[abs(x) < avebw]^2)*0.1295
-  return(data.frame(y = y + rnorm(500, 0, se), x = x))
+  V <- y^4
+  newV <- V/mean(V[abs(x) < avebw])*0.1295^2
+  return(data.frame(y = y + rnorm(500, 0, sqrt(newV)), x = x))
 }
 
 # Functions that implement the residual and wild bootstraps.

### 2016-08-12 main_paper.tex
update the simulation table
1. fix the DGP of heteroskedastic data (now keep the average variance at
0.1295^2, not keep the average standard deviation at 0.1295).
2. use default variance estimator (nearest neighbours) in the two
analytical procedures.

@@
     1 & Wild bootstrap & --0.011 & 0.067 & 0.068 & 0.926 & 0.247 \\ 
-      & CCT            & --0.011 & 0.067 & 0.068 & 0.928 & 0.247 \\ 
-      & Naive          & --0.037 & 0.041 & 0.055 & 0.835 & 0.155 \\ 
+      & CCT            & --0.011 & 0.067 & 0.068 & 0.914 & 0.239 \\ 
+      & Naive          & --0.037 & 0.041 & 0.055 & 0.823 & 0.152 \\ 
     2 & Wild bootstrap & --0.008 & 0.086 & 0.086 & 0.938 & 0.334 \\ 
-      & CCT            & --0.008 & 0.086 & 0.086 & 0.942 & 0.346 \\
-      & Naive          & --0.145 & 0.065 & 0.159 & 0.353 & 0.241 \\
+      & CCT            & --0.008 & 0.086 & 0.086 & 0.932 & 0.346 \\ 
+      & Naive          & --0.145 & 0.065 & 0.159 & 0.311 & 0.224 \\ 
     3 & Wild bootstrap & --0.005 & 0.065 & 0.065 & 0.945 & 0.252 \\ 
-      & CCT            & --0.005 & 0.065 & 0.065 & 0.945 & 0.253 \\ 
-      & Naive          &   0.034 & 0.051 & 0.061 & 0.862 & 0.191 \\ \\
+      & CCT            & --0.005 & 0.065 & 0.065 & 0.934 & 0.244 \\ 
+      & Naive          &   0.034 & 0.051 & 0.061 & 0.851 & 0.185 \\  \\
     \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
     \midrule
-    1 & Wild bootstrap & --0.010 & 0.080 & 0.081 & 0.934 & 0.301 \\
-      & CCT            & --0.010 & 0.080 & 0.081 & 0.936 & 0.301 \\
-      & Naive          & --0.035 & 0.050 & 0.061 & 0.863 & 0.185 \\ 
-    2 & Wild bootstrap & --0.008 & 0.094 & 0.095 & 0.921 & 0.351 \\ 
-      & CCT            & --0.008 & 0.094 & 0.095 & 0.924 & 0.366 \\
-      & Naive          & --0.145 & 0.072 & 0.162 & 0.398 & 0.255 \\  
-    3 & Wild bootstrap & --0.001 & 0.103 & 0.103 & 0.942 & 0.396 \\ 
-      & CCT            & --0.001 & 0.103 & 0.103 & 0.942 & 0.395 \\ 
-      & Naive          &   0.036 & 0.073 & 0.081 & 0.859 & 0.251 \\  
+    1 & Wild bootstrap & --0.010 & 0.073 & 0.074 & 0.935 & 0.276 \\
+      & CCT            & --0.010 & 0.073 & 0.074 & 0.923 & 0.265 \\ 
+      & Naive          & --0.035 & 0.046 & 0.058 & 0.838 & 0.165 \\ 
+    2 & Wild bootstrap & --0.007 & 0.084 & 0.084 & 0.922 & 0.312 \\ 
+      & CCT            & --0.007 & 0.084 & 0.084 & 0.929 & 0.340 \\ 
+      & Naive          & --0.144 & 0.064 & 0.158 & 0.277 & 0.211 \\ 
+    3 & Wild bootstrap & --0.002 & 0.081 & 0.081 & 0.940 & 0.311 \\ 
+      & CCT            & --0.002 & 0.081 & 0.081 & 0.926 & 0.297 \\ 
+      & Naive          &   0.033 & 0.059 & 0.068 & 0.835 & 0.194 \\  
     \bottomrule

### 2016-08-12 main_paper.tex
Edit the description of heteroskedastic DGP
We want to keep the average \sigma^2 equal to 1.

@@
 where $j$ indexes the specific DGP and $z(\gamma)$ is a scale parameter that
-ensures that the average standard deviation in a neighborhood aroundt the cutoff
+ensures that the average variance in a neighborhood around the cutoff
 equals the unconditional value under homoskedasticity; i.e. $z(\gamma)$
@@
 \[
-  z(\gamma)
-    = \frac{1}{\sum_{i = 1}^n \mu_{j}(X_{i})^{\gamma}
+  z(\gamma)^2
+    = \frac{1}{\sum_{i = 1}^n \mu_{j}(X_{i})^{2 \gamma}
     \frac{\1\{\min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h,\bar b)\}}
@@
 heteroskedasticity is motivated by \cite{mackinnon2013thirty}, and we consider
-$gamma$ equal to 0 and 2 for the simulations.
+$\gamma$ equal to 0 and 2 for the simulations.
 We use the same three functional forms for $\mu_{j}$ as CCT.

### 2016-08-12 main_paper.tex
Update the text in simulation section
It is updated because:
1. the heteroskedastic DGP is changed.
2. the option for variance estimator in analytical procedures is
changed.

@@
 We include two other procedures for comparison: CCT's bias-corrected interval
-and a ``naive'' uncorrected estimator, both using the triangular kernel. We
+and a ``naive'' uncorrected estimator. We
 estimate CCT's bias corrected procedure with AMSE-optimal bandwidth and estimate
 the ``naive'' uncorrected interval with the optimal bandwidth $h$ proposed by
-\cite{IK}, and both use the HC3 variance estimator to facilitate comparisons
-with the Wild bootstrap.\footnote{%
+\cite{IK}. We use triangular kernel through out all the three procedures to facilitate direct comparisons.\footnote{%
 Simulation results for other kernels and variance estimators are similar and
@@
 The column ``CI Coverage'' lists the experimental coverage of each interval.  In
-Panel A, all of the intervals from two robust estimators are reasonably close to
+Panel A, all the intervals from two robust estimators are reasonably close to
 their nominal coverage, although they slightly under cover the true treatment
-effect. The uncorrected intervals perform substantially worse---the naive
-analytical interval has coverage as bad as 35\% (in the second DGP) and never
+effect.
+Our proposed bootstrap procedure consistently performs well, as it is about a percentage point closer to nominal coverage than the analytically-corrected interval.
+The uncorrected interval performs substantially worse---the naive
+analytical interval has coverage as bad as 31\% (in the second DGP) and never
 higher than 86\%. In Panel B, the coverage does not change too much from Panel
-A. In presence of heteroskedasticity, the two robust procedures again perform
+A. It slightly increases in DGP 1 and decreases in DGP 2 and 3 for all three procedures. In presence of heteroskedasticity, the two robust procedures again perform
 similarly and have coverage close to the nominal level. The final column, ``CI
-Length,'' indicates that intervals from the two robust procedures have almost
-the same length on average, while interval from the naive procedure has much
+Length,'' indicates that intervals from the two robust procedures have average lengths close to each other, while interval from the naive procedure has much
 shorter length on average. Not surprisingly, the average length of intervals

### 2016-08-12 Reply_Referee2.tex
Tighten and tweak replies in responses to the referees

@@
 that change.
+
+The first referee expressed concern about the possible computational complexity of
+using an iterated bootstrap to produce confidence intervals. This is much less
+of an issue than it appears, because many of the matrix calculations can be
+computed once and then reused in the bootstrap replications. (Any calculation
+that does not involve $Y$ can be reused.) Each bootstrap replication only
+requires a small number of matrix-vector multiplications which can be completed
+very quickly. We have added a short section after Algorithm 2 that explains
+this implementation detail, and we have also provided open source R code that
+implements the procedure efficiently.
 
@@
 
-  Thank you for this suggestion; we have added some additional simulations with conditional heteroskedasticity.
+  Thank you for this suggestion; we have added additional simulations with conditional heteroskedasticity.
 
@@
 
-Please see the discussion to about the relationship between $h$ and $b$ in previous comments number 4.
+Thanks for pointing this out. It is no longer redundant since we have relaxed
+the requirement that $h < b$.
 
@@
 
-Thank you very much for pointing out instances in the proofs that might require checking and clarifications.
-In the new proofs we have added some additional details.
-Since the proof for theorem 2 changed substantially with the adoption of the Wild Bootstrap scheme (which addresses the heteroskedasticity issue, as discussed before) we made substantial changes that hopefully will make the proof's steps clearer to the reader.
+Thank you for pointing this out. We have added much more exposition to the
+Mathematical Appendix.
 

### 2016-08-12 Reply_Referee2.tex
Add 'answer' to referee 2's claim that there is no bootstrap uncertainty in the bias estimate

@@
 
+We're not sure that we understand this comment---there is definitely bootstrap
+uncertainty in the estimated bias in our procedure because we estimate the
+bias with a preliminary bootstrap. We ignore this uncertainty in the theoretical
+results (which is consistent with the bootstrap literature) but it will be
+present in applications.
+
 \item \textit{``In Algorithm 2.1, it should be ``$\hat{g}_{-}$ and $\hat{g}_{+}$''.''}

### 2016-08-12 main_paper.tex
Make 'Wild bootstrap' lowercase everywhere
We were inconsistent. It's all lowercase now

@@
 the bias. The bandwidths, $h$ and $b$,
-are chosen using the AMSE-optimal rule proposed by CCT and the Wild bootstrap
+are chosen using the AMSE-optimal rule proposed by CCT and the wild bootstrap
 uses the ``HC3'' transformation of \citet{DF08}.
@@
 Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
-``Wild bootstrap'' shows results for our proposed bootstrap interval; ``CCT'' shows
+``wild bootstrap'' shows results for our proposed bootstrap interval; ``CCT'' shows
 results for the analytically-corrected interval and ``Naive'' shows results for analytically-uncorrected interval. The first three columns give the bias,
@@
 procedure introduced in this paper.  Our bootstrap estimator uses the
-AMSE-optimal bandwidths proposed by CCT, the uniform kernel, and the HC3 Wild
+AMSE-optimal bandwidths proposed by CCT, the uniform kernel, and the HC3 wild
 bootstrap from \citet{DF08}. In the bootstrap
@@
 
-Normality also follows standard arguments for the Wild
+Normality also follows standard arguments for the wild
 bootstrap. Conditional on the regressors and residuals,

### 2016-08-12 R/application.R
Change the CCT from HC3 to nearest neighbour variance estimator in application

@@ -33,7 +33,7 @@ original <- function(dta, bw) {
 
 robust <- function(dta) {
   bws <- rdbwselect_2014(dta$y, dta$x, kernel = "uni")$bws
-  cct <- rdrobust(dta$y, dta$x, kernel = "uni", h = bws[1], b = bws[2], vce = "hc3")
+  cct <- rdrobust(dta$y, dta$x, kernel = "uni", h = bws[1], b = bws[2])
   t1  <- cct$coef[3]
   ci1 <- cct$ci[3, ]
 

### 2016-08-12 main_paper.tex
Make small changes to wording in introduction

@@
 and the resulting confidence intervals are shown to be asymptotically valid in
-Theorem~\ref{T2}.
+Theorem~\ref{T2}.\footnote{%
+  Since our bootstrap resamples the residuals but not the running variable, many
+  of the quantities used to prodcue the estimates do not change under the
+  bootstrap distribution and can be reused from the original
+  estimate. Exploiting this feature makes the iterated bootstrap much less
+  computationally burdensome; see the discussion following
+  Algoritnm~\ref{Alg2}.} %
 
@@
 demonstrates that the analytical correction proposed by CCT can also be
-implemented through a new bootstrap procedure. We believe that this procedure is
-promising because it can allow applied researchers to construct
-accurate confidence intervals in settings where unusual forms of dependence
-would make it difficult to derive CCT's analytical correction---the dependence
+implemented through a new bootstrap procedure.  This procedure is promising
+because it, like other bootstrap methods, can allow applied researchers to
+construct accurate confidence intervals in settings where correct formulas for
+the asymptotic variance have not yet been derived, as can be the case when there
+is an unusual form of dependence---the dependence
 can be accommodated in principle by modifying the resampling algorithm to one
 that matches the dependence in the dataset. The specific version of the bootstrap
-presented in this paper, however, does not achieve that level of generality yet,
+presented in this paper, however, does not achieve that level of generality,
 and one limitation should be noted in particular. The confidence

### 2016-08-12 main_paper.tex
update the CCT confidence intervals in application
Swicth from HC3 to NN variance estimator. The changes to CIs are very
small, no edit in the text needed.

--- 2016-08-12 main_paper.tex
@@
     LM (2007)         & --1.114 & (--2.138                    & --0.090) & 36  &      &       & 0.027 \\
-    CCT               & --3.795 & (--6.885                    & --0.706) & 3   & .888 & 6.807 &       \\ 
+    CCT               & --3.795 & (--7.040                    & --0.551) & 3   & .888 & 6.807 &       \\ 
     Wild bootstrap    & --3.800 & (--6.781                    & --0.408) & 3   & .888 & 6.807 &       \\
@@
     LM (2007)      & 0.030 & (0.003                      & 0.057) & 7&     &  & 0.032    \\
-    CCT            & 0.055 & (0.013                      & 0.097) & 3&.671 & 8.618       \\
+    CCT            & 0.055 & (0.014                      & 0.096) & 3&.671 & 8.618       \\
     Wild bootstrap & 0.055 & (0.010                      & 0.097) & 3&.671 & 8.618       \\\\
@@
     LM (2007)      & 0.037 & (0.002                      & 0.073) & 7&     &  & 0.032 \T \\
-    CCT            & 0.051 & (0.006                      & 0.096) & 5&.076 & 10.251      \\
+    CCT            & 0.051 & (0.004                      & 0.099) & 5&.076 & 10.251      \\
     Wild bootstrap & 0.052 & (0.006                      & 0.092) & 5&.076 & 10.251      \\

### 2016-08-12 Reply_Referee1.tex

@@
   been developed; for example, analytical expressions for the standard errors
-  with clustered observations have been only recently available, but would be
-  relatively straightforward to calculate with a bootstrap.  We do not claim to
-  achieve this level of generality in this paper but we hope it will serve as a
+  with clustered observations have been only recently available despite heavy
+  demand and interest from applied researchers, but would be relatively
+  straightforward to calculate with a bootstrap.  We do not claim to achieve
+  this level of generality in this paper but we expect that it will serve as a
   stepping stone for these developments.
@@
 
-See discussion on item number 2 in the main comments section above.
+See discussion on item number 2 in the main comments section above. The
+iterations are less computationally demanding than they appear.
 
@@
 
-Thank you very much for pointing out instances in the proofs that might require checking and clarifications.
- In the new proofs we have added details to the statement ``the bootstrap ensures that'', previously on page 19.
+Thank you for calling our attention to these issues.
+ In the new proofs we have added details to the statement ``the bootstrap ensures that,'' previously on page 19.
  Since the proof for theorem 2 changed substantially with the adoption of the Wild Bootstrap scheme

### 2016-08-12 main_paper.tex
Make small changes to theoretical section of the paper
- Tweak Algorithm 2 so that we don't explicitly use tau^{bc} notation
- Add equation numbers for V(h) and C(h,b) and add them as references
  in Theorem 1.

@@
 \end{equation}
-where $\Delta^*(h,b)$ is defined by Equation~\eqref{eq:9}.
+where $\Delta^*(h,b)$ is defined by Equation~\eqref{eq:9} and
+$V^{bc}(h, b) = V(h) + C(h, b)$, both which are defined in Equations~\eqref{eq:8}
+and~\eqref{eq:13} of the Mathematical Appendix.
 \end{theorem}
@@
 
-\begin{algorithm}[Confidence intervals]\label{Alg2}
+\begin{algorithm}[Distribution]\label{Alg2}
   Assume $h$ and $b$ are bandwidths as defined by Assumption~\ref{A2} and
@@
     and the residuals $\hat\varepsilon_i$ just as in Algorithm~\ref{Alg1}.
-  \item Repeat the following steps $B_{2}$ times to produce the
-    bootstrap estimates
-    $\hat\tau_1^{bc*}(h,b), \dots, \hat\tau_{B_{2}}^{bc*}(h,b)$. For the
+  \item Repeat the following steps $B_{2}$ times to produce
+    bootstrap estimates of the bias-corrected estimate. For the
     $k$th replication:
@@
 The matrix $\mathbf{W}_{+,1}$ is not affected by the bootstrap so it can be
-computed once initially and reused in the bootstrap calculations and each
+computed once initially and reused in the bootstrap calculations. Then each
 bootstrap replication just requires a single matrix-vector multiplication. The
@@
 For reference, define the variance terms
-\begin{equation*}
+\begin{equation}\label{eq:8}
   V(h)
@@
   + \Gamma_{+,1}(h)^{-1} \Psi_{+,1,1}(h,h) \Gamma_{+,1}(h)^{-1} \big) e_0
-\end{equation*}
+\end{equation}
 and
-\begin{multline*}
+\begin{multline}\label{eq:13}
   C(h,b) =
@@
     \Big] e_2.
-\end{multline*}
+\end{multline}
 See CCT for more on the motivation and derivation of these formulas.

### 2016-08-12 main_paper.tex
First batch of tweaks for section on simulations.

@@
 procedures proposed in Section~\ref{boot} produce valid, robust confidence
-intervals similar to those obtained by the analytical procedures established
-in CCT. The bootstrap CIs obtained are comparable to the analytical
-alternative, albeit with slightly lower coverage and shorter
-length of the intervals in the specifications implemented. We also find that
-all of the bias corrected methods can offer substantial improvements over
-estimators that do not bias correct.
-
-The Monte Carlo experiments have a similar structure. For all of them, we
-generate 500 i.i.d.\ observations from the DGP
+intervals (CIs) similar to those obtained by the analytical procedures established in CCT. 
+The CIs obtained are comparable to the analytical alternative, and in many cases provide
+ coverage closer to the nominal size of the tests in the specifications implemented.
+ We also observe that all of the bias corrected methods can offer substantial improvements over estimators that do not bias correct.
+
+The Monte Carlo experiments have a similar structure. For all of them, we generate 500 i.i.d.\ observations from the DGP
 \begin{align*}
@@
 comparable with theirs and with the rest of the literature.  The form of
-heteroskedasticity is motivated by \cite{mackinnon2013thirty}, and we consider
-$\gamma$ equal to 0 and 2 for the simulations.
+heteroskedasticity is motivated by \cite{mackinnon2013thirty}. Hence,
+ we consider both homoskedastic and heteroskedastic cases by setting $\gamma$ equal to 0 and 2 for the simulations, respectively.
 We use the same three functional forms for $\mu_{j}$ as CCT.
@@
 \nocite{ludwig2007}%
-The second DGP is based on Ludwig and Miller's (2007) analysis of the Head Start
-program. Funding eligibility is determined at the county level using the
-county's historical poverty rate, with a sharp threshold that determines the
-provision of services. We use the fifth order polynomial estimated on Ludwig and
-Miller's dataset as the conditional expectation for the second DGP:
+The second DGP is based on Ludwig and Miller's (2007) analysis of the Head Start program.
+As described in Section \ref{application}, eligibility to grant-writing assistance is determined
+ at the county level using the county's historical poverty rate, with a sharp threshold that
+ determines the provision of services. We use the fifth order polynomial estimated on Ludwig
+ and Miller's dataset as the conditional expectation for the second DGP:
 \begin{equation*}

### 2016-08-12 main_paper.tex
More tweaks

@@
 
-We include two other procedures for comparison: CCT's bias-corrected interval
-and a ``naive'' uncorrected estimator. We
-estimate CCT's bias corrected procedure with AMSE-optimal bandwidth and estimate
+We include two other procedures for comparison: CCT's bias-corrected interval and a ``naive'' uncorrected estimator.
+ We estimate CCT's bias corrected procedure with AMSE-optimal bandwidth and estimate
 the ``naive'' uncorrected interval with the optimal bandwidth $h$ proposed by
-\cite{IK}. We use triangular kernel through out all the three procedures to facilitate direct comparisons.\footnote{%
-Simulation results for other kernels and variance estimators are similar and
-available upon request.} %
+\cite{IK}. We use triangular kernel throughout all the three procedures to facilitate direct comparisons.\footnote{%
+Simulation results for other kernels and variance estimators produced similar outcomes.} %
 
@@
 Table~\ref{tbl:1} presents the results of these simulations. It consists of two panels, with results for homoskedastic data in Panel A and heteroskedastic data in Panel B. The row labeled
-``wild bootstrap'' shows results for our proposed bootstrap interval; ``CCT'' shows
+``Wild bootstrap'' shows results for our proposed bootstrap based interval; ``CCT'' shows
 results for the analytically-corrected interval and ``Naive'' shows results for analytically-uncorrected interval. The first three columns give the bias,
@@
 Panel A, all the intervals from two robust estimators are reasonably close to 
-their nominal coverage, although they slightly under cover the true treatment
-effect.
-Our proposed bootstrap procedure consistently performs well, as it is about a percentage point closer to nominal coverage than the analytically-corrected interval.
-The uncorrected interval performs substantially worse---the naive
+their nominal coverage, although they slightly under cover the true treatment effect.
+Our proposed bootstrap procedure consistently performs well, as it is about a percentage point 
+closer to nominal coverage than the analytically-corrected interval. The uncorrected interval performs substantially worse---the naive
 analytical interval has coverage as bad as 31\% (in the second DGP) and never

### 2016-08-12 main_paper.tex
Final Changes to Simulation Section.

@@
 
-The column ``CI Coverage'' lists the experimental coverage of each interval.  In 
-Panel A, all the intervals from two robust estimators are reasonably close to 
+The column ``CI Coverage'' lists the experimental coverage of each procedure.  In 
+Panel A, all the intervals produced by the two robust estimators are reasonably close to 
 their nominal coverage, although they slightly under cover the true treatment effect.
@@
 closer to nominal coverage than the analytically-corrected interval. The uncorrected interval performs substantially worse---the naive
-analytical interval has coverage as bad as 31\% (in the second DGP) and never
-higher than 86\%. In Panel B, the coverage does not change too much from Panel
-A. It slightly increases in DGP 1 and decreases in DGP 2 and 3 for all three procedures. In presence of heteroskedasticity, the two robust procedures again perform
-similarly and have coverage close to the nominal level. The final column, ``CI
-Length,'' indicates that intervals from the two robust procedures have average lengths close to each other, while interval from the naive procedure has much
-shorter length on average. Not surprisingly, the average length of intervals
-from all three procedures increases when the data is heteroskedastic.
+analytical interval has coverage as low as 31\% (in the second DGP) and never
+higher than 86\%.
+
+Panel B presents results for the heteroskedastic case. The coverages obtained are similar to those in Panel A and highlight 
+the robustness of the wild bootstrap procedure proposed to heteroskedasticity. The two robust procedures again perform
+similarly and have coverage close to the nominal level. The final column, ``CI Length,'' indicates that intervals from the
+ two robust procedures have average lengths close to each other, while interval from the naive procedure has much shorter length on average.
 
 These are DGPs where the naive confidence intervals are known to perform poorly, 
-and this set of simulation results indicates that our proposed bootstrap approach
-is quite competitive with analytical methods for producing valid intervals.
-Overall, the bootstrap bias-correction procedure proposed in this paper provides
-a simple alternative to obtain valid robust confidence intervals in RD designs
-and similarly well compared to the analytical bias correction procedures proposed
-by CCT.
+and this set of simulation results indicates that our proposed bootstrap approach is 
+quite competitive with analytical methods for producing robust intervals.
+Overall, the bootstrap bias-correction procedure proposed in this paper provides a simple alternative to obtain valid robust confidence intervals in RD designs
+and performs similarly well compared to the analytical bias correction procedures proposed by CCT.
 

### 2016-08-12 main_paper.tex
Tweak simulation text a bit more

@@
 intervals (CIs) similar to those obtained by the analytical procedures established in CCT. 
-The CIs obtained are comparable to the analytical alternative, and in many cases provide
- coverage closer to the nominal size of the tests in the specifications implemented.
  We also observe that all of the bias corrected methods can offer substantial improvements over estimators that do not bias correct.
@@
   z(\gamma)^2
-    = \frac{1}{\sum_{i = 1}^n \mu_{j}(X_{i})^{2 \gamma}
-    \frac{\1\{\min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h,\bar b)\}}
-    {\#\{X_i : \min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h, \bar b)\}}};
+    = \frac{    {\#\{X_i\ :\ \min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h, \bar b)\}}}
+  {\sum_{i = 1}^n \mu_{j}(X_{i})^{2 \gamma}
+  \1\{\min(-\bar h, -\bar b) \leq X_i \leq \max(\bar h,\bar b)\}}.
 \]
-for $\gamma = 0$ we have $z(\gamma) = 1$ and the errors are
+For $\gamma = 0$ we have $z(\gamma) = 1$ and the errors are
 homoskedastic.\footnote{%
@@
 comparable with theirs and with the rest of the literature.  The form of
-heteroskedasticity is motivated by \cite{mackinnon2013thirty}. Hence,
- we consider both homoskedastic and heteroskedastic cases by setting $\gamma$ equal to 0 and 2 for the simulations, respectively.
-We use the same three functional forms for $\mu_{j}$ as CCT.
+heteroskedasticity is motivated by \cite{mackinnon2013thirty}, and we consider
+$\gamma$ equal to 0 and 2 for the simulations.
+We use the same three functional forms for $\mu_{j}$ as CCT, which we describe below.
 
@@
 To estimate the finite-sample coverage of our new bootstrap based confidence interval, we
-simulate 5000 samples from each of the three DGPs ($\gamma = 0$ and $\gamma = 2$) and calculate nominal 95\%
+simulate 5000 samples from each of the three DGPs (with $\gamma = 0$ and $\gamma = 2$) and calculate nominal 95\%
 two-sided confidence intervals. We use 999 bootstrap replications ($B_2$) to

### 2016-08-12 main_paper.tex
Make more small changes to simulation text

@@
 ``Wild bootstrap'' shows results for our proposed bootstrap based interval; ``CCT'' shows
-results for the analytically-corrected interval and ``Naive'' shows results for analytically-uncorrected interval. The first three columns give the bias,
+results for the analytically-corrected interval and ``Naive'' shows results for
+the analytically-uncorrected interval. The first three columns give the bias,
 standard deviation, and Root-MSE of the point
@@
 Panel A, all the intervals produced by the two robust estimators are reasonably close to 
-their nominal coverage, although they slightly under cover the true treatment effect.
-Our proposed bootstrap procedure consistently performs well, as it is about a percentage point 
-closer to nominal coverage than the analytically-corrected interval. The uncorrected interval performs substantially worse---the naive
-analytical interval has coverage as low as 31\% (in the second DGP) and never
+their nominal coverage, although they slightly under-cover the true treatment effect.
+Our proposed bootstrap procedure consistently performs well and it is about a percentage point 
+closer to nominal coverage than the analytically-corrected interval. The uncorrected interval performs substantially worse, with coverage as low as 31\% (in the second DGP) and never
 higher than 86\%.
@@
 the robustness of the wild bootstrap procedure proposed to heteroskedasticity. The two robust procedures again perform
-similarly and have coverage close to the nominal level. The final column, ``CI Length,'' indicates that intervals from the
- two robust procedures have average lengths close to each other, while interval from the naive procedure has much shorter length on average.
-
-These are DGPs where the naive confidence intervals are known to perform poorly, 
+similarly and have coverage close to the nominal level. The bootstrap explicitly
+accounts for heterosedasticity in the DGP; CCT's procedure implicitly accomodates
+smooth heteroskedasticity by estimating the variance in a neighborhood around
+the cutoff.
+
+The final column, ``CI Length,'' indicates that intervals from the
+two robust procedures have average lengths close to each other in all of the DGPs,
+while interval from the naive procedure is much shorter on average.
+
+These are DGPs where the naive confidence intervals are known to perform poorly
 and this set of simulation results indicates that our proposed bootstrap approach is 
-quite competitive with analytical methods for producing robust intervals.
+competitive with analytical methods for producing robust intervals.
 Overall, the bootstrap bias-correction procedure proposed in this paper provides a simple alternative to obtain valid robust confidence intervals in RD designs

### 2016-08-12 main_paper.tex
Remove discussion of bias-corrected ATE point estimates from empirics
The bias-corrected point estimates are not inherently interesting: the uncorrected
estimates are. Consequently, this commit removes detailed discussion of the uncorrected
point estimates from the main text of the paper.

@@
 Results from the two robust procedures are similar to each other but greatly
-differ from the original estimates. The estimated ATEs are as high as --3.795
-from CCT and --3.800 from the bootstrap. Both are significantly different from
-zero, though the confidence intervals are also very wide, which is likely to be
+differ from the original estimates. Both ATE estimates are significantly different from
+zero and indicate a reduction in mortality, although the confidence intervals are
+also very wide, which is likely to be
 due to the much smaller bandwidths used relative to the other estimators
-($h=3.888$, $b=6.807$).
+($h=3.888$, $b=6.807$). The ATE estimate reported are the bias-corrected
+point estimates, and their value indicates that the naive estimates are
+subject to substantial bias.
 
@@
 
-The two robust procedures are again very similar to each other and give slightly
-larger point estimates in both panels. In Panel A, the ATE increases from 0.030
-to 0.055 (CCT and bootstrap). In Panel B, the ATE increases from 0.037
-to 0.051 (CCT) and 0.052 (bootstrap). The confidence intervals tend to shift up
-as well.  In contrast to the striking differences between the conventional
+The two robust procedures are again very similar to each other and give
+statistically significant, positve, estimates. The confidence intervals tend to shift
+relative to the original intervals, increasing both the range of effects consistent
+with the data as well as the lower bound on plausible effects.
+In contrast to the striking differences between the conventional
 and bias-corrected procedures for the mortality estimates, the differences

### 2016-08-12 main_paper.tex
Fix grammar error in paper
Make small tweaks to wording around notation

@@
 \end{assumption}
-To simplify notation, let $m = \min(h,b)$, $m' = \max(h,b)$, and
-define the scaled and truncated kernel functions
+To simplify notation, define the scaled and truncated kernel functions
 \begin{align*}
@@
 procedure, we use 500 bootstraps for bias correction and 999 to calculate the
-confidence intervals. The analytical estimator using CCT's bias correction and variance estimator use
+confidence intervals. The analytical estimator using CCT's bias correction and
+variance estimator uses
 their AMSE-optimal bandwidths as well.
@@
 Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
-everywhere else. Much of the theory in this appendix applies to both
+everywhere else and assume, with some abuse of notation, that the
+dimension of $e_p$ adapts to make matrix and vector operations
+conformable. Much of the theory in this appendix applies to both
 sides of the cutoff symmetrically, so we will use a ``$\bullet$'' as a
@@
 \end{align*}
+with $m = \min(h,b)$.
 Remember that $f$ is the pdf of the running variable. Lemmas
@@
   \Bft_{\bullet}(h) &= \Bf_{\bullet} + o_p(1) \label{eq:11} \\
-  \max(h,b) \times \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
+  \tfrac{hb}{m} \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
   \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
@@
 
-For reference, define the variance terms
+Finally, define the variance components
 \begin{equation}\label{eq:8}
@@
 Given this expression for the iterated bootstrap and the formula for the
-variance conditional on $X$ presented at the end of the introduction to this
+variance conditional on $X$ presented at the end of the introduction to the
 appendix, it suffices to show that

### 2016-08-12 main_paper.tex
Fix small errors in scale factors
This commit fixes a few issues in the proof of Theorem 2 related to
rescaling by h or b. It also fixes an error in the definition of the
variance for the bias-corrected estimator.

@@
 \end{assumption}
-To simplify notation, define the scaled and truncated kernel functions
+To simplify notation, let $m = \min(h,b)$ and
+define the scaled and truncated kernel functions
 \begin{align*}
@@
     \sup_{x,\tau}
-    \Big\rvert \Pr^*\big[ \sqrt{nh}
+    \Big\rvert \Pr^*\big[ \sqrt{nm}
     (\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^*) \leq x \big]
-    - \Pr\big[ \sqrt{nh}
+    - \Pr\big[ \sqrt{nm}
     (\hat\tau(h) - \Delta^*(h,b) - \tau) \leq x \big] \Big\lvert \to^p 0.
@@
 \end{align*}
-with $m = \min(h,b)$.
 Remember that $f$ is the pdf of the running variable. Lemmas
@@
   C(h,b) =
-  \tfrac{1}{n} \, e_2' \big[
+  \tfrac{h^4}{n b^4} \, e_2' \big[
     \Gamma_{+,2}(b)^{-1} \Psi_{+,2,2}(b,b) \Gamma_{+,2}(b)^{-1} \Bf_+(h)^2 +
@@
   \begin{cases}
-    r_2(X_i/b)'H_2(b) \beta_{+,2}^* + \varepsilon_i^* & X_i \geq 0 \\
-    r_2(X_i/b)'H_2(b) \beta_{-,2}^* + \varepsilon_i^* & X_i < 0
+    r_2(X_i/b)'H_2(b)^{-1} \beta_{+,2}^* + \varepsilon_i^* & X_i \geq 0 \\
+    r_2(X_i/b)'H_2(b)^{-1} \beta_{-,2}^* + \varepsilon_i^* & X_i < 0
   \end{cases}
@@
   \sum_{i=1}^n r_1(X_i/h) K_{-,h}(X_i) \varepsilon_i^*\Big) \\
-  &\quad + h^2 e_2' \Gamma_{-,2}(b)^{-1}
+  &\quad + (h/b)^2 \cdot e_2' \Gamma_{-,2}(b)^{-1}
     \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{-,b}(X_i) \varepsilon_i^* \Big) \Bf_-(h) \\
-  &\quad - h^2 e_2' \Gamma_{+,2}(b)^{-1}
-    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{+,b}(X_i) \varepsilon_i^*\Big) \Bf_+(h).
-\end{align*}
+  &\quad - (h/b)^2 \cdot e_2' \Gamma_{+,2}(b)^{-1}
+    \Big(\tfrac{1}{n} \sum_{i=1}^n r_2(X_i/b) K_{+,b}(X_i) \varepsilon_i^*\Big) \Bf_+(h)
+\end{align*}
+with the last equality holding from the relationship between the coefficient
+estimates discussed at the end of the introduction to the appendix.
 We will prove convergence of the variance first, then prove asymptotic
@@
   \tfrac{1}{n} \sum_{i=1}^n r_1(X_i/h) r_2(X_i/b)' K_{\bullet,h}(X_i)
-  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{1}{b^2} \Psit_{\bullet,1,2}(h,b)
-  + o_p(\tfrac{1}{b^2})
+  K_{\bullet,b}(X_i) \hat\varepsilon_i^2 = \tfrac{m}{hb} \Psit_{\bullet,1,2}(h,b)
+  + o_p(\tfrac{m}{hb})
   \label{eq:5} \\
@@
 \begin{equation*}
-  R_\bullet(X_i) = \gamma_1 r_1(X_i/h) K_{\bullet,h}(X_i) + h^2 \gamma_2 r_2(X_i/b) K_{\bullet,b}(X_i)
+  R_\bullet(X_i) = \gamma_1' r_1(X_i/h) K_{\bullet,h}(X_i) +
+  (h/b)^2 \cdot \gamma_2' r_2(X_i/b) K_{\bullet,b}(X_i)
 \end{equation*}
@@
 \citep[See, for example,][Proposition 2.27 and Theorem 23.4.]{VDV00}
-But similar arguments to those used for the variance establish~\eqref{eq:17}
-and complete the proof. \qed
+But similar arguments to those used for the variance establish
+that
+\begin{equation}\label{eq:17}
+  \tfrac{1}{n} \sum_{i} m^{1+\delta} \lvert (R_+(X_i) - R_-(X_i))
+  \hat\varepsilon_i \rvert^{2+\delta}.
+\end{equation}
+obeys the LLN, implying that~\eqref{eq:17} holds and completing the proof. \qed
 

### 2016-08-12 main_paper.tex
Fix spelling and grammar errors

@@
   Since our bootstrap resamples the residuals but not the running variable, many
-  of the quantities used to prodcue the estimates do not change under the
+  of the quantities used to produce the estimates do not change under the
   bootstrap distribution and can be reused from the original
@@
   computationally burdensome; see the discussion following
-  Algoritnm~\ref{Alg2}.} %
+  Algorithm~\ref{Alg2}.} %
 
@@
 
-Panel B presents results for the heteroskedastic case. The coverages obtained are similar to those in Panel A and highlight 
+Panel B presents results for the heteroskedastic case. The coverage obtained is similar to that in Panel A and highlight
 the robustness of the wild bootstrap procedure proposed to heteroskedasticity. The two robust procedures again perform
 similarly and have coverage close to the nominal level. The bootstrap explicitly
-accounts for heterosedasticity in the DGP; CCT's procedure implicitly accomodates
+accounts for heterosedasticity in the DGP; CCT's procedure implicitly accommodates
 smooth heteroskedasticity by estimating the variance in a neighborhood around
@@
 The two robust procedures are again very similar to each other and give
-statistically significant, positve, estimates. The confidence intervals tend to shift
+statistically significant, positive, estimates. The confidence intervals tend to shift
 relative to the original intervals, increasing both the range of effects consistent

### 2016-08-19 reply_1/referee1.tex
[#20] Move referee reports to a subdirectory
I've moved our referee reports for the first resubmission into their own
subdirectory. This lets us put the cover letter for the second
resubmission in a subdirectory too. :)

\documentclass[12pt,fleqn]{article}

% Add commit information from Git to the pdf. It is automatically
% generated with the R script 'tex/git and can be run from
% the command line in the project's top directory via:
%
% $ tex/git
%
% If VERSION.tex does not exist we can't add information from
% Git, so we'll use today's date as a fallback.

\IfFileExists{../VERSION.tex}{\input{../VERSION}}{%
\providecommand\VERSION{\today}}

\input{../tex/setup}
\input{../tex/macros}

\title{Reply to the report by Referee 1 for ``Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs
  with the Uniform Kernel''}

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}.}}

\begin{document}
\maketitle

First, we thank the reviewer for providing detailed and helpful comments, which
we feel have significantly improved the quality of the draft.  Below we provide
replies to the reviewer's specific comments detailing how we address each
comment.

\section{General overview of changes}

For this version of the paper, we have changed the bootstrap method from the
residual bootstrap to the wild bootstrap. We have also updated the simulations
to include DGPs featuring heteroskedasticity. We believe that the residual
bootstrap used in the previous version is theoretically correct even under
heteroskedastcity as long as the conditional variance is assumed to be smooth in
a neighborhood around the cutoff point, since the residual bootstrap we initially
proposed only resampled from that neighborhood, but we agree that in practice
the wild bootstrap is likely to be more accurate and can accommodate forms of
conditional heteroskedasticity that the residual bootstrap can not.

We have also relaxed the ``uniform kernel'' requirement and allow other kernels
that are popular in practice. The title of the paper has been updated to reflect
that change.

The first referee expressed concern about the possible computational complexity of
using an iterated bootstrap to produce confidence intervals. This is much less
of an issue than it appears, because many of the matrix calculations can be
computed once and then reused in the bootstrap replications. (Any calculation
that does not involve $Y$ can be reused.) Each bootstrap replication only
requires a small number of matrix-vector multiplications which can be completed
very quickly. We have added a short section after Algorithm 2 that explains
this implementation detail, and we have also provided open source R code that
implements the procedure efficiently.

Finally, the mathematical appendix defines more notation explicitly and
summarizes several convergence results from Calonico, Cattaneo, and Titiunik
(2014) that are referenced in the proofs and we have made some small additional
changes that the referees suggested.

\section{Specific Comments}

\begin{enumerate}
 \item  \textit{``It is not clear what is special about the uniform kernel. If possible, the authors should consider a general kernel and remove Uniform kernel from the title.''}

 We added results that allow for more general kernels typically used in RDD. The title has been changed accordingly.

\item \textit{``...What are the potential benefits of bootstrap over the analytical calculations.''}

  As now discussed in the text, we believe that this procedure is promising
  because of its ``automatic'' nature. It is easier to implement in cases of
  interest to applied researchers for which the analytical correction has not
  been developed; for example, analytical expressions for the standard errors
  with clustered observations have been only recently available despite heavy
  demand and interest from applied researchers, but would be relatively
  straightforward to calculate with a bootstrap.  We do not claim to achieve
  this level of generality in this paper but we expect that it will serve as a
  stepping stone for these developments.

\item \textit{`` The most critical point: Assumption 1.4 allows for heteroskedasticity but I suspect the residual bootstrap is invalid in this setting...''}

Thanks for raising this concern. See the discussion above.

\item \textit{``Are the bootstrap residuals conditionally centered?...''}

 Yes, the bootstrap residuals are conditionally centered. Hopefully this is clear on the discussion about the wild bootstrap approach.

\item \textit{``I assume $X_{i}^{*}=X_{i}$, right? If so, use $X_{i}$''}

Thank you for this suggestion. We changed it on the latest draft.

\item \textit{``...Is it possible to propose a bootstrap approximation that does not require iterations...?''}

See discussion on item number 2 in the main comments section above. The
iterations are less computationally demanding than they appear.

\item \textit{``As mentioned earlier, I suspect Theorem 2 is incorrect unless conditional homoskedasticity is assumed....''}

  Thanks again. See the discussion above.

\item \textit{``The Monte Carlo should also include conditional heteroskedasticity versions of the used DGPs.''}

  Thank you for this suggestion; we have added some additional simulations with conditional heteroskedasticity.

\item \textit{``The proofs need to include more detailed steps. Be explicit about bootstrap parameters (e.g. $\tau^{*}$). Provide a detailed proof for the statement that follows after ``the bootstrap ensures that'' in page 19. What do you mean by the last formula of page 20? Also, it is not clear what equality in distribution in the first display of page 21 means. Where is $V(h,b)$ defined? I was unable to find it. The authors need to make sure that the convergence in distribution proof is valid under conditional heteroskedasticity.''}

Thank you for calling our attention to these issues.
 In the new proofs we have added details to the statement ``the bootstrap ensures that,'' previously on page 19.
 Since the proof for theorem 2 changed substantially with the adoption of the Wild Bootstrap scheme
 (which addresses the heteroskedasticity issue, as discussed before) we made substantial changes that hopefully
 will make the proof's steps clearer to the reader, addressing the remaining comments.

\item \textit{``Some small typos: ``accommodates'' should be ``accommodated'' in line 4 of page 4; drop non-negligibly in page 7.''}

Thanks. They have been fixed.

\end{enumerate}

\end{document}

### 2016-08-19 reply_1/referee2.tex
[#20] Move referee reports to a subdirectory
I've moved our referee reports for the first resubmission into their own
subdirectory. This lets us put the cover letter for the second
resubmission in a subdirectory too. :)

\documentclass[12pt,fleqn]{article}

% Add commit information from Git to the pdf. It is automatically
% generated with the R script 'tex/git and can be run from
% the command line in the project's top directory via:
%
% $ tex/git
%
% If VERSION.tex does not exist we can't add information from
% Git, so we'll use today's date as a fallback.

\IfFileExists{../VERSION.tex}{\input{../VERSION}}{%
\providecommand\VERSION{\today}}

\input{../tex/setup}
\input{../tex/macros}

\title{Reply to the report by Referee 2 for ``Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs
  with the Uniform Kernel''}

\author{Ot\'avio Bartalotti \and Gray Calhoun \and Yang He\thanks{%
  All authors: Department of Economics, Iowa State University.
  260 Heady Hall, Ames, IA 50011.
  Bartalotti: \protect\url{bartalot@iastate.edu};
  Calhoun: \protect\url{gcalhoun@iastate.edu} and
  \protect\url{http://gray.clhn.org};
  He: \protect\url{yanghe@iastate.edu}.}}

\begin{document}
\maketitle

First, we thank the reviewer for providing detailed and helpful comments, which
we feel have significantly improved the quality of the draft.  Below we provide
replies to the reviewer's specific comments detailing how we address each
comment.

\section{General overview of changes}

For this version of the paper, we have changed the bootstrap method from the
residual bootstrap to the wild bootstrap. We have also updated the simulations
to include DGPs featuring heteroskedasticity. We believe that the residual
bootstrap used in the previous version is theoretically correct even under
heteroskedastcity as long as the conditional variance is assumed to be smooth in
a neighborhood around the cutoff point, since the residual bootstrap we initially
proposed only resampled from that neighborhood, but we agree that in practice
the wild bootstrap is likely to be more accurate and can accommodate forms of
conditional heteroskedasticity that the residual bootstrap can not.

We have also relaxed the ``uniform kernel'' requirement and allow other kernels
that are popular in practice. The title of the paper has been updated to reflect
that change.

The first referee expressed concern about the possible computational complexity of
using an iterated bootstrap to produce confidence intervals. This is much less
of an issue than it appears, because many of the matrix calculations can be
computed once and then reused in the bootstrap replications. (Any calculation
that does not involve $Y$ can be reused.) Each bootstrap replication only
requires a small number of matrix-vector multiplications which can be completed
very quickly. We have added a short section after Algorithm 2 that explains
this implementation detail, and we have also provided open source R code that
implements the procedure efficiently.

Finally, the mathematical appendix defines more notation explicitly and
summarizes several convergence results from Calonico, Cattaneo, and Titiunik
(2014) that are referenced in the proofs and we have made some small additional
changes that the referees suggested.

\section{Specific Comments}

\begin{enumerate}

 \item  \textit{``Page 4 line 4: ``can be accommodated''.''}

 Thanks. This has been fixed.

\item \textit{``Although standard in the RDD literature, it will be useful to distinguish conditions for identification from those for estimation and inference. Most of Assumption 1 is for
estimation and inference, and I suggest adding a short discussion there to explain each component of Assumption 1, and make it clear which are essential for identification. ''}

 Thanks. A short discussion has been added to the main text.

\item \textit{`` To match the notation used in Calonico et al. (2014), I suggest to define $V(h) :=\V[\hat{\tau}(h)|X_{1}, \dots ,X_{n}]$, and use $\hat{V}(h)$ when constructing confidence intervals. See the definition of $V_{SRD}(h_{n})$ in Calonico et al. (2014).''}

 Thank you for the recommendation. Adjustments were made in the draft.

\item \textit{``By assuming the bandwidth condition $b \geq h, nb \rightarrow \infty$ is redundant. Moreover, the bandwidth condition in Theorem 1 of Calonico et al. (2014) reduces to $nh^{5}b^{2} \rightarrow 0$. This paper assumes, additionally, that $nb^{5}h^{2} \rightarrow 0$. It is not clear why the extra condition is needed, and I recommend adding some discussion/explanation.''}

  Thanks for bringing this up. In the general kernel setup developed for this draft it became clear that the condition $h<b$ is not necessary and it has been dropped. Regarding the conditions $nh^{5}b^{2} \rightarrow 0$ and $nb^{5}h^{2} \rightarrow 0$, we originally decided to present the conditions in this form to make it more accessible to the readers. Note that CCT Theorem 1 assumes $n \min\{h^{5},b^{5}\}\max\{h^{2}, b^{2}\} \rightarrow 0$ which is equivalent to our condition now that $b < h$ is allowed.

\item \textit{``Calonico et al. (2014) allow $h/b \rightarrow \rho \in [0,\infty]$, while the assumption used in this paper requires $h/b \leq 1$. It is mentioned in footnote 12 that the condition $h \leq b$ can be generalized with other kernels. Please provide more intuition, and to what extent it can be relaxed.''}

Please see the discussion to about the relationship between $h$ and $b$ in the previous comment.

\item \textit{``Use $\mathbb{P}$ instead of Pr.''}

No problem.

\item \textit{``In Algorithm 1, use $\Delta(h,b)$ or $\hat{\Delta}(h,b)$ instead of $\Delta^{*}(h,b)$, as there is no bootstrap uncertainty in the estimated bias. Accordingly in Algorithm 2, use $\Delta^{*}(h,b)$ or $\hat{\Delta}^{*}(h,b)$ instead of $\Delta^{**}(h,b)$.''}

We're not sure that we understand this comment---there is definitely bootstrap
uncertainty in the estimated bias in our procedure because we estimate the
bias with a preliminary bootstrap. We ignore this uncertainty in the theoretical
results (which is consistent with the bootstrap literature) but it will be
present in applications.

\item \textit{``In Algorithm 2.1, it should be ``$\hat{g}_{-}$ and $\hat{g}_{+}$''.''}

 Thanks. It has been corrected.

\item \textit{``Instead of $\hat{\tau}'(h,b)$ and $V'(h,b)$, I recommend using $\hat{\tau}^{bc}(h,b)$ and $V^{bc}(h,b)$ to make the notation more explicit.''}

Thanks for the suggestion. We have changed this in the paper.

\item \textit{``In Algorithm 1.2(b) and Algorithm 2.2(b), it should be $X_{i}$ rather than $X^{*}_{i}$.''}

Thanks. It is now fixed.

\item \textit{``In Section 4 (Simulation Evidence), the Naive Bootstrap is implemented with nonparametric resampling and the bandwidth is re-calculated for each bootstrap repetition.
This is quite different from the other procedures, and can be misleading. I recommend not including the Naive Bootstrap.''}

Thank you for the recommendation. We dropped the Naive Bootstrap from the Simulation Evidence.

\item \textit{``As mentioned earlier, the wild bootstrap seems to be more appealing in terms of finite sample performance when the variance $\sigma^{2}(x)$ varies near the cutoff. The algebra should not be difficult and I recommend the authors to include theoretical results with the wild bootstrap.''}

Thanks, we've made this change as discussed above.

\item \textit{``It will be helpful to have simulation results for DGPs with heteroskedastic variance.''}

  Thank you for this suggestion; we have added additional simulations with conditional heteroskedasticity.

\item \textit{``In the Mathematical Appendix, the authors used min(h, b), which is redundant. (Page 19, line 4-5)''}

Thanks for pointing this out. It is no longer redundant since we have relaxed
the requirement that $h < b$.

\item \textit{``The Mathematical Appendix should contain more details.''}

Thank you for pointing this out. We have added much more exposition to the
Mathematical Appendix.

\end{enumerate}

\end{document}

### 2016-08-19 reply_2/cover_letter.tex
[#20] Add empty cover letter for second resubmission
Remember, the second resubmission doesn't require specific letters
to the referees.

Closes #20.

--- 2016-08-11 cover_letter.tex
@@
 
-\IfFileExists{./VERSION.tex}{\input{VERSION}}{%
+\IfFileExists{../VERSION.tex}{\input{../VERSION}}{%
 \providecommand\VERSION{\today}}
 
-\input{tex/setup}
-\input{tex/macros}
+\input{../tex/setup}
+\input{../tex/macros}
 
@@
 
-Thank you for your helpful comments. We have made the requested changes. Overall,
-for this version of the paper, we have changed the bootstrap method from the
-residual bootstrap to the wild bootstrap. We have also updated the simulations
-to include DGPs featuring heteroskedasticity. We believe that the residual
-bootstrap used in the previous version is theoretically correct even under
-heteroskedastcity as long as the conditional variance is assumed to be smooth in
-a neighorbood around the cutoff point, since the residual bootstrap we initially
-proposed only resampled from that neighborhood, but we agree that in practice
-the wild bootstrap is likely to be more accurate and can accomodate forms of
-conditional heteroskedasticity that the residual bootstrap can not.
-
-We have also relaxed the ``uniform kernel'' requirement and allow other kernels
-that are popular in practice. The title of the paper has been updated to reflect
-that change.
-
-The first referee expressed concern about the possible computational complexity of
-using an iterated bootstrap to produce confidence intervals. This is much less
-of an issue than it appears, because many of the matrix calculations can be
-computed once and then reused in the bootstrap replications. (Any calculation
-that does not involve $Y$ can be reused.) Each bootstrap replication only
-requires a small number of matrix-vector multiplications which can be completed
-very quickly. We have added a short section after Algorithm 2 that explains
-this implementation detail, and we have also provided open source R code that
-implements the procedure efficiently.
-
-Finally, the mathematical appendix defines more notation explicitly and
-summarizes several convergence results from Calonico, Cattaneo, and Titiunik
-(2014) that are referenced in the proofs and we have made some small additional
-changes that the referees suggested.
-
-The replies to the referees give more details on some of the specific
-changes made to the paper. Thank you for giving us the opportunity to revise
-the paper.
+\strut
 

### 2016-08-23 main_paper.tex
[#16] change 'sup_{x,\tau}' to 'sup_x' in Theorem 2
Minor, basically inconsequential, change to Theorem 2. But one of the
referees wants it so let's do it.

Closes #16.
[#17] Change 'Y_i, X_i' to '{Y_i, X_i}_i' in Assumption 1
Another referee request that is easy to accommodate. Closes #17.
[#18] make beta hat's components more explicit in definition
Partial attempt to address referee 1's 4th bullet.
[#19] Add definition of HC3 transformation
To make the paper self contained, I've added a definition of the
HC3 transformation as suggested by the referee. Closes #19.

@@
 \begin{assumption}[Behavior of the DGP near the cutoff]\label{A1}
-  The random variables $Y_i$, $X_i$ form a random sample of size $n$.
+  The random variables $\{Y_i, X_i\}_{i=1}^n$ form a random sample of size $n$.
   There exists a positive number $\kappa_0$ such that the following
@@
   \begin{equation*}
-    \sup_{x,\tau}
+    \sup_{x}
     \Big\rvert \Pr^*\big[ \sqrt{nm}
@@
 transformation proposed by \citet{DF08} in this paper's Monte Carlo simulations
-and empirical exercise.
+and empirical exercise; i.e.\ Algorithms~\ref{Alg1} and~\ref{Alg2} use the
+transformed residuals
+\begin{equation}\label{eq:14}
+  \frac{\hat\varepsilon_i}{1 - H_{ii}}
+\end{equation}
+instead of $\hat\varepsilon_i$, with $H_{ii}$ the $(i, i)$ element of the matrix
+\begin{equation}\label{eq:15}
+  \mathbf{H} = \mathbf{K}_+^{1/2} \mathbf{X} (\mathbf{X}' \mathbf{K}_+ \mathbf{X})^{-1} \mathbf{X}' \mathbf{K}_+^{1/2}.
+\end{equation}
+The matrix $\mathbf{H}$ is the projection matrix onto the kernel-weighted design
+matrix.
 
@@
 are chosen using the AMSE-optimal rule proposed by CCT and the wild bootstrap
-uses the ``HC3'' transformation of \citet{DF08}.
+uses the ``HC3'' transformation of \citet{DF08}, defined in Equations~\eqref{eq:14}
+and~\eqref{eq:15}.
 
@@
 AMSE-optimal bandwidths proposed by CCT, the uniform kernel, and the HC3 wild
-bootstrap from \citet{DF08}. In the bootstrap
+bootstrap from \citet{DF08}; see Equations~\eqref{eq:14} and~\eqref{eq:15} of
+this paper and the surrounding remarks. In the bootstrap
 procedure, we use 500 bootstraps for bias correction and 999 to calculate the

### 2016-08-24 R/simulation.R
[#22] Fix error in reported bias for simulations
The simulations have been reporting the negative bias, not the actual
bias --- the bias is defined as E(estimator) - parameter. This commit
fixes the error and closes #22.

@@ -62,7 +62,7 @@ simulation.1 <- function(model.id, kernel, heteroskedasticity = F) {
   stopCluster(cl)
   
   t.true    <- ifelse(model.id ==2, -3.45, 0.04)
-  bias      <- t.true - mean(collect.simu[ , 1])
+  bias      <- mean(collect.simu[ , 1]) - t.true
   SD        <- sd(collect.simu[ , 1])
   MSE       <- sqrt(mean((collect.simu[ , 1] - t.true)^2))
   coverage  <- mean(collect.simu[ , 2] <= t.true & collect.simu[ , 3] >= t.true)
@@ -100,7 +100,7 @@ simulation.2 <- function(model.id, kernel, heteroskedasticity = F) {
   stopCluster(cl)
   
   t.true    <- ifelse(model.id ==2, -3.45, 0.04)
-  bias      <- t.true - mean(collect.simu[ , 1])
+  bias      <- mean(collect.simu[ , 1]) - t.true
   SD        <- sd(collect.simu[ , 1])
   MSE       <- sqrt(mean((collect.simu[ , 1] - t.true)^2))
   coverage  <- mean(collect.simu[ , 2] <= t.true & collect.simu[ , 3] >= t.true)
@@ -134,7 +134,7 @@ simulation.3 <- function(model.id, kernel, heteroskedasticity = F) {
   stopCluster(cl)
   
   t.true    <- ifelse(model.id ==2, -3.45, 0.04)
-  bias      <- t.true - mean(collect.simu[ , 1])
+  bias      <- mean(collect.simu[ , 1]) - t.true
   SD        <- sd(collect.simu[ , 1])
   MSE       <- sqrt(mean((collect.simu[ , 1] - t.true)^2))
   coverage  <- mean(collect.simu[ , 2] <= t.true & collect.simu[ , 3] >= t.true)
@@ -172,7 +172,7 @@ simulation.4 <- function(model.id, kernel, heteroskedasticity = F) {
   stopCluster(cl)
   
   t.true    <- ifelse(model.id ==2, -3.45, 0.04)
-  bias      <- t.true - mean(collect.simu[ , 1])
+  bias      <- mean(collect.simu[ , 1]) - t.true
   SD        <- sd(collect.simu[ , 1])
   MSE       <- sqrt(mean((collect.simu[ , 1] - t.true)^2))
   coverage  <- mean(collect.simu[ , 2] <= t.true & collect.simu[ , 3] >= t.true)

### 2016-08-24 main_paper.tex
Make very small notation tweak
I misused hat beta_{+,1} in describing the computational issues in
the paper. This commit changes the discussion a little to try to
avoid using beta-hat.
Fix #21 describe the auxiliary distribution in wild bootstrap
We didn't make it clear that we used two-point distribution in both
simulation section and application section.

@@
 \[
-\hat\beta_{+,1} = \underbrace{(\mathbf{X}' \mathbf{K}_+ \mathbf{X})^{-1} \mathbf{X}' \mathbf{K}_+}_{\mathbf{W}_{+,1}} \mathbf{Y}
+  (\mathbf{X}' \mathbf{K}_+ \mathbf{X})^{-1} \mathbf{X}' \mathbf{K}_+ \mathbf{Y}
+  \equiv \mathbf{W}_{+,1}\mathbf{Y}
 \]
@@
 and~\eqref{eq:15}.
+In our simulation studies as well as the application in the next section, we adopt two-point distribution for the $e_i^*$ when estimating our bootstrap procedure, i.e., $e_i^*$ equals $\frac{1 + \sqrt{5}}{2}$ with probability $ p = \frac{\sqrt{5} - 1}{2 \sqrt{5}}$ and $\frac{1 - \sqrt{5}}{2}$ with probability $1 - p$.
 

### 2016-08-24 main_paper.tex
[#22] Update simulation tables with correct bias values
Commit f12975e updated the R code to report the correct bias values
for each estimator in the Monte Carlo simulations. This commit fixes
the tables to report those values. (This was done by manually flipping
the signs, not by rerunning everything.)

--- 2016-08-23 main_paper.tex
@@
 uses the ``HC3'' transformation of \citet{DF08}, defined in Equations~\eqref{eq:14}
-and~\eqref{eq:15}.
+and~\eqref{eq:15}. In these simulations, we use Mammen's (1993) \nocite{Mam93}
+two-point distribution for $e_i^*$ in the bootstrap:
+\begin{equation}
+  \label{eq:19}
+  e_i^* =
+  \begin{cases}
+    \frac{1 + \sqrt{5}}{2} & \text{with probability\ } \frac{\sqrt{5} - 1}{2 \sqrt{5}} \\
+    \frac{1 - \sqrt{5}}{2} & \text{otherwise}.
+  \end{cases}
+\end{equation}
 
@@
     \midrule
-    1 & Wild bootstrap & --0.011 & 0.067 & 0.068 & 0.926 & 0.247 \\ 
-      & CCT            & --0.011 & 0.067 & 0.068 & 0.914 & 0.239 \\ 
-      & Naive          & --0.037 & 0.041 & 0.055 & 0.823 & 0.152 \\ 
-    2 & Wild bootstrap & --0.008 & 0.086 & 0.086 & 0.938 & 0.334 \\ 
-      & CCT            & --0.008 & 0.086 & 0.086 & 0.932 & 0.346 \\ 
-      & Naive          & --0.145 & 0.065 & 0.159 & 0.311 & 0.224 \\ 
-    3 & Wild bootstrap & --0.005 & 0.065 & 0.065 & 0.945 & 0.252 \\ 
-      & CCT            & --0.005 & 0.065 & 0.065 & 0.934 & 0.244 \\ 
-      & Naive          &   0.034 & 0.051 & 0.061 & 0.851 & 0.185 \\  \\
+    1 & Wild bootstrap & 0.011 & 0.067 & 0.068 & 0.926 & 0.247 \\
+      & CCT            & 0.011 & 0.067 & 0.068 & 0.914 & 0.239 \\
+      & Naive          & 0.037 & 0.041 & 0.055 & 0.823 & 0.152 \\
+    2 & Wild bootstrap & 0.008 & 0.086 & 0.086 & 0.938 & 0.334 \\
+      & CCT            & 0.008 & 0.086 & 0.086 & 0.932 & 0.346 \\
+      & Naive          & 0.145 & 0.065 & 0.159 & 0.311 & 0.224 \\
+    3 & Wild bootstrap & 0.005 & 0.065 & 0.065 & 0.945 & 0.252 \\
+      & CCT            & 0.005 & 0.065 & 0.065 & 0.934 & 0.244 \\
+      & Naive          & --0.034 & 0.051 & 0.061 & 0.851 & 0.185 \\  \\
     \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
     \midrule
-    1 & Wild bootstrap & --0.010 & 0.073 & 0.074 & 0.935 & 0.276 \\
-      & CCT            & --0.010 & 0.073 & 0.074 & 0.923 & 0.265 \\ 
-      & Naive          & --0.035 & 0.046 & 0.058 & 0.838 & 0.165 \\ 
-    2 & Wild bootstrap & --0.007 & 0.084 & 0.084 & 0.922 & 0.312 \\ 
-      & CCT            & --0.007 & 0.084 & 0.084 & 0.929 & 0.340 \\ 
-      & Naive          & --0.144 & 0.064 & 0.158 & 0.277 & 0.211 \\ 
-    3 & Wild bootstrap & --0.002 & 0.081 & 0.081 & 0.940 & 0.311 \\ 
-      & CCT            & --0.002 & 0.081 & 0.081 & 0.926 & 0.297 \\ 
-      & Naive          &   0.033 & 0.059 & 0.068 & 0.835 & 0.194 \\  
+    1 & Wild bootstrap & 0.010 & 0.073 & 0.074 & 0.935 & 0.276 \\
+      & CCT            & 0.010 & 0.073 & 0.074 & 0.923 & 0.265 \\
+      & Naive          & 0.035 & 0.046 & 0.058 & 0.838 & 0.165 \\
+    2 & Wild bootstrap & 0.007 & 0.084 & 0.084 & 0.922 & 0.312 \\
+      & CCT            & 0.007 & 0.084 & 0.084 & 0.929 & 0.340 \\
+      & Naive          & 0.144 & 0.064 & 0.158 & 0.277 & 0.211 \\
+    3 & Wild bootstrap & 0.002 & 0.081 & 0.081 & 0.940 & 0.311 \\
+      & CCT            & 0.002 & 0.081 & 0.081 & 0.926 & 0.297 \\
+      & Naive          & --0.033 & 0.059 & 0.068 & 0.835 & 0.194 \\
     \bottomrule
@@
 AMSE-optimal bandwidths proposed by CCT, the uniform kernel, and the HC3 wild
-bootstrap from \citet{DF08}; see Equations~\eqref{eq:14} and~\eqref{eq:15} of
-this paper and the surrounding remarks. In the bootstrap
+bootstrap from \citet{DF08} with Mammen's (1993) two-point distribution
+on $e^*_i$; see Equations~\eqref{eq:14} and~\eqref{eq:15} of
+this paper and their surrounding remarks as well as Equation~(\ref{eq:19}) for
+formal definitions. In the bootstrap
 procedure, we use 500 bootstraps for bias correction and 999 to calculate the

### 2016-08-24 main_paper.tex
[#13] strengthen equivalence claims between CCT's correction and ours
The proof of Theorem 1 indicates that the bootstrap bias correction
is equivalent to CCT's correction, after abstracting from bootstrap
simulation error. This commit makes that equivalence explicit and
addresses part of Referee 1's first two comments.

@@
   experiments and empirical component of this paper are available online
-  at \protect\url{https://github.com/grayclhn/boot-rd}.}}
+  at \protect\url{https://github.com/grayclhn/boot-rd}. We would like to
+  thank Matias Cattaneo, Juan Carlos Escanciano, Sebastian Calonico, Max Farrell, Helle Bunzel, Brent Kreider, Quentin Brummet, seminar participants at
+  the Advances in Econometrics conference on Regression Discontinuity
+  Designs, Third Annual Conference of the International Association for Applied Econometrics,
+ 2016 North American Summer Meeting of the Econometric Society and the $69^{th}$ European Meeting of the Econometric Society, and especially the two anonymous referees for
+  substantial help and advice on earlier versions of this paper.}}
 
@@
     \begin{align*}
-      \hat\beta_{-} &= \argmin_\beta \sum_{i = 1}^n
-      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{-,b}(X_{i}) \\
-      \hat\beta_{+} &= \argmin_\beta \sum_{i = 1}^n
-      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{+,b}(X_{i}).
+      (\hat\beta_{-,0}, \hat\beta_{-,1}, \hat\beta_{-,2})' &=
+      \argmin_{\beta_0, \beta_1, \beta_2}
+      \sum_{i = 1}^n (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{-,b}(X_{i}) \\
+      (\hat\beta_{+,0}, \hat\beta_{+,1}, \hat\beta_{+,2})' &= \argmin_{\beta_0, \beta_1, \beta_2}
+      \sum_{i = 1}^n (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{+,b}(X_{i}).
     \end{align*}
@@
 \begin{equation}
+  \label{eq:18}
+  \Delta^*(h,b) = h^{2} \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
+  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
+\end{equation}
+almost surely and
+\begin{equation}
   \label{eq:4}
-  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V^{bc}(h, b)^{1/2}}
+  \frac{\hat\tau(h) - \Delta^{*}(h,b) - \tau}{ V^{bc}(h, b)^{1/2}}
   \to^{d} N(0,1),
@@
 
-Theorem~\ref{T1} implies that our bias-corrected
+For practical purposes, Theorem~\ref{T1} implies that our bias-corrected
 estimator has the same asymptotic distribution as CCT's. This equivalence should
@@
 the bias of the local linear model, so they should behave very similarly.
+Equation~\eqref{eq:18} implies an even stronger relationship between the two
+results, that the bias correction is equivalent to CCT's up to simulation error
+in the bootstrap.
 
@@
 bias close to zero, with their standard deviation largely
-determining the estimators' RMSE. Moreover, as Theorem~\ref{T1} suggests, the
-bootstrap and analytically-corrected estimators have essentially the same
-standard deviation across all of the DGPs.
+determining the estimators' RMSE.
+As we remark earlier, the bias correction from the wild bootstrap is equivalent
+to CCT's bias correction up to simulation error from the bootstrap and this
+equivalence is apparent in the Monte Carlo. This equivalence also explains why
+the bootstrap and analytically-corrected estimators have essentially the same
+standard deviation across all of the DGPs.\footnote{%
+  Note that this table reports the estimators' variance across simulations,
+  not the \emph{estimated} variance used for the confidence intervals.} %
 
@@
   \Psi_{\bullet,p} &= \int_{-\infty}^\infty
-     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
+     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du.
 \end{align*}
@@
   \tfrac{hb}{m} \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
-  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
+  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1). \label{eq:12}
 \end{align}
@@
 \end{equation*}
+Equation~\eqref{eq:18} holds because
+$\mu_\bullet^{*(2)} = \hat\mu_{\bullet,2}^{(2)}(b)$ almost surely.
+
 CCT's Lemma A1 implies that
@@
 \end{align}
-The second equality holds because
-$\mu_\bullet^{*(2)} = \hat\mu_{\bullet,2}^{(2)}(b)$ almost surely. Asymptotic
+Asymptotic
 normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$ and
@@
 mean zero random variables for any measurable function $R$, each with
-$p$th absolute moment
-$\lvert R(X_i) \hat\varepsilon_i \rvert^p \E \lvert e_i^*
-\rvert^{p}$.
+$q$th absolute moment
+$\lvert R(X_i) \hat\varepsilon_i \rvert^q \E \lvert e_i^*
+\rvert^{q}$.
 The result then holds as a consequence of the Lindeberg-Feller CLT if

### 2016-08-24 reply_2/cover_letter.tex
[#22] Add discussion of sign error in simulations to cover letter
We should probably mention the fix to Matias. Done :).  Closes #22.
[#13] Add statement about bias correction similarities to cover letter.

@@
 
+Regarding referee 1's comments,
+\begin{itemize}
+\item the referee noticed that the bias and variance of the analytical
+  correction is identical to the bootstrap correction. (Up to reported
+  values --- they do differ in higher decimal places that were not
+  reported.) This led us to examine our theoretical results more
+  carefully and ultimately strengthen Theorem 1. Since both of the
+  corrections are based on the same estimated 2nd order polynomial,
+  the bootstrap and analytical corrections are not just asymptotically
+  equivalent; they are equivalent up to simulation error.
+\item We have also clarified the wording issues addressed in comment 2
+  and explicitly addressed this coincidence.
+\end{itemize}
+Regarding referee 2's comments.
+\begin{itemize}
+\item (placeholder)
+\end{itemize}
+We have also made the small notational changes and new definitions
+the referees requested.
+
+In addition, we discovered a small error in the simulation results ---
+instead of reporting each estimator's bias, we reported the negative
+bias. Since the values were close to zero, this does not have a
+substantive effect on the results but we have, of course, fixed the
+tables.
+
 \noindent%

### 2016-08-24 main_paper.tex
[#21] Make small adjustments to discussion of e_i^*
This commit corrects a grammar error and adds discussion of e_i^* to
the empirical section as well as the simulation section. People often
skip the simulations :)

--- 2016-08-24 main_paper.tex
@@
 uses the ``HC3'' transformation of \citet{DF08}, defined in Equations~\eqref{eq:14}
-and~\eqref{eq:15}.
-In our simulation studies as well as the application in the next section, we adopt two-point distribution for the $e_i^*$ when estimating our bootstrap procedure, i.e., $e_i^*$ equals $\frac{1 + \sqrt{5}}{2}$ with probability $ p = \frac{\sqrt{5} - 1}{2 \sqrt{5}}$ and $\frac{1 - \sqrt{5}}{2}$ with probability $1 - p$.
+and~\eqref{eq:15}. In these simulations, we use Mammen's (1993) \nocite{Mam93}
+two-point distribution for $e_i^*$ in the bootstrap:
+\begin{equation}
+  \label{eq:19}
+  e_i^* =
+  \begin{cases}
+    \frac{1 + \sqrt{5}}{2} & \text{with probability\ } \frac{\sqrt{5} - 1}{2 \sqrt{5}} \\
+    \frac{1 - \sqrt{5}}{2} & \text{otherwise}.
+  \end{cases}
+\end{equation}
 

### 2016-08-25 R/rdfunctions.R
Minor edit of the notes on code
We fixed the heteroskedastic DGP, but didn't change the notes. Now, the
notes match the code.

@@ -26,8 +26,8 @@ average_bw <- function(model.id, kernel) {
 
 ## this function generate data with heteroskedasticity
 # standard error is firstly set to the square of expected outcome
-# rescale all standard error by a common factor 
-# so that they are on average 0.1295 within avebw
+# rescale all variance by a common factor 
+# so that they are on average 0.1295^2 within avebw
 
 generate.data.h <- function(model.id, avebw) {
   x <- 2*rbeta(500, 2, 4) - 1

### 2016-08-25 main_paper.tex
Add a few missing periods to equations in appendix
[#15] Change scale factor statement of asymptotic normality
A referee pointed out that \sqrt{mn} is not the appropriate scale factor for
the RD estimator. This commit changes that scale factor to use the standard
deviation instead in the statement of Theorem 2.

--- 2016-08-24 main_paper.tex
@@
 described in detail by our Algorithm~\ref{Alg1} and the resulting bias corrected
-estimator is shown to be asymptotically normal with mean zero in our
+estimator is shown to be equivalent to CCT's, up to simulation error in the
+bootstrap, and asymptotically normal with mean zero in our
 Theorem~\ref{T1} under AMSE-optimal bandwidth rates.
@@
   Algorithm~\ref{Alg2}.} %
+Simulation results presented in Section~\ref{sim} indicate that this iterated
+bootstrap provides very similar results in finite samples to CCT's analytical
+confidence intervals as well.
 
@@
   $b$ be the bandwidth used to estimate a second local quadratic model. Then
-  $n h \to \infty$, $n b \to \infty$, $n h^{5} b^{2} \to 0$, and
-  $n b^{5} h^{2} \to 0$ as $n \to \infty$.\footnote{%
+  $n h \to \infty$, $n b \to \infty$, and
+  $n \times \min(h, b)^{5} \times \max(h, b)^2$ as $n \to \infty$.\footnote{%
     Unless otherwise stated, all limits in this paper are assumed to hold as
@@
     \sup_{x}
-    \Big\rvert \Pr^*\big[ \sqrt{nm}
-    (\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^*) \leq x \big]
-    - \Pr\big[ \sqrt{nm}
-    (\hat\tau(h) - \Delta^*(h,b) - \tau) \leq x \big] \Big\lvert \to^p 0.
+    \Bigg\rvert \Pr^*\Bigg[
+    \frac{\hat\tau^{*}(h) - \Delta^{**}(h,b) - \tau^*}{\V^*(\hat\tau^{*}(h) - \Delta^{**}(h,b))^{1/2}}
+    \leq x \Bigg]
+    - \Pr\Bigg[\frac{\hat\tau(h) - \Delta^*(h,b) - \tau}{V^{bc}(h,b)^{1/2}}
+    \leq x \Bigg] \Bigg\lvert \to^p 0.
   \end{equation*}

### 2016-08-25 main_paper.tex
Tweak parentheses in Theorem 1

--- 2016-08-24 main_paper.tex
@@
   \label{eq:4}
-  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V^{bc}(h, b)^{1/2}}
+  \frac{\hat\tau(h) - \Delta^{*}(h,b) - \tau}{ V^{bc}(h, b)^{1/2}}
   \to^{d} N(0,1),

### 2016-08-25 main_paper.tex
[#24] Add acknowledgements to front of paper
This is still probably incomplete.

@@
   experiments and empirical component of this paper are available online
-  at \protect\url{https://github.com/grayclhn/boot-rd}.}}
+  at \protect\url{https://github.com/grayclhn/boot-rd}. We would like to
+  thank Matias Cattaneo, Juan Carlos Escanciano, seminar participants at
+  the Advances in Econometrics conference on Regression Discontinuity
+  Designs, and especially the two anonymous referees for helpful and
+  substantive help and advice on earlier versions of this paper.}}
 

### 2016-08-25 main_paper.tex
[#18] Fix small error in definition of beta hat
I had flipped two lines in the statement of beta hat in Algorithm 1. This
commit fixes it.

--- 2016-08-25 main_paper.tex
@@
   \label{eq:4}
-  \frac{\hat\tau(h) - \Delta^{*}(h,b) - \tau}{ V^{bc}(h, b)^{1/2}}
+  \frac{(\hat\tau(h) - \Delta^{*}(h,b) - \tau)}{ V^{bc}(h, b)^{1/2}}
   \to^{d} N(0,1),
@@
 \[
-  (\mathbf{X}' \mathbf{K}_+ \mathbf{X})^{-1} \mathbf{X}' \mathbf{K}_+ \mathbf{Y}
-  \equiv \mathbf{W}_{+,1}\mathbf{Y}
+\hat\beta_{+,1} = \underbrace{(\mathbf{X}' \mathbf{K}_+ \mathbf{X})^{-1} \mathbf{X}' \mathbf{K}_+}_{\mathbf{W}_{+,1}} \mathbf{Y}
 \]
@@
 transformation proposed by \citet{DF08} in this paper's Monte Carlo simulations
-and empirical exercise; i.e.\ Algorithms~\ref{Alg1} and~\ref{Alg2} use the
-transformed residuals
-\begin{equation}\label{eq:14}
-  \frac{\hat\varepsilon_i}{1 - H_{ii}}
-\end{equation}
-instead of $\hat\varepsilon_i$, with $H_{ii}$ the $(i, i)$ element of the matrix
-\begin{equation}\label{eq:15}
-  \mathbf{H} = \mathbf{K}_+^{1/2} \mathbf{X} (\mathbf{X}' \mathbf{K}_+ \mathbf{X})^{-1} \mathbf{X}' \mathbf{K}_+^{1/2}.
-\end{equation}
-The matrix $\mathbf{H}$ is the projection matrix onto the kernel-weighted design
-matrix.
+and empirical exercise.
 
@@
 are chosen using the AMSE-optimal rule proposed by CCT and the wild bootstrap
-uses the ``HC3'' transformation of \citet{DF08}, defined in Equations~\eqref{eq:14}
-and~\eqref{eq:15}. In these simulations, we use Mammen's (1993) \nocite{Mam93}
-two-point distribution for $e_i^*$ in the bootstrap:
-\begin{equation}
-  \label{eq:19}
-  e_i^* =
-  \begin{cases}
-    \frac{1 + \sqrt{5}}{2} & \text{with probability\ } \frac{\sqrt{5} - 1}{2 \sqrt{5}} \\
-    \frac{1 - \sqrt{5}}{2} & \text{otherwise}.
-  \end{cases}
-\end{equation}
+uses the ``HC3'' transformation of \citet{DF08}.
 
@@
     \midrule
-    1 & Wild bootstrap & 0.011 & 0.067 & 0.068 & 0.926 & 0.247 \\
-      & CCT            & 0.011 & 0.067 & 0.068 & 0.914 & 0.239 \\
-      & Naive          & 0.037 & 0.041 & 0.055 & 0.823 & 0.152 \\
-    2 & Wild bootstrap & 0.008 & 0.086 & 0.086 & 0.938 & 0.334 \\
-      & CCT            & 0.008 & 0.086 & 0.086 & 0.932 & 0.346 \\
-      & Naive          & 0.145 & 0.065 & 0.159 & 0.311 & 0.224 \\
-    3 & Wild bootstrap & 0.005 & 0.065 & 0.065 & 0.945 & 0.252 \\
-      & CCT            & 0.005 & 0.065 & 0.065 & 0.934 & 0.244 \\
-      & Naive          & --0.034 & 0.051 & 0.061 & 0.851 & 0.185 \\  \\
+    1 & Wild bootstrap & --0.011 & 0.067 & 0.068 & 0.926 & 0.247 \\ 
+      & CCT            & --0.011 & 0.067 & 0.068 & 0.914 & 0.239 \\ 
+      & Naive          & --0.037 & 0.041 & 0.055 & 0.823 & 0.152 \\ 
+    2 & Wild bootstrap & --0.008 & 0.086 & 0.086 & 0.938 & 0.334 \\ 
+      & CCT            & --0.008 & 0.086 & 0.086 & 0.932 & 0.346 \\ 
+      & Naive          & --0.145 & 0.065 & 0.159 & 0.311 & 0.224 \\ 
+    3 & Wild bootstrap & --0.005 & 0.065 & 0.065 & 0.945 & 0.252 \\ 
+      & CCT            & --0.005 & 0.065 & 0.065 & 0.934 & 0.244 \\ 
+      & Naive          &   0.034 & 0.051 & 0.061 & 0.851 & 0.185 \\  \\
     \multicolumn{7}{l}{Heteroskedastic data with $\gamma = 2$ (Panel B)}  \\
     \midrule
-    1 & Wild bootstrap & 0.010 & 0.073 & 0.074 & 0.935 & 0.276 \\
-      & CCT            & 0.010 & 0.073 & 0.074 & 0.923 & 0.265 \\
-      & Naive          & 0.035 & 0.046 & 0.058 & 0.838 & 0.165 \\
-    2 & Wild bootstrap & 0.007 & 0.084 & 0.084 & 0.922 & 0.312 \\
-      & CCT            & 0.007 & 0.084 & 0.084 & 0.929 & 0.340 \\
-      & Naive          & 0.144 & 0.064 & 0.158 & 0.277 & 0.211 \\
-    3 & Wild bootstrap & 0.002 & 0.081 & 0.081 & 0.940 & 0.311 \\
-      & CCT            & 0.002 & 0.081 & 0.081 & 0.926 & 0.297 \\
-      & Naive          & --0.033 & 0.059 & 0.068 & 0.835 & 0.194 \\
+    1 & Wild bootstrap & --0.010 & 0.073 & 0.074 & 0.935 & 0.276 \\
+      & CCT            & --0.010 & 0.073 & 0.074 & 0.923 & 0.265 \\ 
+      & Naive          & --0.035 & 0.046 & 0.058 & 0.838 & 0.165 \\ 
+    2 & Wild bootstrap & --0.007 & 0.084 & 0.084 & 0.922 & 0.312 \\ 
+      & CCT            & --0.007 & 0.084 & 0.084 & 0.929 & 0.340 \\ 
+      & Naive          & --0.144 & 0.064 & 0.158 & 0.277 & 0.211 \\ 
+    3 & Wild bootstrap & --0.002 & 0.081 & 0.081 & 0.940 & 0.311 \\ 
+      & CCT            & --0.002 & 0.081 & 0.081 & 0.926 & 0.297 \\ 
+      & Naive          &   0.033 & 0.059 & 0.068 & 0.835 & 0.194 \\  
     \bottomrule
@@
 AMSE-optimal bandwidths proposed by CCT, the uniform kernel, and the HC3 wild
-bootstrap from \citet{DF08} with Mammen's (1993) two-point distribution
-on $e^*_i$; see Equations~\eqref{eq:14} and~\eqref{eq:15} of
-this paper and their surrounding remarks as well as Equation~(\ref{eq:19}) for
-formal definitions. In the bootstrap
+bootstrap from \citet{DF08}. In the bootstrap
 procedure, we use 500 bootstraps for bias correction and 999 to calculate the
@@
   \Psi_{\bullet,p} &= \int_{-\infty}^\infty
-     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du.
+     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
 \end{align*}
@@
   \tfrac{hb}{m} \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
-  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1). \label{eq:12}
+  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
 \end{align}

### 2016-08-25 main_paper.tex

--- 2016-08-25 main_paper.tex
@@
   at \protect\url{https://github.com/grayclhn/boot-rd}. We would like to
-  thank Matias Cattaneo, Juan Carlos Escanciano, seminar participants at
+  thank Matias Cattaneo, Juan Carlos Escanciano, Sebastian Calonico, Max Farrell, Helle Bunzel, Brent Kreider, Quentin Brummet, seminar participants at
   the Advances in Econometrics conference on Regression Discontinuity
-  Designs, and especially the two anonymous referees for helpful and
-  substantive help and advice on earlier versions of this paper.}}
+  Designs, Third Annual Conference of the International Association for Applied Econometrics,
+ 2016 North American Summer Meeting of the Econometric Society and the $69^{th}$ European Meeting of the Econometric Society, and especially the two anonymous referees for
+  substantial help and advice on earlier versions of this paper.}}
 

### 2016-08-25 reply_2/cover_letter.tex

--- 2016-08-19 reply_2/cover_letter.tex
@@
 
+Regarding referee 1's comments,
+\begin{itemize}
+\item (placeholder)
+\end{itemize}
+Regarding referee 2's comments.
+\begin{itemize}
+\item (placeholder)
+\end{itemize}
+We have also made the small notational changes and new definitions
+the referees requested.
+
+In addition, we discovered a small error in the simulation results ---
+instead of reporting each estimator's bias, we reported the negative
+bias. Since the values were close to zero, this does not have a
+substantive effect on the results but we have, of course, fixed the
+tables.
+
 \noindent%

### 2016-08-25 main_paper.tex

@@
 \begin{equation}
+  \label{eq:18}
+  \Delta^*(h,b) = h^{2} \Big[\tfrac{\hat{\mu}_{+}^{(2)}(b)}{2} \Bf_{+}(h)
+  - \tfrac{\hat{\mu}_{-}^{(2)}(b)}{2}\Bf_{-}(h) \Big]
+\end{equation}
+almost surely and
+\begin{equation}
   \label{eq:4}

### 2016-08-25 reply_2/cover_letter.tex

--- 2016-08-24 reply_2/cover_letter.tex
@@
 \begin{itemize}
-\item (placeholder)
+\item The first comment pointed out that our bandwidth assumption was
+  unnecessarily strong; we have relaxed it as suggested.
+\item The referee's third comment alerted us to an error in the order
+  of the variance of the bias-corrected estimator that was implicit in
+  the statement of Theorem 2. We have fixed this error by explicitly
+  dividing by the estimator's standard deviation in the statement of
+  the theorem. We have also been more careful in how we apply these
+  scale factors in the proof and have rewritten the last half-page
+  of the proof to rescale several summations individually instead of
+  \textit{en masse}, which fixes our initial errors.
 \end{itemize}

### 2016-08-29 reply_2/cover_letter.tex
Add reference to 'diffs' file in cover letter

@@
 \strut
+
+We have made the requested changes and have tried to address each of
+the points raised by the referees.
 
@@
 
+Finally, to make it easier to see the changes in this version of the
+paper, we have attached a second copy of the paper that highlights the
+specific differences from the previous version. (Blue text has been
+added since the last version; red indicates deleted text.)
+
+Thanks again for giving us this opportunity.
+
 \noindent%

### 2016-08-29 main_paper.tex
Fix duplicate equation references in Theorem 2
Includes thanks to several other people.

--- 2016-08-25 main_paper.tex
@@
   Designs, Third Annual Conference of the International Association for Applied Econometrics,
- 2016 North American Summer Meeting of the Econometric Society and the $69^{th}$ European Meeting of the Econometric Society, and especially the two anonymous referees for
-  substantial help and advice on earlier versions of this paper.}}
+ 2016 North American Summer Meeting of the Econometric Society and the $69^{th}$ European Meeting of the Econometric Society, and especially the two anonymous referees for   substantive help and advice on earlier versions of this paper.}}
 
@@
     \begin{align*}
-      (\hat\beta_{-,0}, \hat\beta_{-,1}, \hat\beta_{-,2})' &=
-      \argmin_{\beta_0, \beta_1, \beta_2}
-      \sum_{i = 1}^n (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{-,b}(X_{i}) \\
-      (\hat\beta_{+,0}, \hat\beta_{+,1}, \hat\beta_{+,2})' &= \argmin_{\beta_0, \beta_1, \beta_2}
-      \sum_{i = 1}^n (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{+,b}(X_{i}).
+      \hat\beta_{-} &= \argmin_\beta \sum_{i = 1}^n
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{-,b}(X_{i}) \\
+      \hat\beta_{+} &= \argmin_\beta \sum_{i = 1}^n
+      (Y_i - \beta_0 - \beta_1 X_i - \beta_2 X_i^2)^{2} K_{+,b}(X_{i}).
     \end{align*}

### 2016-08-29 R/rdfunctions_ForMc.R
Fix #23 HC1 adjustment
Now use the sum of weights to replace n.

@@ -153,14 +153,16 @@ rdboot_ForMc <- function(y, x, a = 0.05, Nbc = 500, Nci = 999, p = 1, q = 2,
   
   e.ql.adj <- switch (residual,
                       HC0 = 1,
-                      HC1 = sqrt(length(yql)/(length(yql) - q - 1)),
+                      HC1 = sqrt(sum(kweight(xql, 0, b, kernel))/
+                                   (sum(kweight(xql, 0, b, kernel)) - q - 1)),
                       HC2 = 1/sqrt(1 - hl),
                       HC3 = 1/(1 - hl)
   )
   
   e.qr.adj <- switch (residual,
                       HC0 = 1,
-                      HC1 = sqrt(length(yqr)/(length(yqr) - q - 1)),
+                      HC1 = sqrt(sum(kweight(xqr, 0, b, kernel))/
+                                   (sum(kweight(xqr, 0, b, kernel)) - q - 1)),
                       HC2 = 1/sqrt(1 - hr),
                       HC3 = 1/(1 - hr)
   )

### 2016-08-29 main_paper.tex
Tweak wording in 'thanks'

@@
   Designs, Third Annual Conference of the International Association for Applied Econometrics,
- 2016 North American Summer Meeting of the Econometric Society and the $69^{th}$ European Meeting of the Econometric Society, and especially the two anonymous referees for   substantive help and advice on earlier versions of this paper.}}
+ 2016 North American Summer Meeting of the Econometric Society and the $69^{th}$ European Meeting of the Econometric Society, and especially the two anonymous referees for
+  substantial help and advice on earlier versions of this paper.}}
 

### 2016-08-30 main_paper.tex
[WIP] Fix error at end of Theorem 2 proof
Closes #25.
Fix a typo in Assumption 2
We accidentally deleted the limit. This commit add the limit "0".

--- 2016-08-25 main_paper.tex
@@
   $n h \to \infty$, $n b \to \infty$, and
-  $n \times \min(h, b)^{5} \times \max(h, b)^2$ as $n \to \infty$.\footnote{%
+  $n \times \min(h, b)^{5} \times \max(h, b)^2 \to 0$ as $n \to \infty$.\footnote{%
     Unless otherwise stated, all limits in this paper are assumed to hold as
@@
 \begin{equation}\label{eq:17}
-  (\tfrac{m}{n})^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
+  \big(\tfrac{1}{n}\big)^{1+\delta/2} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
   \hat\varepsilon_i \rvert^{2+\delta} \to^{p} 0.
@@
 \begin{equation*}
-  R_\bullet(X_i) = \gamma_1' r_1(X_i/h) K_{\bullet,h}(X_i) +
-  (h/b)^2 \cdot \gamma_2' r_2(X_i/b) K_{\bullet,b}(X_i)
+  R_\bullet(X_i) = h^{1/2} \cdot \gamma_1' r_1(X_i/h) K_{\bullet,h}(X_i)
+  + b^{1/2} \cdot \gamma_2' r_2(X_i/b) K_{\bullet,b}(X_i)
 \end{equation*}
@@
 that
-\begin{equation}\label{eq:17}
-  \tfrac{1}{n} \sum_{i} m^{1+\delta} \lvert (R_+(X_i) - R_-(X_i))
-  \hat\varepsilon_i \rvert^{2+\delta}.
+\begin{equation}\label{eq:16}
+  \tfrac{1}{n} \sum_{i} \lvert (R_+(X_i) - R_-(X_i))
+  \hat\varepsilon_i \rvert^{2+\delta}
+  = O_p(h^{-\delta/2}) + O_p(b^{-\delta/2}).
 \end{equation}
-obeys the LLN, implying that~\eqref{eq:17} holds and completing the proof. \qed
+Since $nb \to \infty$ and $n h \to \infty$ by
+assumption,~\eqref{eq:16} implies that~\eqref{eq:17} holds and
+completes the proof. \qed
 

### 2016-08-31 main_paper.tex
[#26] update rdrobust citations
Closes #26

@@
   The simulations and empirical analysis were carried out in the R programming
-  language \citep{R} and rely on the \textit{rdrobust} \citep{rdrobust},
+  language \citep{R} and rely on the \textit{rdrobust}
+  \citep{rdrobust2,rdrobust3},
   \textit{doParallel}, \textit{foreach} \citep{doparallel,foreach}, and

### 2016-09-01 main_paper.tex
Add sentence about CCF.

@@
 estimator. The resulting confidence intervals have accurate coverage even when
-the naive RD interval does not.
+the naive RD interval does not. Furthermore, after analyzing higher-order properties
+of procedures based on analytical bias correction relative to the usual undersmothing approach, \cite{CCF15} argue that explicit bias-correction
+ coupled with an analytical adjustment to the standard errors ``yields confidence intervals 
+with coverage that is accurate, or better, than the best possible undersmoothing approach'' \citep[p.~2]{CCF15}, 
+and provide bandwidth choice procedures which are ``coverage-error optimal.''
 

### 2016-09-02 main_paper.tex
Changes in the discussion of CCF

--- 2016-08-31 main_paper.tex
@@
 estimator. The resulting confidence intervals have accurate coverage even when
-the naive RD interval does not.
+the naive RD interval does not. Furthermore, \cite{CCF15} analyzes properties of
+the proposed bias-corrected studentized statistics based on a fixed-$n$ calculation
+ for standard errors and demonstrates through higher-order expansions that confidence intervals based on these
+ statistics achieve superior coverage-error order relative to undersmoothing.
+Additionally, they provide bandwidth choice procedures which are ``coverage-error optimal.''
 

### 2016-09-02 main_paper.tex
mistake in the sentence about CCF

--- 2016-08-31 main_paper.tex
@@
 estimator. The resulting confidence intervals have accurate coverage even when
-the naive RD interval does not.
+the naive RD interval does not. Furthermore, \cite{CCF15} analyzes properties of
+the proposed bias-corrected studentized statistics based on a fixed-$n$ calculation
+ for standard errors and demonstrates through higher-order expansions that confidence intervals based on these
+ statistics achieve superior coverage-error convergence rates relative to undersmoothing.
+Additionally, they provide bandwidth choice procedures which are ``coverage-error optimal.''
 

### 2016-09-05 main_paper.tex
[#27] Rewrite statement about higher-order refinements in rdrobust

--- 2016-09-02 main_paper.tex
@@
 estimator. The resulting confidence intervals have accurate coverage even when
-the naive RD interval does not. Furthermore, \cite{CCF15} analyzes properties of
-the proposed bias-corrected studentized statistics based on a fixed-$n$ calculation
- for standard errors and demonstrates through higher-order expansions that confidence intervals based on these
- statistics achieve superior coverage-error order relative to undersmoothing.
-Additionally, they provide bandwidth choice procedures which are ``coverage-error optimal.''
+the naive RD interval does not.
+Furthermore, as shown by \citet{CCF15}, these intervals can achieve faster
+convergence rates than previously believed, outperforming intervals produced
+by undersmoothing in some settings while maintaining grater robustness to
+the choice of bandwidth parameter. Previous research by \citet{Hall93} and
+\citet{Neumann97} has found that undersmoothing outperforms naive
+bias-corrected confidence intervals, but \citet{CCF15} show that the naive
+variance estimator implicitly requires more restrictions than CCT's
+expression and those restrictions artificially limit the intervals'
+performance.
 

### 2016-09-05 main_paper.tex
Typo on paragraph on CCF.

@@
 convergence rates than previously believed, outperforming intervals produced
-by undersmoothing in some settings while maintaining grater robustness to
+by undersmoothing in some settings while maintaining greater robustness to
 the choice of bandwidth parameter. Previous research by \citet{Hall93} and

### 2016-09-06 main_paper.tex
Fix weird grammar error in Section 2
Not sure what that last sentence in Section 2 meant to communicate, but it
wasn't pulling it off. I deleted the sentence.

@@
 
-In the next section, we build upon the insight provided by CCT bias-corrected
-estimator and propose a simple bootstrap procedure that can directly construct
+In the next section, we build upon the insight provided by CCT's bias-corrected
+interval and propose a simple bootstrap procedure that can directly construct
 the robust CIs without requiring the derivation of analytical formulas and
 direct estimators for the bias, variance and covariance terms, while relying on
-the same first-order bias correction approximation. Assumption~\ref{A2}
-requirements are identical to CCT.
+the same first-order bias correction approximation.
 
